### 2019-09-16 Aggregation_MIP.tex
First commit for latex repo

\documentclass[11pt]{amsart}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}

\title{A Study of Convective Aggregation}
\author{Levi G. Silvers}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}
\section{Introduction}

Interest in convective self-aggregation has steadily grown over the past 20 years since the initial hints (Held et al. 1993) that simulations of radiative convective equilibrium with interactive clouds systems had a tendency to settle into a conglomerate state of strong convection.  Many questions about this final and seamingly steady state have been raised and few of them satisfactorily answered.  Initially it was unclear if the aggregation was simply a numerical artifact of the idealised experimental configuration.  Many studies have attempted, with some success, to determine what physical mechanisms are responsible for the aggregation.  Interest is now turning to the question of how convective aggregation applies to or is relevant for our understanding of the convective systems we observe.  Due to the idealised experimental configuration, comparison with and inferences based on observations are not trivial.  
\begin{itemize}
  \item{Do models with nearly identical initial and boundary conditions equilibrate to the same state?}
  \item{Are there clear factors that the convective aggregation depends on?}  \huge{ 28\degree}
\end{itemize}

\section{Experimental Configuration}

\begin{itemize}
  \item{Radiative Convective Equilibrium: No land, rotation, diurnal cycle, or horizontal gradients of ozone.}
  \item{Large Domain $3.2 \times 10^6 km^2 \approx 10 \times$ Area of Germany}
  \item{Constant Sea Surface Temperature (SST) =301K}
  \item{Horizontally homogeneous initial conditions, $\theta$ initially perturbed by 0.1K on lowest 3 model levels.}
  \item{All 3 models use same size of domain, SST, zenith angle, and incoming solar insolation.}
  \item{The UCLA model has a different ozone profile and thus the tropopause is lower then in the ICON models.}
\end{itemize}

\section{Results}

The evolution of the Outgoing Longwave Radiation (OLR) and latent heat flux show that the three models are close to equilibrium after 50-80 of simulation.  The individual models adjust at different rates, and all show significant amounts of variability about their mean states.  Note that all three models have fluctuations of between 5-10 $W/m^2$ in their OLR.  Although the two ICON models have identical dynamics, the parameterised physics are quite different, and the resolution is dramatically different.  Considering these differences and the large difference in the energetic state as given by the the latent heat flux/domain mean precipitation it level of agreement between the models with the evolution of OLR is interesting.

Because the boundary conditions and forcing are homogeneous across the domains the basic characteristics of the simulated atmospheres can be seen by looking at the domain mean profiles of meaningful variables.  Examining the mean profiles reveals interesting similarities and differences between the simulations.  These profiles are shown for the end period of each models simulations in Figs. (\ref{fig:vprof}-\ref{fig:vprof_zoom}).   Of particular note are the following points: 
\begin{itemize}
  \item{All models have very dry tropospheres}
  \item{The high resolution ICON model is several degrees colder then the other two models, and has much more upper level cloud cover.}
  \item{The two high resolution models are quite similar in the lowest 2 km, and distinct from the nwp ICON model.}
  \item{UCLA has essentially zero ice, while the two ICON models have comparable quantities of ice.}
\end{itemize}
The structure of the atmospheric boundary layer is known to be critical to the development of deep convection and the response to radiative forcing.  It is therefore expected that differences between the models in the lowest kilometres will have a significant role in the overall behaviour and structure of the atmospheres.  The structure of the lowest 2 $km$ can be more clearly seen in Fig. (\ref{fig:vprof_zoom}).  All models have different heights and strengths of the inversion level as seen in the domain mean temperature.  This results in differing heights for the maximum of low-level cloud cover and cloud liquid water.  Although the models all have an identical fixed surface temperature of 301K, the lowest model level in the atmosphere, equilibrates to different values for each of the models.  Thus we see that the ICON NWP model has the highest temperature in the first model level, followed by the UCLA LES, and then the ICON LES.  The UCLA LES has a relatively low inversion (0.6-0.8 $km$) and the largest maximum in cloud cover and cloud liquid water.  Although the ICON LES has a higher inversion (1.0-1.4 $km$) level, cloud cover maximum, and cloud liquid water maximum than the UCLA LES these two models show a low-level atmospheric structure that is quite similar.  In contrast, the ICON NWP model can barely be said to have an inversion layer and the low-level cloud cover and cloud liquid water are spread out over a much deeper region of the lower troposphere than the other two models.

An obvious advantage of high resolution models is their ability to resolve smaller scale motions.  The mean vertical motion of a region which is 200 $km^2$ will obviously have a much smaller range of values than the mean of a region which is 10 $km^2$.  We see this clearly illustrated in Fig. \ref{fig:wpdf} where ICON NWP is shown to have a dramatically different distribution of values for the vertical velocity.

\begin{figure}[!htb]
   \centering
   \begin{minipage}{0.45\linewidth}
     \includegraphics[width=3.4in]{agg_figs/latheat_3mods_iconuclales_180days.eps}
   \end{minipage}
   \begin{minipage}{0.45\textwidth} %  figure placement: here, top, bottom, or page
     \includegraphics[width=3.4in]{agg_figs/olr_3mods_tseries.eps}
   \end{minipage}
  \caption{Evolution in time of the latent heat flux. ($W/m^2$) (left).  Evolution in time of the outgoing longwave radiation ($W/m^2$) (right)}
  \label{fig:olr_latht}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
       \includegraphics[width=6.5in]{agg_figs/vprof_3mods_final.eps}
   \caption{Domain mean profiles averaged over the last period of each models integration.}
   \label{fig:vprof}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
       \includegraphics[width=6.5in]{agg_figs/vprof_3mods_final_zoom.eps}
   \caption{Domain mean profiles averaged over the last period of each models integration.  Zoomed in on the lowest 5km}
   \label{fig:vprof_zoom}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
       \includegraphics[width=3.in]{agg_figs/w_pdf_3mods_12dnwp.eps}
   \caption{Domain mean profiles averaged over the last period of each models integration.  Zoomed in on the lowest 5km}
   \label{fig:wpdf}
\end{figure}

\begin{figure}[!htb]
   \centering
   \begin{minipage}{0.45\linewidth}
     \includegraphics[width=3.4in]{agg_figs/rce_ecs_20km_301_3M_nwp_wolr.eps}
   \end{minipage}
   \begin{minipage}{0.45\textwidth} %  figure placement: here, top, bottom, or page
     \includegraphics[width=3.4in]{agg_figs/rce_ecs_20km_301_3M_iconles_wolr.eps}
   \end{minipage}
  \caption{Outgoing Longwave Radiation at model top for ICON NWP with vertical velocity greater than 0.1 m/s from mid troposphere overplayed in contours (left).  On the right is the same plot as on left except for ICON LES.}
  \label{fig:olr_latht}
\end{figure}

\begin{figure}[!htb]
   \centering
   \begin{minipage}{0.45\linewidth}
     \includegraphics[width=3.4in]{agg_figs/rce_ecs_20km_301_3M_ucla_wwvp.eps}
   \end{minipage}
   \begin{minipage}{0.45\textwidth} %  figure placement: here, top, bottom, or page
     %\includegraphics[width=3.4in]{agg_figs/rce_ecs_20km_301_3M_ucla_wolr.eps}
     \includegraphics[width=3.4in]{agg_figs/rce_ecs_20km_301_3M_ucla_wwvp.eps}
   \end{minipage}
  \caption{Outgoing Longwave Radiation at model top for ICON NWP with vertical velocity greater than 0.1 m/s from mid troposphere overplayed in contours (left).  On the right is the same plot as on left except for ICON LES.}
  \label{fig:olr_latht}
\end{figure}

\subsection{Measures of Aggregation}

Thus far the phenomena of convective aggregation has been poorly defined and often recognised simply along the lines of, "you know it when you see it."  However, there are clear characteristics that have been consistently associated with aggregation in the previous literature.  These include a visual confirmation of the convective structures forming a conglomerate (often) single mass with the rest of the domain being nearly free of convection, an abnormally dry troposphere (Bretherton et al. 2005), a transition to a higher value of OLR (Wing and Emanuel 2014), and in a loose sense a large subsidence fraction.   Upgradient flux of MSE?

The two high resolution models agree very well in their subsidence fractions.  This subsidence fraction however is much lower than that of the ICON NWP model.  It appears that despite a high degree of convective clustering, the high resolution models have a large amount of very weak vertical motions throughout the domain which drives down the value of the subsidence fraction.  In this situation then the subsidence fraction does not appear to be a particularly informative measure of the degree to which a simulation has aggregated.

Allison Wing recently stated that convective aggregation is, "A spontaneous transition from randomly distributed to organised convection despite homogeneous boundary conditions".  The use here of the word spontaneous is unclear and probably not necessary to aggregation.  It seems possible that a system which does have homogeneous boundary conditions could also aggregate.  One of the dominant mechanisms of convective aggregation seems to be that once the aggregation occurs, the system remains in that state.  We do not have examples of the convection breaking up.  It is hard to imagine a proof of this permanence but based on the previous literature it does seem likely.

\section{Conclusions}

\begin{itemize}
  \item{Similar Characteristics between the models}
  \item{Different Characteristics between the models}
\end{itemize}

\end{document}

### 2019-09-16 Popp_Silvers_2017_1page.tex
First commit for latex repo

\documentclass[11pt]{amsart}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}

\title{Double and Single ITCZs with and without Clouds}
\author{Max Popp and Levi G. Silvers}
%\date{2016}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

\section{Abstract}
A major bias in tropical precipitation over the Pacific in climate simulations stems from the models' tendency to produce two strong distinct intertropical convergence zones (ITCZs) too often. Several mechanisms have been proposed that may contribute to the emergence of two ITCZs, but current theories cannot fully explain the bias. This problem is tackled by investigating how the interaction between atmospheric cloud- radiative effects (ACREs) and the large-scale circulation influences the ITCZ position in an atmospheric general circulation model. Simulations are performed in an idealized aquaplanet setup and the longwave and shortwave ACREs are turned off individually or jointly. The low-level moist static energy (MSE) is shown to be a good predictor of the ITCZ position. Therefore, a mechanism is proposed that explains the changes in MSE and thus ITCZ position due to ACREs consistently across simulations. The mechanism implies that the ITCZ moves equatorward if the Hadley circulation strengthens because of the increased upgradient advection of low-level MSE off the equator. The longwave ACRE increases the meridional heating gradient in the tropics and as a response the Hadley circulation strengthens and the ITCZ moves equatorward. The shortwave ACRE has the opposite effect. The total ACRE pulls the ITCZ equatorward. This mechanism is discussed in other frameworks involving convective available potential energy, gross moist stability, and the energy flux equator. It is thus shown that the response of the large-scale circulation to the shortwave and longwave ACREs is a fundamental driver of changes in the ITCZ position.

\section{Key Points}
\begin{itemize}
  \item{Experiments investigate how the location of the ITCZ depends on the interaction between ACREs and the large-scale circulation}
  \item{Low-level moist static energy is shown to be a good predictor of the ITCZ position}
  \item{Longwave cloud radiative effects drive the ITCZ equatorward while shortwave cloud radiative effects drive it poleward}  
\end{itemize}

\begin{figure}
  \centering 
    \includegraphics[width=2.5in]{poppsilvers_fig1.jpg}
   \caption{Zonal-mean quantities in steady state: (a) the total (convective + large-scale) precipitation, (b) the vertically integrated total (liquid + frozen) water path, (c) the atmospheric energy uptake, and (d) the ACRE. Colors represent the individual experiments ACREoff (black), ACREonLW (red), ACREonSW (blue), and ACREon (orange). The filled circles show the global and the crossed circles the tropical means (from 30°S to 30°N) of precipitation in (a). The horizontal location of the dots is only for visual separation and does not have any particular meaning. Note that the horizontal axes are scaled with the cosine of the latitude.}
   \label{fig:lambdaecs}
\end{figure}

\end{document}

### 2019-09-16 Silvers_WalkerCell.tex
First commit for latex repo

\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{epstopdf}
%\usepackage{pdflatex}
%\usepackage{epsfig}

			% Activate to display a given date or no date
%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\title{Clouds and Radiation in a mock-Walker Circulation}
\author{Levi G. Silvers, Nadir Jeevanjee, and Thomas Robinson}

\begin{document}
\maketitle

\begin{abstract}

% What are climate modelers doing to reduce uncertainties about cloud processes?
The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an idealized equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, non-precipitating clouds with a dry atmosphere above the clouds.  These regions are connected by a large-scale circulation.  We analyze this scenario in a high-resolution and coarse resolution simulation and infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth?s sensitivity to changes in greenhouse gas concentrations.

A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
resolution (25km, 100km) configured 
as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By dramatically decreasing the grid-spacing we resolve much more of the dynamical motion and eliminate some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.

\end{abstract}

%\section{Key Questions}

\textbf{Key Points}
\begin{itemize}
  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
  maximum.}
  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
  changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 30\% higher than for the coarser cases with parameterized convection.}
  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
\end{itemize}

\section{Introduction}

%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.  If an advance in our understanding of the role clouds play in our climate is desired, it is essential that we 
%learn to model the two way interaction between clouds and the circulation.  The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation (imp of lwcre off).  
%Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation connects regions of deep convective activity with the prevalent tropical shallow 
%convection and the radiatively critical stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and the Coriolis force is 
%critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we propose that all of the physics of importance to our particular questions are present 
%in the equatorial manifestation of the Walker circulation (perhaps better in conclusion).  
%
%Current computing capabilities cannot come close to resolving all of the spatial scales which are important in the lifetime of clouds.  
%As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be informed by the solution of the high resolution model.  This approach will help to demonstrate that the influence of clouds on climate is not an intractable problem.
%
%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between radiation and clouds, as well as dynamical motions which range from
%sub-kilometer scales to roughly 10,000 km.     In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and stratocumulus clouds, the tropical 
%Pacific provides an ideal physical context with which to explore the sensitivities and strengths of theoretical models, high-resolution models and general circulation models.  
%The tropical system in the Pacific Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface temperature gradients 
%represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic circulations.
%This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation and how the nonlinear interactions within the system contribute 
%to the cloud feedbacks to perturbations and the overall sensitivity of the system to anthropogenic forcing.
%
%Several studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012) have examined a 
%mock Walker circulation in the context of cloud resolving 
%simulations, or idealized theoretical models.   The comparison between CRMs and simple theory revealed several important 
%similarities (like what? See Bretherton et al., 2006) and a multiplicity of differing results (like what) for different CRM studies. 
%It thus remains unclear what GCM like models should be expected to produce in similar configurations.  
%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified SST. (just before equation 8 of Bretherton et al. 2006)."

%The atmosphere of Earth constantly radiates energy to space.  This cooling of the atmosphere is mostly balanced by warming from the release of latent energy by convective clouds and precipitation.  The details of this balance between cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.  However, clouds contribute to both warming and cooling of the atmosphere.  Deep convective storms and high clouds warm the atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the atmosphere by reflecting the incoming radiation from the sun.  Previous research has repeatedly shown that low-level clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ concentration (Bony and Dufresne, 2005, Sherwood et al. 2014).  However, it has also been shown that the turbulent mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate sensitivity (Zhao, 2014).  The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
%
%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and Emanual, 2014 have shown that idealized models are quite 
%sensitive to the details of the configuration such as domain size and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the purpose of this paper is to use one modeling framework to
%illustrate just what is obtained from a coarse GCM-like model run with idealized boundary conditions.  We then use this modeling framework to compare the results obtained from simulations
%with a resolution of 100, 25, 2, and 1km.
%
%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system the idealization 
%is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, as compared to the observed 
%world.  These simulations are somewhere in the middle of those extremes.  We have decided to keep many of the complex elements of 
%the global climate model  so that we can hopefully better understand the parent model (AM4.0) while learning something concrete about 
%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke large-scale 
%cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
%model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
%understanding and to illuminate some of the idiosyncrasies of the climate models that are currently looked to for information about the 
%future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
%a simple design that incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.
%
%Our simulations are based on the equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures exist beneath rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low level, non-precipitation clouds with a very dry atmosphere above the clouds.  These regions are connected by a large-scale circulation of winds.  By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
%
%Inevitable limitations in computing power necessitate climate studies with Earth-system models to use relatively coarse grid-spacing.  
%%Coarse, statistical Earth-system models which simulate long periods of the climate are necessitated by the limitations of current computers.  
%This research uses a high-resolution cloud-resolving model on a limited spatial domain as a benchmark to compare with the same 
%model at lower resolution configured as a fully 
%parameterized general circulation model.   The modeling approach presented here, made unique by its clean connection between a global climate 
%model and a regional cloud resolving model is  made possible by the flexible modeling system at GFDL.   The goal of this paper is to use this 
%capability to better quantify and understand the connection between tropical convective heating and changes in low clouds.

\textbf{Key Questions}
\begin{itemize}
  \item{How do clouds influence the Walker Circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds in the Walker Cell coupled?}
  \item{When simulating the Walker Circulation, how well does a GCM compare to a CRM?}  
\end{itemize}

\section{Experimental Details and Methods}

To develop the model configuration used for these experiments we started with the same code base as that of the AM4.0 
model (Zhao et al. a,b).  This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations.  Taking 
the AM4.0 physics we use the interactive radiation, deep and shallow convection, large-scale clouds, and boundary layer 
scheme as described in Zhao et al. a,b and the references therein.  The prognostic moisture variables are the specific 
humidity (q), liquid (ql) and frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
8 model levels.  The changes made to the default AM4.0 physics configuration are the following.  The cloud-aerosol 
interactions were turned off to focus on the interaction between clouds, radiation, and the circulation.  The gravity wave drag 
parameterization was turned off 
%(do_cg_drag set to .f.; Alexander-Dunkerton gravity wave drag) 
in order to reduce large oscillations in the horizontal wind field in the top of the model domain.  The convection, radiation, 
large-scale cloud, microphysics, and turbulence parameterization all remain the same as in AM4.0.  
Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the physics are very 
similar to those of AM4.0.  This configuration can also be compared to the simulations described in 
Popp and Silvers, 2017, which used a developmental version of AM4 with almost the same changes to the physics
schemes.
For our simulations using grid spacing of 1km, 2km, and 25km (in select simulations), the double plume (both shallow and deep convection) convective parameterization was 
turned off and the time step of integration increased.

\begin{table}
\begin{center}
\caption{A few specifications of the simulations used most heavily in this study.  The precipitation values in parenthesis are for the experiments
in which LWCRE is off.}
    \begin{tabular}{*{6}{c}}
    \hline
    \hline
 Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection & Precip $(\mathrm{mm/day})$   \\ \hline
  P100 &  100          &   800 $\times$ 16000    &  60              & parameterized           &  4.1 (3.5)          \\ 
    \\
  P100 &  100                & 800 $\times$ 4000     & 60            & parameterized         & 3.9                \\  
    \\
  P25 &  25             & 200 $\times$ 16000      & 60             & parameterized          & 4.0 (3.8)                \\  
    \\
  P25  &  25             & 200 $\times$ 4000      & 60             & parameterized           & 3.84 (3.66)               \\  
    \\
 E25  &   25          & 200 $\times$ 4000      & 60             & explicit          & 3.74 (3.46)               \\  
    \\
 E2   &   2          & 100 $\times$ 4000      & 6             & explicit          & 3.11 (3.50)                \\ 
    \\
 E1   &   1          & 10 $\times$ 4000      & 6             & explicit          & 3.36 (3.74)                \\  \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:lambda}
\end{center}
\end{table}

All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
direction allowing for three dimensional simulations but with a reduced computational cost relative to the global domain which is usually 
used with this model.  The SST is prescribed as a Gaussian function which is 4K warmer in the center (301K/27.85C) of the domain then at the edges (297K/23.85C).  
Thus far the GCM runs with 25km resolution have been run for 5 year.  
The 1km and 2km CRM were run for 6 months.

The simulations with a grid-spacing of 1km and 2km are referred to as cloud resolving simulations.  For our purposes this simply means
that both deep and shallow convective parameterizations are turned off, and that the threshold of grid-cell mean relative humidity 
which triggers new clouds is changed from the default value of 0.8 to 1.0.   The Tiedtke (1993) parameterization scheme for large-scale 
clouds was designed to be used with GCMs having a coarse grid-spacing.  However, there is not a fundamental problem that we are 
aware of in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   The advantage is retaining the 
identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the cloud computations 
relative to many other cloud resolving models.

One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the 
radiation.  This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.   This method was originally pioneered by Slingo and Slingo, 1988 and Randall et al., 1989.  More recently, it has been
implemented as part of the CFMIP series of experiments (Stevens et al. 2012).
In the AM4 code, this is done separately for the longwave and shortwave radiation.  In this study we compare control experiments, 
in which clouds and radiation are fully interactive with experiments in which clouds are
invisible to the longwave radiation.  These experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE off).  
Other than the invisible clouds, the model is the same.  Both longwave and shortwave radiation are present and interactive with 
the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
In general, turning off the longwave cloud radiative effect will have a large impact on the surface budget of a coupled model.  
However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
strongly effected as might be expected.  Experiments with only a water surface at the lower boundary and fixed SST are the
ideal configuration to utilize the LWCRE off experiments.

\section{Results}

The results of our experiments are organized as follows.  First, the general structure and characteristics of the steady state solutions
will be described.   Then, the influence of parameterized convection and the longwave cloud radiative effect on the overturning 
circulation will be shown.  We will then briefly discuss how the circulation changes as a function of domain size.  The last part of the
results will describe and contrast the Walker circulation in a GCM-like configuration and a CRM-like configuration.

The mock-Walker Circulation that emerges from these simulations is a deep overturning circulation.  There are two circulation cells, 
one below $500 \rm{hPa}$  and one above.  Deep-convective activity dominates the region over the warm pool, shallow convection is 
common over a wider range of SSTs, and for the most part stratocumulus 
clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, the atmospheric 
state is much more symmetric about the maximum SST.

We perform a series of sensitivity experiments to highlight the different ways in which these experiments can equilibrate.  To show the sensitive 
nature of the distribution of the precipitation maximum we test the impact of convective parameterization, 
longwave radiation interactions with clouds, domain size, 
and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
because of the sensitivity of the low-level clouds to the longwave radiative cooling.

%%%%%
% section 3.1 results
\begin{figure}
  \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan.eps}
      \caption{Comparison of the steady state relative humidity (shading of top panels) and mass 
      streamfunction (contours) for the experiments
      with a grid-spacing of 25km.  The lower panels show total (liquid + ice) condensates (g/kg).  
      An experiment with fully parameterized convection (P25) is on the left, the same 
      experiment but with the LWCRE off is in the center panel, and the experiment with LWCRE on, but the convective
      parameterization turned off is on the right.  All three panels use the same contour interval for the mass 
      streamfunction (kg/s).}
  \label{fig:rh_psi_P25vsE25}
\end{figure}

We find large differences among the experiments in the domain mean precipitation, condensate/clouds, and circulation.  In particular
the experiments with parameterized convection are much more erratic.  Above about 500 \textit{m} the P25 experiment
has strong domain mean wind shear that clearly influences the structure of the precipitation, as seen in 
five year Hovmoller diagrams.  The degree to which this shear influences the comparison with other experiments is unclear.

"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
greater are being dominated by this second factor.

\subsection{The Asymmetric Influence of Convective Parameterization and the organizing tendency of LWCRE}

% LWCRE has a large impact on LS precip, not so much on convection
% LWCRE has a large impact on the low-level circulation (circulation is stronger when LWCRE is on)
% Are the low-level clouds a connecting point?

% are the impacts of the LWCRE the same for GCMs as they are for CRMs?

% Vertical Velocity and time averaged precipitation
\begin{figure}
  \centering
      \includegraphics[width=0.6\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
  \caption{Precipitation (top) and vertical velocity (bottom) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
  The data has been averaged over the short horizontal dimension of the channel and over the 
  equilibrated part of the experiments.  Control configurations with normal model physics are on the 
  left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
  off (LWCRE off).}
  \label{fig:precip_vertvel}
\end{figure}
%
% below shows that the circulation extremes decrease when the lw cre is switched off.  the case with a 
% grid-spacing of 25 km shows the largest difference 
%
%% max/min values for the stream function with lwcre off:
%(0)	max/min of psiplot ensind  is: 0.3477345977293868 and: -0.2115510906212598   diff = 0.56
%(0)	max/min of psiplot1 is: 0.3195050101301776 and: -0.2795603759630235             diff = 0.60
%(0)	max/min of psiplot2 is: 0.3551683771471268 and: -0.3245916357825396             diff = 0.68
%
%% max/min values for the stream function with lwcre on:
%(0)	max/min of psiplot ensind  is: 0.1346705118433919 and: -0.6774837967222883    diff = 0.81
%(0)	max/min of psiplot1 is: 0.301707822836468 and: -0.3661587052771586                diff = 0.67
%(0)	max/min of psiplot2 is: 0.4634904466711686 and: -0.3170573366946793               diff = 0.78

To illustrate how the double plume convective parameterization influences the atmospheric state we compare the P25 and
E25 simulations in which the only difference is that all convective parameterization is turned off in E25 (refer to a figure with
profiles for E25 and P25).  The P25 experiment represents a GCM-like configuration and compared to E25 has a stronger 
overturning circulation, higher humidity in the deep convective region, and lower humidity in the subsidence region over the 
cooler SST (Figure \ref{fig:rh_psi_P25vsE25}).  Averaged over the full domain, the parameterized convection leads to a 
dryer atmosphere with less 
condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  However, in 
the updraft region the convective parameterization results in more moisture aloft.

One of the most prominent features of our 25km grid-spacing simulations is an asymmetry in both the time-dependent and 
steady-state solutions.  This results in the steady-state precipitation maximum locating off the maximum in SST and is apparent in 
the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.   A tendency of the precipitation to 
occur off of the SST maximum is also apparent in the simulations with a grid-spacing of 100km, although the 25km simulations display 
an irregularity that is greater than the 100km simulations.  Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
distribution has been noted many times 
(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
tended to be symmetric, unlike our results.

For the simulations that are closest to the set up of a GCM, with fully parameterized convection, the steady-state circulation and 
precipitation maximum are located not over the warmest SST but shifted to regions about one degree cooler.  For the case
with a grid-spacing of 25km and a domain width of 4000km, the precipitation maximum can remain shifted off of the maximum in
SST for multiple years.   While focused within the central quarter of the domain, simulations on larger domains and with a 
grid-spacing of 100km also show an aversion to settling over the SST maximum.   When the convective parameterization
is turned off, the overturning circulation becomes weaker and broader (w, and psi), but the precipitation, cloud fields, and 
circulation all consistently reside over the SST maximum.  When the convective parameterization is turned on, a domain mean 
wind shear develops throughout the lowest 10km that acts to shift the convective activity and circulation off of the SST maximum.  
Note: check the wind shear for P25large, P100small, and P100large.

Below is a list of several changes that occur when the LW CRE is off.  The points which have not already been discussed will be later in the paper.

Turning the longwave cloud radiative interactions off tends to:

\begin{itemize}
  \item decrease the strength of the overturning circulation and the domain mean precipitation
  \item increase the midtropospheric RH by $5-15 \% $
  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
  \item weaken the horizontally oriented low-level circulations.   This looks connected to a contracting of relative 
           humidity maxima around 600 hPa.
  \item spread out in geographic space the precipitation maxima
  \item dramatically homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
  \item decrease both the LTS and the EIS, over both the warm and cold regions
%  \item in most cases the symmetry about the SST maximum is increased.
  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
           the 1 and 2 \textit{km} simulations. 
  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
\end{itemize}

%% low level structure
%\begin{figure}
%\begin{center}
%\includegraphics[width=0.95\columnwidth]{walkerfigs/lowlevel_therm_test.eps}
%\caption{{Low-level thermodynamic structure (a-e) and vertical shear (lower right, f).  Solid lines show experiments that include LWCRE, 
%dashed lines experiments without LWCRE.  The yellow dashed-dot line is a 25 km experiment without LWCRE and with all 
%convective parameterization turned off.   Panel e shows the temperature at the lowest model level (thin lines) and the virtual 
%temperature at the lowest model level(thick lines).  The thick black line is the prescribed surface temperature.}}
%\end{center}
%\end{figure}
%

\subsection{Dependence on Domain Size}

%%%%
% section 2 of results

% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
% LW CRE off
\begin{figure}
  \centering
      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcreoff.eps}
      \includegraphics[width=0.6\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre_draft.eps}
  \caption{Normalized probability distributions of the location of the maximum value of precipitation for P25 and P100
  experiments .   Panels on the right (left) show experiments on the domain with a long dimension of 4000 km 
  (16000 km).  Black distributions are for experiments with the LW CRE on and green distributions for experiments 
  with LW CRE off.  The black curves show a Gaussian function with a standard deviation computed for 
  each experiment and an expected location in the center of the domain where the SST is warmest.}
\end{figure}

When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are two of the most 
fundamental choices that must be made.   One the goals of this study was to explore the results of changing grid-spacing over a wide 
range of values.  To simplify the analysis we have in most cases chosen to keep the 
long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies have documented sensitivities to domain size.  With this 
in mind several different domain shapes and sizes have been explored, but always keeping the $4000\, \rm{km}$ long-dimension as the 
primary domain for the analysis.  
Examining the evolution in time of the precipitation field reveals important characteristics of these simulations, and 
illustrates how much the distribution can vary as a function of domain size, parameterization of convection, and the effect of the 
longwave radiation due to clouds.  At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
precipitation over a smaller geographic extent.  
Shown in Figure {\ref{fig:domdep}} are Hovmoller plots of precipitation after 
averaging along the short horizontal dimension.  The four panels show simulations with a grid-
spacing of $25\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ (middle right), and 
simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.    
The structure of the precipitation depends strongly on domain size and shows less dependence on grid-spacing.

% new Hovmoller diagram
\begin{figure}
  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
  \caption{Evolution of precipitation through 3 years of simulation for a grid spacing of 25km (2 panels on right) and
  100km (two panels on left).  For each resolution, domains with a width of 4,000 km and 16,000 km are shown.}
  \label{fig:domdep}
\end{figure}

\begin{figure}
  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
  \caption{Identical to previous figure, except that LW CRE is now off.}
  \label{fig:domdep_lwoff}
\end{figure}

Smaller domain lengths were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
They also found less low-level clouds over the colder SSTs in the smaller domains, relative to a control domain size that was 4x
larger.   We have found larger precipitation rates for the larger domains.  Does our larger domain ascent region change?  Does 
Brethertons SST warm patch size increase with domain size?

% Fraction of Precip due to large-scale precip for large/small experiments with a 25km resolution
\begin{figure}
  \centering
      \includegraphics[width=0.8\columnwidth]{walkerfigs/Conv_vs_LS_hist.eps}
  \caption{Fraction of precipitation that is due to the large-scale(blue) cloud scheme relative to the total 
  precipitation (large-scale plus convective).}
  \label{fig:conv_vs_ls}
\end{figure}

We hypothesize than an important difference between our simulations and previous studies which use GCMs
is that although the deep and shallow convection is parameterized
with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
is much smaller in our simulations than it is for many GCM-type experiments with parameterized convection.   At 25km grid-spacing, 
the majority of condensational heating occurs through the large-scale cloud  scheme.   See Figure \ref{fig:conv_vs_ls}.
%Overall, the fraction of precipitation that is 
%due to the large-scale scheme is roughly 40\%, and in many places it is actually greater than the amount of precipitation 
%produced by the convection scheme.   
%In comparison, many GCMs, have between 70\%-90\% of their precipitation produced by 
%the convective parameterization.  
There are further surprises in the fraction of precipitation that is large-scale.  On our small 
domains, with a bowling alley domain length of 4000 km, the simulations with 100km grid-spacing have values of $f_{ls}$ 
of $75-80\%$.  Often, at GCM-like resolutions such as 100km the convective precipitation would be expected to control much of the
precipitation rather than the large-scale parameterization.  However, when the domain length is increased to 16000 km
$f_{ls}$ decreases to a range of $0-70\%$ that depends strongly on location.  Over the warmest region of the surface the 
precipitation is still dominated by the large-scale scheme.  However, turning off the longwave CRE leads to a dramatic reversal 
in which $60-75\%$ of the precipitation is convective over the warmest SST.  The large domain without the longwave CRE is the 
only configuration in which the convective precipitation is dominant.    If the default, or baseline, configuration of a GCM is built 
with the expectation that the convective parameterization scheme will dominate the production of tropical precipitation, then 
perhaps a configuration that minimizes the convective precipitation will result in a balance between the parameterization 
schemes that is less intuitive, such as an asymmetric response to symmetric forcing.

\subsection{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
General Circulation Model to a Cloud Resolving Model}

It is clear that the overturning circulation in the tropical Pacific encompasses dynamical motions at a host of scales and that the 
different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
Our primary motivation for using the GFDL AM4 on this doubly-periodic domain is that the dynamical core of the model can 
easily be used over a wide range of grid-spacings and can be used to solve either the hydrostatic or nonhydrostatic 
governing equations.  In this section we focus on simulations with grid-spacings that range between 1km and 100km.   
A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that results from the 
overturning circulation at different resolutions.  Shown are the first 180 days of the P25, E25, E2, and E1 simulations.  As the 
grid-spacing decreases towards $1 \, \rm{km}$ the distribution of precipitation becomes more regular and consistently 
centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more variability at later 
times, compared to these first 180 days.  Due to the large expense of the E2 and E1 simulations they were run for 
180 days.  The simulations with explicit convection at resolutions typical of cloud-resolving models (E2, E1) show little 
aversion to the precipitation maximum occurring over the maximum in SST and relative to the P25 and E25 simulations 
they are able to maintain a smoother distribution of  precipitation values over a broader range of SST values.

The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
among the experiments with varying grid-spacing.  All experiments have a multicell vertical structure (consistent with 
Bretherton et al. 2006), in contrast to the single cell that results from simple theoretical models such as the SQTCM.   All 
show a similarly dry mid-tropospheric region where subsidence dominates.  However, the multicelled structure is quite irregular
in the P25 experiment, and a small third cell has developed in the boundary layer of the 1km experiment.  The mid-troposphere 
in the region with deep-convection is more than $40\%$ dryer than it is for the 2km and 1km experiments.

Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
surface enthalpy flux reveals large differences in the symmetry.  Over the SST maximum, E25 has a surface enthalpy flux that is 
60 W/m2 larger than that of the E1 experiment, and the E1 experiment has a very irregular pattern of enthalpy flux in the middle
half of the domain.  It appears that these differences in magnitude and regularity are due to the differing wind speeds at the 
lowest atmospheric level.  It is also work noting that the E1 experiment has a stronger domain mean u wind shear compared 
with the E2 and E25 experiments.  Over the warm patch of SST, the surface enthalpy flux is decreased by the LWCRE for E25, 
E2, and E1 despite these experiments having stronger low-level winds.  This decreased enthalpy flux also corresponds to 
an increased amount of specific humidity in the lowest atmospheric model level.        
%%%%%
% section 3 of results

% Hovmoller diagram of precipitation for the first 6 months of the 25km, 2km, and 1km experiments
% LW CRE on
\begin{figure}
  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case, 25km case with no 
  parameterized convection, 2km control, and 1km control.  Shading indicates mm/day.  The horizontal axis shows the entire 
  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
  Shown is the meridional average. }
  \label{fig:hov_4mods_6mn}
\end{figure}

\begin{figure}
  \centering
      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
  while the P25 and P100 cases show only the first out of five years of the time series.}
    \label{fig:precip_dom_mn}
\end{figure}

\begin{figure}
  \centering
      \includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
          \caption{Domain mean total condensate (liquid + ice).  Solid lines show experiments with LWCRE on
          and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
          convection except the thin yellow lines which have the convective parameterization turned on.}
  \label{fig:TotCond}
\end{figure}

Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
The large oscillations in domain mean precipitation are similar to those noted in previous studies 
(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
of the differences in upper level cloud fraction.   Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by E25, P25, and 
P100 (5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and require a correspondingly larger
amount of condensational heating and precipitation.

\begin{figure}
  \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25v2v1_6pan_lwon.eps}
      %\includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_25vs2vs1_lwon.eps}
      \caption{Comparison of the steady state relative humidity (shading) and mass streamfunction.  
      Shown is E25 (left), E2(center), and E1(right).  All panels use the same contour interval for the 
      mass streamfunction (kg/s).}
  \label{fig:rh_psi_P25E2E1}
\end{figure}

\begin{figure}
  \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25v2v1_6pan_lwoff.eps}
      %\includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_25vs2vs1_lwoff.eps}
      \caption{Same as previous figure except with the longwave CRE turned off.}
  \label{fig:rh_psi_P25E2E1_lwoff}
\end{figure}

The domain mean condensate is an important measure of the steady state reached by these experiments.  The vertical 
distribution of condensate is closely related to the distribution of clouds, it influences the distribution of energy throughout
the atmosphere as well as influencing the outgoing longwave radiation.  It can also indicate the strength of convection 
and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a fundamental difference 
between the GCM-like P25/E25 experiments and the CRM-like E2/E1 experiments with the former having much 
higher values of low-level liquid condensate/cloud and the later having much higher values up upper level ice condensate.  
It is also interesting to note that the LWCRE results in less condensate above 700 hPa for all experiments, and 
more condensate below 700 hPa for the P25/E25 experiments.  The two-dimensional structure of circulation and humidity
shows that the amount of condensate aloft in the deep-convective region increases with resolution while the relative
humidity in the subsidence regions decreases with resolution.  This is consistent with an overturning circulation that 
strengthens as the resolution increases.   This dependence of circulation strength and moisture on resolution is especially 
apparent when the LWCRE is off (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).  When the clouds and radiation are allowed 
to directly interact with each the E2 and E1 simulations appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}).

The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere 
(can we use this to understand the differences in LWCRE?).

\begin{figure}
  \centering
       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft2.eps}
  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
  in the center of the domain where the SST is warmest. }
\end{figure}

An interesting fact that emerges from the domain mean values of precipitation with and without the LW CRE (see table 1) 
is that the response is not the same across the different grid-spacings.  
Turning the LW CRE off for the E1 and E2 results in more precipitation while for the E25, P25, and P100 experiments 
less precipitation results from turning the LW CRE off.  The primary method by which the longwave cloud radiative effect 
influences the atmosphere is by heating the atmosphere in the region between the clouds and the surface.  Larger values 
of ice condensate and upper-level cloud fraction such as we see for the E2 and E1 experiment imply a larger LW CRE relative
to the E25, P25, and P100 experiments.    
This implies there will be less atmospheric heating from 
longwave radiation and a corresponding larger heating due to condensational heating which is consistent with higher values 
of domain mean precipitation for E25, P25, and P100 compared to E2 and E1.  Similarly, the E2 experiment has lower values 
of upper level condensate and higher values of mid-troposphere relative humidity compared to the E1 simulation, which ....??  
Water vapor is an efficient emitor of long-wave radiation and thus greatly facilitates the cooling of the troposphere.  
Popp and Silvers, 2017 showed that that there is dramatically less water vapor in the atmosphere and much less precipitation 
for LW CRE off experiments (see their figure 1).  Our results here for the E25, P25, and P100 are consistent with 
those of Popp and Silvers, 2017.

\begin{figure}
  \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
  \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
  subsidence regions and are shown for the control (LWCRE on) and LWCRE off experiments.}
  \label{fig:cf_tdtlw}
\end{figure}

Superposing the the circulation and relative humidity illustrates the subsidence driven 
drying and the strong moistening that results from ascent over the region of maximum latent heat flux.

% surface enthalpy flux
\begin{figure}
  \centering
  \begin{minipage}{0.4\textwidth}
    \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
    \end{minipage}
    \begin{minipage}{0.4\textwidth}
    \centering
      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
    \end{minipage}
    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
    (latent and sensible heat flux) of the enthalpy.
    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
    \label{fig:enthalpy}
\end{figure}

There are also differences in the lapse-rate below $700 \rm{hPa}$, in the upper-level clouds,
and the domain mean precipitation (Figure \ref{fig:precip_dom_mn}).

\textit{probably insert figure from slides 20 and 21 of IUGG talk.}
We can see clearly that the interactions between longwave radiation and clouds act to dry the troposphere in the regions of subsidence 
more than the cases when the longwave CRE is not active.  This is especially true for the simulations with a grid-spacing of 1 km 
and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the LW CRE on, significant 
low-level clouds are formed, leading to a radiative cooling of almost 10K/day, and a radiative cooling of around -7K/day.   However, 
when the LW CRE is off, there is no appreciable difference in the low-level diabatic profiles among the models with 3 grid-spacings.   It 
is also clearly seen that the LW CRE decreases the upper-level ice-condensate for models of all grid-spacings while dramatically 
increasing the low-level liquid condensate.

When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
enthalpy flux (Figure \ref{fig:enthalpy}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.

Relative to simulations with a grid-spacing of $25 \textit{km}$, the simulations with explicit convection can be characterized as having: 
\begin{itemize}
  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
  that is 40\% higher than in the parameterized, lower resolution simulations.  
  \item two to four times more ice condensate above about 600 hPa but only about half as much liquid condensate below about 700 hPa.
  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
  simulations are 10-20\% higher (3.5-3.9 mm/d).  
  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
  \item much less vertical shear.  
\end{itemize}

%% Domain mean vertical structure for 25km, 2km, and 1km resolutions
%% LW CRE on
%\begin{figure}
%  \includegraphics[width=0.8\columnwidth]{walkerfigs/Walker_VertStr_LWCRE_b.eps}
%  \caption{Domain mean vertical structure for simulations with a grid spacing of 25km (yellow, parameterized convection), 2km (blue), and 1km (green).  
%  All experiments have active LWCRE.  The dotted lines of RH show the mean over the cold pool regions.  Thin lines on the lapse rate panel show the moist adiabat for reference.}
%  \label{fig:vertst_lwcre}
%\end{figure}
%
%% Domain mean vertical structure for 25km, 2km, and 1km resolutions
%% LW CRE off
%\begin{figure}
%  \includegraphics[width=0.86\columnwidth]{walkerfigs/Walker_VertStr_LWCREoff.eps}
%  \caption{Domain mean vertical structure for simulations with a grid spacing of 25km (yellow, parameterized convection), 2km (blue), and 1km (green).  
%  All experiments have LWCRE off.  The dotted lines of RH show the mean over the cold pool regions.  Thin lines on the lapse rate panel show the moist adiabat for reference.}
%  \label{fig:vertst_lwcre_off}
%\end{figure}
%
%% RH and Psi for 1km, 2km, and 25km simulations			
%\begin{figure}
%  \centering
%  \begin{minipage}{0.49\textwidth}
%    \centering
%      %\includegraphics[width=0.5\columnwidth]{randomfigs/psi_rh_1km_lwoff.eps} 
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_1km_ctl.eps} 
%    %\caption{{\bf default}}
%    \end{minipage}
%    \begin{minipage}{0.49\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_1km_lwoff.eps}
%      %\caption{{\bf default}}
%    \end{minipage}
%    \begin{minipage}{0.49\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_2km_ctl.eps}
%      %\caption{{\bf default}}
%    \end{minipage}
%    \begin{minipage}{0.49\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_2km_lwoff.eps}
%      %\caption{{\bf default}}
%    \end{minipage}
%    \begin{minipage}{0.49\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psirh_noconv_ensind0_contint5.eps}
%      %\caption{{\bf default}}
%    \end{minipage}
%    \begin{minipage}{0.49\textwidth}
%    \centering
%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psirh_noconv_lwoff_ensind3_contint5.eps}
%      %\caption{{\bf default}}
%    \end{minipage}
%    \caption{Relative humidity is shown by the shading while the mass streamfunction is given my the black contour lines.  The top row shows the 1km experiments, the middle row the 2km
%    experiments, and the bottom row the 25 km experiments.  Experiments with LWCRE are on the left and 
%    experiments without are on the right.}
%\end{figure}
%

\section{Conclusions}

The results presented in this paper show us that (scientific point learned).    Interactions between the clouds and radiation
act to spatially concentrate the circulation, strengthen the overturning circulation, and dry out the mid-troposphere where 
subsidence dominates (although domain mean condensate is less when LWCRE is on.).

The longwave cloud radiative effect (LWCRE) has been shown to play a dramatic role in the organization of the precipitation
field and the low-level clouds.  This is primarily accomplished by decreasing the amount of precipitation that is produced 
by the large-scale precipitation scheme.  Two major differences between the GCM-like experiments and the CRM-like 
experiments are 4-5 times more low-level clouds and a much dryer mid-troposphere in the GCM-like experiments compared 
to the CRM-like experiments.  The LWCRE also highlights the impact of an increased vertical moisture transport 
in our CRM-like models.

Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
large-scale circulation to a simple Gaussian shaped prescribed SST pattern.  To better understand the role that clouds
and humidity play in determining and driving the circulation we have performed experiments with and without the radiative
effect of clouds, with and without the deep convective parameterization, across multiple domain sizes,  
and using a range of resolutions from 100 km to 1 km grid-spacing.  Our results imply that the convective 
parameterization and the longwave cloud radiative effect strongly interact with each and often lead to 
asymmetric results.

There is a rich literature on tropical overturning circulations.  Much of it is focused on the Hadley circulation and while some
work has looked at the Walker circulation, it has received less attention.  Part of our motivation in using the framework of the 
Walker circulation comes from the fact that all of the major types of tropical cloud types occur regularly within this circulation
and it thus serves as an ideal testbed/laboratory for studying the interactions and interdependencies of different types of 
clouds and the circulation.  While this study has interpreted the experiments in the context of the Walker Circulation, our results 
are also relevant to the deep overturning circulations and meridional SST gradients that define the ITCZ and the Hadley 
Circulation.  In that context, our results are consistent with those of several recent studies (e.g. Harrop and Hartmann, 2016, 
Popp and Silvers, 2017, Dixit et al. 2018, Flaschner et al. 2018).  These studies, as well as the present one, all show that the 
LWCRE acts to constrain the deep convective region.  This results from an increased atmospheric energy uptake and 
strengthening of the overturning circulation where the deep convective clouds occur (Popp and Silvers, 2017).  Consistent with 
these papers, the present work also shows that the LWCRE has a strong influence on the low-level circulation.   When 
the LWCRE is turned off, the low-level circulations shift upward and are not as well organized (reference psi figures).
There is a corresponding change in the low-level cloud fields, longwave radiative cooling, and the domain mean precipitation.
For the experiments with a GCM-like configuration, the LWCRE strongly influences the precipitation from the large-scale
cloud scheme while leaving the precipitation from the convective parameterization scheme largely unchanged.  This leads 
to a much stronger response of the GCM-like experiments to the LWCRE, especially in the low-levels of the troposphere.  
Because we expect the fraction of precipitation that is due to the convective parameterization to be model dependent 
this could explain why GCMs have a large spread in their response to turning off the LWCRE (reference some 
of Aiko's work?).

We have used the tropical overturning circulation to compare the multi-scale interactions between circulation patterns, cloud 
systems, and interactive radiation across experiments with grid-spacing ranging from 100km to 1km.  The flexible modeling
system at GFDL has allowed us to use a single code base in a GCM-like configuration with physics parameterizations 
that are very close to the AM4.0/CM4.0 models as well as in a CRM-like configuration with explicit convection.  While 
there are significant differences between the CRM presented in this paper and more conventional CRMs (e.g. vertical 
grid spacing and threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
like a CRM allows for an enticing testbed for future model development.
These comparisons have highlighted some of the unexpected behaviors of a GCM-like configuration when used with 
highly idealized boundary conditions.  For example, the consistent asymmetry of the circulation and precipitation relative 
to the fixed SST pattern and the dominance of the large-scale precipitation over the convective precipitation.  
The comparisons have also illustrated some 
of the challenges that arise when dramatically increasing the resolution of a GCM.  For example, the lack of shallow 
clouds (both convective and stratocumulus) and the difficulty of comparing clouds in this CRM to other CRMs due to the 
prognostic large-scale cloud scheme used at GFDL.

The goal in developing and using idealized models is to capitalize on their simplicity and learn something about the 
parent system as a result.  Idealized studies focusing on particular parts of the Earth system have shown that the danger of 
such idealized models is that they will not actually be less complex or easier to understand than the Earth system.

The only difference between our simulations and radiative convective equilibrium is a gradient of SST at the lower boundary.
The addition of this small difference creates an undeniable link with the observed tropical atmosphere.  The idealized 
mock -Walker cell configuration serves as an important step between models of pure radiative convective equilibrium
and models which are applicable to a wider range of Earth like conditions.

Although the radiative cooling and condensational heating
 are in many ways similar...   The 1 and 2 \textit{km} experiments transport much more condensate aloft and maintain a 
 relative humidity over the warm pool region that is about 40\% higher than the experiments with parameterized convection.

% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
% LW CRE on
%\begin{figure}
%  \centering
%      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_maxP_4mods_lwcreon.eps}
%       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre.eps}
%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments 
%  with the longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed 
%  for the experiments having a domain width of 4000 km while the bottom panels are for experiments having a 
%  domain width of 16000 km.  The black curves show a Gaussian function with a standard deviation computed for 
%  each experiment and an expected location in the center of the domain where the SST is warmest. }
%\end{figure}

\appendix

%A couple of appendices with extra details which may not be included in the final paper.

\section{Streamfunction}

For a two-dimensional flow in the $\lambda,p$ plane we can write the mass conservation equation in terms of a 
mass streamfunction $\psi$ as: 
\begin{equation}
u =  -\frac{\partial \psi}{\partial p}   \,\, {\rm and} \,\, \omega =\frac{\partial \psi}{a \rm{cos} \phi \partial \lambda}
\end{equation}
with $a$ as the radius of Earth.
This satisfies the continuity equation: 
\begin{equation}
\frac{\partial}{a \rm{cos} \phi\partial\lambda}\left(-\frac{\partial \psi}{\partial p}\right)+\frac{\partial}{\partial p}\left(\frac{\partial \psi}{a \rm{cos}\phi \partial \lambda}\right)=0.
\end{equation}
The streamfunction is therefore defined by two equations and can be solved with either.  The choice is often made based on the 
boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $\rm{kg/s^3}$.  Often, the streamfunction
is computed as a mass streamfunction with units of $\rm{kg/s}$.  Density does not appear above
because pressure is being used as the vertical coordinate.   With height as the vertical coordinate, mass is given by $\rho dxdydz$, 
assuming a hydrostatic atmosphere and rewriting in terms of pressure mass is given by $-(1/g) dxdydp$.
Scaling the equations above by $a/g$ results in $\psi$ having units of $\rm{kg/s}$.

Solving for $\psi$ by integrating the vertical velocity is possible, but requires a boundary condition along one edge of the domain between the surface and the 
top of the atmosphere.  Solving for $\psi$ by integrating the horizontal velocity allows us to set $\psi=0$ along the upper edge of the domain.  
This is both simple, and physically motivated.

% computed with matlab, see StreamFunNew.m script
\begin{equation}
\psi_{i,j+1}= \psi_{i,j}-\frac{a}{g}\sum_{j=32}^1 \left(u_{i,j+1}(p_{j+1}-p_{j})\right).
\end{equation}

In the previous equation, $w, u,$ and $\rho$ have all been averaged in space and time and $p$ is the pressure on full model levels.  The 
radius of Earth is $a$ and the acceleration due to gravity by $g$.  The density, $\rho$ is computed as $ \rho_{i,j}=\frac{p_j}{R T_{v;i,j}}  $  where $R$ and $T_v$ are the gas constant for dry air ($287 \rm{J/kg K}$) and the virtual temperature ($T_v=T(1+q/\epsilon)/(1+q)$), respectively.  The specific humidity is given by $q$ and $\epsilon = 0.622$.

\section{Cloud Water and Cloud Fraction}

The last several generations of the GFDL atmospheric models have used the parameterization developed by Tiedtke (1993) to prognostically compute the grid-cell averaged cloud water ($l$) and cloud fraction ($a$).  The formulation for the local time rate of change from Tiedtke is 
\begin{equation}
  \frac{\partial l}{\partial t} = A(l)+S_{cv}+S_{BL}+C-E-G_{p}-\frac{1}{\rho}\frac{\partial}{\partial z}(\rho\overline{w'l'})_{entr}
\end{equation}
and 
\begin{equation}
  \frac{\partial a}{\partial t} = A(a)+S(a)_{cv}+S(a)_{BL}+S(a)_C-D(a).
\end{equation}
Transport of $l$ or $a$ through the boundaries of a grid is given by $A(l)$ or $A(a)$, the terms ($S_{cv}, S(a)_{cv}, S_{BL}, S(a)_{BL}$, and $S(a)_C$) are the sources of cloud water or cloud fraction from convection, boundary layer turbulence, and condensation, respectively.  The condensation/sublimation rate is given by $C$, $E$ is the evaporation of cloud water, $G_{p}$ is the rate of generation of precipitation by microphysical processes and the $\overline{w'l'}$ term is the flux divergence from entrainment at the top of the cloud layer, and lastly, $D(a)$ is the sink of cloud fraction due to evaporation.

Often, cloud resolving models, or cloud system resolving models, do not predict partially cloudy grid cells, but rather consider a cell to be either cloudy or clear.  If the goal is to more directly compare to cloud resolving models then cloud fraction should not be prognostically predicted but simply tied to a certain value of total condensate in a grid-cell.  However, in the Tiedtke system, the prognostic equation for cloud water depends on the cloud fraction.  As given by equations 16, 24, 26,28, 30, and 33 in Tiedtke's paper, this dependence is present in the $S_{BL}$, $C$, $E$, and $G_{p}$ terms.

\end{document}

### 2019-09-16 Silvers_WalkerCell_old.tex
First commit for latex repo

\documentclass[11pt]{amsart}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}

\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\author{Levi G. Silvers}
%\date{2016}							% Activate to display a given date or no date

\begin{document}
\maketitle
\section{Key Points}
\begin{itemize}
  \item{How do clouds influence the Walker Circulation?}
  \item{To what extent are the deep convective clouds and the low-level clouds in the Walker Cell coupled?}
  \item{When simulating the Walker Circulation, how well does a GCM compare to a CRM?}  
\end{itemize}

\section{Streamfunction}

For a two-dimensional flow in the $\lambda,p$ plane we can write the mass conservation equation in terms of a 
mass streamfunction $\psi$ as: 
\begin{equation}
u =  -\frac{\partial \psi}{\partial p}   \,\, {\rm and} \,\, \omega =\frac{\partial \psi}{a \rm{cos} \phi \partial \lambda}
\end{equation}
with $a$ as the radius of Earth.
This satisfies the continuity eqation: 
\begin{equation}
\frac{\partial}{a \rm{cos} \phi\partial\lambda}\left(-\frac{\partial \psi}{\partial p}\right)+\frac{\partial}{\partial p}\left(\frac{\partial \psi}{a \rm{cos}\phi \partial \lambda}\right)=0.
\end{equation}
The streamfunction is therefore defined in two ways and can be solved with either equation.  The choice is often made based on the 
boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $kg/s^3$.  Often, the streamfunction
is computed as a mass streamfunction with units of $kg/s$.  Density does not appear above
because pressure is being used as the vertical coordinate.   With height as the vertical coordinate, mass is given by $\rho dxdydz$, 
assuming a hydrostatic atmosphere and rewriting in terms of pressure gives mass given by $-(1/g) dxdydp$.
Scaling the equations above by $a/g$ will result in $\psi$ having units of $kg/s$.

Solving for $\psi$ by integrating the vertical velocity is possible, but requires a boundary condition along one edge of the domain between the surface and the 
top of the atmosphere.  In contrast, solving for $\psi$ by integrating the horizontal velocity allows us to set $\psi=0$ along the upper edge of the domain.  
This is both simple, and physically motivated.

Below solves for $\psi$ by integrating the vertical velocity $w$ over $x$ yields
\begin{equation}
\int_0^{x'} \rho(x,p)w(x,p)d{x'}=\int_0^{x'}\frac{\partial \psi(x,p)}{\partial x'}d{x'}
\end{equation}
\begin{equation}
\int_0^{x'} \rho(x,p)w(x,p)d{x'}= \psi(x,p)-\psi(0,p)
\end{equation}
\begin{equation}
\psi(x,p)=\int_0^{x'} \rho(x,p)w(x,p)d{x'} + \psi(0,p)
\end{equation}

We now need an expression for $\psi(0,p)$, this can be found by integrating the zonal velocity $u$ in $p$.
\begin{equation}
\int_{p_{sfc}}^{p'} u(x,p') d{p'} = g\int_{p_{sfc}}^{p'}\frac{\partial\psi}{\partial p'}d{p'}
\end{equation}
\begin{equation}
\int_{p_{sfc}}^{p'} u(x,p') d{p'} = g\psi(x,p)-g\psi(x,p_{sfc}).
\end{equation}
So at $x=0$ we have: 
\begin{equation}
\psi(0,p)=\frac{1}{g}\int_{p_{sfc}}^{p'} u(0,p') d{p'}+\psi(0,p_{sfc}),
\end{equation}
which leads to 
\begin{equation}
\psi(x,p)=\int_0^{x'} \rho(x,p)w(x,p)d{x'} + \frac{1}{g}\int_{p_{sfc}}^{p'} u(0,p') d{p'}+\psi(0,p_{sfc}).
\end{equation}
The term $\psi(0,p_{sfc})$ is simply a constant boundary condition at the atmospheric level closest to the surface and at the first horizontal grid point.   By initializing the $\psi$ field as 0 everywhere I have chosen this to be zero.  Note that while the $u(0,p')$ term is essentially a boundary condition for the computation of $\psi(x,p)$ by integrating $w(x,p)$, it is still dependent on pressure and therefore will change at each level of the atmosphere.      Writing this out in terms of grid points using $i,j$ for $x,p$ we have:
\begin{equation}
\psi_{i,j}= \rho_{i,j} w_{i,j}\Delta x+\sum_{j=p_{sfc}}^j \left(\frac{1}{g}u_{i,j}(p_j-p_{j-1})\right).
\end{equation}
In the previous equation, $w, u,$ and $\rho$ have all been averaged in space and time and $p$ is the pressure on full model levels.  The density, $\rho$ is computed as $ \rho_{i,j}=\frac{p_j}{R T_{v;i,j}}  $  where $R$ and $T_v$ are the gas constant for dry air ($287 \rm{J/kg K}$) and the virtual temperature ($T_v=T(1+q/\epsilon)/(1+q)$), respectively.  The specific humidity is given by $q$ and $\epsilon = 0.622$.

\section{Figures}

% looks like there is an Overfull \hbox here and the figure is not printing....
\begin{figure}[htb]
  \includegraphics{randomfigs/condensate_3mods.eps}
\end{figure}

 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
        %\includegraphics[width=5.0in]{agu/silvers_etal_2016/rce_20km_tqv_20mmto80mm_cathy.eps}
        \includegraphics[width=5.0in]{/Users/silvers/code/matlabscripts/WalkerCirc/figs_ctl/psi_log_1km.pdf}
   \caption{Column integrated water vapor ($\rm{mm}$).  The SST$=301$ K for all domains. 
   %and the time of the snapshots is the same as for Fig. \ref{fig:precvsdom}, but the color scale differs.
   For comparison, the black bar in the 3M, 12M, 50M, and 200M domains represents a length of 830km, corresponding to the short edge length of the 3/4M domain.}
   \label{fig:tqv5dom}
\end{figure}

\end{document}

### 2019-09-16 Silvers_cfmip_draft.tex
First commit for latex repo

\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}
\usepackage{epstopdf}
%\usepackage{pdflatex}
%\usepackage{epsfig}

			% Activate to display a given date or no date
%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\title{Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models}
\author{Levi G. Silvers et al.}

\begin{document}
\maketitle

\begin{abstract}
The newest atmospheric climate model at GFDL, AM4, succeeded at significantly reducing the TOA radiative flux biases as compared to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs (Cess warming experiments), the corresponding coupled climate model, CM4, has high transient and equilibrium climate sensitivities.

We will present a systematic picture of the modeled clouds across a hierarchy of model configurations which utilize this atmospheric model.  This hierarchy includes the CFMIP Aquaplanet and AMIP experiments, fully coupled model experiments (using GFDL's CM4 model) as well as additional AMIP-like experiments with particular SST patterns.  This demonstrates the large range of sensitivities that are possible from a single atmospheric climate model.   Looking at the global mean radiative feedbacks across the different model configurations as well as in the context of CMIP5 and CMIP6 models will allow us to assess to what extent the cloud feedbacks in the idealized experiments relate to the fully coupled experiments and to observed clouds.  
\end{abstract}

%\section{Key Questions}

\textbf{Key Points}
\begin{itemize}
  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
  maximum.}
  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
  changes in the low-level clouds and boundary layer structure.}
  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
  region that is 30\% higher than for the coarser cases with parameterized convection.}
  \item{The mock-Walker Circulation is RCE plus an imposed gradient in surface temperature.  This is a simple design that 
  incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.}
\end{itemize}

\section{introduction}

This paper has a double motivation.  One of the motivations is to illustrate the wide range of sensitivities to perturbations 
that can be achieved with a single base model.  For this purpose we utilize several models from the latest suite of GFDL 
models.  This constitutes a hierarchy of configurations that ranges from an atmosphere only aquaplanet to a fully coupled 
climate model.  Previously the range of climate sensitivities and feedbacks among the large ensemble of climate models 
the world has to offer have been documented largely by examining the multi-model mean results with little attention to 
the variability of sensitivity within a single modeling framework (IPCC; Andrews et al., 2012; Ringer et al., 2014).  By 
focusing on the models from a single modeling center we hope to bring out fresh insight that is lost within a large ensemble.

An additional motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
have participated in CMIP6.  This will largely be done in the context of the amip experiment and comparisons to observations
that overlap with that time period (1979-2014).  The experiments and diagnostics used are taken from the latest 
round of CFMIP which has provided a useful framework to guide experimental design and diagnostic outputs.

\section{Clouds in AM4.0: Comparison between amip and observations}

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
  \label{fig:clt_isccp_calipso}
\end{figure}

\begin{figure}
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_calipso_obs_sim_am4.eps}
  \caption{Comparison of total cloud fraction.  Top shows observations from CALIPSO, processed for GCM comparison.  Middle 
  shows output from the CALIPSO simulator, bottom shows raw model output of clt without a simulator.}
  \label{fig:calipso_sim_vs_mod}
\end{figure}

\begin{figure}
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/ctp_vs_tau_isccp_modis_am4_obs.eps}
  \caption{Joint histograms showing the variations of cloud fraction as a function of cloud top pressure and tau.}
  \label{fig:calipso_sim_vs_mod}
\end{figure}

\begin{figure}
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs.eps}
  \caption{Calipso scumstash}
  \label{fig:calipso_9pan}
\end{figure}

\section{The Role of Clouds in AM4.0/CM4.0/Aquaplanets in Determining and Influencing Climate Sensitivity}

In an attempt to compare to the values of feedback that were reported in Ringer et al., 2014, we use the same method 
to compute the radiative feedbacks for the GFDL models.  That is, for the abrupt $4xCO_{2}$ experiment, feedbacks are 
inferred to be the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies (Gregory et al., 2004).  From the atmosphere only experiments (amip-p4K, amipFuture, and aqua-p4K), the feedbacks are calculated as 
differences in top-of-atmosphere flux anomalies between the perturbation and control experiments.

Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
low clouds.'  See $Stevens_etal_Cookie_overview$ for details.   That paper asks the question of whether single 
model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.

The cloud radiative effect (CRE) is computed as the difference between the all-sky and clear-sky TOA fluxes.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks.  Compare to Ringer et al. 2014.}
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip p4K & Amip Future & Abrupt 4xCO2    \\ \hline
    Net          &   -2.2    &  -1.6              & -1.8           &    -0.84 (from Tim)         \\ 
    \\
    Net CRE      & 0.3      & -0.1            & 0.1           &?            \\  
    \\
    LW CRE       & 0.4       & 0.1            & 0.1           & ?              \\  
    \\
    SW CRE      & -0.7       & -0.1          & -0.2          & ?              \\  
    \\
    LW CLR       & 2.0       & 2.0             & 2.0           & ?             \\  
    \\
    SW CLR      & -0.1      & -0.3            & -0.3          & ?                   \\  \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:lambda}
\end{center}
\end{table}

\begin{figure}
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.86\columnwidth]{cfmipfigs/amip_p4k_future_cldfrac_calip.eps}
  \caption{Calipso scumstash}
  \label{fig:calipso_amip_comparison}
\end{figure}

\end{document}

### 2019-09-16 Silvers_etal_2016_1page.tex
First commit for latex repo

\documentclass[11pt]{amsart}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}

\title{Radiative Convective Equilibrium as A Framework for Studying the Interaction Between Convection and its Large-scale Environment}
\author{Levi G. Silvers, Bjorn Stevens, Thorsten Mauritsen, Marco Giorgetta}
%\date{2016}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

%\keypoints{
%\item Radiative Convective Equilibrium (RCE) is a useful framework to compare, contrast, and harmonize the two extremes of explicit and parameterized convection.
%\item Consistent climates across a range of domain sizes encourage the use of RCE to enhance our ability to model clouds (or cloud systems).  
%\item The response of low clouds to warming, and hence estimation of the climate feedback parameter, is not robust across configurations.
%}

%\section{Abstract}
%An uncertain representation of convective clouds has emerged as one of the key barriers to our understanding of climate sensitivity.  The large gap in resolved spatial scales between General Circulation Models (GCMs) and high resolution models has made a systematic study of convective clouds across model configurations difficult.
%It is shown here that the simulated atmosphere of a GCM in Radiative Convective Equilibrium (RCE) is sufficiently similar across a range of domain sizes to justify the use of RCE to study both a GCM and a high resolution model on the same domain with the goal of improved constraints on the parameterized clouds.
%Simulations of RCE with parameterized convection have been analyzed on domains with areas spanning more than two orders of magnitude 
%($\mathrm{0.80 - 204 \times 10^6 km^2}$), all having the same grid spacing of $13 \mathrm{km}$.    
%The simulated climates on different domains are qualitatively similar in their degree of convective organization, the precipitation rates, and the vertical structure of the clouds and water vapor, with the similarity increasing as the domain size increases.  Sea surface temperature perturbation experiments are used to estimate the climate feedback parameter for the differently configured experiments, and the cloud radiative effect is computed to examine the role which clouds play in the response.   Despite the similar climate states between the domains the feedback parameter varies by more than a factor of two; the hydrological sensitivity parameter is better behaved, varying by a factor of 1.4.  The sensitivity of the climate feedback parameter to domain size is related foremost to a non-systematic response of low-level clouds as well as an increasingly negative longwave feedback on larger domains.

\section{Summary}
Convective parameterizations remain a significant barrier to our understanding of both variability and sensitivity in the Earth system.  This is further complicated by the large gap of scales between General Circulation Models (GCM) and high resolution models.  We show that radiative convective equilibrium is 
a useful tool in this context and study parameterized GCM experiments on domains with areas spanning more than two orders of magnitude 
($\mathrm{0.80 - 204 \times 10^6 km^2}$), all having the same grid spacing of $13 \mathrm{km}$.  The simulated climates on different domains are qualitatively similar in their degree of convective organization, the precipitation rates, and the vertical structure of the clouds and water vapor, with the similarity increasing as the domain size increases.   Despite the similar climate states between the domains the feedback parameter varies by more than a factor of two.  The sensitivity of the climate feedback parameter to domain size is related foremost to a non-systematic response of low-level clouds as well as an increasingly negative longwave feedback on larger domains.

\section{Key Points}
\begin{itemize}
  \item{Radiative Convective Equilibrium (RCE) is a useful framework to compare, contrast, and harmonize the two extremes of explicit and parameterized convection}
  \item{Consistent climates across a range of domain sizes encourage the use of RCE to enhance our ability to model clouds (or cloud systems)}
  \item{The response of low clouds to warming, and hence estimation of the climate feedback parameter, is not robust across configurations}  
\end{itemize}

 \begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
        \includegraphics[width=5.0in]{agu/silvers_etal_2016/rce_20km_tqv_20mmto80mm_cathy.eps}
   \caption{Column integrated water vapor ($\rm{mm}$).  The SST$=301$ K for all domains. 
   %and the time of the snapshots is the same as for Fig. \ref{fig:precvsdom}, but the color scale differs.
   For comparison, the black bar in the 3M, 12M, 50M, and 200M domains represents a length of 830km, corresponding to the short edge length of the 3/4M domain.}
   \label{fig:tqv5dom}
\end{figure}

\begin{figure}
  \centering 
    \includegraphics[width=2.5in]{agu/silvers_etal_2016/feedbk_vs_5dom_cmip5_reds.eps}
   \caption{Feedback parameter as a function of domain size.  
  Bars correspond to a 97.5 \% confidence interval with a one-sided t-test.  A de-correlation time of three weeks was assumed for all domains.  The feedback parameters from CMIP5 models are shown by the black markers.}
   \label{fig:lambdaecs}
\end{figure}

\end{document}

### 2019-09-16 Silvers_etal_2017_1page.tex
First commit for latex repo

\documentclass[11pt]{amsart}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{gensymb}

\title{The diversity of cloud responses to twentieth-century sea surface temperatures}
\author{Levi G. Silvers, David Paynter, and Ming Zhao}
%\date{2016}							% Activate to display a given date or no date

\begin{document}
\maketitle
%\section{}
%\subsection{}

%\keypoints{
%\item Radiative Convective Equilibrium (RCE) is a useful framework to compare, contrast, and harmonize the two extremes of explicit and parameterized convection.
%\item Consistent climates across a range of domain sizes encourage the use of RCE to enhance our ability to model clouds (or cloud systems).  
%\item The response of low clouds to warming, and hence estimation of the climate feedback parameter, is not robust across configurations.
%}

\section{Abstract}
Low-level clouds are shown to be the conduit between the observed sea surface temperatures (SST) 
and large decadal fluctuations of the top of the atmosphere (TOA) radiative imbalance.  The influence 
of low-level clouds on the climate feedback is shown for global mean time
series as well as particular geographic regions.  The changes of clouds are found to be 
important for a mid-century period of high sensitivity and a late century period of low 
sensitivity.  These conclusions are drawn from analysis of amip-piForcing simulations using three 
atmospheric general circulation models (AM2.1, AM3, and AM4.0).  All three models confirm the importance 
of the relationship between the global climate sensitivity and the eastern Pacific 
trends of SST and low-level clouds.  However, this work argues that the variability of the 
climate feedback parameter is not driven by stratocumulus dominated regions in the eastern ocean basins, 
but rather by the cloudy response in the rest of the tropics.

\section{Key Points}
\begin{itemize}
    \item Three climate models driven by observed sea surface temperatures increase then decrease climate sensitivity over the twentieth century
\item Substantial changes of the climate feedback parameter are mirrored by the global mean low-level cloud anomalies
\item This variability is connected to atmospheric stability and not dominated by stratocumulus regions, but by the broader tropics
\end{itemize}

\begin{figure}
   \includegraphics[width=5.in]{agu/silvers_etal_2017/figures/alpha_tseries_6pan.pdf}
  \caption{Time series analysis of AM4.0(black), AM3(green), and AM2.1(blue).  Thick lines are ensemble means, shading gives range of ensemble members.  A) Global climate feedback parameter $-\alpha$ ($\rm{W/m^2 K}$),  
  B) Same as  A) but with contributions from 4 tropical windows (small-dashed) and the rest of tropics (long-dashed),  C)  $\alpha$ ($\rm{W/m^2 K}$) decomposed into the CRE (lower) and CLR (upper) components,   D)  Global mean Low-Cloud Cover parameter $LCC_{LR}$ ($\rm{\% /K}$).  Global $\alpha_{CRE}$ ($\rm{W/m^2 K}$) is decomposed into the short-wave CRE (E) and the long-wave CRE (F).   All time series computed by regression against global, yearly mean surface temperature change.}
  \label{fig:alphacre}
\end{figure}

\end{document}

### 2019-09-16 Summ_Mag_Sch_90.tex
First commit for latex repo

\documentclass[11pt]{report}
% this is a shell to write new latex programs in....

% additional packages
%--------------------latex
\usepackage{amsmath}
\usepackage{times}
\usepackage{indentfirst}
\usepackage[dvips]{graphicx}

% page layout stuff (set as desired)
%------------------
\newlength{\lpgmargin} \setlength{\lpgmargin}{1.0in}
\newlength{\rpgmargin} \setlength{\rpgmargin}{1.0in}
\newlength{\tpgmargin} \setlength{\tpgmargin}{1.0in}
\newlength{\bpgmargin} \setlength{\bpgmargin}{1.0in}

\setlength{\headheight}{0.0in}
\setlength{\headsep}{0.0in}
\setlength{\footskip}{0.5in}

% page layout stuff (leave as is)
%------------------
\setlength{\hoffset}{-1in}
\setlength{\voffset}{-1in}
\setlength{\oddsidemargin}{\lpgmargin}
\setlength{\topmargin}{\tpgmargin}
\setlength{\marginparsep}{0in}
\setlength{\marginparwidth}{0in}
\setlength{\textwidth}{\paperwidth}
   \addtolength{\textwidth}{-\lpgmargin}
   \addtolength{\textwidth}{-\rpgmargin}
\setlength{\textheight}{\paperheight}
   \addtolength{\textheight}{-\tpgmargin}
   \addtolength{\textheight}{-\bpgmargin}
   \addtolength{\textheight}{-\headheight}
   \addtolength{\textheight}{-\headsep}
   \addtolength{\textheight}{-\footskip}

% page style stuff (set as desired)
%-----------------
%\pagestyle{plain}
\pagestyle{plain}

%=============================================================================

\begin{document}

%\centerline{\LARGE \textbf{TeX Shell}}
Paper Summary

Title: \textbf{The Generalization of Semigeostrophic Theory to the 
               $\beta$-Plane}

Authors: Gudrun Magnusdottir and Wayne Schubert

J. Atmos. Sci., 1990

\vspace{0.25in}

%\chapter{1. Introduction}
\begin{enumerate}
\item{\textbf{Introduction}}

Brian Hoskins combined the geostrophic momentum approximation with the
geostrophic coordinate transformation to derive the system of semigeostrophic
equations.  These are almost as simple as the geostrophic equations, but they
succeed at representing fluid behavior (fronts, jets, etc.) that is beyond the
range of physical validity in the geostrophic system.  This derivation depends on
the assumption of a constant Coriolis parameter.

A completely different approach to the semigeostrophic equations was developed
by Salmon, Shutts, and several others.  They started by using Hamiltonian
methods and were able to include a variable Coriolis parameter.  The stated goal
of the this paper by Magnusdottir and Schubert is ``to examine this question of a
variable Coriolis parameter in semigeostrophic theory, not through the use of
Hamiltonian methods, but by more conventional and elementary methods of
analysis.''  The derivation of a $\beta$-plane version of semigeostrophc theory
depends on the use of isentropic and geostrophic coordinates.  This allows the
entire system to be reduced to one predictive and one diagnostic equation.  The
potential pseudodensity is predicted and the inversion of this quantity leads to
the recovery of the balanced wind and mass fields.

\item{\textbf{Semigeostrophic equations on the $\beta$-plane}}

The governing equations are 
\begin{equation}
    \frac{Du_g}{Dt}-(f(Y)v+\beta(y-Y)v_g)+\frac{\partial M}{\partial x}=0,
\end{equation}

\begin{equation}
    \frac{Dv_g}{Dt}+(f(Y)u+\beta(y-Y)u_g)+\frac{\partial M}{\partial y}=0,
\end{equation}

\begin{equation}
    \frac{\partial M}{\partial \theta}=\Pi,
\end{equation}

\begin{equation}
    \frac{D\sigma}{Dt}+\sigma\left(\frac{\partial u}{\partial x}+
    \frac{\partial v}{\partial y}+\frac{\partial\dot{\theta}}{\partial\theta}
    \right)=0,
\end{equation}
\begin{equation}
    (v_g,-u_g)=\frac{1}{f(Y)}\left(\frac{\partial M}{\partial x},
    \frac{\partial M}{\partial y}\right),
\end{equation}
and 
\begin{equation}
    (X,Y)=\left(x+\frac{v_g}{f(Y)},y-\frac{u_g}{f(Y)}\right).
\end{equation}

\item{\textbf{Vorticity, potential vorticity, and potential pseudodensity
equations}}

The predictive equation in flux form is: 
\begin{equation}
    \frac{\partial\sigma^*}{\partial T}+\frac{\partial}{\partial X}\left(
    -\frac{\sigma^*}{f}\frac{\partial M^*}{\partial Y}\right)+
    \frac{\partial}{\partial Y}\left(\frac{\sigma^*}{f}
    \frac{\partial M^*}{\partial X}\right)+
    \frac{\partial}{\partial\Theta}(\sigma^*\dot{\theta})=0
\end{equation}
where $\sigma^*=(f/\zeta)\sigma$ and the total derivative in geostrophic space
has been used.

\item{\textbf{Invertibility principle}}

The potential pseudodensity ($\sigma^*$) is a combination of the mass field and the wind field, both
of these are
related to $M^*$ and as a result, $\sigma^*$ depends only on $M^*$.  To do this we need to use the
geostrophic, hydrostatic, and coordinate transformation relations.  The invertibility system is
given by eqs. 4.3a,b,c.  Has this been solved?  A multigrid solver developed by Fulton (1989) was
mentioned to solve the $f$-plane case.  Is there any chance of a similar multigrid solver being
developed for the spherical version of semi-geostrophic case?

\item{\textbf{Concluding remarks}}

A closed system for predicting the potential pseudodensity has been derived.  The advantage of this
system of the quasi-geostrophic system is the implicit inclusion of the ageostrophic advection in
the coordinate transformation.  A general method of derivation for similar semigeostrophic systems
emerges from this paper.  This system starts with the geostrophic relations, geostrophic
coordinates, and the 'canonical' momentum equations.  These relations are then used to derive the
appropriate momentum equations, and the ageostrophic advection will automatically be implicit.  This
has already been extended to the hemispheric case in spherical coordinates.  Can a different balance
condition be assumed that allows a fully global theory to be developed?

Geostrophic Relations: 
\begin{equation}
    \left(v_g,-u_g\right)=\frac{1}{f(Y)}\left(\frac{\partial M}{\partial x},
    \frac{\partial M}{\partial y}\right).
\end{equation}
Geostrophic Coordinates: 
\begin{equation}
    \left(X,Y\right)=\left(x+\frac{v_g}{f(Y)},y-\frac{u_g}{f(Y)}\right).
\end{equation}
The `desired' canonical momentum equation: 
\begin{equation}
    f\frac{DY}{Dt}=\frac{\partial M^*}{\partial X}, \qquad 
    -f\frac{DX}{Dt}=\frac{\partial M^*}{\partial Y}
\end{equation}
These equations can then be used to derive the corresponding zonal and meridional momentum equations
for the semigeostrophic system.  
\end{enumerate}

Paper Summary

Title: \textbf{Semigeostrophic Theory on the Hemisphere}

Authors: Gudrun Magnusdottir and Wayne Schubert

J. Atmos. Sci., 1991

\vspace{0.25in}

\begin{enumerate}

\item{\textbf{Introduction}}
The original semigeostrophic theory developed by Hoskins, only applied to the $f$-plane.  Using an
approach based on Hamilton's principle, Salmon and Shutts were able to include the effects of a
variable Coriolis parameter.  Using a more `conventional' approach, outlined above, Magnusdottir
and Schubert (1990) were able to generalize the theory to the $\beta$-plane.  In this paper, the
authors further generalize the geostrophic balance and coordinates to derive a hemispheric version
of the theory.  This theory is appropriate for the study of midlatitude dynamics when the
sphericity of the Earth is an important feature of the system.  The primary weakness of this theory
is its lack of validity in the equatorial regions.

``Both the definitions of the geostrophic wind and the spherical geostrophic coordinates are
generalizations of the $\beta$-plane definitions.''  Is this problematic?  The $\beta$-plane is
mathematically a bit odd and doesn't correspond to a physically realizeable situation.  Should the
hemispheric version of semigeostrophic theory be derived from a more physically sound base?

\item{\textbf{Generalizations of the geostrophic momentum approximation and geostrophic 
coordinates}}

The equations for the spherical geostrophic momentum approximation reduce to the primitive
equations when ($u_g,v_g$) are replaced by ($u,v$) and $\Phi$ is replaced by $\phi$.  Maybe they
aren't really based on the $\beta$-plane equations in a problematic way as much as a simplification
of the primitive equations.

The geostrophic relations are: 
\begin{equation}
    \left(v_g\frac{\cos\Phi}{\cos\phi},-u_g\frac{\cos\phi}{\cos\Phi}\right)=
    \frac{1}{2\Omega\sin\Phi}\left(\frac{\partial M}{a\cos\phi\partial\lambda},
    \frac{\partial M}{a\partial\phi}\right), 
\end{equation}    
the geostrophic coordinates are:
\begin{equation}
    (\Lambda,\sin\Phi)=\left(\lambda+\frac{v_g}{a2\Omega\sin\Phi\cos\Phi},
    sin\phi-\frac{u_g\cos\Phi}{a2\Omega\sin\Phi}\right).
\end{equation}

These definitions are justified because they lead to the canonical momentum equations
\begin{equation}
    2\Omega\sin\Phi a\frac{D\Phi}{Dt}=\frac{\partial M^*}{a\cos\Phi\partial\Lambda},
\end{equation}
\begin{equation}
    -2\Omega\sin\Phi a\cos\Phi\frac{D\Lambda}{Dt}=\frac{\partial M^*}{a\partial\Phi}
\end{equation}

This system maintains several fundamental conservation principles of the primitive equations.  The
absolute angular momentum, the kinetic energy (evaluated geostrophically), potential vorticity, and
potential pseudodensity.

\end{enumerate}

Paper Summary

Title: \textbf{Vorticity Coordinates, Transformed Primitive Equations, and a Canonical Form for
Balanced Models}

Authors: Wayne Schubert and Gudrun Magnusdottir

J. Atmos. Sci., 1994

\vspace{0.25in}

Following the general method of derivation outlined above, this paper derives the generalized 
Geostrophic relations as: 
\begin{equation}
    u=\frac{\partial \chi}{\partial x}+\frac{1}{2}f\left[(X-x)\frac{\partial Y}{\partial x}
    -(Y-y)\left(\frac{\partial X}{\partial x}+1\right)\right],
\end{equation}
and 
\begin{equation}
    v=\frac{\partial \chi}{\partial y}+\frac{1}{2}f\left[(X-x)\frac{\partial Y}{\partial y}
    -(Y-y)\left(\frac{\partial X}{\partial y}+1\right)\right].
\end{equation}
These can be reduced to the `normal' geostrophic relations as discussed on page 3311. 
These equations are also known as the Clebsch representations of the velocity field.  The view of
the Clebsch equations being generalizations of the geostrophic coordinates is realized by makeing
the geostrophic approximation, can the same thing be done with the rotational part of the wind?

Notes to self:  There are at least two important elements of semigeostrophic theory.  First, the
implicit inclusion of the ageostrophic wind allowing the semigeostrophic system to use the total
wind for advection rather than just the geostrophic part of the wind.  The second component is the
nonlinear invertibility principle. It seems likely that the first of these is much more important,
if we can keep the ageostrophic wind in the advective terms, but we have to linearize the
invertibility priniciple to solve it, the model will still be much better than the geostrophic
system.

\end{document}

### 2019-09-16 review_Park_etal_2014.tex
First commit for latex repo

\documentclass[11pt, oneside]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}

\title{Review: Extratropical SST key to understand the discrepancy in future Sahel rainfall projections}
\author{Jong-yeon Park, J{\"u}rgen Bader, Daniela Matei; Reviewed by Levi Silvers}
%\date{}							% Activate to display a given date or no date

\begin{document}
\maketitle

\section{General Comments}

\subsection{Overview}

This is a nice study that highlights, and seeks to resolve, a major discrepancy between various projections of rainfall in the Sahel region.  Trying to better understand what mechanisms can lead to precipitation changes as a result of changing greenhouse gas forcing is an inherently interesting subject.  From a technical point of view it is clearly important to understand why different models produce different results.  From an economic point of view the possibility of changing locations for deserts and regions of significant rainfall is also quite important.

The sensitivity experiments that use ECHAM are very nice and add strength to your analysis.  I liked the fact that ECHAM seemed to have a relatively neutral prediction of future Sahel rainfall (S1).  This contrasts well with the GFDL and MIROC models.  It is helpful to show the reader that your hypothesis can be verified with the use of a separate model, and that simply by changing the forcing you can arrive at similar results to the GFDL and MIROC models.

This will be nice paper and make a useful contribution towards a better understanding of both what the atmosphere does over Africa, and why the model ensemble mean is such a poor indicator of the individual models.

\subsection{Questions}

Figure 2 seems to demonstrate your point very well and the contrast between 2.b and 2.d is striking.  It seems that you could almost tell the whole story with this figure.  I have a few questions regarding this figure, and the analysis of the indices in general.  After returning to Figure 2 another time I noticed that the correlation between 2.b and 2.d is similar, could one conclude from this simply that the Sahel rainfall is anti correlated with the tropical index?  Maybe this points to a clear connection between the tropics and extratropics.  Am I correct in thinking that the coefficients of the multi-linear model are computed from the historical simulations?  What does the same analysis show when the coefficients are computed from the RCP 4.5 simulations or from different time periods in the historical period?  For a topic such as future Sahel rainfall, the ensemble mean prediction of the models does not seem too useful, but a mechanistic understanding of what the possible future scenarios could lead to would be interesting and useful.  I think this is what you are trying to do.

I don't think that I agree with the sentence that begins on line 69 with `However, they fail...'.   The fact that the indices differ from the MIROC-ESM does not make it clear to me that the index has failed, perhaps the model is misleading us here?  This raises the general question of which model simulations the authors tend to trust/believe and why.  Figure S1 shows the full range of possible projections.  Is there a physically motivated reason to trust, or to try and develop indices that fit with, the MIROC models?  Perhaps this reveals my lack of knowledge about the observational record, but what do the observations over the past decades in the Sahel tell us?  Is it clear that the rainfall in that region is increasing?

Figure S1 is quite striking, and nicely shows the problem you are working on resolving.  It is noteworthy that all of the MIROC models are grouped together at the extreme end of the figure.  It looks like the Ensemble mean would be almost zero without them.  Figure S2 shows that several of the models which produce wet conditions  also have amplified NH extratropical SST warming.  This is  a good point, and used well in the paper but I am still curious what is really going on in the MIROC models that makes their response so different to the others.  It seems that this study is essentially a comparison of the predicted Sahel rainfall between the GFDL model and the MIROC model.  Do we have a good reason to think that one is a better representation of the Earth system than the other?

I am not sure what the correct, or the most standard method in publications for expressing tenses is.  As a result, sometimes it seems that a statement should be presented in the past tense, and sometimes in the present tense.  An example would be line 14, should `found' be in the past tense as you wrote, or in the present tense?  My inclination is that it should be in the present tense, but I am not grammatically certain.

Why were the names 20C and 21C chosen for the sensitivity experiments?  I am not saying the names need to be changed, but simply that the idea behind the names could be stated to help the reader.  These names could be confusing to the reader if they refer to experiments in which the SST are not constant.  If they indicate the mean values of SST than that should be stated.  Perhaps I missed it.

Do you need to mention both CMIP3 and CMIP5 models?  It could simplify both your abstract and some of the text to simply state that the model discrepancies are present for both phases of the comparison rather than stating it first for CMIP3 and then also discussing the persistence of the model spread for CMIP5.

The sentence which begins on line116 is a bit confusing to me.  Why does this choice of model emphasize what you claim?  In particular, you state that anomalies may be a more dominant driving factor than SST patterns, but this is not obvious to me.  Has this been shown to be the case in other literature?  In general I would guess that patterns would be more important than anomalies, but I do not now.  Are the patterns the same between the various models that you are comparing?  I realize this could open up an entire additional line of research and that it can't all be discussed in this paragraph, but I do think the sentence you have could be further clarified.  Maybe a future paper could examine the dynamical influences of SST patterns in contrast to anomalies?

ln 63 of Supp. Material: I think ECHAM6 is being used to analyze predictions of Sahel rainfall, not the actual Sahel rainfall.

As far as I could see in the paper, all of your analysis covered the months of July, August, and September.  What happens with rainfall in the Sahel during the rest of the year?  Is there as large of a discrepancy among the models for the rest of the year?

Concerning the paragraph in the supplementary material that begins on line 111.  This argument seems reasonable to me, but at first I was confused by the use of the terms `reduced low-level pressure' and `reduction of low-level pressure'.  Initially I thought the magnitude of the low-level system was decreasing, which I believe is opposite your argument.  If you want to leave this the same it is probably ok.  One option for clarity would be to discuss strengthening and weakening of the system which seems to convey a sense of the change in magnitude well.

\section{Spelling/grammatical corrections}

       {\bf  Primary Article}

	\begin{enumerate}

	  \item ln 11, 17:  twenty should be twentieth
	  \item ln 15: I think that changing found to either find or show would be a more natural expression.  See comment above about tenses.  
	  \item ln 63: combination should be plural
	  \item ln 67: `Such statistical model and indices' should be either `Such statistical models and indices' or `Such a statistical model and indices'.  You could also simply say, `Such indices       are similar...' , but that changes the meaning a little bit.  
	  \item ln 70: The end of the sentence which ends on this line should read either `an opposite sign of the trend' or `opposite signs of the trend'.  
	  \item ln 95: I think that  `for future Sahel,'  should  be changed to `for future Sahel rainfall,'.  This could also be a natural breaking point if you want to break the long sentence into two, the second one starting with `The model discrepancy...'  but this is definitely a matter of personal preference.  
	  \item ln 111: `dry' and `wet' here are grammatically incorrect.  There are several possible options such as drying, moistening, becoming more dry etc.  
	  \item ln 117: There should be a `the' before CMIP5.
	  \item ln 118: emphasize should be emphasizes.
	  \item ln 119: This is probably correct as is, but in my opinion the sentence would be cleaner if both `rather' and `different' are dropped. 
	  \item ln 159: There should be a `the' before West.
	  \item ln 161: concerns should be concern.  
	  \item ln 162: This sentence is not so clear.  In particular, what is `its' referring to?  The way this reads, `its' could be the calamities or the rainfall projections.  I could guess that you mean rainfall projections, but I think it can be clearer.      
	  \item ln 166: This should either read `to get a more reliable estimate of' or `to get more reliable estimates'.  
	  \item ln 167: relative should be relatively
	  \item ln 177: `has' should be either `has been' or `was'.
	  \item ln 184: is should be are.
	  \item ln 187: `fitting' should be `fit', there should be a `the' before least-squares.  
	  \item ln 190: There should be a `The' at the beginning of this sentence. 
	  \item ln 192: `has' should be `have'.
	  \item ln 194: `is' should be `are'. 
	  \item ln 197: Do you mean `forced' instead of `prescribed' both here and in line 199?  If you do mean `prescribed' then I think the sentence needs to be reworked a little.  
	  \item ln 198: There should be a `the' before twentieth.  
	  \item ln 200: `is' should be `are'.

	\end{enumerate}

     {\bf Supplementary Information}

	\begin{enumerate}
	  \item ln 12: Should start with either `Although the multi-model ensemble mean shows a...' or `Although multi-model ensemble means show a...' 
	  \item ln 20: There should be a `the' before major challenges and `response of global' should be `response to global'.  
	  \item ln 23: I am pretty sure that Northern Hemisphere should be capitalized.  
	  \item ln 24:  I am a bit confused by this sentence.  Perhaps `stronger' should be replaced by `distinct'?  We can talk about this if you want.  
	  \item ln 61: `show'  should be `shows'.
	  \item ln 83: The symbol used between your two concentrations of $CO_2$ is not clear. 
	  \item ln 99-103: This sentence should be restructured, I think it is not so clear.  
	  \item ln 112: `the' before reduction should be an `a'. 
	  \item ln 116: `wind' should be `winds'.
	  \item ln 129: There should be a `the' before both Tropical and African.  
	  \item ln 142: The `a' before clear evidence should be omitted.    
	\end{enumerate}

\section{Figures}

\begin{enumerate}
  \item Figure 1, in the caption, `twenty-century' should be `twentieth-century'.  
  \item Figure 3, in the caption, `represent' should be changed to `represents an'. 
  \item Figure 4, ln 320 `centuries' should be `century'.  
  \item Figure 4, It looks like the color bars are identical.  I would then remove one (top), and then make 4.a and 4.b the same size as 4c-d.  Feel free to ignore this comment if you prefer otherwise.  
  \item Figure 5 ??  Is this figure 5?  There is no label and no caption.  You need a caption.  What region is being referred to in the title?  The line in the plot should be clearly marked.  You seem to have the same issue with the last figure of the supplementary material.  Is this just a software issue that didn't format you material correctly?  I also don't have a label or caption for the last figure of the supplementary material.  Neither of these figures seem to be discussed in the text and it is not clear what they add to the paper.  Perhaps they are not needed at all?  
  \item Table S1   In my opinion, `experiments prescribed by SSTs' would be clearer if it was ` experiments using prescribed SSTs'.  
  \item Figure S3 ln 233 rainfalls should be rainfall
  \item Figure S5 ln 256 `twentieth' should be followed by `century'.
  \item Figure S10  I think that `Closed' should be `filled'.  All of the circles are closed.  
\end{enumerate}

%\subsection{}

\end{document}

### 2019-09-20 Silvers_Schubert_reply.tex
committing a number of old tex files into the latex_git repo

\documentclass[11pt]{article}

\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\setlength{\footskip}{0.5in}
\setlength{\hoffset}{-1in}
\setlength{\voffset}{-1in}
\setlength{\oddsidemargin}{1.25in}
\setlength{\evensidemargin}{1.25in}
\setlength{\topmargin}{1.0in}
\setlength{\textwidth}{6.0in}
\setlength{\textheight}{9.0in}

\begin{document}

\noindent Manuscript: ``A Theory of Topographically Bound Balanced Motions and Application to Atmospheric Low-Level Jets"

\noindent Authors:  L. G. Silvers and W. H. Schubert

\noindent Date:  23 March 2012

\bigskip
\centerline{Response to Reviewer 1}

\vskip 0.5 cm

\noindent{\bf Major comments:}

\medskip
\noindent{\bf (1)}  The reviewer makes some important points here. We have followed the reviewer's 
advice and moved to an appendix all the mathematical detail concerning the derivation 
of the analytical solution. We have retained in section 3 the important Figures 6--8 and 
the formulas (Equations (17), (18), (20)) from which they are constructed. This reorganization 
does streamline the body of the paper. Concerning the work of Eliassen, his argument is in 
density coordinates rather than isentropic coordinates, with assumptions that cause a loss of 
distinction between $p$ and $\Pi$.  The authors feel it is helpful to present the argument 
in isentropic coordinates because this provides a clarifying step towards 
understanding the dynamics of cyclonic flows around a mountain with a non-isentropic surface.

\medskip
\noindent{\bf(2)}  We believe Reviewer 1 is basically correct in his statement about the 
fundamental assertions of the paper. Concering the first (that two dimensions are adequate), 
this seems acceptable to a first approximation, but note that, since real topography is very 
complicated, we included a brief discussion of the three dimensional, spherical case at the 
end of the paper. Concering the third (that surface potential temperature trumps interior PV), 
we have included some additional discussion (see also the response to major comment 3).    
We have spent the most time on the second point (that the time-mean low-level flows are 
balanced) and have followed the Reviewer's suggestion and computed the geostrophic winds 
from the YOTC geopotential field on isobaric surfaces. The result is that the actual winds 
and the geostrophic winds match well if a light horizontal smoother is applied to the 
geostropic winds. The fact that the geostrophic winds have some noise in them is
probably associated with the fact that the analysis fields are produced by interpolating 
(to isobaric surfaces) the results of the ECMWF hybrid vertical coordinate data. 
We have included some additional discussion of these points, but have tried to keep 
it brief, since it could easily take us on a tangent.

\medskip
\noindent{\bf(3) }  The following text was added, starting in line 98: 
``A complete potential vorticity 
based analysis of LLJs would have to include both the 
potential vorticity at the surface that results from a gradient of potential temperature 
and the potential vorticity of the interior flow.  The surface component is related to 
radiative heating and the atmospheric stratification while the interior component 
is due to convective activity, absolute vorticity, or the stratification.  The interaction 
between the interior quasigeostrophic potential vorticity and the surface gradient of 
potential temperature was reviewed by Hoskins et al. (1985).  A nongeostrophic 
generalization was applied to a wake circulation on the lee side of a mountain by 
Schneider et al.~(2003).  We here focus on the surface potential vorticity.  We do not 
assume that the affect of the surface potential vorticity is greater than that of the 
interior potential vorticity, we are simply demonstrating that LLJs are impacted 
by this surface potential vorticity. ''

The following text was added, starting in line 61:
``Much of the previous research on LLJs can be loosely grouped into two categories.  
The first includes boundary layer processes and forcing on relatively short (diurnal-a few 
days) times scales.  Relevant studies include Blackadar (1957), Holton (1967), Jiang 
et al. (2007), and Rife et al. (2010).  These studies were particularly interested in 
determining the physical mechanisms behind the diurnal oscillation and the phase that 
is observed in many LLJs.  The second category deals mostly with the synoptic-scale, 
monthly or seasonal mean structure of LLJs and includes studies such as Wexler (1961), 
Byerle and Paegle (2002, 2003), and Ting and Wang (2006).  These two groups certainly 
have some overlap.  The research presented here examines the influence of 
topographically bound balanced motions on the synoptic-scale, warm season mean structure of LLJs.''

Also please see the response to reviewer 2 comments 6 and 15.  Text was added which references 
other appropriate studies and provides more historical background.

Further concerning Ting and Wang (2006):
In the abstract of Ting and Wang (2006), they state: ``the effect of thermal forcing is negligible'' 
on the LLJ of the Great Plains.  However, at the end of section 3 in their paper they state, `both thermal 
forcing and transient eddy forcing due to the presence of North American topography play a secondary 
role in the generation and maintenance of the Great Plains LLJ.''  This is confusing to the reader because 
`negligible' is not generally interpreted as `secondary'.  We are not in this study claiming that the heating 
of mountains is the primary generator of LLJs, but simply that it is an additional mechanism that is 
important.  In this regard our conclusions do not seem to be in contradiction with the conclusions of 
Ting and Wang in their section 3.  We also agree with them with the result that one of the dominant 
effects of topography is to force a cyclonic center over the Rocky Mountains (see their pg 1061).

However, the primary difficulty in direct comparisons of our work with other research on the topographic influences 
to the atmosphere is the fact that our model does not include a background flow, while the majority of other 
topographic studies (Ting and Wang, 2006 Rodwell and Hoskins 2001, etc.) do.  Often the fundamental results of 
these studies are dependent on the particular background flow that is assumed to be interacting with the 
topography.  We are simply computing the steady state response that must result from surface PV anomalies.  
The total atmospheric response to topography will include our results plus those of studies that include a nonzero 
background flow.

\bigskip
\noindent{\bf Minor comments: }

Please note that several minor changes and corrections were made to the captions of the figures.

\medskip
\noindent{\bf Figure 1.} Based on Reviewer 1's and Reviewer 2's comments, we have created 
a new Figure 1, using YOTC data.

\medskip
\noindent{\bf Figure 1 caption.} The reanalysis data are every six hours, as is now noted in the caption.

\medskip
\noindent{\bf Line 29. }  Added ``These are two-month mean warm season wind fields averaged using the 
times 0, 6, 12, and 18 UTC."  to lines 29 and 30.

\medskip
\noindent{\bf Line 31} was changed from, ``The YOTC analysis is available from May 2008 through 
April 2010 (see Waliser et al.~2011).'' to, ``The YOTC analysis is available for the two year 
period between May 2008 and April 2010.  Although originally proposed to be a one year research 
program YOTC was extended for an additional year in order to capture a cycle of both La Ni\~na 
and El Ni\~no.'' The sentence,``Two-month means from the summer season in each hemisphere were 
chosen for display." was deleted because it is redundant after the above additions.

\medskip 
\noindent{\bf Line 30. }  This was changed to ``with 15 irregularly spaced vertical levels''.  
This is the highest vertical resolution available when using YOTC data.  These levels are as 
follows in hPa: 1000, 950, 925, 900, 850, 800, 700, 600, 500, 400, 300, 250, 200, 150, and 100.  
We included the actual levels below 400 hPa in the caption of Fig.~2.

\medskip
\noindent{\bf Lines 36--38.}  We intended to imply that the colder ocean has an impact on the structure of the,
isentropes, not simply that the colder a surface is the lower the jet.  Clarifying this is a good suggestion.  
We removed the part ``Due to the relatively cold eastern Pacific" so 
that it now reads simply as ``The coastal LLJs tend to have a wind maximum that is closer to the 
surface than the jets to the east of the mountain ranges.''

\medskip
\noindent{\bf Lines 38--40.}   We have tried to soften this statement, and present our interpretation in a 
straightforward manner.  We are simply implying that the coastal LLJ is undoudtedly influenced by the 
Pacific anticyclone to the west.  This would also be true of the GPLLJ if it was nearer to the Atlantic 
anticyclone.

\medskip
\noindent{\bf Equation 2.}  We followed the reviewer's comment and left $f$ outside of the $x$-derivative.

\medskip
\noindent{\bf Line 116.}  Equation (6) can be obtained by either taking the quotient or the difference of 
equations (2) and (5).  If the reviewer would like both of these possibilities mentioned in the 
text we could write, ``The following equation can be obtained by taking either the difference 
or the quotient of (2) and (5).'' in place of line 116.

\medskip
\noindent{\bf Line 130ff.}  Added just after equation (8): where $\tilde{p}(\theta_B) = p_0$.

\medskip
\noindent{\bf Lines 142--143.} Good point. To better justify the reference state 
profile, we have compared it to Figs.~2 and 3, by adding the following. 
``Although idealized, this reference state profile, with $\theta=331$ K 
at 400 hPa and $\theta=295$ K at 1000 hPa, can be considered typical of the 
profiles found at different locations in Figs.~2 and 3, noting of course that 
the actual values of $\theta$ on the lower boundary in Figs.~2 and 3 have 
a relatively wide range because of the contrast between the cold ocean and 
the warm continent."

\medskip
\noindent{\bf Line 151.} We start with the definition $M-\theta\Pi=\phi$. We then differentiate 
this with respect to $x$ at fixed $\theta$, obtaining 
$(\partial M/\partial x)_\theta-\theta(\partial\Pi/\partial x)_\theta=(\partial\phi/\partial x)_\theta$. 
We then use the geostrophic equation and the thermal wind equation to obtain 
$f[v-\theta(\partial v/\partial\theta)]=(\partial\phi/\partial x)_\theta$, which applies on 
any $\theta$ surface. When it is applied at the $\theta=\theta_B$ surface, we get the lower 
boundary condition. We never get the term $\Pi(\partial\theta/\partial x)_\theta$, assuming 
that is what was meant by $\Pi(d\phi/dx)$ in the comment.

\medskip
\noindent{\bf Lines 207--209.}  ``$\theta_T=360$K is used throughout this study."  was added to line 183.

\medskip
\noindent{\bf Lines 222-223.}  To better illustrate this we have added the following sentence. 
``For example, the actual crest heights shown in the two panels of Fig.~2 are approximately 
4200 m (at 21S) and 3700 m (at 30S), both of which are considerably higher than the critical 
crest heights from the two curves labeled $20^\circ$ and $30^\circ$ latitude in Fig.~8."

\medskip
\noindent{\bf Line 247.}  Yes, we think your interpretation is better, and we 
have modified the text to that wording.

\medskip
\noindent{\bf Line 322. }  To be more precise, the wording here was changed to 
$\Delta\theta=(\theta_T-\theta_B)/N_\theta=65/450=0.144\bar{4}$ K.

\medskip
\noindent{\bf Lines 399--400.}  Concerning the pressure and wind fields in 
the massless layer, we have added the following near the end of section 4. 
``Obviously, the pressure and wind fields in the massless layer do 
not have direct physical meaning. They can be simply regarded as 
a consequence of formulating (and discretizing) the invertibility 
principle on a domain (and grid) that is uniform in $(x,\theta)$ space, 
even though $\theta$ is not uniform on the lower boundary."

\medskip
\noindent{\bf Lines 416--419, and Lines 419--420. } The reviewer raises an important point here. 
Since our paper deals with the invertibility principle rather than the evolution equation 
for PV, we have rewritten this paragraph as follows. 
``The structure of the isentropes for the cases with a warm lower boundary is quite different.  
Near the mountain the isentropes bend downward toward the warm mountain crest. Isentropes that 
intersect the mountain can be considered to run along the mountain crest until they erupt on 
the other side of the mountain. With this interpretation, there is an infinitesimally thin
massless layer of infinite PV on the the mountain crest. Then, by the invertibility principle 
and with uniform PV along isentropes that do not intersect the mountain, there is a cyclonic 
flow with a low-level jet on each side of the mountain."

\medskip
\noindent{\bf Lines 421--426.}   We have rewritten this paragraph as follows. 
``Each of Figs.~11--14 show the wind maxima to be in the lowest layers of 
the fluid and to decay rapidly in the vertical and horizontal directions.  
This matches fairly well with the basic characteristics of observed low-level jets, 
although inclusion of surface friction and boundary layer effects in the theoretical argument 
is probably necessary for accurate placement of the height of the jet maxima. 
In agreement with the insights offered by the invertibility principle, these 
figures show increased (decreased) mountain top vorticity when the isentropes 
are stretched (compressed). These figures clearly indicate that in the absence 
of other factors a sufficiently heated surface will result in a cyclonic wind field.
It is also clear that the jets of opposite sign on either side of the ridge are 
two parts of the response to the forcing, i.e., a sufficiently heated ridge leads  
to a pair LLJs that form a cyclonic couplet. Finally, it is important to remember that 
the balanced, potential vorticity arguments given here apply to the time-averaged 
flow and that there are important superimposed diurnal oscillations (not accurately 
captured by PV invertibility arguments) of the 
type studied by Blackadar (1957), Holton (1967), and Jiang et al.~(2007)."

\medskip
\noindent{\bf Line 429. }  Yes, the term ``couplet" is a good one, and is now used.

\medskip
\noindent{\bf Lines 431--432. } In response to the reviewer's comment we have changed  
``potential vorticity anomalies associated with heated topography'' 
to, ``thin sheet of surface potential vorticity that is the result of the potential temperature anomalies 
along the heated topography''

\medskip
\noindent{\bf Lines 451--453.} Good point. To clear this up we have modified this 
discussion as follows. ``Byerle and Paegle (2003) have discussed the seasonal 
transition from cyclonic to anticyclonic flow in the context of the Great Plains 
low-level jet.  The results presented here suggest that this transition 
is due to the winter potential temperature anomaly dropping below the 
critical value that is needed for a cyclonic circulation."

\bigskip
\bigskip

\noindent PS to Reviewer 1: Thank you for your detailed and insightful review, which has resulted in 
substantial improvements.

\newpage

\noindent Manuscript: ``A Theory of Topographically Bound Balanced Motions and Application to Atmospheric Low-Level Jets"

\noindent Authors:  L. G. Silvers and W. H. Schubert

\noindent Date:  23 March 2012

\bigskip

\centerline{Response to Reviewer 2}

\vskip 0.5 cm

\bigskip
\noindent{\bf Specific comments}

Please note that several minor changes and corrections were made to the captions of the figures.

\medskip
\noindent{\bf 1.} In order to relate the present work with that of Hoskins et al.~(1985) 
and Thorpe (1986), the following text was inserted in the 
Introduction. ``The surface potential 
temperature anomaly shown in the center panel of Fig.~4 represents 
a similar balanced flow structure to those studied by Hoskins et al.~(1985) 
and Thorpe (1986). Their work solved the pressure coordinate form of the 
invertibility principle for synoptic disturbances in gradient wind balance, 
while the present study solves the isentropic coordinate form of the invertibility 
principle for synoptic disturbances in geostrophic balance."  The reference to 
Bretherton's work is included later (see number 6 below).

\medskip
\noindent{\bf 2. and 3.} The reviewer makes an excellent point. We have produced a new 
Figure 1 that uses the higher resolution YOTC data.  ECMWF as the source of the YOTC data 
has now been added to the captions for figures 2 and 3.

\medskip
\noindent{\bf 4.} Reviewer 2 raises an important point about interior convective 
heating and turbulence. To improve our presentation we have modified the discussion 
just under equation (7) by adding the following. 
 ``In the numerical calculations presented in section 4, only 
the assumption concerning the vertical profile of $N(\theta)$ will be
retained. In particular, the lower boundary will not be an isentrope, and the 
potential vorticity will not be uniform on those isentropes that intersect the
lower boundary, although we will still assume the potential vorticity is uniform 
on those isentropes that do not intersect the lower boundary. Thus, the
present work considers only those balanced flows associated with surface 
processes, and not balanced flows associated with interior potential vorticity anomalies.
However, it should be noted that cumulus convection and convective turbulence 
over elevated terrain will result in interior potential vorticity anomalies
and associated balanced flows that are not considerered here."

\medskip
\noindent{\bf 5.} Both Reviewers have questioned the ``reality" of the isentropic 
lower boundary case. Following these suggestions, we have delegated most of
this discussion to the Appendix, so only a summary of the analysis now appears 
in section 3. This shortened section 3 is useful in understanding the
anticyclonic case and the concept of a critical height at which isentropes 
must be punctured by the mountain crest.

\noindent{\bf 6.}  The following text was inserted in the first paragraph of section 4.  
``Lorenz (1955) was the first to define a massless 
layer, not in the context of potential vorticity dynamics but in the 
context of available potential energy. Later, Bretherton (1966) showed 
that a potential temperature gradient along a boundary could 
be replaced by a boundary with constant potential temperature provided a 
concentration of potential vorticity very close to the surface is included.  
Bretherton's concept of a dynamical massless layer has been used in 
many later studies, e.g., Hoskins et al.~(1985), Thorpe (1985, 1986), 
Andrews (1983), Fulton and Schubert (1991), Schneider et al.~(2003), 
and Schneider (2005). The isentropic surface that is just at the earth's 
surface over both the topographic feature and in the 
far-field is labeled $\theta=\theta_B$. Then, defining $\theta_S(x)$ as 
the actual value of potential temperature on the topographic surface,  
the region $\theta_B < \theta < \theta_S(x)$ is the massless layer."

\medskip
\noindent{\bf 7.}  The sentence ``The wind field in the massless layer will not, 
in general, vanish when there is a nonvanishing pressure gradient in the massless 
layer." was changed to: ``The wind field in the massless layer will not, in general vanish."

\medskip
\noindent{\bf 8. } The reviewer raises an excellent point. To remove attention 
from any fields in the massless layer, we have included the following statement 
near the end of section 4. ``Obviously, the pressure and wind fields in the massless layer do 
not have direct physical meaning. They can simply be regarded as 
a consequence of formulating (and discretizing) the invertibility 
principle on a domain (and grid) that is uniform in $(x,\theta)$ space, 
even though $\theta$ is not uniform on the lower boundary."

\medskip
\noindent{\bf 9.} Good point. We considered making $f$ negative for application 
to the Andes. However, we decided to yield to the bias of northern hemisphere 
meteorologists and keep $f$ positive.

\medskip
\noindent{\bf 10.}  We have tried to clarify the captions of several figures. 
The difference between above-ground and below-ground wind 
maxima certainly needed to be clarified. We have changed the caption of figure 
13 to point out that the maximum above-ground value is approximately 5 m s$^{-1}$.

\medskip
\noindent{\bf 11.}  The reviewer raises a good point. We have adopted the reviewer's 
suggestion by eliminating the term ``orographically forced tendency for anticyclonic motion" 
from the somewhat altered discussion on page 20.

\medskip
\noindent{\bf 12.}  The following was added, beginning at the bottom of page 16: ``Based on the previous 
discussion of the critical crest height, and Fig.~2 it is clear that the 
Andes are not isentropic.  For a standard atmosphere, (8) can be used to
determine the appropriate range of surface potential temperature between 
the base and the peak of a mountain.  For a 2 km mountain $\Delta\theta$ can 
be shown to be about  7 K.  When the surface is heated due to radiation or 
other processes, as we expect for the Andes, $\Delta\theta$ will be larger.
Figure 2 can be used a rough estimate of how potential temperature varies 
along the surface.  At 30 S, $\Delta\theta$ on the west side is about 9 K and 
on the east side it is about 15 K.  From the null case shown in Fig.~9, it seems that a surface potential 
temperature anomaly of more than 9 K (i.e., an increase from 295 K in the far 
field to 304 K at the mountain crest) is required to produce a cyclone.  
The parameters used in Figures 11--14 were 
loosely based on this reasoning."

\medskip
\noindent{\bf 13.}  In order to relate the model solutions more closely with 
the observations that were shown in Figs.~2 and 3, we have included the following. 
``Even though the result shown in Fig.~14 is from a highly idealized model, it is 
useful to make a rough comparison with the observations shown in Figs.~2 and
3, noting that the sign of $v$ must be reversed (because of the sign of $f$) 
when comparing Fig.~14 with Fig.~2 and that the mountain height and width used 
in Fig.~14 lie between those of the Andes and the Rockies. The strength and 
location of the low-level jets in Fig.~14 are in rough agreement with those in
Figs.~2 and 3, although the observed jets are slighly elevated off the surface, 
perhaps due to surface frictional effects that are not included in the model. 
Two interesting aspects of Figs.~2 and 3 are the complexity of the topography 
and the E-W asymmetry of the $\theta_S(x)$ field, which is related to the cold
sea surface temperatures west of the continents. Although these refinements 
of the $\phi_S(x)$ and $\theta_S(x)$ fields can be included in the model, they
lie somewhat outside the scope of the present paper."

\medskip
\noindent{\bf 14.}  Yes, this refers to the ``surface" line in the lower panels, 
as is now made clear in the text.

\medskip
\noindent{\bf 15.}  We added to the second paragraph of section 5: ``Past studies of the South American LLJ (Vera et al. 2006) and the Chilean 
Coastal LLJ (Jiang et al. 2010) 
have treated these as isolated phenomena. This tendency dominates studies of 
the LLJs in North America as well (see Holton, 1967, Blackadar, 1957, Wexler, 1962, 
Jiang et al. 2007, etc.).''

\medskip
\noindent{\bf 16.}  We dropped the diabatic from `diabatic heating' as recommended.  The sentence in question 
was modified as follows, ``The results presented here clearly show that these two LLJs can be 
attributed to the PV anomaly that is generated by heating of elevated terrain.''

\medskip
\noindent{\bf 17.}  Capitalized ``Southern Hemisphere" on line 24.

\bigskip
\bigskip

\noindent PS to Reviewer 2: Thank you for your insightful review.

\end{document}

### 2019-09-20 Silvers_etal_2016_revised.tex
committing a number of old tex files into the latex_git repo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified July 2014
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format: two column (default)
% and draft.
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER
% ms    JAMES
% ef    EARTH'S FUTURE
% ea    EARTH AND SPACE SCIENCE
%
%
%
% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

\documentclass[draft,ms]{agutex2015}
%\documentclass[ms]{agutex2015}
% To create numbered lines:

% If you don't already have lineno.sty, you can download it from
% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
% (or search the internet for lineno.sty ctan), available at TeX Archive Network (CTAN).
% Take care that you always use the latest version.

% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:

 \usepackage{lineno}
 \linenumbers*[1]
%  To add line numbers to lines with equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables
%
%
% DO NOT USE \psfrag or \subfigure commands.
%
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
%  \usepackage[dvips]{graphicx}
   \usepackage{graphicx}
%
%  Uncomment the following command to allow illustrations to print
%   when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
\authorrunninghead{SILVERS ET AL.}

% Shorter version of title entered in capital letters:
\titlerunninghead{RCE and convective interaction with environment}

%Corresponding author mailing address and e-mail address:
\authoraddr{Corresponding author: L. G. Silvers,
Program in Atmospheric and Oceanic Sciences,
Princeton University,
Forrestal Campus, 201 Forrestal Road, Princeton, NJ 08540, USA.
(silvers@princeton.edu)}

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

\title{Radiative Convective Equilibrium as A Framework for Studying the Interaction Between Convection and its Large-scale Environment}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

%Levi G. Silvers, Bjorn Stevens, Thorsten Mauritsen, and Marco Giorgetta

%Use \author{\altaffilmark{}} and \altaffiltext{}

% \altaffilmark will produce footnote;
% matching \altaffiltext will appear at bottom of page.

% \authors{L. G. Silvers,\altaffilmark{1}
% Eric Brown,\altaffilmark{1,2} Rick Williams,\altaffilmark{3}
% John B. McDougall\altaffilmark{4}, and S. Visconti\altaffilmark{5}}

 \authors{L. G. Silvers,\altaffilmark{1,2}
 Bjorn Stevens,\altaffilmark{1,} Thorsten Mauritsen,\altaffilmark{1}
 Marco Giorgetta\altaffilmark{1}}

\altaffiltext{1}{The Max Planck Institute for Meteorology,
Hamburg, Germany.}

\altaffiltext{2}{Current Affiliation: Princeton University/GFDL,
Princeton, New Jersey, USA.}

%\altaffiltext{3}{Department of Space Sciences, University of
%Michigan, Ann Arbor, Michigan, USA.}

%\altaffiltext{4}{Division of Hydrologic Sciences, Desert Research
%Institute, Reno, Nevada, USA.}

%\altaffiltext{5}{Dipartimento di Idraulica, Trasporti ed
%Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

%% ------------------------------------------------------------------------ %%
%
%  KEYPOINTS
%
%% ------------------------------------------------------------------------ %%

% Key points are 1 to 3 points that the author provides,
% that are 100 characters or less, that are ultimately published
% with the article.
%% for example:
% \keypoints{\item Here is the first keypoint. what happens if it is a
% long keypoint, like this one. We want to see this wrap please.
% \item This is the second.
% \item And here is the third keypoint
% }

\keypoints{
\item Radiative Convective Equilibrium (RCE) is a useful framework to compare, contrast, and harmonize the two extremes of explicit and parameterized convection.
\item Consistent climates across a range of domain sizes encourage the use of RCE to enhance our ability to model clouds (or cloud systems).  
\item The response of low clouds to warming, and hence estimation of the climate feedback parameter, is not robust across configurations.
}

%% Keypoints will print underneath the abstract.

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

% >> Do NOT include any \begin...\end commands within
% >> the body of the abstract.

\begin{abstract}
Simulations of parameterized Radiative Convective Equilibrium (RCE) have been analyzed across a range of domains with areas spanning more than two orders of magnitude ($\mathrm{0.80 - 204 \times 10^6 km^2}$).  It is shown that the simulated atmosphere of a General Circulation Model (GCM) in RCE is sufficiently similar across a range of domain sizes to justify the use of RCE to study both a GCM and a high resolution model on the same domain with the goal of improved constraints on the parameterized clouds.  The simulated climates on different domains are qualitatively similar in their degree of convective organization, the precipitation rates, and the vertical structure of the clouds, relative humidity, and water vapor.  Sea surface temperature perturbation experiments are used to estimate the climate feedback parameter for the differently configured experiments, and the cloud radiative effect is computed to examine the role which clouds play in the response.   Despite the similar climate states between the domains the feedback parameter varies by more than a factor of two; the hydrological sensitivity parameter is better behaved, varying by a factor of 1.4.  The sensitivity to domain size is related foremost to a non-systematic response of low-level clouds as well as an increasingly negative longwave feedbacks on larger domains.  
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%

% The body of the article must start with a \begin{article} command
%
% \end{article} must follow the references section, before the figures
%  and tables.

\begin{article}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\section{Introduction}

Research over at least the past two decades has shown that an uncertain representation 
of clouds, specifically tropical low-level clouds, is currently the largest source of spread among state-of-the-art climate models [\textit{Cess et al.}, 1989\nocite{Cess_etal_1989}, \nocite{Bony_Dufresne_2005} \textit{Bony and Dufresne}, 2005, \nocite{Stevens_Bony_2013}\textit{Stevens and Bony}, 2013\nocite{Popke_etal_2013}].  Specific limitations of modeled clouds include both features which differ from what one observes (e.g., `too few, too bright', \textit{Webb et al.} [2001]\nocite{Webb_etal_2001}, \textit{Nam et al.} [2012]\nocite{Nam_etal_2012}) as well as features which are inadequately understood
(e.g., controls on cloud vertical structure, \textit{Nuijens et al.} [2015]\nocite{Nuijens_etal_2015}, and organization, \textit{Bretherton et al.} [2005], \textit{Muller and Held} [2012], \textit{Wing and Emanuel} [2014]).
An important reason why clouds remain inadequately represented in models, and poorly understood is the  
%These types of features in General Circulation Model (GCM) simulations hint at the interplay between convective and stratiform clouds, as well as the 
delicacy of the interactions between clouds and circulations (\textit{Bony et al.} [2015]\nocite{Bony_etal_2015}, \textit{Sherwood et al.} [2014]\nocite{Sherwood_etal_2014}). 
%which makes it difficult to separate cause and effect.
The characteristics of clouds in GCMs should be represented
in a manner which is consistent with fundamental theory, observations, and more fundamental models of cloud processes, for instance Cloud Resolving Models (CRMs).
Efforts to better understand the role of moist convection in the climate system would be advanced by an ability to simulate the interaction between convection and the large-scale circulation using both models with parameterized convection and models with explicitly simulated convection.     
However, for these types of problems, making a logical and clear connection between CRMs, and large-scale models that parameterize convection is difficult in large part because of the immensely differing range of parameters and large differences in the range of scales simulated, particularly for climate applications.

Global, or large-scale models using Radiative Convective Equilibrium (RCE) with parameterized convection have led to insights concerning tropical energetics of GCMs and the climate sensitivity (\textit{Popke et al.} [2013], \textit{Becker and Stevens} [2014]\nocite{Becker_Stevens_2014}, \textit{Reed et al.} [2015]\nocite{Reed_etal_2015}), and are increasingly being used to study the interplay between convection and large-scale circulations [\textit{Arnold and Randall}, 2015]\nocite{Arnold_Randall_2015}.  
It has also become clear that even with the relative simplicity of RCE, differences in convective parameterization schemes   
%and other processes dependent determined by subgrid-scale parameterizations, 
play a decisive role on the overall statistics of the simulation [\textit{Popke et al.}, 2013, \textit{Becker et al.}, 2016, \textit{Coppin and Bony}, 2015\nocite{Coppin_Bony_2015}].  
Due to the multiplicity of solutions that previous CRM-RCE simulations [\textit{Held et al.}, 2007, \textit{Jeevanjee and Romps}, 2013\nocite{Jeevanjee_Romps_2013}, \textit{Emanuel et al.}, 2014\nocite{Emanuel_etal_2014}, and \textit{Zhou}, 2015\nocite{Zhou_2015}] have produced which depend on parameterizations, domain size, grid-spacing, and surface temperature, we cannot per se assume that solutions of GCM-RCE simulations will be independent of domain size.  Examining these domain size effects using simulations with parameterized convection, extending to near global scales, is the aim of this paper.

Shown in Figure \ref{fig:precvsdom} are images of the total precipitation rate from simulations using the ICON (ICOsahedral Nonhydrostatic) model with parameterized convection on five different domains ranging in size from slightly larger than Texas ($\mathrm{0.80\times 10^6 \, km^2}$; 3/4M), to almost half of the surface area of the Earth ($\mathrm{204\times 10^6 \, km^2} $; 200M).  The precipitating structures organize on the scale of the domain, and show a slight tendency towards stronger precipitation and more organization as the domain size increases.  However, it will be shown that the solutions are
quite similar when measured more statistically, for instance in terms of the mean subsidence fraction, the mean atmospheric vertical characteristics, and 
the mean vertical structure of the simulated atmosphere.
To the extent that the simulated climates of these domains are similar there is reason to think that improved constraints of the parameterized convective response on a small domain, for instance through the application of cloud resolving models, would also improve the parameterized convection of a global simulation.

Although not specifically focused on details of the convection or cloud feedbacks, early studies of RCE [\textit{Manabe and Strickler}, 1964\nocite{Manabe_Strickler_1964}, \textit{Manabe and Wetherald}, 1967\nocite{Manabe_Wetherald_1967}] led to a fundamental advancement in our understanding of the atmosphere.  The overall surface warming from high clouds and cooling from low clouds was first shown by Manabe and Strickler using this ansatz.   Manabe and Wetherald showed the equilibrium surface temperature warming in RCE, 
for a specified change in atmospheric CO$_2$,
is strongly dependent on whether atmospheric relative humidity or absolute humidity is assumed fixed as the surface is warmed.  
In the ensuing decades cloud resolving models were applied to the context of RCE, albeit less in the context of climate change.  So doing allowed assumptions about the structure of the atmosphere, convection, and clouds to be relaxed as more atmospheric processes could be resolved by the simulations.  These pioneering studies have come back into focus with the realization that convective aggregation arises spontaneously from simulations with an explicit representation of convection (e.g. \textit{Held et al.}, [1993]\nocite{Held_etal_1993}, \textit{Tompkins and Craig}, [1998]\nocite{Tompkins_Craig_1998}, \nocite{Bretherton_etal_2005}\textit{Bretherton et al.}, [2005], \nocite{Muller_Held_2012}\textit{Muller and Held}, [2012]), in ways that depend on temperature [\textit{Wing and Emanuel}, 2014]\nocite{Wing_Emanuel_2014}), thereby raising the question  as to its importance for the climate system [\textit{Bony et al.}, 2015, \textit{Mauritsen and Stevens}, 2015\nocite{Mauritsen_Stevens_2015}, \textit{Coppin and Bony}, 2015]. 
The previously mentioned many studies of RCE cover an immense range of domains and resolutions, from domain sizes that marginally resolve convection and its large-scale environment to global scales.

Previous work has shown how fruitful the strategy of linking convective resolving to parameterized convective models can be.  For example 
the observational analysis by \textit{Redelsperger et al.}, [2002]\nocite{Redelsperger_etal_2002} highlighted a strong dependence of tropical convection on tropospheric humidity.  Convective parameterizations were then shown by \nocite{Derbyshire_etal_2004} \textit{Derbyshire et al.}, [2004] not to reproduce this behavior as modeled by CRMs.  Subsequent to this work the convection scheme in the European Center for Medium-Range Weather Forecasting (ECMWF) model was modified to include a dependence on relative humidity of the entrainment rate by \nocite{Bechtold_etal_2008} \textit{Bechtold et al.}, [2008].  These changes led to significant improvements in the representation of the atmospheric variability in the ECMWF model.  Simulations of the diurnal timing of precipitation have also benefited from comparisons between high-resolution idealized models and global, highly parameterized models [\textit{Rio et al.}, 2009\nocite{Rio_etal_2009}, \textit{Bechtold et al.}, 2014\nocite{Bechtold_etal_2014}].   Similarly, past studies have shown how important such features are to the structure and variability of tropical precipitation features, ranging from the Madden-Julien Oscillation to the inter-tropical convergence zone [\textit{M\"{o}bis and Stevens}, 2012\nocite{Moebis_Stevens_2012}, \textit{Oueslati and Bellon}, 2013]\nocite{Oueslati_Bellon_2013}.

Despite these cases of cooperation between studies with high resolution models and highly parameterized models a cleaner experimental configuration in which CRM and GCMs could be compared would be useful.  This paper explores the possibility of using RCE in this context. 
%proposes that RCE can be used in such a context.  
%Comparisons between simulations with and without explicit convection are not presented here; rather, 
Given computational limitations, a pre-requisite is for important features evident on a small domain, over which convection can be resolved, also to be evident on much larger scales.  We analyze the features of an atmosphere with parameterized convection as a function of domain size to explore the applicability of such a configuration.   In the past, such studies have been hindered by the fact that large-scale models used in climate research were structurally restricted to simulations on global scales.

Simulations with ICON using parameterized physics and a coarse grid, commensurate to what one might use for a high-resolution GCM study, and with an explicit representation of convection on a necessarily fine grid are now feasible for domains on the order of $10^6 \, \rm{km}^2$.  This possibility naturally raises the question as to whether such a comparison is likely to be influenced by the choice of the domain size, or whether there are robust features within the simulations that can be expected to emerge irrespective of a given domain size.  Determining what, if any, is the minimum sized domain should also be helpful in this regard.  
%
The recently developed model ICON 
has the flexibility to allow simulations across a range of scales, thereby providing a unifying framework for studying convection at different scales and with different degrees of parameterization.
In addition to simulations with a fixed SST on domains of different sizes (e.g., Fig. 1) simulations are also performed with a warmer SST to test whether the sensitivity of the simulations to warming is sensitive to domain size.   As if not, this raises the possibility of using CRMs directly, on smaller domains, to constrain estimates of climate sensitivity.

The design of the simulations and details of the model used are presented in the next section.  In section 3 results are presented both in terms of the mean atmospheric state, and the response to a perturbation of 4 K to the SST.  Section 3 also 
explores robust differences in the response to warming, and suggests that 
%the framework constrains many aspects of the changes,
many changes in the simulated atmosphere do not depend on domains size, while the climate sensitivity is sensitive to small differences that are not robust across domain sizes. 
Despite having the same core model and identical physics, the total radiative feedback from warming still varies by about a factor of two.   
Discussion and final conclusions are given in section 4.

\section{Experimental Design \& Model Setup}

\subsection{Methodology}

The framework of RCE is used here as a tool which allows us to focus on the interactions between radiation, large-scale circulation, and clouds without the complicating influence of
heterogeneities imposed on the large scale.   Despite the homogeneity of the forcing, the spontaneous emergence of large-scale overturning circulations, as also emphasized by \textit{Popke et al.}, [2013] makes it possible to capture the interplay of clouds with these circulations, in contrast to (for instance) single column model studies. 
%circulation, land surface, or a changing sea surface.  
% driven by heterogeneities imposed exogenously (?implies B.C.'s are outside system).
Two simulations with constant SST values of 297 K and 301 K are made on five doubly periodic domains of different physical extent but all having identical grid spacing.  To eliminate the heterogeneities 
the Coriolis force is set to zero and the insolation and profiles of trace-gases (e.g., ozone) are likewise made independent of the horizontal grid.
The cosine of the zenith angle is $\pi/4$ and the insolation used is $340.3 \, \rm{W/m}^2$, approximately equal to Earth's global annual mean value.  
There is no diurnal cycle and a surface of water at a fixed temperature defines the lower boundary. 
%Complications due to a dynamic ocean and the required long adjustment time are eliminated by prescribing a fixed value of SST.   
One result of this is that neither the surface nor the top of the atmosphere is expected to have a balanced energy budget.  However, the flux of energy into and out of the atmosphere will be balanced once the energy content of the atmosphere equilibrates with its forcing, which, after the initial adjustment period, remains steady in time except for weather related fluctuations.  
This provides a simple framework for analyzing the behavior of the convection and the sensitivity of the feedback processes %which is simpler than AMIP or CMIP experiments.  
yet retains the full complexity of the physics and dynamical equations.   %Within this framework it is possible to study simulations of RCE on doubly periodic domains which span three orders of magnitude in size.

%We chose to vary the size of the domains to test the flexibility of the modeling framework and the behavior of RCE experiments across a range of domain sizes
%with some of the above questions in mind.   By identifying features of the simulations which were not sensitive to the domain size our goal was to identify the potential of performing very high resolution simulations (and hence computationally very expensive) on the same domain sizes to better understand processes influencing convection and its interaction with the circulation.
  The domain size was chosen to range from near global scale to sizes which have begun to be feasible for use with high resolution models (to motivate comparative studies).  
In all, five different domains were considered, the smallest being
$\mathrm{0.80\times 10^6 km^2}$ (or $8 \times 8$ deg in the tropics) and the largest being about the size of the global tropics ($\mathrm{204\times 10^6 km^2}$).  In addition to varying the size of the domain, simulations with different SST values allow us to examine the climatic response to warming perturbations, and compute the total feedback that results from the warming. 
%

Because there are fewer grid points on the smaller domains, the degree of variability in the domain mean per time step increases as the domain size decreases.  
This is because a given perturbation will have a larger influence on the statistics of a domain with fewer grid points, relative to a domain with more grid points.  
%This can be seen, for example, in the domain mean values of the total precipitation (Figure \ref{fig:precipvtime}).  
To obtain comparable statistics between the various domains, and take advantage of the computational economy of the smaller domains, the length of simulation 
increases as the domain size decreases.  Details of the simulations examined in this paper are given in Table \ref{exptable}.   The periods used for computing feedback and sensitivity parameters and cloud radiative effects (P1) and domain mean profiles (P2) are given in Table \ref{exptable}.   The increased length of P1 was necessary to obtain robust statistics for the feedback parameters of the different domains.

\subsection{Model Details}

%We use the ICON general circulation model with parameterizations that represent radiative transfer, convection, cloud-cover, %cloud processes, and boundary-layer turbulence. The label RCE refers only to a simplification of the boundary conditions.  
%ICON solves the fully three-dimensional nonhydrostatic and compressible Navier-Stokes equations and is described in detail in Z\"{a}ngl et al. (2014)\nocite{Zaengl_etal_2014}.

The horizontal grid used in this study consists of equilateral triangles on a plane with periodic boundary conditions in both dimensions.  The ICON model solves the fully three-dimensional nonhydrostatic and compressible Navier-Stokes equations and is described in detail in \textit{Z\"{a}ngl et al.}, [2015]\nocite{Zaengl_etal_2015}.
All of the simulations described here use triangles with an edge length of 20 km, implying an effective grid spacing of about 13 km (defined as $\sqrt{\rm{cell \, area}}$ in \textit{Z\"{a}ngle et al.}, [2015].  The vertical coordinate is a height-based hybrid coordinate with 60 vertical levels between the surface and the model top at 40 km.  The top of the model uses a Rayleigh damping of the vertical wind following \nocite{Klemp_etal_2008}\textit{Klemp et al.}, [2008] to prevent the reflection of gravity waves from the model top. %starting at 25km.  
  The variables are positioned on a regular-triangular C-grid with a combination of first- and second-order finite difference spatial discretizations.  Time integration is computed with a two time-level predictor-corrector scheme with the physics parameterizations split into slow and fast modes.  Further information on discretization aspects of triangular grids are discussed in \textit{Gassmann} [2011]\nocite{Gassmann_2011} and \textit{Wan et al.}, [2013]\nocite{Wan_etal_2013}. The ongoing development of ICON is a joint project between the Max Planck Institute for Meteorology (MPI-M) and the German Weather Service (Deutsche Wetter Dienst: DWD).  Thus ICON has been developed as a unified modeling framework that functions both as an operational weather forecast model and a global climate model.  
%The German Weather Service implemented ICON as their operational weather forecast model in January of 2015.  
ICON can also be used as a Large Eddy Simulation model capable of explicitly representing canonical cloudy boundary layer flows on grid meshes as fine as 50 m or less [\textit{Dipanker et al.}, 2015]. \nocite{Dipanker_etal_2015}

%here (NWP physics, used operationally at DWD) are derived from a combination of the regional COSMO model (Doms and Sch\"{a}ttler 2004) and the Integrated Forecast System (IFS) model at ECMWF.  
The physics parameterizations used 
in the present study are the NWP physics, so named because they are used operationally by DWD in their global implementation of ICON.
The convective parameterization scheme is based on the Tiedtke mass-flux approach with modifications as discussed by \textit{Bechtold et al.}, [2008].  The radiative transfer scheme is an RRTM scheme similar to that used in the IFS model and identical to that of the ECHAM6.1 model [\textit{Mlawer et al.}, 1997\nocite{Mlawer_etal_1997}, \nocite{Stevens_etal_2013}\textit{Stevens et al.}, 2013].  The microphysics scheme is from the COSMO-EU five-category prognostic scheme [\textit{Seifert}, 2008] predicting rain, snow, cloud ice, cloud liquid water, and water vapor. 
Relative humidity is computed over a liquid surface only.  
The cloud cover scheme is based on a box-function probability density function with an added diagnostic anvil term that uses the detrainment of the convective parameterization.  The boundary layer and turbulence scheme relies on a prognostic equation for turbulent kinetic energy [\textit{Raschendorfer}, 2001].  For these experiments gravity waves are not parameterized.   The development of these schemes is ongoing, those used for this study correspond to revision number 16400.  As an additional option to the NWP physics parameterizations used here, a successor to the ECHAM 6 physics is also being implemented into ICON at MPI-M which will be used for climate studies.

 The profile used for the ozone is representative of the tropics and is the same profile used by \textit{Popke et al.}, [2013].  To trigger the adjustment process perturbations of 0.2 K, white in spatial distribution, were applied to the initial potential temperature field in the lowest four model levels.  The initial values of the vertical, $w,$ and one component, $v$, of the horizontal velocity fields are zero.  In the lowest 2.5 km the horizontal velocity $u$ begins with an exponentially decaying profile ($5 \,\rm{m \, s^{-1}}$ at the surface).  
%which is dissipated to near zero within the first few hours of the experiment.  
For the simulations to behave reasonably it was necessary to specify a minimum surface wind velocity scale used only in the computation of the surface fluxes.   This required adding $0.8 \, \rm{m \, s^{-1}}$  to the default value used in the physics ($0.01 \, \rm{m \, s^{-1}}$).  
%to $0.81 \, \rm{m \, s^{-1}}$ where the second significant digit was retained for convenience. 
The initial profiles for potential temperature,  and water vapor are idealized based upon the best fit to profiles from a large-eddy simulation.  The potential temperature was initialized as $\theta=\theta_{\rm{sfc}}+4.8 z$ below the tropopause and as $\theta=\theta_{\rm{sfc}}+4.8 z_{\rm{tp}}+22.0(z-z_{\rm{tp}})$ at and above the tropopause, where $\theta$ is potential temperature ($\rm{K}$), $z$ is height ($\rm{km}$) and the subscripts `tp' and `sfc' represent the values at the tropopause level and surface, respectively.   The water vapor was initialized as an exponentially decaying concentration with a scale height of 2.8 km.
%To facilitate the proper coupling between the surface and the atmosphere under low-wind conditions the minimum value of the %wind vector which is used in the computation of the bulk surface flux formulae was changed from 0.01 $\rm{m \, s^{-1}}$ to 0.81 %$\rm{m \, s^{-1}}$.  
All experiments use the same grid spacing and time step as discussed previously. 
Our choice of grid cell size with an effective grid spacing of 13 km matches that currently used by DWD operationally.

\section{Results}

The progression from homogeneous initial conditions through a period of dominant wave activity and
eventually a stationary state, or equilibrated state 
is illustrated in Figure \ref{fig:precevol}.  This figure shows the time evolution of the precipitation rate on the 50M domain.  After approximately 25 days of near homogeneous conditions fast, large-amplitude gravity waves as seen in the center panel develop and propagate through the domain.  Approximately 30 days later these waves are no longer the dominant feature and have been replaced by multiple convective systems which move slowly through the domain.  In this later stage the mean values of precipitation, relative humidity, and cloud cover fluctuate about a well defined mean value.  It is this mean environmental state represented in the right panel of Figure \ref{fig:precevol} which we refer to as the mean equilibrium state, or stationary state, and which is analyzed in this study.  The other domains show a similar progression from the initial state to equilibrium.

To give an impression of the relative scale of features present on the
$3/4 \rm{M}$, $12 \rm{M}$, and $200 \rm{M}$ domains Figure \ref{fig:convorg} shows the same data from Figure \ref{fig:precvsdom}, tiled according to scale, periodically repeated to fill a region the size of the $200 \rm{M}$ domain.  The $3/4 \rm{M}$, $3 \rm{M}$, $12 \rm{M}$, and $50 \rm{M}$ domains all show the precipitation and moisture structures to organize on the largest scale available (Figures \ref{fig:precvsdom}, \ref{fig:convorg}, \ref{fig:tqv5dom}).  The 200M domain shows signs that the maximum scale of convective organization may be between the 50M and 200M domains, but this deserves further investigation.

\subsection{Mean Climate}

One method of diagnosing whether the atmosphere has reached a statistically stationary state is to examine the time evolution of various quantities.  After an initial adjustment period with large fluctuations in the energetics of the simulations  stationarity is approached.  
%Once this state has been reached the prognostic variables oscillate about a constant mean value.  
In stationarity short temporal fluctuations of domain means, which diminish with domain size and time-scale, are still apparent, reflecting the dynamic state of the underlying system.
The evolution of the domain mean total precipitation during the first two years of simulation for each of the five domains is shown in Figure \ref{fig:precipvtime}.  Based on the precipitation we judge that all simulations have
reached a stationary state after about 200 days, with the $50\rm{M}$ and $200\rm{M}$ domains adjusting to equilibrium much sooner.  Because the $3/4\rm{M}$, $3\rm{M}$, and $12\rm{M}$ domains all proceed for longer than 2 years, the average value of the precipitation during the last six months of each simulation is shown by the dots at the right of Figure \ref{fig:precipvtime}, confirming that the mean value has indeed been reached during the period shown.  
%There is a systematic variation  of the evolution of the precipitation field as a function of domain size but the differences are relatively small (10\%) as compared to the mean.
%have differences between the models, overall the similarity is more striking than the difference with a range of only about $10\%$ amongst the models.  The domain mean precipitation increases monotonically with domain size.  This is likely related to the near monotonic 
Variations in the precipitation field are progressively smaller as the model domain size increases with an apparent convergence in the mean value for the largest domains.  The mean (of all domains, with SST$=301 \, \rm{K}$) precipitation is $5 \, \rm{mm \,day^{-1}}$ with no simulation deviating by more than 7 \%.
The systematic increase in precipitation with domain size is consistent with the systematic
decrease of upper level clouds (Figure 5).  A decrease in upper level clouds will increase the atmospheric radiative cooling and thus require more convective heating 
%to maintain balance.    
in stationarity.

Basic physical characteristics of the simulated atmospheres can be determined by looking at the domain mean 
thermodynamic profiles.
These are shown for the simulations with $\mathrm{SST}=297 \; \mathrm{K}$ in Figure \ref{fig:prof297}.     Cloud liquid water, cloud cover, and RH, all maximize 
in the lowest kilometer.  The RH drops to 
its tropospheric minimum value ($\approx 15\%$) at about 7km.  Between roughly 12km and 16km there is a maximum 
of relative humidity, cloud cover, and cloud ice, due to radiatively driven mass convergence in the upper troposphere in 
clear skies that is satisfied by the detrainment from convective clouds (e.g., \textit{Hartmann and Larson}[2002]\nocite{Hartmann_Larson_2002}, \textit{Zelinka and 
Hartmann} [2011]\nocite{Zelinka_Hartmann_2011}).   All domains have three peaks in the cloud cover (0.6 km, 5 km, 13 km), with the upper two cloud maxima corresponding to anvil detrainment and melting level clouds, respectively.  The simulations also uniformly produce two peaks of cloud liquid water below 4km (0.8 km, 1.2 km).  Overall, the profiles plausibly represent the mean state of the tropical atmosphere (over ocean)
and show agreement among all domain sizes on the vertical structure of the atmosphere.

%An instructive comparison can be made between the our profiles (Figure \ref{fig:prof297}) and those from Figure 4 in P13.   
Our simulations are not only quite coherent across configurations, the vertical structure of the atmospheres is also 
broadly similar to results found in \textit{Popke et al.} [2013].  
%those found in P13.  
%Profiles shown in our Figure \ref{fig:prof297} can be compared with Figure 4 in P13.  
Their Figure 4 compares two Global RCE versions of ECHAM which differ only by their convection schemes, and one profile from the tropical region of a standard pre-industrial control run from the MPI-ESM-LR model.  
%Several points should be noted by this comparison.  
%First, the qualitative match between the profiles found in this study and those of P13 is quite good.  
Comparing the profiles from our Figure \ref{fig:prof297} with Figure 4 from \textit{Popke et al.} [2013] shows that all simulations have a double peak of RH (1 km, 15 km) and a dry mid-troposphere with RH dropping to between 15\% and 20\% at about $7 \, \rm{km}$.  All simulations have two peaks of cloud cover and cloud liquid water in the lowest $4 \, \rm{km}$.  
%In agreement with our Figure \ref{fig:prof297}, the profiles shown by P13 have a minimum value of tropospheric RH of %close to 20\% between about $6-8 \, \rm{km}$, two peaks of cloud liquid water below 4 km, and maxima of cloud ice of %$3-7 \rm{mg \, kg^{-1}}$.     
More importantly, the differences among our domains in Figure \ref{fig:prof297} are equal to or smaller than the differences between the ECHAM simulations resulting from different physics parameterizations in \textit{Popke et al.} [2013].  
%This is particularly apparent in the RH and temperature profiles.  
%In P13, differences in the physics parameterizations lead to temperature 
%differences of several degrees and a vertical shift in the upper maximum of RH humidity by several km's.  
Among the profiles from \textit{Popke et al.} [2013] for example, there is a difference of $2-3 \rm{km}$ in the vertical placement of the RH,  cloud fraction, and cloud ice around $15 \, \rm{km}$.  The RH humidity at $15 \, \rm{km}$ differs by up to $20 \, \%$ and one of the temperature profiles is several degrees warmer throughout the troposphere.  
%These comparisons indicate that RCE does a reasonable job of simulating the broad characteristics of the tropical environment and that there is some similarity between the global RCE ECHAM model and the planar RCE ICON model.  This similarity is not self-evident 
Considering that ICON and ECHAM differ in dynamical core, physics, resolution, domain and geometry, the similarity of the RCE climates they simulate, both to each other and to the tropical environment of MPI-ESM-LR, points to the broad applicability of the RCE framework.

The organization of convection into large coherent structures has received much attention over the previous two decades. 
Several different metrics (subsidence fraction, distance between clusters, bi-modality of water vapor, tropospheric RH, etc. [e.g., \textit{Bretherton et al.}, 2005; \textit{Tobin et al.}, 2012;  \textit{Coppin and Bony}, 2015]) have been used to determine whether aggregation is occurring in observations or simulations.   To provide a quantification of the convective organization the subsidence fraction is computed.  This measures the fraction of the model domain with subsiding motion ($w < 0 \rm{\, m \, s^{-1}}$), typically associated with non-convective regions.  The subsidence fractions for domains 3/4M, 3M, 12M, 50M, and 200M at an SST=297 K (301 K) are 0.72, 0.79, 0.78, 0.76, and 0.77 (0.70, 0.71, 0.75,  0.72, 0.71), respectively.  These were computed using the vertical velocity on the model level at approximately 5.5 km (comparable to 500 mb).  These subsidence fractions are relatively high compared to estimates from reanalysis 
% (Bony $\approx 0.6$; personal communication) 
and consistent with an aggregated state, although the structure (Fig. 1) is somewhat different than one typically sees in global (e.g., \textit{Coppin and Bony} [2015]) or cloud resolving [\textit{Bretherton et al.}, 2005] simulations. 
%confirm that these models are aggregating even though the resulting atmospheric state continues to fluctuate and is clearly not locked into one configuration.            
% the averaging periods for the subsidence fractions are: 3/4M(last year),3M(4months in year 9),12M(4months in year 4),
%50M(2 months in second year),200M(2 months)

%Snapshots of the precipitation rate as shown in Figure \ref{fig:precvsdom} give a basic sense of the spatial structures that precipitating clouds are forming; this can be complemented by the column integrated water vapor.

The column integrated water vapor for each of the domains is shown in Figure \ref{fig:tqv5dom}, at the same periods of time as seen in Figure \ref{fig:precvsdom}.  This reveals the distribution of the moisture content, even in regions which are not precipitating, and in particular gives a quantitative measure of dry regions.  
%The $3/4 \rm{M}$ domain has a smaller range of values compared to the other four models.  
The driest regions for the $3/4 \rm{M}$ domain is relatively moist with $32$mm of vapor in contrast to the largest four domains which have dry regions that drop to about half as much ($17$ mm) water.    Overall the largest four domains show a similar spatial structure of moisture.  There is a slight tendency for the difference between the maximum and minimum values of column water vapor to 
%increase as the domains increase.  
become more pronounced with increasing domain size.

 One clear sign of convective aggregation is an excessively dry mean atmospheric state ($\approx 20 \% \,  \rm{RH}$ between $2-10 \, \rm{km}$ in \textit{Bretherton et al.} [2005] Figure 4a, \textit{Tobin et al.} [2012]\nocite{Tobin_etal_2012}).  This behavior is not 
%seen in our models,
pronounced in the present simulations (Fig. 5),
 rather the relative humidity profiles are comparable to the tropical mean profiles of comprehensive GCM simulations.  However, the time evolution of the cloud fields and water vapor,  
 %clear organization
 the emergent patterns
 of convection on the largest scales of the domains (Figure \ref{fig:precvsdom}), the persistence of a few large patches of water vapor (Figure \ref{fig:tqv5dom}), and the consistently high values of the subsidence fraction 
 %imply that some degree of organization is occurring on the largest scales. 
 are consistent with an aggregated state.

Despite the overall similarity of the mean state among the five domains, there are quantitative differences in the mean cloud and ice fields, and the spatial structure of the clouds and water vapor.   These differences are most pronounced for the smallest ($3/4 \rm{M}$) domain.  The $3/4 \rm{M}$ domain does not aggregate to the same degree as the larger domains, its low level peaks of cloud cover and cloud liquid water are larger by about 30\% and the cloud ice in the anvil region is larger by 50\%.  Both the vertical thermodynamic structure and the time evolution of precipitation appear to show the atmospheres rapidly converging toward a common structure as the domain size increases with the $50 \rm{M}$ and $200 \rm{M}$ appearing practically indistinguishable.      
%The feedback response to a 4K warming of the surface is surprisingly sensitive to these differences.

\subsection{Sensitivity to Sea-Surface Temperature}

Here we examine the response of the RCE simulations to a uniform SST perturbation of $4 \,\rm{K}$.  The difference between the domain mean profiles for the two sets of simulations is shown in Figure \ref{fig:profdiff}.  The basic behavior and mean vertical structure of the simulations with an SST of $297 \, \rm{K}$ is qualitatively similar to those with an SST of $301 \, \rm{K}$.   Similar to the mean state discussed in the previous section, as the domain size increases the spread of the response among the simulations converge %in Figure \ref{fig:profdiff} 
with the cloud cover, cloud liquid water, and cloud ice appearing practically indistinguishable between 50M and 200M.  At higher SSTs the specific humidity rises and temperature warms throughout the atmosphere for all domains with the maximum warming occurring at $13$-$14 \,\rm{km}$.  While the magnitudes differ, the maximum and minimum of cloud cover, cloud ice, cloud liquid water, and temperature occur at similar levels among the domains.

Cloud cover, cloud ice, and RH all exhibit a spatial dipole of positive and negative values between $10$-$20 \, \rm{km}$ that can be explained by a vertical shift of the profiles as the surface warms (Figure \ref{fig:profdiff}).  
%Oscillations between negative and positive values of the change of RH, cloud cover and cloud ice between $10$-$20 \,\rm{km}$ in Figure 7 can be explained by a vertical shift of the profiles as a result of the warmer surface.
For example, the height of the maximum cloud cover from convective anvil detrainment shifts from $12$-$14 \, \rm{km}$ to $14$-$16 \, \rm{km}$. There is variation between individual simulations in the response of the RH, but for all simulations the RH shifts vertically with warming resulting in a consistent increases of RH above $15 \, \rm{km}$ and between $5$-$8 \, \rm{km}$, and drying between $8-15 \, \rm{km}$.  
The RH difference profiles of all domains have fluctuations on the order of $15 \%$ with roughly the same vertical levels of tropospheric maxima and minima and non-systematic fluctuations in the lowest $4 \, \rm{km}$.
%The simulations presented here and the results from P13 show a clear secondary maxima in the cloud cover which seems related to the freezing level.  
The cloud layer at the melting level %In our simulations this maximum 
shifts uniformly for all domains from a height of $5 \, \rm{km}$ when the SST is $297 \, \rm{K}$ to between $6-7 \, \rm{km}$ in the case with a warmer SST.  
%This shift is apparent (Figure \ref{fig:profdiff}) in the spatial dipole of cloud cover between   $4-7 \, \rm{km}$.

Between the surface and about $5 \, \rm{km}$ the response seen in Figure \ref{fig:profdiff} indicates a non-trivial interaction of changing surface fluxes, cloud cover, and turbulent mixing.  
A number of studies have argued that the response of tropical low clouds to warming is decisive for the determination of the cloud feedbacks on warming.  It has been hypothesized that as SSTs rise, enhanced convective mixing dries out the cloud layer and results in less clouds (e.g., \textit{Rieck et al.} [2012]).    \textit{Brient et al.} [2015]\nocite{Brient_etal_2015} showed that models with a pronounced maximum in low cloud amount at cloud base are most susceptible to convective drying, but not through a reduction of clouds throughout the cloud layer, as shown by \textit{Rieck et al.} [2012],\nocite{Rieck_etal_2012} rather by a reduction of cloud amount at cloud base.  This effect is pronounced in our simulations, and
is robust as it appears irrespective of the domain size.

All domains show a pronounced cloud base peak in liquid water, which is systematically reduced as the surface temperature increases.  
To highlight the response of the moisture content in the boundary layer Figure \ref{fig:profdiffzoom} shows the RH, cloud cover, and cloud liquid water from Figure \ref{fig:profdiff}, along with specific humidity (qv), focused only on the lowest $4 \, \rm{km}$.
%To focus on the moisture content in the boundary layer  Figures \ref{fig:profdiff} and  \ref{fig:profdiffzoom} show the same data/field with the latter zoomed in/changed to emphasize on the lowest $4 \, \rm{km}$.  
Although the domains with an SST of $301 \, \rm{K}$ have higher specific and RH in the lowest $600 \, \rm{m}$ the cloud liquid water and cloud cover (except for 3M) decrease there.   Between the surface and $600 \, \rm{m}$ the change of RH, cloud liquid water, and specific humidity decrease with height for all domains.  %Above $600 \, \rm{m}$ the relationship between these four quantities is less clear.  
%Above this level there is a slight increase (between $1-3 \, \rm{rm}$) of cloud liquid water, cloud cover and RH (see Figure \ref{fig:profdiffzoom}).  
A decrease of cloud cover and cloud liquid water in the BL could indicate a deepening BL with dry tropospheric air being entrained from above.  %These changes seem to indicate a deepening BL in response to a warmer surface.  
%In spite of warmer environments having increased surface fluxes and specific humidity, the studies of Rieck et al 2012 and 
%Sherwood et al. 2014 imply that mixing of BL air with the dry tropospheric air above can result in a decrease of BL clouds and RH.  
%These low-level clouds are known to be important components of the total cloud feedback.  
However, the total response of low clouds to warming in GCMs results from a balance between drying from the convective parameterization and moistening by the turbulence parameterization.  
%The complex dependencies of BL depth and low-level cloud feedback (to what?) have recently been studied by Rieck et al 2012, %Sherwood et al. 2014 and Brient et al. 2015.    
%Low-level clouds represent a sensitive balance between surface fluxes of latent and sensible heat, turbulent and convective fluxes of moisture, and low-level atmospheric stability.  
Different balances between these processes were argued [\textit{Brient et al.}, 2015, \textit{Sherwood et al.}, 2014] to be one of the primary factors leading to the spread of total feedback in CMIP models. 
%Their studies also suggested that a boundary layer which dries with warming is often due to strong mixing by the parameterized convection.  
All of our simulations show a uniform decrease of low-level water vapor and cloud liquid water in response to warming but the response of cloud cover and RH is not systematic across domains.  
The implications of this on the feedback parameter will be discussed in the next section.

The partition between convective and large-scale precipitation is likely to influence a model's climate response to warming [\textit{Held et al.} 2007\nocite{Held_etal_2007}].
%The importance of the partition between convective precipitation and large-scale precipitation was noted as a key characteristic of climate models by Held et al. (2007)\nocite{Held_etal_2007}.   
In the present simulations the parameterized convection scheme accounts for almost all (about 90\%) of the precipitation.  Domains with warmer SSTs have less convective precipitation.  A clear connection between the partitioning of precipitation types and the feedbacks was not found.

\subsection{Climate Change Feedbacks and Hydrologic Cycle Sensitivity}

To estimate the climate feedback parameter, $\lambda$, the difference between the top-of-atmosphere radiance in the warm simulation and the cooler 
simulation is normalized by the SST difference, e.g., following \textit{Cess et al.} [1989].   Given the climate feedback parameter the equilibrium climate sensitivity can be computed as $-F_\mathrm{2\times CO_2}/\lambda$, 
for which purpose we adopt a value of $F_\mathrm{2\times CO_2} = 3.7  \, \rm{Wm^{-2}}$ following \textit{Myhre et al.} [1998]\nocite{Myhre_etal_1998}.  The reader is referred to \textit{Sherwood et al.} [2015]\nocite{Sherwood_etal_2015}, for a broader discussion of forcing and feedback concepts.
 This method is arguably the most direct method for estimating the climate feedback parameter. 
%Specifically, the feedback of the system is computed using the change in the top of the atmosphere radiative imbalance divided by the surface warming.  
%In general, an equilibrated climate system, when perturbed by an external forcing ($F$), will have an unbalanced net radiative flux ($ R$) at the top of the atmosphere.  The adjustment process will eventually change the mean surface temperature ($\Delta T_s$).  This change in mean surface temperature will depend on any feedbacks present in the climate system %.  When this process is linear it 
%and can be written as $\Delta R=F+\lambda\Delta T_s$ with $\lambda$ equal to the total feedbacks parameter ($\rm{Wm}^{-2} \rm{K}^{-1}$).  Once the system is equilibrated and $\Delta R =0$  the total feedback parameter  is $\lambda=-F/\Delta T_s$.  
%To estimate the ECS given the feedback, requires an estimate of the forcing from a doubling of $\rm{CO}_2$.  Here we adopt the value $3.7 \, \rm{Wm^{-2}}$ following Myhre et al. 1998, well knowing that the adjusted forcing is model-dependent.
%%The analysis here assumes a value of external forcing due only to a doubling of $\rm{CO}_2$ with a constant value of $3.7 \rm{W/m^2}$.  
%Traditionally the Equilibrium Climate Sensitivity (ECS) has been defined as the resulting change of surface temperature once the model has reached equilibrium after the concentration of $\rm{CO}_2$ has been doubled.  Because our surface temperature change is fixed, the feedback parameter is computed as the ratio of the TOA radiative imbalance to the prescribed change in surface temperature: $\lambda=\Delta R/\Delta T_s$.
%The climate sensitivity is then computed as $\rm{ECS} = -\rm{F}/\lambda$.
The hydrological sensitivity parameter can similarly be defined (e.g., \textit{Fl\"{a}schner et al} [2016]) as the slope of temperature-dependent precipitation change ($\Delta P/\Delta T$).  This provides an alternate measure of a models response to warming.

% Not sure where you want to take this.  I think the HSP is interesting to compare to the GCMs.  Here this seems to be increasingly robust for the 12M or larger domains.   It is larger than what one usually computes for GCMs but consistent with Fläschner et al (Dagmar's new last name) in that it is systematically higher than what one computes from coupled simulations.

The thus calculated feedback parameters, climate sensitivities, and hydrologic sensitivities of our simulations vary with domain size (Table \ref{tab:lambda}) in a non-systematic fashion.  
Variations in the climate feedback parameter are large, 
($1.8 \pm 0.5$),
and differ by a factor of about 2.1 between the largest and smallest value.  In contrast, variations in the hydrological sensitivity parameter are much smaller, ($2.4 \pm 0.3$), and vary by a factor of 1.4. 
Relative contributions from the long- and shortwave components of the total feedback parameter are also tabulated.  Although the magnitude of the longwave feedback parameters are larger, the range of the shortwave feedback parameters ($2.6  \, \rm{Wm}^{-2} \rm{K}^{-1}$) is greater than those of the longwave feedback parameters ($1.35 \, \rm{Wm}^{-2} \rm{K}^{-1}$).  
The shortwave feedback contributes the most to the variability of the total feedback response, but it is clear that the contribution of the longwave component cannot be neglected for either the climate feedback parameter or the hydrologic sensitivity parameter.  This likely indicates an interplay of multiple mechanisms in the response.  As is to be expected, the hydrological sensitivity scales closely with the change in atmospheric cooling (not shown) which is dominated by longwave feedbacks, (i.e., not variability in shortwave absorption as is evident when looking across climate models (e.g., \textit{Takahashi et al.} [2009])\nocite{Takahashi_2009}) and thus the weakest sensitivity is found in the 3M domain.

The Cloud Radiative Effect (CRE = clear-sky radiance - all-sky radiance) can be used to investigate the role of clouds in the response to a perturbation.  We find that variation in shortwave feedbacks is  dominated by cloud radiative effects (Table 2)   
%Focusing next on the difference between all-sky and clear-sky feedback parameters 
%we find that the variation in shortwave feedbacks is  dominated by cloud radiative effects 
as the clear-sky shortwave feedback is practically domain-size independent, whereas in the longwave both cloud- and non-cloud, here consisting of water vapor and temperature, feedbacks are important.
%For simulations with an SST of 301K the range of CRE is $ 5.2 \, \rm{Wm}^{-2} \rm{K}^{-1}$ while for the simulations with an SST of 297K the range is $ 4.0 \, \rm{Wm}^{-2} \rm{K}^{-1}$.  
Computing the change of CRE ($\Delta \rm{CRE}$) between the simulations with different SSTs and decomposing this into the shortwave and longwave components reveals that the shortwave $\Delta \rm{CRE}$ varies in sync with the total $\Delta \rm{CRE}$ while the longwave $\Delta \rm{CRE}$ is approximately independent of domain size.

The variation in shortwave cloud feedback and $\Delta \rm{CRE}$ across the domain sizes is difficult to ascribe to specific features of the mean state or response.  While the non-systematic response of the low clouds strongly contributes to this variation, other factors also contribute.  
%Although all domains have qualitatively similar climates there is a non-systematic response of the low clouds which contributes to this large spread of the feedback parameter.  
All domains have an increase of upper level clouds between $14-18 \rm{km}$ with the differences in magnitude (up to $5 \%$) contributing to differences in the longwave feedback parameters shown in Table \ref{tab:lambda}.   We also see (Figure \ref{fig:profdiff}) that the response of the low-level specific and relative humidity differs slightly from the cloud cover response indicating the importance of surface fluxes and turbulent mixing.

Considering the only difference among the simulations is the size of the domain, and the similarity of the thermodynamic response (Figure \ref{fig:profdiff}), the spread in the feedback parameters is surprising.  Despite having identical physics parameterizations, the range of feedback parameters that we calculate ($1.3  \, \rm{Wm}^{-2} \rm{K}^{-1}$) is larger than the range from the models which participated in CMIP5 ($1.1 \, \rm{Wm}^{-2} \rm{K}^{-1}$).  To illustrate this the feedback parameters for each domain size are shown in Figure \ref{fig:lambdaecs}.  The values for individual models from CMIP5 are also displayed with the tan colored markers.  
 These results highlight the ability of different simulations to have  similar climates but differing climate sensitivities (\textit{Mauritsen et al.} [2013]\nocite{Mauritsen_etal_2013}, \textit{Zhao et al.} [2015]).

%\section{Discussion}
% 
%Hydrologic Sensitivity Parameter: Seems to have converged for 12M and larger.  Larger than what one usually computes for GCM.
%Consistent with Fl\"{a}schner et al. 2015 in that it is systematically higher than that seen with coupled simulations.

\section{Conclusions}
%
It has been shown that the simulated atmosphere of the ICON GCM with parameterized RCE is sufficiently similar across a range of domain sizes to justify and encourage the use of RCE to study both a GCM and a CRM on the same domain with the goal of improved constraints on the parameterized clouds.  This was demonstrated with SST perturbation simulations on multiple domains in a state of RCE.  
The equilibrated stationary states of the largest four domains have nearly indistinguishable thermodynamic profiles while the smallest domain, $3/4 \, \rm{M}$, differs with less precipitation, more cloud ice, and larger values of cloud cover.  
In addition to these differences, the $3/4 \, \rm{M}$ domain has the lowest subsidence fraction.  As a result the $3/4 \, \rm{M}$ domain appears to be too small for the RCE studies recommended by this study.  
However, for all simulations the low-level RH, cloud cover, and cloud liquid water all maximize below 1km.  All simulations have a peak in cloud cover at the melting level of the same magnitude and the upper level cloud ice, cloud cover, and RH indicate that the vertical extent of convection is similar for all domains.  
There is a small but systematic variation  of the evolution of the precipitation field as a function of domain size but the differences are relatively small ($< 10\%$) as compared to the mean.
Overall, the resulting model state resembles that of the tropical atmosphere on Earth.

Notwithstanding the qualitative similarities of the simulations, quantitative differences lead to a surprisingly large sensitivity of the feedback parameter, and thus the climate sensitivity.  The range of the feedback parameter ($1.3  \, \rm{Wm}^{-2} \rm{K}^{-1}$) is more than a factor of two and is comparable to the range of feedbacks which were obtained by the CMIP5 models (($1.1 \, \rm{Wm}^{-2} \rm{K}^{-1}$), Figure \ref{fig:lambdaecs}).  Due to our experimental setup the different values of the feedback parameter in these simulations cannot be due to differences in the 
subgrid scale parameterization schemes, grid, discretization, or formulations of the dynamical core.  Among the remaining possible factors it seems likely that some combination of nonlinear interactions between the wind field, surface fluxes, low-level clouds, and radiation are responsible for the variations in the feedback.  
We interpret these changes as a manifestation of structural instability  [\textit{McWilliams}, 2007\nocite{McWilliams_2007}] that has been hypothesized to exist in some models, and may also be a characteristic of the natural system.
% inherent in the GCM framework.  In that case there would be a fundamental limit to how accurately a GCM can determine the climate sensitivity.  To what extent is the feedback parameter of CRMs limited by structural instability?

Despite its apparent imprecision in some respects, the paradigm of RCE is a compelling simplification of the atmosphere that is interesting to study, not only for its well appreciated insight into quantities like climate sensitivity, but more fundamentally because of its ability to elucidate the ways in which convection and large-scale circulations interact.

%%% End of body of article:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

\begin{acknowledgments}
The computing resources were provided by Deutsches Klimarechenzentrum (DKRZ).  The research presented here was conducted when LGS was employed by the Max Planck Institute for Meteorology.   Anurag Dipanker and Leonidas Linardakis  assisted with debugging and stimulating discussions.  Cathy Hohenegger read an early version of the manuscript and helped to improve the presentation of our ideas.  The ICON development team at both MPI-M and DWD provided helpful support and motivation throughout the work.  The data used for this study is available upon request.  Princeton University generously supported LGS during the final stage of the writing.  
\end{acknowledgments}

%% ------------------------------------------------------------------------ %%
%%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
%\begin{thebibliography}{}
%\bibliography{/Users/silvers/latex/master_refs}
%\bibliographystyle{agufull08}
%\bibitem[Cess et al.(1989)]{Cess_etal_1989}
%ENTRY
%{
%	AUTHOR = {R. D. Cess and G. L. Potter and J.P. Blanchet},
%	YEAR = {1989},
%	TITLE = {Interpretation of Cloud-Climate Feedback as Produced by 14 Atmospheric General Circulation Models},
%	JOURNAL = {Science},
%	VOLUME = {245},
%	PAGES ={513-516},
%	KEY={Cess_etal_1989}
%}
% Text
%@ARTICLE{Cess_etal_1989,
%	AUTHOR = {R. D. Cess and G. L. Potter and J.P. Blanchet},
%	YEAR = {1989},
%	TITLE = {Interpretation of Cloud-Climate Feedback as Produced by 14 Atmospheric General Circulation Models},
%	JOURNAL = {Science},
%	VOLUME = {245},
%	PAGES ={513-516}
%}

%\end{thebibliography}
%
% Or,
%
% If you use BiBTeX for your references, please use the agufull08.bst file (available at % ftp://ftp.agu.org/journals/latex/journals/Manuscript-Preparation/) to produce your .bbl
% file and copy the contents into your paper here.
%
% Follow these steps:
% 1. Run LaTeX on your LaTeX file.
%
% 2. Make sure the bibliography style appears as \bibliographystyle{agufull08}. Run BiBTeX on your LaTeX
% file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%STOPSTOPSTOP%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{thebibliography}{49}
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{\textit{Arnold and Randall}(2015)}]{Arnold_Randall_2015}
Arnold, N.~P., and D.~A. Randall (2015), Global-scale convective aggregation:
  Implications for the madden-{J}ulian oscillation, \textit{J.\ Adv. \ Model. \
  Earth \ Syst.}, \textit{7}, \doi{10.1002/2015MS000498}.

\bibitem[{\textit{Bechtold et~al.}(2008)\textit{Bechtold, K\"{o}hler, Jung,
  Doblas-Reyes, Leutbecher, Rodwell, Vitart, and Balsamo}}]{Bechtold_etal_2008}
Bechtold, P., M.~K\"{o}hler, T.~Jung, F.~Doblas-Reyes, M.~Leutbecher, M.~J.
  Rodwell, F.~Vitart, and G.~Balsamo (2008), Advances in simulating atmospheric
  variability with the ecmwf model: From synoptic to decadal time-scales,
  \textit{Quart. J. Roy. Meteor. Soc.}, \textit{134}, 1337--1351,
  \doi{10.1002/qj.289}.

\bibitem[{\textit{Bechtold et~al.}(2014)\textit{Bechtold, Semane, Lopez,
  Chaboureau, Beljaars, and Bormann}}]{Bechtold_etal_2014}
Bechtold, P., N.~Semane, P.~Lopez, J.-P. Chaboureau, A.~Beljaars, and
  N.~Bormann (2014), Representing equilibrium and nonequilibrium convection in
  large-scale models, \textit{J. Atmos. Sci.}, \textit{71}, 734--753,
  \doi{10.1175/JAS-D-13-0163.1}.

\bibitem[{\textit{Becker and Stevens}(2014)}]{Becker_Stevens_2014}
Becker, T., and B.~Stevens (2014), Climate and climate sensitivity to changing
  co$_2$ on an idealized land planet, \textit{J.\ Adv. \ Model. \ Earth \
  Syst.}, \textit{6}, \doi{10.1002/2014MS000369}.

\bibitem[{\textit{Bony and Dufresne}(2005)}]{Bony_Dufresne_2005}
Bony, S., and J.~L. Dufresne (2005), Marine boundary layer clouds at the heart
  of tropical cloud feedback uncertainties in climate models, \textit{Geophys.\
  Res.\ Lett.}, \textit{32}, \doi{10.1029/2005GL023851}.

\bibitem[{\textit{Bony et~al.}(2015)\textit{Bony, Stevens, Frierson, Jakob,
  Kageyama, Pincus, Shepherd, Sherwood, Siebesma, Sobel, Watanabe, and
  Webb}}]{Bony_etal_2015}
Bony, S., B.~Stevens, D.~M. Frierson, C.~Jakob, M.~Kageyama, R.~Pincus, T.~G.
  Shepherd, S.~C. Sherwood, A.~P. Siebesma, A.~H. Sobel, M.~Watanabe, and M.~J.
  Webb (2015), Clouds, circulation, and climate sensitivity, \textit{Nat.\
  Geosci.}, \textit{8}, \doi{10.1038/NGEO2398}.

\bibitem[{\textit{Bretherton et~al.}(2005)\textit{Bretherton, Blossey, and
  Khairoutdinov}}]{Bretherton_etal_2005}
Bretherton, C.~S., P.~N. Blossey, and M.~Khairoutdinov (2005), An
  energy-balance analysis of deep convective self-aggregation above uniform
  sst, \textit{J. Atmos. Sci.}, \textit{62}, 4273--4292.

\bibitem[{\textit{Brient et~al.}(2015)\textit{Brient, Schneider, Tan, Bony, Qu,
  and Hall}}]{Brient_etal_2015}
Brient, F., T.~Schneider, Z.~Tan, S.~Bony, X.~Qu, and A.~Hall (2015),
  Shallowness of tropical low clouds as a predictor of climate models' response
  to warming, \textit{Clim.\ Dynam.}, \textit{45},
  \doi{10.1007/s00382-015-2846-0}.

\bibitem[{\textit{Cess et~al.}(1989)\textit{Cess, Potter, and
  Blanchet}}]{Cess_etal_1989}
Cess, R.~D., G.~L. Potter, and J.~Blanchet (1989), Interpretation of
  cloud-climate feedback as produced by 14 atmospheric general circulation
  models, \textit{Science}, \textit{245}, 513--516.

\bibitem[{\textit{Coppin and Bony}(2015)}]{Coppin_Bony_2015}
Coppin, D., and S.~Bony (2015), Physical mechanisms controlling the initiation
  of convective self-aggregation in a General Circulation Model, \textit{J.\
  Adv. \ Model. \ Earth \ Syst.}, \textit{7}, \doi{10.1002/2015MS000571}.

\bibitem[{\textit{Derbyshire et~al.}(2004)\textit{Derbyshire, Beau, Bechtold,
  Grandpeix, Piriou, Redelsperger, and Soares}}]{Derbyshire_etal_2004}
Derbyshire, S.~H., I.~Beau, P.~Bechtold, J.-Y. Grandpeix, J.-M. Piriou, J.-L.
  Redelsperger, and P.~Soares (2004), Sensitivity of moist convection to
  environmental humidity, \textit{Quart. J. Roy. Meteor. Soc.}, \textit{130},
  3055--3079.

\bibitem[{\textit{Dipankar et~al.}(2015)\textit{Dipankar, Stevens, Heinze,
  Moseley, Z\"{a}ngl, Giorgetta, and Brdar}}]{Dipanker_etal_2015}
Dipankar, A., B.~Stevens, R.~Heinze, C.~Moseley, G.~Z\"{a}ngl, M.~Giorgetta,
  and S.~Brdar (2015), Large eddy simulation using the general circulation
  model icon, \textit{J. Adv. Model. Earth Syst.}, \textit{7},
  \doi{10.1002/2015MS000431}.

\bibitem[{\textit{Emanuel et~al.}(2014)\textit{Emanuel, Wing, and
  Vincent}}]{Emanuel_etal_2014}
Emanuel, K., A.~A. Wing, and E.~M. Vincent (2014), Radiative-convective
  instability, \textit{J. Adv. Model. Earth Syst.}, \textit{6},
  \doi{10.1002/2013MS000270}.

%\bibitem[{\textit{Emanuel et~al.}(2014)\textit{Emanuel, Wing, and
 % Vincent}}]{Emanuel_etal_2014}
\bibitem[{\textit{Fl\"{a}schner et~al.}(2016)\textit{Fl\"{a}schner, Mauritsen, and Stevens}}]
%{Fl\"{a}schner_etal_2016}
{Flaeschner_etal_2016}
Fl\"{a}schner, D., T.~Mauritsen, B.~Stevens (2016), Understanding the inter-model spread in global-mean hydrological sensitivity,
  \textit{J.\ Climate},
  \textit{ in press}.

\bibitem[{\textit{Gassmann}(2011)}]{Gassmann_2011}
Gassmann, A. (2011), Inspection of hexagonal and triangular c-grid
  discretizations on the shallow water equations, \textit{J.\ Comput.\ Phys.},
  \textit{230}, 2706--2721, \doi{10.1002/2013MS000270}.

\bibitem[{\textit{Hartmann and Larson}(2002)}]{Hartmann_Larson_2002}
Hartmann, D.~L., and K.~Larson (2002), An important constraint on tropical
  cloud-climate feedback, \textit{Geophys.\ Res.\ Lett.}, \textit{29},
  \doi{10.1029/2002GL015835}.

\bibitem[{\textit{Held et~al.}(1993)\textit{Held, Hemler, and
  Ramaswamy}}]{Held_etal_1993}
Held, I.~M., R.~S. Hemler, and V.~Ramaswamy (1993), Radiative-convective
  equilibrium with explicit two-dimensional moist convection, \textit{J. Atmos.
  Sci.}, \textit{50}, 3909--3927,
  \doi{http://dx.doi.org/10.1175/1520-0469(1993)050<3909:RCEWET>2.0.CO;2}.

\bibitem[{\textit{Held et~al.}(2007)\textit{Held, Zhao, and
  Wyman}}]{Held_etal_2007}
Held, I.~M., M.~Zhao, and B.~Wyman (2007), Dynamic radiative-convective
  equilibria using gcm column physics, \textit{J. Atmos. Sci.}, \textit{64},
  228--238, \doi{10.1175/JAS3825.11}.

\bibitem[{\textit{Jeevanjee and Romps}(2013)}]{Jeevanjee_Romps_2013}
Jeevanjee, N., and D.~M. Romps (2013), Convective self-aggregation, cold pools,
  and domain size, \textit{Geophys.\ Res.\ Lett.}, \textit{40}, 994--99,
  \doi{10.1002/grl.50204}.

\bibitem[{\textit{Klemp et~al.}(2008)\textit{Klemp, Dudhia, and
  Hassiotis}}]{Klemp_etal_2008}
Klemp, J.~B., J.~Dudhia, and A.~D. Hassiotis (2008), An upper gravity-wave
  absorbing layer for nwp applications, \textit{Mon. Wea. Rev.}, \textit{136},
  3987--4004, \doi{10.1175/2008MWR2596.1}.

\bibitem[{\textit{Manabe and Strickler}(1964)}]{Manabe_Strickler_1964}
Manabe, S., and R.~F. Strickler (1964), Thermal equilibrium of the atmosphere
  with a convective adjustment, \textit{J. Atmos. Sci.}, \textit{21}, 361--385.

\bibitem[{\textit{Manabe and Wetherald}(1967)}]{Manabe_Wetherald_1967}
Manabe, S., and R.~T. Wetherald (1967), Thermal equilibrium of the atmosphere
  with a given distribution of relative humidity, \textit{J. Atmos. Sci.},
  \textit{24}, 241--259.

\bibitem[{\textit{Mauritsen and Stevens}(2015)}]{Mauritsen_Stevens_2015}
Mauritsen, T., and B.~Stevens (2015), Missing iris effect as a possible cause
  of muted hydrological change and high climate sensitivity in models,
  \textit{Nat.\ Geosci.}, \textit{8}, 346--351.

\bibitem[{\textit{Mauritsen et~al.}(2013)\textit{Mauritsen, Graversen, Klocke,
  Langen, Stevens, and Tomassini}}]{Mauritsen_etal_2013}
Mauritsen, T., R.~G. Graversen, D.~Klocke, P.~L. Langen, B.~Stevens, and
  L.~Tomassini (2013), Climate feedback efficiency and synergy, \textit{Clim.\
  Dynam.}, \textit{41}, 2539--2554.

\bibitem[{\textit{McWilliams}(2007)}]{McWilliams_2007}
McWilliams, J.~C. (2007), Irreducible imprecision in atmospheric and oceanic
  simulations, \textit{Proc.\ Natl.\ Acad.\ Sci.\ (USA)}, \textit{104},
  8709--8713, \doi{10.1073/pnas.0702971104}.

\bibitem[{\textit{Mlawer et~al.}(1997)\textit{Mlawer, Taubman, Brown, Iacono,
  and Clough}}]{Mlawer_etal_1997}
Mlawer, E.~J., S.~J. Taubman, P.~D. Brown, M.~J. Iacono, and S.~A. Clough
  (1997), Radiative transfer for inhomogeneous atmospheres: {RRTM}, a validated
  correlated-k model for the longwave, \textit{J.\ Geophys.\ Res.},
  \textit{102}, 16,663--16,682.

\bibitem[{\textit{M\"{o}bis and Stevens}(2012)}]{Moebis_Stevens_2012}
M\"{o}bis, B., and B.~Stevens (2012), Factors controlling the position of the
  intertropical convergence zone on an aquaplanet, \textit{J.\ Adv. \ Model. \
  Earth \ Syst.}, \textit{4}, \doi{10.1029/2012MS000199}.

\bibitem[{\textit{Muller and Held}(2012)}]{Muller_Held_2012}
Muller, C.~J., and I.~Held (2012), Detailed investigation of the
  self-aggregation of convection in cloud-resolving simulations, \textit{J.
  Atmos. Sci.}, \textit{69}, 2551--2565, \doi{10.1175/JAS-D-11-0257.1}.

\bibitem[{\textit{Myhre et~al.}(1998)\textit{Myhre, Highwood, Shine, and
  Stordal}}]{Myhre_etal_1998}
Myhre, G., E.~J. Highwood, K.~P. Shine, and F.~Stordal (1998), New estimates of
  radiative forcing due to well mixed greenhouse gases, \textit{Geophys.\ Res.\
  Lett.}, \textit{25}, 2715--2718.

\bibitem[{\textit{Nam et~al.}(2012)\textit{Nam, Bony, Dufresne, and
  Chepfer}}]{Nam_etal_2012}
Nam, C., S.~Bony, J.-L. Dufresne, and H.~Chepfer (2012), The `too few, too
  bright' tropical low-cloud problem in cmip5 models, \textit{Geophys.\ Res.\
  Lett}, \textit{39}, \doi{10.1029/2012GL053421}.

\bibitem[{\textit{Nuijens et~al.}(2015)\textit{Nuijens, Medeiros, Sandu, and
  Ahlgrimm}}]{Nuijens_etal_2015}
Nuijens, L., B.~Medeiros, I.~Sandu, and M.~Ahlgrimm (2015), The behavior of
  trade-wind cloudiness in observations and models: The major cloud components
  and their variability, \textit{J. Adv. Model. Earth Syst.}, \textit{7},
  600--616, \doi{10.1002/2014MS000390}.

\bibitem[{\textit{Oueslati and Bellon}(2013)}]{Oueslati_Bellon_2013}
Oueslati, B., and G.~Bellon (2013), Convective entrainment and large-scale
  organization of tropical precipitation: Sensitivity of the {CNRM-CM5}
  hierarchy of models, \textit{J.\ Climate}, \textit{26}, 2931--2946.

\bibitem[{\textit{Popke et~al.}(2013)\textit{Popke, Stevens, and
  Voigt}}]{Popke_etal_2013}
Popke, D., B.~Stevens, and A.~Voigt (2013), Climate and climate change in a
  radiative-convective equilibrium version of echam6, \textit{J. Adv. Model.
  Earth Syst.}, \textit{5}, 1--14, \doi{10.1029/2012MS000191}.

\bibitem[{\textit{Raschendorfer}(2001)\textit{Raschendorfer}}]{Raschendorfer_2001}
Raschendorfer, M. (2001), The new turbulence parameterization of LM,
 \textit{COSMO Newsl.}, \textit{1}, 89-97. http://www.cosmo-model.org.

\bibitem[{\textit{Redelsperger et~al.}(2002)\textit{Redelsperger, Parsons, and
  Guichard}}]{Redelsperger_etal_2002}
Redelsperger, J., D.~Parsons, and F.~Guichard (2002), Recovery process and
  factors limiting cloud-top height following the arrival of a dry intrusion
  observed during {TOGA-COARE}, \textit{J.\ Atmos.\ Sci.}, \textit{59}.

\bibitem[{\textit{Reed et~al.}(2015)\textit{Reed, Medeiros, Bacmeister, and
  Lauritzen}}]{Reed_etal_2015}
Reed, K.~A., B.~Medeiros, J.~T. Bacmeister, and P.~H. Lauritzen (2015), Global
  radiative-convective equilibrium in the community atmosphere model, version
  5, \textit{J.\ Atmos.\ Sci.}, \textit{72}, 2183--2197,
  \doi{10.1175/JAS-D-14-0268.1}.

\bibitem[{\textit{Rieck et~al.}(2012)\textit{Rieck, Nuijens, and
  Stevens}}]{Rieck_etal_2012}
Rieck, M., L.~Nuijens, and B.~Stevens (2012), Marine boundary layer cloud
  feedbacks in a constant relative humidity atmosphere, \textit{J.\ Atmos.\
  Sci.}, \textit{69}, 2538--2550, \doi{10.1175/JAS-D-11-0203.1}.

\bibitem[{\textit{Rio et~al.}(2009)\textit{Rio, Hourdin, Grandpeix, and
  Lafore}}]{Rio_etal_2009}
Rio, C., F.~Hourdin, J.-Y. Grandpeix, and J.-P. Lafore (2009), Shifting the
  diurnal cycle of parameterized deep convection over land, \textit{Geophys.\
  Res.\ Lett}, \textit{36}, \doi{10.1029/2008GL036799}.

\bibitem[{\textit{Seifert}(2008)\textit{Seifert}}]{Seifert_2008}
Seifert, A. (2008), A revised cloud microphysical parameterization for COSMO-LME,
 \textit{COSMO Newsl.}, \textit{8}, 25-28. http://www.cosmo-model.org.

\bibitem[{\textit{Sherwood et~al.}(2014)\textit{Sherwood, Bony, and
  Dufresne}}]{Sherwood_etal_2014}
Sherwood, S.~C., S.~Bony, and J.~L. Dufresne (2014), Spread in model climate
  sensitivity traced to atmospheric convective mixing, \textit{Nature},
  \textit{505}, 37--42, \doi{10.1038/nature12829}.

\bibitem[{\textit{Sherwood et~al.}(2015)\textit{Sherwood, Bony, Boucher,
  Bretherton, Forster, Gregory, and Stevens}}]{Sherwood_etal_2015}
Sherwood, S.~C., S.~Bony, O.~Boucher, C.~Bretherton, P.~M. Forster, J.~M.
  Gregory, and B.~Stevens (2015), Adjustments in the forcing-feedback framework
  for understanding climate change, \textit{Bull.\ Amer.\ Meteor.\ Soc.},
  \textit{96}, 217--228, \doi{10.1175/BAMS-D-13-00167.1}.

\bibitem[{\textit{Stevens and Bony}(2013)}]{Stevens_Bony_2013}
Stevens, B., and S.~Bony (2013), What are climate models missing?,
  \textit{Science}, \textit{340}, 1053--1054, \doi{10.1126/science.1237554}.

\bibitem[{\textit{Stevens et~al.}(2013)\textit{Stevens, Giorgetta, Esch,
  Mauritsen, Crueger, Rast, Salzmann, Schmidt, Bader, Block, Brokopf, Fast,
  Kinne, Kornblueh, Lohmann, Pincus, Reichler, and
  Roeckner}}]{Stevens_etal_2013}
Stevens, B., M.~Giorgetta, M.~Esch, T.~Mauritsen, T.~Crueger, S.~Rast,
  M.~Salzmann, H.~Schmidt, J.~Bader, K.~Block, R.~Brokopf, I.~Fast, S.~Kinne,
  L.~Kornblueh, U.~Lohmann, R.~Pincus, T.~Reichler, and E.~Roeckner (2013),
  Atmospheric component of the mpi-m earth system model: Echam6, \textit{J.
  Adv. Model. Earth Syst.}, \textit{5}, 146--172, \doi{10.1002/jame.20015}.

\bibitem[{\textit{Takahashi}(2009)}]{Takahashi_2009}
Takahashi, K. (2009), The global hydrological cycle and atmospheric shortwave
  absorption in climate models under co$_2$ forcing, \textit{J.\ Climate},
  \textit{22}, 5667--5675.

\bibitem[{\textit{Tobin et~al.}(2012)\textit{Tobin, Bony, and
  Roca}}]{Tobin_etal_2012}
Tobin, I., S.~Bony, and R.~Roca (2012), Observational evidence for
  relationships between the degree of aggregation of deep convection, water
  vapor, surface fluxes, and radiation, \textit{J.\ Climate}, \textit{25},
  6885--6904.

\bibitem[{\textit{Tompkins and Craig}(1998)}]{Tompkins_Craig_1998}
Tompkins, A., and G.~Craig (1998), Radiative-convective equilibrium in a
  three-dimensional cloud ensemble model, \textit{Quart.\ J.\ Roy.\ Meteor.\
  Soc.}, \textit{124}, 2073--2097.

\bibitem[{\textit{Wan et~al.}(2013)\textit{Wan, Giorgetta, Z\"{a}ngl, Restelli,
  Majewski, Bonaventura, Fr\"{o}hlich, Reinert, Ripodas, Kornblueh, and
  F\"{o}rstner}}]{Wan_etal_2013}
Wan, H., M.~A. Giorgetta, G.~Z\"{a}ngl, M.~Restelli, D.~Majewski,
  L.~Bonaventura, K.~Fr\"{o}hlich, D.~Reinert, P.~Ripodas, L.~Kornblueh, and
  J.~F\"{o}rstner (2013), The icon-1.2 hydrostatic atmospheric dynamical core
  on triangular grids - part 1: Formulation and performance of the baseline
  version, \textit{Geosci. Model Dev.}, \textit{6}, 735--763,
  \doi{10.5194/gmd-6-735-2013}.

\bibitem[{\textit{Webb et~al.}(2001)\textit{Webb, Senior, Bony, and
  Morcrette}}]{Webb_etal_2001}
Webb, M., C.~Senior, S.~Bony, and J.-L. Morcrette (2001), Combining {ERBE} and
  {ISCCP} data to assess clouds in the hadley centre, {ECMWF} and {LMD}
  atmospheric climate models, \textit{Clim.\ Dynam.}, \textit{17}, 905--922.

\bibitem[{\textit{Wing and Emanuel}(2014)}]{Wing_Emanuel_2014}
Wing, A.~A., and K.~A. Emanuel (2014), Physical mechanisms controlling
  self-aggregation of convection in idealized numerical modeling simulations,
  \textit{J. Adv. Model. Earth Syst.}, \textit{6}, 59--74,
  \doi{10.1002/2013MS000269}.

\bibitem[{\textit{Z\"{a}ngl et~al.}(2015)\textit{Z\"{a}ngl, Reinert, Ripodas,
  and Baldauf}}]{Zaengl_etal_2015}
Z\"{a}ngl, G., D.~Reinert, P.~Ripodas, and M.~Baldauf (2015), The
  {ICON}({ICO}sahedral {N}on-hydrostatic modelling framework of {DWD} and
  {MPI-M}: Description of the non-hydrostatic dynamical core), \textit{Quart.
  J. Roy. Meteor. Soc.}, \textit{141}, 563--579, \doi{10.1002/qj.2378}.

\bibitem[{\textit{Zelinka and Hartmann}(2011)}]{Zelinka_Hartmann_2011}
Zelinka, M.~D., and D.~L. Hartmann (2011), The observed sensitivity of high
  clouds to mean surface temperature anomalies in the tropics, \textit{J.\
  Geophys.\ Res.}, \textit{116}, \doi{10.1029/2011JD016459}.

\bibitem[{\textit{Zhou}(2015)}]{Zhou_2015}
Zhou, W. (2015), Non-{R}otating and rotating raditive-{C}onvective equilibrium,
  Ph.D. thesis, Princeton University.

\end{thebibliography}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%STOPSTOPSTOP%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 4. Comment out the old \bibliographystyle and \bibliography commands.
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

%\begin{thebibliography}{}

%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%
%\bibitem[{\textit{Atkinson and Sloan}(1991)}]{AtkinsonSloan}
%Atkinson, K., and I.~Sloan (1991), The numerical solution of first-kind
%  logarithmic-kernel integral equations on smooth open arcs, \textit{Math.
%  Comp.}, \textit{56}(193), 119--139.
%
%\bibitem[{\textit{Colton and Kress}(1983)}]{ColtonKress1}
%Colton, D., and R.~Kress (1983), \textit{Integral Equation Methods in
%  Scattering Theory}, John Wiley, New York.
%
%\bibitem[{\textit{Hsiao et~al.}(1991)\textit{Hsiao, Stephan, and
%  Wendland}}]{StephanHsiao}
%Hsiao, G.~C., E.~P. Stephan, and W.~L. Wendland (1991), On the {D}irichlet
%  problem in elasticity for a domain exterior to an arc, \textit{J. Comput.
%  Appl. Math.}, \textit{34}(1), 1--19.
%
%\bibitem[{\textit{Lu and Ando}(2012)}]{LuAndo}
%Lu, P., and M.~Ando (2012), Difference of scattering geometrical optics
%  components and line integrals of currents in modified edge representation,
%  \textit{Radio Sci.}, \textit{47},  RS3007, \doi{10.1029/2011RS004899}.

%\end{thebibliography}

%Reference citation examples:

%...as shown by \textit{Kilby} [2008].
%...as shown by {\textit  {Lewin}} [1976], {\textit  {Carson}} [1986], {\textit  {Bartholdy and Billi}} [2002], and {\textit  {Rinaldi}} [2003].
%...has been shown [\textit{Kilby et al.}, 2008].
%...has been shown [{\textit  {Lewin}}, 1976; {\textit  {Carson}}, 1986; {\textit  {Bartholdy and Billi}}, 2002; {\textit  {Rinaldi}}, 2003].
%...has been shown [e.g., {\textit  {Lewin}}, 1976; {\textit  {Carson}}, 1986; {\textit  {Bartholdy and Billi}}, 2002; {\textit  {Rinaldi}}, 2003].

%...as shown by \citet{jskilby}.
%...as shown by \citet{lewin76}, \citet{carson86}, \citet{bartoldy02}, and \citet{rinaldi03}.
%...has been shown \citep{jskilbye}.
%...has been shown \citep{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown \citep [e.g.,][]{lewin76,carson86,bartoldy02,rinaldi03}.
%
% Please use ONLY \citet and \citep for reference citations.
% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).

%% ------------------------------------------------------------------------ %%
%
%  END ARTICLE
%
%% ------------------------------------------------------------------------ %%
\end{article}
%
%
%% Enter Figures and Tables here:
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables; all other caption information
%  should be placed in footnotes below the table.
%
%----------------

\begin{table}
    \caption{Length of simulations, SST used, size and names of domains for each simulation.  The M in the domain names stands for million (or Mega) $\rm{km}^2$.  Also shown are two different periods (P1 and P2) of time used for computing mean values from the end of the simulations.  See text and captions for details.}
    \begin{center}
    %\begin{tabular}{| l | l | l | l | p{5cm} |}
    %\begin{tabular}{l*{3}{c}r}
    \begin{tabular}{*{8}{c}}
    \hline
    %\multicolumn{5}{|c|}{Experimental Specifications} \\
    \hline
    Domain    &          Area  ($\rm{km}^2$)         & Edge Length (km)            &   Grid Points    &   SST (K)          & Length (year)    & P1 (year) & P2 (month)     \\ \hline
    3/4M        &   $\mathrm{0.80\times 10^6}$   &  960 $\times$ 831            &    4,608            &  297/301           & 10                     & 9             & 12                    \\
    \\
    3M           & $\mathrm{3.2\times 10^6}$       & 1,920 $\times$ 1,663        &  18,432           &   297/301          & 10                     & 9              & 4                                   \\ 
    \\
    12M         & $\mathrm{12.8\times 10^6}$     & 3,840 $\times$ 3,326        &   73,728          & 297/301            &   4                     & 3              & 8                                               \\ 
    \\
    50M         & $\mathrm{51.1\times 10^6}$     & 7,680 $\times$ 6,651        &  294,912         & 297/301            &    2                    &  1              & 4                                                \\ 
    \\
    200M       & $\mathrm{204\times 10^6} $     & 15,360 $\times$ 13,302     & 1,179,648      & 297/301            &    1                    &  0.6          &  0.76                                     \\ \hline
     \end{tabular}\par
     \label{exptable}
\end{center}
\end{table}

\begin{table}
\begin{center}
\caption{Mean Energetics: Long- and short-wave feedback parameters, total feedback parameter, equilibrium climate sensitivity and hydrologic sensitivity parameter (HSP) (defined as $\Delta P/\Delta T_s$, where $P$ is the total precipitation) as a function of domain size.   Values were averaged over the P1 period.}
    %\begin{tabular}{|c|c|c|c|c|c|}
    \begin{tabular}{*{6}{c}}
    \hline
    \hline
 Domain & $\lambda_{sw}/\lambda_{sw,clr} (\mathrm{W/m^2 K}) $& $\lambda_{lw}/\lambda_{lw,clr}  (\mathrm{W/m^2 K}) $ &   $\lambda  (\mathrm{W/m^2 K}) $ & ECS (K) & HSP ($\mathrm{\%/K}$)   \\ \hline
    0.75 M          &   0.08/0.25    & -1.93/-2.13              & -1.85  $\pm (0.4/0.4)$           &  2.00           &        2.3     \\ 
    \\
    3M                & -0.89/0.25     & -1.49/-1.55            & -2.39 $\pm (0.3/0.3)$         & 1.55                &   1.9  \\  
    \\
    12M             & 0.13/0.23      & -2.28/-2.48             & -2.15 $\pm (0.3/0.2)$          & 1.72                &  2.6   \\  
    \\
    50M             & 1.71/0.25      & -2.84/-2.05             & -1.13 $\pm (0.2/0.2)$           & 3.29               &  2.7  \\  
    \\
    200M          & 0.92/0.25      & -2.51/-2.25             & -1.59  $\pm (0.2/0.1)$          & 2.33                &   2.7    \\  \hline
    \end{tabular}\par
    %\bigskip 
    \label{tab:lambda}
\end{center}
\end{table}

\begin{table}
    \caption{Total cloud cover and column integrated diagnostics.  Water Vapor ($q_v$), Liquid Water ($q_c$), and Ice ($q_i$).  Values were computed over the P2 period.}
    \begin{center}
    %\begin{tabular}{| l | l | l | l | p{5cm} |}
    %\begin{tabular}{l*{3}{c}r}
    \begin{tabular}{*{6}{c}}
    \hline
    %\multicolumn{5}{|c|}{Experimental Specifications} \\
    \hline
    Domain      & Tot Cloud Cover (\%)        & $q_v (\mathrm{kg/m^2}) $  &   $q_c (\mathrm{g/m^2}) $   & $q_i (\mathrm{g/m^2})$    & SST (K)   \\ \hline
    3/4M           &   $\mathrm{82}$  &    39.7            &  15.3    & 6.16              & 297                            \\
                       &       81                &   55.5             &   17.7   & 6.17              & 301  \\
                       \\
 %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
    3M                & $\mathrm{73}$   &  36.4            &   22.2   &      5.03          & 297                                 \\ 
                         &           75             &   52.5             &   25.8  & 5.64               & 301  \\
    \\
 %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
    12M              & $\mathrm{67}$ &  36.4          & 20.4    &        5.26              & 297                                      \\ 
                         &       63              &   49.7          & 39.3    &        6.35             & 301  \\
    \\
  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
    50M               & $\mathrm{63}$ &  37.0     & 24.2      &    5.54                & 297                                    \\ 
                          &       58               &  51.1     &  21.1     &    6.64               & 301  \\
    \\
   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
    200M            & $\mathrm{64} $ &  36.9      & 22.5  &        5.60                  & 297                       \\
                         &       57                &  51.9      & 26.4  &        6.74                 & 301     \\ \hline
    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
     \end{tabular}\par
     \label{colintvars}
\end{center}
\end{table}

% EXAMPLE FIGURE
%
 %\begin{figure}
 %\noindent\includegraphics[width=20pc]{samplefigure.eps}
 %\caption{Caption text here}
 %\label{figure_label}
 %\end{figure}
%
\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
        \includegraphics[width=6.7in]{rce_ecs_20km_5dom_tprec_raster.eps}
   \caption{Precipitation rate ($\rm{mm \, day^{-1}}$) of the equilibrated state for the five domains with a constant SST of $301 \, \rm{K}$.  Domains sizes are labelled as 3/4M, 3M, 12M, 50M, 200M, with increasing numbers indicating a four-fold increase in area (see Table 1).  All have similar subsidence fractions and the convective clusters continuously evolve while moving through the domains.}
   \label{fig:precvsdom}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
       \includegraphics[width=6in]{rce_ecs_20km_384gp_301_totprec_tevol.eps}
   \caption{Evolution in time of the precipitation rate on the 50M domain with an SST of $301 \, \rm{K}$.  Snapshots are from day 10 (left), day 25 (middle), and day 760 (right). }
   \label{fig:precevol}
\end{figure}

\begin{figure}[!htb]
   \centering
   \begin{minipage}{0.31\linewidth}
     \includegraphics[width=2.0in]{rce_ecs_20km_3by4Mx256_301.eps}
   \end{minipage}
   \begin{minipage}{0.31\textwidth} %  figure placement: here, top, bottom, or page
     \includegraphics[width=2.0in]{rce_ecs_20km_12Mx16_301_totp_3008.eps}
   \end{minipage}
   \begin{minipage}{0.31\textwidth} %  figure placement: here, top, bottom, or page
     \includegraphics[width=2.0in]{rce_ecs_301_200M_totp_nolabs.eps}
   \end{minipage}
  \caption{Snapshots in time of total precipitation ($\rm{mm \,day^{-1}}$) for the $\rm{3/4 M (left), 12 M (middle),}$ and $\rm{200M (right)}$ domains tiled according to scale.  Times and colors are same as for Fig. \ref{fig:precvsdom}, $\rm{SST}=301 \, \rm{K}$.}
  \label{fig:convorg}
\end{figure}

\begin{figure}[!htb]
    \centering
    \includegraphics[width=2.5in]{rce_ecs_20km_totprec_5dom_301_green.eps}
    \caption{Domain mean evolution in time of the total precipitation over the first two years with a 30 day running mean for the simulations with 
  an SST=301K.  The 200M simulation was run for a total of one year and thus only extends through half of the figure.  The dots on the right represent the mean total precipitation from the last 6 months of each experiment.}
   %Right, fraction of convective precipitation to total precipitation over the first 2 years.  Solid lines show the 
   %simulations with an SST=301K, dashed lines for simulations with an SSST=297K.}
  \label{fig:precipvtime}
\end{figure}

\begin{figure}[h] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.7in]{fig5_browns.eps}
   %\includegraphics[width=6.7in]{rce_ecs_20km_297_vprof_green.eps}
   \caption{Mean vertical profiles with a constant SST of 297 K.  Values were computed over the P2 period.}
   \label{fig:prof297}
\end{figure}

\begin{figure}[htb] %  figure placement: here, top, bottom, or page
   \centering
        \includegraphics[width=6.0in]{rce_20km_tqv_20mmto80mm_raster.eps}
   \caption{Column integrated water vapor ($\rm{mm}$).  The SST$=301$ K and the time of the snapshots is the same as for Fig. \ref{fig:precvsdom} but the color scale differs.}
   \label{fig:tqv5dom}
\end{figure}

\begin{figure}[h] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{fig7_lthick2_green.eps}
   %\includegraphics[width=6.5in]{rce_ecs_20km_reldiff_24km_green.eps}
   \caption{Difference ($301 \rm{K} - 297 \rm{K}$) of mean vertical profiles between the two sets of fixed SST cases.  Values were computed over the P2 period.}
   \label{fig:profdiff}
\end{figure}

\begin{figure}[h] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{rce_ecs_20km_reldiff_4km.eps}
   \caption{Same data as Figure \ref{fig:profdiff}, zoomed in to reveal boundary layer features.  Values were computed over the P2 period.}
   \label{fig:profdiffzoom}
\end{figure}

\begin{figure}[h] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{vprofile_diffrel200M.eps}
   \caption{Same data as Figure \ref{fig:profdiff}, plotted relative to the 200M domain.  Values were computed over the P2 period.}
   \label{fig:profdiffrel200M}
\end{figure}

\begin{figure}[h]
  \centering 
    \includegraphics[width=2.5in]{feedbk_vs_5dom_green_cmip5.eps}
   \caption{Feedback parameter as a function of domain size.  
  Bars correspond to a 5-95 \% confidence interval with a two-sided t-test.  A de-correlation time of three weeks was assumed for all domains.  The feedback parameters from CMIP5 models are shown as tan colored markers.}
   \label{fig:lambdaecs}
\end{figure}

% ---------------
% EXAMPLE TABLE
%
%\begin{table}
%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
%\centering
%\begin{tabular}{l c}
%\hline
% Run  & Time (min)  \\
%\hline
%  $l1$  & 260   \\
%  $l2$  & 300   \\
%  $l3$  & 340   \\
%  $h1$  & 270   \\
%  $h2$  & 250   \\
%  $h3$  & 380   \\
%  $r1$  & 370   \\
%  $r2$  & 390   \\
%\hline
%\end{tabular}
%\tablenotetext{a}{Footnote text here.}
%\end{table}

% See below for how to make sideways figures or tables.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
% BREAK THE EQUATIONS INTO TWO OR MORE LINES
% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
% using double backslashes (\\).

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

%% ------------------------------------------------------------------------ %%
%
%  SIDEWAYS FIGURE AND TABLE EXAMPLES
%
%% ------------------------------------------------------------------------ %%
%
% For tables and figures, add \usepackage{rotating} to the paper and add the rotating.sty file to the folder.
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{samplefigure.eps}
% \caption{caption here}
% \label{label_here}
% \end{sidewaysfigure}
%
%
%
% \begin{sidewaystable}
% \caption{}
% \begin{tabular}
% Table layout here.
% \end{tabular}
% \end{sidewaystable}
%
%

### 2019-09-20 Silvers_etal_2016_sbmt.tex
committing a number of old tex files into the latex_git repo

--- 2019-09-20 Silvers_etal_2016_revised.tex
@@
 \begin{abstract}
-Simulations of parameterized Radiative Convective Equilibrium (RCE) have been analyzed across a range of domains with areas spanning more than two orders of magnitude ($\mathrm{0.80 - 204 \times 10^6 km^2}$).
+Simulations of parameterized Radiative Convective Equilibrium (RCE) have been analyzed across a range of domains which span three orders of magnitude.
 It is shown that the simulated atmosphere of a General Circulation Model (GCM) in RCE is sufficiently similar across a range of domain sizes to justify the use of RCE to study both a GCM and a high resolution model on the same domain with the goal of improved constraints on the parameterized clouds.
@@
 Sea surface temperature perturbation experiments are used to estimate the climate feedback parameter for the differently configured experiments, and the cloud radiative effect is computed to examine the role which clouds play in the response.
-Despite the similar climate states between the domains the feedback parameter varies by more than a factor of two; the hydrological sensitivity parameter is better behaved, varying by a factor of 1.4.
+Despite the similar climate states between the models the feedback parameter varies by more than a factor of two; the hydrological sensitivity parameter is better behaved, varying by a factor of 1.4.
 The sensitivity to domain size is related foremost to a non-systematic response of low-level clouds as well as an increasingly negative longwave feedbacks on larger domains.
@@
 Research over at least the past two decades has shown that an uncertain representation 
-of clouds, specifically tropical low-level clouds, is currently the largest source of spread among state-of-the-art climate models [\textit{Cess et al.}, 1989\nocite{Cess_etal_1989}, \nocite{Bony_Dufresne_2005} \textit{Bony and Dufresne}, 2005, \nocite{Stevens_Bony_2013}\textit{Stevens and Bony}, 2013\nocite{Popke_etal_2013}].
-Specific limitations of modeled clouds include both features which differ from what one observes (e.g., `too few, too bright', \textit{Webb et al.} [2001]\nocite{Webb_etal_2001}, \textit{Nam et al.} [2012]\nocite{Nam_etal_2012}) as well as features which are inadequately understood
-(e.g., controls on cloud vertical structure, \textit{Nuijens et al.} [2015]\nocite{Nuijens_etal_2015}, and organization, \textit{Bretherton et al.} [2005], \textit{Muller and Held} [2012], \textit{Wing and Emanuel} [2014]).
+of clouds (specifically tropical low-level clouds) is currently the largest source of spread among state-of-the-art climate models [\textit{Cess et al.}, 1989\nocite{Cess_etal_1989}, \nocite{Bony_Dufresne_2005} \textit{Bony and Dufresne}, 2005, \nocite{Stevens_Bony_2013}\textit{Stevens and Bony}, 2013\nocite{Popke_etal_2013}].
+Specific limitations of modeled clouds include both features which differ from what one observes (ex: `too few, too bright', \textit{Webb et al.} [2001]\nocite{Webb_etal_2001}, \textit{Nam et al.} [2012]\nocite{Nam_etal_2012}) as well as features which are inadequately understood
+(e.g., controls on cloud vertical structure, \textit{Nuijens et al.} [2015]\nocite{Nuijens_etal_2015}, and organization, e.g., \textit{Bretherton et al.} [2005], \textit{Muller and Held} [2012], \textit{Wing and Emanuel} [2014]).
 An important reason why clouds remain inadequately represented in models, and poorly understood is the  
 %These types of features in General Circulation Model (GCM) simulations hint at the interplay between convective and stratiform clouds, as well as the 
-delicacy of the interactions between clouds and circulations (\textit{Bony et al.} [2015]\nocite{Bony_etal_2015}, \textit{Sherwood et al.} [2014]\nocite{Sherwood_etal_2014}). 
-%which makes it difficult to separate cause and effect.
+delicacy of the cloud-circulation interaction (\textit{Bony et al.} [2015]\nocite{Bony_etal_2015}, \textit{Sherwood et al.} [2014]\nocite{Sherwood_etal_2014}) which makes it difficult to separate cause and effect.
 The characteristics of clouds in GCMs should be represented
-in a manner which is consistent with fundamental theory, observations, and more fundamental models of cloud processes, for instance Cloud Resolving Models (CRMs).
+in a manner which is consistent with theory, observations, and more fundamental models of cloud processes, for instance Cloud Resolving Models (CRMs).
 Efforts to better understand the role of moist convection in the climate system would be advanced by an ability to simulate the interaction between convection and the large-scale circulation using both models with parameterized convection and models with explicitly simulated convection.
@@
 %and other processes dependent determined by subgrid-scale parameterizations, 
-play a decisive role on the overall statistics of the simulation [\textit{Popke et al.}, 2013, \textit{Becker et al.}, 2016, \textit{Coppin and Bony}, 2015\nocite{Coppin_Bony_2015}].  
+play a decisive role on the overall statistics of the simulation [\textit{Popke et al.}, 2013, \textit{Becker et al.}, 2016, \textit{Coppin and Bony}, 2015\nocite{Coppin_Stevens_2015}].  
 Due to the multiplicity of solutions that previous CRM-RCE simulations [\textit{Held et al.}, 2007, \textit{Jeevanjee and Romps}, 2013\nocite{Jeevanjee_Romps_2013}, \textit{Emanuel et al.}, 2014\nocite{Emanuel_etal_2014}, and \textit{Zhou}, 2015\nocite{Zhou_2015}] have produced which depend on parameterizations, domain size, grid-spacing, and surface temperature, we cannot per se assume that solutions of GCM-RCE simulations will be independent of domain size.
@@
 
-Although not specifically focused on details of the convection or cloud feedbacks, early studies of RCE [\textit{Manabe and Strickler}, 1964\nocite{Manabe_Strickler_1964}, \textit{Manabe and Wetherald}, 1967\nocite{Manabe_Wetherald_1967}] led to a fundamental advancement in our understanding of the atmosphere.
+Although not specifically focused on developingtails of the convection or cloud feedbacks, early studies of RCE [\textit{Manabe and Strickler}, 1964\nocite{Manabe_Strickler_1964}, \textit{Manabe and Wetherald}, 1967\nocite{Manabe_Wetherald_1967}] led to a fundamental advancement in our understanding of the atmosphere.
 The overall surface warming from high clouds and cooling from low clouds was first shown by Manabe and Strickler using this ansatz.
@@
 The design of the simulations and details of the model used are presented in the next section.
-In section 3 results are presented both in terms of the mean atmospheric state, and the response to a perturbation of 4 K to the SST.
-Section 3 also
+In section three the results are presented both in terms of the mean atmospheric state, and the response to a perturbation of 4 K to the SST.
+Section three also
 explores robust differences in the response to warming, and suggests that 
@@
 Despite having the same core model and identical physics, the total radiative feedback from warming still varies by about a factor of two.   
-Discussion and final conclusions are given in section 4.
+Discussion and final conclusions are given in sections four.
 
@@
 
-The framework of RCE is used here as a tool which allows us to focus on the interactions between radiation, large-scale circulation, and clouds without the complicating influence of
+The framework of RCE is used here as a tool which allows us to focus on the interactions between radiation, large-scale circulation, and clouds without the complicating influence 
 heterogeneities imposed on the large scale.
@@
 To eliminate the heterogeneities
-the Coriolis force is set to zero and the insolation and profiles of trace-gases (e.g., ozone) are likewise made independent of the horizontal grid.
-The cosine of the zenith angle is $\pi/4$ and the insolation used is $340.3 \, \rm{W/m}^2$, approximately equal to Earth's global annual mean value.  
-There is no diurnal cycle and a surface of water at a fixed temperature defines the lower boundary. 
-%Complications due to a dynamic ocean and the required long adjustment time are eliminated by prescribing a fixed value of SST.   
+the Coriolis force is set to zero and the insolation and profiles of trace-gases (e.g., ozone) are likewise made independent of the horizontal grid.   There is no diurnal cycle 
+and a surface whose properties are set to those of water at a fixed temperature defines the lower boundary. 
+Complications due to a dynamic ocean and the required long adjustment time are eliminated by prescribing a fixed value of SST.
 One result of this is that neither the surface nor the top of the atmosphere is expected to have a balanced energy budget.
@@
 
+The progression from homogeneous initial conditions through a period of dominant wave activity and
+eventually a stationary state, or equilibrated state 
+is illustrated in Figure \ref{fig:precevol}.
+This figure shows the time evolution of the precipitation rate on the 50M domain.
+After approximately 25 days of near homogeneous conditions fast, large-amplitude gravity waves as seen in the center panel develop and propagate through the domain.
+Approximately 30 days later these waves are no longer the dominant feature and have been replaced by multiple convective systems which move slowly through the domain.
+In this later stage the mean values of precipitation, relative humidity, and cloud cover fluctuate about a well defined mean value.
+It is this mean environmental state represented in the right panel of Figure \ref{fig:precevol} which we refer to as the mean equilibrium state, or stationary state, and which is analyzed in this study.
+The other domains show a similar progression from the initial state to equilibrium.
+
 Because there are fewer grid points on the smaller domains, the degree of variability in the domain mean per time step increases as the domain size decreases.  
-This is because a given perturbation will have a larger influence on the statistics of a domain with fewer grid points, relative to a domain with more grid points.  
 %This can be seen, for example, in the domain mean values of the total precipitation (Figure \ref{fig:precipvtime}).  
-To obtain comparable statistics between the various domains, and take advantage of the computational economy of the smaller domains, the length of simulation 
-increases as the domain size decreases.
-Details of the simulations examined in this paper are given in Table \ref{exptable}.
-The periods used for computing feedback and sensitivity parameters and cloud radiative effects (P1) and domain mean profiles (P2) are given in Table \ref{exptable}.
-The increased length of P1 was necessary to obtain robust statistics for the feedback parameters of the different domains.
+To obtain comparable statistics between the various domains, and take advantage of the computational economy of the smaller domains, the length of simulation and averaging period increases as the domain size decreases.
+To give an impression of the relative scale of features present on the
+$3/4 \rm{M}$, $12 \rm{M}$, and $200 \rm{M}$ domains Figure \ref{fig:convorg} shows them tiled according to scale periodically repeated to fill a region the size of the $200 \rm{M}$ domain.
+In general, precipitation is seen to organize on the largest scale available.
+The 200M domain shows signs that the maximum scale of convective organization may be between the 50M and 200M domains, but this is not conclusive and deserves further investigation.
 
@@
 The ICON model solves the fully three-dimensional nonhydrostatic and compressible Navier-Stokes equations and is described in detail in \textit{Z\"{a}ngl et al.}, [2015]\nocite{Zaengl_etal_2015}.
-All of the simulations described here use triangles with an edge length of 20 km, implying an effective grid spacing of about 13 km (defined as $\sqrt{\rm{cell \, area}}$ in \textit{Z\"{a}ngle et al.}, [2015].
-The vertical coordinate is a height-based hybrid coordinate with 60 vertical levels between the surface and the model top at 40 km.
-The top of the model uses a Rayleigh damping of the vertical wind following \nocite{Klemp_etal_2008}\textit{Klemp et al.}, [2008] to prevent the reflection of gravity waves from the model top.
-%starting at 25km.
 The variables are positioned on a regular-triangular C-grid with a combination of first- and second-order finite difference spatial discretizations.
@@
 %The German Weather Service implemented ICON as their operational weather forecast model in January of 2015.  
-ICON can also be used as a Large Eddy Simulation model capable of explicitly representing canonical cloudy boundary layer flows on grid meshes as fine as 50 m or less [\textit{Dipanker et al.}, 2015].
+ICON can also be used as a Large Eddy Simulation model capable of explicitly representing cannonical cloudy boundary layer flows on grid meshes as fine as 50 m or less [\textit{Dipanker et al.}, 2015].
 \nocite{Dipanker_etal_2015}
@@
 The microphysics scheme is from the COSMO-EU five-category prognostic scheme [\textit{Seifert}, 2008] predicting rain, snow, cloud ice, cloud liquid water, and water vapor.
-Relative humidity is computed over a liquid surface only.  
 The cloud cover scheme is based on a box-function probability density function with an added diagnostic anvil term that uses the detrainment of the convective parameterization.
@@
 
+All of the simulations described here use triangles with an edge length of 20 km, implying an effective grid spacing of about 13 km (defined as $\sqrt{\rm{cell \, area}}$ in \textit{Z\"{a}ngle et al.}, [2015], and a model top at 40 km.
+The vertical coordinate is a z-based hybrid coordinate with 60 vertical levels, which over a water surface, as used here, default to z-levels.
+The top of the model uses a Rayleigh damping of the vertical wind following \nocite{Klemp_etal_2008}\textit{Klemp et al.}, [2008] to prevent the reflection of gravity waves from the model top.
+%starting at 25km.
+
+Details of the simulations examined in this paper are given in Table \ref{exptable}.
 The profile used for the ozone is representative of the tropics and is the same profile used by \textit{Popke et al.}, [2013].
@@
 \section{Results}
-
-The progression from homogeneous initial conditions through a period of dominant wave activity and
-eventually a stationary state, or equilibrated state 
-is illustrated in Figure \ref{fig:precevol}.
-This figure shows the time evolution of the precipitation rate on the 50M domain.
-After approximately 25 days of near homogeneous conditions fast, large-amplitude gravity waves as seen in the center panel develop and propagate through the domain.
-Approximately 30 days later these waves are no longer the dominant feature and have been replaced by multiple convective systems which move slowly through the domain.
-In this later stage the mean values of precipitation, relative humidity, and cloud cover fluctuate about a well defined mean value.
-It is this mean environmental state represented in the right panel of Figure \ref{fig:precevol} which we refer to as the mean equilibrium state, or stationary state, and which is analyzed in this study.
-The other domains show a similar progression from the initial state to equilibrium.
-
-To give an impression of the relative scale of features present on the
-$3/4 \rm{M}$, $12 \rm{M}$, and $200 \rm{M}$ domains Figure \ref{fig:convorg} shows the same data from Figure \ref{fig:precvsdom}, tiled according to scale, periodically repeated to fill a region the size of the $200 \rm{M}$ domain.
-The $3/4 \rm{M}$, $3 \rm{M}$, $12 \rm{M}$, and $50 \rm{M}$ domains all show the precipitation and moisture structures to organize on the largest scale available (Figures \ref{fig:precvsdom}, \ref{fig:convorg}, \ref{fig:tqv5dom}).
-The 200M domain shows signs that the maximum scale of convective organization may be between the 50M and 200M domains, but this deserves further investigation.
-
 \subsection{Mean Climate}
@@
 The evolution of the domain mean total precipitation during the first two years of simulation for each of the five domains is shown in Figure \ref{fig:precipvtime}.
-Based on the precipitation we judge that all simulations have
-reached a stationary state after about 200 days, with the $50\rm{M}$ and $200\rm{M}$ domains adjusting to equilibrium much sooner.
-Because the $3/4\rm{M}$, $3\rm{M}$, and $12\rm{M}$ domains all proceed for longer than 2 years, the average value of the precipitation during the last six months of each simulation is shown by the dots at the right of Figure \ref{fig:precipvtime}, confirming that the mean value has indeed been reached during the period shown.
+Based on the precipitation we judge the simulations to
+have reached a stationary state after about 200 days.
+Because the $3/4\rm{M}$, $3\rm{M}$, and $12\rm{M}$ models all proceed for longer than 2 years, the average value of the precipitation during the last six months of each simulation is shown by the dots at the right of Figure \ref{fig:precipvtime}, confirming that the mean value has indeed been reached during the period shown.
 %There is a systematic variation  of the evolution of the precipitation field as a function of domain size but the differences are relatively small (10\%) as compared to the mean.
@@
 Hartmann} [2011]\nocite{Zelinka_Hartmann_2011}).
-All domains have three peaks in the cloud cover (0.6 km, 5 km, 13 km), with the upper two cloud maxima corresponding to anvil detrainment and melting level clouds, respectively.
-The simulations also uniformly produce two peaks of cloud liquid water below 4km (0.8 km, 1.2 km).
+All domains have three peaks in the cloud cover (0.6km, 5km, 13km), with the upper two cloud maxima corresponding to anvil detrainment and melting level clouds, respectively.
+The simulations also uniformly produce two peaks of cloud liquid water below 4km.
 Overall, the profiles plausibly represent the mean state of the tropical atmosphere (over ocean)
@@
 %First, the qualitative match between the profiles found in this study and those of P13 is quite good.  
-Comparing the profiles from our Figure \ref{fig:prof297} with Figure 4 from \textit{Popke et al.} [2013] shows that all simulations have a double peak of RH (1 km, 15 km) and a dry mid-troposphere with RH dropping to between 15\% and 20\% at about $7 \, \rm{km}$.
-All simulations have two peaks of cloud cover and cloud liquid water in the lowest $4 \, \rm{km}$.
+Comparing the profiles from our Figure \ref{fig:prof297} with Figure 4 from \textit{Popke et al.} [2013] shows that all simulations have a double peak of RH (1 km, 15 km) and a dry mid-troposphere with RH dropping to between 15\% and 20\% at about $7 \rm{km}$.
+All simulations have two peaks of cloud cover and cloud liquid water in the lowest $4 \rm{km}$.
 %In agreement with our Figure \ref{fig:prof297}, the profiles shown by P13 have a minimum value of tropospheric RH of %close to 20\% between about $6-8 \, \rm{km}$, two peaks of cloud liquid water below 4 km, and maxima of cloud ice of %$3-7 \rm{mg \, kg^{-1}}$.
@@
 %differences of several degrees and a vertical shift in the upper maximum of RH humidity by several km's.  
-Among the profiles from \textit{Popke et al.} [2013] for example, there is a difference of $2-3 \rm{km}$ in the vertical placement of the RH,  cloud fraction, and cloud ice around $15 \, \rm{km}$.
-The RH humidity at $15 \, \rm{km}$ differs by up to $20 \, \%$ and one of the temperature profiles is several degrees warmer throughout the troposphere.
+Among the profiles from \textit{Popke et al.} [2013] for example, there is a difference of $2-3 \rm{km}$ in the vertical placement of the RH,  cloud fraction, and cloud ice around $15 \rm{km}$.
+The RH humidity at $15 \rm{km}$ differs by up to $20 \, \%$ and one of the temperature profiles is several degrees warmer throughout the troposphere.
 %These comparisons indicate that RCE does a reasonable job of simulating the broad characteristics of the tropical environment and that there is some similarity between the global RCE ECHAM model and the planar RCE ICON model.
@@
 The organization of convection into large coherent structures has received much attention over the previous two decades. 
-Several different metrics (subsidence fraction, distance between clusters, bi-modality of water vapor, tropospheric RH, etc.
-[e.g., \textit{Bretherton et al.}, 2005; \textit{Tobin et al.}, 2012;  \textit{Coppin and Bony}, 2015]) have been used to determine whether aggregation is occurring in observations or simulations.
-To provide a quantification of the convective organization the subsidence fraction is computed.
-This measures the fraction of the model domain with subsiding motion ($w < 0 \rm{\, m \, s^{-1}}$), typically associated with non-convective regions.
+Several different metrics (subsidence fraction, distance between clusters, bi-modality of water vapor, tropospheric RH, etc.) have been used to determine whether aggregation is occurring in observations or global simulations.
+To provide a quantification of the convective organization the subsidence fraction (following \textit{Coppin and Bony} [2016]) is computed.
+This measures the fraction of the model domain with subsiding motion, typically associated with non-convective regions.
 The subsidence fractions for domains 3/4M, 3M, 12M, 50M, and 200M at an SST=297 K (301 K) are 0.72, 0.79, 0.78, 0.76, and 0.77 (0.70, 0.71, 0.75,  0.72, 0.71), respectively.
@@
 %The $3/4 \rm{M}$ domain has a smaller range of values compared to the other four models.  
-The driest regions for the $3/4 \rm{M}$ domain is relatively moist with $32$mm of vapor in contrast to the largest four domains which have dry regions that drop to about half as much ($17$ mm) water.
+The driest regions for the $3/4 \rm{M}$ domain is relatively moist with $32$mm of vapor in contrast to the largest four models which have dry regions that drop to about half as much ($17$ mm) water.
 Overall the largest four domains show a similar spatial structure of moisture.
@@
 pronounced in the present simulations (Fig. 5),
- rather the relative humidity profiles are comparable to the tropical mean profiles of comprehensive GCM simulations.  However, the time evolution of the cloud fields and water vapor,  
+ rather the relative humidity profiles are comparable to the mean profiles of comprehensive GCM simulations.  However, the time evolution of the cloud fields and water vapor,  
  %clear organization
@@
 There is variation between individual simulations in the response of the RH, but for all simulations the RH shifts vertically with warming resulting in a consistent increases of RH above $15 \, \rm{km}$ and between $5$-$8 \, \rm{km}$, and drying between $8-15 \, \rm{km}$.
-The RH difference profiles of all domains have fluctuations on the order of $15 \%$ with roughly the same vertical levels of tropospheric maxima and minima and non-systematic fluctuations in the lowest $4 \, \rm{km}$.
+The RH difference profiles of all models have fluctuations on the order of $15 \%$ with roughly the same vertical levels of tropospheric maxima and minima and non-systematic fluctuations in the lowest $4 \, \rm{km}$.
 %The simulations presented here and the results from P13 show a clear secondary maxima in the cloud cover which seems related to the freezing level.  
@@
 This likely indicates an interplay of multiple mechanisms in the response.
-As is to be expected, the hydrological sensitivity scales closely with the change in atmospheric cooling (not shown) which is dominated by longwave feedbacks, (i.e., not variability in shortwave absorption as is evident when looking across climate models (e.g., \textit{Takahashi et al.} [2009])\nocite{Takahashi_2009}) and thus the weakest sensitivity is found in the 3M domain.
+As is to be expected, the hydrological sensitivity scales closely with the change in atmospheric cooling (not shown) which is dominated by longwave feedbacks, (i.e., not variability in shortwave absorption as is evident when looking across climate models (e.g., \textit{Takahashi et al.} [2009])\nocite{Takahashi_2009} and thus the weakest sensitivity is found in the 3M domain.
 
@@
 The values for individual models from CMIP5 are also displayed with the tan colored markers.
- These results highlight the ability of different simulations to have  similar climates but differing climate sensitivities (\textit{Mauritsen et al.} [2013]\nocite{Mauritsen_etal_2013}, \textit{Zhao et al.} [2015]).
+ These results highlight the ability of different simulations to have  similar climates but differing climate sensitivities (\textit{Mauritsen et al.} [2012]\nocite{Mauritsen_etal_2013}, \textit{Zhao et al.} [2015]).
 
@@
 
-\bibitem[{\textit{Coppin and Bony}(2015)}]{Coppin_Bony_2015}
+\bibitem[{\textit{Coppin and Bony}(2015)}]{Coppin_Stevens_2015}
 Coppin, D., and S.~Bony (2015), Physical mechanisms controlling the initiation
-  of convective self-aggregation in a General Circulation Model, \textit{J.\
+  of convective self-aggregation in a general circulation model, \textit{J.\
   Adv. \ Model. \ Earth \ Syst.}, \textit{7}, \doi{10.1002/2015MS000571}.
@@
 \begin{table}
-    \caption{Length of simulations, SST used, size and names of domains for each simulation.
-The M in the domain names stands for million (or Mega) $\rm{km}^2$.
-Also shown are two different periods (P1 and P2) of time used for computing mean values from the end of the simulations.
-See text and captions for details.}
+    \caption{Length of simulations, SST used, size and names of domains for each simulation.  The M in the domain names stands for million (or Mega) $\rm{km}^2$.}
     \begin{center}
@@
     %\begin{tabular}{l*{3}{c}r}
-    \begin{tabular}{*{8}{c}}
+    \begin{tabular}{*{5}{c}}
     \hline
@@
     \hline
-    Domain    &          Area  ($\rm{km}^2$)         & Edge Length (km)            &   Grid Points    &   SST (K)          & Length (year)    & P1 (year) & P2 (month)     \\ \hline
-    3/4M        &   $\mathrm{0.80\times 10^6}$   &  960 $\times$ 831            &    4,608            &  297/301           & 10                     & 9             & 12                    \\
+    Domain      & Area                                      & Grid Points    &   SST           & Length         \\ \hline
+    3/4M           &   $\mathrm{0.80\times 10^6 km^2}$  &    4,608            &  297/301 K    & 10 years                                          \\
     \\
-    3M           & $\mathrm{3.2\times 10^6}$       & 1,920 $\times$ 1,663        &  18,432           &   297/301          & 10                     & 9              & 4                                   \\
+ %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
+    3M                & $\mathrm{3.2\times 10^6 km^2}$   &  18,432           &   297/301 K   & 10 years                                          \\ 
     \\
-    12M         & $\mathrm{12.8\times 10^6}$     & 3,840 $\times$ 3,326        &   73,728          & 297/301            &   4                     & 3              & 8                                               \\
+ %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
+    12M              & $\mathrm{12.8\times 10^6 km^2}$ &  73,728          & 297/301 K    &   4 years                                                     \\ 
     \\
-    50M         & $\mathrm{51.1\times 10^6}$     & 7,680 $\times$ 6,651        &  294,912         & 297/301            &    2                    &  1              & 4                                                \\
+  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
+    50M               & $\mathrm{51.1\times 10^6 km^2}$ &  294,912     & 297/301 K      &    2 years                                                     \\ 
     \\
-    200M       & $\mathrm{204\times 10^6} $     & 15,360 $\times$ 13,302     & 1,179,648      & 297/301            &    1                    &  0.6          &  0.76                                     \\ \hline
+   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
+    200M            & $\mathrm{204\times 10^6 km^2} $ & 1,179,648  & 297/301 K   &        1 year                                             \\ \hline
+    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
      \end{tabular}\par
@@
 \caption{Mean Energetics: Long- and short-wave feedback parameters, total feedback parameter, equilibrium climate sensitivity and hydrologic sensitivity parameter (HSP) (defined as $\Delta P/\Delta T_s$, where $P$ is the total precipitation) as a function of domain size.
-Values were averaged over the P1 period.}
+}
     %\begin{tabular}{|c|c|c|c|c|c|}
@@
  Domain & $\lambda_{sw}/\lambda_{sw,clr} (\mathrm{W/m^2 K}) $& $\lambda_{lw}/\lambda_{lw,clr}  (\mathrm{W/m^2 K}) $ &   $\lambda  (\mathrm{W/m^2 K}) $ & ECS (K) & HSP ($\mathrm{\%/K}$)   \\ \hline
-    0.75 M          &   0.08/0.25    & -1.93/-2.13              & -1.85  $\pm (0.4/0.4)$           &  2.00           &        2.3     \\ 
+    0.75 M          &   0.08/0.25    & -1.93/-2.13              & -1.85             &  2.00           &        2.3     \\ 
     \\
-    3M                & -0.89/0.25     & -1.49/-1.55            & -2.39 $\pm (0.3/0.3)$         & 1.55                &   1.9  \\  
+    3M                & -0.89/0.25     & -1.49/-1.55            & -2.39           & 1.55                &   1.9  \\  
     \\
-    12M             & 0.13/0.23      & -2.28/-2.48             & -2.15 $\pm (0.3/0.2)$          & 1.72                &  2.6   \\  
+    12M             & 0.13/0.23      & -2.28/-2.48             & -2.15           & 1.72                &  2.6   \\  
     \\
-    50M             & 1.71/0.25      & -2.84/-2.05             & -1.13 $\pm (0.2/0.2)$           & 3.29               &  2.7  \\  
+    50M             & 1.71/0.25      & -2.84/-2.05             & -1.13            & 3.29               &  2.7  \\  
     \\
-    200M          & 0.92/0.25      & -2.51/-2.25             & -1.59  $\pm (0.2/0.1)$          & 2.33                &   2.7    \\  \hline
+    200M          & 0.92/0.25      & -2.51/-2.25             & -1.59            & 2.33                &   2.7    \\  \hline
     \end{tabular}\par
@@
     \label{tab:lambda}
-\end{center}
-\end{table}
-
-\begin{table}
-    \caption{Total cloud cover and column integrated diagnostics.  Water Vapor ($q_v$), Liquid Water ($q_c$), and Ice ($q_i$).  Values were computed over the P2 period.}
-    \begin{center}
-    %\begin{tabular}{| l | l | l | l | p{5cm} |}
-    %\begin{tabular}{l*{3}{c}r}
-    \begin{tabular}{*{6}{c}}
-    \hline
-    %\multicolumn{5}{|c|}{Experimental Specifications} \\
-    \hline
-    Domain      & Tot Cloud Cover (\%)        & $q_v (\mathrm{kg/m^2}) $  &   $q_c (\mathrm{g/m^2}) $   & $q_i (\mathrm{g/m^2})$    & SST (K)   \\ \hline
-    3/4M           &   $\mathrm{82}$  &    39.7            &  15.3    & 6.16              & 297                            \\
-                       &       81                &   55.5             &   17.7   & 6.17              & 301  \\
-                       \\
- %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
-    3M                & $\mathrm{73}$   &  36.4            &   22.2   &      5.03          & 297                                 \\ 
-                         &           75             &   52.5             &   25.8  & 5.64               & 301  \\
-    \\
- %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
-    12M              & $\mathrm{67}$ &  36.4          & 20.4    &        5.26              & 297                                      \\ 
-                         &       63              &   49.7          & 39.3    &        6.35             & 301  \\
-    \\
-  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
-    50M               & $\mathrm{63}$ &  37.0     & 24.2      &    5.54                & 297                                    \\ 
-                          &       58               &  51.1     &  21.1     &    6.64               & 301  \\
-    \\
-   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
-    200M            & $\mathrm{64} $ &  36.9      & 22.5  &        5.60                  & 297                       \\
-                         &       57                &  51.9      & 26.4  &        6.74                 & 301     \\ \hline
-    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
-     \end{tabular}\par
-     \label{colintvars}
 \end{center}
@@
   \caption{Snapshots in time of total precipitation ($\rm{mm \,day^{-1}}$) for the $\rm{3/4 M (left), 12 M (middle),}$ and $\rm{200M (right)}$ domains tiled according to scale.
-Times and colors are same as for Fig.
+Color scale is same as for Fig.
 \ref{fig:precvsdom}, $\rm{SST}=301 \, \rm{K}$.}
@@
    \centering
-   \includegraphics[width=6.7in]{fig5_browns.eps}
-   %\includegraphics[width=6.7in]{rce_ecs_20km_297_vprof_green.eps}
-   \caption{Mean vertical profiles with a constant SST of 297 K.  Values were computed over the P2 period.}
+   \includegraphics[width=6.7in]{rce_ecs_20km_297_vprof_green.eps}
+   \caption{Mean vertical profiles with a constant SST of 297 K.  The means are computed over a time period of several months, at the end of each simulation.}
    \label{fig:prof297}
@@
    \centering
-   \includegraphics[width=6.5in]{fig7_lthick2_green.eps}
-   %\includegraphics[width=6.5in]{rce_ecs_20km_reldiff_24km_green.eps}
-   \caption{Difference ($301 \rm{K} - 297 \rm{K}$) of mean vertical profiles between the two sets of fixed SST cases.  Values were computed over the P2 period.}
+   \includegraphics[width=6.5in]{rce_ecs_20km_reldiff_24km_green.eps}
+   \caption{Difference ($301 \rm{K} - 297 \rm{K}$) of mean vertical profiles between the two sets of fixed SST cases. }
    \label{fig:profdiff}
@@
    \includegraphics[width=6.5in]{rce_ecs_20km_reldiff_4km.eps}
-   \caption{Same data as Figure \ref{fig:profdiff}, zoomed in to reveal boundary layer features.  Values were computed over the P2 period.}
+   \caption{Same data as Figure \ref{fig:profdiff}, zoomed in to reveal boundary layer features.}
    \label{fig:profdiffzoom}
-\end{figure}
-
-\begin{figure}[h] %  figure placement: here, top, bottom, or page
-   \centering
-   \includegraphics[width=6.5in]{vprofile_diffrel200M.eps}
-   \caption{Same data as Figure \ref{fig:profdiff}, plotted relative to the 200M domain.  Values were computed over the P2 period.}
-   \label{fig:profdiffrel200M}
 \end{figure}

### 2019-09-20 Silvers_etal_2017_draft.tex
committing a number of old tex files into the latex_git repo

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
% Modified July 2014
%
% This template includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% All questions should be e-mailed to latex@agu.org.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format: two column (default)
% and draft.
%
% PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
%
% Choose the journal abbreviation for the journal you are
% submitting to:

% jgrga JOURNAL OF GEOPHYSICAL RESEARCH
% gbc   GLOBAL BIOCHEMICAL CYCLES
% grl   GEOPHYSICAL RESEARCH LETTERS
% pal   PALEOCEANOGRAPHY
% ras   RADIO SCIENCE
% rog   REVIEWS OF GEOPHYSICS
% tec   TECTONICS
% wrr   WATER RESOURCES RESEARCH
% gc    GEOCHEMISTRY, GEOPHYSICS, GEOSYSTEMS
% sw    SPACE WEATHER
% ms    JAMES
% ef    EARTH'S FUTURE
% ea    EARTH AND SPACE SCIENCE
%
%
%
% (If you are submitting to a journal other than jgrga,
% substitute the initials of the journal for "jgrga" below.)

%\documentclass[draft,grl]{agutex2015}
\documentclass[grl]{agutex2015}
% To create numbered lines:

% If you don't already have lineno.sty, you can download it from
% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
% (or search the internet for lineno.sty ctan), available at TeX Archive Network (CTAN).
% Take care that you always use the latest version.

% To activate the commands, uncomment \usepackage{lineno}
% and \linenumbers*[1]command, below:

\usepackage{graphicx}
\usepackage{epstopdf}

% \usepackage{lineno}
% \linenumbers*[1]
%  To add line numbers to lines with equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Figures and Tables
%
%
% DO NOT USE \psfrag or \subfigure commands.
%
%
%  Uncomment the following command to include .eps files
%  (comment out this line for draft format):
%  \usepackage[dvips]{graphicx}
%
%  Uncomment the following command to allow illustrations to print
%   when using Draft:
  \setkeys{Gin}{draft=false}
%
% Substitute one of the following for [dvips] above
% if you are using a different driver program and want to
% proof your illustrations on your machine:
%
% [xdvi], [dvipdf], [dvipsone], [dviwindo], [emtex], [dviwin],
% [pctexps],  [pctexwin],  [pctexhp],  [pctex32], [truetex], [tcidvi],
% [oztex], [textures]
%
% See how to enter figures and tables at the end of the article, after
% references.
%
%% ------------------------------------------------------------------------ %%
%
%  ENTER PREAMBLE
%
%% ------------------------------------------------------------------------ %%

% Author names in capital letters:
\authorrunninghead{SILVERS ET AL.}

% Shorter version of title entered in capital letters:
\titlerunninghead{Cloud Feedbacks in long-AMIP}

%Corresponding author mailing address and e-mail address:
%\authoraddr{Corresponding author: A. B. Smith,
%Department of Hydrology and Water Resources, University of
%Arizona, Harshbarger Building 11, Tucson, AZ 85721, USA.
%(a.b.smith@hwr.arizona.edu)}

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

\title{Decadal variations of cloud feedback in long-AMIP experiments with three GFDL climate models.}
%
% e.g., \title{Terrestrial ring current:
% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
%

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

%Use \author{\altaffilmark{}} and \altaffiltext{}

% \altaffilmark will produce footnote;
% matching \altaffiltext will appear at bottom of page.
\authors{Levi G. Silvers, David Paynter, and Ming Zhao}
% \authors{A. B. Smith,\altaffilmark{1}
% Eric Brown,\altaffilmark{1,2} Rick Williams,\altaffilmark{3}
% John B. McDougall\altaffilmark{4}, and S. Visconti\altaffilmark{5}}

%\altaffiltext{1}{Department of Hydrology and Water Resources,
%University of Arizona, Tucson, Arizona, USA.}

%\altaffiltext{2}{Department of Geography, Ohio State University,
%Columbus, Ohio, USA.}

%\altaffiltext{3}{Department of Space Sciences, University of
%Michigan, Ann Arbor, Michigan, USA.}

%\altaffiltext{4}{Division of Hydrologic Sciences, Desert Research
%Institute, Reno, Nevada, USA.}

%\altaffiltext{5}{Dipartimento di Idraulica, Trasporti ed
%Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

%% ------------------------------------------------------------------------ %%
%
%  KEYPOINTS
%
%% ------------------------------------------------------------------------ %%

% Key points are 1 to 3 points that the author provides,
% that are 100 characters or less, that are ultimately published
% with the article.
%% for example:
% \keypoints{\item Here is the first keypoint. what happens if it is a
% long keypoint, like this one. We want to see this wrap please.
% \item This is the second.
% \item And here is the third keypoint
% }

\keypoints{\item Three models show the Eastern Tropical Pacific as a key location where decadal trends in SST and low-level clouds strongly influence the global energy budget
\item Changes in low-level clouds can be linearly decomposed but with differing magnitudes of dependencies on EIS and SST
\item The cloudy response of the models differs markedly between twentieth century periods with high and low climate sensitivities}
%\item AM2.1, AM3, and AM4g10r8 all show strong twentieth
%century decadal variability of the global feedback parameter.
%\item All three models show increased low-level clouds in the East Pacific
%over recent decades.
%\item Low-level cloud trends depend on both EIS trends 
%and omega trends.}

%% Keypoints will print underneath the abstract.

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

% >> Do NOT include any \begin...\end commands within
% >> the body of the abstract.

\begin{abstract}

Significant decadal variability of the global feedback parameter is shown to be clearly linked to the pattern of surface warming through the evolution of low-clouds and the estimated inversion strength (EIS).  We examine the atmospheric response to changing SST patterns between 1870-2004 using the amip-piForcing experimental configuration with three GFDL atmospheric global climate models (AM2, AM3, and AM4).  There is a notable strengthening of the negative global feedback from the middle period of the 20th century until the present.  We contrast the variability of the cloud response among the models between these two periods.  The changing low-cloud cover is analyzed within a framework that includes trends of the EIS and the mid-tropospheric vertical velocity.

Recently it has been argued that decadal changes in low-level cloud cover over the eastern Pacific ocean basin strongly influence the global net feedback parameter.  These decadal changes of low-level cloud cover have been tied to corresponding changes in the observed sea surface temperatures.  We examine these claims with AM2, AM3, and AM4.  The dominant configuration difference among the models is the parameterization of the convective clouds.  The amip-piForcing experiment provides an ideal configuration to test the range of atmospheric responses to a prescribed but evolving SST pattern.

All three GFDL models confirm the importance of the relationship between the global climate sensitivity and the trends in the eastern Pacific of SST and low-level clouds.  However, there are noteworthy differences in the cloud response of the models.  Despite all three models being driven by observed SSTs, sea ice concentration, and constant preindustrial forcing agents distinct net global feedbacks are simulated.

%Recently it has been argued that decadal changes in low-level cloud cover over the eastern Pacific ocean basin strongly influence the global net feedback parameter.  These decadal changes of low-level cloud cover have been tied to corresponding changes in the observed sea surface temperatures (SST).  We examine this claim in three generations of GFDL atmospheric global climate models $(AM2.1, AM3, and AM4_g10r8)$.  The dominant configuration difference among the models is the parameterization of convective clouds.  Atmospheric experiments with observed SSTs (atmospheric forcing held at constant preindustrial values) between 1870-2004 are examined to elucidate the source of differences between the models.  
%
%All three models are shown to have strong decadal variability in their net feedback parameter, the global mean cloud-radiative effect, and the low-level cloud fields.  All three models confirm the importance of the relationship in the eastern Pacific region between decadal SST patterns and low-level cloud changes.  However, there are noteworthy differences in the cloud response of the models.  
%
%The correlation between changes in low-level cloud cover and the lower tropospheric stability is used to examine the impact of the alternate cumulus parameterizations used by the models.  We approximate the change of low-level cloud with a linear combination of changes in lower tropospheric stability and SST.  The usefulness of this approximation differs among the three models examined.   
%
%Despite all models being driven by observed SSTs, sea ice concentration, and having constant preindustrial atmospheric forcing agents distinct net global feedbacks are simulated. 
%
\end{abstract}

%% ------------------------------------------------------------------------ %%
%
%  BEGIN ARTICLE
%
%% ------------------------------------------------------------------------ %%

% The body of the article must start with a \begin{article} command
%
% \end{article} must follow the references section, before the figures
%  and tables.

\begin{article}

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

\section{Introduction}

The global energy budget of Earth is often considered in a mean, equilibrated context.  However, fluctuations in the TOA net radiative flux are observed on monthly, yearly, and decadal scales.  The decadal variability of the energy budget is also present in the global mean cloud radiative effect.  This paper elucidates the nature of changes to the cloud fields in simulations covering 1871-2005.  By clarifying key geographical regions and particular types of clouds that play a prominent role in the decadal variability of the TOA net radiative flux we hope to increase our confidence in the equilibrated energy budget analysis of Earth.

    \begin{enumerate}
        \item Decadal variations of global feedback in AMIP-like experiments offer an opportunity for 
        mechanistic attribution
        	\begin{enumerate}
	    \item SST patterns have been shown to be important for variations of global 
	    feedback (Gregory and Andrews, 2016).  
	    \item Estimated Inversion Strength (EIS)

	    The lower-tropospheric stability, and the related estimated inversion strength (EIS) has been used as a predictor of low-level clouds in select stratocumulus dominated regions (Klein and Hartmann, 1993, Wood and Hartmann, 2006).  The tropical marine EIS was found by Zhou et al. 2016 to be well correlated with the evolution of tropical tropical low-cloud change.  The EIS can be approximated by a linear combination of the surface temperature and the temperature on the 700hPa pressure level.  In the tropics, this provides a glimpse of one influence of the convection parameterization because the mid-tropospheric temperature is largely determined by the lapse rate in the warm pool regions with strong deep convection.

	    \item Analyzing alternate atmospheric climate models with the same SST 
	    patterns and atmospheric forcing throughout the twentieth century highlights
	    both atmospheric internal variability and the impact of different parameterization 
	    configurations among the models.
	    \item Why AM2.1, AM3, and AM4g10r8?
	\end{enumerate}
	\item Relationship between decadal feedback, equilibrium climate sensitivity, and effective climate sensitivity
	\item Review of Gregory and Andrews 2016, Zhou et al. 2016, Qu et al. 2014,2015, and Paytner et al. 2017
    \end{enumerate}

\section{Method}
%    \begin{enumerate}
 %       \item Description of amipPiForcing experiments
\subsection{Description of amipPiForcing experiments}

        The primary experiment used in this work corresponds to the amip-piForcing experiment.  For this experiment the AGCMs are run using observed SST and sea-ice, but with the forcing due to GHG, aerosol, and solar forcing set to assumed pre-industrial levels and held constant throughout the experiment.  The time simulated is from 1870 to 2005.  The amip-piForcing experiments are sometimes referred to as a `long-AMIP' experiments.  The amip-piForcing experiment has been included as one of the tier-II experiments for CFMIP3 (Webb et al. 2017), for additional details and examples see Gregory and Andrews (2016) and Zhou et al. (2016).

\subsection{Description of AM2.1, AM3, and AM4g10r8}

        The three GFDL atmospheric models analyzed in this paper have many differences, but the those that are thought to be of primary importance to the top-of-the-atmosphere radiation budget are relatively few.  The AM3 and AM4g10r8 models include an aerosol indirect effect by including the cloud drop number as a prognostic variable.  The AM2.1 model diagnosed the cloud drop number.  The parameterization schemes used to represent cumulus convection differs significantly among the three models.  The AM2.1 model uses the Relaxed-Arakawa-Schubert (RAS) scheme, AM3 uses the Donne-Deep scheme for deep convection and the University of Washington shallow convection scheme (UWShCu, Bretherton et al. 2004) for shallow convection.  AM4g10r8 uses a version of the UWShCu scheme that has been modified to include two bulk plumes which can account for both shallow and deep convection.  In addition to these differences, the scheme which computes the radiative transfer was updated from SEALW99/ESFSW99 in AM2.1 and AM3 to SEALW16/ESFSW16 in AM4g10r8.

\subsection{Methodology of Analysis (here or in results?)}        
%        \begin{enumerate}
%            \item Global feedback parameter via Gregory regression sliding window
            Because our interest is in the covariation of R and T rather than the change relative to a control state we compute the differential climate feedback parameter in the same was as in Gregory and Andrews [2016].  That is, linear regression is used to compute the trend between R and T.  The regression is applied to the global yearly mean values over 30 windows.  The values plotted in Figure 1 represent the mid-point of each window.  
 %           \item Global maps and global mean time series of trends per years
            To determine the spatial pattern of changes to particular variables linear regression was used at each grid point.              
 %           \item Estimated Inversion Strength

            The estimated inversion strength can be thought of as a correction to the LTS based on the moist adiabatic profile.  The LTS is defined to be $\rm{LTS}=\theta_{700}-\theta_{sfc}$.  
            To compute the estimated inversion strength (EIS) we follow the approximation made by Wood and Bretherton [2006]: 
            \begin{equation}
              \rm{EIS} = \rm{LTS} - \Gamma^{850}_m (z_{700}-\rm{LCL})
            \end{equation}
            with the lifting condensation level (LCL) calculated as $\rm{LCL}=(20+(T_{sfc}-273.15)/5)(1-RH_{sfc})$.
            The potential temperature gradient for moist-adiabatic processes is calculated as
            \begin{equation}
              \Gamma_m(T,p)=\frac{g}{c_p} \left[ 1-\frac{1+L_v q_s(T,p)/R_a T}{1+L^2_v q_s(T,p)/c_p R_v T^2} \right].
            \end{equation}
            To compute $\Gamma^{850}_m$ we used the temperature on the $850 \rm{hPa}$ pressure level and computed the saturation vapor pressure on the 
            $850 \rm{hPa}$ level using $q_s=610.8 \, \rm{exp}[17.27(T_{850}-273.15)/(T_{850}-35.85)] (\rm{hPa})$.  When the pressure surfaces of interest for these calculations intersect topography 
            the variables we are interested in are not defined.  To account for this, missing vallues of $\rm{T}_{850}$ are set to 50 $K$, $\rm{T}_{sfc}$ is not allowed to be lower than $200$ K, and $\rm{RH}_{sfc}$
            is not allowed to be lower than $5 \%$.

%    \end{enumerate}

\section{Results}

%\begin{enumerate}
 %   \item General Results
\subsection{General Results}

We have shown that all three models exhibit strong decadal variability of the feedback parameter.  The close connection between the global feedback and the CREs is clear based on their respective time series.  Correlations between the global feedback parameter and CRE for each model are: 0.93, 0.93, and 0.81 for AM2.1, AM3, and AM4g10r8, respectively.

Over the second half of the twentieth century AM4g10r8 and AM3 show a strong decrease of the global feedback parameter and the CRE response (Fig. \ref{fig:alphacre}).  Both of these models also have an increasing trend of EIS during this time period (Fig. \ref{fig:alphacre}).  In contrast, AM2.1 has a weak decrease of global feedback parameter and a nearly constant CRE trend during this time period.  The trend of EIS for AM2.1 is relatively flat and less than that for AM4g10r8 and AM3.  
%If the change of LLC can be linearly decomposed into a component due to the EIS and one due to the change of SST I would then expect this to indicate a poorer correlation for AM2.1 compared to AM3 in the tropics.  
Between 1925 and 1955 the average global feedback parameter for AM4, AM3, and AM2.1 changes from average values of (-1.35, -1.02, -1.80) to (-2.22, -2.42, -2.20) between 1975 and 1989.  This represents a dramatic change in the global feedback parameter and determining the cause will be an important part of our ability to understand how clouds influence the global energy budget on decadal time scales.

%Changes in low-cloud cover where approximated by Zhou et al. 2016 as $\Delta \rm{LCC} = \delta \Delta \rm{EIS} - \gamma \Delta \rm{SST}$.  If this holds then to the extent that different models use the same SST fields, the change of LCC should follow the change of EIS.  
%The importance of different SST patterns with the same mean value has been recognized (Andrews et al. 2015).  Is there a similar importance of the EIS pattern?  In this context the hypothesis (Qu et al. 2014,2015) that changes of EIS can be approximated as 
%$\Delta \rm{EIS} \approx \alpha \Delta T_{700}-\beta \Delta T_s $ indicates that the pattern of EIS change is entirely (for the case of the same SST) determined by the change of temperature on the 700 hPa level.  This is an easier quantity to diagnose from GCMs than EIS.

%All three models show an increase of the anomalous tropical mean low-level clouds and EIS between about 1975 and 2005, with the increase in AM2.1 covering the smallest period of time.   
%The tropical marine low-cloud changes in AM4g10r8 are well explained (r=0.96) by a linear combination of the changes in the EIS and the SST.  
%To the extent that the MAC LWP from Norris et al. 2016 represents a realistic trend of LWP the AM4g10r8 LWP trend shows a more realistic trend than AM2.1.  
%Because of the large amount of the anomalous change in low-cloud cover that can be explained by the linear combination of EIS and SST, as in CAM5.3, it is tempting to conclude that AM4g10r8 is doing the best job at reproducing observed relationships between EIS and low-cloud cover.  
%However, AM4 needs to be tested for its representation of the cloud controlling factors which have been discussed by Bretherton, and are shown in Figure 1 of the supplementary material of Zhou et al. 2016.

The period after about 1975 is found by all three models to have a small climate sensitivity (large, negative feedback parameter, Fig. \ref{fig:alphacre}) and a negative CRE.  This period also corresponds in all three models to an increase of tropical mean low-level clouds  (Fig. \ref{fig:lccts}).  Computing the trend of LCC change between 1975-2005 reveals much of this change to be concentrated in the eastern Pacific ocean basins (Fig. \ref{fig:lcceis_late}) in agreement with the findings of Zhou et al. 2016.  Further analysis of the changes to low-level clouds is discussed in the next section.

A strong relationship between LCC and EIS in many regions of the globe is shown by the trends of LCC and EIS between 1975-2005 (Figure \ref{fig:lcceis_late}) and between 1925-1955 (Figure \ref{fig:lcceis_early}).  Both time periods have a large increase of both EIS and LCC in the equatorial eastern Pacific ocean.  However, during the later period there is an increase of LCC throughout much of the Southern Hemispheric oceans while the early period the LCC decreases in much of the Southern Hemispheric oceans and northern midlatitudes.  This is consistent with a positive cloud feedback/large climate sensitivity during the early period and a small cloud feedback/climate sensitivity during the later period (Fig. \ref{fig:alphacre}).

%    \item Multiple Linear Regression 
\subsection{Multiple Linear Regression}

    The anomalous changes of tropical marine low-cloud cover were shown to be well explained by a linear combination of the change in EIS and SST in Zhou et al. 2016.  We explore the linear dependence of low-cloud changes on EIS and SST using multiple linear regression to determine the relative contributions of each component.  The coefficients $\gamma$ and $\delta$ can thus be determined for particular experiments or models in the following assumed relationship: 
    \begin{equation} 
    \Delta \rm{LCC} \approx \gamma \Delta \rm{EIS} - \delta \Delta \rm{SST}.
    \label{eqLCC}
    \end{equation}  
Based on high correlations between changes in low-cloud cover and the linear combination of changes in EIS and SST the above relationship holds fairly well.  However, we find that the relative contributions of EIS and SST to the low-cloud cover is model dependent.  Because the three models examined here all have observationally based SST prescribed, this difference likely indicates differences in the relative importance of the EIS fields which are in turn driven by the temperature on the $700 \rm{hPa}$ surface.  The importance of the low-level and mid-tropospheric temperature field is not surprising.  The direct connection between the temperature field at particular levels with parameterization schemes (convection, turbulence) provides an encouraging link between details of the parameterizations and the low-level cloud field.

Several noteworthy points can be drawn from Table 1.  As shown by the correlation coefficients, the decomposition used by Zhou et al. 2016 to explain the variance in the change of the low-cloud cover is not directly applicable to other models.  Using multiple linear regression to approximate the best fit for each model explains a significantly higher proportion of the variance in the changing low-cloud cover.  Also interesting are the varying coefficients computed for Eq. ref{eqLCC}.  This indicates that each of the models has a different relative sensitivity of low-clouds to EIS and SST.

Several noteworthy points can be drawn from Table 1.  As shown by the correlation coefficients, the decomposition used by Zhou et al. 2016 to explain the variance in the change of the low-cloud cover is not directly applicable to other models.  Using multiple linear regression to approximate the best fit for each model explains a significantly higher proportion of the variance in the changing low-cloud cover.  Also interesting are the varying coefficients computed for Eq. ref{eqLCC}.  This indicates that each of the models has a different relative sensitivity of low-clouds to EIS and SST.

We find some agreement with previously published work, but also some interesting differences.  Our results, as well as those of Grise and Medeiros, 2016, and Paytner et al. 2017 indicate that low-level clouds, and thus the TOA net CRE, strongly depend on both EIS and the large-scale vertical velocity, omega.

\subsection{Linear approximation of the Estimated Inversion Strength}

Changes in the EIS where shown to be well approximated as a linear combination of the surface temperature and the temperature on the $700 \rm{hPa}$ pressure level by Qu et al. 2014.  Specifically,
\begin{equation}
  \Delta \rm{EIS} \approx \alpha \Delta T_{700}-\beta \Delta T_{sfc},
  \label{eq:eis}
\end{equation}
where $T_{sfc}$ and $T_{700}$ are the temperatures on the surface and the $700 \rm{hPa}$ pressure surface, respectively.
This provides an elegant simplification of the EIS and shows its close relation to the lower troposheric stability (different of potential temperature between 700 hPa and the surface).  In the atmosphere the relative influence of the $T_{sfc}$ and $T_{700}$ on the EIS varies depending on location.  One of the strengths of long-AMIP experiments is the use of observed SST so modeled differences in the marine EIS fields will be largely due to modeled differences in $T_{700}$.  Approximations of EIS using eq. \ref{eq:eis} are compared with the simulated change of EIS in Figures \ref{fig:lcceisapp_am4}-\ref{fig:lcceisapp_am2}.  Overall the approximation captures the spatial patterns of changes in the EIS field, but the magnitude is overestimated.

%\end{enumerate}

\section{Conclusions}

The eastern Pacific has been shown to be a key location where decadal trends in SST and low-level clouds can strongly influence the global energy budget.

These changes in low-level clouds were shown to be well modeled by a linear combination of anomalous EIS and SST.  However, the coefficients of the decomposition vary among the models.  This implies that the models do not weight the influence of EIS and SST in the same way.  The response of low-level clouds thus depends to differing degrees on the changes in the 700 hPa temperature.  This provides a relatively simple connection between differing model parameterizations and the response of the clouds to changing SST patterns.

We have also shown that the although the three models respond similarly to the SST patterns between 1975-2005, their response to the SST patterns throughout the twentieth century differs dramatically.  The contrast in response between the period of 1975-2005 and 1925-1955 is emphasized.

Using the observed sea surface temperature and ice concentrations as the lower boundary for the atmosphere eliminates the feedback processes between the atmosphere, land, and ocean in nature.  However, using these observations ensures that the atmospheric models are driven by the the same patterns and magnitudes of warming.  This provides an excellent test of how much freedom of response the atmosphere alone is capable of given similar boundary conditions.

%%% End of body of article:

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Optional Appendix goes here
%
% \appendix resets counters and redefines section heads
% but doesn't print anything.
% After typing \appendix
%
\appendix
%\section{Here Is Appendix Title}
% will show
% Appendix A: Here Is Appendix Title
%
\section{A few of Levi's questions}
\begin{enumerate}

\item The differential climate feedback parameter in Fig. 1 shows a relatively smooth transition from the small negative values during the period 1925-1955 and the larger negative values between 1975-2005.  Why does the time series of tropical change in LCC in Fig. 6 look so different?     It looks almost like there is a 30 year oscillation in the tropical LCC.

\item How much do the differences in the surface temperature data matter?  How much do differences over land matter?

\item Should we incorporate the vertical velocity into the paper?

\item What is the relationship between these results and the 5 typical strato-cumulus regions that are often studied?

\item According to Xu et al. 2014, GFDL-CM2.0, GFDL-CM2.1, GFDL-CM3, GFDL-ESM2G, and GFDL-ESM2M (H,I,f,g,h) all use cloud-top radiative cooling to drive boundary layer turbulence.  Is this also the case for AM4?  They list all three as having a 'K profile' PBL scheme type and a Prognostic cloud scheme type.

\end{enumerate}
This study does not address the known spread of LCC change due to differing sensitivities of models to changing SST.  Because all three of our models are driven with observed SST the different responses are due to differences of the atmospheric response to the boundary conditions (to what extent is the large-scale circulation tied to the SST?).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Optional Glossary or Notation section, goes here
%
%%%%%%%%%%%%%%
% Glossary is only allowed in Reviews of Geophysics
% \section*{Glossary}
% \paragraph{Term}
% Term Definition here
%
%%%%%%%%%%%%%%
% Notation -- End each entry with a period.
% \begin{notation}
% Term & definition.\\
% Second term & second definition.\\
% \end{notation}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS

%\begin{acknowledgments}
%(Text here)
%\end{acknowledgments}

%% ------------------------------------------------------------------------ %%
%%  REFERENCE LIST AND TEXT CITATIONS
%
% Either type in your references using
% \begin{thebibliography}{}
% \bibitem{}
% Text
% \end{thebibliography}
%
% Or,
%
% If you use BiBTeX for your references, please use the agufull08.bst file (available at % ftp://ftp.agu.org/journals/latex/journals/Manuscript-Preparation/) to produce your .bbl
% file and copy the contents into your paper here.
%
% Follow these steps:
% 1. Run LaTeX on your LaTeX file.
%
% 2. Make sure the bibliography style appears as \bibliographystyle{agufull08}. Run BiBTeX on your LaTeX
% file.
%
% 3. Open the new .bbl file containing the reference list and
%   copy all the contents into your LaTeX file here.
%
% 4. Comment out the old \bibliographystyle and \bibliography commands.
%
% 5. Run LaTeX on your new file before submitting.
%
% AGU does not want a .bib or a .bbl file. Please copy in the contents of your .bbl file here.

%\begin{thebibliography}{}

%\providecommand{\natexlab}[1]{#1}
%\expandafter\ifx\csname urlstyle\endcsname\relax
%  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
%  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
%  \urlstyle{rm}\Url}\fi
%
%\bibitem[{\textit{Atkinson and Sloan}(1991)}]{AtkinsonSloan}
%Atkinson, K., and I.~Sloan (1991), The numerical solution of first-kind
%  logarithmic-kernel integral equations on smooth open arcs, \textit{Math.
%  Comp.}, \textit{56}(193), 119--139.
%
%\bibitem[{\textit{Colton and Kress}(1983)}]{ColtonKress1}
%Colton, D., and R.~Kress (1983), \textit{Integral Equation Methods in
%  Scattering Theory}, John Wiley, New York.
%
%\bibitem[{\textit{Hsiao et~al.}(1991)\textit{Hsiao, Stephan, and
%  Wendland}}]{StephanHsiao}
%Hsiao, G.~C., E.~P. Stephan, and W.~L. Wendland (1991), On the {D}irichlet
%  problem in elasticity for a domain exterior to an arc, \textit{J. Comput.
%  Appl. Math.}, \textit{34}(1), 1--19.
%
%\bibitem[{\textit{Lu and Ando}(2012)}]{LuAndo}
%Lu, P., and M.~Ando (2012), Difference of scattering geometrical optics
%  components and line integrals of currents in modified edge representation,
%  \textit{Radio Sci.}, \textit{47},  RS3007, \doi{10.1029/2011RS004899}.

%\end{thebibliography}

%Reference citation examples:

%...as shown by \textit{Kilby} [2008].
%...as shown by {\textit  {Lewin}} [1976], {\textit  {Carson}} [1986], {\textit  {Bartholdy and Billi}} [2002], and {\textit  {Rinaldi}} [2003].
%...has been shown [\textit{Kilby et al.}, 2008].
%...has been shown [{\textit  {Lewin}}, 1976; {\textit  {Carson}}, 1986; {\textit  {Bartholdy and Billi}}, 2002; {\textit  {Rinaldi}}, 2003].
%...has been shown [e.g., {\textit  {Lewin}}, 1976; {\textit  {Carson}}, 1986; {\textit  {Bartholdy and Billi}}, 2002; {\textit  {Rinaldi}}, 2003].

%...as shown by \citet{jskilby}.
%...as shown by \citet{lewin76}, \citet{carson86}, \citet{bartoldy02}, and \citet{rinaldi03}.
%...has been shown \citep{jskilbye}.
%...has been shown \citep{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown \citep [e.g.,][]{lewin76,carson86,bartoldy02,rinaldi03}.
%
% Please use ONLY \citet and \citep for reference citations.
% DO NOT use other cite commands (e.g., \cite, \citeyear, \nocite, \citealp, etc.).

%% ------------------------------------------------------------------------ %%
%
%  END ARTICLE
%
%% ------------------------------------------------------------------------ %%
\end{article}
%
%
%% Enter Figures and Tables here:

\begin{table}
    \caption{Coefficient terms (Eq. \ref{eqLCC}) in the decomposition of $\Delta \rm{LCC}$ for AM2.1, AM3, AM4p0, and CAM5.3.  Also shown are the correlation coefficients between the GFDL models and the decomposition from Zhou et al. 2016, and between each model and the $\Delta \rm{LCC}$ simulated for that model.  All values are computed as tropical means ($\pm 30^{\circ}$).}
    \begin{center}
    %\begin{tabular}{| l | l | l | l | p{5cm} |}
    %\begin{tabular}{l*{3}{c}r}
    \begin{tabular}{*{5}{c}}
    \hline
    %\multicolumn{5}{|c|}{Experimental Specifications} \\
    \hline
    Model      & $\gamma$                                      & $\delta$    &     Zhou et al.  CC       & $\Delta \rm{LCC}$ CC         \\ \hline
    AM2.1           &   4.7  &    -0.1            &  0.59    & 0.88                                          \\
    \\
 %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
    AM3                & 5.6   &  -0.5           &   0.59   & 0.77                                          \\ 
    \\
 %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
    AM4p0              & 3.5 &  -0.3          & 0.70    &   0.70                                                     \\ 
    \\
  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
    CAM5.3               & 3.7 &  -0.9     & 1       &    ??                                                     \\ 
    \\
   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
     \end{tabular}\par
     \label{LCCtable}
\end{center}
\end{table}
%
%
% DO NOT USE \psfrag or \subfigure commands.
%
% Figure captions go below the figure.
% Table titles go above tables; all other caption information
%  should be placed in footnotes below the table.
%
%----------------
% EXAMPLE FIGURE
%
 %\begin{figure}
 %\noindent\includegraphics[width=20pc]{samplefigure.eps}
 %\caption{Caption text here}
 %\label{figure_label}
 %\end{figure}
%

%\begin{figure}
 % \includegraphics[width=6.0in]{figures/alpha_ts_am4am3am2_longamip_30yrwind_phat.pdf}
%  \caption{Time evolution of the global mean feedback parameter ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).  
%  Time series have been computed by linear regression of the global, yearly mean TOA net radiative imbalance and the surface 
%  temperature over a sliding 30 window.}
%\end{figure}

\begin{figure}
 % \includegraphics[width=6.0in]{figures/alpha_2panel_ts_am4am3am2_longamip_30yrwind_allensmbrs.eps}
  \includegraphics[width=6.0in]{figures/alpha_ts_am4am3am2_longamip_30yrwind_mostensmbrs.eps}
  \caption{Upper panel: Time evolution of the global mean feedback parameter ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).  
  Time series have been computed by linear regression of the global, yearly mean TOA net radiative imbalance and the surface 
  temperature over a sliding 30 window.  Lower panel: Time evolution of the global mean Cloud Radiative Effect ($\rm{W/m^2 K}$) for 
  AM4g10r8(black), AM3(red), and AM2.1(blue).}
  \label{fig:alphacre}
\end{figure}

%\begin{figure}
%  \includegraphics[width=6.0in]{figures/alpha_cre_ts_am4am3am2_longamip_30yrwind_phat.pdf}
%  \caption{Time evolution of the global mean Cloud Radiative Effect ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).}
%\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/eistrend_ts_am432_longamip_tr_bold_30yrwind_new.pdf}
  \caption{Time evolution of the global mean Estimated Inversion Strength ($\rm{K/30 yr}$) for AM4g10r8(black), AM3(red), and    
                AM2.1(blue).  Global mean shown as thin solid lines and tropical mean values as thick solid lines.}
  \label{fig:eis}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/lcceis_late.eps}
  \caption{Trends of the low-cloud cover (left) and estimated inversion strength (right) during the period 1975-2005 for AM4 (top), AM3 (middle), and AM2(bottom).  Trends were computed with linear regression at each grid point for the variable of interest.}
  \label{fig:lcceis_late}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/lcceis_early.eps}
  \caption{As in previous figure but for the period 1925-1955.}
  \label{fig:lcceis_early}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/delLCC_AM2AM3AM4_pm30.eps}
  \caption{Time evolution of the tropical mean ($\pm 30^{\circ}$) change in low-cloud cover ($\Delta \rm{LCC}$) for AM2.1(blue), AM3(red), AM4p0(black).  Thick lines show the       simulated $\Delta \rm{LCC}$ while thin lines show $\Delta \rm{LCC}$ approximated using Eq. \ref{eqLCC} with coefficients determined by multiple linear regression (see Table \ref{LCCtable}).  A nine-year running mean has been used to smooth the data series.}
  \label{fig:lccts}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/hccomega_late.eps}
  \caption{Trends of the high-cloud cover (left) and vertical velocity (omega) on the 500 hPa level (right) during the period 1975-2005 for 
                AM4 (top), AM3 (middle), and AM2(bottom).  Trends were computed with linear regression at each grid point for the variable of 
                interest.}
  \label{fig:hccomega_late}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/hccomega_early.eps}
  \caption{As in previous figure but for the period 1925-1955.}
  \label{fig:hccomega_late}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/tref_t700_am4am3am2_late.eps}
  \caption{Trends of the Tref (left) and temperature on the 700hPa level (right) during the period 1975-2005 for AM4 (top), AM3 (middle), and AM2(bottom).  Trends were computed with linear regression at each grid point for the variable of interest.}
  \label{fig:tref_t700_late}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/tref_t700_am4am3am2_early.eps}
  \caption{As in previous figure but for the period 1925-1955.}
  \label{fig:tref_t700_early}
\end{figure}

\begin{figure}
  %\includegraphics[width=6.0in]{figures/am4g10r8_eis_t700_tsurf_trend_endtime1620.eps}
  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am4late.pdf}
  \caption{Trends during the period 1975-2005 for AM4g10r8.  Trends were computed with linear regression at each grid point for the variable of interest.}
  \label{fig:lcceisapp_am4}
\end{figure}

\begin{figure}
  %\includegraphics[width=6.0in]{figures/am3p9_eis_t700.pdf}
  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am3late.pdf}
  \caption{Trends during the period 1975-2005 for AM3.  Trends were computed with linear regression at each grid point for the variable of interest.}
  \label{fig:lcceisapp_am3}
\end{figure}

\begin{figure}
  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am2late.pdf}
  \caption{Trends during the period 1975-2005 for AM2.  Trends were computed with linear regression at each grid point for the variable of interest.}
  \label{fig:lcceisapp_am2}
\end{figure}

%\begin{figure}
%  \includegraphics[width=6.0in]{figures/am4g10r8_ts_anom_zhouetal_fig2c_trop_glob}
%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
%  mean over full time series for AM4g10r8.  
%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
%\end{figure}
%%
%\begin{figure}
%  \includegraphics[width=6.0in]{figures/am3p9_ts_anom_zhouetalfig2c_glob_trop}
%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
%  mean over full time series for AM3.  
%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
%\end{figure}
%%
%\begin{figure}
%  \includegraphics[width=6.0in]{figures/am2_1_ts_anom_zhouetalfig2c_trop_gl}
%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
%  mean over full time series for AM2.1
%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
%\end{figure}
%
\begin{figure}
  \includegraphics[width=6.2in]{figures/glb_rad_trends_late.eps}
  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed between 1975 and 2005.}
\end{figure}

%\begin{figure}
%  \includegraphics[width=6.2in]{figures/glb_trend_am4am3am2_early.pdf}
%  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed over a 30 year period near the middle of the twentieth century.}
%\end{figure}

\begin{figure}
  \includegraphics[width=6.2in]{figures/glb_rad_trends_early.eps}
  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed between 1925 and 1955.}
\end{figure}

%\begin{figure}
%  \includegraphics[width=6.0in]{}
%  \caption{}
%\end{figure}

% ---------------
% EXAMPLE TABLE
%
%\begin{table}
%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
%\centering
%\begin{tabular}{l c}
%\hline
% Run  & Time (min)  \\
%\hline
%  $l1$  & 260   \\
%  $l2$  & 300   \\
%  $l3$  & 340   \\
%  $h1$  & 270   \\
%  $h2$  & 250   \\
%  $h3$  & 380   \\
%  $r1$  & 370   \\
%  $r2$  & 390   \\
%\hline
%\end{tabular}
%\tablenotetext{a}{Footnote text here.}
%\end{table}

% See below for how to make sideways figures or tables.

\end{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% IF YOU HAVE MULTI-LINE EQUATIONS, PLEASE
% BREAK THE EQUATIONS INTO TWO OR MORE LINES
% OF SINGLE COLUMN WIDTH (20 pc, 8.3 cm)
% using double backslashes (\\).

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

%% ------------------------------------------------------------------------ %%
%
%  SIDEWAYS FIGURE AND TABLE EXAMPLES
%
%% ------------------------------------------------------------------------ %%
%
% For tables and figures, add \usepackage{rotating} to the paper and add the rotating.sty file to the folder.
% AGU prefers the use of {sidewaystable} over {landscapetable} as it causes fewer problems.
%
% \begin{sidewaysfigure}
% \includegraphics[width=20pc]{samplefigure.eps}
% \caption{caption here}
% \label{label_here}
% \end{sidewaysfigure}
%
%
%
% \begin{sidewaystable}
% \caption{}
% \begin{tabular}
% Table layout here.
% \end{tabular}
% \end{sidewaystable}
%
%

### 2019-09-20 silvers_etal_grl_revisions_2017_sub.tex
committing a number of old tex files into the latex_git repo

%% 2/18/2016
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalSample.tex: this sample file is for articles formatted with LaTeX
%
% This sample file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements.
%
% PLEASE DO NOT USE YOUR OWN MACROS
% DO NOT USE \newcommand, \renewcommand, or \def.
%
% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
% DO NOT USE \psfrag or \subfigure commands.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Step 1: Set the \documentclass
%
% There are two options for article format:
%
% 1) PLEASE USE THE DRAFT OPTION TO SUBMIT YOUR PAPERS.
% The draft option produces double spaced output.
% 
% 2) numberline will give you line numbers.

% Tip:
%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

%% To submit your paper:
%\documentclass[linenumbers,draft]{agujournal}
\documentclass[linenumbers]{agujournal}

% Now, type in the journal name: \journalname{<Journal Name>}
% ie,
\journalname{Geophysical Research Letters}

%% Choose from this list of Journals:
%
% JGR-Atmospheres
% JGR-Biogeosciences
% JGR-Earth Surface
% JGR-Oceans
% JGR-Planets
% JGR-Solid Earth
% JGR-Space Physics
% Global Biochemical Cycles
% Geophysical Research Letters
% Paleoceanography
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resource Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science

\usepackage{pdflscape}

%% ------------------------------------------------------------------------ %%
%
%  ENTER Title Page commands:
%
%% ------------------------------------------------------------------------ %%

% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general terms then specific results are optimized in
% searches)

% Example: \title{This is a test title}

% (List authors by first name or initial followed by last name and
% separated by commas. Use \affil{} to number affiliations, and
% \thanks{} for author notes.  
% Additional author notes should be indicated with \thanks{} (for
% example, for current addresses).

% Example: \authors{A. B. Author\affil{1}\thanks{Current address, Antartica}, B. C. Author\affil{2,3}, and D. E.
% Author\affil{3,4}\thanks{Also funded by Monsanto.}}

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

%% Corresponding Author:
% Corresponding author mailing address and e-mail address:

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

% Authors are individuals who have significantly contributed to the
% research and preparation of the article. Group authors are allowed, if
% each author in the group is separately identified in an appendix.)

% \affiliation{1}{First Affiliation}
% \affiliation{2}{Second Affiliation}
% \affiliation{3}{Third Affiliation}
% \affiliation{4}{Fourth Affiliation}

%% Keypoints, final entry on title page.
% Example: 
% \begin{keypoints}
% \item	List up to three key points (at least one is required)
% \item	Key Points summarize the main points and conclusions of the article
% \item	Each must be 100 characters or less with no special
% characters or punctuation 
% \end{keypoints}

%% \begin{abstract} begins second page

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Track Changes:
% To add words, \added{<word added>}
% To delete words, \deleted{<word deleted>}
% To replace words, \replace{<word to be replaced>}{<replacement word>}
% To explain why change was made: \explain{<explanation>}

% At the end of the document, use \listofchanges, which will list the
% changes and the page and line number where the change was made.

% When final version, \listofchanges will not produce anything,
% \added{} word will be printed, \deleted{} will take away the word,
% \replaced{}{} will print only the 2nd argument.
% \explain will not print anything.

% Optional argument:
% You can also add additional information to be printed with the list
% of changes, to indicate the initials of the person changing the text,
% and the time and/or date of the change, or any other comment by using
% the optional [] argument:
% \added[AH, 3:30pm, Feb 18, 2016]{added term}
% will yield 
% [AH, 3:30pm, Feb 18, 2016] added term on page...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% ------------------------------------------------------------------------ %%
%
%  TITLE
%
%% ------------------------------------------------------------------------ %%

\title{The diversity of cloud responses to twentieth-century sea surface temperatures}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

\authors{Levi G. Silvers\affil{1}, David Paynter\affil{2}, and Ming Zhao\affil{2}}

% \authors{A. B. Smith\affil{1}\thanks{Current address, McMurdo Station,
% Antartica},
% Eric Brown\affil{1,2}, Rick Williams\affil{3},
% John B. McDougall\affil{4}, and S. Visconti\affil{5}\thanks{Also
% funded by Monsanto.}}

\affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
\affiliation{2}{GFDL/NOAA, Princeton, New Jersey, USA}

%\affiliation{1}{Department of Hydrology and Water Resources,
%University of Arizona, Tucson, Arizona, USA.}
%\affiliation{2}{Department of Geography, Ohio State University,
%Columbus, Ohio, USA.}
%\affiliation{3}{Department of Space Sciences, University of
%Michigan, Ann Arbor, Michigan, USA.}
%\affiliation{4}{Division of Hydrologic Sciences, Desert Research
%Institute, Reno, Nevada, USA.}
%\affiliation{5}{Dipartimento di Idraulica, Trasporti ed
%Infrastrutture Civili, Politecnico di Torino, Turin, Italy.}

%% Corresponding Author
%(include name and email addresses of the corresponding author.  More
%than one corresponding author is allowed in this Word file and for
%publication; but only one corresponding author is allowed in our
%editorial system.)

\correspondingauthor{L. G. Silvers}{silvers@princeton.edu}

%  List up to three key points (at least one is required)
%  Key Points summarize the main points and conclusions of the article
%  Each must be 100 characters or less with no special characters or punctuation

\begin{keypoints}
\item Three climate models driven by observed sea surface temperatures increase then decrease climate sensitivity over the twentieth century
\item Substantial changes of the climate feedback parameter are mirrored by the global mean low-level cloud anomalies
\item This variability is connected to atmospheric stability and not due to stratocumulus dominated regions, but to the broader tropics
\end{keypoints}

%% ------------------------------------------------------------------------ %%
%
%  ABSTRACT
%
%% ------------------------------------------------------------------------ %%

\begin{abstract}
Low-level clouds are shown to be the conduit between the observed sea surface temperatures (SST) 
and large decadal fluctuations of the top of the atmosphere (TOA) radiative imbalance.  The influence 
of low-level clouds on the climate feedback is shown for global mean time
series as well as particular geographic regions.  The changes of clouds are found to be 
important for a mid-century period of high sensitivity and a late century period of low 
sensitivity.  These conclusions are drawn from analysis of amip-piForcing simulations using three 
atmospheric general circulation models (AM2.1, AM3, and AM4.0).  All three models confirm the importance 
of the relationship between the global climate sensitivity and the eastern Pacific 
trends of SST and low-level clouds.  However, this work argues that the variability of the 
climate feedback parameter is not driven by stratocumulus dominated regions in the eastern ocean basins, 
but rather by the cloudy response in the rest of the tropics.
\end{abstract}

% +12 -3 -6

%% ------------------------------------------------------------------------ %%
%
%  TEXT
%
%% ------------------------------------------------------------------------ %%

%%% Suggested section heads:
% \section{Introduction}
% 
% The main text should start with an introduction. Except for short
% manuscripts (such as comments and replies), the text should be divided
% into sections, each with its own heading.

% Headings should be sentence fragments and do not begin with a
% lowercase letter or number. Examples of good headings are:

% \section{Materials and Methods}
% Here is text on Materials and Methods.

% \subsection{A descriptive heading about methods}
% More about Methods.
% 
% \section{Data} (Or section title might be a descriptive heading about data)
% 
% \section{Results} (Or section title might be a descriptive heading about the
% results)
% 
% \section{Conclusions}

\section{Introduction}
Determining how the atmosphere responds to anthropogenic forcing is complicated by the strong decadal variability which is present in the global mean TOA flux of energy ($N$  $\rm{W m^{-2}}$).  Over the historical period (\replaced{here meaning after}{post} 1870) these fluctuations of $N$ include \replaced{both natural and anthropogenic}{forced (natural and anthropogenic) and internal} variability.   One measure of the climate sensitivity is to regress $N$ under fixed radiative forcing versus the change of surface air temperature $T$ as the atmosphere adjusts to a radiative perturbation \citep{Gregory_etal_2004}.  The climate feedback parameter $\alpha$ ($\rm{W m^{-2} K^{-1}}$) is then given by the slope of the regression line.   This technique has been applied to climate models forced with historical SSTs and fixed radiative forcing to obtain an estimate of $\alpha$ over the historical period.   Previously examined models \citep{Gregory_Andrews_2016, Zhou_etal_2016}  (GA16 and Z16 hereafter, respectively) have shown a period of high (small $\alpha$) sensitivity (1925-1955) followed by a period of low (large $\alpha$) sensitivity (1975-2005) irrespective of their long term or equilibrated sensitivity.  It has been conjectured (Z16) that an increase of eastern Pacific low-level clouds played a significant role in the low sensitivity of the later period.  To our knowledge, the influence of clouds on the global energy budget during the high sensitivity early period has not been investigated.  This raises several questions.  What role do clouds over the rest of the globe play?  Was the period of high-sensitivity in the mid twentieth century similarly influenced by particular changes of cloud fields?  If so, what do these influences of clouds on the Earth's energy budget tell us about the cloud feedback that we should expect in \deleted{the} future climate\added{s}?

The impact of low-cloud cover on the radiation budget of Earth has been the source of active research for decades \citep[e.g.,][] {Randall_etal_1984, Klein_Hartmann_1993,Bony_etal_2004, Bony_Dufresne_2005}.   Recently \citet{Qu_etal_2014,Qu_etal_2015} provided a thorough examination of the dependencies between low-cloud cover, the estimated inversion strength (EIS), and surface temperature in both observations, and an ensemble of models from CMIP3 and CMIP5.  They, as did most previous studies \citep [e.g.,][]{Klein_Hartmann_1993,Wood_Bretherton_2006} focused on 5 oceanic regions which are important for stratocumulus decks of radiatively active low-level clouds.  Only recently have the fields of stability, low-level clouds, and low-level temperature begun to be investigated over larger swaths of the globe  \citep {Webb_etal_2015, Rose_Rayborn_2016, Grise_Medeiros_2016, Zhou_etal_2016}.

\replaced{The global energy budget of Earth is often considered in a mean, equilibrated context despite known fluctuations in $N$ (and $\alpha$) on monthly, yearly, and decadal scales (Figure 1a). The decadal variability of the energy budget is also present in the global mean cloud radiative effect (CRE; Figure 1b and Z16).}  
{A linearized forcing-feedback framework has often been used to study the global mean energy budget and asses $\alpha$ despite its known temporal variations %\citep[e.g.,][]{Gregory_etal_2004, Forster_Gregory_2006, Mauritsen_etal_2013}, GA16, Armour, 2017).  
[e.g., \textit{Gregory et al.}, 2004; \textit{Forster and Gregory}, 2006; \textit{Mauritsen et al.}, 2013, GA16, \textit{Armour}, 2017].
This decadal variability of the energy budget is reflected in $\alpha$ and, specifically, in the cloud radiative effect (CRE; Figure 1 a,c,e,f and Z16).}   A better understanding of the role played by clouds in determining $\alpha$ will be useful regardless of whether the changes are due to radiative forcings, natural variability, anthropogenic influences, or changes in the uptake of heat into the oceans \citep{Haugstad_etal_2017}.

This paper examines the atmospheric response to \replaced{changing}{prescribed} SST patterns in simulations of the years 1870-2005.  The use of three atmospheric general circulation models (AGCMs) developed at the Geophysical Fluid Dynamics Laboratory (GFDL;  AM2.1, AM3, and AM4.0) provides a comparison of models with significantly different treatments of the clouds.  
Interdecadal variability of the global feedback parameter has been previously studied \replaced{using the amip-piForcing experiments [GA16,Z16].  However,}{ [GA16, Z16] but} the regional differences between cloud fields during periods of differing sensitivity are still not clearly understood.
\replaced{The amip-piForcing}{These} experiment\added{s} preclude\deleted{s} an analysis of atmosphere-ocean feedback processes, or a direct prediction of how the climate would respond to forcing perturbations.  
However, \replaced{it}{we} utilizes the best estimate of observed SST and sea-ice concentrations \replaced{and}{to} facilitate an analysis of how \deleted{an} AGCM\added{s} respond\deleted{s} to these boundary conditions.
By identifying the \replaced{relationships between these variables and}{response of AGCMs to} key geographic regions of change we intend to move closer to a process level understanding of the connection between SST patterns, clouds, and the climate sensitivity.

%\clearpage

\section{Methods}

\subsection{Description of amip-PiForcing experiments, AM2.1, AM3, and AM4.0}

This work uses the amip-piForcing experiment to investigate the atmospheric response to surface forcing between the years 1870 and 2005.  
The experiment drives AGCMs with observationally based SST and sea-ice concentrations while the forcing due to greenhouse gases, aerosol, and solar forcing, is held constant at assumed pre-industrial levels.  However, due to the different time at which these models \replaced{where}{were} actively used \replaced{there are small differences in the boundary conditions}{the SST and sea-ice fields differed slightly among models}.  
The amip-piForcing experiment \added{develops some of the ideas from \citet{Andrews_2014} and} is one of the CFMIP3 experiments, for additional details and examples see \citet{Webb_etal_2017}, GA16 and Z16.  
For each of the three AGCMs five ensemble members have been used.

\replaced{One of the largest differences among the three GFDL atmospheric models analyzed in this paper is that they each have unique representations of convective clouds.  
The AM4.0 and AM3 models include an aerosol indirect effect with a prognostic cloud drop number.  The AM2.1 model specified the cloud drop number to be 100 (300) 
over ocean (land).  Further documentation of the earlier two GFDL AGCMS can be found in \mbox{\citet{GFDL_GAMDT_2004}} (AM2.1) and \mbox{\citet{Donner_etal_2011}} (AM3).   
Documentation of the AM4.0 model is in the review stage and will be published as \mbox{\textit{Zhao et al.} [2017 a,b].}}{Cumulus cloud parameterizations are one of the largest differences among the GFDL atmospheric models analyzed here.   The AM2.1 model uses the Relaxed-Arakawa-Schubert 
\mbox{\citep{Moorthi_Suarez_1992}} scheme, AM3 uses the Donner-Deep scheme for deep convection \mbox{\citep{Donner_1993}} and the University of Washington scheme (UWShCu, 
\mbox{\citep{Bretherton_etal_2004}}) for shallow convection.  AM4.0 uses a version of the UWShCu scheme that has been modified to include two bulk plumes which account for shallow 
and deep convection.  Documentation of the GFDL AGCMS can be found in \mbox{\citet{GFDL_GAMDT_2004}}, \mbox{\citet{Donner_etal_2011}}, and \mbox{\textit{Zhao et al.} [2017 a,b; submitted]}.}   
Some of the details of the convection scheme in AM4.0 
are given in \citet{Zhao_etal_2016}, and a study looking at the influence of CREs on the intertropical convergence zone with a recent prototype AM4 in aquaplanet mode 
are described in \citet{Popp_Silvers_2017}.

\subsection{Methodology of Analysis}

\begin{figure}
   \includegraphics[width=6.5in]{../figures/alpha_tseries_6pan.pdf}
  \caption{Time series analysis of AM4.0(black), AM3(green), and AM2.1(blue).  Thick lines are ensemble means, shading gives range of ensemble members.  A) Global climate feedback parameter $\alpha$ ($\rm{W/m^2 K}$),  
  B) Same as  A) but with contributions from 4 tropical windows (small-dashed) and the rest of tropics (long-dashed),  C)  $\alpha$ ($\rm{W/m^2 K}$) decomposed into the CRE (lower) and CLR (upper) components,   D)  Global mean Low-Cloud Cover parameter $R_{LCC}$ ($\rm{\% /K}$).  Global $\alpha_{CRE}$ ($\rm{W/m^2 K}$) is decomposed into the short-wave CRE (E) and the long-wave CRE (F).   All time series computed by regression against global, yearly mean surface temperature change.}
  \label{fig:alphacre}
\end{figure}

We are interested in the influence of clouds on the decadal variability of the TOA net global mean radiative flux ($N$).  As in GA16 the global mean energy budget is given by $N=F-\alpha T$, where we have assumed that $R = \alpha T$ and $\alpha$ is the climate feedback parameter.  Our interest is in the covariation of $R$ (global mean \replaced{top of the atmosphere}{TOA} radiative flux change due to some perturbation to the climate) and $T$ (global mean surface air temperature change) rather than the change relative to a control state.  
Smaller values of $\alpha$ require a larger $T$ to balance the imposed perturbation to the system.  
We compute the climate feedback parameter in the same was as in GA16 (their differential climate feedback parameter $\tilde{\alpha}$).  That is, linear regression is used to compute the relationship between $R$ and $T$, given by $\alpha$.  The regression is applied to the global yearly mean values over moving 30\added{-year} windows.  
In the same way we have computed the covariation of the CRE, \added{short-wave (SW) CRE, long-wave (LW) CRE, and the clear-sky fluxes} with $T$, as well as the anomalous global low-cloud cover (LCC; \added{clouds below 680 hPa}) with $T$ ($\alpha_{CRE}$, \added{$\alpha_{SW CRE}$, $\alpha_{LW CRE}$, $\alpha_{CLR}$} and \replaced{\mbox{$\alpha_{LCC}$}}{\mbox{$R_{LCC}$}}, respectively \added{; $R$ denoting regression method}).             
These time series \deleted{of $\alpha$, $\alpha_{CRE}$, and 
$R_{LCC}$} are shown in Figure 
\ref{fig:alphacre} with each point representing the mid-point of a 30 year window.  
We emphasize that the terminology `climate sensitivity' and `climate feedback parameter' here simply refer to measures of the change of radiative balance at TOA with fixed radiative forcing and prescribed SST.  
This \added{method of computing climate sensitivity} is in keeping with previous studies [{\textit{Cess et al.}}, 1989; {\textit{Silvers et al.}}, 2016; GA16] and we assume there is useful \replaced{overlap}{correspondence} between the interaction of clouds and the TOA energy budget found here and in a fully coupled Earth system.  
For amip-piForcing experiments, $F=0$, and the `effective' climate sensitivity can be inferred as $F_{2\times} / \alpha$ where $F_{2\times}$ is an appropriate representative value of radiative forcing due to doubled (relative to pre-industrial) $\rm{CO}_2$ concentrations (we use $F_{2\times}=3.4 \rm{W m}^{-2}$  \citep{Flato_etal_2013}).  This is distinct from the equilibrium climate sensitivity (ECS), defined as the equilibrium response to doubled $\rm{CO}_2$ concentrations.

The strong connection between global clouds and $\alpha$ is shown in Figure \ref{fig:alphacre}.  \replaced{Accordingly, we compute trends at each grid point for LCC, EIS, and SST.  
To compute these spatial patterns of change linear regression was used at each grid point.  The figures focus on ocean regions because it is primarily there that low stratiform clouds are found.}{To investigate the spatial patterns of this connection, we use linear regression to compute trends over time at each grid point for SST, SW CRE, LW CRE, LCC, and EIS (Figs. \ref{fig:am4tsfc}, \ref{fig:trends_lcceis_ts}a).  
Global figures focus on ocean regions because it is primarily there that low stratiform clouds are found.
}

Previous studies have shown lower-tropospheric stability (LTS \deleted{or EIS}) to be a useful diagnostic tool that connects low-cloud changes to the characteristics of the large-scale environment, especially within traditionally defined stratocumulus regions \citep{Klein_Hartmann_1993,Wood_Bretherton_2006, Medeiros_etal_2008, Webb_etal_2015}.               
We analyze the EIS, which can be thought of as a correction to the LTS based on the moist adiabatic profile.  The LTS used by \citet{Klein_Hartmann_1993} was defined as $\rm{LTS}=\theta_{700 hPa}-\theta_{sfc}$ where $\theta$ is the potential temperature and the subscript indicates the level at which the values are taken.   
For EIS we use 
the approximation made by \citet{Wood_Bretherton_2006}:
\begin{equation}
    \rm{EIS} = \rm{LTS} - \Gamma^{850}_m (z_{700}-\rm{LCL})
\end{equation}
Utilizing the moist adiabat ($\Gamma_m^{850}$), height on the 700 hPa surface ($\rm{z_{700}}$), and the lifting condensation level (LCL).  
  Further details of the boundary conditions, parameterizations, and EIS computation are given in the supporting material (SM).

\section{Results}
\subsection{Contrasting time periods of global feedback}

\begin{figure}
  \includegraphics[width=5.in]{../figures/Fig2_tsfc_radflux_6pan_landmask_clon200.pdf}
  \caption{Top row, trends of observationally derived SST values during periods of high and low sensitivity.  To highlight the pattern the mean trend for each period was subtracted.
Middle row, trends of simulated (AM4.0) shortwave (SW) CRE; Bottom row, longwave (LW) CRE.  Left (right) column shows trends between 1925-1955 (1975-2005).  SST fields are from AMIP boundary conditions, PCMDI-AMIP, \citet{Taylor_etal_2000}.  Black boxes in top right panel show window regions discussed in text.}
  \label{fig:am4tsfc}
\end{figure}

\deleted{Fluctuations of the climate feedback indicate changes in the TOA radiative imbalance for a given amount of warming that a system undergoes.}  
\replaced{The evolution of \mbox{$-\alpha$} over the historical period (1870-2005) is shown in Figs. 1a,b}{Strong decadal variability of \mbox{$-\alpha$} 
and global low-cloud cover (\mbox{$R_{LCC}$}) is shown in Figure 1}.  
The thick lines indicate ensemble mean values for the three different AGCMs, shading indicates the range of ensemble members.  Immediately apparent is the period with high sensitivity (small $\alpha$) centered around approximately 1940.  After this the sensitivity of all three models steadily decreases for the remainder of the simulations.  This decadal variability is mirrored in the evolution of \deleted{the CRE ($\alpha_{CRE}$, Fig. 1c),} \added{$\alpha_{CRE}$, $\alpha_{SW CRE}$, and $R_{LCC}$} (Fig. 1c,d,e), while the corresponding time series of clear sky fluxes and $\alpha_{LW CRE}$ remain largely constant (Fig. 1c,f), indicating that the the global energy budget is tightly coupled to fluctuations of the total cloud field.   
The time series of \replaced{$\alpha_{LCC}$}{$R_{LCC}$} in Fig. 1.d shows that the evolution of global mean LCC anomalies closely tracks with the feedback parameter.  This is surprising because we expected radiative effects from high clouds to \replaced{also}{have a larger} influence on $\alpha$, and while the importance of tropical low-level clouds to the uncertainty of climate sensitivity has been demonstrated (Bony and Dufresne, 2005), the contribution of \added {global mean} low-level clouds to the temporal variability of $\alpha$ has been less clear.  
To quantify the influence of regional changes in LCC on the TOA radiative budget the \replaced{long-wave CRE(LWCRE)}{LW CRE} and \replaced{short-wave CRE(SWCRE)}{SW CRE} trends are computed over the two periods of 
\replaced{interest.  Global trends for AM4.0 are shown in Figure \ref{fig:am4tsfc}}{interest (Figure \ref{fig:am4tsfc})}.   \replaced{To identify which regions of the globe are contributing to the variability of $\alpha$ we decompose $\alpha$ into contributions from particular windows.}{To explore contributions from key geographic regions $\alpha$ is spatially decomposed into windows.}

\replaced{The window locations were chosen to represent regions of importance highlighted by our results and previous literature.   To investigate the eastern Pacific region discussed in Z16 we expand the Peruvian and Californian windows from \mbox{\citet{Klein_Hartmann_1993}}.   The Indian, south Atlantic, and southern ocean windows were chosen because of the large trends in LCC there (Fig. \ref{fig:trends_lcceis_ts}; A map showing window locations is given in Fig. 2 of SM.)}{Locations of the windows were chosen to represent regions of importance for stratocumulus between $\pm 30^{\circ}$ based on observations (\citet{Wood_2012}, his Fig. 4.a) and our results (Fig. \ref{fig:trends_lcceis_ts}).  The windows used for this analysis are shown in Figs. \ref{fig:am4tsfc} and \ref{fig:trends_lcceis_ts}.}
\explain{shifted down a few lines}
\deleted{Mean LCC, SWCRE, and EIS in each window over both time periods are tabulated in Table 1 of SM.  Large changes in LCC, SWCRE, and EIS are seen between the early and late periods in Figs. \ref{fig:am4tsfc} and \ref{fig:trends_lcceis_ts}.   From the early to late period the 30-year trends in the eastern Pacific increased by 2.8\%(LCC), decreased by 3.3 $\rm{W m}^{-2}$ (SWCRE), and increased by 0.2 K (EIS).  The other windows show equal or larger changes.   Trends in the south Indian window showed LCC increased by 3.8\%, SWCRE decreased by 6.7 $\rm{W m}^{-2}$, and EIS increased by 0.5 K.}  
\replaced{Decomposing $\alpha$ into regions shows that the variability of $\alpha$ is almost entirely due to the tropical latitudes between $\pm 30^{\circ}$ (thin solid lines, Fig. 1.b).}  
{The feedback parameter has been computed over particular regions ($i$) using
\begin{equation}
   \overline{T}\alpha_{i} = \frac{\int N dA_i}{\int dA} =N_{i}w_i
\end{equation}
with  each $\alpha_i$ computed using linear regression of $N_{i}w_i$ on $\overline{T}$ with a sliding 30-year window and $w_i$ representing the relative area of each window.
For the regions examined during this study $\sum_{i}\alpha_{i}\approx \alpha$ and the variability of $\alpha$ is shown to be almost entirely due to the tropics ($\pm 30^{\circ}$; Fig. 1.b, long-dashed lines).}
Further, tropical regions typically dominated by stratocumulus do not contribute to the variability (Fig. 1.b; \replaced{dotted}{small-dashed} lines equal sum of $\alpha$ over windows shown in Figs \ref{fig:am4tsfc},\ref{fig:trends_lcceis_ts}).  
\deleted{There is also a substantial contribution to the magnitude of $\alpha$ by the latitudes poleward of 30 degrees (not shown).}
\explain{This is not critical, and manuscript needs to be shortened.}

Because there is such a contrast between the `early' period (1925-1955) and the `late' period (1975-2005) in the time series shown in Figure 1 we focus on a comparison between the atmospheric responses to the changing SSTs during these periods.  Between 1925 and 1955 the average global feedback parameter for AM4.0, AM3, and AM2.1 changes from values of (-1.6, -1.0, and -1.8 \, $\rm{W m}^{-2} K^{-1}$) to (-2.7, -2.4, and -2.3 $\rm{W m}^{-2} K^{-1}$) between 1975 and 1989.  
This represents a dramatic change in $\alpha$ and determining the cause will be an important part of our ability to understand how clouds respond to SST patterns and thus influence the global energy budget on decadal time scales.  \added{Mean LCC, SWCRE, and EIS in each window over both time periods are tabulated in Table 1 of SM.  From the early to late period the 30-year trends in the eastern Pacific increased by 2.8\%(LCC), decreased by 3.3 $\rm{W m}^{-2}$ (SWCRE), and increased by 0.2 K (EIS).  The other windows show equal or larger changes.   Trends in the south Indian window showed LCC increased by 3.8\%, SWCRE decreased by 6.7 $\rm{W m}^{-2}$, and EIS increased by 0.5 K.}

Changing SST patterns are the primary atmospheric driver in these experiments.
Anomalous patterns of SST change over each period (trends minus mean trend over that period) are shown in Figure \ref{fig:am4tsfc}.  The later period (1975-2005) is characterized by an east-west dipole in the Pacific ocean.  
As highlighted by Z16, this leads to an increase of LCC in the eastern regions and decreasing cloud feedback.  In contrast, the earlier period SST trend is characterized by negative tropical anomalies and positive anomalies in the higher latitudes.  
We find that the particular response of the low-level clouds to SST patterns differs dramatically between the two periods.  In the early period, the midlatitudes are marked by strongly decreasing low-level cloud.  In the late period the southern hemisphere oceans are almost entirely covered by increasing amounts of low-level cloud (Fig. 3).   
As discussed in the next two sections, there is a clear connection between these SST patterns\added{,} \deleted{and} the LCC\added{,} and EIS fields.

\subsection{Dependence of LCC on EIS and SST}

The known importance of low-level clouds in the global response to climatic perturbations and the importance of SSTs to the low-level cloud fields motivate us to look at how the LCC evolves during the historical period.  We create the anomaly time series, $\Delta \rm{LCC}$, $\Delta \rm{EIS}$, and $\Delta \rm{SST}$ by spatially averaging over the region of interest, removing the climatological time mean, and computing yearly mean values for each variable. 
To probe the dependence of LCC on low-level stability multiple linear regression is used to decompose $\Delta \rm{LCC}$ into a linear combination of $\Delta \rm{EIS}$ and $\Delta \rm{SST}$.  The anomalous changes of tropical marine LCC were shown [\textit{Qu et al.}, 2014; Z16] to be well explained by a linear combination of the change in EIS and SST.  
The coefficients $\gamma$ and $\beta$ can thus be determined for particular experiments or models in the following assumed relationship:

    \begin{equation} 
    \Delta \rm{LCC} \approx \gamma \Delta \rm{EIS} + \beta \Delta \rm{SST}.
    \label{eqLCC}
    \end{equation}

\begin{figure}
    %\includegraphics[width=6.0in]{../figures/Fig3_LCC_EIS_ts_pm60_legend.eps}
    \includegraphics[width=6.0in]{../figures/Fig3_LCC_EIS_ts_pm60.pdf}
    \caption{a) Trends of simulated low-cloud cover (first and second rows) and estimated inversion strength (third and fourth rows).  Rows 1 and 3 show trends between 1925-1955, rows 2 and 4 show trends between 1975-2005.  Column 1,2, and 3 show AM2.1, AM3, and AM4.0, respectively.   b) Mean ($\pm 60^{\circ}$, 9-year running mean) time evolution of low-cloud cover ($\Delta \rm{LCC}$) for AM2.1(blue), AM3(green), AM4.0(black).  Thick lines show simulated $\Delta \rm{LCC}$, thin lines show $\Delta \rm{LCC}$ approximated using Eq. \ref{eqLCC} with coefficients determined by multiple linear regression (SM Table 2).  Dashed lines show $\beta\Delta \rm{SST}$ term.  Black boxes show window regions discussed in text.}
  \label{fig:trends_lcceis_ts}
\end{figure}

\replaced{Values of $\gamma$ and $\beta$ for each of the three AGCMs are given in Table 2 of SM.   Time-series of the mean ($\pm 60^{\circ}$) values of anomalous low cloud cover $\Delta \rm{LCC}$ are shown in Fig. \ref{fig:trends_lcceis_ts}b, time series computed for the ($\pm 30^{\circ}$) are shown in SM Fig. 4.  Thick lines show the ensemble mean $\Delta \rm{LCC}$  values for each of the three AGCMs, thin lines show the $\Delta \rm{LCC}$ computed with equation \ref{eqLCC}, and dotted lines show $\beta \Delta \rm{SST}$.
Based on high correlations between $\Delta \rm{LCC}$ and the linear combination of $\Delta \rm{EIS}$ and $\Delta \rm{SST}$ the above relationship is an excellent approximation.  
The relative contributions of EIS and SST to the low-cloud cover is model dependent.}
{Between $\pm 30^{\circ}$, $(\gamma, \beta)=
(4,7,-0.13; \rm{AM}2.1),(5.6,-0.53; \rm{AM}3)$, and $(4.8,-0.39; \rm{AM}4.0)$ indicating a model dependent relative contribution from EIS and SST to LCC.  Time series of the mean values of anomalous low cloud cover $\Delta \rm{LCC}$ are shown in Fig. \ref{fig:trends_lcceis_ts}b ($\pm 60^{\circ}$) and SM Fig. 3 ($\pm 30^{\circ}$).  Thick lines show the $\Delta \rm{LCC}$  values for each of the three AGCMs, thin lines show the $\Delta \rm{LCC}$ computed with equation \ref{eqLCC}, and \replaced{dotted}{dashed} lines show $\beta \Delta \rm{SST}$.
High correlations between $\Delta \rm{LCC}$ and the linear combination of $\Delta \rm{EIS}$ and $\Delta \rm{SST}$ indicate the above relationship is an excellent approximation.}  
\explain{This paragraph was edited to incorporate details from the SM.}
Because the three models examined here all use prescribed SSTs, this difference likely indicates differences in the relative importance of the EIS fields which are in turn driven by the mid-tropospheric temperature, in this case the temperature \replaced{on the $700 \rm{hPa}$ surface}{at $700 \rm{hPa}$}.  
\explain{unnecessary, and not exactly clear information}
\deleted{The connection between the temperature field at particular levels with parameterization schemes (convection, turbulence) provides a useful link between details of the parameterizations and the LCC field. }   
\explain{moved to end of next paragraph}
\deleted{The successful reconstruction of the mean $\Delta \rm{LCC}$ both in the tropics and between $\pm 60$, as well as the close mirroring between the global fields of LCC and EIS trends (Fig. \ref{fig:trends_lcceis_ts}) indicate how closely tied to the SST pattern the LCC and EIS are.}

Several noteworthy points can be drawn from Figure \ref{fig:trends_lcceis_ts} and SM Table 2.  Increasing EIS leads to increasing LCC but increasing SST leads to decreasing LCC.  
\replaced{As shown by the correlation coefficients in SM Table 2 the particular decomposition used by Z16 to explain the variance in the change of the low-cloud cover is not directly applicable to other models but is specific to CAM5.3.}{The linear decomposition works well for all three GFDL models and CAM5.3, but with differing degrees of dependence among the models on the $\Delta \rm{SST}$ and $\Delta \rm{EIS}$ terms.}     The \replaced{remarkably}{relatively} flat $\beta \Delta \rm{SST}$ time series in Figure \ref{fig:trends_lcceis_ts} indicate that when the midlatitudes are included,  the anomalies of EIS become dominant over the anomalies of SST in determining the changes of LCC.   The precipitous drop of anomolous LCC (Fig. \ref{fig:trends_lcceis_ts} b) corresponds well to the minimum of \replaced{$\alpha_{LCC}$}{$R_{LCC}$} and maxima in $\alpha_{CRE}$ and $\alpha$ around 1940 (Fig. 1).  
\added{The successful reconstruction of the mean $\Delta \rm{LCC}$ in the tropics and between $\pm 60$, as well as the close mirroring between the fields of LCC and EIS trends (Fig. \ref{fig:trends_lcceis_ts}) indicate how closely tied to the SST pattern the LCC and EIS are.}

\subsection{Response of clouds to EIS and SST patterns}

The known connections between LCC and SST \citep{Qu_etal_2014, Zhou_etal_2016, Myers_Norris_2016} combined with the strong linear dependence of LCC anomalies on the EIS field shown in the previous subsection encourage examination of the global trends of LCC and EIS.   
A strong relationship between LCC and EIS in many regions of the globe is seen (Fig. \ref{fig:trends_lcceis_ts}) with the \replaced{thirty}{30}-year trends of LCC and EIS between the late (1975-2005) and early (1925-1955) periods. 
The response of LCC and EIS to the SST patterns is largely consistent among the three models.   Both time periods have an increase of EIS and LCC in the equatorial eastern Pacific ocean.   During the early period the LCC decreases in much of the Southern Hemispheric oceans and northern midlatitudes.
During the later period there is an increase of LCC throughout much of the Southern Hemispheric oceans and a decrease of LCC in the north Atlantic and northwest Pacific.    This is consistent with a \replaced{positive cloud feedback}{positive CRE} (large climate sensitivity) during the early period and a \replaced{small cloud feedback}{negative CRE} (low climate sensitivity) during the later period (Fig. \ref{fig:alphacre}).  Also prominent is the strong Atlantic basin correspondence between LCC and EIS trends during both periods, and the strong shift in the Atlantic from broadly negative trends in the early period to an inter-hemispheric dipole in the late period.  These patterns of LCC modeled during the late period match fairly well with trends of total cloud cover obtained from bias corrected ISCCP observations (SM Fig. 3).

The trends of LCC (Fig. \ref{fig:trends_lcceis_ts}, 1st and 2nd rows) closely mirror the trends of EIS (Fig. \ref{fig:trends_lcceis_ts}, 3rd and 4th rows) and are related to the SST patterns during both periods.  In particular, increasing EIS and LCC occur in regions of decreasing SST (north- and south-eastern Pacific, the Indian ocean, the southern Atlantic, and the southern Ocean).  This relationship has been thoroughly discussed in the literature in the context of stratocumulus regions and subsiding circulations \citep [e.g.,][]{Klein_Hartmann_1993, Wood_Bretherton_2006, Myers_Norris_2013, Qu_etal_2014, Qu_etal_2015}.  Figure \ref{fig:trends_lcceis_ts} shows the relationship to also be important across much of the world ocean.   For example, in the early period we see the dominant changes of LCC to be influenced by decreases of EIS over regions with increased SST.  There is a clear connection between EIS, SST, and LCC outside of the regions of stratocumulus clouds.

\section{Conclusions}

We show that low-level clouds in the trade-wind regions ($\pm 30^{\circ}$) drive the strong decadal variability of the climate feedback parameter over the historical 20th century.  This is distinct from the well known fact that low-level clouds are also the main source of uncertainty \replaced{in}{of} the ECS \replaced{of}{among} GCMs.  
Changes in the LCC fields track excellently with $\alpha$, $\alpha_{CRE}$, and \added{$\alpha_{SW CRE}$}, and are consistent with a period of high sensitivity (small $\alpha$, negative LCC anomalies, and CREs near zero) between 1925-1955 and low sensitivity (large $\alpha$, positive LCC anomalies, and negative CREs) between 1975-2005.   These changes in the cloud fields are ultimately driven by differences in the SST patterns between the two time periods.  The variability is not simply due to a weakening or strengthening of Stratocumulus cloud decks, but rather it is marked by changes in the trade-wind regions as a whole and in particular, the tropical Atlantic.   The southern ocean low-level clouds also have contrasting trends between the two periods.

We have decomposed $\alpha$ into specific geographic regions showing the decadal variability of $\alpha$ to be almost
entirely due to the tropical region between $\pm 30^{\circ}$ (Fig 1.b).   Large regional changes in the trend of LCC mirror changes in EIS and SWCRE even outside of the regions traditionally thought to be influenced by EIS (Figs. 2,3).  Although specific regions traditionally identified with persistent stratocumulus cloud decks show physically consistent relationships between the LCC, SWCRE, and EIS between the two periods of differing sensitivity, they only contribute a total of around $10\%$ to the magnitude of global mean $\alpha$ \added{(Fig 1.b)}.  As computed here the sum of these regions occupy about $6\%$ of the globe.
\added{The same computations with the windows from \citet{Qu_etal_2014} accounts for around $13\%$ of $\alpha$ while occupying about $9\%$ of the globe (SM Fig1).}  \replaced{Their contribution shows little decadal variability (Fig. 1.b.)}{In all cases, contributions to the decadal variability of $\alpha$ from tropical windows are minimal.}

Following the work of \citet{Qu_etal_2014, Qu_etal_2015}, and Z16 we use multiple linear regression to estimate the dependence of $\Delta \rm{LCC}$ on $\Delta \rm{EIS}$ and $\Delta \rm{SST}$ for three AGCMs over the historical period.  
The linear model of LCC change works well when applied to both $\pm 30^{\circ}$ and  $\pm 60^{\circ}$.
\deleted{We find that} The spatial distribution of EIS trends corresponds well to trends of LCC in regions with stratocumulus, trade-wind cumulus, and shallow cumulus clouds.  This indicates that the strong influence of EIS on LCC holds for disparate patterns of SST and across an $\alpha$ range (in this study) of $2.2 \rm{W m}^{-2} \rm{K}^{-1}$ .

Despite the broad similarity of simulations among the three AGCMs used in this study there are differences.  The sensitivities of AM2.1 and AM4.0 are lower than AM3 in the mid twentieth-century consistent with a stronger mid-latitude decrease of low-level clouds in AM3 during that period.  While $\Delta \rm{LCC}$ of all three AGCMs have a linear dependence on $\Delta \rm{EIS}$ and $\Delta \rm{SST}$, the relative dependence on each variable differs among models (SM Table 2).  Over the second half of the twentieth century AM4.0 and AM3 show a strong decrease of $\alpha$ while $\alpha_{CRE}$ decreases by $1.5 \rm{W m}^{-2} \rm{K}^{-1}$ (Fig. \ref{fig:alphacre}).  In contrast, AM2.1 has a weak decrease of $\alpha$ and a decrease of $\alpha_{CRE}$ of only $0.9 \rm{W m}^{-2} \rm{K}^{-1}$ between the two periods.

Recently Gregory and Andrews (GA16) \replaced{showed the}{computed an} effective climate sensitivity over the historical period to be 2K.  This is significantly less than the sensitivity from the corresponding AOGCMs in response to 4x$\rm{CO}_2$ experiments \citep{Andrews_etal_2012}.  
Similarly, the effective climate sensitivities of AM2.1 (1.7K), AM3 (2.0K), and AM4.0 (1.9K) over the historical period are significantly lower than the ECS of the parent AOGCMs (ESM2M (3.3K) and CM3(4.8K), computed from multi-millennia equilibrium runs).  \deleted{The Cess sensitivities of AM2.1, AM3, and AM4.0 are (0.58, 0.73, and 0.57 $\rm{K} $ $ \rm{W}^{-1} \rm{m}^2$, respectively).}  Much of the uncertainty in \replaced{both}{the} ECS \deleted{and the Cess sensitivity} has been attributed to cloud feedbacks 
\citep{Cess_etal_1989, Bony_Dufresne_2005}.  \added{Despite large differences in ECS and effective climate sensitivities among AM2.1, AM3, and AM4.0}
\deleted{nevertheless} this study demonstrates that the cloudy response to changing SST patterns over the historical period is similar \replaced{among AM2.1, AM3, and AM4.0}{for these AGCMs}.

Assuming that $\alpha$ is constant has provided a useful approximation of the Earth's energetic response to perturbations despite the knowledge \citep [e.g.,][]{Senior_Mitchell_2000, Andrews_etal_2012, Armour_etal_2013, Andrews_etal_2015} that $\alpha$ is not constant and that the energetic response is nonlinear.  
Previous work has shown how dependent the equilibrium sensitivity is on low-level clouds in both `fully-comprehensive' Earth-system models \citep{Vial_etal_2013, Sherwood_etal_2014, Paynter_Frolicher_2015} 
as well extremely simplified cases \citep{Silvers_etal_2016}.   Our analysis of the historical period reveals how dependent $\alpha$ is on changes in the global low-level cloud fields.  While \replaced{$\alpha$}{the effective climate sensitivity} over the historical period is distinct from the \replaced{equilibrium climate sensitivity}{ECS}, the influence of clouds on the global energy budget is important for both.   Because our AGCMs are driven by prescribed \replaced{lower boundary conditions with}{SST and sea ice concentrations and} constant atmospheric forcing the relative strength of the feedbacks seen in this study may differ from the feedbacks of a fully interactive Earth system model.  But while the cloud feedbacks in the full Earth system may have a more nuanced response, 
this work clearly documents how the atmospheric cloudy response to particular SST patterns plays a dominant role in the energy budget at the TOA.

Recent work has increasingly highlighted the critical role of cloud base cloudiness in determining the climate sensitivity of GCMs 
\citep{Brient_etal_2015, Vial_etal_2017}.   
The atmospheric stability (EIS or LTS) provides an excellent diagnostic tool with which to determine how parameterized turbulence and convection influence the low-level atmospheric temperature.  This paper shows that EIS simulates LCC very well throughout the global oceans during periods of both high and low sensitivity.   Our demonstration of the strong connection between atmospheric stability, LCC, and $\alpha$ indicates a useful link between GCM parameterizations and the climate sensitivity.

%%% End of body of article

%  ACKNOWLEDGMENTS

\acknowledgments
We thank Mike Winton, Nadir Jeevanjee and two anonymous reviewers for helpful reviews.  Larry Horowitz,  Fanrong Zeng and Tom Delworth are thanked for making data from 
AM2.1 and AM3 available.  Relevant data and scripts used in the analysis are available from LGS upon request.  This paper was prepared by LGS under award NA14OAR4320106 
from the National Oceanic and Atmospheric Administration, U.S. Department of Commerce.  The statements, conclusions, and recommendations
are those of the authors and do not necessarily reflect the views of the National Oceanic and Atmospheric Administration, or the 
U.S Department of Commerce.

%%  REFERENCE LIST AND TEXT CITATIONS

\begin{thebibliography}{32}
\providecommand{\natexlab}[1]{#1}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
  \urlstyle{rm}\Url}\fi

\bibitem[{\textit{Andrews}(2014)}]{Andrews_2014}
Andrews, T. (2014), Using an {AGCM} to diagnose historical effective radiative
  forcing and mechanisms of recent decadal climate change, \textit{JCLI}, 
  \textit{27}, 1193--1209.

\bibitem[{\textit{Andrews et~al.}(2012)\textit{Andrews, Gregory, Webb, and
  Taylor}}]{Andrews_etal_2012}
Andrews, T., J.~M. Gregory, M.~J. Webb, and K.~E. Taylor (2012), Forcing,
  feedbacks and climate sensitivity in {CMIP5} coupled atmosphere-ocean climate
  models, \textit{Geophys.\ Res.\ Lett.}, \textit{39}, 1--7,
  \doi{10.1029/2012GL051607}.

\bibitem[{\textit{Andrews et~al.}(2015)\textit{Andrews, Gregory, and
  Webb}}]{Andrews_etal_2015}
Andrews, T., J.~M. Gregory, and M.~J. Webb (2015), The dependence of radiative
  forcing and feedback on evolving patterns of surface temperature change in
  climate models, \textit{JCLI}, \textit{28}, 1630--1648.

\bibitem[{\textit{Armour}(2017)}]{Armour_2017}
Armour, K. (2017), Energy budget constraints on climate sensitivity in light of
  inconstant climate feedbacks, \textit{Nat.\ Cim.\ Change}, \textit{7},
  \doi{10.1038/NCLIMATE3278}.

\bibitem[{\textit{Armour et~al.}(2013)\textit{Armour, Bitz, and
  Roe}}]{Armour_etal_2013}
Armour, K.~C., C.~M. Bitz, and G.~H. Roe (2013), Time-varying climate
  sensitivity from regional feedbacks, \textit{JCLI}, \textit{26},
  4518--4534.

\bibitem[{\textit{Bony and Dufresne}(2005)}]{Bony_Dufresne_2005}
Bony, S., and J.~L. Dufresne (2005), Marine boundary layer clouds at the heart
  of tropical cloud feedback uncertainties in climate models, \textit{Geophys.\
  Res.\ Lett.}, \textit{32}, \doi{10.1029/2005GL023851}.

\bibitem[{\textit{Bony et~al.}(2004)\textit{Bony, Dufresne, Treut, Morcrette,
  and Senior}}]{Bony_etal_2004}
Bony, S., J.~L. Dufresne, H.~L. Treut, J.-J. Morcrette, and C.~Senior (2004),
  On dynamic and thermodynamic components of cloud changes, \textit{Clim.\
  Dynam.}, \textit{22}, \doi{10.1007/s00382-003-0369-6}.

\bibitem[{\textit{Bretherton et~al.}(2004)\textit{Bretherton, Peters, and
  Back}}]{Bretherton_etal_2004}
Bretherton, C.~S., M.~E. Peters, and L.~E. Back (2004), A new parameterization
  for shallow cumulus convection and its application to marine subtropical
  cloud-topped boundary layers. part i: Description and 1-d results,
  \textit{Mon.\ Wea.\ Rev.}, \textit{132}, 864--882.

\bibitem[{\textit{Brient et~al.}(2015)\textit{Brient, Schneider, Tan, Bony, Qu,
  and Hall}}]{Brient_etal_2015}
Brient, F., T.~Schneider, Z.~Tan, S.~Bony, X.~Qu, and A.~Hall (2015),
  Shallowness of tropical low clouds as a predictor of climate models' response
  to warming, \textit{Clim.\ Dynam.}, \textit{45},
  \doi{10.1007/s00382-015-2846-0}.

\bibitem[{\textit{Cess et~al.}(1989)\textit{Cess, Potter, and
  Blanchet}}]{Cess_etal_1989}
Cess, R.~D., G.~L. Potter, and J.~Blanchet (1989), Interpretation of
  cloud-climate feedback as produced by 14 atmospheric general circulation
  models, \textit{Science}, \textit{245}, 513--516.

\bibitem[{\textit{Donner}(1993)}]{Donner_1993}
Donner, L.~J. (1993), A Cumulus Parameterization Including Mass Fluxes, 
Vertical Momentum Dynamics, and Mesoscale Effects, \textit{JAS},
  \textit{50}, 889--906, \doi{0.1175/1520-0469(1993)050<0889:ACPIMF>2.0.CO;2}.

\bibitem[{\textit{Donner and Coauthors}(2011)}]{Donner_etal_2011}
Donner, L.~J., and Coauthors (2011), The dynamical core, physical
  parameterizations, and basic simulation characteristics of the atmospheric
  component {AM3} of the {GFDL} global coupled model {CM3}, \textit{JCLI},
  \textit{24}, 3484--3519, \doi{10.1175/2011JCLI3955.1}.

\bibitem[{\textit{Forster and Gregory}(2006)}]{Forster_Gregory_2006}
Forster, P.~M., and J.~M. Gregory, (2006), The Climate Sensitivity and Its
Components Diagnosed from Earth Radiation Budget Data, \textit{JCLI}, 
\textit{19}, 39--52, \doi{10.1175/JCLI3611.1}.

\bibitem[{\textit{Flato et al.}(2013)}]{Flato_etal_2013}
Flato et al. (2013), Evaluation of Climate Models, in \textit{Climate Change 2013: The Physical Science Basis.  
Contribution of Working Group I to the Fifth Assessment Report of the Intergovernmental 
Panal on Climate Change}, edited by G. Flato et al., 741--882, Cambridge Univ.
Press, \doi{10.1017/cbo9781107415324.020}.

\bibitem[{\textit{GFDL-GAMDT}(2004)}]{GFDL_GAMDT_2004}
GFDL-GAMDT (2004), The new {GFDL} global atmosphere and land model {AM2}/{LM2}:
  Evaluation with prescribed {SST} simulations, \textit{JCLI}, \textit{17},
  4641--4673, \doi{10.1175/JCLI-3223.1}.

\bibitem[{\textit{Gregory and Andrews}(2016)}]{Gregory_Andrews_2016}
Gregory, J.~M., and T.~Andrews (2016), Variation in climate sensitivity and
  feedback parameters during the historical period, \textit{Geophys.\ Res.\
  Lett.}, \textit{43}, 3911--3920, \doi{10.1002/2016GL068406}.

\bibitem[{\textit{Gregory et~al.}(2004)\textit{Gregory, Ingram, Palmer, Jones,
  Stott, Thorpe, Lowe, Johns, and Williams}}]{Gregory_etal_2004}
Gregory, J.~M., W.~J. Ingram, M.~A. Palmer, G.~S. Jones, P.~A. Stott, R.~B.
  Thorpe, J.~A. Lowe, T.~Johns, and K.~Williams (2004), A new method for
  diagnosing radiative forcing and climate sensitivity, \textit{Geophys.\ Res.\
  Lett.}, \textit{31}, 1--4, \doi{10.1029/2003GL018747}.

\bibitem[{\textit{Grise and Medeiros}(2016)}]{Grise_Medeiros_2016}
Grise, K.~M., and B.~Medeiros (2016), Understanding the varied influence of
  midlatitude jet position on clouds and cloud radiative effects in
  observations and global climate models, \textit{JCLI}, \textit{29},
  9005--9025, \doi{10.1175/JCLI-D-16-0295.1}.

\bibitem[{\textit{Haugstad et~al.}(2017)\textit{Haugstad, Armour, Battisti, and
  Rose}}]{Haugstad_etal_2017}
Haugstad, A.~D., K.~C. Armour, D.~S. Battisti, and B.~E.~J. Rose (2017),
  Relative roles of surface temperature and climate forcing patterns in the
  inconstancy of radiative feedbacks, \textit{Geophys.\ Res.\ Lett.},
  \textit{44}, \doi{10.1002/2017GL074372}.

\bibitem[{\textit{Klein and Hartmann}(1993)}]{Klein_Hartmann_1993}
Klein, S.~A., and D.~L. Hartmann (1993), The seasonal cycle of low stratiform
  clouds, \textit{JCLI}, \textit{6}, 1587--1606,
  \doi{10.1175/1520-0442(1993)006<1587:TSCOLS>2.0.CO;2}.

\bibitem[{\textit{Mauritsen et~al.}(2013)\textit{Mauritsen, Graversen, Klocke,
  Langen, Stevens, and Tomassini}}]{Mauritsen_etal_2013}
Mauritsen, T., R.~G. Graversen, D.~Klocke, P.~L. Langen, B.~Stevens, and
  L.~Tomassini (2013), Climate feedback efficiency and synergy, \textit{Clim.\
  Dynam.}, \textit{41}, 2539--2554.

\bibitem[{\textit{Medeiros et~al.}(2008)\textit{Medeiros, Stevens, Held, Zhao,
  Williamson, Olson, and Bretherton}}]{Medeiros_etal_2008}
Medeiros, B., B.~Stevens, I.~M. Held, M.~Zhao, D.~L. Williamson, J.~G. Olson,
  and C.~S. Bretherton (2008), Aquaplanets, climate sensitivity, and low
  clouds, \textit{JCLI}, \textit{21}, 4974--4991.

\bibitem[{\textit{Moorthi and Suarez}(1992)}]{Moorthi_Suarez_1992}
Moorthi, S., and M.~Suarez (1992), Relaxed arakawa schubert: A parameterization
  of moist convection for general circulation models, \textit{Mon.\ Wea.\
  Rev.}, \textit{120}, 978--1002.

\bibitem[{\textit{Myers and Norris}(2013)}]{Myers_Norris_2013}
Myers, T.~A., and J.~R. Norris (2013), Observational evidence that enhanced
  subsidence reduces subtropical marine boundary layer cloudiness, \textit{JCLI}, 
  \textit{26}, 7507--7524, \doi{10.1175/JCLI-D-12-00736.1}.

\bibitem[{\textit{Myers and Norris}(2016)}]{Myers_Norris_2016}
Myers, T.~A., and J.~R. Norris (2016), Reducing the uncertainty in subtropical
  cloud feedback, \textit{Geophys.\ Res.\ Lett.}, \textit{43},
  \doi{10.1002/2015GL067416}.

\bibitem[{\textit{Paynter and Fr\"{o}licher}(2015)}]{Paynter_Frolicher_2015}
Paynter, D., and T.~Fr\"{o}licher (2015), Sensitivity of radiative forcing,
  ocean heat uptake, and climate feedback to changes in anthropogenic
  greenhouse gases and aerosols, \textit{J.\ Geophys.\ Res.}, \textit{120},
  9837--9854, \doi{10.1002/2015JD023364}.

\bibitem[{\textit{Popp and Silvers}(2017)}]{Popp_Silvers_2017}
Popp, M., and L.~G. Silvers (2017), Double and single {ITCZ}s with and without
  clouds, \textit{JCLI}, \doi{10.1175/JCLI-D-17-0062.1}.

\bibitem[{\textit{Qu et~al.}(2014)\textit{Qu, Hall, Klein, and
  Caldwell}}]{Qu_etal_2014}
Qu, X., A.~Hall, S.~A. Klein, and P.~M. Caldwell (2014), On the spread of
  changes in marine low cloud cover in climate model simulations of the 21st
  century, \textit{Clim.\ Dynam.}, \textit{42},
  \doi{10.1007/s00382-013-1945-z}.

\bibitem[{\textit{Qu et~al.}(2015)\textit{Qu, Hall, Klein, and
  Caldwell}}]{Qu_etal_2015}
Qu, X., A.~Hall, S.~A. Klein, and P.~M. Caldwell (2015), The strength of the
  tropical inversion and its response to climate change in 18 {CMIP5} models,
  \textit{Clim.\ Dynam.}, \textit{45}, \doi{10.1007/s00382-014-2441-9}.

\bibitem[{\textit{Randall et~al.}(1984)\textit{Randall, J.~A.~Coakley, Fairall,
  Kropfli, and Lenschow}}]{Randall_etal_1984}
Randall, D.~A., J.~J.~A.~Coakley, C.~Fairall, R.~A. Kropfli, and D.~H. Lenschow
  (1984), Outlook for research on subtropical marine stratiform clouds,
  \textit{Bull.\ Amer.\ Meteor.\ Soc.}, \textit{65}, 1290--1301.

\bibitem[{\textit{Rose and Rayborn}(2016)}]{Rose_Rayborn_2016}
Rose, B.~E., and J.~Rayborn (2016), The effects of ocean heat uptake on
  transient climate sensitivity, \textit{Curr. Clim. Change Rep.},
  \doi{10.1007/s40641-016-0048-4}.

\bibitem[{\textit{Senior and Mitchell}(2000)}]{Senior_Mitchell_2000}
Senior, C.~A., and J.~F.~B. Mitchell (2000), The time-dependence of climate
  sensitivity, \textit{Geophys.\ Res.\ Lett.}, \textit{27}, 2685--2688,
  \doi{10.1029/2012GL051607}.

\bibitem[{\textit{Sherwood et~al.}(2014)\textit{Sherwood, Bony, and
  Dufresne}}]{Sherwood_etal_2014}
Sherwood, S.~C., S.~Bony, and J.~L. Dufresne (2014), Spread in model climate
  sensitivity traced to atmospheric convective mixing, \textit{Nature},
  \textit{505}, 37--42, \doi{10.1038/nature12829}.

\bibitem[{\textit{Silvers et~al.}(2016)\textit{Silvers, Stevens, Mauritsen, and
  Giorgetta}}]{Silvers_etal_2016}
Silvers, L.~G., B.~Stevens, T.~Mauritsen, and M.~Giorgetta (2016), Radiative
  convective equilibrium as a framework for studying the interaction between
  convection and its large-scale environment, \textit{J.\ Adv. \ Model. \ Earth
  \ Syst.}, \textit{8}, \doi{10.1002/2016MS000629}.

\bibitem[{\textit{Taylor et~al.}(2000)}]{Taylor_etal_2000}
Taylor, K. ~E., and D. Williamson, and F. Zwiers (2000), The sea
  surface temperature and sea-ice concentration boundary conditions
  of {AMIP} {II} simulations, {PCMDI}, Rep. 60, 20 pp., \doi{10.1175/JCLI-D-17-0062.1}.

\bibitem[{\textit{Vial et~al.}(2013)\textit{Vial, Dufresne, and
  Bony}}]{Vial_etal_2013}
Vial, J., J.-L. Dufresne, and S.~Bony (2013), On the interpretation of
  inter-model spread in {CMIP5} climate sensitivity estimates, \textit{Clim.\
  Dynam.}, \textit{41}, 3339--3362, \doi{10.1007/s00382-013-1725-9}.

\bibitem[{\textit{Vial et~al.}(2017)\textit{Vial, Bony, Stevens, and
  Vogel}}]{Vial_etal_2017}
Vial, J., S.~Bony, B.~Stevens, and R.~Vogel (2017), Mechanisms and model
  diversity of trade-wind shallow cumulus cloud feedbacks: A review,
  \textit{Surv. Geophys. Rev.}, \doi{10.1007/s10712-017-9418-2}.

\bibitem[{\textit{Webb et~al.}(2015)\textit{Webb, Lock, Bretherton, Bony, Cole,
  Idelkadi, Kang, Koshiro, Kawai, Ogura, Roehrig, Shin, Mauritsen, Sherwood,
  Vial, Watanabe, Woelfle, and Zhao}}]{Webb_etal_2015}
Webb, M.~J., A.~P. Lock, C.~S. Bretherton, S.~Bony, J.~N. Cole, A.~Idelkadi,
  S.~M. Kang, T.~Koshiro, H.~Kawai, T.~Ogura, R.~Roehrig, Y.~Shin,
  T.~Mauritsen, S.~C. Sherwood, J.~Vial, M.~Watanabe, M.~D. Woelfle, and
  M.~Zhao (2015), The impact of parameterized convection on cloud feedback,
  \textit{Philos.\ Trans.\ Roy.\ Soc.\ London\ A}, \textit{373},
  \doi{10.1098/rsta.2014.0414}.

\bibitem[{\textit{Webb et~al.}(2017)\textit{Webb, Andrews, Bodas-Salcedo, Bony,
  Bretherton, Chadwick, Chepfer, Douville, Good, Kay, Klein, Marchand,
  Medeiros, Siebesma, Skinner, Stevens, Tselioudis, Tsushima, and
  Watanabe}}]{Webb_etal_2017}
Webb, M.~J., T.~Andrews, A.~Bodas-Salcedo, S.~Bony, C.~S. Bretherton,
  R.~Chadwick, H.~Chepfer, H.~Douville, P.~Good, J.~E. Kay, S.~A. Klein,
  R.~Marchand, B.~Medeiros, A.~P. Siebesma, C.~B. Skinner, B.~Stevens,
  G.~Tselioudis, Y.~Tsushima, and M.~Watanabe (2017), The cloud feedback model
  intercomparison project ({CFMIP}) contribution to {CMIP6}, \textit{Geosci. \
  Model \ Dev.}, \textit{10}, \doi{10.5194/gmd-10-359-2017}.

\bibitem[{\textit{Wood}(2012)}]{Wood_2012}
Wood, R., (2012), {REVIEW} Stratocumulus Clouds, \textit{Mon.\ Wea.\
  Rev.}, \textit{140},
  2373--2423, \doi{10.1175/MWR-D-11-00121.1}.

\bibitem[{\textit{Wood and Bretherton}(2006)}]{Wood_Bretherton_2006}
Wood, R., and C.~S. Bretherton (2006), On the relationship between stratiform
  low cloud cover and lower-tropospheric stability, \textit{JCLI}, \textit{19},
  6425--6432, \doi{10.1175/JCLI3988.1}.

\bibitem[{\textit{Zhao et~al.}(2016)\textit{Zhao, Golaz, Held, Ramaswamy, Lin,
  Ming, Ginoux, Wyman, Donner, and Paynter}}]{Zhao_etal_2016}
Zhao, M., J.-C. Golaz, I.~M. Held, V.~Ramaswamy, S.-J. Lin, Y.~Ming, P.~Ginoux,
  B.~Wyman, L.~J. Donner, and D.~Paynter (2016), Uncertainty in model climate
  sensitivity traced to representations of cumulus precipitation microphysics,
  \textit{JCLI}, \textit{29}, 543--560, \doi{10.1175/JCLI-D-15-0191.1}.

\bibitem[{\textit{Zhou et~al.}(2016)\textit{Zhou, Zelinka, and
  Klein}}]{Zhou_etal_2016}
Zhou, C., M.~D. Zelinka, and S.~A. Klein (2016), Impact of decadal cloud
  variations on the earth's energy budget, \textit{Nat.\ Geosci.}, \textit{9},
  \doi{10.1038/ngeo2828}.

\end{thebibliography}

%

%%%
\listofchanges
%%%

\end{document}

%\listofchanges

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Supporting Information
%% (Optional) See AGUSuppInfoSamp.tex/pdf for requirements 
%% for Supporting Information.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2019-09-20 Silvers_WalkerCell.tex
changed eps file name
substantial editing of the text for Silvers_WalkerCell.tex

@@
 
+The results of our experiments are organized as follows.  First, the general structure and characteristics of the steady state solutions
+will be described.   Then, the influence of parameterized convection and the longwave cloud radiative effect on the overturning 
+circulation will be shown.  We will then briefly discuss how the circulation changes as a function of domain size.  The last part of the
+results will describe and contrast the Walker circulation in a GCM-like configuration and a CRM-like configuration as the 
+resolution changes.
+
 \section{Experimental Details and Methods}
 
-To develop the model configuration used for these experiments we started with the same code base as that of the AM4.0 
-model (Zhao et al. a,b).  This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
-which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations.  Taking 
-the AM4.0 physics we use the interactive radiation, deep and shallow convection, large-scale clouds, and boundary layer 
+To develop the model configuration used for these experiments we started with the same code base as that of the 
+recently developed atmospheric global climate model AM4.0 
+(Zhao et al. a,b).  This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
+which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations.  
+The default AM4.0 physics we use includes interactive radiation, parameterized deep- and shallow-convection, 
+a large-scale cloud scheme, and a boundary layer 
 scheme as described in Zhao et al. a,b and the references therein.  The prognostic moisture variables are the specific 
@@
 %(do_cg_drag set to .f.; Alexander-Dunkerton gravity wave drag) 
-in order to reduce large oscillations in the horizontal wind field in the top of the model domain.  The convection, radiation, 
-large-scale cloud, microphysics, and turbulence parameterization all remain the same as in AM4.0.  
-Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the physics are very 
-similar to those of AM4.0.  This configuration can also be compared to the simulations described in 
+in order to reduce large oscillations which developed in the horizontal wind field near the top of the model domain.  
+The convection, radiation, large-scale cloud, microphysics, and turbulence parameterizations all remain the same 
+as in AM4.0.   Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the 
+physics are very similar to those of AM4.0.  This configuration can also be compared to the simulations described in 
 Popp and Silvers, 2017, which used a developmental version of AM4 with almost the same changes to the physics
 schemes.
-For our simulations using grid spacing of 1km, 2km, and 25km (in select simulations), the double plume (both shallow and deep convection) convective parameterization was 
-turned off and the time step of integration increased.
 
@@
 All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
-direction allowing for three dimensional simulations but with a reduced computational cost relative to the global domain which is usually 
-used with this model.  The SST is prescribed as a Gaussian function which is 4K warmer in the center (301K/27.85C) of the domain then at the edges (297K/23.85C).  
-Thus far the GCM runs with 25km resolution have been run for 5 year.  
-The 1km and 2km CRM were run for 6 months.
+direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.
+The SST is prescribed as a Gaussian function which is 4K warmer in the center (301K/27.85C) of the domain then
+at the edges (297K/23.85C).  The GCM runs with 25km and 100km grid-spacing have been run for 5 years while the 
+1km and 2km experiments were run for 6 months.  Experiments with parameterized convection will be labelled with a P prefix, followed
+by a number indicating the grid-spacing in kms while the experiments with explicit convection and no parameterized convection will be 
+labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
+grid-spacing of 25km, while E25 refers to an experiment that is identical to P25 except that the convective parameterization is turned off.
 
-The simulations with a grid-spacing of 1km and 2km are referred to as cloud resolving simulations.  For our purposes this simply means
-that both deep and shallow convective parameterizations are turned off, and that the threshold of grid-cell mean relative humidity 
-which triggers new clouds is changed from the default value of 0.8 to 1.0.   The Tiedtke (1993) parameterization scheme for large-scale 
+To illustrate the strong dependence of our results on domain size, as well as the fundamental role that the LW CRE plays in GCMs
+we utilize fully parameterized experiments with grid-spacing of 25km (P25) and 100km (P100) on domains with a long dimension 
+of 4000 km (`small') and
+16000 km (`large').  To explore the mock-Walker circulation in the context of both a GCM and a CRM we utilize 
+comparisons of the experiments with grid-spacings of 25km (E25), 2km (E2), and 1km (E1) all on a domain with the same long dimension 
+of 4000 km.  The experiments with a grid-spacing of 25km serve as a link between the GCM-like configuration and the CRM-like 
+configuration.  Domains with dimensions of 16000 km are too costly for the 1km and 2km experiments.
+
+The E1 and E2 simulations are in many ways similar to the configuration of so-called cloud resolving models.  
+In particular both the deep and shallow convective parameterizations are turned off, and the threshold of grid-cell mean relative humidity 
+which triggers new clouds is changed from the default value of 0.8 to 1.0.  While a grid spacing of 1 or 2km is clearly not small enough
+to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  The primary 
+difference between the CRM simulations presented in this paper and those of more established CRMs such as SAM is that our model
+has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The Tiedtke (1993) 
+parameterization scheme for large-scale 
 clouds was designed to be used with GCMs having a coarse grid-spacing.  However, there is not a fundamental problem that we are 
@@
 One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the 
-radiation.
-This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.
-This method was originally pioneered by Slingo and Slingo, 1988 and Randall et al., 1989.
-More recently, it has been
+radiation.  This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the 
+atmospheric state.   This method was originally pioneered by Slingo and Slingo, 1988 and Randall et al., 1989.  More recently, it has been
 implemented as part of the CFMIP series of experiments (Stevens et al. 2012).
 In the AM4 code, this is done separately for the longwave and shortwave radiation.  In this study we compare control experiments, 
-in which clouds and radiation are fully interactive with experiments in which clouds are
-invisible to the longwave radiation.  These experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE off).  
-Other than the invisible clouds, the model is the same.  Both longwave and shortwave radiation are present and interactive with 
+in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the longwave radiation.  These 
+experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE off).  
+For the LWCRE off experiments, both the longwave and shortwave radiation are present and interact with 
 the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
-In general, turning off the longwave cloud radiative effect will have a large impact on the surface budget of a coupled model.  
+Normally, turning off the longwave cloud radiative effect would have a large impact on the surface budget of a coupled model.  
 However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
-strongly effected as might be expected.  Experiments with only a water surface at the lower boundary and fixed SST are the
-ideal configuration to utilize the LWCRE off experiments.
+strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
+fixed SST are the ideal configuration to utilize the LWCRE off experiments as a way of diagnosing how clouds interact with 
+the atmospheric state.
 
-\section{Results}
+\section{The organizing influence of LWCRE and the asymmetric results of parameterized convection.}
 
-The results of our experiments are organized as follows.  First, the general structure and characteristics of the steady state solutions
-will be described.   Then, the influence of parameterized convection and the longwave cloud radiative effect on the overturning 
-circulation will be shown.  We will then briefly discuss how the circulation changes as a function of domain size.  The last part of the
-results will describe and contrast the Walker circulation in a GCM-like configuration and a CRM-like configuration.
+The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
+\ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
+SSTs and a humid boundary layer across the full length of the domain.   For the GCM-like configuration (P25, left panels 
+of Figure \ref{fig:rh_psi_P25vsE25}) with fully parameterized convection and with the longwave CRE turned on, there is 
+a strong overturning circulation that results in a humid, condensate loaded troposphere near the middle of the domain 
+and a dry ($< 10\% RH$) subsidence region with almost no condensate above $800 \rm{hPa}$.    
+To illustrate how (how what?  the double-plume convective parameterization influences the atmospheric state) 
+we compare the P25 experiment with analogous experiments in which the longwave CRE is off (P25 LWCRE off, middle 
+panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
+parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).  
+The mass streamfunction and vertical velocity both show the P25 experiment has a stronger overturning circulation 
+than either E25 or P25 LWCRE off.  P25 also has higher humidity in the deep convective region, and lower humidity in 
+the subsidence region over the 
+cooler SST (Figure \ref{fig:rh_psi_P25vsE25}) than either E25 or P25 LWCRE off.  Averaged over the full domain, 
+the parameterized convection leads to a dryer atmosphere with less 
+condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  However, in 
+the updraft region the convective parameterization results in more moisture aloft.
 
-The mock-Walker Circulation that emerges from these simulations is a deep overturning circulation.  There are two circulation cells, 
-one below $500 \rm{hPa}$  and one above.  Deep-convective activity dominates the region over the warm pool, shallow convection is 
-common over a wider range of SSTs, and for the most part stratocumulus 
+There are circulation cells below $500 \rm{hPa}$  and above $500 \rm{hPa}$.  Deep-convective activity dominates the 
+region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
 clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, the atmospheric 
@@
 
-We perform a series of sensitivity experiments to highlight the different ways in which these experiments can equilibrate.  To show the sensitive 
-nature of the distribution of the precipitation maximum we test the impact of convective parameterization, 
+We perform a series of sensitivity experiments to highlight the different ways in which these experiments can equilibrate.  To 
+show the sensitive nature of the distribution of the precipitation maximum we test the impact of convective parameterization, 
 longwave radiation interactions with clouds, domain size, 
@@
 because of the sensitivity of the low-level clouds to the longwave radiative cooling.
+
+The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
+This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
+as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
+SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
+mean shear develops which shifts the precipitation and circulation off center for years at a time.  This appears to be not entirely a 
+result of the convective parameterization, but due to an interaction between the convective parameterization and the LW CRE.
 
@@
 
-\subsection{The Asymmetric Influence of Convective Parameterization and the organizing tendency of LWCRE}
+%\subsection{The Asymmetric Influence of Convective Parameterization and the organizing tendency of LWCRE}
 
@@
 
-To illustrate how the double plume convective parameterization influences the atmospheric state we compare the P25 and
-E25 simulations in which the only difference is that all convective parameterization is turned off in E25 (refer to a figure with
-profiles for E25 and P25).  The P25 experiment represents a GCM-like configuration and compared to E25 has a stronger 
-overturning circulation, higher humidity in the deep convective region, and lower humidity in the subsidence region over the 
-cooler SST (Figure \ref{fig:rh_psi_P25vsE25}).  Averaged over the full domain, the parameterized convection leads to a 
-dryer atmosphere with less 
-condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  However, in 
-the updraft region the convective parameterization results in more moisture aloft.
-
 One of the most prominent features of our 25km grid-spacing simulations is an asymmetry in both the time-dependent and 
@@
 
-Below is a list of several changes that occur when the LW CRE is off.  The points which have not already been discussed will be later in the paper.
-
-Turning the longwave cloud radiative interactions off tends to:
-
-\begin{itemize}
-  \item decrease the strength of the overturning circulation and the domain mean precipitation
-  \item increase the midtropospheric RH by $5-15 \% $
-  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
-  \item weaken the horizontally oriented low-level circulations.   This looks connected to a contracting of relative 
-           humidity maxima around 600 hPa.
-  \item spread out in geographic space the precipitation maxima
-  \item dramatically homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
-  \item decrease both the LTS and the EIS, over both the warm and cold regions
-%  \item in most cases the symmetry about the SST maximum is increased.
-  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
-  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
-           the 1 and 2 \textit{km} simulations. 
-  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
-  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
-\end{itemize}
-
 %% low level structure
@@
 
-\subsection{Dependence on Domain Size}
+\subsection{The Influence of Domain Size on the LWCRE and the LS Parameterized Precipitation}
 
@@
 
-% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
-% LW CRE off
-\begin{figure}
-  \centering
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcreoff.eps}
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre_draft.eps}
-  \caption{Normalized probability distributions of the location of the maximum value of precipitation for P25 and P100
-  experiments .   Panels on the right (left) show experiments on the domain with a long dimension of 4000 km 
-  (16000 km).  Black distributions are for experiments with the LW CRE on and green distributions for experiments 
-  with LW CRE off.  The black curves show a Gaussian function with a standard deviation computed for 
-  each experiment and an expected location in the center of the domain where the SST is warmest.}
-\end{figure}
+%% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
+%% LW CRE off
+%\begin{figure}
+%  \centering
+%      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcreoff.eps}
+%      \includegraphics[width=0.6\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre_draft.eps}
+%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for P25 and P100
+%  experiments .   Panels on the right (left) show experiments on the domain with a long dimension of 4000 km 
+%  (16000 km).  Black distributions are for experiments with the LW CRE on and green distributions for experiments 
+%  with LW CRE off.  The black curves show a Gaussian function with a standard deviation computed for 
+%  each experiment and an expected location in the center of the domain where the SST is warmest.}
+%\end{figure}
+%
 
@@
 range of values.  To simplify the analysis we have in most cases chosen to keep the 
-long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies have documented sensitivities to domain size.  With this 
-in mind several different domain shapes and sizes have been explored, but always keeping the $4000\, \rm{km}$ long-dimension as the 
-primary domain for the analysis.  
+long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies (e.g. Bretherton et al. 2006) have 
+documented sensitivities to domain size.   The analysis of the previous, and of the next section focus on results from experiments using
+a domain with a long domain length of $4000 \, \rm{km}$.  However we do find sensitivity to the domain size and thought it to be
+sufficiently interesting to report.
+
 Examining the evolution in time of the precipitation field reveals important characteristics of these simulations, and 
 illustrates how much the distribution can vary as a function of domain size, parameterization of convection, and the effect of the 
-longwave radiation due to clouds.  At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
-precipitation over a smaller geographic extent.  
-Shown in Figure {\ref{fig:domdep}} are Hovmoller plots of precipitation after 
+longwave radiation due to clouds. 
+Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
 averaging along the short horizontal dimension.  The four panels show simulations with a grid-
@@
 $16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.    
+ At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
+precipitation over a smaller geographic extent.   This is consistent with the idea that CREs strengthen an overturning circulation and
+narrow the region of deep convection (see Popp and Silvers, 2017, HH, Dixit et al. 2019.  etc.).
 The structure of the precipitation depends strongly on domain size and shows less dependence on grid-spacing.
+On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
+experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation which meanders within 
+500 km of the SST maximum at the center of the domain,  
+the experiments without the LW CRE basically have no region with consistently strong precipitaiton.  Instead, 
+smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.
 
@@
 They also found less low-level clouds over the colder SSTs in the smaller domains, relative to a control domain size that was 4x
-larger.   We have found larger precipitation rates for the larger domains.  Does our larger domain ascent region change?  Does 
-Brethertons SST warm patch size increase with domain size?
+larger.   We have found larger precipitation rates for the larger domains.  Does our larger domain ascent region change?
 
@@
       \includegraphics[width=0.8\columnwidth]{walkerfigs/Conv_vs_LS_hist.eps}
-  \caption{Fraction of precipitation that is due to the large-scale(blue) cloud scheme relative to the total 
-  precipitation (large-scale plus convective).}
+  \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective parameterization (black).}
   \label{fig:conv_vs_ls}
@@
 
-\subsection{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
+Below is a list of several changes that occur when the LW CRE is off.  The points which have not already been discussed will be later in the paper.
+
+Turning the longwave cloud radiative interactions off tends to:
+
+\begin{itemize}
+  \item decrease the strength of the overturning circulation and the domain mean precipitation
+  \item increase the midtropospheric RH by $5-15 \% $
+  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
+  \item weaken the horizontally oriented low-level circulations.   This looks connected to a contracting of relative 
+           humidity maxima around 600 hPa.
+  \item spread out in geographic space the precipitation maxima
+  \item dramatically homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
+  \item decrease both the LTS and the EIS, over both the warm and cold regions
+%  \item in most cases the symmetry about the SST maximum is increased.
+  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
+  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
+           the 1 and 2 \textit{km} simulations. 
+  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
+  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
+\end{itemize}
+
+\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
 General Circulation Model to a Cloud Resolving Model}
@@
 different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
-Our primary motivation for using the GFDL AM4 on this doubly-periodic domain is that the dynamical core of the model can 
-easily be used over a wide range of grid-spacings and can be used to solve either the hydrostatic or nonhydrostatic 
-governing equations.  In this section we focus on simulations with grid-spacings that range between 1km and 100km.   
-A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that results from the 
-overturning circulation at different resolutions.  Shown are the first 180 days of the P25, E25, E2, and E1 simulations.  As the 
-grid-spacing decreases towards $1 \, \rm{km}$ the distribution of precipitation becomes more regular and consistently 
+The tropical Pacific also serves as an ideal location to study interactions between clouds and the 
+circulation because it includes strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
+clouds (Johnson et al. 1999) as well as stratocumulus cloud decks along the eastern extremities of the basin.
+Can we hope to simulate all of this in an idealized modeling context?    
+Our initial motivation for using the GFDL AM4 model on this doubly-periodic domain was to simulate this region 
+%that is rich in phenomena 
+in the context of both a GCM and a CRM in the hopes of learning something from the high resolution 
+cases that will help us to improve the development of the GCM.    
+The dynamical core of the current generation GFDL models is ideally suited to this task because it can easily 
+be used over a wide range of resolutions and can solve either the hydrostatic or nonhydrostatic 
+governing equations.  In this section we focus on simulations with grid-spacing of 1km, 2km, and 25km.   
+A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that result from the 
+overturning circulation at different resolutions.  Shown are 180 days precipitation from the P25, E25, E2, and E1 simulations.  As the 
+resolution increases towards $1 \, \rm{km}$ the distribution of precipitation becomes more regular and consistently 
 centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more variability at later 
-times, compared to these first 180 days.  Due to the large expense of the E2 and E1 simulations they were run for 
-180 days.  The simulations with explicit convection at resolutions typical of cloud-resolving models (E2, E1) show little 
-aversion to the precipitation maximum occurring over the maximum in SST and relative to the P25 and E25 simulations 
+times, compared to these first 180 days.  The simulations with explicit convection at resolutions typical of cloud-resolving 
+models (E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST and relative to 
+the P100, P25 and E25 simulations 
 they are able to maintain a smoother distribution of  precipitation values over a broader range of SST values.
 
+\begin{figure}
+  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
+  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
+  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
+  Shading indicates mm/day.  The horizontal axis shows the entire 
+  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  Shown is the meridional average. }
+  \label{fig:hov_4mods_6mn}
+\end{figure}
+
+Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
+the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
+simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+The large oscillations in domain mean precipitation are similar to those noted in previous studies 
+(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
+mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
+of the differences in upper level cloud fraction and will be further discussed.
+
+Superposing the circulation and relative humidity illustrates the subsidence driven 
+drying and the strong moistening that results from ascent over the region of maximum latent heat flux.
+
 The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
-among the experiments with varying grid-spacing.  All experiments have a multicell vertical structure (consistent with 
+among the experiments with varying resolutions.  All experiments have a multicell vertical structure (consistent with 
 Bretherton et al. 2006), in contrast to the single cell that results from simple theoretical models such as the SQTCM.   All 
@@
 in the P25 experiment, and a small third cell has developed in the boundary layer of the 1km experiment.  The mid-troposphere 
-in the region with deep-convection is more than $40\%$ dryer than it is for the 2km and 1km experiments.
+of the P25 experiment is more than $40\%$ dryer in the region with deep-convection than for the 2km and 1km experiments.
 
@@
 half of the domain.  It appears that these differences in magnitude and regularity are due to the differing wind speeds at the 
-lowest atmospheric level.  It is also work noting that the E1 experiment has a stronger domain mean u wind shear compared 
+lowest atmospheric level.  It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
 with the E2 and E25 experiments.  Over the warm patch of SST, the surface enthalpy flux is decreased by the LWCRE for E25, 
@@
 % LW CRE on
-\begin{figure}
-  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
-  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case, 25km case with no 
-  parameterized convection, 2km control, and 1km control.  Shading indicates mm/day.  The horizontal axis shows the entire 
-  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the meridional average. }
-  \label{fig:hov_4mods_6mn}
-\end{figure}
 
@@
 
-Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
-the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
-simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
-The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
-mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
-of the differences in upper level cloud fraction.   Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
+Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
 fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by E25, P25, and 
@@
 and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a fundamental difference 
+(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a significant difference 
 between the GCM-like P25/E25 experiments and the CRM-like E2/E1 experiments with the former having much 
-higher values of low-level liquid condensate/cloud and the later having much higher values up upper level ice condensate.  
+higher values of low-level liquid condensate/cloud and the later having much higher values of upper level ice 
+condensate.  The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
+regions of the CRM-like experiments.     
 It is also interesting to note that the LWCRE results in less condensate above 700 hPa for all experiments, and 
@@
 humidity in the subsidence regions decreases with resolution.  This is consistent with an overturning circulation that 
-strengthens as the resolution increases.   This dependence of circulation strength and moisture on resolution is especially 
-apparent when the LWCRE is off (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).  When the clouds and radiation are allowed 
+strengthens as the resolution increases.  When the clouds and radiation are allowed 
 to directly interact with each the E2 and E1 simulations appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}).   
+This dependence of circulation strength and moisture on resolution is especially 
+apparent when the LWCRE is off (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).
 
 The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
+where the differences in strength of the overturning circulation are most pronounced. 
 (can we use this to understand the differences in LWCRE?).
@@
 
-An interesting fact that emerges from the domain mean values of precipitation with and without the LW CRE (see table 1) 
-is that the response is not the same across the different grid-spacings.  
-Turning the LW CRE off for the E1 and E2 results in more precipitation while for the E25, P25, and P100 experiments 
-less precipitation results from turning the LW CRE off.  The primary method by which the longwave cloud radiative effect 
-influences the atmosphere is by heating the atmosphere in the region between the clouds and the surface.  Larger values 
-of ice condensate and upper-level cloud fraction such as we see for the E2 and E1 experiment imply a larger LW CRE relative
-to the E25, P25, and P100 experiments.    
+An interesting fact that emerges from the domain mean values of precipitation (see table 1) 
+is that the sign of the response to LWCRE is not the same across the different grid-spacings.  
+Turning the LW CRE off for the E1 and E2 experiments results in more precipitation while, 
+for the E25, P25, and P100 
+experiments, less precipitation results from turning the LW CRE off.  
+The primary method by which the longwave cloud 
+radiative effect influences the atmosphere is by heating the atmosphere in the region between the clouds and the surface.  
+Larger values of ice condensate and upper-level cloud fraction such as we see for the E2 and E1 experiment 
+therefore imply a larger LW CRE relative to the E25, P25, and P100 experiments in which there are fewer clouds 
+aloft that can emit downwelling longwave radiation.  When the warming effect of the upper level clouds 
+in the E1 and E2 experiments is removed in the LWCRE off experiments the energy balance of the atmosphere 
+must be maintained through an increase of latent heating and subsequent increase of precipitation.  This is 
+reflected in table 1.  The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
+is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
+The low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  For 
+GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
+convective parameterization, and one part from the large-scale cloud scheme.  Figure \ref{fig:conv_vs_ls} shows 
+that when the LWCRE is turned off for the P25 and P100 experiments, the decrease in precipitation comes from 
+a reduction in the large-scale cloud scheme precipitation and not from a decrease in the convective precipitation.       
 This implies there will be less atmospheric heating from 
@@
 \end{figure}
-
-Superposing the the circulation and relative humidity illustrates the subsidence driven 
-drying and the strong moistening that results from ascent over the region of maximum latent heat flux.
 
@@
 
-\textit{probably insert figure from slides 20 and 21 of IUGG talk.}
 We can see clearly that the interactions between longwave radiation and clouds act to dry the troposphere in the regions of subsidence 
@@
 
+References:
+
+Bretherton et al. 2006
+Jeevanjee et al. 2018
+Kuang and Wofsy
+Muller and Held, 2012
+Popp and Silvers, 2017
+Patrizio and Randall, 2019
+Randall et al., 1989
+Silvers et al. 2016
+Slingo and Slingo, 1988
+Stevens et al. 2012
+Zhao et al. 2018a
+Zhao et al. 2018b
+
 % PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 

### 2019-09-20 Silvers_WalkerCell.tex
replaced the enthalpy flux figure with a four panel figure showing the low-level variables of interest, including enthalpy.

@@
        %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
-       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft2.eps}
+       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
   \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
@@
 
-% surface enthalpy flux
 \begin{figure}
   \centering
-  \begin{minipage}{0.4\textwidth}
-    \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
-    \end{minipage}
-    \begin{minipage}{0.4\textwidth}
-    \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
-    \end{minipage}
-    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
-    (latent and sensible heat flux) of the enthalpy.
-    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
-    \label{fig:enthalpy}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
+  \caption{Variables important to boundary layer energy fluxes.
+Top left panel shows the surface enthalpy flux ($\rm{W m^{-2}}$) and top right panel shows the equivalent potential temperature on the model level closest to the surface.
+The panel on bottom left shows the $u$ wind ($\rm{m s^{-1)}}$)
+  on the model level closest to the surface and the panel on bottom right shows the domain mean
+  $\rm{u}$ wind.}
+  \label{fig:LowLevelVars}
 \end{figure}
+
+%% surface enthalpy flux
+%\begin{figure}
+%  \centering
+%  \begin{minipage}{0.4\textwidth}
+%    \centering
+%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
+%    \end{minipage}
+%    \begin{minipage}{0.4\textwidth}
+%    \centering
+%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
+%    \end{minipage}
+%    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
+%    (latent and sensible heat flux) of the enthalpy.
+%    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
+%    \label{fig:enthalpy}
+%\end{figure}
 
@@
 When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
-enthalpy flux (Figure \ref{fig:enthalpy}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
+enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
 large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 

### 2019-10-14 Silvers_WalkerCell.tex
many changes to Silvers_WalkerCell including a new table and significant text changes.

@@
 dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
-and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.
-To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an idealized equatorial tropical Pacific.
-In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective storms.
-In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, non-precipitating clouds with a dry atmosphere above the clouds.
-These regions are connected by a large-scale circulation.
-We analyze this scenario in a high-resolution and coarse resolution simulation and infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
-This cooling is a key ingredient in the determination of the Earth?s sensitivity to changes in greenhouse gas concentrations.
+and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  To elucidate this 
+coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an idealized equatorial tropical Pacific.   In 
+the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective storms.   In contrast, 
+the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, non-precipitating clouds with a dry 
+atmosphere above the clouds.  These regions are connected by a large-scale circulation.  We analyze this scenario in a high-resolution 
+and coarse resolution simulation and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
+thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth's sensitivity to 
+changes in greenhouse gas concentrations.
 
@@
 resolution (25km, 100km) configured 
-as a fully parameterized general circulation model.
-Both models use approximately the same spatial domain.
-The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.
-By dramatically decreasing the grid-spacing we resolve much more of the dynamical motion and eliminate some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
+as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
+derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
+dramatically decreasing the grid-spacing we resolve much more of the dynamical motion and eliminate some of the statistical 
+approximations of clouds, and thus more explicitly simulate some of their impacts.
 
@@
 %capability to better quantify and understand the connection between tropical convective heating and changes in low clouds.    
+\textbf{Paragraphs of Introduction}
+\begin{itemize}
+  \item{Citation of Walker, Bjerness, and Johnson et al. papers to set the stage}
+  \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
+  circulations.  Previous studies of RCE have proven to be a 
+  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.}
+  \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
+  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
+  in particular.}
+\end{itemize}
 
@@
 \end{itemize}
+
+We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
+highlight both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
+we test the impact of convective parameterization, 
+longwave radiation interactions with clouds, domain size, 
+and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
+because of the sensitivity of the low-level clouds to the longwave radiative cooling.
 
@@
 \begin{center}
-\caption{A few specifications of the simulations used most heavily in this study.  The precipitation values in parenthesis are for the experiments
-in which LWCRE is off.}
+\caption{A few specifications of the simulations used most heavily in this study.  In the Convection
+column, `prm'  indicates that convection is parameterized and `exp' indicates convection is explicity.  
+The precipitation values in parenthesis are for the experiments in which LWCRE is off.}
     \begin{tabular}{*{6}{c}}
@@
     \hline
- Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection & Precip $(\mathrm{mm/day})$   \\ \hline
-  P100 &  100          &   800 $\times$ 16000    &  60              & parameterized           &  4.1 (3.5)          \\ 
     \\
-  P100 &  100                & 800 $\times$ 4000     & 60            & parameterized         & 3.9                \\  
+ Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection & 
+ $\overline{\rm{P}} (\mathrm{mm/day})$    \\ \hline
+  P100L &  100          &   800 $\times$ 16000    &  60              & prm           &  4.1 (3.5)          \\ 
     \\
-  P25 &  25             & 200 $\times$ 16000      & 60             & parameterized          & 4.0 (3.8)                \\  
+  P100 &  100                & 800 $\times$ 4000     & 60            & prm         & 3.9 (3.7)               \\  
     \\
-  P25  &  25             & 200 $\times$ 4000      & 60             & parameterized           & 3.84 (3.66)               \\  
+  P25L &  25             & 200 $\times$ 16000      & 60             & prm          & 4.0 (3.8)                \\  
     \\
- E25  &   25          & 200 $\times$ 4000      & 60             & explicit          & 3.74 (3.46)               \\  
+  P25  &  25             & 200 $\times$ 4000      & 60             & prm           & 3.8 (3.7)               \\  
     \\
- E2   &   2          & 100 $\times$ 4000      & 6             & explicit          & 3.11 (3.50)                \\ 
+ E25  &   25          & 200 $\times$ 4000      & 60             & exp          & 3.7 (3.5)               \\  
     \\
- E1   &   1          & 10 $\times$ 4000      & 6             & explicit          & 3.36 (3.74)                \\  \hline
+ E2   &   2          & 100 $\times$ 4000      & 6             & exp          & 3.1 (3.4)                \\ 
+    \\
+ E1   &   1          & 10 $\times$ 4000      & 6             & exp          & 3.3 (3.7)                \\  \hline
+
+    \end{tabular}\par
+    %\bigskip 
+    \label{tab:lambda}
+\end{center}
+\end{table}
+
+\begin{table}
+\begin{center}
+\caption{Domain mean precipitation ($\overline{\rm{P}}$) and outgoing longwave radiation 
+($\overline{\rm{OLR}}$).
+The values in parenthesis are for the experiments in which LWCRE is off.}
+    \begin{tabular}{*{3}{c}}
+    \hline
+    \hline
+    \\
+ Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$   \\ \hline
+  P100L   &  4.1 (3.5)   &  283.1 (286.9)          \\ 
+    \\
+  P100 &   3.9 (3.7)   &  283.2 (296.4)             \\  
+    \\
+  P25L &   4.0 (3.8)  &  281.2 (290.7)             \\  
+    \\
+  P25  &   3.8 (3.7)    & 282.9 (293.6)             \\  
+    \\
+ E25  & 3.7 (3.5)    &   271.9 (286.8)               \\  
+    \\
+ E2   &  3.1 (3.4)   &  266.2 (285.5)               \\ 
+    \\
+ E1   &  3.3 (3.7)   &  269.3 (289.2)               \\  \hline
 
@@
 
-There are circulation cells below $500 \rm{hPa}$  and above $500 \rm{hPa}$.  Deep-convective activity dominates the 
+Superposing the circulation and relative humidity illustrates the subsidence driven 
+drying and the strong moistening that results from ascent over the region of maximum latent heat flux.  
+Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  Deep-convective activity dominates the 
 region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
@@
 state is much more symmetric about the maximum SST.  
+We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, and 
+circulation (see table 1).  In particular
+the experiments with parameterized convection are much more erratic.
 
-We perform a series of sensitivity experiments to highlight the different ways in which these experiments can equilibrate.  To 
-show the sensitive nature of the distribution of the precipitation maximum we test the impact of convective parameterization, 
-longwave radiation interactions with clouds, domain size, 
-and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
-because of the sensitivity of the low-level clouds to the longwave radiative cooling.
+One of the most prominent features of our GCM-like (in particular, P25) simulations is an asymmetry in both the time-dependent and 
+steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).
+The steady-state precipitation maximum is located  not over the warmest SST but is
+shifted to slightly cooler temperatures.  The asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, 
+specific humidity, and radiative heating.  
+For most of these cases the asymmetry appears as an aversion of the precipitation maxima to reside over the SST maximum.  
+For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^-1}$) domain
+mean shear develops above about 500 \textit{m} which shifts the precipitation and circulation off center for years at a time.
+When the convective parameterization
+is turned off (E25), the overturning circulation becomes weaker and broader (w, and psi), and the precipitation, cloud fields, and 
+circulation all consistently reside over the SST maximum.   
+While the parameterized convection plays a large role in driving this asymmetry it appears to be not entirely a 
+result of the convective parameterization, but also due to an interaction between the convective 
+parameterization and the LW CRE.   The degree to which this asymmetry influences the comparison with other experiments is 
+unclear.    Note: check the wind shear for P25large, P100small, and P100large (E25 has less shear than E1 or E2).
 
-The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
-This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
-as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
-SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
-mean shear develops which shifts the precipitation and circulation off center for years at a time.  This appears to be not entirely a 
-result of the convective parameterization, but due to an interaction between the convective parameterization and the LW CRE.
+Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
+distribution have been noted many times in previous literature
+(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
+tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
+entirely explicit (discussed further in section 4).
 
@@
 
-We find large differences among the experiments in the domain mean precipitation, condensate/clouds, and circulation.  In particular
-the experiments with parameterized convection are much more erratic.  Above about 500 \textit{m} the P25 experiment
-has strong domain mean wind shear that clearly influences the structure of the precipitation, as seen in 
-five year Hovmoller diagrams.  The degree to which this shear influences the comparison with other experiments is unclear.
-
 "... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
@@
 greater are being dominated by this second factor.
+
+Now talk about the organizing influence of LWCRE...
 
@@
 
-One of the most prominent features of our 25km grid-spacing simulations is an asymmetry in both the time-dependent and 
-steady-state solutions.  This results in the steady-state precipitation maximum locating off the maximum in SST and is apparent in 
-the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.   A tendency of the precipitation to 
-occur off of the SST maximum is also apparent in the simulations with a grid-spacing of 100km, although the 25km simulations display 
-an irregularity that is greater than the 100km simulations.  Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
-distribution has been noted many times 
-(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
-tended to be symmetric, unlike our results.
+\begin{figure}
+  \centering
+      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
+  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
+  while the P25 and P100 cases show only the first out of five years of the time series.}
+    \label{fig:precip_dom_mn}
+\end{figure}
 
-For the simulations that are closest to the set up of a GCM, with fully parameterized convection, the steady-state circulation and 
-precipitation maximum are located not over the warmest SST but shifted to regions about one degree cooler.  For the case
-with a grid-spacing of 25km and a domain width of 4000km, the precipitation maximum can remain shifted off of the maximum in
-SST for multiple years.   While focused within the central quarter of the domain, simulations on larger domains and with a 
-grid-spacing of 100km also show an aversion to settling over the SST maximum.   When the convective parameterization
-is turned off, the overturning circulation becomes weaker and broader (w, and psi), but the precipitation, cloud fields, and 
-circulation all consistently reside over the SST maximum.  When the convective parameterization is turned on, a domain mean 
-wind shear develops throughout the lowest 10km that acts to shift the convective activity and circulation off of the SST maximum.  
-Note: check the wind shear for P25large, P100small, and P100large.
+Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
+the total radiative cooling the time evolution of the precipitation serves as a useful measure of whether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
+simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+The large oscillations in domain mean precipitation are similar to those noted in previous studies 
+(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
+mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
+of the differences in upper level cloud fraction and will be discussed further in a later section.
 
@@
 
-\subsection{The Influence of Domain Size on the LWCRE and the LS Parameterized Precipitation}
+\section{The Influence of Domain Size on the LWCRE and the LS Parameterized Precipitation: Change Title?}
 
@@
 range of values.  To simplify the analysis we have in most cases chosen to keep the 
-long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies (e.g. Bretherton et al. 2006) have 
+long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies (e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013) have 
 documented sensitivities to domain size.   The analysis of the previous, and of the next section focus on results from experiments using
@@
 narrow the region of deep convection (see Popp and Silvers, 2017, HH, Dixit et al. 2019.  etc.).
-The structure of the precipitation depends strongly on domain size and shows less dependence on grid-spacing.
+The structure of the precipitation changes more as a function of domain size than it does as a function of grid-spacing. 
 On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
@@
 Smaller domain lengths were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
-They also found less low-level clouds over the colder SSTs in the smaller domains, relative to a control domain size that was 4x
+They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
 larger.   We have found larger precipitation rates for the larger domains.  Does our larger domain ascent region change?
@@
 
-We hypothesize than an important difference between our simulations and previous studies which use GCMs
-is that although the deep and shallow convection is parameterized
-with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
-is much smaller in our simulations than it is for many GCM-type experiments with parameterized convection.   At 25km grid-spacing, 
-the majority of condensational heating occurs through the large-scale cloud  scheme.   See Figure \ref{fig:conv_vs_ls}.
-%Overall, the fraction of precipitation that is 
-%due to the large-scale scheme is roughly 40\%, and in many places it is actually greater than the amount of precipitation 
-%produced by the convection scheme.   
-%In comparison, many GCMs, have between 70\%-90\% of their precipitation produced by 
-%the convective parameterization.  
-There are further surprises in the fraction of precipitation that is large-scale.  On our small 
-domains, with a bowling alley domain length of 4000 km, the simulations with 100km grid-spacing have values of $f_{ls}$ 
-of $75-80\%$.  Often, at GCM-like resolutions such as 100km the convective precipitation would be expected to control much of the
-precipitation rather than the large-scale parameterization.  However, when the domain length is increased to 16000 km
-$f_{ls}$ decreases to a range of $0-70\%$ that depends strongly on location.  Over the warmest region of the surface the 
-precipitation is still dominated by the large-scale scheme.  However, turning off the longwave CRE leads to a dramatic reversal 
-in which $60-75\%$ of the precipitation is convective over the warmest SST.  The large domain without the longwave CRE is the 
-only configuration in which the convective precipitation is dominant.    If the default, or baseline, configuration of a GCM is built 
-with the expectation that the convective parameterization scheme will dominate the production of tropical precipitation, then 
-perhaps a configuration that minimizes the convective precipitation will result in a balance between the parameterization 
-schemes that is less intuitive, such as an asymmetric response to symmetric forcing.
+Although the domain mean total precipitation is constrained by the radiative cooling of the atmosphere, the amount of 
+precipitation that is produced by the convection scheme or the large-scale cloud scheme is not constrained. 
+The distribution of convective and large-scale precipitation can often give a hint of how the condensational heating
+in a GCM is being distributed among the parameterizations.  Precipitation from each of these two components is
+shown in Figure \ref{fig:conv_vs_ls}.  From this we can see that in the regions of large-scale ascent, most of the 
+precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE strongly influences the 
+large-scale precipitation but has a much weaker impact on the convective precipitation.  With the single exception 
+of the P100 LW CRE off experiment, the convective precipitation
+produces relatively little of the total precipitation for both resolutions and on both domains.
 
-Below is a list of several changes that occur when the LW CRE is off.  The points which have not already been discussed will be later in the paper.
+%We hypothesize than an important difference between our simulations and previous studies which use GCMs
+%is that although the deep and shallow convection is parameterized
+%with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
+%is much smaller in our simulations than it is for many GCM-type experiments with parameterized convection.   At 25km grid-spacing, 
+%the majority of condensational heating occurs through the large-scale cloud  scheme (Figure \ref{fig:conv_vs_ls}).
+%%Overall, the fraction of precipitation that is 
+%%due to the large-scale scheme is roughly 40\%, and in many places it is actually greater than the amount of precipitation 
+%%produced by the convection scheme.   
+%%In comparison, many GCMs, have between 70\%-90\% of their precipitation produced by 
+%%the convective parameterization.  
+%There are further surprises in the fraction of precipitation that is large-scale.  On our small 
+%domains, with a bowling alley domain length of 4000 km, the simulations with 100km grid-spacing have values of $f_{ls}$ 
+%of $75-80\%$.  Often, at GCM-like resolutions such as 100km the convective precipitation would be expected to control much of the
+%precipitation rather than the large-scale parameterization.  However, when the domain length is increased to 16000 km
+%$f_{ls}$ decreases to a range of $0-70\%$ that depends strongly on location.  Over the warmest region of the surface the 
+%precipitation is still dominated by the large-scale scheme.   The large domain without the longwave CRE is the 
+%only configuration in which the convective precipitation is dominant.    If the default, or baseline, configuration of a GCM is built 
+%with the expectation that the convective parameterization scheme will dominate the production of tropical precipitation, then 
+%perhaps a configuration that minimizes the convective precipitation will result in a balance between the parameterization 
+%schemes that is less intuitive, such as an asymmetric response to symmetric forcing.
 
-Turning the longwave cloud radiative interactions off tends to:
+Below is a list summarizing several of the changes that occur when the LW CRE is off.
+The points which have not already been discussed will be later in the paper.
+Turning the LW CRE interactions off tends to:
 
 \begin{itemize}
-  \item decrease the strength of the overturning circulation and the domain mean precipitation
+  \item decrease the strength of the overturning circulation and the domain mean precipitation (P100,P25,E25)
   \item increase the midtropospheric RH by $5-15 \% $
   \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
-  \item weaken the horizontally oriented low-level circulations.   This looks connected to a contracting of relative 
-           humidity maxima around 600 hPa.
+  \item weaken the horizontally oriented low-level circulations.   
   \item spread out in geographic space the precipitation maxima
-  \item dramatically homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
+  \item homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
   \item decrease both the LTS and the EIS, over both the warm and cold regions
-%  \item in most cases the symmetry about the SST maximum is increased.
   \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
@@
 circulation because it includes strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-clouds (Johnson et al. 1999) as well as stratocumulus cloud decks along the eastern extremities of the basin.
-Can we hope to simulate all of this in an idealized modeling context?    
-Our initial motivation for using the GFDL AM4 model on this doubly-periodic domain was to simulate this region 
+clouds (Johnson et al. 1999), as well as stratocumulus cloud decks along the eastern extremities of the basin.
+Can we hope to simulate all of this in a single idealized modeling context?    
+Our initial motivation for using the GFDL AM4 model on a doubly-periodic domain was to simulate this region 
 %that is rich in phenomena 
-in the context of both a GCM and a CRM in the hopes of learning something from the high resolution 
-cases that will help us to improve the development of the GCM.    
+in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
+would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
+interactions of the tropical Pacific.    
 The dynamical core of the current generation GFDL models is ideally suited to this task because it can easily 
@@
 A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that result from the 
-overturning circulation at different resolutions.  Shown are 180 days precipitation from the P25, E25, E2, and E1 simulations.  As the 
+overturning circulation at different resolutions.  Shown are 180 days of precipitation from the P25, E25, E2, and 
+E1 simulations.  As the 
 resolution increases towards $1 \, \rm{km}$ the distribution of precipitation becomes more regular and consistently 
-centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more variability at later 
-times, compared to these first 180 days.  The simulations with explicit convection at resolutions typical of cloud-resolving 
+centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more 
+variability at later 
+times, compared to these first 180 days.  The simulations with explicit convection at resolutions typical of 
+cloud-resolving 
 models (E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST and relative to 
@@
 
-Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
-the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
-simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
-The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
-mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
-of the differences in upper level cloud fraction and will be further discussed.
-
-Superposing the circulation and relative humidity illustrates the subsidence driven 
-drying and the strong moistening that results from ascent over the region of maximum latent heat flux.
-
 The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
@@
 Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
-surface enthalpy flux reveals large differences in the symmetry.  Over the SST maximum, E25 has a surface enthalpy flux that is 
+surface enthalpy flux reveals large differences in the symmetry.   Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
+the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
+without (thin lines) the LW CRE.  
+Over the SST maximum, E25 has a surface enthalpy flux that is 
 60 W/m2 larger than that of the E1 experiment, and the E1 experiment has a very irregular pattern of enthalpy flux in the middle
-half of the domain.  It appears that these differences in magnitude and regularity are due to the differing wind speeds at the 
-lowest atmospheric level.  It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
-with the E2 and E25 experiments.  Over the warm patch of SST, the surface enthalpy flux is decreased by the LWCRE for E25, 
-E2, and E1 despite these experiments having stronger low-level winds.  This decreased enthalpy flux also corresponds to 
-an increased amount of specific humidity in the lowest atmospheric model level.        
+half of the domain.  It appears that these differences in magnitude and regularity are due to the differing wind speeds among 
+the three experiments.  The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere
+and the E1 experiment also has the largest domain mean wind shear of the three models.  This is consistent with the 
+strong asymmetries of the P25 experiment being connected to a large domain mean wind shear in that experiment.  
+It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
+with the E2 and E25 experiments.  Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
+enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
+This decreased enthalpy flux also corresponds to an increased amount of specific humidity in the lowest atmospheric 
+model level.        
 %%%%%
@@
 
-\begin{figure}
-  \centering
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
-  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
-  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
-  while the P25 and P100 cases show only the first out of five years of the time series.}
-    \label{fig:precip_dom_mn}
-\end{figure}
+%\begin{figure}
+%  \centering
+%      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+%  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
+%  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
+%  while the P25 and P100 cases show only the first out of five years of the time series.}
+%    \label{fig:precip_dom_mn}
+%\end{figure}
 
@@
 Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
-fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by E25, P25, and 
-P100 (5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and require a correspondingly larger
-amount of condensational heating and precipitation.
+fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
+P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
+require a correspondingly larger amount of condensational heating and precipitation.
 
@@
 distribution of condensate is closely related to the distribution of clouds, it influences the distribution of energy throughout
-the atmosphere as well as influencing the outgoing longwave radiation.  It can also indicate the strength of convection 
+the atmosphere as well as the outgoing longwave radiation.  It can also indicate the strength of convection 
 and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
@@
 condensate.  The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
-regions of the CRM-like experiments.     
-It is also interesting to note that the LWCRE results in less condensate above 700 hPa for all experiments, and 
-more condensate below 700 hPa for the P25/E25 experiments.  The two-dimensional structure of circulation and humidity
-shows that the amount of condensate aloft in the deep-convective region increases with resolution while the relative
-humidity in the subsidence regions decreases with resolution.  This is consistent with an overturning circulation that 
-strengthens as the resolution increases.  When the clouds and radiation are allowed 
-to directly interact with each the E2 and E1 simulations appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}).   
-This dependence of circulation strength and moisture on resolution is especially 
-apparent when the LWCRE is off (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).
+regions of the CRM-like experiments.     It is also interesting to note that the LWCRE results in less condensate 
+above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
+
+The influence of resolution on the atmospheric state is clearly illustrated with the LW CRE off experiments shown 
+in Figure \ref{fig:rh_psi_P25E2E1_lwoff}.
+The two-dimensional structure of circulation and humidity shows that the amount of condensate aloft in the 
+deep-convective region and the range of relative
+humidity values between the ascent and descent regions increase with resolution.  It is also apparent in Figure
+\ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa decreases with increasing resolution.  
+This is consistent with an overturning circulation that 
+strengthens as the resolution increases.  Figure \ref{fig:rh_psi_P25E2E1_lwoff} also shows greater asymmetries 
+and generally weaker circulations below about 500 hPa.  
+When the clouds and radiation are allowed to directly interact with each other the E2 and E1 simulations 
+appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}).  The simulations with LW CRE also have a better
+organized and stronger circulation below 500 hPa.
 
@@
        %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
-       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
+       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft2.eps}
   \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
@@
 
-An interesting fact that emerges from the domain mean values of precipitation (see table 1) 
+An interesting fact that emerges from the domain mean values of precipitation (see Table 1) 
 is that the sign of the response to LWCRE is not the same across the different grid-spacings.
+When clouds are not allowed to interact with the longwave radiation the atmosphere can cool 
+much more efficiently, as evidenced by larger values of OLR for all experiments when the LWCRE is
+off.  Typically, the atmospheric cooling can be thought of as a proxy for the mean precipitation 
+because the cooling is primarily offset by condensational heating.  This is clearly not the case 
+for the E25, P25, and P100 cases for which the domain mean precipitation rates decrease despite
+an increased amount of atmospheric cooling.  The implication is that the requisite atmospheric 
+heating is coming from a process other than condensation.  The solution lies in the energy 
+budget of the surface.  A fixed SST means that in all cases the upward flux of longwave energy
+is constant, the upward flux of sensible heat flux will be mostly fixed (barring variations in surface
+wind), and changes in downward shortwave flux will not be able to warm the surface.  However, 
+the dramatic decrease of low-level clouds for the E25, P25, and P100 experiments when LWCRE is
+off strongly influences the net flux of longwave energy at the surface (does the downwelling longwave
+flux change becuase there are less clouds or because they are invisible to radiation?).  Under 
+natural conditions, the surface is warmed by a downward flux of longwave radiation due to the clouds
+above.  When this source of atmospheric energy loss is removed in the LWCRE off experiments 
+the upwelling longwave flux of radiation plays a larger role in warming the atmosphere that more 
+than compensates for the increased OLR.  Thus, with an increase in atmospheric warming on 
+the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off, there is less need for condensational heating and the 
+mean precipitation rate actually decreases.  The large decrease of low-level clouds also 
+leads to a large increase of downward shortwave radiation.  The only slightly increases the
+fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) but also contributes to 
+heating the atmosphere.
 Turning the LW CRE off for the E1 and E2 experiments results in more precipitation while, 
@@
 must be maintained through an increase of latent heating and subsequent increase of precipitation.  This is 
-reflected in table 1.  The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
+reflected in Table 1.  The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
 is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
-The low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  For 
+However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  For 
 GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
@@
     \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
-  \caption{Variables important to boundary layer energy fluxes.
-Top left panel shows the surface enthalpy flux ($\rm{W m^{-2}}$) and top right panel shows the equivalent potential temperature on the model level closest to the surface.
-The panel on bottom left shows the $u$ wind ($\rm{m s^{-1)}}$)
-  on the model level closest to the surface and the panel on bottom right shows the domain mean
-  $\rm{u}$ wind.}
-  \label{fig:LowLevelVars}
+    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
+    For all panels, thick lines show control experiments with the LW CRE on, thin lines show experiments
+    with the LW CRE off.}
+    \label{fig:enthalpy}
 \end{figure}
@@
 When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
-enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
+enthalpy flux (Figure \ref{fig:enthalpy}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
 large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
@@
   \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
-  \item much less vertical shear.  
+  %\item much less vertical shear.  
 \end{itemize}
@@
 subsidence dominates (although domain mean condensate is less when LWCRE is on.).
+
+It is remarkable that the control simulations (LW CRE on) have a precipitation rate  that can vary by as much as 
+20\% despite have have the same prescribed SST and incoming radiation.  The simulations also all have the same radiation,
+turbulence, large-scale cloud and microphysics parameterizations and all use the same dynamical core.
 

### 2019-10-14 Silvers_cfmip_draft.tex
a few minor changes to Silvers_cfmip_draft which will likely clash with the incoming version...

@@
 \begin{itemize}
-  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
-  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
-  maximum.}
-  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
-  changes in the low-level clouds and boundary layer structure.}
-  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
-  region that is 30\% higher than for the coarser cases with parameterized convection.}
-  \item{The mock-Walker Circulation is RCE plus an imposed gradient in surface temperature.  This is a simple design that 
-  incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.}
+  \item{The AM4.0 TOA cloud radiative effect shows small biases compared with CERES-EBAF observations, both versions 
+  2.8 and 4.1.}
+  \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
+  \item{Various configurations of a single global climate model lead to climate sensitivities that range from blah to about 5K.}
 \end{itemize}
 
-\section{introduction}
+\section{Introduction}
 
@@
 
+Can we shed lite on which particular component of the cloud feedbacks lead to large changes in the sensitivity?
+
 \section{Clouds in AM4.0: Comparison between amip and observations}
+
+During the developmental of the AM4.0 GFDL model particular care was given to ensuring that the energy budget at 
+the top of the atmosphere compared well with observations.  The data set that was most heavily leaned on to ensure 
+this was the CERES-EBAF TOA radiative fluxes, version 2.8.  Based on AM4.0 data that was used for the CMIP6 AMIP
+experiment, the total TOA flux bias is 989898, the bias in CRE 
+due to longwave radiative fluxes is $-2.4 \rm{W m^{-2}} $ and the bias due to CRE of the shortwave radiative fluxes   
+is $-1.1 \rm{W m^{-2}} $.  About the same time the AM4.0 development was frozen and the process of documentation 
+underway, the CERES-EBAF was updated to version 4.1.  When comparing the same AM4.0 AMIP experiment to the 
+newer version of CERES-EBAF data we find biases of $-2.2 \rm{W m^{-2}} $ for the longwave CRE and 
+$-2.9 \rm{W m^{-2}} $ for the shortwave CRE.   Should these biases be computed using only the AMIP years that 
+correspond to the CERES years?   As previously discussed (e.g. Kay et al., 2012) these longwave and shortwave CRE 
+biases are difficult to interpret because model developers often tune models to match particular CERES-EBAF data 
+sets despite the well known fact that different versions of the CERES-EBAF data lead to changes in the observed CRE of
+several $\rm{W m^{-2}}$.   Our aim in discussing this for AM4.0 is transparency in the model development process, as 
+well as to point out that both versions of the CERES-EBAF data show similar shortcomings of the spatial patters of the 
+simulated clouds  from AM4.0 in the AMIP experiment.
 
@@
 % figure generated with cloud_table_AM4fig.ncl
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs.eps}
-  \caption{Calipso scumstash}
+  \includegraphics[angle=90,width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs_vs_AM4.eps}
+  \caption{Calipso scumstash.  Black line shows meridional profiles of AM4.0 cloud fraction and blue line shows
+  the meridional profile from CALIPSO.}
   \label{fig:calipso_9pan}
@@
 
+The Cess sensitivity for AM4.0 ($0.57 \, \rm{K\, W^{-1} m^2}$, Z18b, pg 26) is closer to the Cess sensitivity 
+% see page 39 of Zhao et al. 2018 part 1 for discussion of Cess sensitivity.  
+of AM2.1 ($0.54 \, \rm{K\, W^{-1} m^2}$) than AM3.  This is partly due to the method of converting convective cloud condensate to precipitation 
+in the convection scheme.   Z18b on the same page describes a Cess sensitivity with AM4.0 when the drop number
+is fixed of ($0.52 \, \rm{K\, W^{-1} m^2}$).  As discussed in Z18b and Winton et al. 2019, despite a Cess sensitivity similar to AM2.1, 
+the TCR and ECS of CM4.0 are larger than those of CM2.1, and close to those of CM3.   This clearly 
+shows that using the Cess sensitivity to infer the TCR or ECS is not reliable (does not work).   Is the ratio of TCR to
+Cess sensitivity useful?
+
 \begin{figure}

### 2019-10-14 Silvers_Schubert_LLJ.tex

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% this is the version Modified on 1-27-2012 and then sent to Wayne 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% The following two commands will generate a PDF that follows all the requirements for submission
% and peer review.  Uncomment these commands to generate this output (and comment out the two lines below.)
%
% DOUBLE SPACE VERSION FOR SUBMISSION TO THE AMS
\documentclass[12pt]{article}
\usepackage{ametsoc}
\usepackage{lineno}
\linenumbers
%
% The following two commands will generate a single space, double column paper that closely
% matches an AMS journal page.  Uncomment these commands to generate this output (and comment
% out the two lines above. FOR AUTHOR USE ONLY. PAPERS SUBMITTED IN THIS FORMAT WILL BE RETURNED
% TO THE AUTHOR for submission with the correct formatting.
%
% TWO COLUMN JOURNAL PAGE LAYOUT FOR AUTHOR USE ONLY
%%%%\documentclass[10pt]{article}
%%%%\usepackage{ametsoc2col}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ABSTRACT
%
% Enter your Abstract here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\myabstract}{The subject of this study is topographically bound low level jets, such 
as the South American summertime low level jet on the east side of the Andes 
and its companion, the Chilean low level jet on the west side of the Andes. 
These jets are interpreted as balanced flows that obey the potential vorticity 
invertibility principle. This invertibility principle is expressed in 
isentropic coordinates, and the mathematical issue of isentropes that intersect 
the topography is treated by the method of a massless layer. In this way, the 
low level jets on the west and east sides of the Andes can both be attributed to 
the infinite potential vorticity that lies in the infinitesimally thin massless 
layer on the topographic feature. To obtain a cyclonic flow centered on the 
topographic feature, the mountain crest must have been heated enough to draw 
down the overlying isentropic surfaces; otherwise, isentropic surfaces bend
upward at the mountain crest and an anticyclonic flow is produced. Both 
anticyclonic and cyclonic solutions are obtained here using analytical and 
numerical methods to solve the invertibility principle. The summertime, 
topographically bound flows discussed here are quite distinct from the 
wintertime Rossby wavetrain patterns that occur when strong westerlies impinge 
on the topography. 
}
%
\begin{document}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TITLE
%
% Enter your TITLE here
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\textbf{\large{A Theory of Topographically Bound Balanced Motions 
                      and Application to Atmospheric Low-Level Jets}}}
%
% Author names, with corresponding author information. 
% [Update and move the \thanks{...} block as appropriate.]
%
\author{\textsc{Levi G. Silvers}
				\thanks{\textit{Corresponding author address:} 
				Levi Silvers, Colorado State University, 
				Fort Collins, CO 80523. 
				\newline{E-mail: levi@atmos.colostate.edu}}\quad\textsc{and Wayne H. Schubert}\\
\textit{\footnotesize{Colorado State University, Fort Collins, Colorado}}
\and 
%\centerline{\textsc{Extra Author}}\\% Add additional authors, different insitution
%\centerline{\textit{\footnotesize{Affiliation, City, State/Province, Country}}}
}
%
% Formatting done here...Authors should skip over this.  See above for abstract.
\ifthenelse{\boolean{dc}}
{
\twocolumn[
\begin{@twocolumnfalse}
\amstitle

% Start Abstract (Enter your Abstract above.  Do not enter any text here)
\begin{center}
\begin{minipage}{13.0cm}
\begin{abstract}
	\myabstract
	\newline
	\begin{center}
		\rule{38mm}{0.2mm}
	\end{center}
\end{abstract}
\end{minipage}
\end{center}
\end{@twocolumnfalse}
]
}
{
\amstitle
\begin{abstract}
\myabstract
\end{abstract}
\newpage
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% MAIN BODY OF PAPER
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}

     South American mean January 2003 winds at 925 mb are shown in Fig.~1. 
A striking feature is the strong cyclonic flow centered on the Andes.  
The South American low-level jet (SALLJ) is evident in the northerly flow 
east of the Andes, while the Chilean coastal low-level jet is evident in the
southerly flow over the eastern Pacific Ocean.  These Southern Hemisphere 
low level jets are analogous to the summertime 
low level jets around the mountainous regions of North America, i.e., the 
Great Plains low level jet (GPLLJ) and the California coastal low level jet.

     Figures 2 and 3 show east-west cross sections of the mean meridional 
wind fields and the mean isentropes observed during the Year of Tropical 
Convection (YOTC).  These are two-month mean warm season wind fields averaged using the 
times 00, 6, 12, and 18 UTC.  The 
resolution of these ECMWF analysis fields is $0.5^{\circ}\times 0.5^{\circ}$ 
with 11 irregularly spaced vertical levels.  The YOTC analysis is available for the two 
year period between May 2008 and April 2010.  Although originally proposed to be 
a one year research program YOTC was extended for an additional year in order to 
capture a cycle of both La Nina and El Nino.  Wind fields around 
the Andes are shown at 21S and 30S.  The SALLJ often maximizes near 20S, 
while, as seen in Fig.~2, the coastal LLJ is stronger farther south. Cross 
sections of the wind fields around the Rocky Mountains are shown at 30N and 35N.  
The GPLLJ maximizes at about 25N, but as seen in Fig.~3, it is still quite
strong at 30N and 35N.  Due to 
the relatively cold eastern Pacific, the coastal LLJs tend to have a wind 
maximum that is closer to the surface than the jets to the east of 
the mountain ranges. The coastal jets are also broader than the 
plains jets because of the influence of the Pacific anticyclonic 
circulations to the west. Isentropes are generally drawn down over the 
mountain ranges, thereby intersecting the Earth's surface along
the sides and crests of the mountains.   
It should be noted that, on individual days, these low level jets can be 
considerably stronger than shown on two-month mean cross sections. 
For example, Vera et al.~(2006, their Fig.~8b) show a specific SALLJ 
event in February 2003 with a maximum wind of 25 m s$^{-1}$ at a height 
of 800-700 hPa.  
The cyclonic motion centered on the mountain 
ranges is the most obvious feature of the wind fields in these figures.  The 
North American Regional Reanalysis also clearly shows a dominant 
cyclonic circulation (see Jiang et al. 2007, their Fig.~1) over the Rocky Mountains.

One of the first climatologies of LLJs was given by Bonner (1968), along with an often 
used set of wind shear criteria to define LLJs.   Stensrud (1996) provided a
review of LLJs and in particular, their significant influence on the global climate.  
An excellent review 
of the literature relevant to LLJs and analysis of the dynamical mechanisms that have been 
historically proposed to explain the existence and variability of LLJs was given by Jiang et al. 2007.
Much of the previous research on LLJs can be loosely grouped into two categories.  
The first includes boundary layer processes and forcing on relatively short (diurnal-a few 
days) times scales.  Relevant studies include Blackadar (1957), Holton (1967), Jiang 
et al. (2007), and Rife et al. (2010).  These studies were particularly interested in 
determining the physical mechanisms behind the diurnal oscillation and the phase that 
is observed in many LLJs.  The second category deals mostly with the synoptic-scale, 
monthly or seasonal mean structure of LLJs and includes studies such as Wexler (1961), 
Byerle and Paegle (2002, 2003), and Ting and Wang (2006).  These two groups certainly 
have some overlap.  The research presented here examines the influence of 
topographically bound balanced motions on the synoptic-scale, warm season mean structure of LLJs.

    The theoretical study most relevant to the present work is that of 
Eliassen (1980), who investigated the steady, topographically bound, balanced 
response of a rotating, stratified fluid to orography. Although Eliassen did 
not specifically apply his theory to LLJs, his results provide 
physical insight into the dynamical characteristics of these phenomena.  
Eliassen defined isentropic obstacles as those for which  
the lowermost isentrope continuously follows the geopotential surface.  
A non-isentropic obstacle is one whose geopotential surface punctures 
the lowermost isentropes. Eliassen showed that solutions of the potential 
vorticity invertibility principle for an isentropic ridge were only possible 
if the height of that ridge did not exceed a critical value. This `subcritical 
ridge' case is illustrated by the left panel of Fig.~4, which shows that   
the isentropes are compressed as they bend up over the 
mountain crest, thereby producing a balanced anticyclonic flow above the crest. 
If the `critical crest height' is exceeded, the ridge must 
puncture the lowermost isentropes. Two other cases not investigated by 
Eliassen are shown in the middle and right panels of Fig.~4.           
The middle panel shows a surface of constant geopotential that has 
been locally heated. In this case the isentropes bend downward and a 
balanced, cyclonic flow is produced.  
The surface potential temperature anomaly shown in the center panel of Fig. 4 represents 
a similar balanced flow structure as those studied by Thorpe (1986).  His work examined 
synoptic disturbances in gradient wind balance, this study looks at synoptic disturbances in 
geostrophic balance.  A combination of the two cases 
shown in the left and middle panels results in the heated obstacle shown 
in the right panel. Obviously, the right panel is the case most relevant 
to the observations shown in Figs.~2 and 3.

    The purpose of the present paper is to extend the analysis of Eliassen to 
include all three cases shown in Fig.~4, and to thereby demonstrate that many LLJs 
can be interpreted as balanced flows attributed, through the potential 
vorticity invertibility principle, to the infinite potential vorticity 
that resides in the massless layer over locally heated topography 
such as illustrated in the right panel of Fig.~4. 
A complete potential vorticity based analysis of LLJs would have to include both the 
potential vorticity at the surface that results from a gradient of potential temperature 
and the potential vorticity of the interior flow.  The surface component is related to 
radiative heating and the atmospheric stratification while the interior component 
is due to convective activity, absolute vorticity, or the stratification.  The interaction 
between the interior quasigeostrophic potential vorticity and the surface gradient of 
potential temperature was reviewed by Hoskins et al. (1985).  A nongeostrophic 
generalization was applied to a wake circulation on the lee side of a mountain by 
Schneider et al. (2003).  We here focus on the surface potential vorticity.  We do not 
assume that the affect of the surface potential vorticity is greater than that of the 
interior potential vorticity, we are simply demonstrating that LLJs are impacted 
by this surface potential vorticity.
The outline of the paper 
is as follows. Section 2 presents the $f$-plane invertibility principle in 
isentropic coordinates.  Section 3 derives analytical solutions for the  
subcritical isentropic ridge case. An analytical formula for the critical 
crest height is then derived.  The analytical methods used in section 3 
yield closed form solutions only in cases where there is no massless 
layer (i.e., the lower boundary is an isentropic surface). In order to compute 
the wind and mass fields that result from locally heated lower boundaries,  
section 4 solves the invertibility principle using a finite-difference 
approximation.  An analysis is then made of the results and how they 
compare to observations of LLJs.  Concluding remarks, including a discussion 
of a generalization from $f$-plane theory to the sphere, are given in section 5.

\section{Invertibility principle}          %%%%%%%%%   Section 2   %%%%%%%%%%%%%%

     Consider hydrostatic, geostrophic, $y$-independent motions of a compressible 
stratified fluid on an $f$-plane. Using the potential temperature $\theta$ 
as the vertical coordinate, the potential vorticity is given by 
\begin{linenomath*}
\begin{equation}                        % Equation (1)
        P = \left(f + \frac{\partial v}{\partial x}\right)
	    \left(-\frac{1}{g}\frac{\partial p}{\partial\theta}\right)^{-1},  
\end{equation} 
\end{linenomath*}
with $f$ denoting the constant Coriolis parameter, $g$ the acceleration of 
gravity, $v(x,\theta)$ the meridional component of the geostrophic flow, 
and $p(x,\theta)$ the pressure. Expressing the density by 
$\rho=p/(RT)=c_p p/(R\theta\Pi)$, it is easily shown that 
$\theta\rho(d\Pi/dp)=1$, where $\Pi=c_p(p/p_0)^{R/c_p}$, 
with $p_0$ denoting the constant reference pressure, 
$R$ the gas constant, and $c_p$ the specific heat at constant pressure. 
This allows (1) to be written in the form 
\begin{linenomath*}
\begin{equation}                       % Equation (2)
    \frac{g}{\theta\rho P}\frac{\partial(v+fx)}{\partial x}
                        + \frac{\partial\Pi}{\partial\theta} = 0.   
\end{equation} 
\end{linenomath*}
Using the geostrophic relation $fv=(\partial M/\partial x)$ and 
the hydrostatic relation $\Pi=(\partial M/\partial\theta)$, where 
$M=\theta\Pi+\phi$ is the Montgomery potential and $\phi$ is the 
geopotential, we can write the thermal wind relation in the form 
\begin{linenomath*}
\begin{equation}                       % Equation (3)
       f\frac{\partial v}{\partial\theta} 
      - \frac{\partial\Pi}{\partial x} = 0.   
\end{equation} 
\end{linenomath*}

With proper boundary conditions and with $P(x,\theta)$ specified, 
(2) and (3) constitute an invertibility problem for the unknown 
functions $v(x,\theta)$ and $\Pi(x,\theta)$.  
Because of the dependence of $\rho$ on $\Pi$, (2) is nonlinear. However, 
the nonlinearity is weak, and for the analytical solutions 
presented in section 3, it will be removed by replacing $\rho(x,\theta)$ 
with the specified far-field profile $\tilde{\rho}(\theta)$. For the 
numerical solutions presented in section 4, this nonlinearity will 
be retained.

\section{Analytical solution for the case of an isentropic mountain}   
 %%%%  Section 3  %%%%

     For the analytical results presented in this section it is preferable 
to work with deviations from the far-field values. In the far-field the flow 
vanishes, and the pressure and potential vorticity take on the horizontally 
homogeneous values $\tilde{p}(\theta)$ and $\tilde{P}(\theta)$, which are 
related by 
 \begin{linenomath*}
\begin{equation}                       % Equation (4)
     \tilde{P} = f\left(-\frac{1}{g}\frac{\partial\tilde{p}}{\partial\theta}\right)^{-1}. 
\end{equation}
 \end{linenomath*}
Denoting the far-field density by $\tilde{\rho}(\theta)$, it is easily shown 
that $\theta\tilde{\rho}(d\tilde{\Pi}/d\tilde{p})=1$, where 
$\tilde{\Pi}=c_p(\tilde{p}/p_0)^{R/c_p}$. This allows (4) to be written in the form 
\begin{linenomath*}
\begin{equation}                      % Equation (5)
        \frac{gf}{\theta\tilde{\rho}\tilde{P}}
      + \frac{\partial\tilde{\Pi}}{\partial\theta} = 0.   
\end{equation} 
\end{linenomath*}
Taking the difference of (2) and (5), we obtain 
\begin{linenomath*}
\begin{equation}                      % Equation (6)
        \frac{\tilde{\rho}\tilde{P}}{\rho P}\frac{\partial v}{\partial x} 
      + \left(\frac{f\theta^2N^2}{g^2}\right)
        \frac{\partial\Pi'}{\partial\theta} = f\left(1 - \frac{\tilde{\rho}\tilde{P}}{\rho P}\right),  
\end{equation} 
\end{linenomath*}
where $\Pi'(x,\theta)=\Pi(x,\theta)-\tilde{\Pi}(\theta)$ is the Exner function anomaly, 
and where the buoyancy frequency $N(\theta)$ is defined by 
\begin{linenomath*}
\begin{equation}                      % Equation (7)
    N^2(\theta) = \frac{g^2}{\theta^2}\left(-\frac{d\tilde{\Pi}}{d\theta}\right)^{-1}.  
\end{equation} 
\end{linenomath*}

    In the analysis of this section, four simplifying assumptions are made: (i) the lower 
boundary is assumed to be an isentropic surface;  (ii) the factors $(\tilde{\rho}/\rho)$ 
in (6) are approximated by unity; (iii) on each isentropic surface the potential 
vorticity $P$ is assumed to be equal to its far-field value $\tilde{P}$, so that the 
right hand side of (6) vanishes and the coefficient of $(\partial v/\partial x)$ 
becomes unity; (iv) the reference state buoyancy frequency 
$N(\theta)$ is assumed to be inversely proportional to $\theta$, i.e., 
$N(\theta)=N_B \theta_B/\theta$, where $N_B$ and $\theta_B$ are constants, 
which results in a constant coefficient for the second term in (6).    
Assumptions (i), (ii), and (iv) will be relaxed in section 4. The relaxation 
of assumption (i) will prove crucial for the simulation of topographically bound 
cyclonic flows such as those illustrated in Figs.~1--3.

    For the particular reference state $N(\theta)=N_B \theta_B/\theta$, 
the definition (7) can be integrated to obtain 
\begin{linenomath*}
\begin{equation}                    % Equation (8)
   \tilde{\Pi}(\theta) = c_p - \frac{g^2}{\theta_B^2 N_B^2}\left(\theta - \theta_B\right), 
\end{equation}
\end{linenomath*}
where $\tilde{p}(\theta_B)=p_0$.  The reference state hydrostatic equation $d\tilde{M}/d\theta=\tilde{\Pi}$ 
can then be integrated to obtain 
\begin{linenomath*}
\begin{equation}                    % Equation (9)
   \tilde{M}(\theta) = c_p \theta - \frac{g^2}{2\theta_B^2 N_B^2}
                             \left(\theta - \theta_B\right)^2,
\end{equation}
\end{linenomath*}
where we have assumed $\tilde{\phi}(\theta_B)=0$.
Since $\tilde{\phi}(\theta)=\tilde{M}(\theta)-\theta\tilde{\Pi}(\theta)$, we can 
use (8) and (9) to obtain 
\begin{linenomath*}
\begin{equation}                    % Equation (10)
   \tilde{\phi}(\theta) = \frac{g^2}{2\theta_B^2 N_B^2}\left(\theta^2 - \theta_B^2\right). 
\end{equation}
\end{linenomath*}

The relationship of pressure and potential temperature for the reference 
state, as determined from (8), is plotted in Fig.~5, where we have chosen 
$c_p=1004.5$ J kg$^{-1}$ K$^{-1}$, $g=9.8$ m s$^{-2}$, $\theta_B=295$K, 
and $(\theta_B/g)N_B^2=5.1373$ K km$^{-1}$.  This choice of $\theta_B$ 
and $N_B$ results in a profile with $\tilde{p}(\theta)=150$ hPa at $\theta=360$ K. 
The associated value of $N_B$ is $1.3064 \times 10^{-2}$ s$^{-1}$ and $\theta_T=360$K
is used throughout this study. 
Although idealized, this profile can be considered typical of the 
subtropics in the warm season.

     With the four simplifying assumptions listed above, the Cauchy-Riemann conditions 
(6) and (3) simplify to (11) and (12) below. We shall require that (11) and 
(12) hold in a region that includes an underlying 
topographic feature whose geopotential is specified by $\phi_S(x)$.  
As for boundary conditions, we require that 
$v$ and $\Pi'$ approach zero in the far-field, which is expressed in (13). 
We also require that the upper boundary is both an isentropic ($\theta=\theta_T$) 
and isobaric surface, which is expressed as (14). 
To formulate the lower boundary condition we combine the $x$-derivative of 
$M-\theta\Pi=\phi$ with the geostrophic and hydrostatic relations to obtain 
$f[v-\theta(\partial v/\partial\theta)]=(\partial\phi/\partial x)$, which, 
when applied at $\theta=\theta_B$ yields (15). In summary, the elliptic problem is 
\begin{linenomath*}
\begin{equation}                    % Equation (11)
        \frac{\partial v}{\partial x} 
      + \left(\frac{f\theta_B^2 N_B^2}{g^2}\right)
        \frac{\partial \Pi'}{\partial\theta} = 0, 
\end{equation} 
\end{linenomath*}
\begin{linenomath*}
\begin{equation}                    % Equation (12)
       f\frac{\partial v}{\partial\theta} 
      - \frac{\partial\Pi'}{\partial x} = 0,  
\end{equation} 
\end{linenomath*}
with boundary conditions
\begin{linenomath*} 
\begin{equation}                     % Equation (13)
        v \to 0 \,\,\, {\rm and}  \,\,\,   \Pi' \to 0   \,\,\,  {\rm as} \,\,\,   x \to \pm\infty,  	
\end{equation}           
\end{linenomath*}
\begin{linenomath*}
\begin{equation}	             % Equation (14)
        \Pi' = 0                \,\, {\rm at} \,\,\, \theta = \theta_T, 
\end{equation}
\end{linenomath*}
\begin{linenomath*}
\begin{equation}                     % Equation (15)            
        f\left(v - \theta\frac{\partial v}{\partial\theta}\right) = \frac{d\phi_S(x)}{dx}    
	                       \,\, {\rm at} \,\,\, \theta = \theta_B.          
\end{equation} 
\end{linenomath*}
This elliptic problem can be solved using Fourier integral transforms.  The details can be 
found in the appendix.
For all the calculations presented in this paper  
we have chosen the geopotential on the lower boundary as 
\begin{linenomath*}
\begin{equation}                           % Equation (16)
   \phi_S(x) = gH e^{-x^2/a^2},  
\end{equation} 
\end{linenomath*}
where the constants $H$ and $a$ respectively specify the mountain height and width. Using (A9), (A10), and (A11) in (A2) and (A4), we obtain 
\begin{linenomath*}
\begin{equation}                    % Equation (17)
    v(x,\theta) = -\frac{gHa}{f\sqrt{\pi}}\int_0^\infty  k e^{-a^2 k^2/4}
                \left(\frac{e^{-\kappa(\theta-\theta_B)} + e^{-\kappa(2\theta_T-\theta_B-\theta)}}
		 {1 + \kappa\theta_B + (1 - \kappa\theta_B)e^{-2\kappa(\theta_T-\theta_B)}}\right)\sin(kx) \, dk,   
\end{equation}  
\end{linenomath*}

\begin{linenomath*}
\begin{equation}                    % Equation (18)
    \Pi'(x,\theta) = -\frac{g^2Ha}{f\theta_B N_B\sqrt{\pi}} \int_0^\infty k e^{-a^2 k^2/4}
                \left(\frac{e^{-\kappa(\theta-\theta_B)} - e^{-\kappa(2\theta_T-\theta_B-\theta)}}
	         {1 + \kappa\theta_B + (1 - \kappa\theta_B)e^{-2\kappa(\theta_T-\theta_B)}}\right)\cos(kx) \, dk.    
\end{equation}  
\end{linenomath*}

Equations (17) and (18) are the Fourier integral representations of the 
solutions to the invertibility problem (11)--(15). Plots of the solutions 
$v(x,\theta)$ and $\Pi'(x,\theta)$ are easily constructed through numerical 
evaluation of the Fourier integrals at each point of an array of points in 
$(x,\theta)$-space. In the construction of several of the figures shown here, 
we have chosen to display isolines of $v$ and $\theta$ in $(x,p)$-space  
in addition to isolines of $v$ and $p$ in $(x,\theta)$-space. Conversion between 
these two representations is simply a matter of interpolation.

     Figure 6 shows a plot of the solutions $v(x,p)$ and $\theta(x,p)$ for 
$f=7.3\times 10^{-5}$ s$^{-1}$, $a=500$ km, and $H=1500$ m. Figure 7 shows a similar 
plot with $H=2500$ m. As can be seen from Fig.~7, when $H=2500$ m the layer 
$295 \le \theta \le 296$ K is almost massless near the mountain crest. In fact, 
for $H$ greater than 2560 m, this layer does become massless at the mountain crest. 
In other words, for this particular mountain shape and far-field reference state, 
the critical crest height is approximately $H_{\rm crit}=2560$ m.  Following an 
argument similar to that of Eliassen (1980), a formula for the critical height 
can be obtained as follows. When $H=H_{\rm crit}$, 
$(\partial\Pi/\partial\theta)=(\partial\tilde{\Pi}/\partial\theta)+(\partial\Pi'/\partial\theta)=0$ 
at the crest, or equivalently, using (8),  
\begin{linenomath*}
\begin{equation}                           % Equation (30)
      \frac{\partial\Pi'}{\partial\theta} = \frac{g^2}{\theta_B^2 N_B^2}
          \,\,\, {\rm at} \,\,\, x=0 \,\,\, {\rm and} \,\,\, \theta=\theta_B.   
\end{equation} 
\end{linenomath*}
Using (29) for $\Pi'$, with $H$ replaced by $H_{\rm crit}$, we can rewrite (30) as 
\begin{linenomath*}
\begin{equation}                          % Equation (31)
    H_{\rm crit} = \frac{fa}{N_B I(a)},  	
\end{equation} 
\end{linenomath*}
where  
\begin{linenomath*}
\begin{equation}                          % Equation (32)
    I(a) = \frac{1}{\sqrt{\pi}} \int_0^\infty  
                    \left(\frac{\hat{a}^2 \hat{\kappa}^2
		   \left\{1 + \exp[-2\hat{\kappa}(\theta_T-\theta_B)/\theta_B]\right\}} 
		           {1 + \hat{\kappa} + (1 - \hat{\kappa}) 
	                      \exp[-2\hat{\kappa}(\theta_T-\theta_B)/\theta_B]}\right) 
			    \exp\left(-\hat{a}^2\hat{\kappa}^2/4\right) \, d\hat{\kappa}, 	
\end{equation} 
\end{linenomath*}
with $\hat{a}=(fN_B/g)a$ denoting the dimensionless mountain width and with 
$\hat{\kappa}=\kappa\theta_B$. Figure 8 shows $H_{\rm crit}$ as a function 
of $a$ for five different values of $f$. These results indicate that broad mountains 
can be relatively high but still below the critical crest height.  They also indicate that the crest 
height of the central Andes is supercritical.

     In concluding this section we note that the wind and mass fields 
displayed in Figs.~6 and 7 can also be interpreted as solutions of 
the following geostrophic adjustment problem (Eliassen 1980).   
Initially, a stably stratified fluid is in a state of rest over 
a level bottom surface on an $f$-plane. Over some arbitrary time 
interval, the bottom topography is raised to its final shape and 
any transient inertia-gravity waves are allowed to disperse away. 
The final adjusted wind and mass fields are then determined via the 
potential vorticity invertibility principle (11)--(15), with the 
bottom topography appearing in the lower boundary condition of this 
invertibility principle. If the crest height of the topography is 
not raised above the critical value, the lowest isentropic surface 
remains attached to the topography. However, if the crest of the 
topography is raised above the critical value, the topography punctures 
the lowest isentropic surfaces, so that potential temperature now varies 
along the lower boundary. In either case, the flow around the obstacle 
is anticyclonic, a result of Coriolis turning of fluid that flows 
away from the rising mountain crest. This anticyclonic, topographically 
bound, balanced flow is not useful for describing cyclonic 
flows such as those shown in Figs.~1--3. Thus, in the  
next section we consider the related problem of the balanced wind 
and mass fields near a topographic feature that has been heated 
by radiative processes, resulting in a cyclonic flow around the obstacle. 
This will allow us to interpret the South American low level jet 
and the Chilean low level jet as parts of the topographically bound 
motion associated with the PV anomaly produced by solar heating of the Andes.

\section{Numerical solution for the case of a nonisentropic lower boundary}   %%%  Section 4  %%%

     The analytical solutions discussed in section 3 are for the special 
case in which the topographic surface is also an isentropic surface. 
When isentropic surfaces intersect the topographic surface, they can 
be considered to run just under the topographic surface with a pressure 
equal to the surface pressure, thereby forming a massless layer with 
infinite potential vorticity 
(i.e., $\partial p/\partial\theta \to 0$ and $P \to \infty$). 
Lorenz (1955) was the first to define such a massless layer just under the surface 
of the ground.  The inhomogenous potential temperature at a boundary was also 
treated by Bretherton (1966).  His approach was different from that of Lorenz in that 
Bretherton showed that a potential temperature gradient along a boundary could 
be replaced by a boundary with constant potential temperature provided a 
concentration of potential vorticity very close to the surface is included.  Bretherton’s 
conception of the massless layer was used by Hoskins et al. (1985), Thorpe (1985, 1986), and 
Schneider et al. (2003).  The approach of Lorenz was used by Andrews (1983), 
Fulton and Schubert (1991), and Schneider (2005).  Both approaches are equally 
valid and here we choose to follow the convention defined by Lorenz.
The isentropic surface that is just below the earth's surface 
over the topographic feature and is at the earth's surface in the 
far-field is labeled $\theta=\theta_B$. Then, defining $\theta_S(x)$ as 
the value of potential temperature on the topographic surface,  
the region $\theta_B < \theta < \theta_S(x)$ is the massless layer. 
When there is a massless layer, the $1/P$ factor 
in the first term of (2) takes on the value of zero (i.e., $P \to \infty$) 
in the massless layer. This introduces a variable coefficient effect that 
removes the advantages of using Fourier transforms. Thus, in this section, 
we solve a discretized (finite difference) version of the invertibility 
problem using an iterative method. In particular, we shall obtain solutions 
for the second and third cases shown schematically in Fig.~4.

     When the invertibility principle is solved using finite difference methods  
rather than Fourier transform methods, it is unnecessary to separate the fields 
into a far-field part and a deviation part, as was done in section 3.  
Thus, returning to (2) and making use of the geostrophic  
relation $fv=(\partial M/\partial x)$ and the hydrostatic relation  
$\Pi=(\partial M/\partial\theta)$, we obtain (33) below, where the 
density $\rho$ is given in terms of $M$ by (34). Note that the appearance 
of $\rho$ (as opposed to $\tilde{\rho}$) in the top line of (33) retains 
the previously discussed weak nonlinearity, which is easily incorporated 
into the iterative method. The top line of (33) holds above the 
massless layer, while in the massless layer $P \to \infty$ and the top 
line reduces to the bottom line of (33). To obtain the lateral 
boundary conditions (35) we have assumed that the far-field (i.e., $x=\pm L$)  
value of $M$ is equal to the specified function $\tilde{M}(\theta)$.  
To obtain the upper boundary condition (36) we have assumed that the 
upper isentropic surface ($\theta = \theta_T$) is also an isobaric surface
with a constant Exner function $\Pi_T$.  To formulate the lower boundary 
condition (37) we have applied the general relation 
$M-\theta(\partial M/\partial\theta)=\phi$ at $\theta=\theta_B$.   
In summary, the elliptic problem is 
\begin{linenomath*}
\begin{equation}                          % Equation (33)
   \begin{split}
        \frac{g}{f\theta\rho P}
        \left(f^2 + \frac{\partial^2 M}{\partial x^2}\right) 
     &+ \frac{\partial^2 M}{\partial\theta^2} = 0  
              \,\,\,\, {\rm for} \,\,\,\, \theta_S(x) < \theta \le \theta_T,  \\
     &  \frac{\partial^2 M}{\partial\theta^2} = 0  
	      \,\,\,\, {\rm for} \,\,\,\,   \theta_B \le \theta < \theta_S(x),
   \end{split}
\end{equation} 
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                         % Equation (34)
   \rho = \frac{p_0}{R\theta}                             
         \left(\frac{1}{c_p}\frac{\partial M}{\partial\theta}\right)^{c_v/R},     
\end{equation} 
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                         % Equation (35)
                M = \tilde{M}(\theta)             \,\,\, {\rm at} \,\,\,   x = \pm L,    
\end{equation}
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                         % Equation (36)
        \frac{\partial M}{\partial\theta} = \Pi_T  \,\, {\rm at} \,\,\, \theta = \theta_T, 
\end{equation}
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                         % Equation (37)
        M - \theta\frac{\partial M}{\partial\theta} = \phi_S(x)    
	                                         \,\, {\rm at} \,\,\, \theta = \theta_B,          
\end{equation}
\end{linenomath*}
where $c_v=c_p-R$ is the specific heat at constant volume.

     To solve (33)--(37) for $M(x,\theta)$, we must specify the constants $\theta_B$, 
$\theta_T$, $\Pi_T$, $L$, and the functions $P(x,\theta)$, $\theta_S(x)$ $\phi_S(x)$, 
and $\tilde{M}(\theta)$.  In section 3 we assumed that $\theta_S(x)$ was equal to 
the constant $\theta_B$, so there was no massless layer. We also assumed that 
$P(x,\theta)=\tilde{P}(\theta)$, so the potential vorticity did not vary along 
$\theta$-surfaces. With these assumptions, the interior anticyclonic flow was 
determined entirely by $\phi_S(x)$ and $\tilde{M}(\theta)$.

     Now consider the more 
general case where $\theta_S(x) \ne \theta_B$, $\phi_S(x) \ne 0$, 
$P(x,\theta)=\tilde{P}(\theta)$ for $\theta_S(x) < \theta \le \theta_T$, 
but $P(x,\theta) \to \infty$ for $\theta_B \le \theta < \theta_S(x)$. In 
this case there is a massless layer on the mountain slope.  However, even 
in this case there is a resting, horizontally homogeneous solution if the 
functions $\theta_S(x)$, $\phi_S(x)$, and $\tilde{M}(\theta)$ are specified 
in a particular way. This particular specification can be obtained by simply 
noting that $M(x,\theta)=\tilde{M}(\theta)$ for 
$\theta_S(x) \le \theta \le \theta_T$ is a resting solution. The Exner function 
and the geopotential associated with this solution are 
$\Pi(x,\theta)=\tilde{\Pi}(\theta)$ and $\phi(x,\theta)=\tilde{\phi}(\theta)$. 
If this geopotential field is to match the topography, we must have  
\begin{linenomath*}
\begin{equation}                             % Equation (38)
       \phi_S(x) = \tilde{\phi}(\theta_S(x)).  
\end{equation}
\end{linenomath*}
In other words, if $\phi_S(x)$, $\theta_S(x)$, and $\tilde{\phi}(\theta)$ 
are specified in such a way that (38) is satisfied, the solutions of the 
elliptic problem (33)--(37) are $v(x,\theta)=0$ and 
$\Pi(x,\theta)=\tilde{\Pi}(\theta)$ for $\theta_S(x) \le \theta \le \theta_T$. 
For the far-field profile specified by (10) and the Gaussian mountain 
specified by (26), the constraint (38) can be rearranged to 
\begin{linenomath*}
\begin{equation}                            % Equation (39)
   \theta_S(x) = \theta_B \left(1 + \frac{2N^2 H}{g} e^{-x^2/a^2}\right)^{1/2}. 
\end{equation}
\end{linenomath*}
This can serve as a useful check on any numerical procedure for solving 
(33)--(37).  This case is shown in Fig.~9.  It is interesting to note that the wind field in the massless 
layer does not vanish.  The wind field in the massless layer will not, in general 
vanish.

     To discretize the problem (33)--(37) we introduce the grid points 
$(x_j,\, \theta_k)=(-L+j\Delta x,\, \theta_B+k\Delta\theta)$ with 
$j=0,1,\ldots,J$ and $k=0,1,\ldots,K$, where $\Delta x=2L/J$ and 
$\Delta\theta=(\theta_T-\theta_B)/K$. We then seek an approximate 
solution with gridpoint values $M_{j,k}$ satisfying the discrete equation 
\begin{linenomath*}
\begin{equation}                          % Equation (40)
   \begin{split}
     & A_{j,k}\left[(f\Delta x)^2 + M_{j-1,k} -2M_{j,k} + M_{j+1,k}\right]    \\ 
     &                  \qquad    + M_{j,k-1} -2M_{j,k} + M_{j,k+1} = 0, 
   \end{split}
\end{equation}
\end{linenomath*}
where the dimensionless coefficient $A_{j,k}$ is defined by 
\begin{linenomath*}
\begin{equation}                          % Equation (41)
   A_{j,k} = \frac{g(\Delta\theta)^2}{f\theta_k \rho_{j,k} P_{j,k}(\Delta x)^2}.   
\end{equation}
\end{linenomath*}
The discretized versions of (36) and (37) are
\begin{linenomath*} 
\begin{equation}                          % Equation (42)
     M_{j,K} - M_{j,K-1} = \Pi_T \Delta\theta, 
\end{equation}
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                          % Equation (43)
     M_{j,0} - \frac{\theta_B}{\Delta\theta} 
	       \left(M_{j,1} - M_{j,0}\right) = \phi_S(x_j).
\end{equation}
\end{linenomath*}
%
Note that (40) applies both outside and inside the massless layer, with 
$A_{j,k} \ne 0$ outside the massless layer and $A_{j,k}=0$ inside the massless 
layer. Also note that the problem is nearly 
isotropic on the grid outside the massless layer if $A_{j,k}\approx 1$, which 
can serve as a rough guide for the choice of the ratio $\Delta\theta/\Delta x$. 
Using typical values of the quantities on the right hand side of (41), 
we obtain the rough guide 
$(\Delta\theta/\Delta x) \approx (1 \, {\rm K})/(57 \, {\rm km})$. For 
the numerical solutions presented here, we have chosen $\Delta x = 8$ km 
and $\Delta\theta = 0.14$ K, resulting in a grid with $J=750$ and $K=450$ 
for the domain $-4000 \le x \le 4000$ km and $295 \le \theta \le 360$ K.

     We solve the discrete equations (40)--(43) using 
the following successive over-relaxation (SOR) procedure. 
Denoting the current estimate of $M_{j,k}$ by $\hat{M}_{j,k}$  
(not to be confused with the `hat' notation in 
section 3 to denote the Fourier component of a variable), 
and sweeping through the grid in lexicographic order, we first 
compute the current estimate of density from 
\begin{linenomath*}
\begin{equation}                          % Equation (44)
   \hat{\rho}_{j,k} = \frac{p_0}{R\theta_k} 
       \left(\frac{\hat{M}_{j,k+1} - \hat{M}_{j,k-1}}
                  {c_p 2\Delta\theta}\right)^{c_v/R},       
\end{equation}
\end{linenomath*}
%
the current estimate of the dimensionless coefficient from 
\begin{linenomath*}
\begin{equation}                          % Equation (45)
   \hat{A}_{j,k} = 
  \begin{cases}
   \displaystyle{\frac{g(\Delta\theta)^2}{f\theta_k \hat{\rho}_{j,k} P_{j,k}(\Delta x)^2}}
                          & {\rm if} \,\,\, \theta_S(x_j) < \theta_k < \theta_T     \\[1.5ex]
              0           & {\rm if} \,\,\, \theta_B      < \theta_k < \theta_S(x_j) 
  \end{cases}   
\end{equation}
\end{linenomath*}
%
and then the current residual from   
\begin{linenomath*}
\begin{equation}                           % Equation (46)                      
   \begin{split}
   \hat{r}_{j,k} 
        &= \hat{M}_{j,k-1} + \hat{M}_{j,k+1} 
	 - 2\left(1 + \hat{A}_{j,k}\right)\hat{M}_{j,k}    \\
	&+ \hat{A}_{j,k}\left[(f\Delta x)^2 + \hat{M}_{j-1,k} + \hat{M}_{j+1,k}\right].     
   \end{split}
\end{equation}
\end{linenomath*}
%
The solution estimate on the interior is then updated by 
\begin{linenomath*}
\begin{equation}                           % Equation (47)
   \hat{M}_{j,k} \leftarrow \hat{M}_{j,k}
                      + \frac{\omega\hat{r}_{j,k}}{2\left(1+\hat{A}_{j,k}\right)}, 
\end{equation}
\end{linenomath*}
%
where $\omega$ is the overrelaxation factor and (46) and (47) are computed at 
the grid points $1 \le j \le J-1, \,\, 1 \le k \le K-1$. Finally, the top 
and bottom boundary points are updated from the boundary conditions (42) 
and (43), written in the form 
\begin{linenomath*}
\begin{equation}                          % Equation (48)
     \hat{M}_{j,K} \leftarrow \hat{M}_{j,K-1} + \Pi_T \Delta\theta 
                        \quad {\rm for} \quad 1 \le j \le J-1,
\end{equation}
\end{linenomath*}
%
\begin{linenomath*}
\begin{equation}                          % Equation (49)
     \hat{M}_{j,0} \leftarrow \frac{(\theta_B/\Delta\theta)\hat{M}_{j,1} + \phi_S(x_j)} 
	                       {1 + (\theta_B/\Delta\theta)} 
	                 \quad {\rm for} \quad 1 \le j \le J-1.   
\end{equation}
\end{linenomath*}
Equations (44)--(49) are iterated, starting with the initial estimate 
$\hat{M}_{j,k}=\tilde{M}(\theta_k)$. This initial estimate does not change 
on the lateral boundaries $j=0$ and $j=J$.    
In order to gauge the convergence rate, we have monitored the norm of the residual 
as iteration proceeds. Experience shows that, when this norm has decreased by 
approximately two orders of magnitude, the wind field no longer significantly changes 
with further iterations.  All of the figures shown have 
been iterated until the residual has decreased by more than two orders of magnitude.     
Based on numerical tests, over-relaxation factors between $1.7$ and $1.95$ have 
been used.

     The above iterative procedure determines the Montgomery potential in 
the entire domain for a given surface geopotential $\phi_S(x)$, a given 
surface potential temperature $\theta_S(x)$, and a given $\tilde{M}(\theta)$. 
From the Montgomery potential, the wind field can be easily recovered 
using geostrophic balance, and the pressure field can be computed using 
the hydrostatic approximation. As a ``null" test of this numerical procedure, 
we have specified $\tilde{M}(\theta)$ according to (9), $\phi_S(x)$ 
according to (26), and $\theta_S(x)$ according to (39). This combination 
should result in no flow and a horizontally homogeneous mass field outside 
the massless layer. 
The numerical solution is shown in Fig.~9, which agrees well with the 
expected result. Note that, when the solution is displayed in $(x,\theta)$-space 
(bottom panel of Fig.~9), there is an anticyclonic flow confined entirely to the massless layer 
so that this anticyclone does not appear when the solution is displayed in 
$(x,p)$-space (top panel).

     Figure 10 shows the solution computed for an isentropic ridge of the 
same height (2500 m) as the ridge shown in Fig.~7.  A comparison of these 
two figures shows that the solution derived using Fourier transforms and the 
solution found with the above iterative procedure are similar, but 
the maximum winds in Fig.~10 are 1.8 m s$^{-1}$ stronger than those in Fig.~7.   
These figures are not expected to be identical because Fig.~7 was 
computed assuming the density was equal to the far-field density (which depends 
only on $\theta$) while Fig.~10 was computed with density as a function of 
$x$ and $\theta$.  The difference between Figs.~7 and 10 is primarily due to 
the difference in the right hand side of (6). Figure 7 results from the 
assumptions $(\tilde{\rho}/\rho) \to 1$ and $(\tilde{P}/P \to 1)$, so that 
the right hand side of (6) vanishes. Figure 10 results from the assumption 
$(\tilde{P}/P \to 1)$, so that the right hand side of (6) becomes 
$f(\tilde{\rho}/\rho)[(\rho/\tilde{\rho})-1]$, which is negative near 
the mountain crest since $\rho < \tilde{\rho}$ there.  This negative right 
hand side of (6) leads to a slightly stronger anticyclone in Fig.~10 
compared to Fig.~7. Note that the errors caused by the assumption  
$(\tilde{\rho}/\rho) \to 1$ are expected to be less for cases in which 
the crest height is much smaller than the critical crest height.

     Figures 11--14 show the wind fields that result from the three 
simple cases represented schematically in Fig.~4.  An isentropic ridge with 
a crest height of 1800 m is shown in Fig.~11 and can be clearly identified 
by the fact that the isentropes do not intersect the ridge and the flow is 
anticyclonic.  A flat lower boundary with a potential temperature anomaly 
of 6 K is shown in Fig.~12, which results in a 12.7 m s$^{-1}$ cyclonic flow.  
Figure 13 combines these two forcing cases into a warm ridge with a crest 
height of 1800 m and a surface potential temperature anomaly of 6 K.  
Note that the isentropic lower surface (Fig.~11) has anticyclonic flow anchored over 
the ridge, but for the case of the flat lower boundary the flow is cyclonic. 
The warm ridge with a potential temperature anomaly of $6$ K has anticyclonic flow 
but when the potential temperature anomaly is increased to $12$ K (Fig.~14), the flow 
becomes cyclonic. This demonstrates the competing influences of the purely orographic 
forcing and the surface thermal forcing. Once the surface potential temperature anomaly 
has grown strong enough to overcome the anticyclonic flow associated with an 
isentropic obstacle, the wind field produced by a warm ridge 
becomes cyclonic and grows with the potential temperature anomaly.

It can also be shown that as the width of the ridge
increases for a given potential temperature anomaly, the influence of the 
anomaly is spread out and effectively acts as a weaker anomaly.

     It is also apparent in ($x,\theta$)-space that the isentropic ridge 
case does not contain a massless layer, but for the warm flat lower boundary 
and the warm ridge, a massless layer is present and marked as the area below 
the thick black line.  Pressure in the massless layer is independent of 
$\theta$, as is clear from the vertical isobars within the massless layers 
of Figs.~12--14.   
Although the pressure is independent of $\theta$ in the massless layer, 
it does vary with $x$, resulting in a nonzero wind field.  
The velocity is required to satisfy the lower boundary condition  
(37), which can be seen as the slope of the velocity increases with 
the magnitude of the velocity along the lower boundary.  The 
concept of nonzero velocity underneath the surface is 
admittedly strange, but is valid based on the governing equations.

     For the case of an isentropic lower boundary the potential vorticity is uniform
on each $\theta$ surface.  This leads to an intuitive explanation 
for the wind field response to the mountain as seen in Figs.~6, 7, and 10.  
Recall that, in the absence of heating, mass cannot cross the isentropic 
surfaces.  This constrains how the mass field can adjust when the
isentropes are moved up or down.  One of the primary benefits to using 
isentropic coordinates is the simplicity of the
expression for potential vorticity.  The denominator of the potential 
vorticity is given by the pseudodensity $-(1/g)(\partial p/\partial\theta)$, 
which becomes smaller when the isentropes are compressed, as occurs over the crest 
of an isentropic ridge.  Because the potential vorticity is uniform,
the decrease in magnitude of the denominator implies the numerator also must 
decrease.  The only part of the numerator that can decrease in magnitude is 
$\partial v/\partial x$, so a negative isentropic relative vorticity  
is required, which is exactly what Figs.~6, 7, and 10 show.  It is apparent that the 
velocity gradient is greatest where the isentropes are the most compressed.  
Similar reasoning can be applied to the case of stretched isentropes with the only
difference being the sign of the isentropic relative vorticity.

     The structure of the isentropes for the cases with a warm lower boundary is quite 
different.  The heating forces mass across isentropic surfaces.  As radiation 
heats the surface, an upslope motion is generated.  When the mass moves upward 
it is transferred from one isentropic layer to the next potentially warmer layer.  This is what 
physically causes the isentropes to bend down towards the heated surface.  The 
stretched isentropic layers generate a wind field that is oriented opposite 
to that which results from the isentropic case with compressed isentropes.

     Each of Figs.~11--14 show the wind maximum to be in the lowest layers of 
the fluid and to decay rapidly in the vertical and horizontal directions.  
This matches well with the basic characteristics of low-level jets.  In agreement
with the insights offered by the invertibility principle these figures show 
an increased gradient in the velocity field when the isentropes are either compressed 
or stretched. These figures clearly indicate that in the absence of other factors 
a sufficiently heated surface will result in a cyclonic wind field.

It is also clear that the jets of opposite sign on either side of the ridge are 
two components of the same response to the forcing.  A heated ridge does not lead 
to a single LLJ, but two LLJs that form a cyclonic or anticyclonic circulation.

\section{Concluding remarks}

     The results presented here show that the surface potential vorticity 
singularity that is the result of the potential temperature anomalies 
along the heated topography plays a key role in the  
dynamics of atmospheric low-level jets.  This conclusion has been  
reached by solving the invertibility principle for the balanced 
response of a stratified fluid to forcing along the lower boundary.  
As shown in Fig.~4, we have studied three types of lower boundary forcing:  
an isentropic ridge along the lower boundary, in which case $\phi_S(x) \ne 0$
and $\theta_S(x)=\theta_B$; a locally heated, flat lower boundary, in which 
case $\phi_S(x)=0$ and $\theta_S(x) \ne \theta_B$; and a heated ridge, 
in which case $\phi_S(x) \ne 0$ and $\theta_S(x) \ne \theta_B$.  
Isentropic ridges produce an anticyclonic wind field. The closer the 
ridge height comes to the critical crest height, the tighter the isentropes 
are packed over the ridge and the stronger the corresponding wind field.  
In contrast, the case of a locally heated flat lower boundary results in a 
cyclonic wind field.  When these two cases are combined into the case 
of a heated ridge, the winds are reduced due to the competing effects 
of the orography ($\phi_S$) and the heating ($\theta_S$). For small 
potential temperature anomalies on the surface, the influence of $\phi_S$ 
is dominant and the wind field is anticyclonic.  However, for surface 
potential temperature anomalies that are larger and closer 
to those observed in YOTC, the heating along the lower boundary is the 
dominant effect, and the wind field is cyclonic.  As an example of 
these competing effects, the heated ridge 
shown in Fig.13, with a potential temperature anomaly of 6K, has an 
anticyclonic flow, while the heated ridge shown in Fig.~14, with a 
potential temperature anomaly of 12K, has a cyclonic flow.  Byerle and Paegle (2003) 
noted a change from cyclonic to anticyclonic flow during the North American winter. 
They attributed this to a change in the zonal flow and the interaction 
with the orography.  The results presented here suggest that this transition 
is due to the winter potential temperature anomaly dropping below the critical value 
that is needed for a cyclonic circulation.

     Past studies of the South American LLJ and the Chilean Coastal LLJ 
have treated these as isolated phenomena. The results presented here clearly 
show that these two LLJs can be attributed to the PV anomaly that is generated 
by diabatic heating of the elevated terrain of the Andes. Although we have 
only treated $\phi_S(x)$ and $\theta_S(x)$ functions that are symmetric about 
$x=0$, the YOTC observations shown in Fig.~2 indicate that surface potential
temperatures are colder on the west side due to cold upwelling in the eastern 
Pacific Ocean. Incorporation of this asymmetry in the specified $\theta_S(x)$
leads to a corresponding asymmetry in the LLJs (i.e., a stronger Chilean LLJ).

     Two limiting aspects of the present work are the $f$-plane and 
$y$-independent assumptions. This raises the obvious question as to 
whether it is possible to generalize the present theory to   
balanced flows on the sphere. Such a generalization has 
been given by Silvers (2011). The specified topography and the specified 
potential temperature on the lower boundary are then given by 
$\phi_S(\lambda,\mu)$ and $\theta_S(\lambda,\mu)$, where $\lambda$ is the 
longitude and $\mu$ is the sine of the latitude. The relation between the mass 
field and the wind field is assumed to be the local linear balance 
(Schubert et al.~2009) condition 
$M(\lambda,\mu,\theta)=2\Omega\mu \, \psi(\lambda,\mu,\theta)$, where 
$\psi(\lambda,\mu,\theta)$ is the streamfunction for the nondivergent 
(i.e., zero isentropic divergence) part of the flow. Then, the spherical 
generalization of (3) is  
\begin{linenomath*}
\begin{equation}                          % Equation (6.1)
   \begin{split}
        \frac{g}{\theta\rho P}
        \left(2\Omega\mu + \nabla^2 \psi\right) 
     &+ 2\Omega\mu\frac{\partial^2 \psi}{\partial\theta^2} = 0  
        \,\,\,\, {\rm for} \,\,\,\, \theta_S(\lambda,\mu) < \theta \le \theta_T,  \\
     &  2\Omega\mu\frac{\partial^2 \psi}{\partial\theta^2} = 0  
	\,\,\,\, {\rm for} \,\,\,\,   \theta_B \le \theta < \theta_S(\lambda,\mu),
   \end{split}
\end{equation} 
\end{linenomath*}
where $\nabla^2$ is the two-dimensional (fixed $\theta$) Laplacian operator 
on the sphere.  With appropriate boundary conditions, (50) constitutes an 
invertibility principle for topographically bound flows on the sphere. Solution 
of this three-dimensional elliptic problem allows treatment of much more realistic 
topography $\phi_S(\lambda,\mu)$ than was treated in sections 3 and 4.

\begin{acknowledgment} 
We would like to thank Brian McNoldy, Scott Fulton, Thomas Birner, David Randall, Paul Ciesielski, 
Richard Johnson, Matthew Masarik,    
and Richard Taft for their valuable advice. This research has been supported 
by the National Science Foundation under Grant ATM-0837932 and 
under the Science and Technology Center for Multi-Scale Modeling of 
Atmospheric Processes, managed by Colorado State University 
through cooperative agreement No.~ATM-0425247.  Workstation computing 
resources were provided through a gift from the Hewlett-Packard Corporation.  
\end{acknowledgment}

% Use appendix}[A], {appendix}[B], etc. etc. in place of appendix if you have multiple appendixes.
%\ifthenelse{\boolean{dc}}
%{}
%{\clearpage}
\begin{appendix}
\section*{\begin{center}Analytic solution using Fourier integral transforms\end{center}}

      To solve the invertibility problem (11)--(15) we use Fourier integral transforms.  
For simplicity we assume that the specified function $\phi_S(x)$  
is symmetric in $x$, so that $\Pi'(x,\theta)$ is symmetric in $x$ and $v(x,\theta)$ is 
antisymmetric in $x$.  The Fourier sine transform pair for $v(x,\theta)$ is  
\begin{linenomath*}
\begin{equation}                    % Equation (A1)
   \hat{v}(k,\theta) = \frac{2}{\pi} \int_0^\infty  v(x,\theta)\sin(kx) \, dx, 
\end{equation}
\end{linenomath*}
\begin{linenomath*}
\begin{equation}                    % Equation (A2)
        v(x,\theta) = \int_0^\infty \hat{v}(k,\theta) \sin(kx) \, dk, 
\end{equation} 
\end{linenomath*}
while the Fourier cosine transform pair for $\Pi'(x,\theta)$ is 
\begin{linenomath*}
\begin{equation}                    % Equation (A3)
   \hat{\Pi}'(k,\theta) = \frac{2}{\pi} \int_0^\infty  \Pi'(x,\theta)\cos(kx) \, dx, 
\end{equation}
\end{linenomath*}

\begin{linenomath*}
\begin{equation}                    % Equation (A4)
         \Pi'(x,\theta) = \int_0^\infty \hat{\Pi}'(k,\theta) \cos(kx) \, dk.
\end{equation} 
\end{linenomath*}
A similar cosine transform pair exists for the surface geopotential $\phi_S(x)$ and its 
transform $\hat{\phi}_S(k)$.

     We now wish to Fourier transform (11), (12), (14), and (15). To Fourier 
transform (11) and (14) we multiply them by $\cos(kx)$ and integrate over $x$ 
from $0$ to $\infty$, thereby obtaining (A5) and (A7) below.  To Fourier transform 
(12) and (15) we multiply them by $\sin(kx)$ and integrate over $x$ from $0$ to $\infty$, 
thereby obtaining (A6) and (A8) below. In summary, the Fourier transform of the elliptic 
problem (11)--(15) is
\begin{linenomath*} 
\begin{equation}                    % Equation (A5)
     k\hat{v} + \left(\frac{f\theta_B^2 N_B^2}{g^2}\right) \frac{d\hat{\Pi}'}{d\theta} = 0,    
\end{equation} 
\end{linenomath*}

\begin{linenomath*}
\begin{equation}                    % Equation (A6) 
         f\frac{d\hat{v} }{d\theta}  + k \hat{\Pi}'  = 0,  
\end{equation} 
\end{linenomath*}
with boundary conditions
\begin{linenomath*} 
\begin{equation}                    % Equation (A7)
        \hat{\Pi}' = 0               \,\,\, {\rm at}  \,\,\, \theta = \theta_T,  
\end{equation}
\end{linenomath*}

\begin{linenomath*}
\begin{equation}                    % Equation (A8)	
       \theta\frac{d\hat{v}}{d\theta} - \hat{v} = \frac{k}{f}\hat{\phi}_S(k)   
                                      \,\,\, {\rm at}  \,\,\, \theta = \theta_B.           
\end{equation}
\end{linenomath*}
    As can be confirmed by direct substitution, the solutions 
of (A5)--(A8) are\footnote{The solutions of (A5)--(A8) can also be expressed 
in terms of $\cosh(\kappa\theta)$ and $\sinh(\kappa\theta)$, but for large horizontal 
wavenumbers, numerical evaluation of the hyperbolic representation of the solution 
presents a practical difficulty since the ratio of very large numbers is involved. 
This difficulty does not occur in the exponential representation (A9)--(A10), 
since this representation avoids evaluation of exponential functions with large 
positive exponents.} 
\begin{linenomath*}      
\begin{equation}                    % Equation (A9)
    \hat{v}(k,\theta) = -\frac{k}{f}\hat{\phi}_S(k)
        \left(\frac{e^{-\kappa(\theta-\theta_B)} + e^{-\kappa(2\theta_T-\theta_B-\theta)}}
         {1 + \kappa\theta_B + (1 - \kappa\theta_B)e^{-2\kappa(\theta_T-\theta_B)}}\right),   
\end{equation}  
\end{linenomath*}

\begin{linenomath*}
\begin{equation}                    % Equation (A10)
    \frac{\theta_B N_B}{g}\hat{\Pi}'(k,\theta)   
     = -\frac{k}{f}\hat{\phi}_S(k)
        \left(\frac{e^{-\kappa(\theta-\theta_B)} - e^{-\kappa(2\theta_T-\theta_B-\theta)}}
         {1 + \kappa\theta_B + (1 - \kappa\theta_B)e^{-2\kappa(\theta_T-\theta_B)}}\right).    
\end{equation} 
\end{linenomath*}
where $\kappa(k) = gk/(f\theta_B N_B)$. 
The 
Fourier cosine transform of (16) yields
\begin{linenomath*} 
\begin{equation}                           % Equation (A11)
   \hat{\phi}_S(k) = \frac{gH a}{\sqrt{\pi}} e^{-a^2 k^2/4}.  
\end{equation} 
\end{linenomath*}

\end{appendix}
%\subsection{First appendix secondary heading}
%
%\subsection{Second appendix secondary heading}
%
%\subsubsection{First appendix tertiary heading}
%
%\subsubsection{Second appendix tertiary heading}
%
%\paragraph{First appendix quaternary heading}
%
%\paragraph{Second appendix quaternary heading}
%
%\end{appendix}

% Create a bibliography directory and place your .bib file there.
% -REMOVE ALL DIRECTORY PATHS TO REFERENCE FILES BEFORE SUBMITTING TO THE AMS FOR PEER REVIEW
%\ifthenelse{\boolean{dc}}
%{}
%{\clearpage}
%\bibliographystyle{ametsoc}
%\bibliography{references}

\section{References}

%Byerle, L.~A., and J. Paegle, 2002: Description of the seasonal cycle of low-level flows flanking the Andes
%and their interannual variability. {\sl Meteorologica}, {\bf 27}, 71--88.

Bonner, W.~D., 1968: Climatology of the low level jet. 
{\sl Mon.\ Wea.\ Rev.}, {\bf 96}, 833--850.

Byerle, L.~A., and J. Paegle, 2003: Modulation of the Great Plains low-level jet and moisture transports 
by orography and large-scale circulations. {\sl J.\ Geophys.\ Res.}, {\bf 108}, 8611 %, doi:10.1029/2002JD003005.

Eliassen, A., 1980: Balanced motion of a stratified, rotating fluid induced by bottom topography.  
{\sl Tellus}, {\bf 32}, 537--547.

Jiang, X., N.-C. Lau, I. M. Held, and J. J. Ploshay, 2007: Mechanisms of the Great Plains 
low-level jet as simulated in an AGCM. {\sl J.\ Atmos.\ Sci.}, {\bf 64}, 532--547.  
%doi: 10.1175/JAS3847.1

Kanamitsu, M., W. Ebisuzaki, J. Woollen, S.-K. Yang, J. J. Hnilo, M. Fiorino, 
and G. L. Potter, 2002: NCEP-DOE AMIP-II Reanalysis (R-2). 
{\sl Bull.\ Amer.\ Meteor.\ Soc.}, {\bf 83}, 1631--1643.

Nogu\'es-Paegle, J., J. Paegle, and Coauthors, 2001: American low level jets---A scientific 
prospectus and implementation plan. 
Available online at \\ http://www.clivar.org/organization/vamos/Publications/alls.pdf

Schubert, W.H., R.K. Taft, and L.G. Silvers, 2009: Shallow water quasi-geostrophic theory on the sphere.
{\sl J. Adv. Model. Earth Syst.},{\bf 1}(2),17 pp. % doi: 10.3894/JAMES.2009.1.2.

Silvers, L.~G., 2011: A theory of topographically bound balanced motions and 
application to atmospheric low-level jets. Ph.D. Dissertation, Department 
of Atmospheric Science, Colorado State University.

Stensrud, D. J., 1996: Importance of low-level jets to climate: A review. 
{\sl J.\ Climate}, {\bf 9}, 1698--1711.

Tarasova, T. A., J. P. R. Fernandez, I. A. Pisnichenko, J. A. Marengo, J. C. Ceballos, and M. J. Bottino, 2006: 
Impact of new solar radiation parameterization in the Eta Model on the simulation of summer climate over South America. {\sl J. Applied Meteorology and Climatology}, {\bf 45}, 318--333. 
% doi: 10.1175/JAM2342.1

%Ting, M., and Hailan Wang, 2006: The role of the North American topography on the maintenance of the 
%Great Plains summer Low-Level Jet.  {\sl J. Atmos. \ Sci.}, {\bf 63}, 1056--1068.

Vera, C., J. Baez, M. Douglas, C.~B. Emmanuel, J. Marengo, J. Meitin, M. Nicolini, 
J. Nogues-Paegle, J. Paegle, O. Penalba, P. Salio, C. Saulo, M.~A. Silva Dias, 
P. Silva Dias, and E. Zipser, 2006: The South American low-level jet experiment.  
{\sl Bull.\ Amer.\ Meteor.\ Soc.}, {\bf 87}, 63--77.

Waliser, D., M. Moncrieff, D. Burridge, and Coauthors, 2011: The `Year' of tropical convection 
(May 2008 to April 2010): Climate variability and weather highlights. {\sl Bull.\ Amer.\ Meteor.\ Soc.}, 
{\sl submitted}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% FIGURES-REMOVE ALL DIRECTORY PATHS TO FIGURE FILES BEFORE SUBMITTING TO THE AMS FOR PEER REVIEW
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]                             % Figure 1
  \noindent\includegraphics[width=19pc,angle=0]{meanwind925_combined.eps}
\caption{January 2003 mean 925 hPa wind (scale of 10 m s$^{-1}$ vector 
 indicated just below the colorbar) from the NCEP-DOE Reanalysis II data 
 (Kanamitsu et al. 2002), which has the horizontal/vertical 
 resolution T62/L28.  Vectors are not drawn in the region of the Andes 
 above 925 hPa (at T62 horizontal resolution).  The background map shows 
 topography (see colorbar, scale is 100's m), with the La Plata river 
 basin outlined in red.  Adapted from Tarasova et al.~(2006) and 
 Nogu\`es-Paegle et al.~(2001).}
\end{figure}

%
%
\begin{figure}[t]                             % Figure 2
  \noindent\includegraphics[width=19pc,angle=0]{andesxsec.eps}
\caption{Mean warm season analysis of meridional wind at 21 S (top) and 30 S 
(bottom) from the ECMWF  Year of Tropical Convection (YOTC) data.  The magnitude of the meridional wind is 
given by the colorbar; 
black contours are isentropes.}
\end{figure}   
%
\begin{figure}[t]                              % Figure 3 
  \noindent\includegraphics[width=19pc,angle=0]{rockiesxsec.eps}
\caption{Mean warm season reanalysis meridional wind field at 30 N (top) and 35 N 
(bottom) from the ECMWF Year of Tropical Convection (YOTC) data.  The magnitude of wind is given by 
the colorbar, black contours are isentropes.}
\end{figure}

\begin{figure}[t]                 % Figure 4
  \noindent\includegraphics[width=39pc,angle=0]{schematicfinal.eps}
\caption{Schematic vertical cross sections representing the three 
idealized configurations studied here. Contours represent lines of 
constant potential temperature (isentropes), with the vertical axes 
interpreted as height. On the left is an isentropic obstacle, the 
middle is a heated flat lower surface, and the right is a heated obstacle.}
\end{figure}

\begin{figure}[t]                             % Figure 5 
\noindent\includegraphics[width=19pc,angle=0]{refstatB.eps}
\caption{Reference pressure $\tilde{p}$ as a function of $\theta$, computed from (8).}
\end{figure}

\begin{figure}[t]                      % Figure 6
\noindent\includegraphics[width=19pc,angle=0]{vim_px_H1500_lat30.eps}
\caption{Cross-section plot of meridional wind ($v$, colors) and potential temperature 
($\theta$, solid lines) near a `Gaussian isentropic mountain' with half-width $a=500$ km 
and crest height $H=1500$ m. The potential temperature on the mountain surface is 295 K, and the flow 
is anticyclonic. The contour intervals are 1 m s$^{-1}$ for $v$ and 2 K for $\theta$.  
The extreme values of $v$ are $+11.5$ m s$^{-1}$ on the west side (dark red) of the mountain 
and $-11.5$ m s$^{-1}$ on the east side (dark blue).}
\end{figure}

\begin{figure}[t]                      % Figure 7
\noindent\includegraphics[width=19pc,angle=0]{vim_px_H2500_lat30.eps}
\caption{Same as Fig.~6, but with crest height $H=2500$ m.   
The peak values of $v$ are $\pm19.2$ m s$^{-1}$.}
\end{figure}

\begin{figure}[t]                      % Figure 8 
\noindent\includegraphics[width=19pc,angle=0]{crit_Hvs_width.eps}
\caption{Critical height $H_{\rm crit}$ of a Gaussian mountain as a function of half-width 
at five latitudes.}
\end{figure}

\begin{figure}[t]                               % Figure 9 
\noindent\includegraphics[width=19pc,angle=0]{zerowind1.eps}
\caption{A null case (i.e., no flow), in which $\tilde{\phi}(\theta)$, 
$\phi_S(x)$, and $\theta_S(x)$ are specified such that (38) is satisfied. 
In this particular null case, $\tilde{\phi}(\theta)$ is given by (10), 
$\phi_S(x)$ by (26), and $\theta_S(x)$ by (39). Black contours are 
isentropes (top) and isobars (bottom). The anticyclone in the massless 
layer of the bottom panel is not apparent in the top panel since
the massless layer has ``zero thickness" in $(x,p)$-space.}
\end{figure}

\begin{figure}[t]                     % Figure 10 
\noindent\includegraphics[width=19pc,angle=0]{SORtest.eps}
\caption{Meridional wind field (shading, warm colors are 
positive, cool colors negative, and the contour interval is 1 m s$^{-1}$) for an 
isentropic lower boundary computed using SOR.  The maximum 
height of the Gaussian mountain is $2500$ m and its halfwidth is 500 km. 
The maximum winds are 21.0 m s$^{-1}$.}
\end{figure}

\begin{figure}[t]                               % Figure 11
\noindent\includegraphics[width=19pc,angle=0]{ist1c_lap.eps}
\caption{Meridional wind field (shading, 1 m s$^{-1}$ intervals) for an isentropic 
ridge with $H=1800$ m and a Gaussian half-width of $a=600$ km. The flow is anticyclonic with $v_{\rm max}=15.4$ m s$^{-1}$.  
Black contours are isentropes (top) and isobars (bottom).}
\end{figure}

\begin{figure}[t]                          % Figure 12 
\noindent\includegraphics[width=19pc,angle=0]{flb4c.eps}
\caption{Meridional wind field (shading, 1 m s$^{-1}$ intervals) for a  
flat lower surface having a 6 K  warm temperature anomaly with a Gaussian halfwidth 
of $a=600$ km. The resulting winds have $v_{\rm max}=12.7$ m s$^{-1}$.  The massless 
layer in ($x,p$)-space (top) is indicated by black object along the lower boundary while 
in ($x,\theta$)-space (bottom) it is indicated by the thick black line.  
Contour spacing for the pressure field in the massless layer is 1 hPa.}
\end{figure}

\begin{figure}[t]                         % Figure 13 
\noindent\includegraphics[width=19pc,angle=0]{hr11.eps}
\caption{Meridional wind field (shading, 1 m s$^{-1}$ intervals) for 
a heated ridge with a 6 K potential temperature anomaly, $H=1800$ m, 
$a=600$ km, $v_{\rm max}=11.13$ m s$^{-1}$.  The massless layer is 
indicated by the black object (top) and the thick black line (bottom).  
Halfwidth of ridge is 900 km. Contour spacing of isobars(bottom)  
is 50 hPa except for lowest contour of 975 hPa.}
\end{figure}

%\begin{figure}[t]                        % Figure 14 
%\noindent\includegraphics[width=29pc,angle=0]{flb5b.eps}
%\caption{Same as Fig.~11 except with a 12 K surface potential temperature anomaly.  
%The flow is cyclonic with $v_{\rm max}=27.27$ m s$^{-1}$.  In the lower panel the 
%contour spacing for pressure is 50 hPa above the massless layer and 4 hPa in the 
%massless layer.}
%\end{figure}

 \begin{figure}[t]                      % Figure 14
\noindent\includegraphics[width=19pc,angle=0]{hr6b.eps}
\caption{Same as Fig.~12 except with a 12 K surface potential temperature anomaly.  
The isentropes now bend down toward higher pressure and the flow is cyclonic 
with $v_{\rm max}=10.3$ m s$^{-1}$.}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% TABLES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\begin{table}[t]
%\caption{This is a sample table caption and table layout.  Enter as many tables as
%  necessary at the end of your manuscript. Table from Lorenz (1963).}\label{t1}
%\begin{center}
%\begin{tabular}{ccccrrcrc}
%\hline\hline
%$N$ & $X$ & $Y$ & $Z$\\
%\hline
% 0000 & 0000 & 0010 & 0000 \\
% 0005 & 0004 & 0012 & 0000 \\
% 0010 & 0009 & 0020 & 0000 \\
% 0015 & 0016 & 0036 & 0002 \\
% 0020 & 0030 & 0066 & 0007 \\
% 0025 & 0054 & 0115 & 0024 \\
%\hline
%\end{tabular}
%\end{center}
%\end{table}
%
\end{document}

%%%%%%%%%%%%%%   Extra Pieces   *******************

     The basic characteristics of the wind field from the YOTC data shown 
in Figs.~3--4 agrees well with the results shown in Fig.~14.  The orientation 
of the wind field (cyclonic)  is the same and the magnitude is similar to that 
shown by the YOTC data. Because a steady state has been assumed the time 
evolution of potential vorticity and wind can obviously not be seen.  This 
model only computes the wind field that results from the potential vorticity 
at an instant in time. Alternately, this could be interpreted as the potential 
vorticity averaged over a time interval.  The figures in section 5 can be 
interpreted as representing means of roughly 1-3 months.  If the temperature 
distribution along the lower boundary is made larger, say 20K 
(see Jiang et al.~2010), the wind speeds are closer to what would be expected 
for daily or weekly mean fields. The parameters used to compute all of the 
wind fields shown in section 5 were chosen to be comparable to Earth-like 
mountains with realistic temperature anomalies along the lower boundary.  
It is probably not appropriate to make direct comparisons between the results 
of section 5 and observations of specific jet events or even climatologies 
because the assumptions of a steady, nonviscous fluid will certainly lead to 
discrepancies between the computed and observed wind fields, especially along 
the lower boundary, which is precisely where the LLJ maxima in section 5 are 
located. Performing a comprehensive comparison between these results and 
observations of LLJs is beyond the scope of this work.

### 2019-10-14 Silvers_WalkerCell.tex

@@
 
+The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
+This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
+as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
+SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
+mean shear develops which shifts the precipitation and circulation off center for years at a time.  This appears to be not entirely a 
+result of the convective parameterization, but due to an interaction between the convective parameterization and the LW CRE.
+
 %%%%%
@@
 of the differences in upper level cloud fraction and will be discussed further in a later section.
+
+%One of the most prominent features of our 25km grid-spacing simulations is an asymmetry in both the time-dependent and 
+%steady-state solutions.  This results in the steady-state precipitation maximum locating off the maximum in SST and is apparent in 
+%the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.   A tendency of the precipitation to 
+%occur off of the SST maximum is also apparent in the simulations with a grid-spacing of 100km, although the 25km simulations display 
+%an irregularity that is greater than the 100km simulations.  Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
+%distribution has been noted many times 
+%(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
+%tended to be symmetric, unlike our results.   
+%
+%For the simulations that are closest to the set up of a GCM, with fully parameterized convection, the steady-state circulation and 
+%precipitation maximum are located not over the warmest SST but shifted to regions about one degree cooler.  For the case
+%with a grid-spacing of 25km and a domain width of 4000km, the precipitation maximum can remain shifted off of the maximum in
+%SST for multiple years.   While focused within the central quarter of the domain, simulations on larger domains and with a 
+%grid-spacing of 100km also show an aversion to settling over the SST maximum.   When the convective parameterization
+%is turned off, the overturning circulation becomes weaker and broader (w, and psi), but the precipitation, cloud fields, and 
+%circulation all consistently reside over the SST maximum.  When the convective parameterization is turned on, a domain mean 
+%wind shear develops throughout the lowest 10km that acts to shift the convective activity and circulation off of the SST maximum.  
+%Note: check the wind shear for P25large, P100small, and P100large.
 
@@
 
+Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
+the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
+simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+The large oscillations in domain mean precipitation are similar to those noted in previous studies 
+(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
+mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
+of the differences in upper level cloud fraction and will be further discussed.
+
+Superposing the circulation and relative humidity illustrates the subsidence driven 
+drying and the strong moistening that results from ascent over the region of maximum latent heat flux.
+
 The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
@@
 
-%\begin{figure}
-%  \centering
-%      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
-%  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
-%  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
-%  while the P25 and P100 cases show only the first out of five years of the time series.}
-%    \label{fig:precip_dom_mn}
-%\end{figure}
-
 \begin{figure}
@@
 
+%  \caption{Variables important to boundary layer energy fluxes.
+Top left panel shows the surface enthalpy flux ($\rm{W m^{-2}}$) and top right panel shows the equivalent potential temperature on the model level closest to the surface.
+The panel on bottom left shows the $u$ wind ($\rm{m s^{-1)}}$)
+%  on the model level closest to the surface and the panel on bottom right shows the domain mean
+%  $\rm{u}$ wind.}
+
 %% surface enthalpy flux
@@
 Walker circulation comes from the fact that all of the major types of tropical cloud types occur regularly within this circulation
-and it thus serves as an ideal testbed/laboratory for studying the interactions and interdependencies of different types of 
 clouds and the circulation.  While this study has interpreted the experiments in the context of the Walker Circulation, our results 

### 2019-10-14 Silvers_cfmip_draft.tex

@@
 the top of the atmosphere compared well with observations.  The data set that was most heavily leaned on to ensure 
-this was the CERES-EBAF TOA radiative fluxes, version 2.8.  Based on AM4.0 data that was used for the CMIP6 AMIP
+this was the CERES-EBAF TOA radiative fluxes, version 2.8 (Loeb et al., 2009).  Based on AM4.0 data that was used for 
+the CMIP6 AMIP
 experiment, the total TOA flux bias is 989898, the bias in CRE 
@@
 simulated clouds  from AM4.0 in the AMIP experiment.
+
+Paragraph summarizing the basic characteristics of clouds in AM4.0 as stated by Ming's papers.  We could also summarize 
+what David finds about clouds in AM4.0 in his paper.
 
@@
 
-In an attempt to compare to the values of feedback that were reported in Ringer et al., 2014, we use the same method 
+In order to compare to the values of feedback that were reported in Ringer et al., 2014, we use the same method 
 to compute the radiative feedbacks for the GFDL models.  That is, for the abrupt $4xCO_{2}$ experiment, feedbacks are 
-inferred to be the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies (Gregory et al., 2004).
-From the atmosphere only experiments (amip-p4K, amipFuture, and aqua-p4K), the feedbacks are calculated as
+inferred to be the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
+(Gregory et al., 2004).  From the atmosphere only experiments (amip-p4K, amipFuture, and aqua-p4K), the feedbacks are calculated as 
 differences in top-of-atmosphere flux anomalies between the perturbation and control experiments.
@@
 \begin{center}
-\caption{Global mean radiative feedbacks.  Compare to Ringer et al. 2014.}
+\caption{Global mean radiative feedbacks.  The values for the Abrupt 4xCO2 experiment
+have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.}
     \begin{tabular}{*{5}{c}}
@@
  Feedback & Aqua p4K & Amip p4K & Amip Future & Abrupt 4xCO2    \\ \hline
-    Net          &   -2.2    &  -1.6              & -1.8           &    -0.84 (from Tim)         \\ 
+    Net          &   -2.2    &  -1.6              & -1.8           &    -0.46 (-0.84; Tim)         \\ 
     \\
-    Net CRE      & 0.3      & -0.1            & 0.1           &?            \\  
+    Net CRE      & 0.3      & -0.1            & 0.1           & 0.65   \\  
     \\
-    LW CRE       & 0.4       & 0.1            & 0.1           & ?              \\  
+    LW CRE       & 0.4       & 0.1            & 0.1           & 0.14    \\  
     \\
-    SW CRE      & -0.7       & -0.1          & -0.2          & ?              \\  
+    SW CRE      & -0.7       & -0.1          & -0.2          & -0.5              \\  
     \\
-    LW CLR       & 2.0       & 2.0             & 2.0           & ?             \\  
+    LW CLR       & 2.0       & 2.0             & 2.0           & 1.7             \\  
     \\
-    SW CLR      & -0.1      & -0.3            & -0.3          & ?                   \\  \hline
+    SW CLR      & -0.1      & -0.3            & -0.3          & -0.6                   \\  \hline
 
@@
 
+\section{What are we learning?}
+
+Experiments using Cess-like uniform SST warming as a proxy for climate change have successfully predicted that much of the differences 
+among models is due to the cloud radiative affect.  However, we also know that the sensitivity derived from Cess-like experiments is not
+a good predictor of the climate sensitivity for a parent, coupled model.  Comparison of Cess-sensitivities and coupled model sensitivities 
+combined with patterned prescribed SST experiments using AGCM have demonstrated the significant role of a pattern-effect in determining 
+the sensitivity of a model.
+
+We also know that a method which uses linear regression of a constant forcing experiment to estimate the climate sensitivity only 
+provides an accurate measure of the climate sensitivity when the initial 20-50 years of simulation are excluded from the analysis.  
+The climate sensitivities of models that have been run to equilibrium with millenial-scale simulations show a large discrepency in the
+different time periods used to estimate this sensitivity.
+
+Clouds in a climate model are highly maleable while also being a dominant factor controlling what the climate sensitivity is for that model.  
+Yet we do not have satisfactory clouds constraints to impose on the clouds of a climate model.  If improving the representation of low-level
+clouds in the GFDL model was the first priority, it could be done.  However it is not the first priority and doing so degrades other elements of 
+the climate.
+
 \end{document}

### 2019-10-14 Silvers_etal_grl_SMrevisions_2017_sub.tex

--- 2019-09-20 Silvers_etal_2017_draft.tex
@@
 % AGUtmpl.tex: this template file is for articles formatted with LaTeX2e,
-% Modified July 2014
+% Modified November 2013
 %
@@
 %
-% FOR FIGURES, DO NOT USE \psfrag or \subfigure.
+% FOR FIGURES, DO NOT USE \psfrag
 %
@@
 % ef    EARTH'S FUTURE
-% ea    EARTH AND SPACE SCIENCE
 %
@@
 
-%\documentclass[draft,grl]{agutex2015}
-\documentclass[grl]{agutex2015}
-% To create numbered lines:
+\documentclass[draft,grl]{agutexSI}
 
-% If you don't already have lineno.sty, you can download it from
-% http://www.ctan.org/tex-archive/macros/latex/contrib/ednotes/
-% (or search the internet for lineno.sty ctan), available at TeX Archive Network (CTAN).
-% Take care that you always use the latest version.
-
-% To activate the commands, uncomment \usepackage{lineno}
-% and \linenumbers*[1]command, below:
-
-\usepackage{graphicx}
-\usepackage{epstopdf}
-
-% \usepackage{lineno}
-% \linenumbers*[1]
-%  To add line numbers to lines with equations:
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-% Figures and Tables
+%
+%  SUPPORTING INFORMATION TEMPLATE
+%
+%% ------------------------------------------------------------------------ %%
 %
 %
+%Please use this template when formatting and submitting your Supporting Information.
+
+%This template serves as both a “table of contents” for the supporting information for your article and as a summary of files.
+%
+%
+%OVERVIEW
+%
+%Please note that all supporting information will be peer reviewed with your manuscript.
+%In general, the purpose of the supporting information is to enable authors to provide and archive auxiliary information such as data %tables, method information, figures, video, or computer software, in digital formats so that other scientists can use it.
+%The key criteria are that the data:
+% 1. supplement the main scientific conclusions of the paper but are not essential to the conclusions (with the exception of
+%    including %data so the experiment can be reproducible);
+% 2. are likely to be usable or used by other scientists working in the field;
+% 3. are described with sufficient precision that other scientists can understand them, and
+% 4. are not exe files.
+%
+%USING THIS TEMPLATE
+%
+%***All references should be included in the reference list of the main paper so that they can be indexed, linked, and counted as citations.  The reference section does not count toward length limits.
+%
+%All Supporting text and figures should be included in this document.
+Insert supporting information content into each appropriate section of the template.
+%Figures and tables should appear above each caption.
+To add additional captions, simply copy and paste each sample caption as needed.
+
+%Tables may be included, but can also be uploaded separately, especially if they are larger than 1 page, or if necessary for retaining table formatting.
+Data sets, large tables, movie files, and audio files should be uploaded separately, following AGU naming conventions.
+Include their captions in this document and list the file name with the caption.
+You will be prompted to upload these files on the Upload Files tab during the submission process, using file type “Supporting Information (SI)”
+
+%IMPORTANT NOTE ON FIGURES AND TABLES
+% Placeholders for figures and tables appear after the \end{article} command, after references.
 % DO NOT USE \psfrag or \subfigure commands.
 %
-%
 %  Uncomment the following command to include .eps files
-%  (comment out this line for draft format):
 % \usepackage[dvips]{graphicx}
+ % \usepackage[dvipdf]{graphicx}
+  \usepackage{graphicx}
 %
@@
 \setkeys{Gin}{draft=false}
+%\setkeys{Gin}{draft=true}
 %
@@
 %
-% See how to enter figures and tables at the end of the article, after
-% references.
 %
@@
 % Shorter version of title entered in capital letters:
+%\titlerunninghead{SHORT TITLE}
 \titlerunninghead{Cloud Feedbacks in long-AMIP}
@@
 %Corresponding author mailing address and e-mail address:
-%\authoraddr{Corresponding author: A. B. Smith,
+\authoraddr{Corresponding author: L. G. Silvers,
+Princeton University/GFDL, Princeton, New Jersey, USA.
+(silvers@princeton.edu)}
 %Department of Hydrology and Water Resources, University of
@@
 
-\title{Decadal variations of cloud feedback in long-AMIP experiments with three GFDL climate models.}
+%\includegraphics{agu_pubart-white_reduced.eps}
+
+\title{Supporting Information for ``The diversity of cloud responses to twentieth-century sea surface temperatures"}
 %
-% e.g., \title{Terrestrial ring current:
-% Origin, formation, and decay $\alpha\beta\Gamma\Delta$}
+% e.g., \title{Supporting Information for "Terrestrial ring current:
+% Origin, formation, and decay $\alpha\beta\Gamma\Delta$"}
 %
+%DOI: 10.1002/%insert paper number here%
 
@@
 % matching \altaffiltext will appear at bottom of page.
-\authors{Levi G. Silvers, David Paynter, and Ming Zhao}
+
+\authors{Levi G. Silvers\altaffilmark{1}, David Paynter\altaffilmark{2}, and Ming Zhao\altaffilmark{2}}
+
+\altaffiltext{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
+\altaffiltext{2}{GFDL/NOAA, Princeton, New Jersey, USA}
+
 % \authors{A. B. Smith,\altaffilmark{1}
@@
 %
-%  KEYPOINTS
-%
-%% ------------------------------------------------------------------------ %%
-
-% Key points are 1 to 3 points that the author provides,
-% that are 100 characters or less, that are ultimately published
-% with the article.
-%% for example:
-% \keypoints{\item Here is the first keypoint. what happens if it is a
-% long keypoint, like this one. We want to see this wrap please.
-% \item This is the second.
-% \item And here is the third keypoint
-% }
-
-\keypoints{\item Three models show the Eastern Tropical Pacific as a key location where decadal trends in SST and low-level clouds strongly influence the global energy budget
-\item Changes in low-level clouds can be linearly decomposed but with differing magnitudes of dependencies on EIS and SST
-\item The cloudy response of the models differs markedly between twentieth century periods with high and low climate sensitivities}
-%\item AM2.1, AM3, and AM4g10r8 all show strong twentieth
-%century decadal variability of the global feedback parameter.
-%\item All three models show increased low-level clouds in the East Pacific
-%over recent decades.
-%\item Low-level cloud trends depend on both EIS trends 
-%and omega trends.}
-
-%% Keypoints will print underneath the abstract.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  ABSTRACT
-%
-%% ------------------------------------------------------------------------ %%
-
-% >> Do NOT include any \begin...\end commands within
-% >> the body of the abstract.
-
-\begin{abstract}
-
-Significant decadal variability of the global feedback parameter is shown to be clearly linked to the pattern of surface warming through the evolution of low-clouds and the estimated inversion strength (EIS).
-We examine the atmospheric response to changing SST patterns between 1870-2004 using the amip-piForcing experimental configuration with three GFDL atmospheric global climate models (AM2, AM3, and AM4).
-There is a notable strengthening of the negative global feedback from the middle period of the 20th century until the present.
-We contrast the variability of the cloud response among the models between these two periods.
-The changing low-cloud cover is analyzed within a framework that includes trends of the EIS and the mid-tropospheric vertical velocity.
-
-Recently it has been argued that decadal changes in low-level cloud cover over the eastern Pacific ocean basin strongly influence the global net feedback parameter.
-These decadal changes of low-level cloud cover have been tied to corresponding changes in the observed sea surface temperatures.
-We examine these claims with AM2, AM3, and AM4.
-The dominant configuration difference among the models is the parameterization of the convective clouds.
-The amip-piForcing experiment provides an ideal configuration to test the range of atmospheric responses to a prescribed but evolving SST pattern.
-
-All three GFDL models confirm the importance of the relationship between the global climate sensitivity and the trends in the eastern Pacific of SST and low-level clouds.
-However, there are noteworthy differences in the cloud response of the models.
-Despite all three models being driven by observed SSTs, sea ice concentration, and constant preindustrial forcing agents distinct net global feedbacks are simulated.
-
-%Recently it has been argued that decadal changes in low-level cloud cover over the eastern Pacific ocean basin strongly influence the global net feedback parameter.
-These decadal changes of low-level cloud cover have been tied to corresponding changes in the observed sea surface temperatures (SST).
-We examine this claim in three generations of GFDL atmospheric global climate models $(AM2.1, AM3, and AM4_g10r8)$.
-The dominant configuration difference among the models is the parameterization of convective clouds.
-Atmospheric experiments with observed SSTs (atmospheric forcing held at constant preindustrial values) between 1870-2004 are examined to elucidate the source of differences between the models.
-%
-%All three models are shown to have strong decadal variability in their net feedback parameter, the global mean cloud-radiative effect, and the low-level cloud fields.
-All three models confirm the importance of the relationship in the eastern Pacific region between decadal SST patterns and low-level cloud changes.
-However, there are noteworthy differences in the cloud response of the models.
-%
-%The correlation between changes in low-level cloud cover and the lower tropospheric stability is used to examine the impact of the alternate cumulus parameterizations used by the models.
-We approximate the change of low-level cloud with a linear combination of changes in lower tropospheric stability and SST.
-The usefulness of this approximation differs among the three models examined.
-%
-%Despite all models being driven by observed SSTs, sea ice concentration, and having constant preindustrial atmospheric forcing agents distinct net global feedbacks are simulated. 
-%
-\end{abstract}
-
-%% ------------------------------------------------------------------------ %%
-%
 %  BEGIN ARTICLE
@@
 
-\section{Introduction}
+\noindent\textbf{Contents of this file}
+%%%Remove or add items as needed%%%
+\begin{enumerate}
+\item Additional Information for Boundary Condition and Parameterization details
+\item Additional Results
+\item Computational details of the Estimated Inversion Strength
+\item Figures S1 to S4
+\item Tables S1 to S2
+%if Tables are larger than 1 page, upload as separate excel file
+\end{enumerate}
+%\noindent\textbf{Additional Supporting Information (Files uploaded separately)}
+%\begin{enumerate}
+%\item Captions for Datasets S1 to Sx
+%\item Captions for large Tables S1 to Sx (if larger than 1 page, upload as separate excel file)
+%\item Captions for Movies S1 to Sx
+%\item Captions for Audio S1 to Sx
+%\end{enumerate}
 
-The global energy budget of Earth is often considered in a mean, equilibrated context.
-However, fluctuations in the TOA net radiative flux are observed on monthly, yearly, and decadal scales.
-The decadal variability of the energy budget is also present in the global mean cloud radiative effect.
-This paper elucidates the nature of changes to the cloud fields in simulations covering 1871-2005.
-By clarifying key geographical regions and particular types of clouds that play a prominent role in the decadal variability of the TOA net radiative flux we hope to increase our confidence in the equilibrated energy budget analysis of Earth.
+\noindent\textbf{Additional Information for Boundary Condition and Parameterization Details}
+%Type or paste your text here. The introduction gives a brief overview of the supporting information. You should include information %about as many of the following as possible (when appropriate):
+% 1. a general overview of the kind of data files;
+% 2. information about when and how the data were collected or created;
+% 3. a general description of processing steps used;
+% 4. any known imperfections or anomalies in the data.
+This experiment drives AGCMs with observationally based SST and sea-ice concentrations while the forcing due to greenhouse gases, aerosol, and solar forcing, is held constant at assumed pre-industrial levels.
+However, due to the different time at which these models were actively used there are small differences in the boundary conditions.
+For the SST and sea ice concentration boundary conditions the AM2.1 model uses a combination of HADISST and NOAA data [Hurrel et al., 2008], AM3 uses version 1 of HADISST, and AM4.0 uses PCMDI-AMIP SST and sea ice boundary conditions which have been derived from observations, the method of derivation is described in Taylor et al.
+2000 and Hurrel et al., 2008 with current details available at https://pcmdi.llnl.gov/mips/amip/.
+The preindustrial forcing is based on assumed values from 1860 for AM2.1 and AM3, but from 1850 for AM4.0.
+It is not expected that these differences in the initial conditions and boundary conditions would lead to alternate climate responses.
+The land surface evolves freely.
 
-    \begin{enumerate}
-        \item Decadal variations of global feedback in AMIP-like experiments offer an opportunity for 
-        mechanistic attribution
-        	\begin{enumerate}
-	    \item SST patterns have been shown to be important for variations of global 
-	    feedback (Gregory and Andrews, 2016).  
-	    \item Estimated Inversion Strength (EIS)
+The AM4.0 and AM3 models include an aerosol indirect effect with a prognostic cloud drop number.  The AM2.1 model specified the cloud drop number to be 100 (300) over ocean (land).
 
-	    The lower-tropospheric stability, and the related estimated inversion strength (EIS) has been used as a predictor of low-level clouds in select stratocumulus dominated regions (Klein and Hartmann, 1993, Wood and Hartmann, 2006).
-The tropical marine EIS was found by Zhou et al.
-2016 to be well correlated with the evolution of tropical tropical low-cloud change.
-The EIS can be approximated by a linear combination of the surface temperature and the temperature on the 700hPa pressure level.
-In the tropics, this provides a glimpse of one influence of the convection parameterization because the mid-tropospheric temperature is largely determined by the lapse rate in the warm pool regions with strong deep convection.
+\noindent\textbf{Additional Results}
 
-	    \item Analyzing alternate atmospheric climate models with the same SST 
-	    patterns and atmospheric forcing throughout the twentieth century highlights
-	    both atmospheric internal variability and the impact of different parameterization 
-	    configurations among the models.
-	    \item Why AM2.1, AM3, and AM4g10r8?
-	\end{enumerate}
-	\item Relationship between decadal feedback, equilibrium climate sensitivity, and effective climate sensitivity
-	\item Review of Gregory and Andrews 2016, Zhou et al. 2016, Qu et al. 2014,2015, and Paytner et al. 2017
-    \end{enumerate}
+The paper by Qu et al., 2014 documented an inter-model analysis of the statistics from 5 geographic windows which were identified as important for low cloud cover.
+Their windows encompass large swaths of the oceans which include many cloud types.
+We have computed the regional decomposition of the climate feedback parameter over their 5 windows using the same methodology described in our primary manuscript (SPZ herafter; Silvers, Paynter, and Zhao).
+Results are shown in Figure \ref{fig:quwindows}.
+This figure is identical to SPZ Figure 1.b, but with the climate feedback parameter computed with Qu et al.'s windows shown as the thin small-dashed lines.   
+The rest of the tropics (between $\pm 30^{\circ}$ minus the 5 windows) are shown with thin long-dashed lines.
+The conclusion that most of the decadal variability of the climate feedback parameter is due to the greater tropics and not due to the regions defined by these specific geographic windows holds true.
+There is very little difference between the results of the windows used in the primary analysis and those from Qu et al., 2014.
+This indicates that even if our region of interest is expanded, and the northern tropical Atlantic region included as in Qu et al., 2014, the temporal variability of $\alpha$ is still not captured.
 
-\section{Method}
-%    \begin{enumerate}
- %       \item Description of amipPiForcing experiments
-\subsection{Description of amipPiForcing experiments}
+The change of the total cloud field (computed as the linear 30 year trend)  as observed by ISCCP between 1983-2009 is shown in Figure \ref{fig:isccp}.
+Although the pattern of cloud cover changes is complex many of the regions of increasing cloud occur over regions with a weak or even decreasing trend of surface temperature (compare with the late period of Figure 2 of SPZ).
+This agrees well with the results of Z16 and implies that low-level stability is likely an important factor in the change of global cloud fields.
 
-        The primary experiment used in this work corresponds to the amip-piForcing experiment.
-For this experiment the AGCMs are run using observed SST and sea-ice, but with the forcing due to GHG, aerosol, and solar forcing set to assumed pre-industrial levels and held constant throughout the experiment.
-The time simulated is from 1870 to 2005.
-The amip-piForcing experiments are sometimes referred to as a `long-AMIP' experiments.
-The amip-piForcing experiment has been included as one of the tier-II experiments for CFMIP3 (Webb et al.
-2017), for additional details and examples see Gregory and Andrews (2016) and Zhou et al.
-(2016).
+%To quantify the influence of regional changes in LCC on the TOA radiative budget the long-wave CRE (LWCRE) and short-wave CRE (SWCRE) trends are computed over the two periods of interest.
+Global fields for AM4.0 are shown in Figs. 2 and 3 of SPZ and mean values over the windows described in SPZ are given in SM Table 1.  
+%The windows used to compute mean values for SM Table 1 were chosen to represent regions of importance highlighted by our results and previous literature.  
+%The eastern Pacific window mimics the area of importance discussed in Z16.
+We used the definition of the Peruvian and Californian windows from Klein and Hartmann, 1993, expanded them and added them together to measure the LCC and SWCRE trends in the eastern Pacific.
+The Indian, south Atlantic, and southern ocean windows were chosen because of the large trends in both the LCC and SWCRE there (see figs.
+2 and 3 of SPZ).
+SM Table 1 shows a large increase of LCC trend in the late period in all windows, which coincides to a significant strengthening of the negative SWCRE.  
+This should be contrasted with the fact that in the early period all regions have either a decrease in LCC, or only a small increase.
+The decreasing LCC of the early period correspond to positive SWCRE.
+This confirms the importance of the east Pacific region but shows that the LCC trend in the other regions have an equally large (if not larger) impact on the SWCRE.
+%The changing SWCRE of these 4 regions is consistent with a more sensitive climate during the early period and a less sensitive climate in the  late period.
 
-\subsection{Description of AM2.1, AM3, and AM4g10r8}
+The linear decomposition of the low-level cloud field given by equation 3 and illustrated with Figure 3.b in SPZ is further examined here.
+The results of the decomposition for the latitude ranges $\pm 30^{\circ}$ and $\pm 60^{\circ}$ are tabulated in in SM Table 2.
+Shown are the coefficients $\gamma$ and $\beta$ for each model as well as the correlation coefficients between the LCC anomaly from model output compared with the linear approximation of the LCC anomaly using $\gamma$ and $\beta$.
+For completeness we also show the time series for the region between $\pm 30^{\circ}$ in Figure 3.
 
-        The three GFDL atmospheric models analyzed in this paper have many differences, but the those that are thought to be of primary importance to the top-of-the-atmosphere radiation budget are relatively few.
-The AM3 and AM4g10r8 models include an aerosol indirect effect by including the cloud drop number as a prognostic variable.
-The AM2.1 model diagnosed the cloud drop number.
-The parameterization schemes used to represent cumulus convection differs significantly among the three models.
-The AM2.1 model uses the Relaxed-Arakawa-Schubert (RAS) scheme, AM3 uses the Donne-Deep scheme for deep convection and the University of Washington shallow convection scheme (UWShCu, Bretherton et al.
-2004) for shallow convection.
-AM4g10r8 uses a version of the UWShCu scheme that has been modified to include two bulk plumes which can account for both shallow and deep convection.
-In addition to these differences, the scheme which computes the radiative transfer was updated from SEALW99/ESFSW99 in AM2.1 and AM3 to SEALW16/ESFSW16 in AM4g10r8.
+\noindent\textbf{Computational details of the Estimated Inversion Strength}
 
-\subsection{Methodology of Analysis (here or in results?)}        
-%        \begin{enumerate}
-%            \item Global feedback parameter via Gregory regression sliding window
-            Because our interest is in the covariation of R and T rather than the change relative to a control state we compute the differential climate feedback parameter in the same was as in Gregory and Andrews [2016].
-That is, linear regression is used to compute the trend between R and T.
-The regression is applied to the global yearly mean values over 30 windows.
-The values plotted in Figure 1 represent the mid-point of each window.
- %           \item Global maps and global mean time series of trends per years
-            To determine the spatial pattern of changes to particular variables linear regression was used at each grid point.              
- %           \item Estimated Inversion Strength
-
-            The estimated inversion strength can be thought of as a correction to the LTS based on the moist adiabatic profile.  The LTS is defined to be $\rm{LTS}=\theta_{700}-\theta_{sfc}$.  
-            To compute the estimated inversion strength (EIS) we follow the approximation made by Wood and Bretherton [2006]: 
+To compute the EIS following Wood and Bretherton we use 
 \begin{equation}
-              \rm{EIS} = \rm{LTS} - \Gamma^{850}_m (z_{700}-\rm{LCL})
+  \rm{EIS}=\rm{LTS}-\Gamma_m^{850}(z_{700}-\rm{LCL})
 \end{equation}
 with the lifting condensation level (LCL) calculated as $\rm{LCL}=(20+(T_{sfc}-273.15)/5)(1-RH_{sfc})$.
+
             The potential temperature gradient for moist-adiabatic processes is calculated as
@@
 
-%    \end{enumerate}
+%\clearpage
 
-\section{Results}
+%Delete all unused file types below. Copy/paste for multiples of each file type as needed.
+%\noindent\textbf{Text S1.}
+%Type or paste text here.
+This should be additional explanatory text, such as: extended descriptions of results, full details of models, extended lists of acknowledgements etc.
+It should not be additional discussion, analysis, interpretation or critique.
+It should not be an additional scientific experiment or paper.
+%
+%Repeat for any additional Supporting Text
 
-%\begin{enumerate}
- %   \item General Results
-\subsection{General Results}
+%%Enter Data Set, Movie, and Audio captions here
+%%EXAMPLE CAPTIONS
 
-We have shown that all three models exhibit strong decadal variability of the feedback parameter.
-The close connection between the global feedback and the CREs is clear based on their respective time series.
-Correlations between the global feedback parameter and CRE for each model are: 0.93, 0.93, and 0.81 for AM2.1, AM3, and AM4g10r8, respectively.
+%\noindent\textbf{Data Set S1.} %Type or paste caption here.
+%upload your dataset(s) to AGU's journal submission site and select "Supporting Information (SI)" as the file type. Following naming %convention: ds01.
 
-Over the second half of the twentieth century AM4g10r8 and AM3 show a strong decrease of the global feedback parameter and the CRE response (Fig.
-\ref{fig:alphacre}).
-Both of these models also have an increasing trend of EIS during this time period (Fig.
-\ref{fig:alphacre}).
-In contrast, AM2.1 has a weak decrease of global feedback parameter and a nearly constant CRE trend during this time period.
-The trend of EIS for AM2.1 is relatively flat and less than that for AM4g10r8 and AM3.
-%If the change of LLC can be linearly decomposed into a component due to the EIS and one due to the change of SST I would then expect this to indicate a poorer correlation for AM2.1 compared to AM3 in the tropics.
-Between 1925 and 1955 the average global feedback parameter for AM4, AM3, and AM2.1 changes from average values of (-1.35, -1.02, -1.80) to (-2.22, -2.42, -2.20) between 1975 and 1989.
-This represents a dramatic change in the global feedback parameter and determining the cause will be an important part of our ability to understand how clouds influence the global energy budget on decadal time scales.
+%Repeat for any additional Supporting data sets
 
-%Changes in low-cloud cover where approximated by Zhou et al.
-2016 as $\Delta \rm{LCC} = \delta \Delta \rm{EIS} - \gamma \Delta \rm{SST}$.
-If this holds then to the extent that different models use the same SST fields, the change of LCC should follow the change of EIS.
-%The importance of different SST patterns with the same mean value has been recognized (Andrews et al.
-2015).
-Is there a similar importance of the EIS pattern?
-In this context the hypothesis (Qu et al.
-2014,2015) that changes of EIS can be approximated as
-%$\Delta \rm{EIS} \approx \alpha \Delta T_{700}-\beta \Delta T_s $ indicates that the pattern of EIS change is entirely (for the case of the same SST) determined by the change of temperature on the 700 hPa level.
-This is an easier quantity to diagnose from GCMs than EIS.
+%\noindent\textbf{Movie S1.} %Type or paste caption here.
+%upload your movie(s) to AGU's journal submission site and select, "Supporting Information %(SI)" as the file type. Following naming convention: ms01.
 
-%All three models show an increase of the anomalous tropical mean low-level clouds and EIS between about 1975 and 2005, with the increase in AM2.1 covering the smallest period of time.   
-%The tropical marine low-cloud changes in AM4g10r8 are well explained (r=0.96) by a linear combination of the changes in the EIS and the SST.  
-%To the extent that the MAC LWP from Norris et al. 2016 represents a realistic trend of LWP the AM4g10r8 LWP trend shows a more realistic trend than AM2.1.  
-%Because of the large amount of the anomalous change in low-cloud cover that can be explained by the linear combination of EIS and SST, as in CAM5.3, it is tempting to conclude that AM4g10r8 is doing the best job at reproducing observed relationships between EIS and low-cloud cover.
-%However, AM4 needs to be tested for its representation of the cloud controlling factors which have been discussed by Bretherton, and are shown in Figure 1 of the supplementary material of Zhou et al.
-2016.
+%Repeat any additional Supporting movies
 
-The period after about 1975 is found by all three models to have a small climate sensitivity (large, negative feedback parameter, Fig.
-\ref{fig:alphacre}) and a negative CRE.
-This period also corresponds in all three models to an increase of tropical mean low-level clouds  (Fig.
-\ref{fig:lccts}).
-Computing the trend of LCC change between 1975-2005 reveals much of this change to be concentrated in the eastern Pacific ocean basins (Fig.
-\ref{fig:lcceis_late}) in agreement with the findings of Zhou et al.
-2016.
-Further analysis of the changes to low-level clouds is discussed in the next section.
+%\noindent\textbf{Audio S1.} %Type or paste caption here.
+%upload your audio file(s) to AGU's journal submission site and select "Supporting Information %(SI)" as the file type. Following naming convention: auds01.
 
-A strong relationship between LCC and EIS in many regions of the globe is shown by the trends of LCC and EIS between 1975-2005 (Figure \ref{fig:lcceis_late}) and between 1925-1955 (Figure \ref{fig:lcceis_early}).
-Both time periods have a large increase of both EIS and LCC in the equatorial eastern Pacific ocean.
-However, during the later period there is an increase of LCC throughout much of the Southern Hemispheric oceans while the early period the LCC decreases in much of the Southern Hemispheric oceans and northern midlatitudes.
-This is consistent with a positive cloud feedback/large climate sensitivity during the early period and a small cloud feedback/climate sensitivity during the later period (Fig.
-\ref{fig:alphacre}).
-
-%    \item Multiple Linear Regression 
-\subsection{Multiple Linear Regression}
-
-    The anomalous changes of tropical marine low-cloud cover were shown to be well explained by a linear combination of the change in EIS and SST in Zhou et al.
-2016.
-We explore the linear dependence of low-cloud changes on EIS and SST using multiple linear regression to determine the relative contributions of each component.
-The coefficients $\gamma$ and $\delta$ can thus be determined for particular experiments or models in the following assumed relationship:
-    \begin{equation} 
-    \Delta \rm{LCC} \approx \gamma \Delta \rm{EIS} - \delta \Delta \rm{SST}.
-    \label{eqLCC}
-    \end{equation}  
-Based on high correlations between changes in low-cloud cover and the linear combination of changes in EIS and SST the above relationship holds fairly well.
-However, we find that the relative contributions of EIS and SST to the low-cloud cover is model dependent.
-Because the three models examined here all have observationally based SST prescribed, this difference likely indicates differences in the relative importance of the EIS fields which are in turn driven by the temperature on the $700 \rm{hPa}$ surface.
-The importance of the low-level and mid-tropospheric temperature field is not surprising.
-The direct connection between the temperature field at particular levels with parameterization schemes (convection, turbulence) provides an encouraging link between details of the parameterizations and the low-level cloud field.
-
-Several noteworthy points can be drawn from Table 1.
-As shown by the correlation coefficients, the decomposition used by Zhou et al.
-2016 to explain the variance in the change of the low-cloud cover is not directly applicable to other models.
-Using multiple linear regression to approximate the best fit for each model explains a significantly higher proportion of the variance in the changing low-cloud cover.
-Also interesting are the varying coefficients computed for Eq.
-ref{eqLCC}.
-This indicates that each of the models has a different relative sensitivity of low-clouds to EIS and SST.
-
-Several noteworthy points can be drawn from Table 1.
-As shown by the correlation coefficients, the decomposition used by Zhou et al.
-2016 to explain the variance in the change of the low-cloud cover is not directly applicable to other models.
-Using multiple linear regression to approximate the best fit for each model explains a significantly higher proportion of the variance in the changing low-cloud cover.
-Also interesting are the varying coefficients computed for Eq.
-ref{eqLCC}.
-This indicates that each of the models has a different relative sensitivity of low-clouds to EIS and SST.
-
-We find some agreement with previously published work, but also some interesting differences.
-Our results, as well as those of Grise and Medeiros, 2016, and Paytner et al.
-2017 indicate that low-level clouds, and thus the TOA net CRE, strongly depend on both EIS and the large-scale vertical velocity, omega.
-
-\subsection{Linear approximation of the Estimated Inversion Strength}
-
-Changes in the EIS where shown to be well approximated as a linear combination of the surface temperature and the temperature on the $700 \rm{hPa}$ pressure level by Qu et al. 2014.  Specifically,
-\begin{equation}
-  \Delta \rm{EIS} \approx \alpha \Delta T_{700}-\beta \Delta T_{sfc},
-  \label{eq:eis}
-\end{equation}
-where $T_{sfc}$ and $T_{700}$ are the temperatures on the surface and the $700 \rm{hPa}$ pressure surface, respectively.
-This provides an elegant simplification of the EIS and shows its close relation to the lower troposheric stability (different of potential temperature between 700 hPa and the surface).
-In the atmosphere the relative influence of the $T_{sfc}$ and $T_{700}$ on the EIS varies depending on location.
-One of the strengths of long-AMIP experiments is the use of observed SST so modeled differences in the marine EIS fields will be largely due to modeled differences in $T_{700}$.
-Approximations of EIS using eq.
-\ref{eq:eis} are compared with the simulated change of EIS in Figures \ref{fig:lcceisapp_am4}-\ref{fig:lcceisapp_am2}.
-Overall the approximation captures the spatial patterns of changes in the EIS field, but the magnitude is overestimated.
-
-%\end{enumerate}
-
-\section{Conclusions}
-
-The eastern Pacific has been shown to be a key location where decadal trends in SST and low-level clouds can strongly influence the global energy budget.
-
-These changes in low-level clouds were shown to be well modeled by a linear combination of anomalous EIS and SST.
-However, the coefficients of the decomposition vary among the models.
-This implies that the models do not weight the influence of EIS and SST in the same way.
-The response of low-level clouds thus depends to differing degrees on the changes in the 700 hPa temperature.
-This provides a relatively simple connection between differing model parameterizations and the response of the clouds to changing SST patterns.
-
-We have also shown that the although the three models respond similarly to the SST patterns between 1975-2005, their response to the SST patterns throughout the twentieth century differs dramatically.
-The contrast in response between the period of 1975-2005 and 1925-1955 is emphasized.
-
-Using the observed sea surface temperature and ice concentrations as the lower boundary for the atmosphere eliminates the feedback processes between the atmosphere, land, and ocean in nature.
-However, using these observations ensures that the atmospheric models are driven by the the same patterns and magnitudes of warming.
-This provides an excellent test of how much freedom of response the atmosphere alone is capable of given similar boundary conditions.
+%Repeat for any additional Supporting audio files
 
 %%% End of body of article:
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% Optional Appendix goes here
-%
-% \appendix resets counters and redefines section heads
-% but doesn't print anything.
-% After typing \appendix
-%
-\appendix
-%\section{Here Is Appendix Title}
-% will show
-% Appendix A: Here Is Appendix Title
-%
-\section{A few of Levi's questions}
-\begin{enumerate}
-
-\item The differential climate feedback parameter in Fig.
-1 shows a relatively smooth transition from the small negative values during the period 1925-1955 and the larger negative values between 1975-2005.
-Why does the time series of tropical change in LCC in Fig.
-6 look so different?
-It looks almost like there is a 30 year oscillation in the tropical LCC.
-
-\item How much do the differences in the surface temperature data matter?  How much do differences over land matter?
-
-\item Should we incorporate the vertical velocity into the paper?
-
-\item What is the relationship between these results and the 5 typical strato-cumulus regions that are often studied?
-
-\item According to Xu et al.
-2014, GFDL-CM2.0, GFDL-CM2.1, GFDL-CM3, GFDL-ESM2G, and GFDL-ESM2M (H,I,f,g,h) all use cloud-top radiative cooling to drive boundary layer turbulence.
-Is this also the case for AM4?
-They list all three as having a 'K profile' PBL scheme type and a Prognostic cloud scheme type.
-
-\end{enumerate}
-This study does not address the known spread of LCC change due to differing sensitivities of models to changing SST.
-Because all three of our models are driven with observed SST the different responses are due to differences of the atmospheric response to the boundary conditions (to what extent is the large-scale circulation tied to the SST?).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 %
-% Optional Glossary or Notation section, goes here
+% Optional Notation section goes here
 %
-%%%%%%%%%%%%%%
-% Glossary is only allowed in Reviews of Geophysics
-% \section*{Glossary}
-% \paragraph{Term}
-% Term Definition here
-%
-%%%%%%%%%%%%%%
 % Notation -- End each entry with a period.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  ACKNOWLEDGMENTS
-
-%\begin{acknowledgments}
-%(Text here)
-%\end{acknowledgments}
 
@@
 %   copy all the contents into your LaTeX file here.
+\begin{thebibliography}{6}
+\providecommand{\natexlab}[1]{#1}
+\expandafter\ifx\csname urlstyle\endcsname\relax
+  \providecommand{\doi}[1]{doi:\discretionary{}{}{}#1}\else
+  \providecommand{\doi}{doi:\discretionary{}{}{}\begingroup
+  \urlstyle{rm}\Url}\fi
+
+%\bibitem[{\textit{Bretherton et~al.}(2004)\textit{Bretherton, Peters, and
+%  Back}}]{Bretherton_etal_2004}
+%Bretherton, C.~S., M.~E. Peters, and L.~E. Back (2004), A new parameterization
+%  for shallow cumulus convection and its application to marine subtropical
+%  cloud-topped boundary layers. part i: Description and 1-d results,
+%  \textit{Mon.\ Wea.\ Rev.}, \textit{132}, 864--882.
+%
+%\bibitem[{\textit{Donner and Coauthors}(2011)}]{Donner_etal_2011}
+%Donner, L.~J., and Coauthors (2011), The dynamical core, physical
+%  parameterizations, and basic simulation characteristics of the atmospheric
+%  component {AM3} of the {GFDL} global coupled model {CM3}, \textit{JCLI},
+%  \textit{24}, 3484--3519, \doi{10.1175/2011JCLI3955.1}.
+%
+%\bibitem[{\textit{GFDL-GAMDT}(2004)}]{GFDL_GAMDT_2004}
+%GFDL-GAMDT (2004), The new {GFDL} global atmosphere and land model {AM2}/{LM2}:
+%  Evaluation with prescribed {SST} simulations, \textit{JCLI}, \textit{17},
+%  4641--4673, \doi{10.1175/JCLI-3223.1}.
+
+\bibitem[{\textit{Hurrell et~al.}(2008)\textit{Hurrell, Hack, Shea, Caron, and
+  Rosinski}}]{Hurrell_etal_2008}
+Hurrell, J.~W., J.~J. Hack, D.~Shea, J.~Caron, and J.~Rosinski (2008), A new
+  sea surface temperature and sea ice boundary dataset for the community
+  atmosphere model, \textit{JCLI}, \textit{21}, 5145--5153,
+  \doi{10.1175/2008jcli2292.1}.
+
+%\bibitem[{\textit{Moorthi and Suarez}(1992)}]{Moorthi_Suarez_1992}
+%Moorthi, S., and M.~Suarez (1992), Relaxed arakawa schubert: A parameterization
+%  of moist convection for general circulation models, \textit{Mon.\ Wea.\
+%  Rev.}, \textit{120}, 978--1002.
+
+\bibitem[{\textit{Norris and Evan}(2015)}]{Norris_Evan_2015}
+Norris, J, R., and A.T..~Evan (2015), Cloud Properties from ISCCP and PATMOS-x Corrected for Spurious Variability Related to Changes in Satellite Orbits, Instrument Calibrations, and Other Factors.
+\textit{Research Data Archive at the National Center for Atmospheric Research, Computational and Information Systems Laboratory}.,
+Accessed June 1 2017,
+\doi{10.5065/D62J68XR}.
+
+\bibitem[{\textit{Qu et~al.}(2014)\textit{Qu, Hall, Klein, and
+  Caldwell}}]{Qu_etal_2014}
+Qu, X., A.~Hall, S.~A. Klein, and P.~M. Caldwell (2014), On the spread of
+  changes in marine low cloud cover in climate model simulations of the 21st
+  century, \textit{Clim.\ Dynam.}, \textit{42},
+  \doi{10.1007/s00382-013-1945-z}.
+
+\bibitem[{\textit{Taylor et~al.}(2000)}]{Taylor_etal_2000}
+Taylor, K. ~E., and D. Williamson, and F. Zwiers (2000), The sea
+  surface temperature and sea-ice concentration boundary conditions
+  of {AMIP} {II} simulations, {PCMDI}, Rep. 60, 20 pp., \doi{10.1175/JCLI-D-17-0062.1}.
+
+\bibitem[{\textit{Wood and Bretherton}(2006)}]{Wood_Bretherton_2006}
+Wood, R., and C.~S. Bretherton (2006), On the relationship between stratiform
+  low cloud cover and lower-tropospheric stability, \textit{JCLI}, \textit{19},
+  6425--6432, \doi{10.1175/JCLI3988.1}.
+
+\end{thebibliography}
 %
@@
 \end{article}
+\clearpage
+
+% Delete all unused file types below. Copy/paste for multiples of each file type as needed.
+
+% enter figures and tables here:
 %
-%
-%% Enter Figures and Tables here:
-
-\begin{table}
-    \caption{Coefficient terms (Eq.
-\ref{eqLCC}) in the decomposition of $\Delta \rm{LCC}$ for AM2.1, AM3, AM4p0, and CAM5.3.
-Also shown are the correlation coefficients between the GFDL models and the decomposition from Zhou et al.
-2016, and between each model and the $\Delta \rm{LCC}$ simulated for that model.
-All values are computed as tropical means ($\pm 30^{\circ}$).}
-    \begin{center}
-    %\begin{tabular}{| l | l | l | l | p{5cm} |}
-    %\begin{tabular}{l*{3}{c}r}
-    \begin{tabular}{*{5}{c}}
-    \hline
-    %\multicolumn{5}{|c|}{Experimental Specifications} \\
-    \hline
-    Model      & $\gamma$                                      & $\delta$    &     Zhou et al.  CC       & $\Delta \rm{LCC}$ CC         \\ \hline
-    AM2.1           &   4.7  &    -0.1            &  0.59    & 0.88                                          \\
-    \\
- %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
-    AM3                & 5.6   &  -0.5           &   0.59   & 0.77                                          \\ 
-    \\
- %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
-    AM4p0              & 3.5 &  -0.3          & 0.70    &   0.70                                                     \\ 
-    \\
-  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
-    CAM5.3               & 3.7 &  -0.9     & 1       &    ??                                                     \\ 
-    \\
-   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
-    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
-     \end{tabular}\par
-     \label{LCCtable}
-\end{center}
-\end{table}
-%
-%
-% DO NOT USE \psfrag or \subfigure commands.
-%
-% Figure captions go below the figure.
-% Table titles go above tables; all other caption information
-%  should be placed in footnotes below the table.
-%
-%----------------
 % EXAMPLE FIGURE
-%
- %\begin{figure}
- %\noindent\includegraphics[width=20pc]{samplefigure.eps}
+% ---------------
+% \begin{figure}
+%\setfigurenum{S1} %%Change number for each figure
+% \noindent\includegraphics[width=20pc]{samplefigure.eps}
 %\caption{Caption text here}
@@
  %\end{figure}
-%
-
-%\begin{figure}
- % \includegraphics[width=6.0in]{figures/alpha_ts_am4am3am2_longamip_30yrwind_phat.pdf}
-%  \caption{Time evolution of the global mean feedback parameter ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).  
-%  Time series have been computed by linear regression of the global, yearly mean TOA net radiative imbalance and the surface 
-%  temperature over a sliding 30 window.}
-%\end{figure}
 
  \begin{figure}
- % \includegraphics[width=6.0in]{figures/alpha_2panel_ts_am4am3am2_longamip_30yrwind_allensmbrs.eps}
-  \includegraphics[width=6.0in]{figures/alpha_ts_am4am3am2_longamip_30yrwind_mostensmbrs.eps}
-  \caption{Upper panel: Time evolution of the global mean feedback parameter ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).  
-  Time series have been computed by linear regression of the global, yearly mean TOA net radiative imbalance and the surface 
-  temperature over a sliding 30 window.  Lower panel: Time evolution of the global mean Cloud Radiative Effect ($\rm{W/m^2 K}$) for 
-  AM4g10r8(black), AM3(red), and AM2.1(blue).}
-  \label{fig:alphacre}
-\end{figure}
-
-%\begin{figure}
-%  \includegraphics[width=6.0in]{figures/alpha_cre_ts_am4am3am2_longamip_30yrwind_phat.pdf}
-%  \caption{Time evolution of the global mean Cloud Radiative Effect ($\rm{W/m^2 K}$) for AM4g10r8(black), AM3(red), and AM2.1(blue).}
-%\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/eistrend_ts_am432_longamip_tr_bold_30yrwind_new.pdf}
-  \caption{Time evolution of the global mean Estimated Inversion Strength ($\rm{K/30 yr}$) for AM4g10r8(black), AM3(red), and    
-                AM2.1(blue).  Global mean shown as thin solid lines and tropical mean values as thick solid lines.}
-  \label{fig:eis}
+ \includegraphics[width=4.0in]{alpha_tseries_1pan_quwindows.eps}
+ \caption{Time series analysis of AM4.0(black), AM3(green), and AM2.1(blue). Global climate feedback parameter $\alpha$ ($\rm{W/m^2 K}$),  
+  decomposed into contributions from tropical windows (small-dashed), the rest of tropics (long-dashed), and the global value (solid).  Figure is identical to Figure 1.B in SPZ
+  but with the addition of values (thin lines) computed using the 5 'low cloud region' windows from Qu et al. 2014 (thin, small-dashed) and the rest of the tropics (thin, long-dashed).}
+   \label{fig:quwindows}
  \end{figure}
@@
  \begin{figure}
-  \includegraphics[width=6.0in]{figures/lcceis_late.eps}
-  \caption{Trends of the low-cloud cover (left) and estimated inversion strength (right) during the period 1975-2005 for AM4 (top), AM3 (middle), and AM2(bottom).
-Trends were computed with linear regression at each grid point for the variable of interest.}
-  \label{fig:lcceis_late}
+  \includegraphics[width=4.0in]{isccp_tc_trend_19832005_norm.eps}
+  \caption{Trend of total cloud fraction (\% per 30 yr) using ISCCP data between 1983 and 2005.
+The magnitude has been normalized to result in a trend per 30 years, comparable to figures in main article showing trends of cloud fraction.
+The ISCCP data has been corrected to remove spurious artifacts.
+See \textit{Norris and Evan}, [2015]}
+  \label{fig:isccp}
 \end{figure}
@@
 \begin{figure}
-  \includegraphics[width=6.0in]{figures/lcceis_early.eps}
-  \caption{As in previous figure but for the period 1925-1955.}
-  \label{fig:lcceis_early}
+  \includegraphics[width=4.0in]{LCC_appbyeis_ensmn_ts_pm30.eps}
+  \caption{Time evolution of the tropical mean ($\pm 30^{\circ}$) change in low-cloud cover ($\Delta \rm{LCC}$) for AM2.1(blue), AM3(red), AM4.0(black).
+Thick lines show the       simulated $\Delta \rm{LCC}$ while thin lines show $\Delta \rm{LCC}$ approximated using Eq.
+2 with coefficients determined by multiple linear regression (see Table \ref{LCCtable}).
+A nine-year running mean has been used to smooth the data series.}
+  \label{fig:lccts_pm30}
 \end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/delLCC_AM2AM3AM4_pm30.eps}
-  \caption{Time evolution of the tropical mean ($\pm 30^{\circ}$) change in low-cloud cover ($\Delta \rm{LCC}$) for AM2.1(blue), AM3(red), AM4p0(black).
-Thick lines show the       simulated $\Delta \rm{LCC}$ while thin lines show $\Delta \rm{LCC}$ approximated using Eq.
-\ref{eqLCC} with coefficients determined by multiple linear regression (see Table \ref{LCCtable}).
-A nine-year running mean has been used to smooth the data series.}
-  \label{fig:lccts}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/hccomega_late.eps}
-  \caption{Trends of the high-cloud cover (left) and vertical velocity (omega) on the 500 hPa level (right) during the period 1975-2005 for 
-                AM4 (top), AM3 (middle), and AM2(bottom).  Trends were computed with linear regression at each grid point for the variable of 
-                interest.}
-  \label{fig:hccomega_late}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/hccomega_early.eps}
-  \caption{As in previous figure but for the period 1925-1955.}
-  \label{fig:hccomega_late}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/tref_t700_am4am3am2_late.eps}
-  \caption{Trends of the Tref (left) and temperature on the 700hPa level (right) during the period 1975-2005 for AM4 (top), AM3 (middle), and AM2(bottom).
-Trends were computed with linear regression at each grid point for the variable of interest.}
-  \label{fig:tref_t700_late}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/tref_t700_am4am3am2_early.eps}
-  \caption{As in previous figure but for the period 1925-1955.}
-  \label{fig:tref_t700_early}
-\end{figure}
-
-\begin{figure}
-  %\includegraphics[width=6.0in]{figures/am4g10r8_eis_t700_tsurf_trend_endtime1620.eps}
-  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am4late.pdf}
-  \caption{Trends during the period 1975-2005 for AM4g10r8.  Trends were computed with linear regression at each grid point for the variable of interest.}
-  \label{fig:lcceisapp_am4}
-\end{figure}
-
-\begin{figure}
-  %\includegraphics[width=6.0in]{figures/am3p9_eis_t700.pdf}
-  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am3late.pdf}
-  \caption{Trends during the period 1975-2005 for AM3.  Trends were computed with linear regression at each grid point for the variable of interest.}
-  \label{fig:lcceisapp_am3}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.0in]{figures/glb_eis_llc_t700_tsurf_trend_6pan_am2late.pdf}
-  \caption{Trends during the period 1975-2005 for AM2.  Trends were computed with linear regression at each grid point for the variable of interest.}
-  \label{fig:lcceisapp_am2}
-\end{figure}
-
-%\begin{figure}
-%  \includegraphics[width=6.0in]{figures/am4g10r8_ts_anom_zhouetal_fig2c_trop_glob}
-%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
-%  mean over full time series for AM4g10r8.  
-%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
-%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
-%\end{figure}
-%%
-%\begin{figure}
-%  \includegraphics[width=6.0in]{figures/am3p9_ts_anom_zhouetalfig2c_glob_trop}
-%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
-%  mean over full time series for AM3.  
-%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
-%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
-%\end{figure}
-%%
-%\begin{figure}
-%  \includegraphics[width=6.0in]{figures/am2_1_ts_anom_zhouetalfig2c_trop_gl}
-%  \caption{Global (top) and tropical (bottom) mean time series of low-level cloud anomalies (thick, solid line) computed relative to the 
-%  mean over full time series for AM2.1
-%  Also shown (thick dashed) is a an approximation of the low-level cloud anomalies computed as the linear combination of the EIS (thin solid) and the 
-%  temperature at 2m (Tref: thin dashed).  Time series have been smoothed with a 9 year running mean filter.}
-%\end{figure}
-%
-\begin{figure}
-  \includegraphics[width=6.2in]{figures/glb_rad_trends_late.eps}
-  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed between 1975 and 2005.}
-\end{figure}
-
-%\begin{figure}
-%  \includegraphics[width=6.2in]{figures/glb_trend_am4am3am2_early.pdf}
-%  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed over a 30 year period near the middle of the twentieth century.}
-%\end{figure}
-
-\begin{figure}
-  \includegraphics[width=6.2in]{figures/glb_rad_trends_early.eps}
-  \caption{TOA radiative fluxes $\rm{W/m^2 per 30yr}$ for AM4g10r8 (left), AM3 (center), and AM2.1(right).  Fields are trends computed between 1925 and 1955.}
-\end{figure}
-
-%\begin{figure}
-%  \includegraphics[width=6.0in]{}
-%  \caption{}
-%\end{figure}
 
@@
 %\begin{table}
+%\settablenum{S1} %%Change number for each table
 %\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
@@
 
-% See below for how to make sideways figures or tables.
+\begin{table}
+    \caption{Mean values of LCC, SWCRE, and EIS trends over select geographic windows of interest.
+All values computed for ensemble mean of AM4.0 experiments.
+Locations of windows are: East Pacific: (210-240 E; 10-30 N)+(250-280 E; 10-30 S); Indian: (60-90 E; 10-30 S); S.
+Atlantic: (330-360 E; 10-30 S); S.
+Ocean: (circumglobal; 50-60S)}
+    \begin{center}
+    %\begin{tabular}{| l | l | l | l | p{5cm} |}
+    %\begin{tabular}{l*{3}{c}r}
+    \begin{tabular}{*{5}{c}}
+    \hline
+    %\multicolumn{5}{|c|}{Experimental Specifications} \\
+    \hline
+    Region   &    Period   &  LCC ($\% / 30 \rm{yr}$)                   & SWCRE ($\rm{W/m^2 per 30 \rm{yr}}$)     &   EIS  ($\rm{K} / 30 \rm{yr}$) \\ \hline
+    East Pacific           &   1925-1955  &   0.12                                               &        0.26      &    0.01                              \\
+                                         &    1975-2005 &   2.91                                               &       -3.05     &     0.23    \\
+    \\
+ %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
+    Indian                     &   1925-1955    &   -0.78                                           &         3.41     &   0.09                    \\ 
+                                         &    1975-2005    &   3.06                                            &        -3.28     &   0.62       \\
+    \\
+ %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
+    S. Atlantic            &   1925-1955    & -0.41                                             &        1.06      &   0.03                          \\ 
+                                        &    1975-2005    &  2.42                                             &       -3.19      &   0.24  \\
+    \\
+  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
+    S. Ocean         &   1925-1955       & -1.30                                                &       0.86       &  -0.24       \\ 
+                                    &    1975-2005      &  0.62                                                &      -1.28       &   0.19    \\
+    \\
+   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
+    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
+     \end{tabular}\par
+     \label{LCCtable}
+\end{center}
+\end{table}
+
+\begin{table}
+    \caption{Coefficient terms in the decomposition of $\Delta \rm{LCC}$ (Eq. 3).  % for AM2.1, AM3, AM4.0, and CAM5.3.  
+    Columns 4 and 5 show correlation coefficients between the linear approximation (Eq. 3) for  each model and the $\Delta \rm{LCC}$ simulated for that model.  
+ Values are computed from time series of monthly means between years 1870 and 2005.  For reference comparable values from
+ Zhou et al. 2016 are also shown for the CAM5.3 model.}
+    \begin{center}
+    %\begin{tabular}{| l | l | l | l | p{5cm} |}
+    %\begin{tabular}{l*{3}{c}r}
+    \begin{tabular}{*{5}{c}}
+    \hline
+    %\multicolumn{5}{|c|}{Experimental Specifications} \\
+    \hline
+    Model      & $\gamma \pm 30^{\circ} (60^{\circ})$               & $\beta \pm 30^{\circ} (60^{\circ})$          & $\Delta \rm{LCC} \pm 30^{\circ}$      &   $\Delta \rm{LCC} \pm 60^{\circ}$  \\ \hline
+    AM2.1           &   4.7 (3.8)                  &    -0.13 (-0.02)                       &         0.89                       &    0.92                              \\
+    \\
+ %                         &                                                       &                         &  301 K    &  10 years                                         \\ \hline
+    AM3             & 5.6   (3.6)                   &  -0.53 (-0.13)                       &         0.78                       &   0.82                      \\ 
+    \\
+ %                         &                                                              &                          &  301 K    &   10 years                                               \\ \hline
+    AM4.0        & 4.8   (3.8)                    &  -0.39  (0.02)                   &          0.83                          &   0.87                           \\ 
+    \\
+  %                        &                                                 &                       & 301K       &       4 years                                                \\ \hline
+    CAM5.3     & 3.7                      &  -0.9                         &           0.76                                          &   -        \\ 
+    \\
+   %                       &                                                 &                                     & 301 K     &         2 years                                              \\ \hline
+    %                      &                                                 &                                     &  301 K               &     1 year                        \\ \hline
+     \end{tabular}\par
+     \label{LCCtable}
+\end{center}
+\end{table}
+
+% ---------------
+%
+% EXAMPLE LARGE TABLE (UPLOADED SEPARATELY)
+%\begin{table}
+%\settablenum{S1} %%Change number for each table
+%\caption{Time of the Transition Between Phase 1 and Phase 2\tablenotemark{a}}
+%\end{table}
 

### 2019-10-14 Silvers_WalkerCell.tex
commit probably old changes to the tex file that will likely result in conflicts when merged.

--- 2019-09-20 Silvers_WalkerCell.tex
@@
 
+\begin{figure}
+  \centering
+      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
+  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
+  while the P25 and P100 cases show only the first out of five years of the time series.}
+    \label{fig:precip_dom_mn}
+\end{figure}
+
 For the simulations that are closest to the set up of a GCM, with fully parameterized convection, the steady-state circulation and 
@@
 Note: check the wind shear for P25large, P100small, and P100large.
+
+Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
+the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
+simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+The large oscillations in domain mean precipitation are similar to those noted in previous studies 
+(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
+mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
+of the differences in upper level cloud fraction and will be further discussed.
 
@@
 
+\begin{figure}
+  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
+  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
+  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
+  Shading indicates mm/day.  The horizontal axis shows the entire 
+  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  Shown is the meridional average. }
+  \label{fig:hov_4mods_6mn}
+\end{figure}
+
 It is clear that the overturning circulation in the tropical Pacific encompasses dynamical motions at a host of scales and that the 
@@
 they are able to maintain a smoother distribution of  precipitation values over a broader range of SST values.
-
-\begin{figure}
-  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
-  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
-  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
-  Shading indicates mm/day.  The horizontal axis shows the entire 
-  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the meridional average. }
-  \label{fig:hov_4mods_6mn}
-\end{figure}
-
-Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
-the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
-simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
-The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
-mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
-of the differences in upper level cloud fraction and will be further discussed.
 
@@
       \includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
-          \caption{Domain mean total condensate (liquid + ice).  Solid lines show experiments with LWCRE on
+          \caption{Domain mean total condensate (liquid + ice) for P25 (thin yellow), E25 (yellow), 
+          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on
           and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
@@
       \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25v2v1_6pan_lwon.eps}
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_25vs2vs1_lwon.eps}
-      \caption{Comparison of the steady state relative humidity (shading) and mass streamfunction.  
+      \caption{The steady state relative humidity (shading) and mass streamfunction (black contours).  
       Shown is E25 (left), E2(center), and E1(right).  All panels use the same contour interval for the 
@@
       \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25v2v1_6pan_lwoff.eps}
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_25vs2vs1_lwoff.eps}
           \caption{Same as previous figure except with the longwave CRE turned off.}
@@
 
-\begin{figure}
-  \centering
-       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
-       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
-  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
-  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
-  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
-  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
-  in the center of the domain where the SST is warmest. }
-\end{figure}
+%\begin{figure}
+%  \centering
+%       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
+%       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
+%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
+%  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
+%  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
+%  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
+%  in the center of the domain where the SST is warmest. }
+%\end{figure}
 
@@
 and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
-there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the LW CRE on, significant 
-low-level clouds are formed, leading to a radiative cooling of almost 10K/day, and a radiative cooling of around -7K/day.   However, 
-when the LW CRE is off, there is no appreciable difference in the low-level diabatic profiles among the models with 3 grid-spacings.   It 
-is also clearly seen that the LW CRE decreases the upper-level ice-condensate for models of all grid-spacings while dramatically 
-increasing the low-level liquid condensate.
+there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the 
+LW CRE on, significant low-level clouds are formed, leading to a radiative cooling of almost 10K/day, 
+and a radiative cooling of around -7K/day.   However, when the LW CRE is off, there is no appreciable 
+difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It 
+is also clearly seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 
+experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure 
+\ref{fig:TotCond}).
 
-When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
-enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
-large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
-regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
+When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar 
+distribution and magnitude of surface enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the 
+LW CRE is on, there are differences between the resolutions that can be as large as $80 \, \rm{W/
+m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are 
+confined to the regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
 would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
 
-Relative to simulations with a grid-spacing of $25 \textit{km}$, the simulations with explicit convection can be characterized as having: 
+Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
 \begin{itemize}
@@
   that is 40\% higher than in the parameterized, lower resolution simulations.  
-  \item two to four times more ice condensate above about 600 hPa but only about half as much liquid condensate below about 700 hPa.
+  \item two to four times more ice condensate above 600 hPa but only about half as much liquid condensate below 700 hPa.
   \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 

### 2019-10-14 Silvers_WalkerCell.tex

--- 2019-10-14 Silvers_WalkerCell.tex
@@
 %Note: check the wind shear for P25large, P100small, and P100large.
+
+Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
+the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
+simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+The large oscillations in domain mean precipitation are similar to those noted in previous studies 
+(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
+mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
+of the differences in upper level cloud fraction and will be further discussed.
 
@@
 General Circulation Model to a Cloud Resolving Model}
+
+\begin{figure}
+  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
+  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
+  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
+  Shading indicates mm/day.  The horizontal axis shows the entire 
+  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  Shown is the meridional average. }
+  \label{fig:hov_4mods_6mn}
+\end{figure}
 
@@
 
-\begin{figure}
-  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
-  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
-  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
-  Shading indicates mm/day.  The horizontal axis shows the entire 
-  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the meridional average. }
-  \label{fig:hov_4mods_6mn}
-\end{figure}
-
-Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
-the total radiative cooling the time evolution of the precipitation serves as a useful measure of wether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
-simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
-The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
-mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
-of the differences in upper level cloud fraction and will be further discussed.
-
 Superposing the circulation and relative humidity illustrates the subsidence driven 
@@
 and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
-there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the LW CRE on, significant 
-low-level clouds are formed, leading to a radiative cooling of almost 10K/day, and a radiative cooling of around -7K/day.   However, 
-when the LW CRE is off, there is no appreciable difference in the low-level diabatic profiles among the models with 3 grid-spacings.   It 
-is also clearly seen that the LW CRE decreases the upper-level ice-condensate for models of all grid-spacings while dramatically 
-increasing the low-level liquid condensate.
-
-When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar distribution and magnitude of surface 
-enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the LW CRE is on, there are differences between the resolutions that can be as 
-large as $80 \, \rm{W/m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are confined to the 
-regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
+there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the 
+LW CRE on, significant low-level clouds are formed, leading to a radiative cooling of almost 10K/day, 
+and a radiative cooling of around -7K/day.   However, when the LW CRE is off, there is no appreciable 
+difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It 
+is also clearly seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 
+experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure 
+\ref{fig:TotCond}).
+
+When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar 
+distribution and magnitude of surface enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the 
+LW CRE is on, there are differences between the resolutions that can be as large as $80 \, \rm{W/
+m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are 
+confined to the regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
 would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
 
-Relative to simulations with a grid-spacing of $25 \textit{km}$, the simulations with explicit convection can be characterized as having: 
+Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
 \begin{itemize}

### 2019-10-16 Silvers_WalkerCell.tex
several changes to Silvers_WalkerCell.tex, mostly textual changes

--- 2019-10-14 Silvers_WalkerCell.tex
@@
   circulations.  Previous studies of RCE have proven to be a 
-  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.}
+  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
+  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
+  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
+  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
+  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
+  a forced compositing of the data (Bretherton et al. 2005, Muller and Held, 2012).}
   \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
   convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
-  in particular.}
+  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
+  this methodology for unifying our understanding.}
 \end{itemize}
@@
 To illustrate how (how what?  the double-plume convective parameterization influences the atmospheric state) 
-we compare the P25 experiment with analogous experiments in which the longwave CRE is off (P25 LWCRE off, middle 
+we compare the P25 experiment with analogous experiments in which the longwave CRE is turned off (P25 LWCRE off, middle 
 panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
@@
 drying and the strong moistening that results from ascent over the region of maximum latent heat flux.  
-Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  Deep-convective activity dominates the 
+Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  
+Deep-convective activity dominates the 
 region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
 clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, the atmospheric 
-state is much more symmetric about the maximum SST.  
-We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, and 
-circulation (see table 1).  In particular
-the experiments with parameterized convection are much more erratic.
-
-One of the most prominent features of our GCM-like (in particular, P25) simulations is an asymmetry in both the time-dependent and 
+state is much more symmetric about the maximum SST.  We also find large differences among the experiments in the domain mean 
+precipitation, condensate/clouds, and circulation (see table 1).  In particular the experiments with parameterized convection are 
+much more erratic.
+
+One of the most prominent features of our GCM-like (in particular, P25) simulations is an asymmetry relative to the 
+symmetric SST distribution in both the time-dependent and 
 steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).  
+This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$. 
 The steady-state precipitation maximum is located  not over the warmest SST but is
@@
 mean shear develops above about 500 \textit{m} which shifts the precipitation and circulation off center for years at a time.
-When the convective parameterization
-is turned off (E25), the overturning circulation becomes weaker and broader (w, and psi), and the precipitation, cloud fields, and 
+When the convective parameterization is turned off (E25), the overturning circulation becomes weaker and 
+broader (w, and psi), and the precipitation, cloud fields, and 
 circulation all consistently reside over the SST maximum.   
@@
 
-Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
-distribution have been noted many times in previous literature
-(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
+Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted many times in 
+previous literature (Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018))
+but the irregularities have 
 tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
@@
 
-The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
-This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
-as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
-SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
-mean shear develops which shifts the precipitation and circulation off center for years at a time.  This appears to be not entirely a 
-result of the convective parameterization, but due to an interaction between the convective parameterization and the LW CRE.
+%The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
+%This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
+%as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
+%SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
+%mean shear develops which shifts the precipitation and circulation off center for years at a time.
 
@@
 
-Now talk about the organizing influence of LWCRE...
+The default experimental configuration includes radiation that is fully interactive with the clouds, water vapor, and 
+temperature of the atmospheric state.  It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
+results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
+relative to the case with the LW CRE off.   A stronger and spatially concentrated circulation for cases when the 
+clouds interact with the longwave radiation can also be seen in Figures 4, 5, 9 and 10 and is particular apparent in 
+the cases with a large domain (16000 km long dimension).  This will be discussed further in the next section.
 
@@
 
-Because of the close connection between the domain mean value of precipitation, atmospheric condensational heating, and 
-the total radiative cooling the time evolution of the precipitation serves as a useful measure of whether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that after about 30 days, the P25, E2, and E1
-simulations begin to oscillate about a mean state that is roughly constant over periods greater than about 30 days. 
+Because of the tight constraints that connect the domain mean precipitation, atmospheric condensational heating, and 
+the total radiative cooling, the time evolution of the precipitation serves as a useful measure of whether a model has 
+reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that this equilibrium is reached after about 30 
+days for the E2, and E1 simulations, and after about 50 days for the P25 and P100 simulations.   After the initial adjustments
+the simulations all oscillate about mean precipitation values which, with the exception of E2, increases with the grid-spacing 
+(Table 1).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
+about the domain mean precipitation is smaller helps to justify the 6 month simulation times for E1 and E2.  
+%The period of oscillation is much larger for the GCM like simulations than it is for the CRM like oscillations.
 The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   The experiments with a higher resolution have a lower value of domain
-mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  This can be understood as a consequence
-of the differences in upper level cloud fraction and will be discussed further in a later section.
-
-%One of the most prominent features of our 25km grid-spacing simulations is an asymmetry in both the time-dependent and 
-%steady-state solutions.  This results in the steady-state precipitation maximum locating off the maximum in SST and is apparent in 
-%the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.   A tendency of the precipitation to 
-%occur off of the SST maximum is also apparent in the simulations with a grid-spacing of 100km, although the 25km simulations display 
-%an irregularity that is greater than the 100km simulations.  Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST 
-%distribution has been noted many times 
-%(Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018)) but the irregularities have 
-%tended to be symmetric, unlike our results.   
-%
-%For the simulations that are closest to the set up of a GCM, with fully parameterized convection, the steady-state circulation and 
-%precipitation maximum are located not over the warmest SST but shifted to regions about one degree cooler.  For the case
-%with a grid-spacing of 25km and a domain width of 4000km, the precipitation maximum can remain shifted off of the maximum in
-%SST for multiple years.   While focused within the central quarter of the domain, simulations on larger domains and with a 
-%grid-spacing of 100km also show an aversion to settling over the SST maximum.   When the convective parameterization
-%is turned off, the overturning circulation becomes weaker and broader (w, and psi), but the precipitation, cloud fields, and 
-%circulation all consistently reside over the SST maximum.  When the convective parameterization is turned on, a domain mean 
-%wind shear develops throughout the lowest 10km that acts to shift the convective activity and circulation off of the SST maximum.  
-%Note: check the wind shear for P25large, P100small, and P100large.
-
-%% low level structure
-%\begin{figure}
-%\begin{center}
-%\includegraphics[width=0.95\columnwidth]{walkerfigs/lowlevel_therm_test.eps}
-%\caption{{Low-level thermodynamic structure (a-e) and vertical shear (lower right, f).  Solid lines show experiments that include LWCRE, 
-%dashed lines experiments without LWCRE.  The yellow dashed-dot line is a 25 km experiment without LWCRE and with all 
-%convective parameterization turned off.   Panel e shows the temperature at the lowest model level (thin lines) and the virtual 
-%temperature at the lowest model level(thick lines).  The thick black line is the prescribed surface temperature.}}
-%\end{center}
-%\end{figure}
-%
+(Silvers et al., 2016; Patrizio and Randall, 2019).   
+%The experiments with a higher resolution have a lower value of domain
+%mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  
+This can be understood as a consequence
+of the differences in upper level cloud fraction and the surface energy budget 
+and will be discussed further in a later section.
 
@@
 
-%%%%
-% section 2 of results
-
-%% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
-%% LW CRE off
-%\begin{figure}
-%  \centering
-%      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcreoff.eps}
-%      \includegraphics[width=0.6\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre_draft.eps}
-%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for P25 and P100
-%  experiments .   Panels on the right (left) show experiments on the domain with a long dimension of 4000 km 
-%  (16000 km).  Black distributions are for experiments with the LW CRE on and green distributions for experiments 
-%  with LW CRE off.  The black curves show a Gaussian function with a standard deviation computed for 
-%  each experiment and an expected location in the center of the domain where the SST is warmest.}
-%\end{figure}
-%
-
-When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are two of the most 
-fundamental choices that must be made.   One the goals of this study was to explore the results of changing grid-spacing over a wide 
-range of values.  To simplify the analysis we have in most cases chosen to keep the 
-long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies (e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013) have 
-documented sensitivities to domain size.   The analysis of the previous, and of the next section focus on results from experiments using
-a domain with a long domain length of $4000 \, \rm{km}$.  However we do find sensitivity to the domain size and thought it to be
-sufficiently interesting to report.
-
-Examining the evolution in time of the precipitation field reveals important characteristics of these simulations, and 
-illustrates how much the distribution can vary as a function of domain size, parameterization of convection, and the effect of the 
-longwave radiation due to clouds. 
+When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
+two of the most fundamental choices that must be made.   One the goals of this study was to explore the results of 
+changing grid-spacing over a wide range of values.  To simplify the analysis we have in most cases chosen to keep the 
+long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
+(e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013) have documented sensitivities to domain 
+size.   The analysis of the previous, and of the next section focus on results from experiments using
+a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting sensitivities to the domain size that are noted here.
+
+The evolution in time of the precipitation field reveals important characteristics of these simulations, and 
+illustrates how much the distribution can vary as a function of domain size, parameterization of convection, 
+and the effect of the longwave radiation due to clouds. 
 Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
@@
 500 km of the SST maximum at the center of the domain,  
-the experiments without the LW CRE basically have no region with consistently strong precipitaiton.  Instead, 
-smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.
+the experiments without the LW CRE basically have no region with consistently strong precipitation.  Instead, 
+smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously notes, these
+GCM-like simulations equilibrate after approximately 50 days.  However, it is interesting to note a dramatic change in 
+the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
+precipitation does not significantly change in these cases, only the spatial structure.
 
@@
 They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
-larger.   We have found larger precipitation rates for the larger domains.  Does our larger domain ascent region change?
+larger.   We have found larger precipitation rates for the larger domains.  Based on the precipitation fields (Hovmollers) it is 
+possible that we have fewer low-level clouds over the colder SSTs in agreement with B06, but this needs to be checked.   Does our larger domain ascent region change?
 
@@
 precipitation that is produced by the convection scheme or the large-scale cloud scheme is not constrained. 
-The distribution of convective and large-scale precipitation can often give a hint of how the condensational heating
+The distribution of convective and large-scale precipitation can often indicate how the condensational heating
 in a GCM is being distributed among the parameterizations.  Precipitation from each of these two components is
 shown in Figure \ref{fig:conv_vs_ls}.  From this we can see that in the regions of large-scale ascent, most of the 
-precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE strongly influences the 
-large-scale precipitation but has a much weaker impact on the convective precipitation.  With the single exception 
-of the P100 LW CRE off experiment, the convective precipitation
-produces relatively little of the total precipitation for both resolutions and on both domains.
+precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE dramatically increases
+the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective precipitation 
+but acts to spatially concentrate it.  With the single exception 
+of the P100 LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
+both resolutions and on both domains.
 
@@
 
-\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
-General Circulation Model to a Cloud Resolving Model}
+%\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
+%General Circulation Model to a Cloud Resolving Model}
+\section{Dependence on Resolution: From a General Circulation Model to a Cloud Resolving Model}
 

### 2019-10-16 Silvers_WalkerCell.tex

@@
 \section{Dependence on Resolution: From a General Circulation Model to a Cloud Resolving Model}
+
+\begin{figure}
+  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
+  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
+  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
+  Shading indicates mm/day.  The horizontal axis shows the entire 
+  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  Shown is the meridional average. }
+  \label{fig:hov_4mods_6mn}
+\end{figure}
 

### 2019-10-16 Silvers_cfmip_draft.tex
textual changes to section one

@@
   \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
-  \item{Various configurations of a single global climate model lead to climate sensitivities that range from blah to about 5K.}
+  \item{Various configurations of a single global climate model lead to climate sensitivities that range from 2.1K (Cess) to 
+  about 5K (Winton's ECS).}
 \end{itemize}
@@
 
+Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
+the clouds which are simulated by AM4.0 over the recent observational period of 1979-2014.  We do this by comparing
+satellite based observations with the clouds in the AMIP experiment that is part of GFDLs contribution to CMIP6.  In 
+order to compare the observed and modeled clouds as consistently as possible across multiple platforms we have 
+used the satellite simulators which are included in COSP as part of the efforts of the CFMIP community 
+(Bodas-Salcedo et al. 2011).  By using multiple complimentary satellite datasets and simulators we can benefit from 
+the different strengths of each satellite while largely circumventing the known problems and discrepancies of the 
+observational data sets.
+
+As a starting point we look at the total cloud fraction.  The ISCCP and CALIPSO products agree fairly well on the 
+global mean cloud fraction (65 and 67\%, respectively).   By this measure there are too few clouds in AM4.0 
+(biases of -15 and -12 \%).   The ISCCP and CALIPSO data agree well over the oceans, with most of the differences
+occuring over land (particularly north of 30).
+
+Paragraph summarizing the basic characteristics of clouds in AM4.0 as stated by Ming's papers.  We could also summarize 
+what David finds about clouds in AM4.0 in his paper.
+
 During the developmental of the AM4.0 GFDL model particular care was given to ensuring that the energy budget at 
@@
 simulated clouds  from AM4.0 in the AMIP experiment.
-
-Paragraph summarizing the basic characteristics of clouds in AM4.0 as stated by Ming's papers.  We could also summarize 
-what David finds about clouds in AM4.0 in his paper.
 

### 2019-10-17 Silvers_cfmip_draft.tex
added text about satellites

@@
 
-This paper has a double motivation.  One of the motivations is to illustrate the wide range of sensitivities to perturbations 
+This paper has a double motivation.  First, to illustrate the wide range of sensitivities to perturbations 
 that can be achieved with a single base model.  For this purpose we utilize several models from the latest suite of GFDL 
@@
 
-An additional motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
+A second motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
 have participated in CMIP6.  This will largely be done in the context of the amip experiment and comparisons to observations
@@
 Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
-the clouds which are simulated by AM4.0 over the recent observational period of 1979-2014.  We do this by comparing
+the clouds which are simulated by AM4.0 over the recent observational period of 1979-2014.  This is done by comparing
 satellite based observations with the clouds in the AMIP experiment that is part of GFDLs contribution to CMIP6.  In 
 order to compare the observed and modeled clouds as consistently as possible across multiple platforms we have 
-used the satellite simulators which are included in COSP as part of the efforts of the CFMIP community 
-(Bodas-Salcedo et al. 2011).  By using multiple complimentary satellite datasets and simulators we can benefit from 
+used a selection of the satellite simulators which are included in COSP as part of the efforts of the CFMIP community 
+(Bodas-Salcedo et al. 2011).  This paper highlights simulators of the algorithms for three satellites based datasets: 
+ISCCP (the International Satellite Cloud Climatology Project), MODIS (the Moderate Resolution Imaging Spectroradiometer), 
+MISR (the Multiangle Imaging Spectro-Radiometer), and CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder 
+Satellite Observation; Chepfer et al., 2010; Cesana and Chepfer, 2013).  By using multiple complimentary satellite 
+datasets and simulators we can benefit from 
 the different strengths of each satellite while largely circumventing the known problems and discrepancies of the 
@@
 
-As a starting point we look at the total cloud fraction.  The ISCCP and CALIPSO products agree fairly well on the 
+Discrepancies among the many observational data sets has been extensively discussed in the literature and are 
+beyond the scope of this paper.  The curious reader can find detailed discussions in Kay et al., 2012; 
+Marchand et al. 2010 and?; Pincus et al., 2012; Cesana et al. ?; Stephens et al., 2018.  However, we note that ISCCP is useful due to 
+the longevity of the record (1983 - 2008 in Z18 figure) and MODIS has a detection algorithm that is an improvement upon ISCCP's and
+thus does a better job of detecting mid-level clouds and excluding partly filled pixels.   Of the three passive satellite products 
+(ISCCP, MODIS, and MISR), MODIS is considered to have the most accurate readings of high-topped clouds.  
+The height of clouds is determined with a stereo height retrieval method in MISR that is distinct from that used by
+both ISCCP and MODIS.  Because of this we have more confidence in the low and mid-level cloud readings 
+from MISR, as well as the cumulus clouds (Marchand et al. 2010; Zhang et al., 2019).   The CALIPSO observations
+are derived from a Lidar that allows for a direct measure of vertical structure of the clouds.
+
+As a starting point we look at the total cloud fraction in Figure \ref{fig:clt_isccp_calipso}.  The ISCCP and 
+CALIPSO products agree fairly well on the 
 global mean cloud fraction (65 and 67\%, respectively).   By this measure there are too few clouds in AM4.0 
@@
 occuring over land (particularly north of 30).
+
+The global structure of the cloud fields are shown for the upper level, mid level, and low levels in 
+Figure \ref{fig:calipso_9pan}.  The longitudinally averaged cloud fraction is shown as a function of latitude in the 
+left most panels.  There is a large under-estimation of cloud fraction by (AM4.0: dashed; CALIPSO: solid) between plus/minus 30 
+degrees for both mid and low-level clouds.   AM4.0 does a much better job with the upper level tropical clouds 
+although there is still a negative bias.   The global maps detail where the biases are occurring.  In the upper 
+levels the clouds are underestimated roughly equally among the deep-tropical and stratocumulus regions.  In the
+mid-levels the bias tends to be larger over tropical land and in the region of the inter-tropical convergence zone.  
+In the mid-levels there are large biases over much of the tropical Pacific ocean, as well as in the stratocumulus
+zones and the southern tropical Atlantic ocean.
 

### 2019-10-23 Silvers_cfmip_draft.tex
added MISR figures (preliminary)

@@
 
+\begin{figure}
+% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
+  \includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
+  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
+  \label{fig:clt_isccp_calipso}
+\end{figure}
+
+\begin{figure}
+% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
+  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/testplot_oldconts.pdf}
+  \caption{Comparison thick (optical depth between 3.6 and 60) thin (optical depth between 0.3 and 3.6) clouds the 
+  MISR simulator in  AM4 with observations from MISR (bottom panels).}
+  \label{fig:misr}
+\end{figure}
+
+\begin{figure}
+% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_calipso_obs_sim_am4.eps}
+  \caption{Comparison of total cloud fraction.  Top shows observations from CALIPSO, processed for GCM comparison.  Middle 
+  shows output from the CALIPSO simulator, bottom shows raw model output of clt without a simulator.}
+  \label{fig:calipso_sim_vs_mod}
+\end{figure}
+
 Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
@@
 
+\begin{figure}
+% figure generated with cloud_table_AM4fig.ncl
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/ctp_vs_tau_isccp_modis_am4_obs.eps}
+  \caption{Joint histograms showing the variations of cloud fraction as a function of cloud top pressure and tau.}
+  \label{fig:calipso_sim_vs_mod}
+\end{figure}
+
+\begin{figure}
+% figure generated with cloud_table_AM4fig.ncl
+  \includegraphics[angle=90,width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs_vs_AM4.eps}
+  \caption{Calipso scumstash.  Black line shows meridional profiles of AM4.0 cloud fraction and blue line shows
+  the meridional profile from CALIPSO.}
+  \label{fig:calipso_9pan}
+\end{figure}
+
 As a starting point we look at the total cloud fraction in Figure \ref{fig:clt_isccp_calipso}.  The ISCCP and 
@@
 
+The MISR satellite is thought to provide good estimates of low-level clouds heights and amounts.  For this reason
+and for comparison with both Kay et al., 2012, and Zhang et al., 2019 we compare observations from MISR
+and the AM4.0 simulator output in Figure \ref{fig:misr}.  The optical depth is used to distinguish
+between the thick and thin clouds.  Consistent with comparisons with ISCCP and CALIPSO we see that AM4.0
+has fewer clouds than observed.  The pattern of thick clouds observed by MISR is reproduced fairly well, except in 
+the tropical Indian Ocean.  The pattern of thin clouds is not reproduced as well, particularly in the southern hemisphere 
+tropics.
+
 The global structure of the cloud fields are shown for the upper level, mid level, and low levels in 
 Figure \ref{fig:calipso_9pan}.  The longitudinally averaged cloud fraction is shown as a function of latitude in the 
-left most panels.  There is a large under-estimation of cloud fraction by (AM4.0: dashed; CALIPSO: solid) between plus/minus 30 
+left most panels.  There is a large under-estimation of cloud fraction by (AM4.0: dashed; CALIPSO: solid) between 
+plus/minus 30 
 degrees for both mid and low-level clouds.   AM4.0 does a much better job with the upper level tropical clouds 
@@
 
-\begin{figure}
-% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
-  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
-  \label{fig:clt_isccp_calipso}
-\end{figure}
-
-\begin{figure}
-% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_calipso_obs_sim_am4.eps}
-  \caption{Comparison of total cloud fraction.  Top shows observations from CALIPSO, processed for GCM comparison.  Middle 
-  shows output from the CALIPSO simulator, bottom shows raw model output of clt without a simulator.}
-  \label{fig:calipso_sim_vs_mod}
-\end{figure}
-
-\begin{figure}
-% figure generated with cloud_table_AM4fig.ncl
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/ctp_vs_tau_isccp_modis_am4_obs.eps}
-  \caption{Joint histograms showing the variations of cloud fraction as a function of cloud top pressure and tau.}
-  \label{fig:calipso_sim_vs_mod}
-\end{figure}
-
-\begin{figure}
-% figure generated with cloud_table_AM4fig.ncl
-  \includegraphics[angle=90,width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs_vs_AM4.eps}
-  \caption{Calipso scumstash.  Black line shows meridional profiles of AM4.0 cloud fraction and blue line shows
-  the meridional profile from CALIPSO.}
-  \label{fig:calipso_9pan}
-\end{figure}
-
 \section{The Role of Clouds in AM4.0/CM4.0/Aquaplanets in Determining and Influencing Climate Sensitivity}
 
+% A paragraph, either here or earlier that clearly states to what degree and why we think that changes in clouds
+% are a critical element in determining why different models have different sensitivities.  Papers that should probably
+% be cited are Bony and Dufresne, 2005, Webb et al. (the convection off paper), the Bretherton review on cloud 
+% feedbacks, the CFMIP paper?  It would be  nice to cite more of the original papers and less of the review papers.  
+% Probably some of Zelinka's papers.
+
+The recent model development efforts at GFDL, and participation in CMIP6/CFMIP have provided a 
+unique/valuable opportunity to analyze a group of models that are built on the same code base while 
+spanning a wide range of model configurations.  The model types include (should we include any of the
+efforts from the RCE or Walker Cell configurations?) an Aquaplanet, and AGCM, 
+and a AOGCM.  When combined with a variety of boundary conditions this creates a hierarchy of
+models which are all derived from or dependent on the same atmospheric code base (AM4.0).  It is a 
+bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.      
+Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
+group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
+The clouds in these simulations are responding to a variety of different conditions including different
+patterns of prescribed SST, the presence or absence of land/ice, and in the case of the aquaplanet
+experiments, a lack of cloud-aerosol interactions which is present in the amip and coupled experiments.
+
+% Ringer et al 2014 comparison
 In order to compare to the values of feedback that were reported in Ringer et al., 2014, we use the same method 
@@
 inferred to be the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
-(Gregory et al., 2004).  From the atmosphere only experiments (amip-p4K, amipFuture, and aqua-p4K), the feedbacks are calculated as 
+(Gregory et al., 2004).  From the atmosphere only experiments (amip-p4K, amipFuture, and aqua-p4K), the feedbacks 
+are calculated as 
 differences in top-of-atmosphere flux anomalies between the perturbation and control experiments.
 
+% Beta feedback??  relavent?
 Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
 changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
-low clouds.'  See $Stevens_etal_Cookie_overview$ for details.   That paper asks the question of whether single 
+low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
 model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
@@
 have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.}
-    \begin{tabular}{*{5}{c}}
+    \begin{tabular}{*{6}{c}}
     \hline
     \hline
- Feedback & Aqua p4K & Amip p4K & Amip Future & Abrupt 4xCO2    \\ \hline
-    Net          &   -2.2    &  -1.6              & -1.8           &    -0.46 (-0.84; Tim)         \\ 
+ Feedback & Aqua p4K & Amip m4K & Amip p4K & Amip Future & Abrupt 4xCO2    \\ \hline
+    Net          &   -2.2  & ??  &  -1.6              & -1.8           &    -0.46 (-0.84; Tim)         \\ 
     \\
-    Net CRE      & 0.3      & -0.1            & 0.1           & 0.65   \\  
+    Net CRE      & 0.3   & ??  & -0.1            & 0.1           & 0.65   \\  
     \\
-    LW CRE       & 0.4       & 0.1            & 0.1           & 0.14    \\  
+    LW CRE       & 0.4   & ??  & 0.1            & 0.1           & 0.14    \\  
     \\
-    SW CRE      & -0.7       & -0.1          & -0.2          & -0.5              \\  
+    SW CRE      & -0.7  & ?? & -0.1          & -0.2          & -0.5              \\  
     \\
-    LW CLR       & 2.0       & 2.0             & 2.0           & 1.7             \\  
+    LW CLR       & 2.0   & ?? & 2.0             & 2.0           & 1.7             \\  
     \\
-    SW CLR      & -0.1      & -0.3            & -0.3          & -0.6                   \\  \hline
+    SW CLR      & -0.1  & ?? & -0.3            & -0.3          & -0.6                   \\  \hline
 
@@
 
+% SST patterns, the pattern effect.  Should my discussion paragraph of the pattern effect be 
+% the same paragraph/discussion as when I discuss Cess experiments?  
 The Cess sensitivity for AM4.0 ($0.57 \, \rm{K\, W^{-1} m^2}$, Z18b, pg 26) is closer to the Cess sensitivity 
@@
 
+One of our goals was to highlight and learn from the influence of clouds feedbacks across a range of GFDL based models.  Our hope 
+is that by looking at models from a single institution rather than a larger ensemble of CMIP models we will avoid inadvertantly 
+masking important relationships by a multi-model ensemble mean.
+
 \end{document}

### 2019-10-23 Silvers_WalkerCell.tex
changed exp to expl
added subsidence fraction to table 2, minor textual revisions

@@
 \documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
+%\documentclass[draft]{agujournal2019}
 \usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
@@
 
-\textbf{Key Points}
+\textbf{Key Points: choose three}
 \begin{itemize}
@@
   maximum.}
+  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
+  maximum away from the SST maximum.}
   \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
@@
 \begin{center}
-\caption{A few specifications of the simulations used most heavily in this study.  In the Convection
-column, `prm'  indicates that convection is parameterized and `exp' indicates convection is explicity.  
-The precipitation values in parenthesis are for the experiments in which LWCRE is off.}
-    \begin{tabular}{*{6}{c}}
+\caption{Specifications of the simulations used most heavily in this study.  In the Convection
+column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.}
+    \begin{tabular}{*{5}{c}}
     \hline
@@
     \\
- Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection & 
- $\overline{\rm{P}} (\mathrm{mm/day})$    \\ \hline
-  P100L &  100          &   800 $\times$ 16000    &  60              & prm           &  4.1 (3.5)          \\ 
-    \\
-  P100 &  100                & 800 $\times$ 4000     & 60            & prm         & 3.9 (3.7)               \\  
-    \\
-  P25L &  25             & 200 $\times$ 16000      & 60             & prm          & 4.0 (3.8)                \\  
-    \\
-  P25  &  25             & 200 $\times$ 4000      & 60             & prm           & 3.8 (3.7)               \\  
-    \\
- E25  &   25          & 200 $\times$ 4000      & 60             & exp          & 3.7 (3.5)               \\  
-    \\
- E2   &   2          & 100 $\times$ 4000      & 6             & exp          & 3.1 (3.4)                \\ 
-    \\
- E1   &   1          & 10 $\times$ 4000      & 6             & exp          & 3.3 (3.7)                \\  \hline
-
-    \end{tabular}\par
-    %\bigskip 
-    \label{tab:lambda}
-\end{center}
-\end{table}
-
-\begin{table}
-\begin{center}
-\caption{Domain mean precipitation ($\overline{\rm{P}}$) and outgoing longwave radiation 
-($\overline{\rm{OLR}}$).
-The values in parenthesis are for the experiments in which LWCRE is off.}
-    \begin{tabular}{*{3}{c}}
-    \hline
-    \hline
-    \\
- Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$   \\ \hline
-  P100L   &  4.1 (3.5)   &  283.1 (286.9)          \\ 
-    \\
-  P100 &   3.9 (3.7)   &  283.2 (296.4)             \\  
-    \\
-  P25L &   4.0 (3.8)  &  281.2 (290.7)             \\  
-    \\
-  P25  &   3.8 (3.7)    & 282.9 (293.6)             \\  
-    \\
- E25  & 3.7 (3.5)    &   271.9 (286.8)               \\  
-    \\
- E2   &  3.1 (3.4)   &  266.2 (285.5)               \\ 
-    \\
- E1   &  3.3 (3.7)   &  269.3 (289.2)               \\  \hline
+ Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection     \\ \hline
+  P100L &  100          &   800 $\times$ 16000    &  60              & prm                   \\ 
+    \\
+  P100 &  100                & 800 $\times$ 4000     & 60            & prm                     \\  
+    \\
+  P25L &  25             & 200 $\times$ 16000      & 60             & prm                     \\  
+    \\
+  P25  &  25             & 200 $\times$ 4000      & 60             & prm                   \\  
+    \\
+ E25  &   25          & 200 $\times$ 4000      & 60             & expl                \\  
+    \\
+ E2   &   2          & 100 $\times$ 4000      & 6             & expl                   \\ 
+    \\
+ E1   &   1          & 10 $\times$ 4000      & 6             & expl                 \\  \hline
 
@@
 relative to many other cloud resolving models.
+
+\begin{table}
+\begin{center}
+\caption{Domain mean precipitation ($\overline{\rm{P}}$), outgoing longwave radiation 
+($\overline{\rm{OLR}}$), and fraction of domain that is subsiding at the 532 hPa level.
+Values in parenthesis correspond to experiments whith LWCRE is off.}
+    \begin{tabular}{*{4}{c}}
+    \hline
+    \hline
+    \\
+ Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$ & SF   \\ \hline
+  P100L   &  4.1 (3.5)   &  283.1 (286.9)    & 0.89 (0.61)      \\ 
+    \\
+  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 0.73 (0.71)           \\  
+    \\
+  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 0.78 (0.69)          \\  
+    \\
+  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 0.80 (0.72)          \\  
+    \\
+ E25  & 3.7 (3.5)    &   271.9 (286.8)   & -            \\  
+    \\
+ E2   &  3.1 (3.4)   &  266.2 (285.5)    & 0.83 (0.77)           \\ 
+    \\
+ E1   &  3.3 (3.7)   &  269.3 (289.2)    & 0.78 (0.78)         \\  \hline
+
+    \end{tabular}\par
+    %\bigskip 
+    \label{tab:lambda}
+\end{center}
+\end{table}
 
@@
 region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
-clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, the atmospheric 
-state is much more symmetric about the maximum SST.  We also find large differences among the experiments in the domain mean 
-precipitation, condensate/clouds, and circulation (see table 1).  In particular the experiments with parameterized convection are 
-much more erratic.
+clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, 
+the atmospheric state is much more symmetric about the maximum SST.  We also find large differences among the 
+experiments in the domain mean precipitation, condensate/clouds, and circulation (see Table 2).  In particular the 
+experiments with parameterized convection are much more erratic.
 
@@
 
-%The abnormality, or asymmetry, of the P25 simulation was the first surprising feature noticed by the authors.
-%This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$.  For some of the other cases observed, such
-%as P100 (on the small domain), the asymmetry can be described as an aversion of the precipitation maxima to reside over the 
-%SST maximum while in other cases, such as the P25 case shown in \ref{fig:rh_psi_P25vsE25}, a strong ($1 \, \rm{m s^-1}$) domain
-%mean shear develops which shifts the precipitation and circulation off center for years at a time.
-
 %%%%%
@@
 the cases with a large domain (16000 km long dimension).  This will be discussed further in the next section.
+
+Previous studies have shown that cloud radiative effect act to strengthen and contract an overturning 
+(e.g. Popp and Silvers, 2017, and others (Muller and Held?)).  This was shown to be due to an increased low-level flux
+of moist static energy into the convective regions.
 
@@
 
-Superposing the circulation and relative humidity illustrates the subsidence driven 
-drying and the strong moistening that results from ascent over the region of maximum latent heat flux.
-
 The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
@@
 mean precipitation rate actually decreases.  The large decrease of low-level clouds also 
-leads to a large increase of downward shortwave radiation.  The only slightly increases the
-fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) but also contributes to 
+leads to a large increase of downward shortwave radiation.  This only slightly increases the
+fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) but does contribute to 
 heating the atmosphere.
+
 Turning the LW CRE off for the E1 and E2 experiments results in more precipitation while, 
-for the E25, P25, and P100 
-experiments, less precipitation results from turning the LW CRE off.  
-The primary method by which the longwave cloud 
-radiative effect influences the atmosphere is by heating the atmosphere in the region between the clouds and the surface.  
+for the E25, P25, and P100 experiments, less precipitation results from turning the LW CRE off.  
+The primary method by which the longwave cloud radiative effect influences the atmosphere is by 
+heating the atmosphere in the region between the clouds and the surface.  
 Larger values of ice condensate and upper-level cloud fraction such as we see for the E2 and E1 experiment 
@@
 is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
-However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  For 
-GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
+However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.
+
+For GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
 convective parameterization, and one part from the large-scale cloud scheme.  Figure \ref{fig:conv_vs_ls} shows 
@@
 a reduction in the large-scale cloud scheme precipitation and not from a decrease in the convective precipitation.       
-This implies there will be less atmospheric heating from 
-longwave radiation and a corresponding larger heating due to condensational heating which is consistent with higher values 
+This implies (is this connected to previous sentence?) there will be less atmospheric heating from 
+longwave radiation (but doesn't LW just cool the atmosphere?) and a corresponding 
+larger heating due to condensational heating which is consistent with higher values 
 of domain mean precipitation for E25, P25, and P100 compared to E2 and E1.  Similarly, the E2 experiment has lower values 
 of upper level condensate and higher values of mid-troposphere relative humidity compared to the E1 simulation, which ....??  
-Water vapor is an efficient emitor of long-wave radiation and thus greatly facilitates the cooling of the troposphere.  
+Water vapor is an efficient emitter of long-wave radiation and thus greatly facilitates the cooling of the troposphere.  
 Popp and Silvers, 2017 showed that that there is dramatically less water vapor in the atmosphere and much less precipitation 
-for LW CRE off experiments (see their figure 1).  Our results here for the E25, P25, and P100 are consistent with 
-those of Popp and Silvers, 2017.
+for LW CRE off experiments (see their figure 1b).  Our results here for the E25, P25, and P100 are consistent with 
+those of Popp and Silvers, 2017 because the low-level condensate strongly decreases when the LWCRE is off.  This is not 
+the case for E2 and E1.  Those experiments have very little low-level condensate to begin with and thus do not experience 
+large changes in low-level condensate when the LWCRE is off.  They do however have a large increase of upper
+level condensate for the LWCRE off experiments.   This is a large difference in the way that models with explicit convection 
+respond to the LWCRE compared to more traditional large-scale models with parameterized convection.
 
@@
 
+%\begin{thebibliography}{}
+%
+%\bibitem[{\textit{Bretherton et~al.}(2005)\textit{Bretherton, Blossey, and
+%  Khairoutdinov}}]{Bretherton_etal_2005}
+%Bretherton, C.~S., P.~N. Blossey, and M.~Khairoutdinov (2005), An
+%  energy-balance analysis of deep convective self-aggregation above uniform
+%  sst, \textit{J. Atmos. Sci.}, \textit{62}, 4273--4292.
+%
+%%\bibitem[{\textit{Jeevanjee and Romps}(2013)}]{Jeevanjee_Romps_2013}
+%%Jeevanjee, N., and D.~M. Romps (2013), Convective self-aggregation, cold pools,
+%%  and domain size, \textit{Geophys.\ Res.\ Lett.}, \textit{40}, 994--99,
+%%  \doi{10.1002/grl.50204}.
+%  
+%\end{thebibliography}
+
+%%% Acknowledgements
+%\begin{acknowledgments}
+%(Levi's acknowledgements)
+%\end{acknowledgments}
+
 \end{document}

### 2019-10-24 Silvers_WalkerCell.tex
textaul edits to Silvers_WalkerCell.tex

@@
-\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
-%\documentclass[draft]{agujournal2019}
-\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
-\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
+%\documentclass[11pt]{article}   	% use "amsart" instead of "article" for AMSLaTeX format
+\documentclass[draft]{agujournal2019}
+\usepackage{url} %this package should fix any errors with URLs in refs.
+\usepackage{lineno}
+\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage{soul}
+\linenumbers
+%\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
+%\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
 %\geometry{landscape}                		% Activate for for rotated page geometry
 %\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
-\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
+%\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
 								% TeX will automatically convert eps --> pdf in pdflatex		
-\usepackage{amssymb}
-\usepackage{gensymb}
-\usepackage{epstopdf}
+%\usepackage{amssymb}
+%\usepackage{gensymb}
+%\usepackage{epstopdf}
 %\usepackage{pdflatex}
 %\usepackage{epsfig}
+
+\draftfalse
+
+\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}
+
+\begin{document}
 
@@
 \title{Clouds and Radiation in a mock-Walker Circulation}
-\author{Levi G. Silvers, Nadir Jeevanjee, and Thomas Robinson}
-
-\begin{document}
-\maketitle
+\authors{Levi G. Silvers, Nadir Jeevanjee, and Thomas Robinson}
+
+\correspondingauthor{Levi Silvers}{levi.silvers@stonybrook.edu}
+
+%\textbf{Key Points: choose three}
+\begin{keypoints}
+  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
+  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
+  maximum.}
+  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
+  maximum away from the SST maximum.}
+  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
+  changes in the low-level clouds and boundary layer structure.}
+  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
+  region that is 30\% higher than for the coarser cases with parameterized convection.}
+  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
+\end{keypoints}
 
@@
 %\section{Key Questions}
-
-\textbf{Key Points: choose three}
-\begin{itemize}
-  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
-  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
-  maximum.}
-  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
-  maximum away from the SST maximum.}
-  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
-  changes in the low-level clouds and boundary layer structure.}
-  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
-  region that is 30\% higher than for the coarser cases with parameterized convection.}
-  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
-\end{itemize}
 
@@
   between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
-  a forced compositing of the data (Bretherton et al. 2005, Muller and Held, 2012).}
+  a forced compositing of the data (\cite{Bretherton_etal_2005} Bretherton et al. 2005, Muller and Held, 2012).}
   \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
@@
 \caption{Domain mean precipitation ($\overline{\rm{P}}$), outgoing longwave radiation 
-($\overline{\rm{OLR}}$), and fraction of domain that is subsiding at the 532 hPa level.
+($\overline{\rm{OLR}}$), and subsidence fraction (SF)  or fraction of domain that is subsiding at the 532 hPa level.
 Values in parenthesis correspond to experiments whith LWCRE is off.}
@@
 and a dry ($< 10\% RH$) subsidence region with almost no condensate above $800 \rm{hPa}$.    
-To illustrate how (how what?  the double-plume convective parameterization influences the atmospheric state) 
-we compare the P25 experiment with analogous experiments in which the longwave CRE is turned off (P25 LWCRE off, middle 
+To illustrate some of the sensitivities to convection and the interaction between clouds, radiation, and the large-scale 
+circulation we compare the P25 experiment with analogous experiments in which the longwave CRE is turned 
+off (P25 LWCRE off, middle 
 panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
@@
 the parameterized convection leads to a dryer atmosphere with less 
-condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  However, in 
-the updraft region the convective parameterization results in more moisture aloft.
+condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  
+However, in the updraft region the convective parameterization results in more moisture aloft.
 
@@
 region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
-clouds are absent.  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, 
+clouds are absent (based on what?).  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, 
 the atmospheric state is much more symmetric about the maximum SST.  We also find large differences among the 
-experiments in the domain mean precipitation, condensate/clouds, and circulation (see Table 2).  In particular the 
+experiments in the domain mean precipitation, condensate/clouds, and circulation (see Table 2).  In general the 
 experiments with parameterized convection are much more erratic.
 
-One of the most prominent features of our GCM-like (in particular, P25) simulations is an asymmetry relative to the 
+One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry relative to the 
 symmetric SST distribution in both the time-dependent and 
@@
 specific humidity, and radiative heating.  
-For most of these cases the asymmetry appears as an aversion of the precipitation maxima to reside over the SST maximum.  
+In the Hovmoller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse to 
+residing over the SST maximum.  
 For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^-1}$) domain
@@
 broader (w, and psi), and the precipitation, cloud fields, and 
-circulation all consistently reside over the SST maximum.   
+circulation all consistently reside over the SST maximum (for about 1 year before going haywire).   
 While the parameterized convection plays a large role in driving this asymmetry it appears to be not entirely a 
@@
 tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
-entirely explicit (discussed further in section 4).
+entirely explicit (E25, E2, and E1, discussed further in section 4).
 
@@
       streamfunction (contours) for the experiments
-      with a grid-spacing of 25km.  The lower panels show total (liquid + ice) condensates (g/kg).  
+      with a grid-spacing of 25km.  The lower panels show the total (liquid + ice) condensate (g/kg).  
       An experiment with fully parameterized convection (P25) is on the left, the same 
       experiment but with the LWCRE off is in the center panel, and the experiment with LWCRE on, but the convective
-      parameterization turned off is on the right.  All three panels use the same contour interval for the mass 
+      parameterization turned off is on the right (E25).  All three panels use the same contour interval for the mass 
       streamfunction (kg/s).}
@@
 
-Previous studies have shown that cloud radiative effect act to strengthen and contract an overturning 
-(e.g. Popp and Silvers, 2017, and others (Muller and Held?)).  This was shown to be due to an increased low-level flux
-of moist static energy into the convective regions.
+Previous studies have shown that cloud radiative effects act to strengthen and contract an overturning circulation 
+(e.g. Popp and Silvers, 2017, HH, and others (Muller and Held?)).  This was shown to be due to an increased low-level flux
+of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
+convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
+region of persistent deep convection and a state of aggregation.   One of the simplest measures of convective 
+aggregation and the large-scale circulation is the fraction of the domain in which the air is subsiding, the 
+subsidence fraction (SF).  As convection becomes more organized, or aggregated, SF will increase.  We expect 
+for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
+fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE on
+have a larger SF (with the exception of E1, for which SF is constant).  Our prescribed SST warm patch ensures that our simulations will 
+be `aggregated' to some degree.  However, the subsidence fraction is a useful metric even in this case which 
+includes an additional constraint than RCE.  Given identical SSTs, the variations in SF give a measure of variability
+driven entirely by the atmosphere.
 
@@
 days for the E2, and E1 simulations, and after about 50 days for the P25 and P100 simulations.   After the initial adjustments
-the simulations all oscillate about mean precipitation values which, with the exception of E2, increases with the grid-spacing 
-(Table 1).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
+the simulations all oscillate about mean precipitation values which tend to increase with the grid-spacing 
+(Table 2).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
 about the domain mean precipitation is smaller helps to justify the 6 month simulation times for E1 and E2.  
@@
 %mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  
-This can be understood as a consequence
-of the differences in upper level cloud fraction and the surface energy budget 
+This can be understood as a consequence of the differences in upper level cloud fraction and the surface energy budget 
 and will be discussed further in a later section.
@@
 long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
-(e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013) have documented sensitivities to domain 
-size.   The analysis of the previous, and of the next section focus on results from experiments using
-a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting sensitivities to the domain size that are noted here.
+(e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013; sens of what? Patrizio and Randall? Silvers?) have 
+documented sensitivities to domain size.   The analysis of the previous, and of the next sections focus on results from 
+experiments using a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting 
+sensitivities to the domain size that are noted here.
 
@@
 averaging along the short horizontal dimension.  The four panels show simulations with a grid-
-spacing of $25\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ (middle right), and 
+spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ (middle right), and 
 simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
@@
 They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
-larger.   We have found larger precipitation rates for the larger domains.  Based on the precipitation fields (Hovmollers) it is 
-possible that we have fewer low-level clouds over the colder SSTs in agreement with B06, but this needs to be checked.   Does our larger domain ascent region change?
+larger.   In contrast, here larger domains have larger precipitation rates (Table 2).  For the LWCRE off cases, we also find a more 
+focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the ascent region changes little between P25 
+and P25L but for P100 and P100L the ascent region is much more focuses on the large domain.    
+How do our low-level clouds over the colder SSTs compare with the findings of B06 (check the condensate for small vs. large 
+domains)?
 
@@
 
-Although the domain mean total precipitation is constrained by the radiative cooling of the atmosphere, the amount of 
-precipitation that is produced by the convection scheme or the large-scale cloud scheme is not constrained. 
+The domain mean total precipitation is constrained by the radiative cooling of the atmosphere.  However, in 
+models with the convection parameterized the 
+total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
+While the relative contribution is not well constrained, it is thought to influence the atmospheric state (Held et al., what part of the state?). 
 The distribution of convective and large-scale precipitation can often indicate how the condensational heating
-in a GCM is being distributed among the parameterizations.  Precipitation from each of these two components is
-shown in Figure \ref{fig:conv_vs_ls}.  From this we can see that in the regions of large-scale ascent, most of the 
-precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE dramatically increases
+in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
+Precipitation from each of these two components is
+shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
+In the regions of large-scale ascent, most of the 
+precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE (thick lines) dramatically increases
 the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective precipitation 
-but acts to spatially concentrate it.  With the single exception 
-of the P100 LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
-both resolutions and on both domains.
+but does act to spatially concentrate it.  With the single exception 
+of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
+both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
+seen in Figure \ref{fig:domdep_lwoff} corresponds to decrease in the large-scale precipitation of about 65\% in P25L case
+and an almost complete elimination of the large-scale precipitation in the P100L case.
 
@@
 
-Below is a list summarizing several of the changes that occur when the LW CRE is off.
-The points which have not already been discussed will be later in the paper.
-Turning the LW CRE interactions off tends to:
-
-\begin{itemize}
-  \item decrease the strength of the overturning circulation and the domain mean precipitation (P100,P25,E25)
-  \item increase the midtropospheric RH by $5-15 \% $
-  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
-  \item weaken the horizontally oriented low-level circulations.   
-  \item spread out in geographic space the precipitation maxima
-  \item homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
-  \item decrease both the LTS and the EIS, over both the warm and cold regions
-  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
-  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
-           the 1 and 2 \textit{km} simulations. 
-  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
-  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
-\end{itemize}
-
 %\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
@@
   longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the meridional average. }
+  Shown is the average over the small dimension of the channel domain. }
   \label{fig:hov_4mods_6mn}
@@
 
+% this paragraph should perhaps be moved to the introduction...
 It is clear that the overturning circulation in the tropical Pacific encompasses dynamical motions at a host of scales and that the 
@@
 be used over a wide range of resolutions and can solve either the hydrostatic or nonhydrostatic 
-governing equations.  In this section we focus on simulations with grid-spacing of 1km, 2km, and 25km.   
+governing equations.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
+      \caption{The steady state relative humidity (shading) and mass streamfunction (black contours).  
+      Shown is E25 (left), E2(center), and E1(right).  All panels use the same contour interval for the 
+      mass streamfunction (kg/s).}
+  \label{fig:rh_psi_P25E2E1}
+\end{figure}
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
+          \caption{Same as previous figure except with the longwave CRE turned off.}
+  \label{fig:rh_psi_P25E2E1_lwoff}
+\end{figure}
+
+In this section we focus on simulations with grid-spacing of 1km, 2km, and 25km.   
 A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that result from the 
@@
 centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more 
-variability at later 
-times, compared to these first 180 days.  The simulations with explicit convection at resolutions typical of 
-cloud-resolving 
-models (E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST and relative to 
-the P100, P25 and E25 simulations 
+variability at later times, compared to these first 180 days.  The simulations with explicit convection at resolutions 
+typical of cloud-resolving models (E2, E1) show little aversion to the precipitation maximum occurring over 
+the maximum in SST and relative to the P100, P25 and E25 simulations 
 they are able to maintain a smoother distribution of  precipitation values over a broader range of SST values.
 
-The steady state relative humidity and overturning circulation show an interesting combination of similarities and differences
+The steady state relative humidity and overturning circulation (Figures \ref{fig:rh_psi_P25E2E1} and 
+\ref{fig:rh_psi_P25E2E1_lwoff}) show an interesting combination of similarities and differences
 among the experiments with varying resolutions.  All experiments have a multicell vertical structure (consistent with 
@@
 of the P25 experiment is more than $40\%$ dryer in the region with deep-convection than for the 2km and 1km experiments. 
+The high resolution experiments also have higher amounts of condensate throughout the troposphere, and much higher
+relative humidity above about 300 hPa.
 
@@
 
+Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
+fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
+P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
+require a correspondingly larger amount of condensational heating and precipitation.
+
 \begin{figure}
@@
 \end{figure}
-
-Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
-fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
-P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
-require a correspondingly larger amount of condensational heating and precipitation.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
-      \caption{The steady state relative humidity (shading) and mass streamfunction (black contours).  
-      Shown is E25 (left), E2(center), and E1(right).  All panels use the same contour interval for the 
-      mass streamfunction (kg/s).}
-  \label{fig:rh_psi_P25E2E1}
-\end{figure}
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
-          \caption{Same as previous figure except with the longwave CRE turned off.}
-  \label{fig:rh_psi_P25E2E1_lwoff}
-\end{figure}
-
-The domain mean condensate is an important measure of the steady state reached by these experiments.  The vertical 
-distribution of condensate is closely related to the distribution of clouds, it influences the distribution of energy throughout
-the atmosphere as well as the outgoing longwave radiation.  It can also indicate the strength of convection 
-and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a significant difference 
-between the GCM-like P25/E25 experiments and the CRM-like E2/E1 experiments with the former having much 
-higher values of low-level liquid condensate/cloud and the later having much higher values of upper level ice 
-condensate.  The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
-regions of the CRM-like experiments.     It is also interesting to note that the LWCRE results in less condensate 
-above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
 
@@
 
+The domain mean condensate is an important measure of the steady state reached by these experiments.  The vertical 
+distribution of condensate is closely related to the distribution of clouds.  This in turn influences the distribution of 
+energy throughout the atmosphere and the longwave radiation that is emitted to space.  It can also indicate the 
+strength of convection 
+and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
+(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a significant difference 
+between the GCM-like P25/E25 experiments and the CRM-like E2/E1 experiments with the former having much 
+higher values of low-level liquid condensate/cloud and the later having much higher values of upper level ice 
+condensate.  The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
+regions of the CRM-like experiments.     It is also interesting to note that the LWCRE results in less condensate 
+above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
+
 The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
@@
 
-An interesting fact that emerges from the domain mean values of precipitation (see Table 1) 
+An interesting fact that emerges from the domain mean values of precipitation (see Table 2) 
 is that the sign of the response to LWCRE is not the same across the different grid-spacings.
@@
 flux change becuase there are less clouds or because they are invisible to radiation?).  Under 
-natural conditions, the surface is warmed by a downward flux of longwave radiation due to the clouds
+natural conditions with an interactive surface, the surface is warmed by a downward flux of longwave 
+radiation due to the clouds
 above.  When this source of atmospheric energy loss is removed in the LWCRE off experiments 
 the upwelling longwave flux of radiation plays a larger role in warming the atmosphere that more 
-than compensates for the increased OLR.  Thus, with an increase in atmospheric warming on 
-the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off, there is less need for condensational heating and the 
-mean precipitation rate actually decreases.  The large decrease of low-level clouds also 
+than compensates for the increased OLR at the top of the atmosphere.  Thus, with an increase in 
+atmospheric warming on 
+the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off, there is less need for condensational 
+heating.  The mean precipitation rate actually decreases.  The large decrease of low-level clouds also 
 leads to a large increase of downward shortwave radiation.  This only slightly increases the
@@
 asymmetric results.
+
+Below is a list summarizing several of the changes that occur when the LW CRE is off.  Turning the LW CRE interactions off tends to:
+
+\begin{itemize}
+  \item decrease the strength of the overturning circulation and the domain mean precipitation (P100,P25,E25)
+  \item increase the midtropospheric RH by $5-15 \% $
+  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
+  \item weaken the horizontally oriented low-level circulations.   
+  \item spread out in geographic space the precipitation maxima
+  \item homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
+  \item decrease both the LTS and the EIS, over both the warm and cold regions
+  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
+  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
+           the 1 and 2 \textit{km} simulations. 
+  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
+  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
+\end{itemize}
 
@@
 
+\acknowledgments
+Funding for this work came from both GFDL and Stony Brook.  Data and scripts are available from author upon request
+
+%\bibliography{references}
 %\begin{thebibliography}{}

### 2019-10-29 Silvers_WalkerCell.tex
relatively minor text edits to Silvers_WalkerCell.tex.  Addition of two .bib files that contain references to use in Silvers_WalkerCell.tex

@@
   between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
-  a forced compositing of the data (\cite{Bretherton_etal_2005} Bretherton et al. 2005, Muller and Held, 2012).}
+  a forced compositing of the data  
+  \cite{Bretherton2005, Muller2012}.
+  %Bretherton et al. 2005, Muller and Held, 2012)
+  }
   \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
@@
 and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
-because of the sensitivity of the low-level clouds to the longwave radiative cooling.
+because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
 
@@
 To develop the model configuration used for these experiments we started with the same code base as that of the 
-recently developed atmospheric global climate model AM4.0 
-(Zhao et al. a,b).  This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
+recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b}.
+%(Zhao et al. a,b).  
+This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
 which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations.  
@@
 physics are very similar to those of AM4.0.  This configuration can also be compared to the simulations described in 
-Popp and Silvers, 2017, which used a developmental version of AM4 with almost the same changes to the physics
+\cite{Popp2017}, %Popp and Silvers, 2017, 
+which used a developmental version of AM4 with almost the same changes to the physics
 schemes.
@@
 and a dry ($< 10\% RH$) subsidence region with almost no condensate above $800 \rm{hPa}$.    
+This atmospheric state has the same fundamental characteristics as the Walker circulation, the Hadley Cell, and 
+experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations and 
+convective aggregation.
+
 To illustrate some of the sensitivities to convection and the interaction between clouds, radiation, and the large-scale 
@@
 steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).  
-This asymmetry is also present on larger domains and at a resolution of $100 \, \rm{km}$. 
+This asymmetry is also present in P25 experiments on larger domains and at a resolution of $100 \, \rm{km}$. 
 The steady-state precipitation maximum is located  not over the warmest SST but is
@@
 Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted many times in 
-previous literature (Bretherton et al. 2006, Kuang and Wofsy, Ming Zhao (personal communication, see Jeevanjee et al. 2018))
+previous literature \cite{Bretherton2006, Wofsy2012} (Ming Zhao (personal communication, see Jeevanjee et al. 2018))
 but the irregularities have 
@@
       \caption{Comparison of the steady state relative humidity (shading of top panels) and mass 
-      streamfunction (contours) for the experiments
-      with a grid-spacing of 25km.  The lower panels show the total (liquid + ice) condensate (g/kg).  
+      streamfunction (contours) for experiments
+      with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.  The lower panels 
+      show the total (liquid + ice) condensate (g/kg).  
       An experiment with fully parameterized convection (P25) is on the left, the same 
@@
 Previous studies have shown that cloud radiative effects act to strengthen and contract an overturning circulation 
-(e.g. Popp and Silvers, 2017, HH, and others (Muller and Held?)).  This was shown to be due to an increased low-level flux
+(e.g. Popp and Silvers, 2017, HH, and others (Muller and Held?), Albern et al., 2019).  This is 
+due to an increased low-level flux
 of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
@@
 be `aggregated' to some degree.  However, the subsidence fraction is a useful metric even in this case which 
-includes an additional constraint than RCE.  Given identical SSTs, the variations in SF give a measure of variability
-driven entirely by the atmosphere.
+includes an additional constraint than RCE.  Given identical SSTs, the different SFs give a measure of variability
+that is driven entirely by the atmosphere.
 
@@
 
+Despite the same boundary conditions and model base, the experiments documented here have a
+large range of domain mean precipitation ($\rm{\overline{P}}$, Table 2) that varies by as much as 
+0.6 $\rm{mm/d}$ (3.5-4.1 in parameterized experiments; 3.1-3.7 in explicit experiments).
+This highlights how dominant the interaction between clouds and radiation can be in determining the 
+characteristics of a system.
 Because of the tight constraints that connect the domain mean precipitation, atmospheric condensational heating, and 
@@
 The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-(Silvers et al., 2016; Patrizio and Randall, 2019).   
+\cite{Silvers2016, Patrizio2019}
+%(Silvers et al., 2016; Patrizio and Randall, 2019).   
 %The experiments with a higher resolution have a lower value of domain
 %mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  
-This can be understood as a consequence of the differences in upper level cloud fraction and the surface energy budget 
-and will be discussed further in a later section.
+Differences in $\rm{\overline{P}}$ can be understood as a consequence of the differences in upper level cloud fraction 
+and the surface energy budget and will be discussed further in a later section.
 
@@
 long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
-(e.g. Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013; sens of what? Patrizio and Randall? Silvers?) have 
-documented sensitivities to domain size.   The analysis of the previous, and of the next sections focus on results from 
+\cite{Bretherton2005, Bretherton2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
+(e.g. Bretherton et al., 2005; Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013; 
+Silvers et al., 2016; Patrizio and Randall, 2019) have 
+documented sensitivities of the equilibrated state to domain size.   
+The analysis of the previous, and of the next sections focus on results from 
 experiments using a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting 
@@
 averaging along the short horizontal dimension.  The four panels show simulations with a grid-
-spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ (middle right), and 
+spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ 
+(middle right), and 
 simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
@@
  At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
-precipitation over a smaller geographic extent.   This is consistent with the idea that CREs strengthen an overturning circulation and
+precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
+strengthen an overturning circulation and
 narrow the region of deep convection (see Popp and Silvers, 2017, HH, Dixit et al. 2019.  etc.).
-The structure of the precipitation changes more as a function of domain size than it does as a function of grid-spacing. 
+The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
 On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
@@
 smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously notes, these
-GCM-like simulations equilibrate after approximately 50 days.  However, it is interesting to note a dramatic change in 
+GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
 the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
@@
 
-Smaller domain lengths were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
+Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
 They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
-larger.   In contrast, here larger domains have larger precipitation rates (Table 2).  For the LWCRE off cases, we also find a more 
+larger.   In contrast, here larger domains have larger precipitation rates (Table 2).  For the LWCRE off cases, in agreement 
+with \citeA{Bretherton2006} we find a more 
 focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the ascent region changes little between P25 
@@
       \includegraphics[width=0.8\columnwidth]{walkerfigs/Conv_vs_LS_hist.eps}
-  \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective parameterization (black).}
+  \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective 
+  parameterization (black).  Experiments with the LW CRE off are shown with thin lines.  
+  Panels on the left show large domains with a width of 16000 km and
+  panels on the right show domains with a width of 4000 km.}
   \label{fig:conv_vs_ls}
@@
 total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
-While the relative contribution is not well constrained, it is thought to influence the atmospheric state (Held et al., what part of the state?). 
-The distribution of convective and large-scale precipitation can often indicate how the condensational heating
+While the relative contribution of each component is not well constrained, it is thought to influence the 
+atmospheric state (Held et al., what part of the state?). 
+The distribution of convective and large-scale precipitation indicates how the condensational heating
 in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
@@
 the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective precipitation 
-but does act to spatially concentrate it.  With the single exception 
+but does act to spatially concentrate it.  With the exception 
 of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
 both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
-seen in Figure \ref{fig:domdep_lwoff} corresponds to decrease in the large-scale precipitation of about 65\% in P25L case
+seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
 and an almost complete elimination of the large-scale precipitation in the P100L case.
@@
 Can we hope to simulate all of this in a single idealized modeling context?    
-Our initial motivation for using the GFDL AM4 model on a doubly-periodic domain was to simulate this region 
+Our initial motivation for using the GFDL AM4 model on a doubly-periodic domain was to simulate 
+a tropical Pacific-like region 
 %that is rich in phenomena 
@@
 would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
-interactions of the tropical Pacific.    
+interactions of the tropical Pacific and improve our ability to model this region in a GCM.    
 The dynamical core of the current generation GFDL models is ideally suited to this task because it can easily 
@@
       \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
-      \caption{The steady state relative humidity (shading) and mass streamfunction (black contours).  
-      Shown is E25 (left), E2(center), and E1(right).  All panels use the same contour interval for the 
+      \caption{The equilibrated state of the Walker cell as a function of resolution.  
+      Experiments shown are E25 (left), E2(center), and E1(right). Top panels show the 
+      steady state relative humidity (shading) and mass streamfunction (black contours)
+      while bottom panels show the total condensation (liquid + ice).  
+      All panels use the same contour interval for the 
       mass streamfunction (kg/s).}
@@
 centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more 
-variability at later times, compared to these first 180 days.  The simulations with explicit convection at resolutions 
+variability at later times compared to these first 180 days.  The simulations with explicit convection at resolutions 
 typical of cloud-resolving models (E2, E1) show little aversion to the precipitation maximum occurring over 
 the maximum in SST and relative to the P100, P25 and E25 simulations 
-they are able to maintain a smoother distribution of  precipitation values over a broader range of SST values.
+they are able to maintain a smoother distribution of  precipitation over a broader range of SST values.
 
@@
 %\end{figure}
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
+  \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
+  subsidence regions and are shown for the control (LWCRE on) and LWCRE off experiments.}
+  \label{fig:cf_tdtlw}
+\end{figure}
 
@@
   \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
-  \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
-  subsidence regions and are shown for the control (LWCRE on) and LWCRE off experiments.}
-  \label{fig:cf_tdtlw}
-\end{figure}
-
-\begin{figure}
-  \centering
     \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
@@
 would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
-
-Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
-\begin{itemize}
-  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
-  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
-  that is 40\% higher than in the parameterized, lower resolution simulations.  
-  \item two to four times more ice condensate above 600 hPa but only about half as much liquid condensate below 700 hPa.
-  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
-  simulations are 10-20\% higher (3.5-3.9 mm/d).  
-  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
-  %\item much less vertical shear.  
-\end{itemize}
 
@@
 
+Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
+\begin{itemize}
+  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
+  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
+  that is 40\% higher than in the parameterized, lower resolution simulations.  
+  \item two to four times more ice condensate above 600 hPa but only about half as much liquid condensate below 700 hPa.
+  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
+  simulations are 10-20\% higher (3.5-3.9 mm/d).  
+  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
+  %\item much less vertical shear.  
+\end{itemize}
+
 There is a rich literature on tropical overturning circulations.  Much of it is focused on the Hadley circulation and while some
@@
 
+\bibliography{Silvers_WalkerCell}
+
 %\bibliography{references}

### 2019-10-31 Silvers_WalkerCell.tex
added reference for Bjerknes 69 and a small amount of text

@@
 \begin{itemize}
-  \item{Citation of Walker, Bjerness, and Johnson et al. papers to set the stage}
+  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus/congestus, and congestus clouds.
+The Hadley circulation connects the tropical pacific with subtropics and has been extensively studies (review paper?).
+The circulation first
+  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep convection to the 
+  eastern Pacific region which tends to be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  This circulation
+   has come to be 
+  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).
+Previous studies have focused on observations (Walker, Bjerknes), theory (Geisler, 1981),
+  or modeling studies (Bretherton et al., 2006; Wofsy and Kuang, 2012).  The modeling studies have compared theoretical models with cloud
+  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker Circulation with 
+  simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
   \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
@@
   a forced compositing of the data  
-  \cite{Bretherton2005, Muller2012}.
-  %Bretherton et al. 2005, Muller and Held, 2012)
-  }
+  \cite{Bretherton2005, Muller2012}.}
   \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 

### 2019-11-01 Silvers_WalkerCell.tex
added precipitable water to table 2.  added one total condensate figure, changed the other one.

@@
 \caption{Domain mean precipitation ($\overline{\rm{P}}$), outgoing longwave radiation 
-($\overline{\rm{OLR}}$), and subsidence fraction (SF)  or fraction of domain that is subsiding at the 532 hPa level.
+($\overline{\rm{OLR}}$), precipitable water ($\overline{\rm{PW}}$), and subsidence fraction (SF)  
+or fraction of domain that is subsiding at the 532 hPa level.
 Values in parenthesis correspond to experiments whith LWCRE is off.}
-    \begin{tabular}{*{4}{c}}
+    \begin{tabular}{*{5}{c}}
     \hline
@@
     \\
- Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$ & SF   \\ \hline
-  P100L   &  4.1 (3.5)   &  283.1 (286.9)    & 0.89 (0.61)      \\ 
-    \\
-  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 0.73 (0.71)           \\  
-    \\
-  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 0.78 (0.69)          \\  
-    \\
-  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 0.80 (0.72)          \\  
-    \\
- E25  & 3.7 (3.5)    &   271.9 (286.8)   & -            \\  
-    \\
- E2   &  3.1 (3.4)   &  266.2 (285.5)    & 0.83 (0.77)           \\ 
-    \\
- E1   &  3.3 (3.7)   &  269.3 (289.2)    & 0.78 (0.78)         \\  \hline
+ Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
+  P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.89 (0.61)      \\ 
+    \\
+  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.73 (0.71)           \\  
+    \\
+  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.69)          \\  
+    \\
+  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.72)          \\  
+    \\
+ E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & -            \\  
+    \\
+ E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.83 (0.77)           \\ 
+    \\
+ E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.78 (0.78)         \\  \hline
 
@@
 
+\begin{figure}
+  \centering
+       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
+          \caption{Domain mean total condensate (liquid + ice) for P100 (red) and P25 (yellow) on the domain 
+          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
+          and dashed lines experiments with LWCRE off.}
+  \label{fig:TotCond}
+\end{figure}
+
 Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
@@
   \centering
-      \includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
+      %\includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
+       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
           \caption{Domain mean total condensate (liquid + ice) for P25 (thin yellow), E25 (yellow), 
@@
           and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
-          convection except the thin yellow lines which have the convective parameterization turned on.}
+          convection.}
   \label{fig:TotCond}

### 2019-11-01 Silvers_WalkerCell.tex
minor changes to intro outline

--- 2019-10-29 Silvers_WalkerCell.tex
@@
 \begin{itemize}
-  \item{Citation of Walker, Bjerness, and Johnson et al. papers to set the stage}
+  \item{Citation of Walker, Bjerness, and Johnson et al. papers to set the stage for why we are writing this paper.  The reality is that we 
+  were also inspired by Schneider et al.
+2017.
+Is it possible to tie all that together in a sensible way?
+Johnson et al.
+discusses the trade inversion and the high statitic stability in the subtropics.
+He contrasts the thermodynamic arguments of Kloesel and Albrecht (1989)
+  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?}
   \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
@@
 circulation because it includes strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-clouds (Johnson et al. 1999), as well as stratocumulus cloud decks along the eastern extremities of the basin.
+clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
 Can we hope to simulate all of this in a single idealized modeling context?    

### 2019-11-01 Silvers_WalkerCell.tex

--- 2019-11-01 Silvers_WalkerCell.tex
@@
   simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
+The reality is that we 
+  were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
+Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
+the thermodynamic arguments of Kloesel and Albrecht (1989) 
+  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?}
   \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale

### 2019-11-01 Silvers_WalkerCell.tex
significant textual edits and updates to reference

@@
 the thermodynamic arguments of Kloesel and Albrecht (1989) 
-  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?}
+  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
   \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
@@
   \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
-  \caption{Evolution of precipitation through 3 years of simulation for a grid spacing of 25km (2 panels on right) and
-  100km (two panels on left).  For each resolution, domains with a width of 4,000 km and 16,000 km are shown.}
+  \caption{Evolution of precipitation through 3 years of simulation.  From left, large domain 100km, (P100L); 
+  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
+  For each resolution, the only difference between the two experiments shown is a domain length of 
+  16,000 km or 4,000 km.}
   \label{fig:domdep}
@@
   \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
-  \caption{Identical to previous figure, except that LW CRE is now off.}
+  \caption{Identical to previous figure, except that LW CRE is now off.  Evolution of precipitation through 
+  3 years of simulation.  From left, large domain 100km, (P100L); 
+  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
+  For each resolution, the only difference between the two experiments shown is a domain length of 
+  16,000 km or 4,000 km.}
   \label{fig:domdep_lwoff}
@@
           and dashed lines experiments with LWCRE off.}
-  \label{fig:TotCond}
+  \label{fig:TotCond_P25P100}
 \end{figure}
@@
 
-Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
-surface enthalpy flux reveals large differences in the symmetry.   Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
-the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
-without (thin lines) the LW CRE.  
-Over the SST maximum, E25 has a surface enthalpy flux that is 
-60 W/m2 larger than that of the E1 experiment, and the E1 experiment has a very irregular pattern of enthalpy flux in the middle
-half of the domain.  It appears that these differences in magnitude and regularity are due to the differing wind speeds among 
-the three experiments.  The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere
-and the E1 experiment also has the largest domain mean wind shear of the three models.  This is consistent with the 
-strong asymmetries of the P25 experiment being connected to a large domain mean wind shear in that experiment.  
-It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
-with the E2 and E25 experiments.  Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
-enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
-This decreased enthalpy flux also corresponds to an increased amount of specific humidity in the lowest atmospheric 
-model level.        
-%%%%%
-% section 3 of results
-
-% Hovmoller diagram of precipitation for the first 6 months of the 25km, 2km, and 1km experiments
-% LW CRE on
-
-Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
-fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
-P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
-require a correspondingly larger amount of condensational heating and precipitation.
-
 \begin{figure}
@@
 
-The influence of resolution on the atmospheric state is clearly illustrated with the LW CRE off experiments shown 
-in Figure \ref{fig:rh_psi_P25E2E1_lwoff}.
-The two-dimensional structure of circulation and humidity shows that the amount of condensate aloft in the 
-deep-convective region and the range of relative
-humidity values between the ascent and descent regions increase with resolution.  It is also apparent in Figure
+The influence of resolution on the atmospheric state can be clearly seen in the two-dimensional structure 
+of circulation and humidity.   Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show 
+the humidity, condensate, and circulation with and without the LWCRE.  Both figures illustrate that the E1
+and E2 experiments have a stronger deep overturning circulation above the warm patch and they have 
+significantly more condensate aloft in this region.      
+It is also apparent in Figure \ref{fig:rh_psi_P25E2E1} and 
 \ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa decreases with increasing resolution.  
 This is consistent with an overturning circulation that 
-strengthens as the resolution increases.  Figure \ref{fig:rh_psi_P25E2E1_lwoff} also shows greater asymmetries 
+strengthens as the resolution increases and transports more moisture to the mid-troposphere.
+It is also consistent with weaker mixing from shallow clouds as resolution decreases as
+discussed in \citeA{Pauluis2006}.   
+Figure \ref{fig:rh_psi_P25E2E1_lwoff} also shows greater asymmetries 
 and generally weaker circulations below about 500 hPa.  
-When the clouds and radiation are allowed to directly interact with each other the E2 and E1 simulations 
-appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}).  The simulations with LW CRE also have a better
-organized and stronger circulation below 500 hPa.
+When the clouds and radiation directly interact with each other the experiments have a better
+organized and stronger circulation below 500 hPa and the E2 and E1 simulations 
+appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}) than they do with LWCRE off.
 
@@
 strength of convection 
-and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for P25, E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE off (dashed lines).  There is a significant difference 
-between the GCM-like P25/E25 experiments and the CRM-like E2/E1 experiments with the former having much 
+and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
+(solid lines) and the corresponding experiments with the LWCRE off (dashed lines), profiles for the experiments
+with parameterized convection were discussed in the previous section (Figure \ref{fig:TotCond_P25P100}).  
+There is a significant difference 
+between the GCM-like P100, P25 and E25 experiments and the CRM-like E2 and E1 experiments with the former having much 
 higher values of low-level liquid condensate/cloud and the later having much higher values of upper level ice 
-condensate.  The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
-regions of the CRM-like experiments.     It is also interesting to note that the LWCRE results in less condensate 
-above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
-
-The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
-where the differences in strength of the overturning circulation are most pronounced. 
-(can we use this to understand the differences in LWCRE?).
+condensate.  \citeA{Pauluis2006} showed that for decreasing resolution an RCE model had a moist bias in the 
+subcloud layer and a dry bias in the troposphere above.  This is what our results show as well.
+
+Examining the LWCRE reveals an interesting difference between the coarse experiments with parameterized convection
+and the CRM-like experiments.  Interactive LWCRE lead to less upper level ice-condensate for our CRM experiments
+with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  The opposite occurs for our 
+GCM-like experiments.  The interactive LWCRE increase the amount of upper level ice-condensate 
+(Figure \ref{fig:TotCond_P25P100}.     
+The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
+regions of the CRM-like experiments.     
+%the LWCRE results in less condensate 
+%above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
+
+%The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
+%where the differences in strength of the overturning circulation are most pronounced. 
+%(can we use this to understand the differences in LWCRE?).
+
+Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
+surface enthalpy flux reveals large differences in the symmetry.   Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
+the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
+without (thin lines) the LW CRE.  
+Over the SST maximum, E25 has a surface enthalpy flux that is 
+60 W/m2 larger than that of the E1 experiment, and the E1 experiment has a very irregular pattern of enthalpy flux in the middle
+half of the domain.  It appears that these differences in magnitude and regularity are due to the differing low-level 
+wind speeds among 
+the three experiments.  The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere.  
+This is consistent with the 
+strong asymmetries of the P25 experiment being connected to a large domain mean wind shear in that experiment.  
+It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
+with the E2 and E25 experiments.  Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
+enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
+This decreased enthalpy flux also corresponds to an increased amount of specific humidity in the lowest atmospheric 
+model level.
+
+Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
+fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
+P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
+require a correspondingly larger amount of condensational heating and precipitation.
 
@@
 
-An interesting fact that emerges from the domain mean values of precipitation (see Table 2) 
-is that the sign of the response to LWCRE is not the same across the different grid-spacings.
-When clouds are not allowed to interact with the longwave radiation the atmosphere can cool 
-much more efficiently, as evidenced by larger values of OLR for all experiments when the LWCRE is
-off.  Typically, the atmospheric cooling can be thought of as a proxy for the mean precipitation 
-because the cooling is primarily offset by condensational heating.  This is clearly not the case 
-for the E25, P25, and P100 cases for which the domain mean precipitation rates decrease despite
-an increased amount of atmospheric cooling.  The implication is that the requisite atmospheric 
-heating is coming from a process other than condensation.  The solution lies in the energy 
-budget of the surface.  A fixed SST means that in all cases the upward flux of longwave energy
-is constant, the upward flux of sensible heat flux will be mostly fixed (barring variations in surface
-wind), and changes in downward shortwave flux will not be able to warm the surface.  However, 
-the dramatic decrease of low-level clouds for the E25, P25, and P100 experiments when LWCRE is
-off strongly influences the net flux of longwave energy at the surface (does the downwelling longwave
-flux change becuase there are less clouds or because they are invisible to radiation?).  Under 
-natural conditions with an interactive surface, the surface is warmed by a downward flux of longwave 
-radiation due to the clouds
-above.  When this source of atmospheric energy loss is removed in the LWCRE off experiments 
+An interesting point that emerges from the domain mean values of precipitation (see Table 2) 
+is that the sign of the response to LWCRE is not the same across the different resolutions.
+When clouds are not allowed to interact with the longwave radiation the atmosphere 
+emits more radiation to space, as evidenced by larger values of $\overline{\rm{OLR}}$ 
+for all experiments when the LWCRE is
+off.  Atmospheric radiative cooling can be thought of as a proxy for the mean precipitation 
+because the cooling is balanced primarily by condensational heating.  Larger values of 
+$\overline{\rm{OLR}}$ would correspond to larger values of $\overline{\rm{P}}$.  
+This is clearly not the case 
+for the E25, P25, and P100 cases.   \textit{The domain mean precipitation rates decrease despite
+an increased amount of atmospheric cooling.}  The implication is that the requisite atmospheric 
+heating must come from a process other than condensation.
+
+The solution lies in the energy budget of the surface.  
+A fixed SST means that the upward flux of longwave energy
+is constant.  The upward flux of sensible heat flux will be mostly fixed (barring variations in surface
+wind) because changes in the downward flux of solar radiation will not warm the surface.  
+However, the dramatic decrease of low-level clouds for the E25, P25, and P100 LWCRE off 
+experiments strongly influences the net flux of longwave energy at the surface. 
+Low-level clouds normally serve as a significant source of longwave radiative cooling 
+for the atmosphere.  Making these clouds invisible to radiation creates a source of 
+effective atmospheric warming.  
+%(does the downwelling longwave
+%flux change because there are less clouds or because they are invisible to radiation?).  
+With an interactive surface, the surface temperature is influenced
+by a downward flux of longwave radiation from the clouds above.  
+When this source of atmospheric energy loss is removed in the LWCRE off experiments 
 the upwelling longwave flux of radiation plays a larger role in warming the atmosphere that more 
-than compensates for the increased OLR at the top of the atmosphere.  Thus, with an increase in 
+than compensates for the increased OLR at the top of the atmosphere.  There is an increase in 
 atmospheric warming on 
-the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off, there is less need for condensational 
-heating.  The mean precipitation rate actually decreases.  The large decrease of low-level clouds also 
-leads to a large increase of downward shortwave radiation.  This only slightly increases the
-fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) but does contribute to 
-heating the atmosphere.
-
-Turning the LW CRE off for the E1 and E2 experiments results in more precipitation while, 
-for the E25, P25, and P100 experiments, less precipitation results from turning the LW CRE off.  
+the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off and thus there is less need for 
+condensational heating.  The mean precipitation rate actually decreases.  
+The large decrease of low-level clouds also leads to an increase of downward shortwave 
+radiation.  Because of the low albedo of water
+this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
+but does contribute slightly to heating the atmosphere.
+
+In contrast to the P100, P25, and E25 experiments just discussed, turning the LW CRE off for 
+the E1 and E2 experiments results in more precipitation.  This can be understood as follows.  
 The primary method by which the longwave cloud radiative effect influences the atmosphere is by 
 heating the atmosphere in the region between the clouds and the surface.  
-Larger values of ice condensate and upper-level cloud fraction such as we see for the E2 and E1 experiment 
-therefore imply a larger LW CRE relative to the E25, P25, and P100 experiments in which there are fewer clouds 
-aloft that can emit downwelling longwave radiation.  When the warming effect of the upper level clouds 
+Larger values of ice condensate and upper-level cloud fraction as seen in the E2 and E1 experiment 
+(Figure \ref{fig:TotCond}) 
+therefore imply a larger atmospheric heating due to the CRE relative to the E25, P25, and P100 
+experiments in which have fewer clouds aloft (Figures \ref{fig:TotCond} and \ref{fig:TotCond_P25P100}).  
+When the warming effect of the upper level clouds 
 in the E1 and E2 experiments is removed in the LWCRE off experiments the energy balance of the atmosphere 
 must be maintained through an increase of latent heating and subsequent increase of precipitation.  This is 
-reflected in Table 1.  The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
-is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
-However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.
-
-For GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
-convective parameterization, and one part from the large-scale cloud scheme.  Figure \ref{fig:conv_vs_ls} shows 
-that when the LWCRE is turned off for the P25 and P100 experiments, the decrease in precipitation comes from 
-a reduction in the large-scale cloud scheme precipitation and not from a decrease in the convective precipitation.       
-This implies (is this connected to previous sentence?) there will be less atmospheric heating from 
-longwave radiation (but doesn't LW just cool the atmosphere?) and a corresponding 
-larger heating due to condensational heating which is consistent with higher values 
-of domain mean precipitation for E25, P25, and P100 compared to E2 and E1.  Similarly, the E2 experiment has lower values 
-of upper level condensate and higher values of mid-troposphere relative humidity compared to the E1 simulation, which ....??  
+reflected in Table 2.
+
+These experiments provide insight into the different mechanisms by which the clouds in GCMs and CRMs
+interact with longwave radiation in the atmosphere.  Because there are so many more low-level clouds in 
+the GCM-like experiments we see a strong response to upwelling radiation from the surface.  In contrast, 
+the abundance of upper-level ice condensate, and lack of low-level condensate in the CRM-like 
+experiments results in the primary interaction
+between clouds and radiation being in the atmosphere below the upper level clouds.
+
+%The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
+%is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
+%However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  
+%
+%For GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
+%convective parameterization, and one part from the large-scale cloud scheme.  Figure \ref{fig:conv_vs_ls} shows 
+%that when the LWCRE is turned off for the P25 and P100 experiments, the decrease in precipitation comes from 
+%a reduction in the large-scale cloud scheme precipitation and not from a decrease in the convective precipitation.
+
+%This implies (is this connected to previous sentence?) there will be less atmospheric heating from 
+%longwave radiation (but doesn't LW just cool the atmosphere?) and a corresponding 
+%larger heating due to condensational heating which is consistent with higher values 
+%of domain mean precipitation for E25, P25, and P100 compared to E2 and E1.
+
+%Similarly, the E2 experiment has lower values 
+%of upper level condensate and higher values of mid-troposphere relative humidity compared to the E1 simulation, which ....??
+
 Water vapor is an efficient emitter of long-wave radiation and thus greatly facilitates the cooling of the troposphere.  
-Popp and Silvers, 2017 showed that that there is dramatically less water vapor in the atmosphere and much less precipitation 
-for LW CRE off experiments (see their figure 1b).  Our results here for the E25, P25, and P100 are consistent with 
-those of Popp and Silvers, 2017 because the low-level condensate strongly decreases when the LWCRE is off.  This is not 
-the case for E2 and E1.  Those experiments have very little low-level condensate to begin with and thus do not experience 
-large changes in low-level condensate when the LWCRE is off.  They do however have a large increase of upper
-level condensate for the LWCRE off experiments.   This is a large difference in the way that models with explicit convection 
-respond to the LWCRE compared to more traditional large-scale models with parameterized convection.
+Popp and Silvers, 2017 showed that there is dramatically less condensate in the atmosphere and much less precipitation 
+(at the equator) 
+for LW CRE off experiments (see their figure 1a,b).  Our results here for the E25, P25, and P100 are consistent with 
+those of Popp and Silvers, 2017 because the low-level condensate are strongly decreased when the LWCRE is off.  
+%This is not the case for E2 and E1.  Those experiments have little low-level condensate to begin with 
+%%and thus do not experience 
+%%large changes in low-level condensate when the LWCRE is off.  
+%but they do have a large increase of upper
+%level condensate for the LWCRE off experiments.   
+%This is a large difference in the way that models with explicit convection 
+%respond to the LWCRE compared to more traditional large-scale models with parameterized convection.
 
@@
 \end{figure}
-
-%  \caption{Variables important to boundary layer energy fluxes.
-Top left panel shows the surface enthalpy flux ($\rm{W m^{-2}}$) and top right panel shows the equivalent potential temperature on the model level closest to the surface.
-The panel on bottom left shows the $u$ wind ($\rm{m s^{-1)}}$)
-%  on the model level closest to the surface and the panel on bottom right shows the domain mean
-%  $\rm{u}$ wind.}
-
-%% surface enthalpy flux
-%\begin{figure}
-%  \centering
-%  \begin{minipage}{0.4\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOn.eps} 
-%    \end{minipage}
-%    \begin{minipage}{0.4\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/sfcenthalpyflx_3mods_lwcreOff.eps}
-%    \end{minipage}
-%    \caption{Surface enthalpy flux (solid lines) for the three grid-spacings.  Dashed lines show the individual components 
-%    (latent and sensible heat flux) of the enthalpy.
-%    On the left are experiments with LWCRE on and on the right, the same experiments but with LWCRE off.}
-%    \label{fig:enthalpy}
-%\end{figure}
-
-There are also differences in the lapse-rate below $700 \rm{hPa}$, in the upper-level clouds,
-and the domain mean precipitation (Figure \ref{fig:precip_dom_mn}).
 
@@
 would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
-
-%% Domain mean vertical structure for 25km, 2km, and 1km resolutions
-%% LW CRE on
-%\begin{figure}
-%  \includegraphics[width=0.8\columnwidth]{walkerfigs/Walker_VertStr_LWCRE_b.eps}
-%  \caption{Domain mean vertical structure for simulations with a grid spacing of 25km (yellow, parameterized convection), 2km (blue), and 1km (green).  
-%  All experiments have active LWCRE.  The dotted lines of RH show the mean over the cold pool regions.  Thin lines on the lapse rate panel show the moist adiabat for reference.}
-%  \label{fig:vertst_lwcre}
-%\end{figure}
-%
-%% Domain mean vertical structure for 25km, 2km, and 1km resolutions
-%% LW CRE off
-%\begin{figure}
-%  \includegraphics[width=0.86\columnwidth]{walkerfigs/Walker_VertStr_LWCREoff.eps}
-%  \caption{Domain mean vertical structure for simulations with a grid spacing of 25km (yellow, parameterized convection), 2km (blue), and 1km (green).  
-%  All experiments have LWCRE off.  The dotted lines of RH show the mean over the cold pool regions.  Thin lines on the lapse rate panel show the moist adiabat for reference.}
-%  \label{fig:vertst_lwcre_off}
-%\end{figure}
-%
-%% RH and Psi for 1km, 2km, and 25km simulations			
-%\begin{figure}
-%  \centering
-%  \begin{minipage}{0.49\textwidth}
-%    \centering
-%      %\includegraphics[width=0.5\columnwidth]{randomfigs/psi_rh_1km_lwoff.eps} 
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_1km_ctl.eps} 
-%    %\caption{{\bf default}}
-%    \end{minipage}
-%    \begin{minipage}{0.49\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_1km_lwoff.eps}
-%      %\caption{{\bf default}}
-%    \end{minipage}
-%    \begin{minipage}{0.49\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_2km_ctl.eps}
-%      %\caption{{\bf default}}
-%    \end{minipage}
-%    \begin{minipage}{0.49\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psi_rh_2km_lwoff.eps}
-%      %\caption{{\bf default}}
-%    \end{minipage}
-%    \begin{minipage}{0.49\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psirh_noconv_ensind0_contint5.eps}
-%      %\caption{{\bf default}}
-%    \end{minipage}
-%    \begin{minipage}{0.49\textwidth}
-%    \centering
-%      \includegraphics[width=0.96\columnwidth]{walkerfigs/psirh_noconv_lwoff_ensind3_contint5.eps}
-%      %\caption{{\bf default}}
-%    \end{minipage}
-%    \caption{Relative humidity is shown by the shading while the mass streamfunction is given my the black contour lines.  The top row shows the 1km experiments, the middle row the 2km
-%    experiments, and the bottom row the 25 km experiments.  Experiments with LWCRE are on the left and 
-%    experiments without are on the right.}
-%\end{figure}
-%
 

### 2019-11-05 Silvers_WalkerCell.tex
several textual edits related to domain size dependence

@@
 \begin{keypoints}
-  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
-  precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
-  maximum.}
+%  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
+ % precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
+%  maximum.}
   \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
@@
 % What are climate modelers doing to reduce uncertainties about cloud processes?
-The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
-greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
-dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
-and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  To elucidate this 
-coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an idealized equatorial tropical Pacific.   In 
-the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective storms.   In contrast, 
-the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, non-precipitating clouds with a dry 
-atmosphere above the clouds.  These regions are connected by a large-scale circulation.  We analyze this scenario in a high-resolution 
-and coarse resolution simulation and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
+%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
+%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
+%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
+%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
+%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
+%idealized equatorial tropical Pacific.
+
+In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective 
+storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
+non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
+connected by a large-scale circulation.  
+We analyze this circulation with high-resolution 
+and coarse resolution simulations and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
 thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth's sensitivity to 
@@
 derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
-dramatically decreasing the grid-spacing we resolve much more of the dynamical motion and eliminate some of the statistical 
-approximations of clouds, and thus more explicitly simulate some of their impacts.
+dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
+some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
 
@@
 \begin{itemize}
-  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus/congestus, and congestus clouds.
-The Hadley circulation connects the tropical pacific with subtropics and has been extensively studies (review paper?).
-The circulation first
-  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep convection to the 
-  eastern Pacific region which tends to be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  This circulation
-   has come to be 
-  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).
-Previous studies have focused on observations (Walker, Bjerknes), theory (Geisler, 1981),
-  or modeling studies (Bretherton et al., 2006; Wofsy and Kuang, 2012).  The modeling studies have compared theoretical models with cloud
-  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker Circulation with 
-  simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
-The reality is that we 
-  were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
+  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
+  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
+  extensively studies (review paper?).  The circulation first 
+  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
+  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
+  subtropics, stratocumulus clouds.  This circulation has come to be 
+  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
+  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
+  observations (Walker, Bjerknes), theory (Geisler, 1981), 
+  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
+  modeling studies have compared theoretical models with cloud
+  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
+  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
+  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
  Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
@@
 
+Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
+cumulus, and cumulus congestus clouds all interact with each other.  The Hadley circulation connects the tropical 
+pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
+  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep 
+  convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
+  subtropics, stratocumulus clouds.  This circulation has come to be 
+  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 
+  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory 
+  (Geisler, 1981), or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
+  Kuang, 2012)).  Some of these modeling studies have compared theoretical models with cloud
+  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker 
+  Circulation with simulations from a GCM used on a doubly periodic domain.
+
 We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
-highlight both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
+show both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
 we test the impact of convective parameterization, 
 longwave radiation interactions with clouds, domain size, 
-and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain size and resolution
-because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
-
-The results of our experiments are organized as follows.  First, the general structure and characteristics of the steady state solutions
-will be described.   Then, the influence of parameterized convection and the longwave cloud radiative effect on the overturning 
-circulation will be shown.  We will then briefly discuss how the circulation changes as a function of domain size.  The last part of the
-results will describe and contrast the Walker circulation in a GCM-like configuration and a CRM-like configuration as the 
-resolution changes.
+and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
+size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
+
+The results of our experiments are organized as follows.  Details of the model and the particular experiments used are described
+in the next section.  The longwave cloud radiative effect is an important element for all of the experiments and will be 
+discussed in all of the sections.   
+Section three describes the tendency of experiments with parameterized convection to settle into states which 
+do not mirror the symmetry of the prescribed sea surface temperature.   
+Then, section four shows how the distribution of precipitation changes as a function of domain size.  
+Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration. 
+Conclusions from this study will then be summarized.
 
@@
 \caption{Specifications of the simulations used most heavily in this study.  In the Convection
-column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.}
+column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.
+All of the experiments listed here were also run with the longwave cloud radiative effect turned off.
+These will be referred to as P100L LWCRE off, etc.  }
     \begin{tabular}{*{5}{c}}
@@
 
-"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
-double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
-was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
-vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
-Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
-turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
-greater are being dominated by this second factor.
+%"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
+%double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
+%was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
+%vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
+%Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
+%turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
+%greater are being dominated by this second factor.
 
@@
 \cite{Bretherton2005, Bretherton2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
-(e.g. Bretherton et al., 2005; Bretherton et al., 2006; Muller and Held, 2012; Jeevanjee and Romps, 2013; 
-Silvers et al., 2016; Patrizio and Randall, 2019) have 
-documented sensitivities of the equilibrated state to domain size.   
+have documented sensitivities of the equilibrated state to domain size for similar experiments
+of radiative convective equilibrium.   
 The analysis of the previous, and of the next sections focus on results from 
-experiments using a domain with a long domain length of $4000 \, \rm{km}$.  However we do find interesting 
-sensitivities to the domain size that are noted here.
-
-The evolution in time of the precipitation field reveals important characteristics of these simulations, and 
-illustrates how much the distribution can vary as a function of domain size, parameterization of convection, 
-and the effect of the longwave radiation due to clouds. 
+experiments using a domain with a long domain length of $4,000 \, \rm{km}$.  However when comparing those results
+to experiments with a long domain length of $16,000 \, \rm{km}$, we find interesting 
+sensitivities to the domain size that are described in this section.
+
+The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
+function of domain size, parameterization of convection, and the effect of the longwave radiation due to clouds. 
 Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
@@
 $16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.
+
 At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
@@
 strengthen an overturning circulation and
-narrow the region of deep convection (see Popp and Silvers, 2017, HH, Dixit et al. 2019.  etc.).
+narrow the region of deep convection (see Popp and Silvers, 2017, Harrop and Hartmann, Dixit et al. 2019.  etc.).
 The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
 On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
-experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation which meanders within 
-500 km of the SST maximum at the center of the domain,  
+experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation 
+meandering within 500 km of the SST maximum at the center of the domain,  
 the experiments without the LW CRE basically have no region with consistently strong precipitation.  Instead, 
-smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously notes, these
-GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
+smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously noted, 
+these GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
 the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
@@
 
+An additional change that results from increasing the domain width is an upward shift of the cloud fields.  This is 
+shown with the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low level maximum of 
+condensate is shifted from near 900 hPa in the small domain (thin lines) to between 700-800 hPa in 
+the large domain (thick lines).  There is also a vertical shift in the upper level ice condensate, but it is less
+pronounced.
+
 % new Hovmoller diagram
@@
   \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
-  \caption{Evolution of precipitation through 3 years of simulation.  From left, large domain 100km, (P100L); 
+  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
+  25km and 100km.  From left, large domain 100km, (P100L); 
   small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
@@
 
-Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
-They also found less low-level clouds over the colder SSTs in the small domains, relative to a control domain size that was 4x
-larger.   In contrast, here larger domains have larger precipitation rates (Table 2).  For the LWCRE off cases, in agreement 
-with \citeA{Bretherton2006} we find a more 
-focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the ascent region changes little between P25 
-and P25L but for P100 and P100L the ascent region is much more focuses on the large domain.    
-How do our low-level clouds over the colder SSTs compare with the findings of B06 (check the condensate for small vs. large 
-domains)?
+The domain mean total precipitation is constrained by the radiative cooling of the atmosphere.  
+However, in models with the convection parameterized, the 
+total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
+The relative contribution of each component is not well constrained and \citeA{Held2007} have shown 
+that the fraction of the precipitation that is due to the large-scale cloud scheme is closely linked 
+to low cloud cover and total condensate.  
+The distribution of convective and large-scale precipitation indicates how the condensational heating
+in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
+Precipitation from each of these two components is
+shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
+In the regions of large-scale ascent, most of the 
+precipitation derives from the large-scale cloud scheme.  
+Following the terminology of \citeA{Held2007} we could say that most of the precipitation is 
+coming from `gridpoint storms' in which the upper level moisture is being supplied not 
+by the convective parameterization but from the boundary layer as a result of large-scale upwelling.
+We also see that the LW CRE (thick lines) dramatically increases
+the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective 
+precipitation 
+but does act to spatially concentrate it.  With the exception 
+of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
+both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
+seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
+and an almost complete elimination of the large-scale precipitation in the P100L case.    
+The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low level cloud radiative
+effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction.  
+We also demonstrate that is through the longwave cloud radiative effect that this connection is enabled.
 
@@
 
-The domain mean total precipitation is constrained by the radiative cooling of the atmosphere.  However, in 
-models with the convection parameterized the 
-total precipitation is composed of precipitation from the convection scheme and the large-scale cloud scheme. 
-While the relative contribution of each component is not well constrained, it is thought to influence the 
-atmospheric state (Held et al., what part of the state?). 
-The distribution of convective and large-scale precipitation indicates how the condensational heating
-in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
-Precipitation from each of these two components is
-shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
-In the regions of large-scale ascent, most of the 
-precipitation derives from the large-scale cloud scheme.  We also see that the LW CRE (thick lines) dramatically increases
-the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective precipitation 
-but does act to spatially concentrate it.  With the exception 
-of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
-both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
-seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
-and an almost complete elimination of the large-scale precipitation in the P100L case.
+Smaller domains were found to have a more focused ascent region and larger precipitation rates in B06.
+They also found less low-level clouds over the colder SSTs in the small domains (1,024 km wide), relative 
+to a control domain with a width of 4,096 km.   In contrast, here larger domains have larger precipitation rates (Table 2).  
+We find fewer low-clouds on the large domain experiments (P25L, P100L), but a mid-level cloud 
+maximum (Figure \ref{fig:TotCond_P25P100}).   There are notable differences in the domain mean condensate between 
+the default and large domains.  Overall the large domains show an upward shift of condensate and have 
+a much stronger upper level response to the LWCRE being turned off.
+For the LWCRE off cases, in agreement with B06 we find a more 
+focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
+changes little between P25 
+and P25L but for P100 and P100L the ascent region is much more focused on the large domain.
 
@@
 
+We were struck by three particular changes due strictly do a 4-fold increase in domain width.
+A dramatic widening of the precipitation distribution when the LW CRE is off, a shifting of low level clouds upward by more than 100 hPa, and
+a strong dependence of the quantity of precipitation produced by the large-scale scheme on the LW CRE.
+
 The longwave cloud radiative effect (LWCRE) has been shown to play a dramatic role in the organization of the precipitation
@@
 
-References:
-
-Bretherton et al. 2006
-Jeevanjee et al. 2018
-Kuang and Wofsy
-Muller and Held, 2012
-Popp and Silvers, 2017
-Patrizio and Randall, 2019
-Randall et al., 1989
-Silvers et al. 2016
-Slingo and Slingo, 1988
-Stevens et al. 2012
-Zhao et al. 2018a
-Zhao et al. 2018b
+%References: 
+%
+%Bretherton et al. 2006
+%Jeevanjee et al. 2018
+%Kuang and Wofsy
+%Muller and Held, 2012
+%Popp and Silvers, 2017
+%Patrizio and Randall, 2019
+%Randall et al., 1989
+%Silvers et al. 2016
+%Slingo and Slingo, 1988
+%Stevens et al. 2012
+%Zhao et al. 2018a
+%Zhao et al. 2018b
 
@@
 
-%\bibliography{references}
-%\begin{thebibliography}{}
-%
-%\bibitem[{\textit{Bretherton et~al.}(2005)\textit{Bretherton, Blossey, and
-%  Khairoutdinov}}]{Bretherton_etal_2005}
-%Bretherton, C.~S., P.~N. Blossey, and M.~Khairoutdinov (2005), An
-%  energy-balance analysis of deep convective self-aggregation above uniform
-%  sst, \textit{J. Atmos. Sci.}, \textit{62}, 4273--4292.
-%
-%%\bibitem[{\textit{Jeevanjee and Romps}(2013)}]{Jeevanjee_Romps_2013}
-%%Jeevanjee, N., and D.~M. Romps (2013), Convective self-aggregation, cold pools,
-%%  and domain size, \textit{Geophys.\ Res.\ Lett.}, \textit{40}, 994--99,
-%%  \doi{10.1002/grl.50204}.
-%  
-%\end{thebibliography}
-
 %%% Acknowledgements

### 2019-11-07 Silvers_WalkerCell.tex
text edits to the section comparing E25, E2, and E1

@@
 
+  Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
+and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
+The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
+because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
+clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
+Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
+GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
+%that is rich in phenomena 
+in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
+would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
+interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
+of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
+range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.
+
 We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
@@
 results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
-relative to the case with the LW CRE off.   A stronger and spatially concentrated circulation for cases when the 
+relative to the case with the LWCRE-off.   A stronger and spatially concentrated circulation for cases when the 
 clouds interact with the longwave radiation can also be seen in Figures 4, 5, 9 and 10 and is particular apparent in 
@@
 Previous studies have shown that cloud radiative effects act to strengthen and contract an overturning circulation 
-(e.g. Popp and Silvers, 2017, HH, and others (Muller and Held?), Albern et al., 2019).  This is 
+(e.g. Popp and Silvers, 2017, Harrop and Hartmann, and others (Muller and Held?), Albern et al., 2019).  This is 
 due to an increased low-level flux
@@
 for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
-fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE on
+fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE-on
 have a larger SF (with the exception of E1, for which SF is constant).  Our prescribed SST warm patch ensures that our simulations will 
@@
   left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
-  off (LWCRE off).}
+  off (LWCRE-off).}
   \label{fig:precip_vertvel}
@@
 simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
-$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LW CRE off.
-
-At all resolutions the Hovmoller plots show that the longwave CRE acts to concentrate the 
+$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
+
+At all resolutions the Hovmoller plots show that the LWCRE acts to concentrate the 
 precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
@@
 The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
-On the large domains, the difference between experiments with and without LW CRE is extreme.  In contrast to the control 
+On the large domains, the difference between experiments with and without LWCRE is extreme.  In contrast to the control 
 experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation 
 meandering within 500 km of the SST maximum at the center of the domain,  
-the experiments without the LW CRE basically have no region with consistently strong precipitation.  Instead, 
+the experiments without the LWCRE basically have no region with consistently strong precipitation.  Instead, 
 smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously noted, 
@@
 
-An additional change that results from increasing the domain width is an upward shift of the cloud fields.  This is 
+An additional unexpected change that results from increasing the domain width is an upward shift of the cloud fields.  This is 
 shown with the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low level maximum of 
@@
 We also see that the LW CRE (thick lines) dramatically increases
-the large-scale precipitation.  The LW CRE has a much smaller effect on the magnitude of the convective 
+the large-scale precipitation.  The LWCRE has a much smaller effect on the magnitude of the convective 
 precipitation 
 but does act to spatially concentrate it.  With the exception 
-of the P100L LW CRE off experiment, the convective precipitation produces relatively little of the total precipitation for 
+of the P100L LWCRE-off experiment, the convective precipitation produces relatively little of the total precipitation for 
 both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
@@
 a much stronger upper level response to the LWCRE being turned off.
-For the LWCRE off cases, in agreement with B06 we find a more 
+For the LWCRE-off cases, in agreement with B06 we find a more 
 focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
@@
 %General Circulation Model to a Cloud Resolving Model}
-\section{Dependence on Resolution: From a General Circulation Model to a Cloud Resolving Model}
+\section{Dependence on Resolution: From a General Circulation Model to Cloud Resolving}
 
@@
 
-% this paragraph should perhaps be moved to the introduction...
-It is clear that the overturning circulation in the tropical Pacific encompasses dynamical motions at a host of scales and that the 
-different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
-The tropical Pacific also serves as an ideal location to study interactions between clouds and the 
-circulation because it includes strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
-Can we hope to simulate all of this in a single idealized modeling context?    
-Our initial motivation for using the GFDL AM4 model on a doubly-periodic domain was to simulate 
-a tropical Pacific-like region 
-%that is rich in phenomena 
-in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
-would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
-interactions of the tropical Pacific and improve our ability to model this region in a GCM.    
-The dynamical core of the current generation GFDL models is ideally suited to this task because it can easily 
-be used over a wide range of resolutions and can solve either the hydrostatic or nonhydrostatic 
-governing equations.
+% ..... moved to introduction .... 
+%Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
+%and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
+%The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
+%because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
+%clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
+%Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
+%GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
+%in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
+%would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
+%interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
+%of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
+%range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.
 
@@
 
-In this section we focus on simulations with grid-spacing of 1km, 2km, and 25km.   
+We now show results that originated with our motivation to simulate a tropical Pacific-like region 
+in the context of both a GCM and a CRM.  In this section we focus on simulations with grid-spacing of 
+1km, 2km, and 25km all in a domain with a width of 4,000 km.  Overall there is good agreement on 
+the basic circulation pattern, distribution of mid-tropospheric condensate, and sensitivity of the surface
+enthalpy flux to low-level winds.  However, the E25/P25 simulations produce much more low-level cloud
+and as a result have a different response to the LWCRE.  The low-level differences among the models
+result in different spatial distributions and amounts of precipitation.
+
 A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that result from the 
 overturning circulation at different resolutions.  Shown are 180 days of precipitation from the P25, E25, E2, and 
-E1 simulations.  As the 
-resolution increases towards $1 \, \rm{km}$ the distribution of precipitation becomes more regular and consistently 
+E1 simulations.  As the resolution increases the distribution of precipitation becomes more regular and consistently 
 centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more 
-variability at later times compared to these first 180 days.  The simulations with explicit convection at resolutions 
+variability at later times compared to these first 180 days (similar to what is seen in Figure \ref{fig:domdep_lwoff} 
+for the P25 and P100 LWCRE off experiments).  The simulations with explicit convection at resolutions 
 typical of cloud-resolving models (E2, E1) show little aversion to the precipitation maximum occurring over 
-the maximum in SST and relative to the P100, P25 and E25 simulations 
-they are able to maintain a smoother distribution of  precipitation over a broader range of SST values.
-
-The steady state relative humidity and overturning circulation (Figures \ref{fig:rh_psi_P25E2E1} and 
-\ref{fig:rh_psi_P25E2E1_lwoff}) show an interesting combination of similarities and differences
-among the experiments with varying resolutions.  All experiments have a multicell vertical structure (consistent with 
-Bretherton et al. 2006), in contrast to the single cell that results from simple theoretical models such as the SQTCM.   All 
-show a similarly dry mid-tropospheric region where subsidence dominates.  However, the multicelled structure is quite irregular
-in the P25 experiment, and a small third cell has developed in the boundary layer of the 1km experiment.  The mid-troposphere 
-of the P25 experiment is more than $40\%$ dryer in the region with deep-convection than for the 2km and 1km experiments. 
-The high resolution experiments also have higher amounts of condensate throughout the troposphere, and much higher
-relative humidity above about 300 hPa.
+the maximum in SST and relative to the P100, P25 and E25 simulations they are able to maintain a 
+smoother distribution of  precipitation over a broader range of SST values.
+
+The influence of resolution on the atmospheric state can be clearly seen in the two-dimensional structure 
+of circulation and humidity.
+The steady state relative humidity and overturning circulation show both similarities and differences
+among the experiments at varying resolutions with and without LWCRE (Figures \ref{fig:rh_psi_P25E2E1} and 
+\ref{fig:rh_psi_P25E2E1_lwoff}).
+Perhaps the most obvious similarity is the double celled structure in the mass streamfunction and the most 
+obvious difference being the difference in humidity of 40\% between E1, E2, and E25 in the center of the domain.  
+%The mid-troposphere 
+%of the P25 experiment is more than $40\%$ dryer in the region with deep-convection than for the 2km and 
+%1km experiments.  All experiments have a multicell vertical structure (consistent with B06), in contrast to 
+% the single cell that results from simple theoretical models such as the SQTCM (see B06).   
+All experiments show a mid-tropospheric relative humidity minimum over the cooler SSTs where subsidence 
+dominates.  The multicelled structure is quite irregular in the P25 experiment, and a small third cell has 
+developed in the boundary layer of the 1km experiment.   The high resolution experiments also have 
+higher amounts of condensate throughout the troposphere, and much higher relative humidity 
+above about 300 hPa.
 
@@
 
-The influence of resolution on the atmospheric state can be clearly seen in the two-dimensional structure 
-of circulation and humidity.   Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show 
-the humidity, condensate, and circulation with and without the LWCRE.  Both figures illustrate that the E1
-and E2 experiments have a stronger deep overturning circulation above the warm patch and they have 
-significantly more condensate aloft in this region.      
-It is also apparent in Figure \ref{fig:rh_psi_P25E2E1} and 
-\ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa decreases with increasing resolution.  
+Compared to E25 both E1 and E2 experiments have a stronger deep overturning circulation above the warm 
+patch and they have significantly more condensate aloft in this region.    It is also apparent in Figures 
+\ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa 
+decreases with increasing resolution.  
 This is consistent with an overturning circulation that 
-strengthens as the resolution increases and transports more moisture to the mid-troposphere.
-It is also consistent with weaker mixing from shallow clouds as resolution decreases as
-discussed in \citeA{Pauluis2006}.   
-Figure \ref{fig:rh_psi_P25E2E1_lwoff} also shows greater asymmetries 
+strengthens as the resolution increases and transports more moisture from the low-levels to the 
+mid-troposphere.  It is also consistent with weaker mixing from shallow clouds as resolution decreases as
+discussed in \citeA{Pauluis2006}.   Figure \ref{fig:rh_psi_P25E2E1_lwoff}, with LWCRE-off, shows greater asymmetries 
 and generally weaker circulations below about 500 hPa.  
 When the clouds and radiation directly interact with each other the experiments have a better
-organized and stronger circulation below 500 hPa and the E2 and E1 simulations 
-appear much more similar (Figure \ref{fig:rh_psi_P25E2E1}) than they do with LWCRE off.
+organized and stronger circulation below 500 hPa.  A comparison of Figures \ref{fig:rh_psi_P25E2E1} and 
+\ref{fig:rh_psi_P25E2E1_lwoff} also shows that the E2 and E1 simulations are much more 
+similar when the clouds and radiation interact than they are with LWCRE-off.  In particular, the subsidence 
+region drying and condensate aloft in the upwelling region have a clearer dependence on resolution when 
+the LWCRE is off.  This suggests that the interactions between clouds and radiation can help the 
+atmospheric state converge towards a particular solution.
 
@@
 energy throughout the atmosphere and the longwave radiation that is emitted to space.  It can also indicate the 
-strength of convection 
-and vertical mass transport.     Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE off (dashed lines), profiles for the experiments
+strength of convection and vertical mass transport.     
+Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
+(solid lines) and the corresponding experiments with the LWCRE-off (dashed lines).  Profiles for the experiments
 with parameterized convection were discussed in the previous section (Figure \ref{fig:TotCond_P25P100}).  
@@
 condensate.  \citeA{Pauluis2006} showed that for decreasing resolution an RCE model had a moist bias in the 
-subcloud layer and a dry bias in the troposphere above.  This is what our results show as well.
+sub-cloud layer and a dry bias in the troposphere above.  Although our experiments are not strictly in RCE, our 
+results agree with those from \citeA{Pauluis2006}.
 
 Examining the LWCRE reveals an interesting difference between the coarse experiments with parameterized convection
-and the CRM-like experiments.  Interactive LWCRE lead to less upper level ice-condensate for our CRM experiments
-with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  The opposite occurs for our 
+and the CRM-like experiments.  Interactive LWCRE leads to less upper level ice-condensate for our CRM experiments
+with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  The opposite occurs for the 
 GCM-like experiments.  The interactive LWCRE increase the amount of upper level ice-condensate 
-(Figure \ref{fig:TotCond_P25P100}.     
-The LWCRE off experiments influence the low-levels of the GCM-like experiments, and the upper-level
-regions of the CRM-like experiments.     
-%the LWCRE results in less condensate 
-%above 700 hPa for all experiments, and more condensate below 700 hPa for the P25/E25 experiments.
+(Figure \ref{fig:TotCond_P25P100}).    The Influence of the LWCRE on low-level clouds is consistent for both the 
+GCM-like and CRM-like experiments.  The LWCRE leads to more low-level clouds/condensate although the 
+increase is very slight for the E1 and E2 experiments.  Overall, the LWCRE-off experiments influence the low-levels 
+of the GCM-like experiments, and the upper-level regions of the CRM-like experiments.
 
@@
 
+\begin{figure}
+  \centering
+    \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
+    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
+    For all panels, thick lines show control experiments with the LW CRE on, thin lines show experiments
+    with the LW CRE off.}
+    \label{fig:enthalpy}
+\end{figure}
+
 Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
@@
 the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
-without (thin lines) the LW CRE.  
-Over the SST maximum, E25 has a surface enthalpy flux that is 
-60 W/m2 larger than that of the E1 experiment, and the E1 experiment has a very irregular pattern of enthalpy flux in the middle
-half of the domain.  It appears that these differences in magnitude and regularity are due to the differing low-level 
-wind speeds among 
-the three experiments.  The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere.  
-This is consistent with the 
-strong asymmetries of the P25 experiment being connected to a large domain mean wind shear in that experiment.  
-It is also worth noting that the E1 experiment has a stronger domain mean u wind shear compared 
-with the E2 and E25 experiments.  Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
-enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
-This decreased enthalpy flux also corresponds to an increased amount of specific humidity in the lowest atmospheric 
-model level.
-
+without (thin lines) the LWCRE.  Over the SST maximum, E25 has a surface enthalpy flux that is $60 \, \rm{W/m^2}$ 
+larger than that of the E1 experiment, and the E1 experiment has an irregular pattern of enthalpy flux in the middle
+half of the domain.  These differences in magnitude and regularity are apparently due to differences in the low-level 
+wind speeds among the experiments.  When the LWCRE is off, the difference in the enthalpy flux between E25 and E2/E1 
+over the warmest SSTs is reduced from $60 \, \rm{W/m^2}$ to about $20 \, \rm{W/m^2}$ and the enthalpy
+flux for E1and E2 become very similar over the warmest SSTs.  This implies that the interactions between clouds
+and the longwave radiation have a massive influence on the surface energy budget even for the case of prescribed
+SSTs with no land.     
+%The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere.  
+%This is consistent with the strong asymmetries of the P25 experiment being connected to a large domain 
+%mean wind shear in that experiment.
+
+It is also interesting to note that despite stronger low-level winds, E25, E2, and E1 all have a weaker surface
+enthalpy flux when the clouds and radiation are interactive.  This is initially surprising because as represented 
+by bulk parameterizations, both the sensible heat flux and the latent heat flux are directly proportional to the 
+magnitude of a measure of the low-level wind.  However, the sensible and latent heat fluxes are also 
+proportional to the gradient of moisture and temperature between the surface and lowest atmospheric 
+level.    
+%Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
+%enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
+E25, E2, and E1 all show an increased amount of specific humidity (not shown) in the lowest atmospheric 
+model level that is reflected in the equivalent potential temperature (Figure \ref{fig:enthalpy}, top right).  This 
+implies that the gradient of moisture and temperature is smaller when the LWCRE is active and thus accounts 
+for the lower surface enthalpy flux relative to when LWCRE is off.         
+It is also worth noting that in contrast to the P25 case which has strong domain mean shear, E25 has less domain 
+mean u wind shear then E1.
+
+%This manifestation of the strong interactions between clouds and the circulation 
+%would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
+
+We now turn our attention to the clouds in the regions of subsidence over the cooler SSTs.
 Figure \ref{fig:cf_tdtlw} shows E2 to have the largest (about 17\%) upper level mean cloud
 fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
-P100, E25, and P25 (3-5\%).   Less upper level clouds will allow more radiative cooling of the atmosphere and 
-require a correspondingly larger amount of condensational heating and precipitation.
-
-%\begin{figure}
-%  \centering
-%       %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_6pan_25vs2vs1_lwoff_lwon.eps}
-%       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_3pan_25vs2vs1_lwoff_lwon_draft.eps}
-%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments with the 
-%  longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed for the experiments 
-%  having a domain width of 4000 km while the bottom panels are for experiments having a domain width of 16000 km.  The 
-%  black curves show a Gaussian function with a standard deviation computed for each experiment and an expected location 
-%  in the center of the domain where the SST is warmest. }
-%\end{figure}
+P100, E25, and P25 (3-5\%).  As noted in the discussion about the total condensate, the CRM-like models 
+produce large values of upper-level cloud with minimal low-level clouds while the GCM-like models
+do the opposite with large amounts of low-level clouds and 5\% or less of upper level-couds.   
+While the large difference among the upper-level clouds only slightly shifts the radiative cooling in the
+upper troposphere, there is a strong change of the radiative cooling around 900 hPa where the 
+differences in low-level clouds occur.  
+%Less upper level clouds will allow more radiative cooling of the atmosphere and 
+%require a correspondingly larger amount of condensational heating and precipitation.
 
@@
   \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
-  subsidence regions and are shown for the control (LWCRE on) and LWCRE off experiments.}
+  subsidence regions and are shown for the control (LWCRE-on) and LWCRE-off experiments.}
   \label{fig:cf_tdtlw}
@@
 emits more radiation to space, as evidenced by larger values of $\overline{\rm{OLR}}$ 
-for all experiments when the LWCRE is
-off.  Atmospheric radiative cooling can be thought of as a proxy for the mean precipitation 
-because the cooling is balanced primarily by condensational heating.  Larger values of 
-$\overline{\rm{OLR}}$ would correspond to larger values of $\overline{\rm{P}}$.  
-This is clearly not the case 
-for the E25, P25, and P100 cases.   \textit{The domain mean precipitation rates decrease despite
-an increased amount of atmospheric cooling.}  The implication is that the requisite atmospheric 
-heating must come from a process other than condensation.
-
-The solution lies in the energy budget of the surface.  
-A fixed SST means that the upward flux of longwave energy
-is constant.  The upward flux of sensible heat flux will be mostly fixed (barring variations in surface
+for all experiments when the LWCRE is off.  Atmospheric radiative cooling can be thought of 
+as a proxy for the mean precipitation because the cooling is balanced primarily by 
+condensational heating.  Larger values of $\overline{\rm{OLR}}$ would correspond to 
+larger values of $\overline{\rm{P}}$.  This is clearly not the case for the E25, P25, and 
+P100 cases.   \textit{The domain mean precipitation rates decrease despite an increased 
+amount of atmospheric cooling.}  The implication is that the requisite atmospheric heating 
+must come from a process other than condensation.
+
+The solution lies in the energy budget of the surface.  Prescribed SST means that the upward flux of 
+longwave radiation is constant.  The upward flux of sensible heat flux will be mostly fixed 
+(barring variations in surface
 wind) because changes in the downward flux of solar radiation will not warm the surface.  
@@
 experiments strongly influences the net flux of longwave energy at the surface. 
-Low-level clouds normally serve as a significant source of longwave radiative cooling 
-for the atmosphere.  Making these clouds invisible to radiation creates a source of 
-effective atmospheric warming.  
+Low-level clouds serve as a significant source of longwave radiative cooling 
+for the atmosphere (Figure \ref{fig:cf_tdtlw}).  Making these clouds invisible to radiation creates 
+a source of effective atmospheric warming.  
 %(does the downwelling longwave
@@
 the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off and thus there is less need for 
-condensational heating.  The mean precipitation rate actually decreases.  
+condensational heating and the mean precipitation rate actually decreases.  
 The large decrease of low-level clouds also leads to an increase of downward shortwave 
@@
 Larger values of ice condensate and upper-level cloud fraction as seen in the E2 and E1 experiment 
-(Figure \ref{fig:TotCond}) 
-therefore imply a larger atmospheric heating due to the CRE relative to the E25, P25, and P100 
-experiments in which have fewer clouds aloft (Figures \ref{fig:TotCond} and \ref{fig:TotCond_P25P100}).  
-When the warming effect of the upper level clouds 
-in the E1 and E2 experiments is removed in the LWCRE off experiments the energy balance of the atmosphere 
-must be maintained through an increase of latent heating and subsequent increase of precipitation.  This is 
-reflected in Table 2.
+(Figure \ref{fig:TotCond}) therefore imply a larger atmospheric heating due to the CRE relative to the 
+E25, P25, and P100 experiments in which have fewer clouds aloft (Figures \ref{fig:TotCond}, 
+\ref{fig:TotCond_P25P100}, and \ref{fig:cf_tdtlw}).  When the warming effect of the upper level clouds 
+in the E1 and E2 experiments is removed in the LWCRE off experiments the energy balance of 
+the atmosphere must be maintained through an increase of latent heating and subsequent increase 
+of precipitation.  This is reflected in Table 2.
 
 These experiments provide insight into the different mechanisms by which the clouds in GCMs and CRMs
-interact with longwave radiation in the atmosphere.  Because there are so many more low-level clouds in 
+interact with longwave radiation in the atmosphere.
+
+Because there are so many more low-level clouds in 
 the GCM-like experiments we see a strong response to upwelling radiation from the surface.  In contrast, 
-the abundance of upper-level ice condensate, and lack of low-level condensate in the CRM-like 
-experiments results in the primary interaction
-between clouds and radiation being in the atmosphere below the upper level clouds.
-
-%The decrease of precipitation for LWCRE off experiments for the P25 and P100 experiments
-%is harder to explain because there is much less upper level cloud to influence the mid-tropospheric heating.  
-%However, the low-level clouds of the P25 and P100 experiments are dramatically reduced when the LWCRE is off.  
+the abundance of upper-level ice condensate, and lack of low-level condensate in the CRM-like experiments 
+results in the primary interaction between clouds and radiation being in the atmosphere below the upper level clouds.
+
 %
@@
 
-%This implies (is this connected to previous sentence?) there will be less atmospheric heating from 
-%longwave radiation (but doesn't LW just cool the atmosphere?) and a corresponding 
-%larger heating due to condensational heating which is consistent with higher values 
-%of domain mean precipitation for E25, P25, and P100 compared to E2 and E1.
-
 %Similarly, the E2 experiment has lower values 
@@
 
-Water vapor is an efficient emitter of long-wave radiation and thus greatly facilitates the cooling of the troposphere.  
-Popp and Silvers, 2017 showed that there is dramatically less condensate in the atmosphere and much less precipitation 
-(at the equator) 
-for LW CRE off experiments (see their figure 1a,b).  Our results here for the E25, P25, and P100 are consistent with 
-those of Popp and Silvers, 2017 because the low-level condensate are strongly decreased when the LWCRE is off.  
+Water vapor is an efficient emitter of longwave radiation and thus greatly facilitates the cooling of the troposphere.  
+\citeA{Popp2017} showed that there is dramatically less condensate in the atmosphere and much less precipitation 
+(at the equator) for LW CRE off experiments (see their figure 1a,b).  Our results here for the E25, P25, and P100 
+are consistent with those of \citeA{Popp2017} because the low-level condensate are strongly decreased 
+when the LWCRE is off.  
 %This is not the case for E2 and E1.  Those experiments have little low-level condensate to begin with 
@@
 
-\begin{figure}
-  \centering
-    \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
-    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
-    For all panels, thick lines show control experiments with the LW CRE on, thin lines show experiments
-    with the LW CRE off.}
-    \label{fig:enthalpy}
-\end{figure}
-
-We can see clearly that the interactions between longwave radiation and clouds act to dry the troposphere in the regions of subsidence 
-more than the cases when the longwave CRE is not active.  This is especially true for the simulations with a grid-spacing of 1 km 
-and 2 km.  While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, 
+The upper panels of Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show that the 
+interactions between longwave radiation and clouds enhance
+the drying of the troposphere in regions 
+of subsidence more than the cases when the longwave CRE is not active.  This is especially true for the 
+simulations with a grid-spacing of 1 km and 2 km.  While the mid-tropospheric profiles of diabatic 
+heating and cooling are similar between the LW CRE on/off simulations, 
 there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the 
@@
 and a radiative cooling of around -7K/day.   However, when the LW CRE is off, there is no appreciable 
-difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It 
-is also clearly seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 
-experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure 
-\ref{fig:TotCond}).
-
-When the LW CRE is off, the simulations with resolutions of 1km, 2km, and 25km all show a similar 
-distribution and magnitude of surface enthalpy flux (Figure \ref{fig:LowLevelVars}).  However, when the 
-LW CRE is on, there are differences between the resolutions that can be as large as $80 \, \rm{W/
-m^2}$.   These differences in surface enthalpy flux are due largely to the latent heat flux and are 
-confined to the regions with ascending circulations over the warmer SST.  This manifestation of the strong interactions between clouds and the circulation 
-would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
+difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It is also clearly 
+seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 experiments but 
+dramatically increases the low-level liquid condensate for E25 and P25 (Figure \ref{fig:TotCond}).
 

### 2019-11-08 Silvers_WalkerCell.tex
changes to the conclusions and the section on resolution dependence

@@
 (Figure \ref{fig:TotCond}) therefore imply a larger atmospheric heating due to the CRE relative to the 
-E25, P25, and P100 experiments in which have fewer clouds aloft (Figures \ref{fig:TotCond}, 
+E25, P25, and P100 experiments in which there are fewer clouds aloft (Figures \ref{fig:TotCond}, 
 \ref{fig:TotCond_P25P100}, and \ref{fig:cf_tdtlw}).  When the warming effect of the upper level clouds 
@@
 the atmosphere must be maintained through an increase of latent heating and subsequent increase 
-of precipitation.  This is reflected in Table 2.
+of precipitation as reflected in Table 2.
 
@@
 (at the equator) for LW CRE off experiments (see their figure 1a,b).  Our results here for the E25, P25, and P100 
-are consistent with those of \citeA{Popp2017} because the low-level condensate are strongly decreased 
+are consistent with those of \citeA{Popp2017} because the low-level condensate is strongly decreased 
 when the LWCRE is off.  
@@
 interactions between longwave radiation and clouds enhance
-the drying of the troposphere in regions 
-of subsidence more than the cases when the longwave CRE is not active.  This is especially true for the 
-simulations with a grid-spacing of 1 km and 2 km.  While the mid-tropospheric profiles of diabatic 
-heating and cooling are similar between the LW CRE on/off simulations, 
-there is a very strong response below about 850 hPa for the 25km model.  At that grid-spacing, with the 
-LW CRE on, significant low-level clouds are formed, leading to a radiative cooling of almost 10K/day, 
-and a radiative cooling of around -7K/day.   However, when the LW CRE is off, there is no appreciable 
-difference in the low-level diabatic profiles among the E25, E2, and E1 experiments.   It is also clearly 
-seen that the LW CRE decreases the upper-level ice-condensate for E25, E2, and E1 experiments but 
-dramatically increases the low-level liquid condensate for E25 and P25 (Figure \ref{fig:TotCond}).
+the drying of the troposphere in regions of subsidence more than the cases when the longwave CRE is not active.  
+This is especially true for the simulations with a grid-spacing of 1 km and 2 km.  While the mid-tropospheric 
+profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, there is a very strong 
+response below about 850 hPa for the 25km and 100km models.  At that grid-spacing, with the LW CRE on, significant low-level 
+clouds are formed, leading to a radiative cooling on the order of -10K/day.   
+However, when the LW CRE is off, there is little appreciable difference in the low-level diabatic profiles among the 
+P100, P25, E25, E2, and E1 experiments.   It is also clearly seen that the LW CRE decreases the upper-level ice-condensate 
+for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and 
+P25 (Figure \ref{fig:TotCond}).
 
@@
 
-The results presented in this paper show us that (scientific point learned).    Interactions between the clouds and radiation
-act to spatially concentrate the circulation, strengthen the overturning circulation, and dry out the mid-troposphere where 
-subsidence dominates (although domain mean condensate is less when LWCRE is on.).
-
-It is remarkable that the control simulations (LW CRE on) have a precipitation rate  that can vary by as much as 
-20\% despite have have the same prescribed SST and incoming radiation.  The simulations also all have the same radiation,
+%The results presented in this paper show us that (scientific point learned).    Interactions between the clouds and radiation
+%act to spatially concentrate the circulation, strengthen the overturning circulation, and dry out the mid-troposphere where 
+%subsidence dominates (although domain mean condensate is less when LWCRE is on.).
+
+We have used the framework of the tropical overturning circulation to compare the multi-scale interactions between 
+circulation patterns, cloud systems, and interactive radiation across experiments with grid-spacing ranging from 
+1km to 100km.  The flexible modeling
+system at GFDL has allowed us to use a single code base in a GCM-like configuration with physics parameterizations 
+that are very close to the AM4.0/CM4.0 models as well as in a CRM-like configuration with explicit convection.  While 
+there are significant differences between the CRM presented in this paper and more conventional CRMs (e.g. vertical 
+grid spacing and threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
+like a CRM provides an enticing testbed for future model development.
+These comparisons have highlighted some of the unexpected behaviors of a GCM-like configuration when used with 
+idealized boundary conditions.  For example, the consistent asymmetry of the circulation and precipitation relative 
+to the fixed SST pattern and the dominance of the large-scale precipitation over the convective precipitation.  
+The comparisons have also illustrated some of the challenges that arise when dramatically increasing the resolution 
+of a GCM.  For example, the lack of shallow 
+clouds (both convective and stratocumulus) and the difficulty of comparing clouds in this CRM to other CRMs due to the 
+prognostic large-scale cloud scheme used at GFDL.
+
+%Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
+%large-scale circulation to a simple Gaussian shaped prescribed SST pattern.
+
+To better understand the role that clouds
+and humidity play in driving and responding to the circulation we have performed experiments with and without the radiative
+effect of clouds, with and without the deep convective parameterization, across multiple domain sizes and resolutions.  
+Our results show that the convective 
+parameterization and the longwave cloud radiative effect strongly interact with each other and often lead to 
+asymmetric results.
+
+It is remarkable that the control simulations (LWCRE on) have a precipitation rate  that can vary by as much as 
+20\% despite have have the same prescribed SST and incoming radiation.  All simulations have the same radiation,
 turbulence, large-scale cloud and microphysics parameterizations and all use the same dynamical core.
@@
 We were struck by three particular changes due strictly do a 4-fold increase in domain width.
-A dramatic widening of the precipitation distribution when the LW CRE is off, a shifting of low level clouds upward by more than 100 hPa, and
-a strong dependence of the quantity of precipitation produced by the large-scale scheme on the LW CRE.
-
-The longwave cloud radiative effect (LWCRE) has been shown to play a dramatic role in the organization of the precipitation
-field and the low-level clouds.  This is primarily accomplished by decreasing the amount of precipitation that is produced 
-by the large-scale precipitation scheme.  Two major differences between the GCM-like experiments and the CRM-like 
-experiments are 4-5 times more low-level clouds and a much dryer mid-troposphere in the GCM-like experiments compared 
-to the CRM-like experiments.  The LWCRE also highlights the impact of an increased vertical moisture transport 
+A dramatic widening of the precipitation distribution when the LWCRE is off, a shifting of low level clouds upward by more than 100 hPa, and
+a strong dependence of the quantity of precipitation produced by the large-scale scheme on the LWCRE.   
+The LWCRE also highlights the impact of an increased vertical moisture transport 
 in our CRM-like models.
 
-Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
-large-scale circulation to a simple Gaussian shaped prescribed SST pattern.  To better understand the role that clouds
-and humidity play in determining and driving the circulation we have performed experiments with and without the radiative
-effect of clouds, with and without the deep convective parameterization, across multiple domain sizes,  
-and using a range of resolutions from 100 km to 1 km grid-spacing.  Our results imply that the convective 
-parameterization and the longwave cloud radiative effect strongly interact with each and often lead to 
-asymmetric results.
-
-Below is a list summarizing several of the changes that occur when the LW CRE is off.  Turning the LW CRE interactions off tends to:
+%The longwave cloud radiative effect (LWCRE) has been shown to play a dramatic role in the organization of the precipitation
+%field and the low-level clouds.  
+%%This is primarily accomplished by decreasing the amount of precipitation that is produced 
+%%by the large-scale precipitation scheme.  
+%Two major differences between the GCM-like experiments and the CRM-like 
+%experiments are 4-5 times more low-level clouds and a much dryer mid-troposphere in the GCM-like experiments compared 
+%to the CRM-like experiments.  The LWCRE also highlights the impact of an increased vertical moisture transport 
+%in our CRM-like models.
+
+Below is a list summarizing several of the changes that occur when the LWCRE is turned off.  Turning the LWCRE 
+interactions off tends to:
 
@@
   \item increase the midtropospheric RH by $5-15 \% $
-  \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
+ % \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
   \item weaken the horizontally oriented low-level circulations.   
@@
 \begin{itemize}
-  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered over the maximum of SST.  
-  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models can have a relative humidity 
+  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered 
+  over the maximum of SST.  
+  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models 
+  can have a relative humidity 
   that is 40\% higher than in the parameterized, lower resolution simulations.  
@@
   simulations are 10-20\% higher (3.5-3.9 mm/d).  
-  \item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
+  %\item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
   %\item much less vertical shear.  
@@
 work has looked at the Walker circulation, it has received less attention.  Part of our motivation in using the framework of the 
-Walker circulation comes from the fact that all of the major types of tropical cloud types occur regularly within this circulation
-clouds and the circulation.  While this study has interpreted the experiments in the context of the Walker Circulation, our results 
-are also relevant to the deep overturning circulations and meridional SST gradients that define the ITCZ and the Hadley 
-Circulation.  In that context, our results are consistent with those of several recent studies (e.g. Harrop and Hartmann, 2016, 
+Walker circulation comes from the fact that all of the major types of tropical clouds occur regularly within the region 
+identified with the Walker circulation.  While this study has interpreted the experiments in the context of the Walker 
+Circulation, our results are also relevant to the deep overturning circulations and meridional SST gradients that define 
+the ITCZ and the Hadley Circulation.  In that context, our results are consistent with those of several recent studies 
+(e.g. Harrop and Hartmann, 2016, 
 Popp and Silvers, 2017, Dixit et al. 2018, Flaschner et al. 2018).  These studies, as well as the present one, all show that the 
@@
 these papers, the present work also shows that the LWCRE has a strong influence on the low-level circulation.   When 
-the LWCRE is turned off, the low-level circulations shift upward and are not as well organized (reference psi figures).
+the LWCRE is turned off, the low-level circulations shift upward and are not as well organized (see Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
 There is a corresponding change in the low-level cloud fields, longwave radiative cooling, and the domain mean precipitation.
@@
 Because we expect the fraction of precipitation that is due to the convective parameterization to be model dependent 
-this could explain why GCMs have a large spread in their response to turning off the LWCRE (reference some 
-of Aiko's work?).
-
-We have used the tropical overturning circulation to compare the multi-scale interactions between circulation patterns, cloud 
-systems, and interactive radiation across experiments with grid-spacing ranging from 100km to 1km.  The flexible modeling
-system at GFDL has allowed us to use a single code base in a GCM-like configuration with physics parameterizations 
-that are very close to the AM4.0/CM4.0 models as well as in a CRM-like configuration with explicit convection.  While 
-there are significant differences between the CRM presented in this paper and more conventional CRMs (e.g. vertical 
-grid spacing and threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
-like a CRM allows for an enticing testbed for future model development.
-These comparisons have highlighted some of the unexpected behaviors of a GCM-like configuration when used with 
-highly idealized boundary conditions.  For example, the consistent asymmetry of the circulation and precipitation relative 
-to the fixed SST pattern and the dominance of the large-scale precipitation over the convective precipitation.  
-The comparisons have also illustrated some 
-of the challenges that arise when dramatically increasing the resolution of a GCM.  For example, the lack of shallow 
-clouds (both convective and stratocumulus) and the difficulty of comparing clouds in this CRM to other CRMs due to the 
-prognostic large-scale cloud scheme used at GFDL.
-
-The goal in developing and using idealized models is to capitalize on their simplicity and learn something about the 
-parent system as a result.  Idealized studies focusing on particular parts of the Earth system have shown that the danger of 
-such idealized models is that they will not actually be less complex or easier to understand than the Earth system.
+this could explain why GCMs have a large spread in their response to turning off the LWCRE (Aiko's work?).
 
 The only difference between our simulations and radiative convective equilibrium is a gradient of SST at the lower boundary.
-The addition of this small difference creates an undeniable link with the observed tropical atmosphere.  The idealized 
+The addition of this small difference creates a concrete link with the observed tropical atmosphere.  The idealized 
 mock -Walker cell configuration serves as an important step between models of pure radiative convective equilibrium
-and models which are applicable to a wider range of Earth like conditions.
-
-Although the radiative cooling and condensational heating
- are in many ways similar...   The 1 and 2 \textit{km} experiments transport much more condensate aloft and maintain a 
- relative humidity over the warm pool region that is about 40\% higher than the experiments with parameterized convection.
+and models which are applicable to a wider range of Earth like conditions.   The goal in developing and using idealized models is to capitalize on their simplicity and learn something about the 
+parent system as a result.  Idealized studies focusing on particular aspects of the Earth system have shown that a 
+real danger of idealized models is that they will not actually be easier to understand than the Earth system.
+
+What are we to conclude from this array of results?  Our CRMs succeed (by construction) at representing a far more 
+realistic range of turbulent motions and thus presumably do a better job of explicit mixing compared to the GCM-like 
+configurations.  However, the increase in resolved scales comes at the cost of most of the low-level clouds (\textit{what is 
+the observed cloud fraction in the tropical Pacific below 700 hPa?}).  The GCM-like simulations match the CRM-like 
+simulations  in the general two celled structure of the overturning circulation and the approximate distribution of condensate.  
+While the GCM-like simulations succeed at producing 20-30\% low-level cloud fraction they produce very little upper-level 
+clouds and the distribution of the precipitation is erratic and dependent on interactions between the convective 
+parameterization and the interactions between longwave radiation and clouds.  The solutions of the GCM-like simulations 
+also have a large dependence on the size of the domain.  Larger domains have more precipitation and domain mean 
+cloud profiles shift upward by more than 100 hPa.  The amount of precipitation, and the structure of the precipitation and clouds 
+is heavily dependent on the interaction between clouds and the longwave radiation.  This dependence strongly mediates
+the large-scale cloud parameterization, rather than the convective parameterization.  The longwave cloud radiative 
+effect acts to concentrate the regions of precipitation and increases the domain mean value.
+
+We have learned that for high resolution models with explicit convection the upper-level clouds dominate the impact
+of interactions between clouds and radiation while for GCM-like simulations it is the low-level clouds that dominate
+this impact.
+
+%The domain mean precipitable water is higher (as is P) when the LWCRE is on.   What does this imply?  Precipitation 
+%efficiency or mixing?  The total water is PW plus condensates right?  So the Precipitation efficiency would only speak
+%to the condensed part I think.
 
@@
 %
-%Bretherton et al. 2006
-%Jeevanjee et al. 2018
+
 %Kuang and Wofsy
-%Muller and Held, 2012
-%Popp and Silvers, 2017
-%Patrizio and Randall, 2019
+
 %Randall et al., 1989
-%Silvers et al. 2016
 %Slingo and Slingo, 1988
 %Stevens et al. 2012
-%Zhao et al. 2018a
-%Zhao et al. 2018b
-
-% PDF for location of precip maximum of precipitation for experiments at both 25km and 100km resolutions 
-% LW CRE on
-%\begin{figure}
-%  \centering
-%      %\includegraphics[width=0.96\columnwidth]{walkerfigs/hist_maxP_4mods_lwcreon.eps}
-%       \includegraphics[width=0.96\columnwidth]{walkerfigs/hist_4pan_25vs100_lwcre.eps}
-%  \caption{Normalized probability distributions of the location of the maximum value of precipitation for experiments 
-%  with the longwave CRE on.  All panels show cases with parameterized convection, the top panels are computed 
-%  for the experiments having a domain width of 4000 km while the bottom panels are for experiments having a 
-%  domain width of 16000 km.  The black curves show a Gaussian function with a standard deviation computed for 
-%  each experiment and an expected location in the center of the domain where the SST is warmest. }
-%\end{figure}
 

### 2019-11-08 Silvers_WalkerCell.tex
more text changes, mostly trying to make a bit shorter before sending it to Nadir and Tom

@@
   \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
-  region that is 30\% higher than for the coarser cases with parameterized convection.}
+  region that is 40\% higher than for the coarser cases with parameterized convection.}
   \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
@@
 connected by a large-scale circulation.  
-We analyze this circulation with high-resolution 
-and coarse resolution simulations and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
-thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the Earth's sensitivity to 
-changes in greenhouse gas concentrations.
-
-A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
-resolution (25km, 100km) configured 
-as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
-derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
-dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
-some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
+We analyze an idealization of this circulation with high-resolution 
+and coarse resolution simulations. 
+%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
+%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
+%%Earth's sensitivity to 
+%%changes in greenhouse gas concentrations.
+%
+%A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
+%resolution (25km, 100km) configured 
+%as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
+%derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
+%dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
+%some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
 
 \end{abstract}
-
-%\section{Key Questions}
 
@@
 %capability to better quantify and understand the connection between tropical convective heating and changes in low clouds.
-\textbf{Paragraphs of Introduction}
-\begin{itemize}
-  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
-  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
-  extensively studies (review paper?).  The circulation first 
-  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
-  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
-  subtropics, stratocumulus clouds.  This circulation has come to be 
-  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
-  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
-  observations (Walker, Bjerknes), theory (Geisler, 1981), 
-  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
-  modeling studies have compared theoretical models with cloud
-  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
-  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
-  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
- Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
- the thermodynamic arguments of Kloesel and Albrecht (1989) 
-  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
-  \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
-  circulations.  Previous studies of RCE have proven to be a 
-  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
-  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
-  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
-  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
-  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
-  a forced compositing of the data  
-  \cite{Bretherton2005, Muller2012}.}
-  \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
-  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
-  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
-  this methodology for unifying our understanding.}
-\end{itemize}
+
+%\textbf{Paragraphs of Introduction}
+%\begin{itemize}
+%  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
+%  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
+%  extensively studies (review paper?).  The circulation first 
+%  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
+%  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
+%  subtropics, stratocumulus clouds.  This circulation has come to be 
+%  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
+%  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
+%  observations (Walker, Bjerknes), theory (Geisler, 1981), 
+%  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
+%  modeling studies have compared theoretical models with cloud
+%  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
+%  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
+%  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
+% Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
+% the thermodynamic arguments of Kloesel and Albrecht (1989) 
+%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
+%  \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
+%  circulations.  Previous studies of RCE have proven to be a 
+%  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
+%  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
+%  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
+%  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
+%  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
+%  a forced compositing of the data  
+%  \cite{Bretherton2005, Muller2012}.}
+%  \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
+%  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
+%  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
+%  this methodology for unifying our understanding.}
+%\end{itemize}
 
@@
 
-\appendix
-
-%A couple of appendices with extra details which may not be included in the final paper.
-
-\section{Streamfunction}
-
-For a two-dimensional flow in the $\lambda,p$ plane we can write the mass conservation equation in terms of a 
-mass streamfunction $\psi$ as: 
-\begin{equation}
-u =  -\frac{\partial \psi}{\partial p}   \,\, {\rm and} \,\, \omega =\frac{\partial \psi}{a \rm{cos} \phi \partial \lambda}
-\end{equation}
-with $a$ as the radius of Earth.
-This satisfies the continuity equation: 
-\begin{equation}
-\frac{\partial}{a \rm{cos} \phi\partial\lambda}\left(-\frac{\partial \psi}{\partial p}\right)+\frac{\partial}{\partial p}\left(\frac{\partial \psi}{a \rm{cos}\phi \partial \lambda}\right)=0.
-\end{equation}
-The streamfunction is therefore defined by two equations and can be solved with either.  The choice is often made based on the 
-boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $\rm{kg/s^3}$.  Often, the streamfunction
-is computed as a mass streamfunction with units of $\rm{kg/s}$.  Density does not appear above
-because pressure is being used as the vertical coordinate.   With height as the vertical coordinate, mass is given by $\rho dxdydz$, 
-assuming a hydrostatic atmosphere and rewriting in terms of pressure mass is given by $-(1/g) dxdydp$.
-Scaling the equations above by $a/g$ results in $\psi$ having units of $\rm{kg/s}$.
-
-Solving for $\psi$ by integrating the vertical velocity is possible, but requires a boundary condition along one edge of the domain between the surface and the 
-top of the atmosphere.  Solving for $\psi$ by integrating the horizontal velocity allows us to set $\psi=0$ along the upper edge of the domain.  
-This is both simple, and physically motivated.
-
-% computed with matlab, see StreamFunNew.m script
-\begin{equation}
-\psi_{i,j+1}= \psi_{i,j}-\frac{a}{g}\sum_{j=32}^1 \left(u_{i,j+1}(p_{j+1}-p_{j})\right).
-\end{equation}
-
-In the previous equation, $w, u,$ and $\rho$ have all been averaged in space and time and $p$ is the pressure on full model levels.  The 
-radius of Earth is $a$ and the acceleration due to gravity by $g$.
+%\appendix
+%
+%%A couple of appendices with extra details which may not be included in the final paper.  
+%
+%\section{Streamfunction}
+%
+%For a two-dimensional flow in the $\lambda,p$ plane we can write the mass conservation equation in terms of a 
+%mass streamfunction $\psi$ as: 
+%\begin{equation}
+%u =  -\frac{\partial \psi}{\partial p}   \,\, {\rm and} \,\, \omega =\frac{\partial \psi}{a \rm{cos} \phi \partial \lambda}
+%\end{equation}
+%with $a$ as the radius of Earth.
+%This satisfies the continuity equation: 
+%\begin{equation}
+%\frac{\partial}{a \rm{cos} \phi\partial\lambda}\left(-\frac{\partial \psi}{\partial p}\right)+\frac{\partial}{\partial p}\left(\frac{\partial \psi}{a \rm{cos}\phi \partial \lambda}\right)=0.
+%\end{equation}
+%The streamfunction is therefore defined by two equations and can be solved with either.  The choice is often made based on the 
+%boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $\rm{kg/s^3}$.  Often, the streamfunction
+%is computed as a mass streamfunction with units of $\rm{kg/s}$.  Density does not appear above
+%because pressure is being used as the vertical coordinate.   With height as the vertical coordinate, mass is given by $\rho dxdydz$, 
+%assuming a hydrostatic atmosphere and rewriting in terms of pressure mass is given by $-(1/g) dxdydp$.
+%Scaling the equations above by $a/g$ results in $\psi$ having units of $\rm{kg/s}$.  
+%
+%Solving for $\psi$ by integrating the vertical velocity is possible, but requires a boundary condition along one edge of the domain between the surface and the 
+%top of the atmosphere.  Solving for $\psi$ by integrating the horizontal velocity allows us to set $\psi=0$ along the upper edge of the domain.  
+%This is both simple, and physically motivated.
+
+%% computed with matlab, see StreamFunNew.m script
+%\begin{equation}
+%\psi_{i,j+1}= \psi_{i,j}-\frac{a}{g}\sum_{j=32}^1 \left(u_{i,j+1}(p_{j+1}-p_{j})\right).
+%\end{equation}
+%
+%In the previous equation, $w, u,$ and $\rho$ have all been averaged in space and time and $p$ is the pressure on full model levels.  The 
+%radius of Earth is $a$ and the acceleration due to gravity by $g$.
 The density, $\rho$ is computed as $ \rho_{i,j}=\frac{p_j}{R T_{v;i,j}}  $  where $R$ and $T_v$ are the gas constant for dry air ($287 \rm{J/kg K}$) and the virtual temperature ($T_v=T(1+q/\epsilon)/(1+q)$), respectively.
 The specific humidity is given by $q$ and $\epsilon = 0.622$.
-
-\section{Cloud Water and Cloud Fraction}
-
-The last several generations of the GFDL atmospheric models have used the parameterization developed by Tiedtke (1993) to prognostically compute the grid-cell averaged cloud water ($l$) and cloud fraction ($a$).
+%
+%
+%\section{Cloud Water and Cloud Fraction}
+%
+%The last several generations of the GFDL atmospheric models have used the parameterization developed by Tiedtke (1993) to prognostically compute the grid-cell averaged cloud water ($l$) and cloud fraction ($a$).
 The formulation for the local time rate of change from Tiedtke is
-\begin{equation}
-  \frac{\partial l}{\partial t} = A(l)+S_{cv}+S_{BL}+C-E-G_{p}-\frac{1}{\rho}\frac{\partial}{\partial z}(\rho\overline{w'l'})_{entr}
-\end{equation}
-and 
-\begin{equation}
-  \frac{\partial a}{\partial t} = A(a)+S(a)_{cv}+S(a)_{BL}+S(a)_C-D(a).
-\end{equation}
-Transport of $l$ or $a$ through the boundaries of a grid is given by $A(l)$ or $A(a)$, the terms ($S_{cv}, S(a)_{cv}, S_{BL}, S(a)_{BL}$, and $S(a)_C$) are the sources of cloud water or cloud fraction from convection, boundary layer turbulence, and condensation, respectively.
+%\begin{equation}
+%  \frac{\partial l}{\partial t} = A(l)+S_{cv}+S_{BL}+C-E-G_{p}-\frac{1}{\rho}\frac{\partial}{\partial z}(\rho\overline{w'l'})_{entr}
+%\end{equation}
+%and 
+%\begin{equation}
+%  \frac{\partial a}{\partial t} = A(a)+S(a)_{cv}+S(a)_{BL}+S(a)_C-D(a).
+%\end{equation}
+%Transport of $l$ or $a$ through the boundaries of a grid is given by $A(l)$ or $A(a)$, the terms ($S_{cv}, S(a)_{cv}, S_{BL}, S(a)_{BL}$, and $S(a)_C$) are the sources of cloud water or cloud fraction from convection, boundary layer turbulence, and condensation, respectively.
 The condensation/sublimation rate is given by $C$, $E$ is the evaporation of cloud water, $G_{p}$ is the rate of generation of precipitation by microphysical processes and the $\overline{w'l'}$ term is the flux divergence from entrainment at the top of the cloud layer, and lastly, $D(a)$ is the sink of cloud fraction due to evaporation.
-
-Often, cloud resolving models, or cloud system resolving models, do not predict partially cloudy grid cells, but rather consider a cell to be either cloudy or clear.
+%
+%Often, cloud resolving models, or cloud system resolving models, do not predict partially cloudy grid cells, but rather consider a cell to be either cloudy or clear.
 If the goal is to more directly compare to cloud resolving models then cloud fraction should not be prognostically predicted but simply tied to a certain value of total condensate in a grid-cell.
@@
 As given by equations 16, 24, 26,28, 30, and 33 in Tiedtke's paper, this dependence is present in the $S_{BL}$, $C$, $E$, and $G_{p}$ terms.
-
+%
 \acknowledgments

### 2019-11-12 Silvers_WalkerCell.tex
minor changes, mostly to add a reference or two.

@@
   subtropics, stratocumulus clouds.  This circulation has come to be 
-  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; Bretherton et al., 
+  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
+  \citeA{Raymond1994}; Bretherton et al., 
   2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory 
-  (Geisler, 1981), or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
+  (Geisler, 1981), or modeling studies (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
   Kuang, 2012)).  Some of these modeling studies have compared theoretical models with cloud

### 2019-11-12 Silvers_cfmip_draft.tex
added the HML_CF_cfmip_bias.eps figure and a brief description

@@
 
+\begin{figure}
+% figure generated with cloud_table_AM4fig.ncl
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/HML_CF_cfmip.eps}
+  \caption{Cloud fraction from several of the CMIP6 experiments.}
+  \label{fig:cf_hml_manyexps}
+\end{figure}
+
+\begin{figure}
+% figure generated with cloud_table_AM4fig.ncl
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/HML_CF_cfmip_bias.eps}
+  \caption{Cloud fraction from several of the CMIP6 experiments.}
+  \label{fig:cf_hml_bias}
+\end{figure}
+
+Plotting the cloud fields as a function of latitude and height highlights some of the similarities and differences 
+between the various experiments.  In general the clouds in the amip and historical simulations are similar to 
+each other, as we would expect.  The differences between the clouds of these experiments are due to the 
+different SST pattern that the two experiments have.  We can thus see how the clouds change as a result 
+of SST biases over the observational period.  Two warming experiments have been plotted, amip p4K and 
+the coupled abrupt 4xCO2 experiment.  The cloud fields in these experiments are similar to each other, with 
+the differences again likely coming from the different SST patterns that result from a fully coupled system.  The 
+cooling experiment is rather unique and tends to have cloud fraction changes in the opposite direction as 
+the warming experiments.
+
 % Beta feedback??  relavent?

### 2019-11-13 Silvers_WalkerCell.tex
minor changes, addition of Tiedtke reference

@@
 \title{Clouds and Radiation in a mock-Walker Circulation}
-\authors{Levi G. Silvers, Nadir Jeevanjee, and Thomas Robinson}
+\authors{Levi G. Silvers, and Thomas Robinson}
 
@@
 %  maximum.}
+  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant}
   \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
@@
 %\begin{itemize}
-%  \item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
+%\item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
 %  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
@@
 %  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
-%  \item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
+%\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
 %  circulations.  Previous studies of RCE have proven to be a 
@@
 %  \cite{Bretherton2005, Muller2012}.}
-%  \item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
+%\item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
 %  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
@@
 pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
-  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated by deep 
+  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is 
+  dominated by deep 
   convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
   subtropics, stratocumulus clouds.  This circulation has come to be 
-  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
+  known as the Walker Circulation and while receiving less attention than the Hadley circulation, there have been 
+  notable studies (e.g. Geisler, 1981; 
   \citeA{Raymond1994}; Bretherton et al., 
-  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations (Walker, Bjerknes), theory 
+  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations 
+  (Walker, Bjerknes), theory 
   (Geisler, 1981), or modeling studies (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
   Kuang, 2012)).  Some of these modeling studies have compared theoretical models with cloud
-  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker 
-  Circulation with simulations from a GCM used on a doubly periodic domain.
+  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations 
+  of the Walker Circulation with simulations from a GCM within a flexible dynamical framework that draws on the 
+  same code base for both models.
 
@@
 show both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
-we test the impact of convective parameterization, 
-longwave radiation interactions with clouds, domain size, 
-and the resolution, or grid-spacing.    Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
+we test the impact of convective parameterization, longwave radiation interactions with clouds, domain size, 
+and the resolution, or grid-spacing.  Elements of this study that distinguish it from previous research on the Walker 
+circulation are the use of fully interactive radiation, and the comparisons with a state-of-the-art general circulation
+model configuration.   Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
 size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
@@
 difference between the CRM simulations presented in this paper and those of more established CRMs such as SAM is that our model
-has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The Tiedtke (1993) 
+has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The \citeA{Tiedtke1993} 
 parameterization scheme for large-scale 
@@
 \acknowledgments
-Funding for this work came from both GFDL and Stony Brook.  Data and scripts are available from author upon request
+The authors thank Leo Donner, Nadir Jeevanjee, and Juho Iipponen for helpful discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
+Funding for this work came from both GFDL and Stony Brook.
+Data and scripts are available from author upon request
 

### 2019-11-13 Silvers_WalkerCell_nofigs.tex
this is just a version of the manuscript with no figures so that I can print it out without wasting as much paper

--- 2019-11-13 Silvers_WalkerCell.tex
@@
 \section{Introduction}
-
-%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.
-If an advance in our understanding of the role clouds play in our climate is desired, it is essential that we
-%learn to model the two way interaction between clouds and the circulation.
-The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation (imp of lwcre off).
-%Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation connects regions of deep convective activity with the prevalent tropical shallow 
-%convection and the radiatively critical stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and the Coriolis force is 
-%critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we propose that all of the physics of importance to our particular questions are present 
-%in the equatorial manifestation of the Walker circulation (perhaps better in conclusion).  
-%
-%Current computing capabilities cannot come close to resolving all of the spatial scales which are important in the lifetime of clouds.  
-%As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
-%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be informed by the solution of the high resolution model.
-This approach will help to demonstrate that the influence of clouds on climate is not an intractable problem.
-%
-%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between radiation and clouds, as well as dynamical motions which range from
-%sub-kilometer scales to roughly 10,000 km.
-In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and stratocumulus clouds, the tropical
-%Pacific provides an ideal physical context with which to explore the sensitivities and strengths of theoretical models, high-resolution models and general circulation models.  
-%The tropical system in the Pacific Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface temperature gradients 
-%represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic circulations.
-%This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation and how the nonlinear interactions within the system contribute 
-%to the cloud feedbacks to perturbations and the overall sensitivity of the system to anthropogenic forcing.
-%
-%Several studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012) have examined a 
-%mock Walker circulation in the context of cloud resolving 
-%simulations, or idealized theoretical models.   The comparison between CRMs and simple theory revealed several important 
-%similarities (like what? See Bretherton et al., 2006) and a multiplicity of differing results (like what) for different CRM studies. 
-%It thus remains unclear what GCM like models should be expected to produce in similar configurations.  
-%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
-%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
-%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
-%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
-%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
-%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
-%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified SST. (just before equation 8 of Bretherton et al. 2006)."
-
-%The atmosphere of Earth constantly radiates energy to space.
-This cooling of the atmosphere is mostly balanced by warming from the release of latent energy by convective clouds and precipitation.
-The details of this balance between cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.
-However, clouds contribute to both warming and cooling of the atmosphere.
-Deep convective storms and high clouds warm the atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the atmosphere by reflecting the incoming radiation from the sun.
-Previous research has repeatedly shown that low-level clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ concentration (Bony and Dufresne, 2005, Sherwood et al.
-2014).
-However, it has also been shown that the turbulent mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate sensitivity (Zhao, 2014).
-The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
-%
-%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and Emanual, 2014 have shown that idealized models are quite 
-%sensitive to the details of the configuration such as domain size and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
-%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the purpose of this paper is to use one modeling framework to
-%illustrate just what is obtained from a coarse GCM-like model run with idealized boundary conditions.  We then use this modeling framework to compare the results obtained from simulations
-%with a resolution of 100, 25, 2, and 1km.
-%
-%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system the idealization 
-%is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, as compared to the observed 
-%world.  These simulations are somewhere in the middle of those extremes.  We have decided to keep many of the complex elements of 
-%the global climate model  so that we can hopefully better understand the parent model (AM4.0) while learning something concrete about 
-%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke large-scale 
-%cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
-%model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
-%understanding and to illuminate some of the idiosyncrasies of the climate models that are currently looked to for information about the 
-%future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
-%a simple design that incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.
-%
-%Our simulations are based on the equatorial tropical Pacific.
-In the western Pacific warm sea surface temperatures exist beneath rising atmospheric motion and deep convective storms.
-In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low level, non-precipitation clouds with a very dry atmosphere above the clouds.
-These regions are connected by a large-scale circulation of winds.
-By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
-%
-%Inevitable limitations in computing power necessitate climate studies with Earth-system models to use relatively coarse grid-spacing.  
-%%Coarse, statistical Earth-system models which simulate long periods of the climate are necessitated by the limitations of current computers.  
-%This research uses a high-resolution cloud-resolving model on a limited spatial domain as a benchmark to compare with the same 
-%model at lower resolution configured as a fully 
-%parameterized general circulation model.   The modeling approach presented here, made unique by its clean connection between a global climate 
-%model and a regional cloud resolving model is  made possible by the flexible modeling system at GFDL.   The goal of this paper is to use this 
-%capability to better quantify and understand the connection between tropical convective heating and changes in low clouds.
-
-%\textbf{Paragraphs of Introduction}
-%\begin{itemize}
-%\item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
-%  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
-%  extensively studies (review paper?).  The circulation first 
-%  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
-%  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
-%  subtropics, stratocumulus clouds.  This circulation has come to be 
-%  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
-%  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
-%  observations (Walker, Bjerknes), theory (Geisler, 1981), 
-%  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
-%  modeling studies have compared theoretical models with cloud
-%  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
-%  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
-%  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
-% Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
-% the thermodynamic arguments of Kloesel and Albrecht (1989) 
-%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
-%\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
-%  circulations.  Previous studies of RCE have proven to be a 
-%  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
-%  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
-%  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
-%  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
-%  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
-%  a forced compositing of the data  
-%  \cite{Bretherton2005, Muller2012}.}
-%\item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
-%  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
-%  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
-%  this methodology for unifying our understanding.}
-%\end{itemize}
 
@@
 
-%%%%%
-% section 3.1 results
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan.eps}
-      \caption{Comparison of the steady state relative humidity (shading of top panels) and mass 
-      streamfunction (contours) for experiments
-      with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.  The lower panels 
-      show the total (liquid + ice) condensate (g/kg).  
-      An experiment with fully parameterized convection (P25) is on the left, the same 
-      experiment but with the LWCRE off is in the center panel, and the experiment with LWCRE on, but the convective
-      parameterization turned off is on the right (E25).  All three panels use the same contour interval for the mass 
-      streamfunction (kg/s).}
-  \label{fig:rh_psi_P25vsE25}
-\end{figure}
-
-%"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
-%double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
-%was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
-%vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
-%Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
-%turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
-%greater are being dominated by this second factor.
-
 The default experimental configuration includes radiation that is fully interactive with the clouds, water vapor, and 
@@
 that is driven entirely by the atmosphere.
-
-%\subsection{The Asymmetric Influence of Convective Parameterization and the organizing tendency of LWCRE}
-
-% LWCRE has a large impact on LS precip, not so much on convection
-% LWCRE has a large impact on the low-level circulation (circulation is stronger when LWCRE is on)
-% Are the low-level clouds a connecting point?
-
-% are the impacts of the LWCRE the same for GCMs as they are for CRMs?
-
-% Vertical Velocity and time averaged precipitation
-\begin{figure}
-  \centering
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
-  \caption{Precipitation (top) and vertical velocity (bottom) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
-  The data has been averaged over the short horizontal dimension of the channel and over the 
-  equilibrated part of the experiments.  Control configurations with normal model physics are on the 
-  left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
-  off (LWCRE-off).}
-  \label{fig:precip_vertvel}
-\end{figure}
-%
-% below shows that the circulation extremes decrease when the lw cre is switched off.  the case with a 
-% grid-spacing of 25 km shows the largest difference 
-%
-%% max/min values for the stream function with lwcre off:
-%(0)	max/min of psiplot ensind  is: 0.3477345977293868 and: -0.2115510906212598   diff = 0.56
-%(0)	max/min of psiplot1 is: 0.3195050101301776 and: -0.2795603759630235             diff = 0.60
-%(0)	max/min of psiplot2 is: 0.3551683771471268 and: -0.3245916357825396             diff = 0.68
-%
-%% max/min values for the stream function with lwcre on:
-%(0)	max/min of psiplot ensind  is: 0.1346705118433919 and: -0.6774837967222883    diff = 0.81
-%(0)	max/min of psiplot1 is: 0.301707822836468 and: -0.3661587052771586                diff = 0.67
-%(0)	max/min of psiplot2 is: 0.4634904466711686 and: -0.3170573366946793               diff = 0.78
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
-  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
-  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
-  while the P25 and P100 cases show only the first out of five years of the time series.}
-    \label{fig:precip_dom_mn}
-\end{figure}
 
@@
 pronounced.
-
-% new Hovmoller diagram
-\begin{figure}
-  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
-  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
-  25km and 100km.  From left, large domain 100km, (P100L); 
-  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
-  For each resolution, the only difference between the two experiments shown is a domain length of 
-  16,000 km or 4,000 km.}
-  \label{fig:domdep}
-\end{figure}
-
-\begin{figure}
-  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
-  \caption{Identical to previous figure, except that LW CRE is now off.  Evolution of precipitation through 
-  3 years of simulation.  From left, large domain 100km, (P100L); 
-  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
-  For each resolution, the only difference between the two experiments shown is a domain length of 
-  16,000 km or 4,000 km.}
-  \label{fig:domdep_lwoff}
-\end{figure}
-
-\begin{figure}
-  \centering
-       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice) for P100 (red) and P25 (yellow) on the domain 
-          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
-          and dashed lines experiments with LWCRE off.}
-  \label{fig:TotCond_P25P100}
-\end{figure}
 
@@
 
-% Fraction of Precip due to large-scale precip for large/small experiments with a 25km resolution
-\begin{figure}
-  \centering
-      \includegraphics[width=0.8\columnwidth]{walkerfigs/Conv_vs_LS_hist.eps}
-  \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective 
-  parameterization (black).  Experiments with the LW CRE off are shown with thin lines.  
-  Panels on the left show large domains with a width of 16000 km and
-  panels on the right show domains with a width of 4000 km.}
-  \label{fig:conv_vs_ls}
-\end{figure}
-
 Smaller domains were found to have a more focused ascent region and larger precipitation rates in B06.
@@
 
-%We hypothesize than an important difference between our simulations and previous studies which use GCMs
-%is that although the deep and shallow convection is parameterized
-%with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
-%is much smaller in our simulations than it is for many GCM-type experiments with parameterized convection.   At 25km grid-spacing, 
-%the majority of condensational heating occurs through the large-scale cloud  scheme (Figure \ref{fig:conv_vs_ls}).
-%%Overall, the fraction of precipitation that is 
-%%due to the large-scale scheme is roughly 40\%, and in many places it is actually greater than the amount of precipitation 
-%%produced by the convection scheme.   
-%%In comparison, many GCMs, have between 70\%-90\% of their precipitation produced by 
-%%the convective parameterization.  
-%There are further surprises in the fraction of precipitation that is large-scale.  On our small 
-%domains, with a bowling alley domain length of 4000 km, the simulations with 100km grid-spacing have values of $f_{ls}$ 
-%of $75-80\%$.  Often, at GCM-like resolutions such as 100km the convective precipitation would be expected to control much of the
-%precipitation rather than the large-scale parameterization.  However, when the domain length is increased to 16000 km
-%$f_{ls}$ decreases to a range of $0-70\%$ that depends strongly on location.  Over the warmest region of the surface the 
-%precipitation is still dominated by the large-scale scheme.   The large domain without the longwave CRE is the 
-%only configuration in which the convective precipitation is dominant.    If the default, or baseline, configuration of a GCM is built 
-%with the expectation that the convective parameterization scheme will dominate the production of tropical precipitation, then 
-%perhaps a configuration that minimizes the convective precipitation will result in a balance between the parameterization 
-%schemes that is less intuitive, such as an asymmetric response to symmetric forcing.
-
 %\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
@@
 \section{Dependence on Resolution: From a General Circulation Model to Cloud Resolving}
-
-\begin{figure}
-  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
-  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
-  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
-  Shading indicates mm/day.  The horizontal axis shows the entire 
-  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the average over the small dimension of the channel domain. } 
-  \label{fig:hov_4mods_6mn}
-\end{figure}
-
-% ..... moved to introduction .... 
-%Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
-%and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
-%The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
-%because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-%clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
-%Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
-%GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
-%in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
-%would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
-%interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
-%of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
-%range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
-      \caption{The equilibrated state of the Walker cell as a function of resolution.  
-      Experiments shown are E25 (left), E2(center), and E1(right). Top panels show the 
-      steady state relative humidity (shading) and mass streamfunction (black contours)
-      while bottom panels show the total condensation (liquid + ice).  
-      All panels use the same contour interval for the 
-      mass streamfunction (kg/s).}
-  \label{fig:rh_psi_P25E2E1}
-\end{figure}
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
-          \caption{Same as previous figure except with the longwave CRE turned off.}
-  \label{fig:rh_psi_P25E2E1_lwoff}
-\end{figure}
 
@@
 
-\begin{figure}
-  \centering
-      %\includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
-       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice) for P25 (thin yellow), E25 (yellow), 
-          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on
-          and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
-          convection.}
-  \label{fig:TotCond}
-\end{figure}
-
 Compared to E25 both E1 and E2 experiments have a stronger deep overturning circulation above the warm 
@@
 
-%The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
-%where the differences in strength of the overturning circulation are most pronounced. 
-%(can we use this to understand the differences in LWCRE?).
-
-\begin{figure}
-  \centering
-    \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
-    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
-    For all panels, thick lines show control experiments with the LW CRE on, thin lines show experiments
-    with the LW CRE off.}
-    \label{fig:enthalpy}
-\end{figure}
-
 Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
@@
 %require a correspondingly larger amount of condensational heating and precipitation.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
-  \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
-  subsidence regions and are shown for the control (LWCRE-on) and LWCRE-off experiments.}
-  \label{fig:cf_tdtlw}
-\end{figure}
 

### 2019-11-20 Silvers_cfmip_draft.tex
added detail to captions.  added text describing some of the relevant experiments.  added a few figures of zonal cloud profiles.

@@
 
-\section{Clouds in AM4.0: Comparison between amip and observations}
+\section{Clouds in AM4.0: Comparison between AMIP and observations}
 
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
-  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/testplot_oldconts.pdf}
-  \caption{Comparison thick (optical depth between 3.6 and 60) thin (optical depth between 0.3 and 3.6) clouds the 
-  MISR simulator in  AM4 with observations from MISR (bottom panels).}
+  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
+  \caption{Observed and modeled clouds.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
+  and thin (optical depth between 0.3 and 3.6) 
+  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
+  derived with the MISR simulator.  Data from all vertical levels is used.}
   \label{fig:misr}
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/clt_calipso_obs_sim_am4.eps}
-  \caption{Comparison of total cloud fraction.  Top shows observations from CALIPSO, processed for GCM comparison.  Middle 
-  shows output from the CALIPSO simulator, bottom shows raw model output of clt without a simulator.}
+  \includegraphics[width=0.86\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
+  \caption{As in previous figure except that here only clouds below 3km are shown.  Clouds shown are divided into thick 
+  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
+  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
+  with the MISR simulator (amip experiment).}
   \label{fig:calipso_sim_vs_mod}
@@
   \includegraphics[width=0.86\columnwidth]{cfmipfigs/ctp_vs_tau_isccp_modis_am4_obs.eps}
-  \caption{Joint histograms showing the variations of cloud fraction as a function of cloud top pressure and tau.}
+  \caption{Joint histograms showing the variations of cloud fraction as a function of cloud top pressure and tau.
+  Figure taken from Zhao et al., 2018}
   \label{fig:calipso_sim_vs_mod}
@@
   \includegraphics[angle=90,width=0.86\columnwidth]{cfmipfigs/calip_9pan_amip_obs_vs_AM4.eps}
-  \caption{Calipso scumstash.  Black line shows meridional profiles of AM4.0 cloud fraction and blue line shows
-  the meridional profile from CALIPSO.}
+  \caption{Cloud Fraction observed by CALIPSO (2007-2016) and modeled with the CALIPSO satelite simulator 
+  (amip experiment).
+  Dashed line shows meridional profiles of AM4.0 cloud fraction and solid line shows
+  the meridional profile of observed cloud fraction.  With only a few exceptions in the polar regions, AM4 underestimates
+  clouds in all three vertical ranges with the largest underestimate being of low-level clouds between +/-30.}
   \label{fig:calipso_9pan}
@@
 
+The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
+three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
+differences in the measures of sensitivity reveal important details of the physics that underly the response
+of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
+experiments are the historical simulation (historical: 1850-2014),  the abrupt quadroupling of CO2 concentration 
+ (abrupt-4xCO2: 150 years), and the experiment in which the concentration of CO2 is increased by 1\% 
+ per year from the pre-industrial until the concentration is doubled (1pctCO2: 150 years, doubling at year 70).  
+The historical simulation is our best attempt at using our coupled GCM to reproduce the historical 
+record found in observations.  This has frequently been used to estimate the climate sensitivity using the 
+energy budget method (Otto et al., 2013, Armour et al., Andrews et al., Winton et al., 2020).  The abrupt-4xCO2
+experiment has been utilized by the IPCC to derive measures ECS among the CMIP5 and CMIP6 models
+using a linear regression of the change in TOA radiative fluxes and surface air temperature over the first 
+150 years of simulation (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
+CO2 concentration, the 1pctCO2 experiment allows the Earth system to adjust to slowly increasing concentrations.  
+The sensitivity taken from this experiment is argued to be more relevant for an assessment of the 
+near term impact of the climate change because it is calculated based on a doubling of CO2.
+
 % Ringer et al 2014 comparison
@@
   \includegraphics[width=0.86\columnwidth]{cfmipfigs/HML_CF_cfmip_bias.eps}
-  \caption{Cloud fraction from several of the CMIP6 experiments.}
+  \caption{Cloud fraction bias relative to the AM4.0 amip experiment.}
   \label{fig:cf_hml_bias}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_clim_amip_hist.eps}
+  \caption{Cloud fraction between 1979-2014 for the amip and historical experiments.  The CALIPSO
+  observations range from January 2007 through December 2016.  Note that the regions poleward of
+  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  It is 
+  also interesting that having an interactive surface only leads to a minimally improved CF bias.}
+  \label{fig:calipso_amip_comparison}
 \end{figure}
@@
 \begin{center}
-\caption{Global mean radiative feedbacks.  The values for the Abrupt 4xCO2 experiment
-have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.}
-    \begin{tabular}{*{6}{c}}
+\caption{Global mean radiative feedbacks.  The cloud radiative effect (CRE) is computed as
+ the clear sky minus all sky flux. The values for the Abrupt 4xCO2 experiment
+have been estimated from a linear fit of the years 51-300.  Compare to Ringer et al. 2014.
+Values in parenthesis are most recent values.  Why are they different than the Amip p4K 
+original values?}
+    \begin{tabular}{*{7}{c}}
     \hline
     \hline
- Feedback & Aqua p4K & Amip m4K & Amip p4K & Amip Future & Abrupt 4xCO2    \\ \hline
-    Net          &   -2.2  & ??  &  -1.6              & -1.8           &    -0.46 (-0.84; Tim)         \\ 
+ Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2    \\ \hline
+    Net          &   -2.2 (-2.2) & ?? (-1.9)  &  -1.6 (-1.8)      & ?? (-1.9)      & -1.8 (-2.1)    &    -0.46 (-0.84; Tim)         \\ 
     \\
-    Net CRE      & 0.3   & ??  & -0.1            & 0.1           & 0.65   \\  
+    Net CRE      & 0.3 (0.3)  & ?? (0.0)  & -0.1(-0.1)    & ?? (-0.0)         & 0.1 (0.1)          & 0.65   \\  
     \\
-    LW CRE       & 0.4   & ??  & 0.1            & 0.1           & 0.14    \\  
+    LW CRE       & 0.4 (0.4)  & ?? (0.2)  & 0.1 (0.2)  & ?? (0.2)        & 0.1 (0.1)          & 0.14    \\  
     \\
-    SW CRE      & -0.7  & ?? & -0.1          & -0.2          & -0.5              \\  
+    SW CRE      & -0.7 (-0.7) & ?? (-0.2) & -0.1 (-0.1)  & ?? (-0.1)      & -0.2 (-0.2)         & -0.5              \\  
     \\
-    LW CLR       & 2.0   & ?? & 2.0             & 2.0           & 1.7             \\  
+    LW CLR       & 2.0 (2.0)  & ?? (2.3) & 2.0 (2.3)   & ??  (2.3)       & 2.0 (2.4)         & 1.7             \\  
     \\
-    SW CLR      & -0.1  & ?? & -0.3            & -0.3          & -0.6                   \\  \hline
+    SW CLR      & -0.1 (-0.1)  & ?? (-0.4) & -0.3 (-0.4)    & ?? (-0.4)        & -0.3 (-0.4)          & -0.6                   \\  \hline
 
@@
   \includegraphics[width=0.86\columnwidth]{cfmipfigs/amip_p4k_future_cldfrac_calip.eps}
-  \caption{Calipso scumstash}
+  \caption{Cloud fraction for amip related experiments.  Observations from CALIPSO are shown for reference.}
+  \label{fig:calipso_amip_comparison}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_warming.eps}
+  \caption{Cloud fraction for experiments with warming.  For reference cloud fraction from amip is also shown.}
+\end{figure}
+
+\begin{figure}
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_warming_amipbias.eps}
+  \caption{Cloud fraction bias for experiments with warming.  The bias is computed relative to the amip experiment. 
+  For the low-level clouds note that the coupled experiments have CF maximum (5-6\%) at -20 annd -75 where the prescribed uniform warming
+  does not.  The coupled model experiments produce much less CF in the latitudes between 30-70.  All warming experiments have more 
+  arctic low-level clouds than the amip experiment.  Keep in mind the amip experiment has too many arctic low-level clouds based
+  on the CALIPSO data.}
   \label{fig:calipso_amip_comparison}
@@
 \section{What are we learning?}
+
+How much do clouds contribute to our uncertainty in the climate sensitivity?  
+Which clouds (high, mid, low, thick, thin, geographic regions) contribute to this uncertainty?
+Why do we do a poor job with these clouds in models?
 

### 2019-12-20 Silvers_WalkerCell.tex
made quite a few changes.  some of them substantial.  don't feel like explaining now.

@@
 cumulus, and cumulus congestus clouds all interact with each other.  The Hadley circulation connects the tropical 
-pacific with subtropics and has been extensively studies (review paper?).  The circulation first 
+pacific with the subtropics and has been extensively studied (review paper?).  The circulation first 
   noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is 
@@
   (Walker, Bjerknes), theory 
-  (Geisler, 1981), or modeling studies (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
-  Kuang, 2012)).  Some of these modeling studies have compared theoretical models with cloud
-  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations 
-  of the Walker Circulation with simulations from a GCM within a flexible dynamical framework that draws on the 
-  same code base for both models.
+  (Geisler, 1981), or modeling (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
+  Kuang, 2012)).  The modeling studies have primarily used models referred to as Cloud-system 
+  Resolving Models (CRM), 
+  which has meant a grid-spacing of less than 5km and no convective parameterization.    One of the primary 
+  motivations of this paper is to compare cloud resolving model simulations 
+  of the Walker Circulation with simulations from a GCM within a flexible dynamical framework that draws on a 
+  single code base for both models.
 
@@
 and the resolution, or grid-spacing.  Elements of this study that distinguish it from previous research on the Walker 
-circulation are the use of fully interactive radiation, and the comparisons with a state-of-the-art general circulation
+circulation are the use of fully interactive radiation, and the direct comparisons with a state-of-the-art general circulation
 model configuration.   Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
@@
 
-The results of our experiments are organized as follows.  Details of the model and the particular experiments used are described
+The paper is organized as follows.  Details of the model and the particular experiments used are described
 in the next section.  The longwave cloud radiative effect is an important element for all of the experiments and will be 
@@
 16000 km (`large').  To explore the mock-Walker circulation in the context of both a GCM and a CRM we utilize 
-comparisons of the experiments with grid-spacings of 25km (E25), 2km (E2), and 1km (E1) all on a domain with the same long dimension 
+comparisons of the experiments with grid-spacings of 25km (P25 and E25), 2km (E2), and 1km (E1) all on a domain with the same long dimension 
 of 4000 km.  The experiments with a grid-spacing of 25km serve as a link between the GCM-like configuration and the CRM-like 
-configuration.  Domains with dimensions of 16000 km are too costly for the 1km and 2km experiments.
+configuration.  The only difference between these two experiments is that E25 has both the shallow and deep convective parameterizations turned 
+off so that all of the convection in that experiment is explicit, as it is in E2 and E1.  Domains with dimensions of 16000 km where judged too 
+costly for the 1km and 2km experiments.  Basic experimental details and the naming convection for the experiments are shown in Table 1.
 
@@
 atmospheric state.   This method was originally pioneered by Slingo and Slingo, 1988 and Randall et al., 1989.  More recently, it has been
-implemented as part of the CFMIP series of experiments (Stevens et al. 2012).
+implemented as part of the CFMIP series of experiments (Stevens et al. 2012, Webb et al., 2017).
 In the AM4 code, this is done separately for the longwave and shortwave radiation.  In this study we compare control experiments, 
@@
 \ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
-SSTs and a humid boundary layer across the full length of the domain.   For the GCM-like configuration (P25, left panels 
-of Figure \ref{fig:rh_psi_P25vsE25}) with fully parameterized convection and with the longwave CRE turned on, there is 
-a strong overturning circulation that results in a humid, condensate loaded troposphere near the middle of the domain 
-and a dry ($< 10\% RH$) subsidence region with almost no condensate above $800 \rm{hPa}$.    
-This atmospheric state has the same fundamental characteristics as the Walker circulation, the Hadley Cell, and 
+SSTs and a humid boundary layer across the full length of the domain.    Large concentrations of condensate are 
+present in the mid-troposphere over the warmer SSTs, while the regions with subsiding circulations are 
+dry ($< 10\% RH$) above about $900 \rm{hPa}$.  The left panels of Figure \ref{fig:rh_psi_P25vsE25}  show that our 
+control GCM experiment has a stronger, more concentrated circulation with more condensate in the convective
+region and a dryer subsidence region, relative to the cases with the LWCRE off (middle panels) and with the
+convective parameterization off (right panels).
+
+%
+%It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
+%results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
+%relative to the case with the LWCRE-off.   A stronger and spatially concentrated circulation for cases when the 
+%clouds interact with the longwave radiation can also be seen in Figures 4, 5, 9 and 10 and is particular apparent in 
+%the cases with a large domain (16000 km long dimension).
+
+This state has the same fundamental characteristics as the Walker circulation, the Hadley Cell, and 
 experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations and 
@@
 
-To illustrate some of the sensitivities to convection and the interaction between clouds, radiation, and the large-scale 
-circulation we compare the P25 experiment with analogous experiments in which the longwave CRE is turned 
-off (P25 LWCRE off, middle 
-panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
-parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).  
-The mass streamfunction and vertical velocity both show the P25 experiment has a stronger overturning circulation 
-than either E25 or P25 LWCRE off.  P25 also has higher humidity in the deep convective region, and lower humidity in 
-the subsidence region over the 
-cooler SST (Figure \ref{fig:rh_psi_P25vsE25}) than either E25 or P25 LWCRE off.  Averaged over the full domain, 
-the parameterized convection leads to a dryer atmosphere with less 
-condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  
-However, in the updraft region the convective parameterization results in more moisture aloft.
-
-Superposing the circulation and relative humidity illustrates the subsidence driven 
-drying and the strong moistening that results from ascent over the region of maximum latent heat flux.  
-Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  
-Deep-convective activity dominates the 
-region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part stratocumulus 
-clouds are absent (based on what?).  When the coupling between the circulation and clouds is broken, by turning off the longwave CRE, 
-the atmospheric state is much more symmetric about the maximum SST.  We also find large differences among the 
-experiments in the domain mean precipitation, condensate/clouds, and circulation (see Table 2).  In general the 
-experiments with parameterized convection are much more erratic.
-
-One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry relative to the 
-symmetric SST distribution in both the time-dependent and 
-steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).  
-This asymmetry is also present in P25 experiments on larger domains and at a resolution of $100 \, \rm{km}$. 
-The steady-state precipitation maximum is located  not over the warmest SST but is
-shifted to slightly cooler temperatures.  The asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, 
-specific humidity, and radiative heating.  
-In the Hovmoller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse to 
-residing over the SST maximum.  
-For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^-1}$) domain
-mean shear develops above about 500 \textit{m} which shifts the precipitation and circulation off center for years at a time.
-When the convective parameterization is turned off (E25), the overturning circulation becomes weaker and 
-broader (w, and psi), and the precipitation, cloud fields, and 
-circulation all consistently reside over the SST maximum (for about 1 year before going haywire).   
-While the parameterized convection plays a large role in driving this asymmetry it appears to be not entirely a 
-result of the convective parameterization, but also due to an interaction between the convective 
-parameterization and the LW CRE.   The degree to which this asymmetry influences the comparison with other experiments is 
-unclear.    Note: check the wind shear for P25large, P100small, and P100large (E25 has less shear than E1 or E2).
-
-Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted many times in 
-previous literature \cite{Bretherton2006, Wofsy2012} (Ming Zhao (personal communication, see Jeevanjee et al. 2018))
-but the irregularities have 
-tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
-entirely explicit (E25, E2, and E1, discussed further in section 4).
-
-%%%%%
-% section 3.1 results
 \begin{figure}
@@
 
+%To illustrate some of the sensitivities of the GCM to convection and the interaction between clouds, radiation, and 
+%the large-scale 
+%circulation we compare the P25 experiment with analogous experiments in which the longwave CRE is turned 
+%off (P25 LWCRE off, middle 
+%panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
+%parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).  
+The mass streamfunction and vertical velocity both show the P25 experiment has a stronger overturning circulation 
+than either E25 or P25 LWCRE off.  P25 also has higher humidity in the deep convective region, and lower humidity in 
+the subsidence region over the 
+cooler SST (Figure \ref{fig:rh_psi_P25vsE25}) than either E25 or P25 LWCRE off.
+
+Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less 
+condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  
+However, in the updraft region the convective parameterization results in more moisture aloft.
+
+As the domain size increases, so does the domain mean precipitable water.  Active LWCREs lead
+to larger values of barPW in all cases (Table 2).  (Does this tell us anything about precipitation efficiency?)  
+It is also interesting to note that barPW varies by as much as 30\%.
+
+Superposing the circulation and relative humidity (as in Figure \ref{fig:rh_psi_P25vsE25}) illustrates the subsidence driven 
+drying and the strong moistening that results from ascent over the region of maximum latent heat flux.  
+Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  
+Deep-convective activity dominates the 
+region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part 
+stratocumulus clouds are absent (based on what?).  When the coupling between the circulation and clouds is 
+broken, by turning off the longwave CRE, the atmospheric state is much more symmetric about the maximum 
+SST.  We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, 
+and circulation (see Table 2).  In general the experiments with parameterized convection are much more erratic.
+
+One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry relative to the 
+symmetric SST distribution in both the time-dependent and 
+steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).  
+This asymmetry is also present in P25 experiments on larger domains and with a grid-spacing of $100 \, \rm{km}$. 
+The steady-state precipitation maximum is located  not over the warmest SST but is
+shifted to slightly cooler temperatures.  This asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, 
+specific humidity, and radiative heating.  
+In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse to 
+residing over the SST maximum.  
+For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^{-1}}$) domain
+mean shear develops above about 500 \textit{m} which shifts the precipitation and circulation off center for years at a time.
+When the convective parameterization is turned off (E25), the overturning circulation becomes weaker and 
+broader (w, and psi), and the precipitation, cloud fields, and 
+circulation all consistently reside over the SST maximum (for about 1 year before going haywire).   
+While the parameterized convection plays a large role in driving this asymmetry it appears to be not entirely a 
+result of the convective parameterization, but also due to an interaction between the convective 
+parameterization and the LWCRE.   The degree to which this asymmetry influences the comparison with other experiments is 
+unclear.
+
+Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted many times in 
+previous literature \cite{Bretherton2006, Wofsy2012} (Ming Zhao, see Jeevanjee et al. 2018)
+but the irregularities have 
+tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
+entirely explicit (E25, E2, and E1, discussed further in section 4), but strikingly different than for P25.
+
 %"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
@@
 
-The default experimental configuration includes radiation that is fully interactive with the clouds, water vapor, and 
-temperature of the atmospheric state.  It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
-results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
-relative to the case with the LWCRE-off.   A stronger and spatially concentrated circulation for cases when the 
-clouds interact with the longwave radiation can also be seen in Figures 4, 5, 9 and 10 and is particular apparent in 
-the cases with a large domain (16000 km long dimension).  This will be discussed further in the next section.
-
-Previous studies have shown that cloud radiative effects act to strengthen and contract an overturning circulation 
-(e.g. Popp and Silvers, 2017, Harrop and Hartmann, and others (Muller and Held?), Albern et al., 2019).  This is 
-due to an increased low-level flux
-of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
-convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
-region of persistent deep convection and a state of aggregation.   One of the simplest measures of convective 
-aggregation and the large-scale circulation is the fraction of the domain in which the air is subsiding, the 
-subsidence fraction (SF).  As convection becomes more organized, or aggregated, SF will increase.  We expect 
-for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
-fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE-on
-have a larger SF (with the exception of E1, for which SF is constant).  Our prescribed SST warm patch ensures that our simulations will 
-be `aggregated' to some degree.  However, the subsidence fraction is a useful metric even in this case which 
-includes an additional constraint than RCE.  Given identical SSTs, the different SFs give a measure of variability
-that is driven entirely by the atmosphere.
-
-%\subsection{The Asymmetric Influence of Convective Parameterization and the organizing tendency of LWCRE}
-
 % LWCRE has a large impact on LS precip, not so much on convection
@@
 
-% are the impacts of the LWCRE the same for GCMs as they are for CRMs?
-
-% Vertical Velocity and time averaged precipitation
 \begin{figure}
@@
 
+Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
+overturning circulation 
+(e.g. Popp and Silvers, 2017, Harrop and Hartmann, (Muller and Held?), Albern et al., 2019).  This is 
+due to an increased low-level flux
+of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
+convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
+region of persistent deep convection and a state of aggregation.   One of the simplest measures of convective 
+aggregation and the large-scale circulation is the fraction of the domain in which the air is subsiding, the 
+subsidence fraction (SF).  As convection becomes more organized, or aggregated, the SF will increase.  We expect 
+for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
+fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE-on
+have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
+dependence of aggregated atmospheric states on temperature (\citeA{Khairoutdinov2010}; \citeA{Wing2014}).  
+While there does appear to be a dependence 
+on temperature, Table 2 illustrates how much the aggregated 
+state can vary among experiments with identical SST.  Having a prescribed SST warm 
+patch ensures that the simulations will be `aggregated' to some degree.  Rather than indicating whether an 
+experiment is aggregated, the SF here measures the spatial extent of the overturning circulation.  The SF provides a 
+simple way of quantifying the degree of organization that is present.  Given identical SSTs, the  range of 
+different SFs provide a measure of variability that is driven entirely by the interactions between 
+convection, radiation, and the large-scale circulation.
+
 \section{The Influence of Domain Size on the LWCRE and the LS Parameterized Precipitation: Change Title?}
@@
 function of domain size, parameterization of convection, and the effect of the longwave radiation due to clouds. 
-Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovmoller plots of precipitation after 
+Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovm{\"o}ller plots of precipitation after 
 averaging along the short horizontal dimension.  The four panels show simulations with a grid-
@@
 
-At all resolutions the Hovmoller plots show that the LWCRE acts to concentrate the 
+At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the 
 precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
@@
 in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
-Precipitation from each of these two components is
-shown in Figure \ref{fig:conv_vs_ls} as a function of both resolution and domain size.  
-In the regions of large-scale ascent, most of the 
-precipitation derives from the large-scale cloud scheme.  
-Following the terminology of \citeA{Held2007} we could say that most of the precipitation is 
-coming from `gridpoint storms' in which the upper level moisture is being supplied not 
+Precipitation from each of these two components isshown in Figure \ref{fig:conv_vs_ls} as a function of 
+both resolution and domain size.  In the regions of large-scale ascent, most of the precipitation derives 
+from the large-scale cloud scheme.  Following the terminology of \citeA{Held2007} we could say that most 
+of the precipitation is coming from `gridpoint storms' in which the upper level moisture is being supplied not 
 by the convective parameterization but from the boundary layer as a result of large-scale upwelling.
-We also see that the LW CRE (thick lines) dramatically increases
+We also see that the LWCRE (thick lines) dramatically increases
 the large-scale precipitation.  The LWCRE has a much smaller effect on the magnitude of the convective 
-precipitation 
-but does act to spatially concentrate it.  With the exception 
+precipitation but does act to spatially concentrate it.  With the exception 
 of the P100L LWCRE-off experiment, the convective precipitation produces relatively little of the total precipitation for 
@@
 effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction.  
-We also demonstrate that is through the longwave cloud radiative effect that this connection is enabled.
+We also demonstrate that it is through the longwave cloud radiative effect that this connection is enabled.
 
@@
 
-We now show results that originated with our motivation to simulate a tropical Pacific-like region 
+We now show results that resulted from our motivation to simulate a tropical Pacific-like region 
 in the context of both a GCM and a CRM.  In this section we focus on simulations with grid-spacing of 
@@
 
-Compared to E25 both E1 and E2 experiments have a stronger deep overturning circulation above the warm 
+Compared to E25 both the E1 and E2 experiments have a stronger deep overturning circulation above the warm 
 patch and they have significantly more condensate aloft in this region.    It is also apparent in Figures 
@@
 region drying and condensate aloft in the upwelling region have a clearer dependence on resolution when 
-the LWCRE is off.  This suggests that the interactions between clouds and radiation can help the 
+the LWCRE is off.  This suggests that the interactions between clouds and radiation help the 
 atmospheric state converge towards a particular solution.
@@
 The domain mean condensate is an important measure of the steady state reached by these experiments.  The vertical 
-distribution of condensate is closely related to the distribution of clouds.  This in turn influences the distribution of 
-energy throughout the atmosphere and the longwave radiation that is emitted to space.  It can also indicate the 
+distribution of condensate is closely related to the distribution of clouds.  This in turn influences the distribution and
+flow of energy throughout the atmosphere and the longwave radiation that is emitted to space.  It can also indicate the 
 strength of convection and vertical mass transport.     
@@
 with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  The opposite occurs for the 
-GCM-like experiments.  The interactive LWCRE increase the amount of upper level ice-condensate 
-(Figure \ref{fig:TotCond_P25P100}).    The Influence of the LWCRE on low-level clouds is consistent for both the 
+GCM-like experiments.  The interactive LWCRE increases the amount of upper level ice-condensate 
+(Figure \ref{fig:TotCond_P25P100}).    The influence of the LWCRE on low-level clouds is consistent for both the 
 GCM-like and CRM-like experiments.  The LWCRE leads to more low-level clouds/condensate although the 
@@
 Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
-surface enthalpy flux reveals large differences in the symmetry.   Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
+surface enthalpy flux reveals large differences in the symmetry of the near surface energetics.   
+Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
 the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
@@
 over the warmest SSTs is reduced from $60 \, \rm{W/m^2}$ to about $20 \, \rm{W/m^2}$ and the enthalpy
-flux for E1and E2 become very similar over the warmest SSTs.  This implies that the interactions between clouds
-and the longwave radiation have a massive influence on the surface energy budget even for the case of prescribed
-SSTs with no land.     
+flux for E1and E2 become very similar over the warmest SSTs.   Thus even for the case of prescribed SSTs and no
+land surface the interactions between clouds and the longwave radiation have a massive influence on the 
+surface energy budget.
+
 %The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere.  
@@
 fraction in the subsidence region, with the E1 experiment having the next largest cloud fraction (10\%), followed by 
-P100, E25, and P25 (3-5\%).  As noted in the discussion about the total condensate, the CRM-like models 
+P100, E25, and P25 (3-5\%).  As noted in the discussion of the total condensate, the CRM-like models 
 produce large values of upper-level cloud with minimal low-level clouds while the GCM-like models
@@
 An interesting point that emerges from the domain mean values of precipitation (see Table 2) 
-is that the sign of the response to LWCRE is not the same across the different resolutions.
+is that the sign of the response to LWCRE is not the same between CRM and GCM experiments.
 When clouds are not allowed to interact with the longwave radiation the atmosphere 
@@
 larger values of $\overline{\rm{P}}$.  This is clearly not the case for the E25, P25, and 
-P100 cases.   \textit{The domain mean precipitation rates decrease despite an increased 
+P100 experiments.   \textit{The domain mean precipitation rates decrease despite an increased 
 amount of atmospheric cooling.}  The implication is that the requisite atmospheric heating 
@@
 for the atmosphere (Figure \ref{fig:cf_tdtlw}).  Making these clouds invisible to radiation creates 
-a source of effective atmospheric warming.  
+a source of effective atmospheric warming.   The large decrease of low-level clouds also leads to an increase of downward shortwave 
+radiation at the surface.  Because of the low albedo of water
+this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
+and contributes minimally to heating the atmosphere.
 %(does the downwelling longwave
@@
 condensational heating and the mean precipitation rate actually decreases.
-The large decrease of low-level clouds also leads to an increase of downward shortwave 
-radiation.  Because of the low albedo of water
-this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
-but does contribute slightly to heating the atmosphere.
 
@@
 This is especially true for the simulations with a grid-spacing of 1 km and 2 km.  While the mid-tropospheric 
-profiles of diabatic heating and cooling are similar between the LW CRE on/off simulations, there is a very strong 
-response below about 850 hPa for the 25km and 100km models.  At that grid-spacing, with the LW CRE on, significant low-level 
+profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
+response below about 850 hPa for the 25km and 100km models.  At that grid-spacing, with the LWCRE on, significant low-level 
 clouds are formed, leading to a radiative cooling on the order of -10K/day.   
-However, when the LW CRE is off, there is little appreciable difference in the low-level diabatic profiles among the 
+However, when the LWCRE is off, there is little appreciable difference in the low-level diabatic profiles among the 
 P100, P25, E25, E2, and E1 experiments.   It is also clearly seen that the LW CRE decreases the upper-level ice-condensate 
@@
 there are significant differences between the CRM presented in this paper and more conventional CRMs (e.g. vertical 
-grid spacing and threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
+grid spacing and a threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
 like a CRM provides an enticing testbed for future model development.
@@
 and humidity play in driving and responding to the circulation we have performed experiments with and without the radiative
-effect of clouds, with and without the deep convective parameterization, across multiple domain sizes and resolutions.  
+effect of clouds, with and without the convective parameterization, across multiple domain sizes and resolutions.  
 Our results show that the convective 
@@
 It is remarkable that the control simulations (LWCRE on) have a precipitation rate  that can vary by as much as 
-20\% despite have have the same prescribed SST and incoming radiation.  All simulations have the same radiation,
+20\% despite having the same prescribed SST and incoming radiation.  All simulations have the same radiation,
 turbulence, large-scale cloud and microphysics parameterizations and all use the same dynamical core.

### 2020-04-24 Silvers_WalkerCell.tex
substantial chagnes to text, structure, and figures of Silvers_WalkerCell.tex

@@
 \title{Clouds and Radiation in a mock-Walker Circulation}
-\authors{Levi G. Silvers, and Thomas Robinson}
+\authors{Levi G. Silvers\affil{1,*}, and Thomas Robinson\affil{2}}
+
+\affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
+\affiliation{2}{SAIC, Science Applications International Corporation, Reston, VA, USA}
+\affiliation{*}{Current Affiliation: School of Marine and Atmospheric Sciences, Stony Brook University, Stony Brook, NY, USA}
 
@@
   \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant}
-  \item{Interactions between clouds and radiation combined with parameterized convection act to shift the precipitation 
+  \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation 
   maximum away from the SST maximum.}
-  \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
-  changes in the low-level clouds and boundary layer structure.}
+ % \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
+ % changes in the low-level clouds and boundary layer structure.}
   \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
   region that is 40\% higher than for the coarser cases with parameterized convection.}
-  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
+%  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
 \end{keypoints}
@@
 %To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
-%idealized equatorial tropical Pacific.
-
-In the western Pacific warm sea surface temperatures prevail beneath rising atmospheric motion and deep convective 
+%idealized equatorial tropical Pacific over a range of resolutions.
+
+In the western Pacific warm sea surface temperatures (SST) prevail beneath rising atmospheric motion and deep convective 
 storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
 non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
-connected by a large-scale circulation.  
-We analyze an idealization of this circulation with high-resolution 
-and coarse resolution simulations. 
+connected by a large-scale circulation referred to as the Walker circulation.  
+We analyze an idealization of this circulation to compare the multi-scale interactions between circulations,
+cloud systems, and interactive radiation across experiments with grid-spacing ranging from 1km to 100km.  
+These experiments thus span the range of resolutions between General Circulation Models (GCMs) and 
+Cloud-system Resolving Models (CRMs).  
+Our GCM-like experiments have a large low-level cloud fraction but the CRM-like experiments have more
+upper-level clouds.  This difference in the dominant cloud type leads to opposite atmospheric responses 
+to changes in the longwave cloud radiative effect (LWCRE).  An active LWCRE leads to increased 
+precipitation for GCMs, but decreased precipitation for CRMs.  Decreasing the resolution to 1km and 2km
+results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.
+
+Numerous studies of the Walker Circulation have used simplified 
+theoretical or numerical models.  The focus of this paper is to simulate a mock-Walker
+Circulation with a full-physics General Circulation Model (GCM) run with idealized boundary conditions to provide 
+a connection between the simpler models 
+%and the complex interactions between clouds, 
+%radiation and the large-scale circulation that are present in the tropical Pacific 
+and current GCMs.
+The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory (GFDL).
+By dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate
+some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
+This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes
+a large-scale circulation.
 %% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
 %%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
-%%Earth's sensitivity to 
-%%changes in greenhouse gas concentrations.
-%
-%A high resolution (1km) cloud resolving model is used here as a benchmark to compare with the same model at lower 
-%resolution (25km, 100km) configured 
-%as a fully parameterized general circulation model.  Both models use approximately the same spatial domain.  The climate model used is 
-%derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory.  By 
-%dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate 
-%some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
+%%Earth's sensitivity to changes in greenhouse gas concentrations (think radiator fins).
+%
+%Both models use approximately the same spatial domain.
 
@@
 
+\section*{Plain Language Summary}
+Interactions between clouds, radiation, and dynamics all contribute
+to the large-scale tropical motions and are fundamental to the Walker circulation.  
+The Walker circulation is the name of the loop consisting of westward surface winds towards the western tropical Pacific, 
+strong upward motion and deep convection over that region, 
+%of the western tropical Pacific, 
+and the return eastward winds aloft that 
+eventually sink towards the surface in the eastern Pacific basin.  
+We focus on an idealization of the Walker circulation (a mock-Walker circulation) 
+in which the strong rising motion and deep convection is driven by a patch of warm sea surface temperature (SST).  
+%Interactions between the radiative flux of energy and clouds are fundamental to the nature of the Walker circulation.  
+The results show that the response of the atmosphere to the 
+radiative flux of energy depends strongly on the relative amount of clouds at different heights. % type of cloud that is dominant in the atmosphere.  
+It is further shown that GCM-like models are dominated by low-clouds while CRM-like models 
+are dominated by high-clouds.  This work also argues that an idealized Walker circulation is an 
+excellent configuration with which to better understand the interactions between clouds, radiation and circulation 
+and to push the development of models forward.   Models of mock-Walker circulations represents
+an intermediate tier in a hierarchy of models between RCE and more Earth-like models.
+
+%The clouds in this system play a fundamental role in setting the 
+%characteristics of the mock-Walker circulation and the dominant cloud types are heavily dependent on 
+%what type of model is used to simulate them.
+
+%Our simulations are based on the equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures exist beneath 
+%rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface 
+%temperatures and low-level, non-precipitation clouds with a very dry atmosphere above the clouds.  These regions are connected by a
+ %large-scale circulation of winds.  By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep 
+ %convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
+
 \section{Introduction}
 
-%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.
-If an advance in our understanding of the role clouds play in our climate is desired, it is essential that we
-%learn to model the two way interaction between clouds and the circulation.
-The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation (imp of lwcre off).
-%Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation connects regions of deep convective activity with the prevalent tropical shallow 
-%convection and the radiatively critical stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and the Coriolis force is 
-%critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we propose that all of the physics of importance to our particular questions are present 
-%in the equatorial manifestation of the Walker circulation (perhaps better in conclusion).  
+%Clouds are much more than passive conglomerates of tracers in a turbulent fluid.  
+%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.  If an advance in our understanding 
+%of the role clouds play in our climate is desired, it is essential that we learn to model the two-way interaction between clouds 
+%and the circulation.  The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation 
+%(imp of lwcre off).  Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation 
+%connects regions of deep convective activity with the prevalent tropical shallow convection and the radiatively critical 
+%stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
+%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we 
+%propose that all of the physics of importance to our particular questions are present in the equatorial manifestation of the Walker 
+%circulation.  
 %
@@
 %As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
-%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be informed by the solution of the high resolution model.
-This approach will help to demonstrate that the influence of clouds on climate is not an intractable problem.
-%
-%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between radiation and clouds, as well as dynamical motions which range from
-%sub-kilometer scales to roughly 10,000 km.
-In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and stratocumulus clouds, the tropical
-%Pacific provides an ideal physical context with which to explore the sensitivities and strengths of theoretical models, high-resolution models and general circulation models.  
-%The tropical system in the Pacific Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface temperature gradients 
-%represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic circulations.
-%This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation and how the nonlinear interactions within the system contribute 
-%to the cloud feedbacks to perturbations and the overall sensitivity of the system to anthropogenic forcing.
-%
-%Several studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012) have examined a 
-%mock Walker circulation in the context of cloud resolving 
-%simulations, or idealized theoretical models.   The comparison between CRMs and simple theory revealed several important 
-%similarities (like what? See Bretherton et al., 2006) and a multiplicity of differing results (like what) for different CRM studies. 
-%It thus remains unclear what GCM like models should be expected to produce in similar configurations.  
-%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
-%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
-%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
-%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
-%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
-%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
-%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified SST. (just before equation 8 of Bretherton et al. 2006)."
-
-%The atmosphere of Earth constantly radiates energy to space.
-This cooling of the atmosphere is mostly balanced by warming from the release of latent energy by convective clouds and precipitation.
-The details of this balance between cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.
-However, clouds contribute to both warming and cooling of the atmosphere.
-Deep convective storms and high clouds warm the atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the atmosphere by reflecting the incoming radiation from the sun.
-Previous research has repeatedly shown that low-level clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ concentration (Bony and Dufresne, 2005, Sherwood et al.
-2014).
-However, it has also been shown that the turbulent mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate sensitivity (Zhao, 2014).
-The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
-%
-%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and Emanual, 2014 have shown that idealized models are quite 
-%sensitive to the details of the configuration such as domain size and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
-%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the purpose of this paper is to use one modeling framework to
-%illustrate just what is obtained from a coarse GCM-like model run with idealized boundary conditions.  We then use this modeling framework to compare the results obtained from simulations
-%with a resolution of 100, 25, 2, and 1km.
-%
-%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system the idealization 
-%is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, as compared to the observed 
-%world.  These simulations are somewhere in the middle of those extremes.  We have decided to keep many of the complex elements of 
-%the global climate model  so that we can hopefully better understand the parent model (AM4.0) while learning something concrete about 
-%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke large-scale 
-%cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
+%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in 
+%particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be 
+%informed by the solution of the high resolution model.  Demonstration of this would help to show that the influence of clouds on 
+%climate is not an intractable problem.
+%
+%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between 
+%radiation and clouds, as well as dynamical motions which range from sub-kilometer scales to roughly 10,000 km.     
+%In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and 
+%stratocumulus clouds, the tropical Pacific provides an ideal physical context with which to explore the sensitivities and 
+%strengths of theoretical models, high-resolution models and general circulation models.  The tropical system in the Pacific 
+%Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface 
+%temperature gradients represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic 
+%circulations.  This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation 
+%and how the nonlinear interactions within the system contribute to the cloud feedbacks to perturbations and the overall 
+%sensitivity of the system to anthropogenic forcing.
+%
+%It remains unclear what GCM like models should be expected to produce in similar configurations.
+
+%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified 
+%SST. (just before equation 8 of Bretherton et al. 2006)."
+
+%The atmosphere of Earth constantly radiates energy to space.  This cooling of the atmosphere is mostly balanced by 
+%warming from the release of latent energy by convective clouds and precipitation.  The details of this balance between 
+%cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.  However, clouds 
+%contribute to both warming and cooling of the atmosphere.  Deep convective storms and high clouds warm the 
+%atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the 
+%atmosphere by reflecting the incoming radiation from the sun.  Previous research has repeatedly shown that low-level 
+%clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ 
+%concentration (Bony and Dufresne, 2005, Sherwood et al. 2014).  However, it has also been shown that the turbulent 
+%mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate 
+%sensitivity (Zhao, 2014).  The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
+%
+%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and 
+%Emanual, 2014 have shown that idealized models are quite sensitive to the details of the configuration such as domain size 
+%and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
+%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the 
+%purpose of this paper is to use one modeling framework to illustrate what is obtained from a coarse GCM-like model run 
+%with idealized boundary conditions.  We then use this same modeling framework to compare the results obtained from 
+%simulations with a resolution of 100, 25, 2, and 1km.     
+%
+%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system 
+%the idealization is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, 
+%as compared to the observed world.  These simulations are somewhere in the middle of those extremes.  We have 
+%decided to keep many of the complex elements of the global climate model  so that we can hopefully better understand 
+%the parent model (AM4.0) while learning something concrete about 
+%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke 
+%large-scale cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
 %model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
@@
 %future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
-%a simple design that incorporates additional complexity which is critical for the connection to observed atmospheric phenomena.
-%
-%Our simulations are based on the equatorial tropical Pacific.
-In the western Pacific warm sea surface temperatures exist beneath rising atmospheric motion and deep convective storms.
-In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low level, non-precipitation clouds with a very dry atmosphere above the clouds.
-These regions are connected by a large-scale circulation of winds.
-By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
+%a simple design that incorporates additional complexity which strengthens the connection to observed atmospheric phenomena.
+%
 %
@@
 
-%\textbf{Paragraphs of Introduction}
-%\begin{itemize}
-%\item{Within the tropical Pacific are strong overturning circulations, deep convective towers, abundant shallow cumulus, 
-%  and cumulus congestus clouds.  The Hadley circulation connects the tropical pacific with subtropics and has been 
-%  extensively studies (review paper?).  The circulation first 
-%  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is dominated 
-%  by deep convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
-%  subtropics, stratocumulus clouds.  This circulation has come to be 
-%  known as the Walker Circulation and has received much less attention than the Hadley circulation (Geisler, 1981; 
-%  Bretherton et al., 2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on 
-%  observations (Walker, Bjerknes), theory (Geisler, 1981), 
-%  or modeling studies (Grabowski et al.,2000, Bretherton et al., 2006; Wofsy and Kuang, 2012, Kuang, 2012)).  Some of these 
-%  modeling studies have compared theoretical models with cloud
-%  resolving models.  One of the primary motivations of this paper is to compare cloud resolving model simulations of the Walker    
-%  Circulation with simulations from a GCM used on a doubly periodic domain.    What about Johnson et al.?}
 %  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
@@
 %  \cite{Bretherton2005, Muller2012}.}
-%\item{On the importance of reducing component, or sub-grid scale uncertainty through the use of both parameterized and explicit 
-%  convection.  This paragraph could also cite papers which have helped to validate RCE in general, and the channel RCE configuration
-%  in particular.  To what extent do RCE simulations of CSA agree between GCMs and CRMs?  Perhaps here I can hint at the utility of 
-%  this methodology for unifying our understanding.}
-%\end{itemize}
-
-\textbf{Key Questions}
-\begin{itemize}
-  \item{How do clouds influence the Walker Circulation?}
-  \item{To what extent are the deep convective clouds and the low-level clouds in the Walker Cell coupled?}
-  \item{When simulating the Walker Circulation, how well does a GCM compare to a CRM?}  
-\end{itemize}
-
-Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
-cumulus, and cumulus congestus clouds all interact with each other.  The Hadley circulation connects the tropical 
-pacific with the subtropics and has been extensively studied (review paper?).  The circulation first 
-  noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the Indonesian region that is 
-  dominated by deep 
-  convection to the eastern Pacific region which tends to be populated more by shallow cumulus and, in the 
-  subtropics, stratocumulus clouds.  This circulation has come to be 
-  known as the Walker Circulation and while receiving less attention than the Hadley circulation, there have been 
-  notable studies (e.g. Geisler, 1981; 
-  \citeA{Raymond1994}; Bretherton et al., 
-  2006; Wofsy and Kuang, 2012; Schwendike et al., 2014).  Previous studies have focused on observations 
-  (Walker, Bjerknes), theory 
-  (Geisler, 1981), or modeling (\citeA{Grabowski2000}, Bretherton et al., 2006; Wofsy and Kuang, 2012, 
-  Kuang, 2012)).  The modeling studies have primarily used models referred to as Cloud-system 
-  Resolving Models (CRM), 
-  which has meant a grid-spacing of less than 5km and no convective parameterization.    One of the primary 
-  motivations of this paper is to compare cloud resolving model simulations 
-  of the Walker Circulation with simulations from a GCM within a flexible dynamical framework that draws on a 
-  single code base for both models.
-
-  Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
-and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
+
 The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
 because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
-Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
-GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
-%that is rich in phenomena 
+clouds \cite{Johnson1999} as well as stratocumulus cloud decks along the eastern extremities of the basin.
+%Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
+%cumulus, and cumulus congestus clouds all interact with each other.  
+These overturning circulations encompass dynamical motions at scales
+ranging from meters to thousands of km's all of which interact with each of the different cloud types.
+% interact with the circulation on scales ranging from meters to thousands of km's.  
+%The Hadley circulation connects the tropical pacific with the subtropics and has been extensively 
+%studied (review paper?).  
+The circulation first noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the 
+Indonesian region that is dominated by deep convection to the eastern Pacific region which tends to 
+be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  
+This circulation, now known as the Walker Circulation, is a response to the 
+longitudinal asymmetries in the tropical atmospheric heating and is tightly coupled with 
+the El Nino Southern Oscillation.    
+The Walker Circulation is a compelling example of both thermodynamic and dynamic interactions
+between moisture and the large-scale circulation.  It is also a framework that can be compared 
+to observations and tested with a variety of model configurations.
+
+% Part of our motivations in using the framework of the Walker circulation comes from the fact that 
+% all of the major types of tropical clouds occur regularly within the region identified with the Walker
+% circulation.  In addition, the ability to focus on the equator without rotational effects simplifies
+% the dynamics.
+
+It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
+Recent work has shown that the interactions between clouds, patterns of Sea Surface Temperature (SST), and the circulation 
+in the tropical Pacific play an important role in determining the cloud feedback and the decadal 
+variability of the climate feedback 
+\cite<e.g.,>[]{Andrews_Webb_2018, Zhou_etal_2016, Silvers_etal_2018, Fueglistaler_2019}.
+While the Hadley circulation connects the tropics with the midlatitudes,  
+the Walker circulation is one of the primary mechanisms by which the clouds, SST and circulations 
+are coupled to each other in the tropics.  
+%While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
+%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical 
+%extra-tropical connections, 
+We propose that focusing on the Walker Circulation can lead to new insights into 
+several questions that are critical to a better understanding of the tropical climate and cloud processes.    
+These questions include: 
+\begin{itemize}
+  \item{How do clouds influence the overturning circulation?}
+  \item{To what extent are the deep convective clouds and the low-level clouds coupled through 
+  the overturning circulation?}
+  \item{When simulating tropical overturning circulations, how well does a GCM compare to a CRM?}  
+\end{itemize}
+%These interactions are influenced not only by the Walker circulation, but also the Hadley 
+%cell and convectively coupled tropical waves.  
+In global and Earth-like GCM simulations, the interplay between the overturning 
+circulation and clouds is difficult to disentangle from other active processes such as
+the Hadley cell and convectively coupled tropical waves.  
+%the large-scale circulation and clouds do not 
+%act on each other in isolation but are also influenced by a host of other phenomena such as 
+%the Hadley cell and convectively coupled tropical waves.  
+Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized 
+context have been restricted to relatively small domain sizes and highly simplified physics parameterizations.  
+The result is a gap in the types of simulation for this region that is so important to our 
+understanding of clouds in the Earth's climate system.  
+%The Walker circulation embodies an ideal combination of physical processes that can help us to connect the findings from CRMs, 
+%GCMs, and the observed world.
+
+% Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
+% that transports so much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
+% Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
+% This region of the globe has been recognized to be of critical importance to the global energy budget 
+% for decades (Rhiel and Malkus ?, Pierrehumbert, 1995?)
+
+This work uses the framework of a mock-Walker circulation to simulate an overturning tropical circulation with 
+both a GCM-like model and a CRM-like model.
+ Idealized models of the Walker circulation were first called `mock-Walker circulations' by \citeA{Raymond_1994}.  
+\citeA{Raymond_1994} envisioned an idealized Walker circulation as,``a possible venue for testing ideas 
+about the interaction of dynamics, moist convection, and sea-air transfers that is simple enough to 
+be understandable, but rich enough to be interesting."
+Using the mock-Walker circulation as a tool to help distill the processes in complex climate models into 
+concrete understanding was also proposed by \citeA{Jeevanjee_etal_2017}.
+There have been many notable studies of the Walker Circulation \cite<e.g.,>[]{Geisler_1981, Raymond_1994, Grabowski2000, Tompkins_2001, Bretherton_Sobel_2002, Bretherton_etal_2006, Wofsy_Kuang_2012, Schwendike_etal_2014}.
+Previous studies have focused on observations \cite{Bjerknes1969, Schwendike_etal_2014}, theory \cite{Gill_1980, Geisler_1981, Raymond_1994,Bretherton_Sobel_2002}, or a combination of modeling and simple theory
+\cite{Grabowski2000, Sobel_etal_2004, Peters_Bretherton_2005, Bretherton_etal_2006, Wofsy_Kuang_2012,Kuang_2012}.  
+The modeling studies have primarily used models we refer to as Cloud-system 
+Resolving Models (CRMs; grid-spacing of less than 5km, no convective parameterization).  
+Multiple studies have presented elegant conceptual and theoretical models of the overturning tropical circulation 
+\cite{Raymond_1994, Pierrehumbert_1995, Larson_etal_1999, Bretherton_Sobel_2002}.  
+However, these simplified theoretical models of the circulation differ from each other in important details and 
+have different parameter dependencies.  
+Their simplicity helps to provide insight into those models, but is difficult to translate
+to the tropical climates produced by GCMs.  
+Most of these previous studies greatly simplify both the radiation and the representation of clouds.  
+They point to the importance of the interactions between clouds, radiation and the large-scale circulation while 
+avoiding much of the complexity of those processes.   
+%The work presented in this paper uses the full-physics of the recently developed GCM AM4.0
+%in a context usually reserved for CRMs as a means to create more overlap between these 
+%model types and help us to better understand the tropical climate.
+
+%Several elements distinguish this study from previous research on the Walker 
+%circulation.  
+Current climate models continue to be developed with an increasingly fine resolution and 
+the domain size used with CRMs continues to grow.  As a result the line between these two types 
+of models has become blurred and there is a need to systematically compare the clouds and their 
+influence on the climate produced by each type of model (Schneider et al., 2017).
+By simulating a mock-Walker Circulation in the context of both a GCM and a CRM we 
+illustrate how inextricable the interactions between clouds and radiation are to the coupling 
+of moisture with the large-scale circulation.     
+The model used here is based on the GFDL AM4.0 GCM that participated in CMIP6, 
+having a full suite of physics parameterizations.  
+%This includes fully interactive radiation and for the GCM-like cases convective parameterization 
+% for both deep and shallow convective clouds.  
+Rather than a full global domain all of our experiments use a doubly-periodic domain.  
+%We use fully interactive radiation 
+%(\citeA{Raymond_1994}; Tompkins, 2001; \citeA{Kuang_2012}; \citeA{Wofsy_Kuang_2012} used either fixed or gray radiative cooling).    
+The combination of a doubly periodic domain and a current generation climate model allow us to analyze the interactions of the 
+circulation and clouds in simulations with grid-spacing that ranges from 1km to 100km.  
+We thus study a full-physics GCM in an idealized context that is relevant to observed tropical systems, to theoretical
+models of the tropical circulation, and to many of the recent studies of radiative convective equilibrium (RCE).   
+%Our experiments with a grid-spacing of 1km have a higher resolution then the previous studies with CRMs.
+
+%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
+%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
+%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
+%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
+%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
+%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
+%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified 
+%SST. (just before equation 8 of Bretherton et al. 2006)."
+
+% Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
+% size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
+
+The broad goal of this paper is to clarify the two-way interactions between the Walker circulation and 
+the various cloud types that are prevalent in the tropical Pacific.   Our specific goal is
+to compare the Walker circulation and clouds simulated with a GCM-like model to analogous 
+simulations from a CRM-like model using one modeling framework based on a single code base. 
+This also serves as the framework with which we naively attempt to transition a GCM 
+towards a CRM.  Our initial motivation for using the 
+GFDL AM4.0 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
 in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
 would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
-interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
-of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
-range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.
-
-We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  To 
-show both the robust features of the simulations and the sensitive nature of the distribution of the precipitation maximum 
-we test the impact of convective parameterization, longwave radiation interactions with clouds, domain size, 
-and the resolution, or grid-spacing.  Elements of this study that distinguish it from previous research on the Walker 
-circulation are the use of fully interactive radiation, and the direct comparisons with a state-of-the-art general circulation
-model configuration.   Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
-size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
+interactions of the tropical Pacific and improve our ability to model this region in a GCM.    
+We perform a series of sensitivity experiments that highlight the different ways in which these experiments can equilibrate.  
+The climatology of the precipitation, both the amount and location, is particularly sensitive to changes in the configuration.   
+We demonstrate the impact to the mean state of convective parameterization, LW radiative interactions with clouds, domain size, 
+and the resolution, or grid-spacing.
 
 The paper is organized as follows.  Details of the model and the particular experiments used are described
-in the next section.  The longwave cloud radiative effect is an important element for all of the experiments and will be 
-discussed in all of the sections.   
-Section three describes the tendency of experiments with parameterized convection to settle into states which 
-do not mirror the symmetry of the prescribed sea surface temperature.   
+in the next section. Section three describes the tendency of experiments with parameterized convection 
+to settle into states which do not mirror the symmetry of the prescribed sea surface temperature.   
 Then, section four shows how the distribution of precipitation changes as a function of domain size.  
-Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration. 
-Conclusions from this study will then be summarized.
+Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration and
+section 6 includes a brief discussion and lists some of the impacts of the LWCRE and changing 
+resolution.  Conclusions from this study will then be summarized in the last section.   
+The LWCRE is an important element for all of the experiments and will be 
+discussed throughout the paper.
 
@@
 
+All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
+direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.  
+The domain is flat, not rotating, and has uniform and constant insolation.
+The lower boundary of the domain is a water covered surface with the SST prescribed as a time invariant Gaussian function 
+which is 4K warmer in the center (301K/27.85C) of the domain then 
+at the edges (297K/23.85C).  
 To develop the model configuration used for these experiments we started with the same code base as that of the 
-recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b}.
-%(Zhao et al. a,b).  
-This includes the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
-which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations.  
+recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b} (Z18a and Z18b hereafter).
+AM4.0 uses the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
+which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations
+over a wide range of resolutions.   
+Current generation global GFDL models use 
+a cubed-sphere grid that is composed of six tiles.  We use the model on a single doubly-periodic
+tile.  This allows the grid-spacing and domain size to be easily changed to minimize the cost of computations.
+This study focuses on experiments with grid-spacing of 100km, 25km, 2km, and 1km on several different
+sizes of domain.  Additional details are given in Table \ref{tab:experimentspecs}.
+
 The default AM4.0 physics we use includes interactive radiation, parameterized deep- and shallow-convection, 
 a large-scale cloud scheme, and a boundary layer 
-scheme as described in Zhao et al. a,b and the references therein.  The prognostic moisture variables are the specific 
+scheme as described in Z18a,b, and the references therein.  The prognostic moisture variables are the specific 
 humidity (q), liquid (ql) and frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
 levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
-8 model levels.  The changes made to the default AM4.0 physics configuration are the following.  The cloud-aerosol 
+8 model levels.  The changes made to the default AM4.0 physics configuration are as follows.  The cloud-aerosol 
 interactions were turned off to focus on the interaction between clouds, radiation, and the circulation.  The gravity wave drag 
@@
 as in AM4.0.   Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the 
-physics are very similar to those of AM4.0.  This configuration can also be compared to the simulations described in 
-\cite{Popp2017}, %Popp and Silvers, 2017, 
-which used a developmental version of AM4 with almost the same changes to the physics
-schemes.
+physics are very similar to those of AM4.0.  
+This configuration of AM4.0 physics was initially used by \citeA{Popp_Silvers_2017} and as the aquaplanet model that 
+was used as part of GFDL's contribution to the CFMIP component of CMIP6.
+
+% Time step information
+% Based on an earlier version of the experiments (see notes lgs_081318):
+%
+%    Grid Spacing                dt
+%.         1km                        5s
+%.         2km                       20s
+%.         25km                    600s
+%.       100km                    600s
+%
 
 \begin{table}
+
 \begin{center}
-\caption{Specifications of the simulations used most heavily in this study.  In the Convection
+\caption{Specifications of the simulations used most heavily in this study.  The length of time step is represented by `dt'.  In the Convection
 column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.
-All of the experiments listed here were also run with the longwave cloud radiative effect turned off.
-These will be referred to as P100L LWCRE off, etc.  }
-    \begin{tabular}{*{5}{c}}
+All of the experiments listed here were also run with the LWCRE turned off and are referred to as LWCRE-off.
+These will be referred to as P100L LWCRE-off, etc.  }
+    \begin{tabular}{*{6}{c}}
     \hline
@@
     \\
- Name & Grid Spacing $(\mathrm{km})$ & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection     \\ \hline
-  P100L &  100          &   800 $\times$ 16000    &  60              & prm                   \\ 
+ Name & Grid Spacing $(\mathrm{km})$ & dt (s) & Domain $ (\mathrm{km^2}) $& Length $(\mathrm{months}) $ & Convection     \\ \hline
+  P100L &  100      & 600    &   800 $\times$ 16000    &  60              & prm                   \\ 
     \\
-  P100 &  100                & 800 $\times$ 4000     & 60            & prm                     \\  
+  P100 &  100     & 600           & 800 $\times$ 4000     & 60            & prm                     \\  
     \\
-  P25L &  25             & 200 $\times$ 16000      & 60             & prm                     \\  
+  P25L &  25    & 600         & 200 $\times$ 16000      & 60             & prm                     \\  
     \\
-  P25  &  25             & 200 $\times$ 4000      & 60             & prm                   \\  
+  P25  &  25    & 600         & 200 $\times$ 4000      & 60             & prm                   \\  
     \\
- E25  &   25          & 200 $\times$ 4000      & 60             & expl                \\  
+ E25  &   25   & 600       & 200 $\times$ 4000      & 60             & expl                \\  
     \\
- E2   &   2          & 100 $\times$ 4000      & 6             & expl                   \\ 
+ E2   &   2   & 20       & 100 $\times$ 4000      & 6             & expl                   \\ 
     \\
- E1   &   1          & 10 $\times$ 4000      & 6             & expl                 \\  \hline
+ E1   &   1    & 5      & 10 $\times$ 4000      & 6             & expl                 \\  \hline
 
@@
     %\bigskip 
-    \label{tab:lambda}
+    \label{tab:experimentspecs}
 \end{center}
@@
 
-All simulations use a nonhydrostatic dynamical core, with prescribed SSTs and a doubly periodic domain which is elongated in the zonal 
-direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.  
-The SST is prescribed as a Gaussian function which is 4K warmer in the center (301K/27.85C) of the domain then 
-at the edges (297K/23.85C).  The GCM runs with 25km and 100km grid-spacing have been run for 5 years while the 
-1km and 2km experiments were run for 6 months.  Experiments with parameterized convection will be labelled with a P prefix, followed
-by a number indicating the grid-spacing in kms while the experiments with explicit convection and no parameterized convection will be 
+One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the radiation.  
+This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the 
+atmospheric state.   This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
+More recently, it has been
+implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
+In the AM4 code, this is done separately for the longwave (LW) and shortwave radiation.  
+In this study we compare control experiments, in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the LW radiation.  
+These experiments in which clouds do not interact with the LW radiation are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
+For the LWCRE-off experiments, both the LW and shortwave radiation are present and interact with 
+the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
+Turning off the LWCRE would have a large impact on the surface budget of a coupled model.  
+However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
+strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
+fixed SST are the ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
+the atmospheric state.
+
+The experiments with 100km and 25km grid-spacing have been run for 5 years while the 
+1km and 2km experiments were run for 6 months.  Experiments with parameterized convection are labelled with a P prefix, followed
+by a number indicating the grid-spacing in kilometers while the experiments with explicit convection (no parameterized convection) will be 
 labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
 grid-spacing of 25km, while E25 refers to an experiment that is identical to P25 except that the convective parameterization is turned off. 
-
-To illustrate the strong dependence of our results on domain size, as well as the fundamental role that the LW CRE plays in GCMs
-we utilize fully parameterized experiments with grid-spacing of 25km (P25) and 100km (P100) on domains with a long dimension 
-of 4000 km (`small') and
-16000 km (`large').  To explore the mock-Walker circulation in the context of both a GCM and a CRM we utilize 
+The naming convection for each of the experiments shown in Table \ref{tab:experimentspecs}.   
+Throughout this paper the P100 and P25 experiments, both with and without the LWCRE on are referred to as `GCM-like' and
+`CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
+Using the CRM-like terminology acknowledges that this model configuration has not been developed as a CRM, has a vertical resolution that is more coarse than other CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.
+
+To examine the dependence of our results on domain size, as well as the fundamental role that the LW CRE plays in GCMs
+we run the fully parameterized experiments (P25 and P100) on domains with a long dimension of 4000 km (`small') and 16000 km (`large').  
+To explore the mock-Walker circulation in the context of both a GCM and a CRM we utilize 
 comparisons of the experiments with grid-spacings of 25km (P25 and E25), 2km (E2), and 1km (E1) all on a domain with the same long dimension 
-of 4000 km.  The experiments with a grid-spacing of 25km serve as a link between the GCM-like configuration and the CRM-like 
+of 4000 km.  The experiments with a grid-spacing of 25km (P25 and E25) serve as a link between the GCM-like configuration and the CRM-like 
 configuration.  The only difference between these two experiments is that E25 has both the shallow and deep convective parameterizations turned 
-off so that all of the convection in that experiment is explicit, as it is in E2 and E1.  Domains with dimensions of 16000 km where judged too 
-costly for the 1km and 2km experiments.  Basic experimental details and the naming convection for the experiments are shown in Table 1.
+off so that all of the convection in that experiment is explicit, as it is in E2 and E1.  Domains with dimensions of 16000 km were judged too 
+costly for the 1km and 2km experiments.
 
@@
 to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  The primary 
-difference between the CRM simulations presented in this paper and those of more established CRMs such as SAM is that our model
-has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The \citeA{Tiedtke1993} 
-parameterization scheme for large-scale 
-clouds was designed to be used with GCMs having a coarse grid-spacing.  However, there is not a fundamental problem that we are 
-aware of in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   The advantage is retaining the 
-identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the cloud computations 
-relative to many other cloud resolving models.
+difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
+System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
+has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The large-scale cloud
+scheme is based on the \citeA{Tiedtke1993} parameterization.  This was originally designed to be used with GCMs having a coarse grid-spacing
+and includes prognostic equations for both cloud liquid water and cloud fraction.  
+However, we are not aware of a fundamental problem in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   
+The advantage is retaining the identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the 
+cloud computations relative to many other cloud resolving models.
 
@@
 or fraction of domain that is subsiding at the 532 hPa level.
-Values in parenthesis correspond to experiments whith LWCRE is off.}
+Values in parenthesis correspond to LWCRE-off experiments.}
     \begin{tabular}{*{5}{c}}
@@
     \\
- Name &   $\overline{\rm{P}} (\mathrm{mm/day})$ & $\overline{\rm{OLR}} (\rm{W \, m^-2})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
+ Name &   $\overline{\rm{P}} (\mathrm{mm \,d^{-1}})$ & $\overline{\rm{OLR}} (\rm{W \, m^{-2}})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
   P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.89 (0.61)      \\ 
@@
     %\bigskip 
-    \label{tab:lambda}
+    \label{tab:experimentmeans}
 \end{center}
 \end{table}
-
-One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the 
-radiation.  This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the 
-atmospheric state.   This method was originally pioneered by Slingo and Slingo, 1988 and Randall et al., 1989.  More recently, it has been
-implemented as part of the CFMIP series of experiments (Stevens et al. 2012, Webb et al., 2017).
-In the AM4 code, this is done separately for the longwave and shortwave radiation.  In this study we compare control experiments, 
-in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the longwave radiation.  These 
-experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE off).  
-For the LWCRE off experiments, both the longwave and shortwave radiation are present and interact with 
-the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
-Normally, turning off the longwave cloud radiative effect would have a large impact on the surface budget of a coupled model.  
-However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
-strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
-fixed SST are the ideal configuration to utilize the LWCRE off experiments as a way of diagnosing how clouds interact with 
-the atmospheric state.
-
-\section{The organizing influence of LWCRE and the asymmetric results of parameterized convection.}
-
-The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
-\ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
-SSTs and a humid boundary layer across the full length of the domain.    Large concentrations of condensate are 
-present in the mid-troposphere over the warmer SSTs, while the regions with subsiding circulations are 
-dry ($< 10\% RH$) above about $900 \rm{hPa}$.  The left panels of Figure \ref{fig:rh_psi_P25vsE25}  show that our 
-control GCM experiment has a stronger, more concentrated circulation with more condensate in the convective
-region and a dryer subsidence region, relative to the cases with the LWCRE off (middle panels) and with the
-convective parameterization off (right panels).
-
-%
-%It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
-%results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
-%relative to the case with the LWCRE-off.   A stronger and spatially concentrated circulation for cases when the 
-%clouds interact with the longwave radiation can also be seen in Figures 4, 5, 9 and 10 and is particular apparent in 
-%the cases with a large domain (16000 km long dimension).
-
-This state has the same fundamental characteristics as the Walker circulation, the Hadley Cell, and 
-experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations and 
-convective aggregation.
-
-\begin{figure}
-  \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan.eps}
-      \caption{Comparison of the steady state relative humidity (shading of top panels) and mass 
-      streamfunction (contours) for experiments
-      with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.  The lower panels 
-      show the total (liquid + ice) condensate (g/kg).  
-      An experiment with fully parameterized convection (P25) is on the left, the same 
-      experiment but with the LWCRE off is in the center panel, and the experiment with LWCRE on, but the convective
-      parameterization turned off is on the right (E25).  All three panels use the same contour interval for the mass 
-      streamfunction (kg/s).}
-  \label{fig:rh_psi_P25vsE25}
-\end{figure}
 
@@
 %parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).
-The mass streamfunction and vertical velocity both show the P25 experiment has a stronger overturning circulation 
-than either E25 or P25 LWCRE off.  P25 also has higher humidity in the deep convective region, and lower humidity in 
-the subsidence region over the 
-cooler SST (Figure \ref{fig:rh_psi_P25vsE25}) than either E25 or P25 LWCRE off.
-
-Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less 
-condensate (both liquid and ice) and with weaker radiative cooling and condensational heating (below 800 hPa).  
-However, in the updraft region the convective parameterization results in more moisture aloft.
-
-As the domain size increases, so does the domain mean precipitable water.  Active LWCREs lead
-to larger values of barPW in all cases (Table 2).  (Does this tell us anything about precipitation efficiency?)  
-It is also interesting to note that barPW varies by as much as 30\%.
-
-Superposing the circulation and relative humidity (as in Figure \ref{fig:rh_psi_P25vsE25}) illustrates the subsidence driven 
-drying and the strong moistening that results from ascent over the region of maximum latent heat flux.  
-Figure \ref{fig:rh_psi_P25vsE25} shows two distinct circulation cells with one below, and one above $500 \rm{hPa}$.  
-Deep-convective activity dominates the 
-region over the warm pool, shallow convection is common over a wider range of SSTs, and for the most part 
-stratocumulus clouds are absent (based on what?).  When the coupling between the circulation and clouds is 
-broken, by turning off the longwave CRE, the atmospheric state is much more symmetric about the maximum 
-SST.  We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, 
-and circulation (see Table 2).  In general the experiments with parameterized convection are much more erratic.
-
-One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry relative to the 
-symmetric SST distribution in both the time-dependent and 
-steady-state solutions (Figures \ref{fig:rh_psi_P25vsE25},  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}).  
-This asymmetry is also present in P25 experiments on larger domains and with a grid-spacing of $100 \, \rm{km}$. 
-The steady-state precipitation maximum is located  not over the warmest SST but is
-shifted to slightly cooler temperatures.  This asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, 
-specific humidity, and radiative heating.  
-In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse to 
-residing over the SST maximum.  
+
+\section{The Influence of Interactive Radiation on Clouds and the Organization of the mock-Walker Circulation}
+
+%\section{The radiative influence on the clouds and organization of the mock-Walker circulation}
+
+The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
+\ref{fig:precip_vertvel} to be characterized by a strong overturning circulation with precipitation focused over the warmer 
+SSTs and a humid boundary layer across the full length of the domain.    Superposing the circulation and relative 
+humidity (Figure \ref{fig:rh_psi_P25vsE25}) clearly shows the results of subsidence driven 
+drying over regions with cooler SST (at the edges of the domain) and the strong moistening that results from ascent over the region of high
+SST (in the center of the domain) where the latent heat flux is large.   The circulation is illustrated by the combination of 
+the mass streamfunction in Figure \ref{fig:rh_psi_P25vsE25} and the vertical velocity in Figure \ref{fig:precip_vertvel}.   
+The mass streamfunction illustrates the 
+two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
+High concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
+circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
+Two distinct circulation cells are present with one below, and one above $500 \, \rm{hPa}$.   
+%Deep-convective activity dominates the region over the warm pool, shallow convection is common 
+%over a wider range of SSTs, and for the most part stratocumulus clouds are absent.
+It is worth noting that this state of deep overturning circulation with convection 
+and precipitation concentrated in the region of ascent and a dry troposphere in the regions of descent is common
+to the Walker circulation, tropical two-box models (e.g. Pierrehumbert, 1995, Larson et al., 1999), and 
+experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations 
+and convective aggregation (e.g. Bretherton et al., 2005).
+
+When the coupling between the circulation and clouds is broken by making the clouds invisible to the 
+LW radiation, the atmospheric state is more symmetric about the maximum SST and the weaker circulation
+is more spread out horizontally.   The mass streamfunction and vertical velocity both show the 
+P25 (Figure \ref{fig:rh_psi_P25vsE25}, left panels; Figure \ref{fig:precip_vertvel}) experiment to have 
+a stronger, more concentrated overturning circulation than either E25 (right panels) or P25 LWCRE-off (center panels).   
+The control GCM experiment (P25) also has higher RH and more condensate in the convective
+region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
+Averaged over the full domain, the P25 case with paramterized convection results in a 
+dryer atmosphere with less condensate (both liquid and ice). 
+%and with weaker radiative cooling and condensational heating (below 800 hPa). 
+A stronger and spatially concentrated circulation for cases when the clouds interact with the LW 
+radiation can also be seen in Figures 4, 5, 9 and 10 and is particularly apparent in 
+the cases with a large domain (16000 km long dimension).   
+We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, 
+and circulation (see Table \ref{tab:experimentmeans}).  In general the experiments with parameterized convection are much more erratic. 
+Active LWCRE also leads to lower
+values of domain mean OLR and higher domain mean precipitable water (PW) in all cases.
+
+%
+%It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
+%results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
+%relative to the case with the LWCRE-off.
+
+\begin{figure}
+  \centering
+      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan_new.eps}
+      \caption{The equilibrated state of the Walker cell for three configurations with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.
+      Shown in the top panels is the relative humidity (shading) and mass streamfunction (black contours).
+      The same contour interval for the mass 
+      streamfunction (kg/s) is used in all panels.
+      The lower panels show the total (liquid + ice) condensate (g/kg).  
+      Deep and shallow convection are fully parameterized (P25) in the panels on the left, the center panels show P25 LWCRE-off, 
+      and the experiment with LWCRE on, but the convective
+      parameterization turned off is on the right (E25).}
+  \label{fig:rh_psi_P25vsE25}
+\end{figure}
+
+%
+One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry (relative to the 
+symmetric SST distribution) in both the time-dependent and steady-state solutions.  
+This asymmetry is also present in P25 experiments on larger domains and with a grid-spacing of $100 \, \rm{km}$ 
+(Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
+The steady-state precipitation maximum is located  not over the warmest SST but is shifted to slightly cooler temperatures.  
+This asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.  
+In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse 
+to residing over the SST maximum.  
 For the P25 case shown in Figure \ref{fig:rh_psi_P25vsE25} a strong ($1 \, \rm{m \, s^{-1}}$) domain
-mean shear develops above about 500 \textit{m} which shifts the precipitation and circulation off center for years at a time.
-When the convective parameterization is turned off (E25), the overturning circulation becomes weaker and 
-broader (w, and psi), and the precipitation, cloud fields, and 
-circulation all consistently reside over the SST maximum (for about 1 year before going haywire).   
-While the parameterized convection plays a large role in driving this asymmetry it appears to be not entirely a 
+mean shear develops above about 500 m which shifts the precipitation and circulation off center for years at a time.  
+When the convective parameterization is turned off (E25), the overturning circulation 
+becomes weaker and broader (seen in w, and the mass streamfunction), and the precipitation, cloud fields, and 
+circulation reside over the SST maximum (but only for about 1 year before the variability 
+increases).    
+While the parameterized convection plays a large role in driving this asymmetry, it appears to be not entirely a 
 result of the convective parameterization, but also due to an interaction between the convective 
-parameterization and the LWCRE.   The degree to which this asymmetry influences the comparison with other experiments is 
-unclear.
-
-Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted many times in 
-previous literature \cite{Bretherton2006, Wofsy2012} (Ming Zhao, see Jeevanjee et al. 2018)
-but the irregularities have 
-tended to be symmetric about the SST maximum.  This is broadly consistent with our simulations when the convection is 
-entirely explicit (E25, E2, and E1, discussed further in section 4), but strikingly different than for P25.
+parameterization and the LWCRE.   The degree to which this asymmetry influences the comparison with other 
+experiments is unclear.
+
+Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted 
+many times in previous literature \cite{Bretherton_etal_2006, Wofsy_Kuang_2012}; Ming Zhao, see \citeA{Jeevanjee_etal_2017}
+but the irregularities have tended to be symmetric about the SST maximum.  This is broadly consistent 
+with our simulations when the convection is entirely explicit (E25, E2, and E1, discussed further in section 
+4), but is strikingly different than for the P25 and P100 experiments.
 
@@
 
-% LWCRE has a large impact on LS precip, not so much on convection
+% LWCRE has a large impact on LS precip, not so much on convective precipitation
 % LWCRE has a large impact on the low-level circulation (circulation is stronger when LWCRE is on)
@@
   \centering
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
+      \includegraphics[width=0.8\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
   \caption{Precipitation (top) and vertical velocity (bottom) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
-  The data has been averaged over the short horizontal dimension of the channel and over the 
-  equilibrated part of the experiments.  Control configurations with normal model physics are on the 
+  The data have been averaged over the short horizontal dimension of the channel and over the 
+  equilibrated part of the experiments.  Control configurations with default model physics are on the 
   left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
@@
   \centering
-      \includegraphics[width=0.6\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+      \includegraphics[width=0.8\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
   \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
-  Thick lines are the control experiments, thin lines have no LW CRE.  All data is shown for the E1 and E2 cases
+  Thick lines are the control experiments, thin lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 cases
   while the P25 and P100 cases show only the first out of five years of the time series.}
@@
 Despite the same boundary conditions and model base, the experiments documented here have a
-large range of domain mean precipitation ($\rm{\overline{P}}$, Table 2) that varies by as much as 
+large range of domain mean precipitation ($\rm{\overline{P}}$, Table \ref{tab:experimentmeans}) that varies by as much as 
 0.6 $\rm{mm/d}$ (3.5-4.1 in parameterized experiments; 3.1-3.7 in explicit experiments).
@@
 the total radiative cooling, the time evolution of the precipitation serves as a useful measure of whether a model has 
-reached statistical equilibrium.  Figure \ref{fig:precip_dom_mn} demonstrates that this equilibrium is reached after about 30 
+reached a state of stationarity, or statistical balance.  Figure \ref{fig:precip_dom_mn} demonstrates that this equilibrium is reached after about 30 
 days for the E2, and E1 simulations, and after about 50 days for the P25 and P100 simulations.   After the initial adjustments
 the simulations all oscillate about mean precipitation values which tend to increase with the grid-spacing 
-(Table 2).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
+(Table \ref{tab:experimentmeans}).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
 about the domain mean precipitation is smaller helps to justify the 6 month simulation times for E1 and E2.  
@@
 The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-\cite{Silvers2016, Patrizio2019}
+\cite{Silvers2016, Patrizio2019}.
 %(Silvers et al., 2016; Patrizio and Randall, 2019).   
@@
 overturning circulation 
-(e.g. Popp and Silvers, 2017, Harrop and Hartmann, (Muller and Held?), Albern et al., 2019).  This is 
+\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}; Li et al??).  This is 
 due to an increased low-level flux
@@
 convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
-region of persistent deep convection and a state of aggregation.   One of the simplest measures of convective 
-aggregation and the large-scale circulation is the fraction of the domain in which the air is subsiding, the 
-subsidence fraction (SF).  As convection becomes more organized, or aggregated, the SF will increase.  We expect 
+region of persistent deep convection and a state of aggregation (work in a citation of M{\"u}ller and Hohenegger, 2019).   
+\textit{RCE studies showing convective self-aggregation have illustrated the 
+dependence of the details of the aggregation on the domain size, the physics, or other details of the 
+study.  Using a mock-Walker circulation allows one to study controlled convective aggregation rather 
+then spontaneous convective self-aggregation.  The added constraint of the fixed warm-patch could lead 
+to clarification of the processes that drive important atmospheric interactions.}
+One of the simplest measures of convective aggregation and the large-scale circulation is the fraction of the domain 
+in which the air is subsiding, referred to as the subsidence fraction (SF).  
+As convection becomes more organized, or aggregated, the SF will increase.  We expect 
 for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
-fraction.  This is precisely what we see in Table 2.  For each of our experiments, the cases with LWCRE-on
+fraction.  This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments, the cases with LWCRE-on
 have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
-dependence of aggregated atmospheric states on temperature (\citeA{Khairoutdinov2010}; \citeA{Wing2014}).  
+dependence of aggregated atmospheric states on temperature (\citeA{Khairoutdinov2010}; \citeA{Wing2014}; Cronin and Wing, 2017).  
 While there does appear to be a dependence 
-on temperature, Table 2 illustrates how much the aggregated 
+on temperature, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
 state can vary among experiments with identical SST.  Having a prescribed SST warm 
-patch ensures that the simulations will be `aggregated' to some degree.  Rather than indicating whether an 
-experiment is aggregated, the SF here measures the spatial extent of the overturning circulation.  The SF provides a 
-simple way of quantifying the degree of organization that is present.  Given identical SSTs, the  range of 
-different SFs provide a measure of variability that is driven entirely by the interactions between 
+patch ensures that the simulations will be `aggregated' to some degree.  
+The SF indicates not only whether an 
+experiment is aggregated, but also the spatial extent of the overturning circulation.  
+Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
 convection, radiation, and the large-scale circulation.
 
-\section{The Influence of Domain Size on the LWCRE and the LS Parameterized Precipitation: Change Title?}
+\section{The Influence of Domain Size on Low-level Clouds and the Large-scale Precipitation}
 
@@
 long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
-\cite{Bretherton2005, Bretherton2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
+\cite{Bretherton2005, Bretherton_etal_2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
 have documented sensitivities of the equilibrated state to domain size for similar experiments
 of radiative convective equilibrium.   
-The analysis of the previous, and of the next sections focus on results from 
+The analysis of the previous, and of the next, sections focus on results from 
 experiments using a domain with a long domain length of $4,000 \, \rm{km}$.  However when comparing those results
@@
 The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
-function of domain size, parameterization of convection, and the effect of the longwave radiation due to clouds. 
+function of domain size, parameterization of convection, and the effect of the LW radiation due to clouds. 
 Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovm{\"o}ller plots of precipitation after 
 averaging along the short horizontal dimension.  The four panels show simulations with a grid-
-spacing of $25\, \rm{km}$ on a domain with a horizontal width of $4000\, \rm{km}$ (far right) and $16000\, \rm{km}$ 
-(middle right), and 
-simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal width of $4000\, \rm{km}$ (middle left) and 
-$16000\, \rm{km}$ (far left).  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
+spacing of $25\, \rm{km}$ on a domain with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$, and 
+simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and 
+$16000\, \rm{km}$.  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
 
@@
 precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
-strengthen an overturning circulation and
-narrow the region of deep convection (see Popp and Silvers, 2017, Harrop and Hartmann, Dixit et al. 2019.  etc.).
-The structure of the precipitation changes more as a function of domain size than it does as a function of resolution. 
-On the large domains, the difference between experiments with and without LWCRE is extreme.  In contrast to the control 
-experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong precipitation 
-meandering within 500 km of the SST maximum at the center of the domain,  
-the experiments without the LWCRE basically have no region with consistently strong precipitation.  Instead, 
-smaller cells or lines of precipitation develop within an area that is roughly 8000 km wide.  As previously noted, 
-these GCM-like simulations equilibrate after approximately 50 days.  However, there is also a dramatic change in 
+strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
+\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  The structure of the precipitation changes more 
+as a function of domain size than it does as a function of resolution. 
+On the large domains, the difference between experiments with and without LWCRE is extreme.  
+In contrast to the control experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong 
+precipitation meandering within about 500 km of the SST maximum at the center of the domain,  the large domain experiments 
+without the LWCRE have an 8000 km wide region in which the precipitation consistently develops (Figure {\ref{fig:domdep_lwoff}).  
+Smaller cells and lines of precipitation develop within this large area with no apparent preference to settle
+over the center of the domain where the SST is a maximum.  As previously noted, 
+these GCM-like simulations equilibrate after approximately 50 days.  There is also a dramatic change in 
 the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
@@
 
-An additional unexpected change that results from increasing the domain width is an upward shift of the cloud fields.  This is 
+An additional unexpected change that results from increasing the domain size is an upward shift of the cloud fields.  This is 
 shown with the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low level maximum of 
@@
 pronounced.  
+As the domain size increases, so does the domain mean precipitable water ($\overline{\rm{PW}}$).  Active LWCREs lead
+to larger values of $\overline{\rm{PW}}$ in all cases (Table \ref{tab:experimentmeans}).  
+%(Does this tell us anything about precipitation efficiency?)  
+$\overline{\rm{PW}}$ varies by as much as 30\% among the experiments.
 
@@
 \begin{figure}
-  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
+ % \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
+  \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwon_huge.eps}
   \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
-  25km and 100km.  From left, large domain 100km, (P100L); 
-  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
-  For each resolution, the only difference between the two experiments shown is a domain length of 
-  16,000 km or 4,000 km.}
+  25km and 100km.  Panel A shows the 100km experiment on the large domain 100km, (P100L); 
+  B, 25km on large domain, (P25L); C, 100km on small domain, (P100); and D, 25km on small domain 
+  (P25).  For each resolution, the only difference between the two experiments shown is a domain length of 
+  16,000 km or 4,000 km.
+All cases have an SST of 301 K at the center and 297K at the edges.
+The plotted values are: 1,5,10,15,20,30,40,50,60,70,80,90.
+Data have been averaged over the short horizontal dimension.}
   \label{fig:domdep}
@@
 \begin{figure}
-  \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
-  \caption{Identical to previous figure, except that LW CRE is now off.  Evolution of precipitation through 
-  3 years of simulation.  From left, large domain 100km, (P100L); 
-  small domain 100km, (P100); large domain 25km, (P25L); small domain 25km (P25).  
-  For each resolution, the only difference between the two experiments shown is a domain length of 
-  16,000 km or 4,000 km.}
+  %\includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
+  \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwoff_huge.eps}
+  \caption{Identical to previous figure, except that the clouds do not interact with the longwave radiation; the LWCRE is off.}
   \label{fig:domdep_lwoff}
@@
        \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice) for P100 (red) and P25 (yellow) on the domain 
+          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P100 (red) and P25 (yellow) on the domain 
           with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
-          and dashed lines experiments with LWCRE off.}
+          and dashed lines the LWCRE-off experiments.}
   \label{fig:TotCond_P25P100}
@@
 in a GCM is being distributed among the parameterizations, and what is triggering the precipitation.  
-Precipitation from each of these two components isshown in Figure \ref{fig:conv_vs_ls} as a function of 
+Precipitation from each of these two components is shown in Figure \ref{fig:conv_vs_ls} as a function of 
 both resolution and domain size.  In the regions of large-scale ascent, most of the precipitation derives 
@@
 The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low level cloud radiative
-effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction.  
-We also demonstrate that it is through the longwave cloud radiative effect that this connection is enabled.
+effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction (check 
+the figures that show convective and large-scale precip separately).  
+\textit{We also demonstrate that it is through the LW cloud radiative effect that this connection is enabled.}
+The low-level clouds are strongly influenced by both the size of the domain and by the LW cloud 
+radiative effect.  The fact that the partitioning of precipitation by the convective and large-scale 
+parameterizations depends on both the size of the domain and the longwave cloud 
+radiative effect could imply that the changes of the low-level clouds are being driven largely by 
+sensitivities of the parameterized physics.
 
@@
   \centering
-      \includegraphics[width=0.8\columnwidth]{walkerfigs/Conv_vs_LS_hist.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/Conv_vs_LS_Precip.eps}
   \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective 
-  parameterization (black).  Experiments with the LW CRE off are shown with thin lines.  
+  parameterization (black).  
   Panels on the left show large domains with a width of 16000 km and
-  panels on the right show domains with a width of 4000 km.}
+  panels on the right show domains with a width of 4000 km.  LWCRE-off experiments are shown with dashed lines.  }
   \label{fig:conv_vs_ls}
@@
 
-Smaller domains were found to have a more focused ascent region and larger precipitation rates in B06.
+Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
 They also found less low-level clouds over the colder SSTs in the small domains (1,024 km wide), relative 
-to a control domain with a width of 4,096 km.   In contrast, here larger domains have larger precipitation rates (Table 2).  
+to a control domain with a width of 4,096 km.   In contrast, here larger domains have larger precipitation 
+rates (Table \ref{tab:experimentmeans}).  
 We find fewer low-clouds on the large domain experiments (P25L, P100L), but a mid-level cloud 
@@
 %General Circulation Model to a Cloud Resolving Model}
-\section{Dependence on Resolution: From a General Circulation Model to Cloud Resolving}
+\section{From a General Circulation to Cloud Resolving Model: Dependence on Resolution}
 
 \begin{figure}
-  \includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
-  \caption{Evolution of precipitation through the first 6 months of simulation for (left to right) the 25km control case (P25), 
-  25km case with no parameterized convection (E25), 2km control (E2), and 1km control (E1).  
-  Shading indicates mm/day.  The horizontal axis shows the entire 
-  longitudinal domain of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
-  Shown is the average over the small dimension of the channel domain. } 
+  %\includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
+  \includegraphics[width=0.96\columnwidth]{walkerfigs/hov_precip_25vs2vs1_6mn_huge.eps}
+  \caption{Evolution of precipitation through the first 6 months of simulation for (a) the 25km control case (P25), 
+  (b) 25km case with no parameterized convection (E25), (c) 2km control (E2), and (d) 1km control (E1).  
+  The horizontal axis shows the entire longitudinal width of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  Data have been averaged over the short horizontal dimension.} 
   \label{fig:hov_4mods_6mn}
@@
 
-% ..... moved to introduction .... 
-%Overturning circulations in the tropical Pacific atmosphere encompass dynamical motions at a host of scales 
-%and the different cloud types interact with the circulation on scales ranging from meters to thousands of km's.  
-%The tropical Pacific is an ideal location to study interactions between clouds and the circulation 
-%because it combines strong overturning circulations, abundant shallow cumulus, congestus, and cumulonimbus 
-%clouds \cite{Johnson1999}, as well as stratocumulus cloud decks along the eastern extremities of the basin.
-%Can we hope to simulate all of this in a single idealized modeling context?   Our initial motivation for using the 
-%GFDL AM4 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
-%in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
-%would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
-%interactions of the tropical Pacific and improve our ability to model this region in a GCM.    The dynamical core 
-%of the current generation GFDL models is ideally suited to this task because it can easily be used over a wide 
-%range of resolutions and can solve either the hydrostatic or nonhydrostatic governing equations.
-
 \begin{figure}
   \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1.eps}
+      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwon_new.eps}
       \caption{The equilibrated state of the Walker cell as a function of resolution.  
@@
   \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
+      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
+      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff_new.eps}
           \caption{Same as previous figure except with the longwave CRE turned off.}
@@
 
-We now show results that resulted from our motivation to simulate a tropical Pacific-like region 
-in the context of both a GCM and a CRM.  In this section we focus on simulations with grid-spacing of 
-1km, 2km, and 25km all in a domain with a width of 4,000 km.  Overall there is good agreement on 
-the basic circulation pattern, distribution of mid-tropospheric condensate, and sensitivity of the surface
-enthalpy flux to low-level winds.  However, the E25/P25 simulations produce much more low-level cloud
-and as a result have a different response to the LWCRE.  The low-level differences among the models
-result in different spatial distributions and amounts of precipitation.
-
-A glance at Figure \ref{fig:hov_4mods_6mn} shows notable differences in the precipitation structure that result from the 
-overturning circulation at different resolutions.  Shown are 180 days of precipitation from the P25, E25, E2, and 
-E1 simulations.  As the resolution increases the distribution of precipitation becomes more regular and consistently 
-centered over the SST maxima in the middle of the domain.  Both the P25 and E25 simulations show more 
-variability at later times compared to these first 180 days (similar to what is seen in Figure \ref{fig:domdep_lwoff} 
-for the P25 and P100 LWCRE off experiments).  The simulations with explicit convection at resolutions 
-typical of cloud-resolving models (E2, E1) show little aversion to the precipitation maximum occurring over 
-the maximum in SST and relative to the P100, P25 and E25 simulations they are able to maintain a 
-smoother distribution of  precipitation over a broader range of SST values.
+We now show results from our simulations of a mock-Walker circulation with both a GCM-like and a CRM-like configuration.  
+In this section we focus on simulations with grid-spacing of 
+1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
+The models agree on 
+the basic circulation pattern and the spatial distribution of mid-tropospheric condensate.  
+However, the E25/P25 simulations produce 4 to 5 times as much low-level cloud and 
+condensate as E2/E1 in the subsiding regions.   As a result the models have a different response 
+to the LWCRE.  The differences in the boundary layer of the wind, enthalpy flux, and 
+temperature among the models result in different spatial distributions and amounts of 
+precipitation in the equilibrated state.
+
+Notable differences in the precipitation structure that result from the overturning circulation at different resolutions are shown in Figure \ref{fig:hov_4mods_6mn}.  
+Shown are 180 days of precipitation from the P25 (left to right), E25, E2, and E1 simulations.  
+As the resolution increases the distribution of precipitation becomes more regular and consistently centered over the SST maxima in the middle of 
+the domain.  Both the P25 and E25 simulations show more variability at later times compared to these 
+first 180 days (similar to what is seen in Figures \ref{fig:domdep}  and \ref{fig:domdep_lwoff} for the P25 and P100 LWCRE-off).  
+The simulations with explicit convection at resolutions typical of cloud-resolving models 
+(E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST.
+Relative to the P100, P25 and E25 simulations, the cloud resolving simulations are able to maintain a smoother distribution of 
+precipitation over a broader range of SST values.
 
 The influence of resolution on the atmospheric state can be clearly seen in the two-dimensional structure 
-of circulation and humidity.
-The steady state relative humidity and overturning circulation show both similarities and differences
-among the experiments at varying resolutions with and without LWCRE (Figures \ref{fig:rh_psi_P25E2E1} and 
-\ref{fig:rh_psi_P25E2E1_lwoff}).
+of circulation and humidity (Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
+%The steady state relative humidity and overturning circulation show both similarities and differences
+%among the experiments at varying resolutions with and without LWCRE .
 Perhaps the most obvious similarity is the double celled structure in the mass streamfunction and the most 
-obvious difference being the difference in humidity of 40\% between E1, E2, and E25 in the center of the domain.  
+obvious difference being the humidity in the center of the domains (RH range of $>$ 40\%). % among E1, E2, and E25.  
 %The mid-troposphere 
@@
 All experiments show a mid-tropospheric relative humidity minimum over the cooler SSTs where subsidence 
-dominates.  The multicelled structure is quite irregular in the P25 experiment, and a small third cell has 
-developed in the boundary layer of the 1km experiment.   The high resolution experiments also have 
+dominates.  The E25 experiment has a fairly symmetric double celled structure in stark contrast to the irregular circulation 
+that is present in the P25 experiment (compare with Figure \ref{fig:rh_psi_P25vsE25}). 
+A small third cell has developed in the boundary layer of the 1km experiment.   The high resolution experiments also have 
 higher amounts of condensate throughout the troposphere, and much higher relative humidity 
-above about 300 hPa.
+above 200 hPa.
 
@@
        \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice) for P25 (thin yellow), E25 (yellow), 
+          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P25 (thin yellow), E25 (yellow), 
           E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on
-          and dashed lines experiments with LWCRE off.  All lines correspond to experiments with explicit 
+          while dashed lines show the LWCRE-off experiments.  All lines correspond to experiments with explicit 
           convection.}
@@
 \ref{fig:rh_psi_P25E2E1_lwoff} also shows that the E2 and E1 simulations are much more 
-similar when the clouds and radiation interact than they are with LWCRE-off.  In particular, the subsidence 
-region drying and condensate aloft in the upwelling region have a clearer dependence on resolution when 
-the LWCRE is off.  This suggests that the interactions between clouds and radiation help the 
-atmospheric state converge towards a particular solution.
-
-The domain mean condensate is an important measure of the steady state reached by these experiments.  The vertical 
-distribution of condensate is closely related to the distribution of clouds.  This in turn influences the distribution and
-flow of energy throughout the atmosphere and the longwave radiation that is emitted to space.  It can also indicate the 
-strength of convection and vertical mass transport.     
+similar when the clouds and radiation interact than they are with LWCRE-off.  However, the subsidence 
+region drying and condensate aloft in the upwelling region have a clearer dependence on resolution for the
+LWCRE-off experiments.  This suggests that the interactions between clouds and radiation help the 
+atmosphere to converge towards a particular state that is less dependent on resolution.
+
+The domain mean condensate is closely related to the distribution of clouds and is an important measure of the 
+steady state reached by these experiments.  This in turn influences 
+the distribution and flow of energy throughout the atmosphere and the radiation that is emitted to space.  
+It can also indicate the strength of convection and vertical mass transport.     
 Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE-off (dashed lines).  Profiles for the experiments
+(solid lines) and the corresponding experiments with the LWCRE-off (dashed lines).  Similar profiles for the experiments
 with parameterized convection were discussed in the previous section (Figure \ref{fig:TotCond_P25P100}).  
-There is a significant difference 
-between the GCM-like P100, P25 and E25 experiments and the CRM-like E2 and E1 experiments with the former having much 
-higher values of low-level liquid condensate/cloud and the later having much higher values of upper level ice 
-condensate.  \citeA{Pauluis2006} showed that for decreasing resolution an RCE model had a moist bias in the 
-sub-cloud layer and a dry bias in the troposphere above.  Although our experiments are not strictly in RCE, our 
-results agree with those from \citeA{Pauluis2006}.
-
-Examining the LWCRE reveals an interesting difference between the coarse experiments with parameterized convection
-and the CRM-like experiments.  Interactive LWCRE leads to less upper level ice-condensate for our CRM experiments
-with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  The opposite occurs for the 
-GCM-like experiments.  The interactive LWCRE increases the amount of upper level ice-condensate 
-(Figure \ref{fig:TotCond_P25P100}).    The influence of the LWCRE on low-level clouds is consistent for both the 
-GCM-like and CRM-like experiments.  The LWCRE leads to more low-level clouds/condensate although the 
-increase is very slight for the E1 and E2 experiments.  Overall, the LWCRE-off experiments influence the low-levels 
-of the GCM-like experiments, and the upper-level regions of the CRM-like experiments.
+There is a substantial difference between the GCM-like P100, P25, and E25 experiments and the CRM-like E2 and E1 experiments 
+with the former having much higher values of low-level liquid condensate and the later having much higher values of upper level ice condensate.
+Although our experiments differ from RCE, the results are consistent with \citeA{Pauluis2006} who showed that for
+decreasing resolution an RCE model had a moist bias in the sub-cloud layer and a dry bias in the troposphere above.  
+%Although our experiments are not strictly in RCE, our results agree with those from \citeA{Pauluis2006}.
+
+Comparing experiments with and without the LWCRE highlights key differences between our GCM and CRM experiments.  
+The upper panels of Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show that the 
+interactions between LW radiation and clouds lead to an enhanced
+drying of the troposphere in regions of subsidence, relative to the cases when the LWCRE is not active.  
+This is especially true for the simulations with a grid-spacing of 1 km and 2 km.  
+Interactive LWCRE leads to less upper level ice-condensate for our CRM experiments
+with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  
+The opposite occurs with GCM-like experiments (Figure \ref{fig:TotCond_P25P100}) for which interactive LWCRE increase 
+the amount of upper level ice-condensate.    
+%The influence of the LWCRE on low-level clouds is consistent for both the 
+%GCM-like and CRM-like experiments.  
+Below about 700 hPa turning off the LWCRE leads to a strong decrease in condensate
+in the GCM experiments, but a negligible decrease in the condensate of the CRMs.    
+The profiles of diabatic cooling are similar among all LWCRE-off experiments.  
+But when the LWCRE is on, the GCM like experiments have up to twice as much diabatic cooling as the GCM like experiments below 850 hPa.
+%While the mid-tropospheric 
+%profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
+%response below about 850 hPa for the 25km and 100km models.  
+%At that grid-spacing, with the LWCRE on, significant low-level 
+%clouds are formed, leading to a radiative cooling on the order of -10K/day.   
+%However, when the LWCRE is off the radiative cooling decreases to - 3-5 K/day and there is little appreciable 
+%difference in the low-level diabatic profiles among the 
+%P100, P25, E25, E2, and E1 experiments.   
+%It is also clearly seen that the LWCRE decreases the upper-level ice-condensate 
+%for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and 
+%P25 (Figure \ref{fig:TotCond}).  
+The LWCRE plays a major role in determining the equilibrium RH, total condensate, and LW radiative 
+heating of the troposphere.  However the manifestations of interactions between clouds and radiation as indicated
+by these characteristics differ dramatically between the GCM and CRM experiments.   
+%Overall, the LWCRE-off experiments influence the low-levels 
+%of the GCM-like experiments, and the upper-level regions of the CRM-like experiments.
 
@@
   \centering       
-    \includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
-    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
-    For all panels, thick lines show control experiments with the LW CRE on, thin lines show experiments
-    with the LW CRE off.}
+    %\includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
+    \includegraphics[width=0.96\columnwidth]{walkerfigs/lowlevel_New.eps}
+    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection for experiments
+    with explicit convection.  The surface enthalpy flux (a) is the latent plus sensible heat flux.  Panels b and c show 
+    the equivalent potential temperature (b) and zonal wind (c) at the lowest model level in the atmosphere.  Panel 
+    d shows the domain mean zonal wind throughout the depth of the domain.}
     \label{fig:enthalpy}
@@
 Despite a fairly regular distribution of precipitation around the SST maximum for experiments with increasing resolution, the 
-surface enthalpy flux reveals large differences in the symmetry of the near surface energetics.   
+surface enthalpy flux (latent plus sensible heat fluxes) reveals large differences in the symmetry of the near surface energetics.   
 Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
@@
 half of the domain.  These differences in magnitude and regularity are apparently due to differences in the low-level 
-wind speeds among the experiments.  When the LWCRE is off, the difference in the enthalpy flux between E25 and E2/E1 
+wind speeds among the experiments.  For the LWCRE-off experiments, the difference in the enthalpy flux between E25 and E2/E1 
 over the warmest SSTs is reduced from $60 \, \rm{W/m^2}$ to about $20 \, \rm{W/m^2}$ and the enthalpy
-flux for E1and E2 become very similar over the warmest SSTs.   Thus even for the case of prescribed SSTs and no
-land surface the interactions between clouds and the longwave radiation have a massive influence on the 
+flux for E1 and  E2 become very similar over the warmest SSTs.   Thus even for the case of prescribed SSTs and no
+land surface the interactions between clouds and the LW radiation have a massive influence on the 
 surface energy budget.
@@
 It is also interesting to note that despite stronger low-level winds, E25, E2, and E1 all have a weaker surface
-enthalpy flux when the clouds and radiation are interactive.  This is initially surprising because as represented 
+enthalpy flux when the clouds and radiation are allowed to interact.  This is initially surprising because as represented 
 by bulk parameterizations, both the sensible heat flux and the latent heat flux are directly proportional to the 
@@
 implies that the gradient of moisture and temperature is smaller when the LWCRE is active and thus accounts 
-for the lower surface enthalpy flux relative to when LWCRE is off.         
+for the lower surface enthalpy flux relative to the LWCRE-off experiments.         
 It is also worth noting that in contrast to the P25 case which has strong domain mean shear, E25 has less domain 
@@
       \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
-  \caption{Cloud fraction and temperature tendency due to longwave radiation.  Profiles were computed in the 
+  \caption{Cloud fraction (CF) and temperature tendency due to longwave radiation (tdtlw).  Profiles were computed in the 
   subsidence regions and are shown for the control (LWCRE-on) and LWCRE-off experiments.}
@@
 
-An interesting point that emerges from the domain mean values of precipitation (see Table 2) 
+An interesting point that emerges from the domain mean values of precipitation (see Table \ref{tab:experimentmeans}) 
 is that the sign of the response to LWCRE is not the same between CRM and GCM experiments.
-When clouds are not allowed to interact with the longwave radiation the atmosphere 
+When clouds are not allowed to interact with the LW radiation, the atmosphere 
 emits more radiation to space, as evidenced by larger values of $\overline{\rm{OLR}}$ 
-for all experiments when the LWCRE is off.  Atmospheric radiative cooling can be thought of 
-as a proxy for the mean precipitation because the cooling is balanced primarily by 
-condensational heating.  Larger values of $\overline{\rm{OLR}}$ would correspond to 
+for all LWCRE-off experiments.  Atmospheric radiative cooling can be thought of 
+as a proxy for the mean precipitation because the cooling is usually balanced primarily by 
+condensational heating.  Larger values of $\overline{\rm{OLR}}$ would then correspond to 
 larger values of $\overline{\rm{P}}$.  This is clearly not the case for the E25, P25, and 
-P100 experiments.   \textit{The domain mean precipitation rates decrease despite an increased 
-amount of atmospheric cooling.}  The implication is that the requisite atmospheric heating 
+P100 experiments.   The domain mean precipitation rates decrease despite an increased 
+amount of atmospheric cooling.  The implication is that the requisite atmospheric heating 
 must come from a process other than condensation.
 
-The solution lies in the energy budget of the surface.  Prescribed SST means that the upward flux of 
-longwave radiation is constant.  The upward flux of sensible heat flux will be mostly fixed 
-(barring variations in surface
+Examining the energy budget of the surface and the role played by the low-level clouds
+reveals the source of the extra atmospheric heating for the E25, P25, and 
+P100 experiments.  
+Prescribed SST generates an upward flux of LW radiation that is constant.  
+The upward flux of sensible heat flux will be mostly fixed (barring variations in surface
 wind) because changes in the downward flux of solar radiation will not warm the surface.  
-However, the dramatic decrease of low-level clouds for the E25, P25, and P100 LWCRE off 
-experiments strongly influences the net flux of longwave energy at the surface. 
-Low-level clouds serve as a significant source of longwave radiative cooling 
+%However, the dramatic decrease of low-level clouds for the E25, P25, and P100 LWCRE off 
+%experiments strongly influences the net flux of shortwave energy to the surface (not sure about this sentence). 
+Low-level clouds serve as a significant source of LW radiative cooling 
 for the atmosphere (Figure \ref{fig:cf_tdtlw}).  Making these clouds invisible to radiation creates 
-a source of effective atmospheric warming.   The large decrease of low-level clouds also leads to an increase of downward shortwave 
+a source of effective atmospheric warming.   When this source of atmospheric energy loss is 
+removed in the LWCRE-off experiments the upwelling LW flux of radiation plays a larger 
+role in warming the atmosphere that more than compensates for the increased OLR at the 
+top of the atmosphere.  There is an increase in atmospheric warming on the order of 
+$20 \, \rm{W \,m^{-2}}$ for the LWCRE-off experiments and 
+thus additional condensational heating is not needed to balance the increase of OLR. 
+Thus the mean precipitation rate actually decreases as shown in Table \ref{tab:experimentmeans}.   
+These results for E25, P25, and P100 are consistent with \citeA{Popp_Silvers_2017}  who 
+showed dramatically less condensate in the atmosphere and much less precipitation 
+(at the equator) for LWCRE-off experiments (see their Figure 1).  
+%Our results here for the E25, P25, and P100 are consistent with those of \citeA{Popp2017} 
+%because the low-level condensate is strongly decreased when the LWCRE is off.  
+The large decrease of low-level clouds also leads to an increase of downward shortwave 
 radiation at the surface.  Because of the low albedo of water
@@
 %flux change because there are less clouds or because they are invisible to radiation?).  
-With an interactive surface, the surface temperature is influenced
-by a downward flux of longwave radiation from the clouds above.  
-When this source of atmospheric energy loss is removed in the LWCRE off experiments 
-the upwelling longwave flux of radiation plays a larger role in warming the atmosphere that more 
-than compensates for the increased OLR at the top of the atmosphere.  There is an increase in 
-atmospheric warming on 
-the order of $20 \, \rm{W \,m^{-2}}$ when then LWCRE is off and thus there is less need for 
-condensational heating and the mean precipitation rate actually decreases.
-
-In contrast to the P100, P25, and E25 experiments just discussed, turning the LW CRE off for 
-the E1 and E2 experiments results in more precipitation.  This can be understood as follows.  
-The primary method by which the longwave cloud radiative effect influences the atmosphere is by 
+With an interactive surface, the surface temperature would be influenced
+by the downward flux of both LW and shortwave radiation that a change of 
+cloud fraction would lead to.
+
+% The interaction between clouds and the longwave radiation increases, or decreases, precipitation depending
+% on wether high or low clouds are dominant.
+
+% The ways in which clouds interact with their local environment: heat exchange through phase changes, 
+% absorption of radiation, emission of radiation.  But how much do these influence the large-scale circulation?
+
+In contrast to the E25, P25, and P100 experiments just discussed, turning the LWCRE off for 
+the E1 and E2 experiments results in more precipitation.  This can be explained as follows.  
+One of the primary methods by which the LWCRE influences the atmosphere is by 
 heating the atmosphere in the region between the clouds and the surface.  
@@
 \ref{fig:TotCond_P25P100}, and \ref{fig:cf_tdtlw}).  When the warming effect of the upper level clouds 
-in the E1 and E2 experiments is removed in the LWCRE off experiments the energy balance of 
-the atmosphere must be maintained through an increase of latent heating and subsequent increase 
-of precipitation as reflected in Table 2.
+in the E1 and E2 experiments is removed in the LWCRE-off experiments the energy balance of 
+the atmosphere is maintained through an increase of latent heating and subsequent increase 
+of precipitation (Table \ref{tab:experimentmeans}).
 
 These experiments provide insight into the different mechanisms by which the clouds in GCMs and CRMs
-interact with longwave radiation in the atmosphere.
-
-Because there are so many more low-level clouds in 
-the GCM-like experiments we see a strong response to upwelling radiation from the surface.  In contrast, 
+interact with LW radiation in the atmosphere.  Because there are so many more low-level clouds in 
+the GCM-like experiments there is a strong response to upwelling radiation from the surface.  In contrast, 
 the abundance of upper-level ice condensate, and lack of low-level condensate in the CRM-like experiments 
@@
 
-Water vapor is an efficient emitter of longwave radiation and thus greatly facilitates the cooling of the troposphere.  
-\citeA{Popp2017} showed that there is dramatically less condensate in the atmosphere and much less precipitation 
-(at the equator) for LW CRE off experiments (see their figure 1a,b).  Our results here for the E25, P25, and P100 
-are consistent with those of \citeA{Popp2017} because the low-level condensate is strongly decreased 
-when the LWCRE is off.  
+%Water vapor is an efficient emitter of longwave radiation and thus greatly facilitates the cooling of the troposphere.
+
 %This is not the case for E2 and E1.  Those experiments have little low-level condensate to begin with 
@@
 
-The upper panels of Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show that the 
-interactions between longwave radiation and clouds enhance
-the drying of the troposphere in regions of subsidence more than the cases when the longwave CRE is not active.  
-This is especially true for the simulations with a grid-spacing of 1 km and 2 km.  While the mid-tropospheric 
-profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
-response below about 850 hPa for the 25km and 100km models.  At that grid-spacing, with the LWCRE on, significant low-level 
-clouds are formed, leading to a radiative cooling on the order of -10K/day.   
-However, when the LWCRE is off, there is little appreciable difference in the low-level diabatic profiles among the 
-P100, P25, E25, E2, and E1 experiments.   It is also clearly seen that the LW CRE decreases the upper-level ice-condensate 
-for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and 
-P25 (Figure \ref{fig:TotCond}).
+\section{Discussion} % and Summary of the Impact of the LWCRE and Grid-spacing on the Atmospheric State}
+
+This section lists some of the main ways in which the LWCRE and the grid spacing influence
+the clouds, the circulation, and the energetics of the mock-Walker circulation.   Some, but not all of these 
+points have been noted by previous studies.  
+Impacts of turning off the interaction between clouds and the LW radiation (LWCRE-off) include the following:
+
+\begin{itemize}
+  \item A decreased strength of the overturning circulation and the domain mean precipitation (P100,P25,E25).
+  \item The domain mean midtropospheric relative humidity increases by $5-15 \% $.
+ % \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
+  \item The horizontally oriented low-level circulations weaken, and with the regions of high precipitation, spread out 
+  in geographic space.  
+  \item Over the region with warm SST the surface enthalpy flux among models is in much better agreement, 
+  especially between the experiments with 1 and 2 \textit{km} grid-spacing.
+  primarily because of changes in the latent heat flux.
+  \item decrease both the LTS and the EIS, over both the warm and cold regions ???
+  \item A decreased spatial gradient of $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$ on the lowest 
+  atmospheric level.  
+  %\item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
+  %        the 1 and 2 \textit{km} simulations. 
+  % \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
+  \item When convection is parameterized the total domain mean condensate decreases at all heights (Figure \ref{fig:TotCond_P25P100}), in contrast to 
+  when the convection is explicit and the LWCRE-off experiments have more condensate aloft and less at low-levels (Figure \ref{fig:TotCond}).    
+\end{itemize}
+
+Relative to simulations with a grid-spacing of $100 \textrm{km}$ and $25 \textrm{km}$, the $1 \textrm{km}$ and 
+$2 \textrm{km}$ experiments have the following characteristics: 
+\begin{itemize}
+  \item The domain mean precipitation response to LWCRE is opposite to that of the $100 \textrm{km}$ 
+  and $25 \textrm{km}$ experiments.
+  \item Overturning circulations (as measured by vertical velocity) are stronger and are more consistently centered 
+  over the maximum of SST.  
+  \item The regions with upwelling motion as well as the upper troposphere have higher relative humidity.   
+  Between 600-800 hPa the $1 \textrm{km}$ and $2 \textrm{km}$ models can have a relative humidity 
+  that is 40\% higher than in the parameterized, lower resolution simulations.  
+  \item Above about 600 hPa there is two to four times more ice condensate, but only about half as much liquid condensate below 700 hPa.
+  \item There is less domain mean precipitation in the E1 and E2 experiments (Table \ref{tab:experimentmeans}).  Values for 1 and 2 km simulations are in the 3.1-3.7 mm/d range, while those 
+  for the $100 \textrm{km}$ and $25 \textrm{km}$ experiments are about 10-25\% higher (3.5-4.1 mm/d).  
+  %\item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
+  %\item much less vertical shear.  
+\end{itemize}
+
+It is remarkable that despite having the same prescribed SST and incoming radiation
+the control simulations (LWCRE on) have a precipitation rate  that can vary by as much as 
+25\%, wildly different precipitation structures, and surface enthalpy fluxes that vary by as much as 
+60 $\rm{W/m^2}$.
+All simulations use the same dynamical core, radiation, turbulence, large-scale cloud and microphysics parameterizations.  
+Results from these experiments demonstrate that the cloud type
+plays a fundamental role in determining how the radiative fluxes couple
+the large-scale circulation to the moisture.  The large differences in the surface enthalpy flux
+appear to be due to relatively small differences in the winds near the surface.  This is not necessarily
+surprising and is likely the source of much of the differences among the experiments.  The 
+large influence of the low-level wind  and enthalpy flux on the structure of precipitation, 
+low-level moisture and clouds, and mid-tropospheric humidity in the convective regions is 
+consistent with previous studies showing the importance of the low-level wind fields for precipitation 
+\cite{Wofsy_Kuang_2012}, Fermepin and Bony, 2014, boundary layer properties \cite{Raymond_1994}, and even the climate 
+sensitivity (Silvers et al., 2016).
+
+%Numerous simplified models of tropical dynamics, or the mock-Walker circulation have been developed 
+%(e.g \citeA{Raymond_1994}, Pierrehumbert, 1995; Larson et al., 1999; Neelin and Zeng, 2000; 
+%Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005).  
+Many of the previous studies of mock-Walker circulations or simplified models of tropical dynamics (e.g. \citeA{Raymond_1994}, Pierrehumbert, 1995; Larson et al., 1999; Neelin and Zeng, 2000; 
+Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005)
+have focused on simplifying the physics parameterizations as much as possible while still maintaining the interactions between convection and radiation.  
+While these have proven useful, they have remained complex enough to make comparisons with other models 
+difficult and the degree to which the simplifying assumptions influence the conclusions is unclear.    
+The approach of this paper is different.  We study an idealized configuration with the full complexity of a GCM. 
+Pierrehumbert (1995) argued that cloud processes are not the leading cause of the 
+stable tropical climate but that it is, `the ability of
+the atmospheric circulation to create dry air pools in regions of large-scale subsidence' 
+-these are the Radiator Fins-, that serve as a cooling (thus stabilizing) mechanism for Earth's tropical climate.  
+Our results demonstrate how strongly the cloud radiative effects influence the circulations that set up the Radiator Fins.  
+Experiments with prescribed SST preclude the possibility of studying feedbacks
+between the circulation, and the relative area of warm and cold SST regions.  
+However, the interaction between clouds, radiation, and the circulation does lead to changes in the area of the dry 
+regions above the boundary layer that allow the tropics to efficiently cool to space and maintain an energetic balance.   
+%Pierrehumbert lists
+%determining the size of these 'radiator fins' and the quantity of RH as some of the critical unsolved questions.  That 
+%work depended critically on an interactive surface that allowed for the size of the two regions to change.  It is interesting
+%in the work presented here that the SST is fixed, and yet the subsidence fraction, tropospheric RH over the cold pools, 
+%and overall energetics can still change despite a fixed surface temperature.   
+%While the usefulness of such methods is clear, part of our motivation was to leave the GCM configuration as close to the parent model (AM4.0)
+%as possible and see what range of equilibrium states are reached.   
+Using mock-Walker simulations to benchmark a GCM with a CRM was proposed by \citeA{Jeevanjee_etal_2017}.
+This was part of our initial motivation but is predicated on physics parameterizations that are simple enough 
+to allow for a clean comparison. 
+%generate a better understanding of the physical processes.  
+Utilizing something like Kessler microphysics, 
+fixed radiative cooling, and a binary large-scale cloud scheme would provide an elegant comparison between 
+models.  However, making such changes to the GCM used in this paper would result in a model so different from AM4.0 
+that the CRM would no longer serve as a benchmark to AM4.0.   We have chosen to keep the GCM as close as 
+possible to AM4.0.
+More intermediate steps are necessary to create a clean link between CRMs and GCMs.  
+%Allowing for interactive radiation and sophisticated cloud parameterizations significantly
+%complicates the outcome of experiments, but also brings the model configuration very close to the original GCM. 
+The complexity of our results highlights the need for continued work with simple theoretical models such as the 
+Quasiequilibrium Tropical Circulation Model (QTCM; Neelin and Zeng, 2000) and the Simplified QTCM, or SQTCM 
+(Sobel et al., 2004; Peters and Bretherton, 2005, Bretherton et al., 2006).  
+Our results also show that the mock-Walker circulation is an ideal configuration with which to test developments in 
+large-scale cloud or microphysics parameterization schemes.  
+This is an important step in the ongoing process of merging GCMs and CRMs into a global CRM.
+
+There is a rich literature on tropical overturning circulations.  While this study has interpreted the experiments 
+in the context of the Walker Circulation, our results are also relevant to the deep overturning circulations and 
+meridional SST gradients that define the Intertropical Convergence Zone (ITCZ) and the Hadley Circulation.  
+In that context, our results are consistent with those of several recent studies 
+(e.g. Fermepin and Bony, 2014; Harrop and Hartmann, 2016; Popp and Silvers, 2017; Dixit et al. 2018; Flaschner et al. 2018; Albern et al., 2018).  
+Those studies, as well as the present one, show that the LWCRE acts to constrain, or tighten, the deep convective region.  
+This results from an increased atmospheric energy uptake and strengthening of the overturning circulation where the deep convective clouds occur (Popp and Silvers, 2017).  
+Also consistent with this previous work, the present paper shows that the LWCRE has a strong influence on the low-level circulation.   
+When the LWCRE is turned off, the low-level circulations shift upward and are not as well organized 
+(see Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
+There is a corresponding change in the low-level cloud fields, LW radiative cooling, and the domain mean precipitation.
+For the experiments with a GCM-like configuration, the LWCRE strongly influences the precipitation from the large-scale
+cloud scheme while leaving the precipitation from the convective parameterization scheme largely unchanged.  This 
+contributes to a much stronger response of the GCM-like experiments to the LWCRE, especially in the low-levels of the 
+troposphere.  
+Albern et al., 2018 showed that there is a large spread in the CRE response to warming among GCMs.  
+Our expectation is that the fraction of precipitation that is due to the convective parameterization will be dependent on the 
+GCM.   The disparate influence of the LWCRE on the large-scale precipitation could explain some of the model
+spread in the CRE response to warming.
 
@@
 
+We have used the framework of the tropical overturning circulation, specifically the Walker Circulation, 
+to compare the multi-scale interactions between large-scale circulations, cloud systems, and interactive 
+radiation across experiments with grid-spacing ranging from 1km to 100km.   
+To better isolate the role that clouds and humidity play in driving and responding to the 
+circulation, experiments have been performed with and without the radiative effect of clouds, with and without the 
+convective parameterization, using various domain sizes.  Our results show that 
+the convective parameterization and the longwave cloud radiative effect (LWCRE) strongly interact with each other and 
+often lead to asymmetric results and large differences in the equilibrated state of the atmosphere.
+
+%Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
+%large-scale circulation to a simple Gaussian shaped prescribed SST pattern. 
 %The results presented in this paper show us that (scientific point learned).    Interactions between the clouds and radiation
@@
 
-We have used the framework of the tropical overturning circulation to compare the multi-scale interactions between 
-circulation patterns, cloud systems, and interactive radiation across experiments with grid-spacing ranging from 
-1km to 100km.  The flexible modeling
-system at GFDL has allowed us to use a single code base in a GCM-like configuration with physics parameterizations 
-that are very close to the AM4.0/CM4.0 models as well as in a CRM-like configuration with explicit convection.  While 
-there are significant differences between the CRM presented in this paper and more conventional CRMs (e.g. vertical 
-grid spacing and a threshold based `binary' cloud scheme), the prospect of so easily converting a GCM into something 
-like a CRM provides an enticing testbed for future model development.
-These comparisons have highlighted some of the unexpected behaviors of a GCM-like configuration when used with 
-idealized boundary conditions.  For example, the consistent asymmetry of the circulation and precipitation relative 
-to the fixed SST pattern and the dominance of the large-scale precipitation over the convective precipitation.  
-The comparisons have also illustrated some of the challenges that arise when dramatically increasing the resolution 
-of a GCM.  For example, the lack of shallow 
-clouds (both convective and stratocumulus) and the difficulty of comparing clouds in this CRM to other CRMs due to the 
-prognostic large-scale cloud scheme used at GFDL.
-
-%Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
-%large-scale circulation to a simple Gaussian shaped prescribed SST pattern.
-
-To better understand the role that clouds
-and humidity play in driving and responding to the circulation we have performed experiments with and without the radiative
-effect of clouds, with and without the convective parameterization, across multiple domain sizes and resolutions.  
-Our results show that the convective 
-parameterization and the longwave cloud radiative effect strongly interact with each other and often lead to 
-asymmetric results.
-
-It is remarkable that the control simulations (LWCRE on) have a precipitation rate  that can vary by as much as 
-20\% despite having the same prescribed SST and incoming radiation.  All simulations have the same radiation,
-turbulence, large-scale cloud and microphysics parameterizations and all use the same dynamical core.
-
-We were struck by three particular changes due strictly do a 4-fold increase in domain width.
-A dramatic widening of the precipitation distribution when the LWCRE is off, a shifting of low level clouds upward by more than 100 hPa, and
-a strong dependence of the quantity of precipitation produced by the large-scale scheme on the LWCRE.   
-The LWCRE also highlights the impact of an increased vertical moisture transport 
-in our CRM-like models.
+%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system 
+%the idealization is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, 
+%as compared to the observed world.  These simulations are somewhere in the middle of those extremes.  We have 
+%decided to keep many of the complex elements of the global climate model  so that we can hopefully better understand 
+%the parent model (AM4.0) while learning something concrete about 
+%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke 
+%large-scale cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
+%model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
+%understanding and to illuminate some of the idiosyncrasies of the climate models that are currently looked to for information about the 
+%future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
+%a simple design that incorporates additional complexity which strengthens the connection to observed atmospheric phenomena.
+
+Perhaps the most interesting result is that the GCM-like experiments have a relatively large low-level 
+cloud fraction while the CRM-like experiments have a large upper-level cloud fraction.  
+This difference in the dominant cloud type leads to opposite atmospheric responses to changes of the LWCRE.  
+The LWCRE increases the domain mean precipitation ($\overline{\rm{P}}$) for the GCMs but 
+decreases it for the CRMs (Table \ref{tab:experimentmeans}).  
+Over the regions with cooler SSTs the large low-level cloud fraction of the GCMs 
+acts as a source of radiative cooling that is balanced by condensational heating in the control case.  
+A strong decrease of low-level clouds in the GCMs
+for the LWCRE-off experiments removes this cooling and condensational heating.  The increase 
+of precipitation that is expected in the LWCRE-off case as a result of increased LW cooling to space is not enough
+to overcome the decreased condensational heating at low-levels, with a net effect of less precipitation.  
+Over the regions with cooler SSTs, the CRMs have very few (less than \%5) low-level clouds and as a result the 
+change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
+\textit{reference to Watanabe et al 2018?  Watanabe et al., 2018 found a similar relationship between 
+low-clouds and precipitation in the context climate change experiments.}
+This highlights how sensitive the energetics of the tropical atmosphere are to the distribution of clouds and 
+their interaction with the radiation.
+
+Decreasing the grid-spacing from $100 \textrm{km}$ to 1km allowed for the parameterization of both deep and shallow 
+convection to be turned off, resulting in a more direct simulation of the dynamics that are
+fundamental to the overturning tropical circulation.  The resulting atmospheric state has a stronger overturning 
+circulation, a much more humid (40\% higher RH) deep convective region, and less $\overline{\rm{P}}$ .  
+Relative to the GCM-like simulations the 1 and 2km simulations have two to four times as much condensate
+aloft but only about half as much below 700 hPa.  This increase of vertical moisture transport with increasing 
+resolution is particularly apparent in the LWCRE-off experiments (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).
+
+Three striking changes occur as a result of a four-fold increase in domain width.  The low-level clouds shift 
+upward by more than 100 hPa, there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments,  
+%and a strong dependence of the quantity of precipitation produced by the large-scale cloud scheme on the LWCRE. 
+and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation.    
+This impact on the large-scale precipitation occurs for the GCM-like experiments on smaller domains as well, 
+but is particularly pronounced in the large domain experiments.  
+%Larger domains have more precipitation.  
+%The amount of precipitation, and the structure of the precipitation and clouds 
+%is heavily dependent on the interaction between clouds and the longwave radiation.  This interaction strongly mediates
+%the precipitation from the large-scale cloud parameterization, not the convective precipitation  
+This dependence on domain size could imply that 4000 km is not large enough to contain the largest 
+scales that are important for the overturning circulation.  Another reason for the domain 
+size dependence could be the changing scale of the warm and cold regions of SST.
+
+The flexible modeling system at GFDL has allowed us to use a single code base in a GCM-like configuration with 
+physics parameterizations that are very close to the AM4.0/CM4.0 models as well as in a CRM-like configuration 
+with explicit convection.  While there are significant differences between the CRM presented in this paper and more 
+conventional CRMs (e.g. vertical grid spacing and a threshold based `binary' cloud scheme), the prospect of so 
+easily converting a GCM into something like a CRM provides an enticing testbed for seeking process level 
+understanding and future model development.   This can be thought of as a top-down approach to developing 
+a global CRM which should complement efforts that start with a regional large-eddy simulation (LES) model or CRM model and work 
+towards a global model (e.g. Schneider et al., 2017; Schneider et al., 2019).
+The comparisons presented in this paper have highlighted some of the unexpected behaviors of a GCM-like 
+configuration when used with idealized boundary conditions.  
+Two examples include the consistent asymmetry of the circulation and precipitation relative 
+to the fixed SST pattern, and the dominance of the large-scale precipitation over the convective precipitation.  
+The comparisons have also illustrated some of the challenges that arise when dramatically increasing the resolution of a GCM.  
+These include the lack of shallow clouds in the CRM (both convective and stratocumulus) and the difficulty of comparing 
+clouds in this CRM to other CRMs due to the prognostic large-scale cloud scheme.  
+These are not fundamental challenges and motivate future work.
 
@@
 
-Below is a list summarizing several of the changes that occur when the LWCRE is turned off.  Turning the LWCRE 
-interactions off tends to:
-
-\begin{itemize}
-  \item decrease the strength of the overturning circulation and the domain mean precipitation (P100,P25,E25)
-  \item increase the midtropospheric RH by $5-15 \% $
- % \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
-  \item weaken the horizontally oriented low-level circulations.   
-  \item spread out in geographic space the precipitation maxima
-  \item homogenize the surface enthalpy flux over the warm pool, primarily through the latent heat flux
-  \item decrease both the LTS and the EIS, over both the warm and cold regions
-  \item decrease the lowest level $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$.  
-  \item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
-           the 1 and 2 \textit{km} simulations. 
-  \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
-  \item amplify the larger values of ice condensate aloft for the explicit simulations.  
-\end{itemize}
-
-Relative to simulations with a grid-spacing of $25 \textit{km}$, the E2 and E1 experiments can be characterized as having: 
-\begin{itemize}
-  \item stronger overturning circulations (as measured by vertical velocity) which are more consistently centered 
-  over the maximum of SST.  
-  \item higher relative humidity in the upwelling regions and aloft.   Between 600-800 hPa the explicit models 
-  can have a relative humidity 
-  that is 40\% higher than in the parameterized, lower resolution simulations.  
-  \item two to four times more ice condensate above 600 hPa but only about half as much liquid condensate below 700 hPa.
-  \item less domain mean precipitation.  Values for 1 and 2 km simulations are in the 3.2-3.5 mm/d range, while those for the 25 km 
-  simulations are 10-20\% higher (3.5-3.9 mm/d).  
-  %\item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
-  %\item much less vertical shear.  
-\end{itemize}
-
-There is a rich literature on tropical overturning circulations.  Much of it is focused on the Hadley circulation and while some
-work has looked at the Walker circulation, it has received less attention.  Part of our motivation in using the framework of the 
-Walker circulation comes from the fact that all of the major types of tropical clouds occur regularly within the region 
-identified with the Walker circulation.  While this study has interpreted the experiments in the context of the Walker 
-Circulation, our results are also relevant to the deep overturning circulations and meridional SST gradients that define 
-the ITCZ and the Hadley Circulation.  In that context, our results are consistent with those of several recent studies 
-(e.g. Harrop and Hartmann, 2016, 
-Popp and Silvers, 2017, Dixit et al. 2018, Flaschner et al. 2018).  These studies, as well as the present one, all show that the 
-LWCRE acts to constrain the deep convective region.  This results from an increased atmospheric energy uptake and 
-strengthening of the overturning circulation where the deep convective clouds occur (Popp and Silvers, 2017).  Consistent with 
-these papers, the present work also shows that the LWCRE has a strong influence on the low-level circulation.   When 
-the LWCRE is turned off, the low-level circulations shift upward and are not as well organized (see Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
-There is a corresponding change in the low-level cloud fields, longwave radiative cooling, and the domain mean precipitation.
-For the experiments with a GCM-like configuration, the LWCRE strongly influences the precipitation from the large-scale
-cloud scheme while leaving the precipitation from the convective parameterization scheme largely unchanged.  This leads 
-to a much stronger response of the GCM-like experiments to the LWCRE, especially in the low-levels of the troposphere.  
-Because we expect the fraction of precipitation that is due to the convective parameterization to be model dependent 
-this could explain why GCMs have a large spread in their response to turning off the LWCRE (Aiko's work?).
-
-The only difference between our simulations and radiative convective equilibrium is a gradient of SST at the lower boundary.
-The addition of this small difference creates a concrete link with the observed tropical atmosphere.  The idealized 
-mock -Walker cell configuration serves as an important step between models of pure radiative convective equilibrium
-and models which are applicable to a wider range of Earth like conditions.   The goal in developing and using idealized models is to capitalize on their simplicity and learn something about the 
-parent system as a result.  Idealized studies focusing on particular aspects of the Earth system have shown that a 
-real danger of idealized models is that they will not actually be easier to understand than the Earth system.
-
-What are we to conclude from this array of results?  Our CRMs succeed (by construction) at representing a far more 
-realistic range of turbulent motions and thus presumably do a better job of explicit mixing compared to the GCM-like 
-configurations.  However, the increase in resolved scales comes at the cost of most of the low-level clouds (\textit{what is 
-the observed cloud fraction in the tropical Pacific below 700 hPa?}).  The GCM-like simulations match the CRM-like 
-simulations  in the general two celled structure of the overturning circulation and the approximate distribution of condensate.  
-While the GCM-like simulations succeed at producing 20-30\% low-level cloud fraction they produce very little upper-level 
-clouds and the distribution of the precipitation is erratic and dependent on interactions between the convective 
-parameterization and the interactions between longwave radiation and clouds.  The solutions of the GCM-like simulations 
-also have a large dependence on the size of the domain.  Larger domains have more precipitation and domain mean 
-cloud profiles shift upward by more than 100 hPa.  The amount of precipitation, and the structure of the precipitation and clouds 
-is heavily dependent on the interaction between clouds and the longwave radiation.  This dependence strongly mediates
-the large-scale cloud parameterization, rather than the convective parameterization.  The longwave cloud radiative 
-effect acts to concentrate the regions of precipitation and increases the domain mean value.
-
-We have learned that for high resolution models with explicit convection the upper-level clouds dominate the impact
-of interactions between clouds and radiation while for GCM-like simulations it is the low-level clouds that dominate
-this impact.
+Mock -Walker cell configurations are an important step between models of RCE and models which simulate a wider range of Earth like conditions.
+The only difference between our simulations and radiative convective equilibrium (RCE) is the gradient of SST at the lower boundary.  
+The addition of this small difference from pure RCE creates a concrete link with the observed tropical atmosphere.  
+The goal in developing and using idealized models is to capitalize on their simplicity in such a way that key elements of the 
+process in question become clear.  
+In this case the processes of interest are the coupling between clouds, radiation, and the large-scale circulation.  
+Studies using RCE have been fruitful but insufficient to fully illuminate these processes while typical GCM studies are often too complex to untangle.  
+%Idealized studies focusing on particular aspects of the Earth system have shown that a danger of idealized models is 
+%that they will not actually be easier to understand than the Earth system.   
+%Sometimes the difficulty of interpreting results from Aquaplanet and full-physics RCE
+%simulations give this impression.}.  
+Many of the characteristics from RCE experiments that have aggregated are present in mock-Walker simulations.   
+Deep convection is anchored to a single location with high humidity and is surrounded by dry subsiding regions.  
+It would be interesting to see how consistent the degree of aggregation and drying is among 
+different models, as well as the response to warming SSTs.  The configuration of a mock-Walker circulation 
+is ideal for studying the effects of aggregation in a system that is more constrained than pure RCE.     
+Prescribing a warm region of SST does not fully determine the large-scale circulation.  
+This paper clearly shows how much variability there still is between the large-scale circulation, clouds, 
+and fluxes of energy (radiative and surface enthalpy).
+%While it may seem that prescribing a warm region of SST fully determines the large-scale circulation, 
+%the results presented in this paper clearly show how much room there is for the large-scale circulation 
+%to interact with the clouds and the fluxes of energy, both radiative and surface enthalpy.   
+The initial results from the RCE Model Intercomparison Project (RCEMIP; Wing et al., 2020) show a wide range of variability among the models.
+Adding the extra constraint of an overturning circulation forced by a prescribed gradient of SST would provide a context within which the 
+wide range of results from RCEMIP could be reexamined and expanded upon.
+
+% INCLUDE??
+%Doubly periodic CRM simulations of RCE are abundant.  Doubly periodic simulations of RCE with a full set 
+%of GCM physics are less common (e.g. Held et al., 2007; Silvers et al., 2016).  As argued in Held et al., 2007, and 
+%utilized in Silvers et al., 2016, it is important to study idealized models with the same physics and resolution of 
+%GCMs, 'especially if that GCM is being used to make climate change predictions that help form the basis for 
+%society's response to global warming.'
+
+%\textit{this paragraph is pretty repetative with earlier parts of the section.  do I want these point here or earlier?}
+%What are we to conclude from this array of results?  
+%Our CRMs resolve a far broader 
+%range of turbulent motions and thus do a better job of explicit mixing compared to the GCM-like 
+%configurations.  However, the increase in resolved scales comes at the cost of most of the low-level clouds (\textit{what is 
+%the observed cloud fraction in the tropical Pacific below 700 hPa?}).  The GCM-like simulations match the CRM-like 
+%simulations  in the general two celled structure of the overturning circulation and the approximate distribution of condensate.  
+%While the GCM-like simulations succeed at producing 20-30\% low-level cloud fraction they produce few upper-level 
+%clouds and the distribution of the precipitation is erratic and dependent on interactions between the convective 
+%parameterization and the strength of the longwave cloud radiative effect.  
+%
+
+During the course of this research, it became apparent how fundamentally different the calculations of large scale clouds are between CRMs and GCMs.
+Increasing computing resources will continue to blur the line that distinguishes GCMs from CRMs. 
+As the grid-spacing of models decreases so too does the necessity of representing convection with parameterizations. 
+\textit{As a result, the details of the large-scale cloud scheme will be increasingly important for a correct 
+understanding of the role played by tropical clouds in the processes that are linked to interactions between clouds,
+radiation, and the large-scale circulations.}  
+For high resolution models with explicit convection, the upper-level clouds dominate the impact of interactions between 
+clouds and radiation, but for GCM-like simulations the low-level clouds dominate this impact.  
+Determining the respective roles of high and low clouds as mediators between radiative effects and the large-scale overturning 
+circulations in the observable atmosphere should be a high priority in future research.
 
@@
 %Stevens et al. 2012
+%Tompkins, 2001
+% Li et al. 2015?  How do our conclusions about the CRE at TOA relate to their conclusions about the ACRE?  Same question with Harrop and Hartmann
+% Popp and Bony?
+% Kelly and Randall, 2001?
 
@@
 %The streamfunction is therefore defined by two equations and can be solved with either.  The choice is often made based on the 
-%boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $\rm{kg/s^3}$.  Often, the streamfunction
-%is computed as a mass streamfunction with units of $\rm{kg/s}$.  Density does not appear above
-%because pressure is being used as the vertical coordinate.   With height as the vertical coordinate, mass is given by $\rho dxdydz$, 
-%assuming a hydrostatic atmosphere and rewriting in terms of pressure mass is given by $-(1/g) dxdydp$.
+%boundary conditions.  Dimensionally, $\psi$ must have units of velocity multiplied by pressure, or $\rm{kg/s^3}$.  
+%Often, the streamfunction is computed as a mass streamfunction with units of $\rm{kg/s}$.  
+%Density does not appear above because pressure is being used as the vertical coordinate.   
+%With height as the vertical coordinate, mass is given by $\rho dxdydz$, assuming a hydrostatic atmosphere and rewriting in terms of pressure, mass is given by $-(1/g) dxdydp$.
 %Scaling the equations above by $a/g$ results in $\psi$ having units of $\rm{kg/s}$.  
@@
 \acknowledgments
-The authors thank Leo Donner, Nadir Jeevanjee, and Juho Iipponen for helpful discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
-Funding for this work came from both GFDL and Stony Brook.
+The authors thank Leo Donner, Nadir Jeevanjee, and Juho Iipponen for discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
+The expertise of Ming Zhao with the physics of AM4.0 also proved helpful in many conversations related to this work.
+LGS performed the experiments and wrote the paper under award NA14OAR4320106 from the National Oceanic and Atmospheric Administration, U.S.
+Department of Commerce.
+LGS also acknowledges recent partial support through Stony Brook University from award NSF AGS1830729.
 Data and scripts are available from author upon request
@@
 \bibliography{Silvers_WalkerCell}
+
+%Reference citation instructions and examples:
+%
+% Please use ONLY \cite and \citeA for reference citations.
+% \cite for parenthetical references
+% ...as shown in recent studies (Simpson et al., 2019)
+% \citeA for in-text citations
+% ...Simpson et al. (2019) have shown...
+%
+%
+%...as shown by \citeA{jskilby}.
+%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
+%...has been shown \cite{jskilbye}.
+%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
+%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
+%...has been shown by \cite <e.g.,>[and others]{lewin76}.
+%
+% apacite uses < > for prenotes and [ ] for postnotes
+% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
+%
 

### 2020-04-24 Silvers_cfmip.tex
tex file for cfmip paper

\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers

\draftfalse

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\begin{document}

			% Activate to display a given date or no date
%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
\title{Clouds and Sensitivities Across a Hierarchy of GFDL CMIP6 Models}
\authors{Levi G. Silvers, David Paynter, V. Balaji, Chris Blanton, Chris Dupuis, Jeffrey Durachta, Huan Guo, 
Isaac Held, Richard Hemmler, Jasmin G. John, Pu Lin, Colleen McHugh, Serguei Nikonov, Jeffrey Ploshay, Aparna Radhakrishnan, 
Kristopher Rand, Thomas Robinson, Hans Vahlenkamp, Chandin Wilson, Bruce Wyman, Yujin Zeng, Ming Zhao}
% Isaac Held?  Michael Winton?  Pu Lin? Songmiao Fan?  M. Daniel Schwarzkopf?

\correspondingauthor{Levi Silvers}{levi.silvers@stonybrook.edu}

%\textbf{Key Points: choose three}
\begin{keypoints}
  \item{The AM4.0 TOA cloud radiative effect shows small biases compared with CERES-EBAF observations, versions 
  2.8 and 4.1.}
  \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
  \item{AM4.0 low-level clouds have a negative bias (relative to MISR) that is larger for thin clouds, relative to thick.}
  \item{Various configurations of a single global climate model lead to climate sensitivities that range from 2.1K (Cess) to 
  about 5K (Winton's ECS).}
\end{keypoints}

\begin{abstract}
Observations of cloud fraction from multiple satellites are compared to the clouds simulated by 
GFDL's new AM4 climate model.  
The new atmospheric climate model succeeded at significantly reducing the TOA radiative flux biases as compared 
to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs 
(Cess-type warming experiments), the corresponding coupled climate model, CM4, has high transient and 
equilibrium climate sensitivities.

A systematic picture is presented of the modeled clouds across a hierarchy of model configurations which utilize 
the AM4 and CM4 climate models.  This hierarchy includes the CFMIP Aquaplanet and \textit{amip} experiments, 
fully coupled model experiments as well as additional \textit{amip}-like experiments with particular SST patterns.  
We demonstrate the large range of sensitivities that are possible from a single parent atmospheric climate model.   
Looking at the global mean radiative feedbacks across the different model configurations as well as in the context 
of CMIP5 and CMIP6 models will allow us to assess to what extent the cloud feedbacks in the idealized 
experiments relate to the fully coupled experiments and to observed clouds.  
\end{abstract}

\section*{Plain Language Summary}
[ enter your Plain Language Summary here or delete this section]

\section{Introduction}

% thoughts from Zhao et al. 2018 part 1, section 4
% Attention to the observed TOA radiative fluxes were given a high priority during the development of AM4.0 first 
% of the relatively high confidence in the observations, and second because it was anticipated that these fluxes
% are an important component in the coupled simulations of CM4.0.   Figure 2 shows that AM4.0 does a better 
% job simulating RLUT and RSUT than any other of the compared CMIP5 models.   Not only was the global 
% mean bias of (-0.77 W/m2) an improvement over AM3 and AM2.1 (-4.11 and -3.16 W/m2), but the spatial pattern 
% was improved over almost the entire world ocean.   Fluxes at the TOA for AM4.0 largely corrected over reflection
% throughout most of the oceans and an over absorption of solar radiation in the Southern Hemisphere ocean 
% south of ~60 degrees.

This paper has a double motivation.  First, to illustrate the wide range of climate sensitivities to external perturbations 
that can be achieved with a single base model.  For this purpose we utilize several models from the new suite of GFDL 
models that participated in CMIP6.  This constitutes a hierarchy of configurations that ranges from an atmosphere only 
aquaplanet to a fully coupled 
climate model.  Previously the range of climate sensitivities and feedbacks among the ensemble of climate models 
the world has to offer have been documented largely by examining the multi-model mean results with less attention to 
the variability of sensitivity within a single modeling framework (IPCC; \citeA{Andrews_etal_2012, Ringer_etal_2014}).  By 
focusing on the models from a single modeling center we seek fresh insight that could be buried within a large ensemble.

\begin{figure}
  \centering
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
  \includegraphics[width=0.6\columnwidth]{cfmipfigs/ISCCP_CALIPSO_clt_correctedBiasPattern_nogrid.eps}
  %\includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
  \caption{Comparison of total cloud fraction from the AM4 \textit{amip} experiment with two observational 
  data sets: ISCCP (left) and CALIPSO (right).  The top row shows the observational data.  The bottom row
  shows the result of subtracting the observations from the AM4.0 data.  Numbers in the title above each 
  panel give the global mean cloud fraction (top), and the bias of global mean cloud fraction (bottom)}
  \label{fig:clt_isccp_calipso}
\end{figure}

A second motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
have participated in CMIP6.  This will largely be done in the context of the amip experiment and comparisons to observations
that overlap with parts of that time period (1979-2014).  The experiments and diagnostics used are taken from the latest 
round of CFMIP which has provided a useful framework with which to evaluate cloud feedbacks.

It has been known for decades that  the spread of cloud feedbacks among models contributes to a large portion of the 
spread in climate sensitivity among those same models \cite{Cess_etal_1989, Bony_Dufresne_2005}.  
This has recently been confirmed \cite{Zelinka_etal_2020} for a collection of CMIP6 models.  \citeA{Zelinka_etal_2020} also showed that 
the average effective climate sensitivity (based on a regression analysis of the first 150 years of the abrupt-4xCO2 
experiment) for CMIP6 models appears to be higher than that for the CMIP5 models.  This was attributed to an 
increase of the warming from low level cloud feedbacks.  Their analysis included GFDL models used in CMIP5 (CM3) 
and CMIP6 (CM4), but interestingly
these models did not fit the mold described by the ensemble averages.  The effective climate sensitivity of 
CM4 is slightly smaller than CM3 (3.89 vs. 3.96K) and the SW cloud feedback for CM4 (0.03 W/m2K) is much
weaker than that of CM3 (0.60 W/m2K).

Based on constant temperature perturbation experiments CM4 was expected to be significantly less sensitive 
than CM3 \cite{Zhao_2014}.
Recent research has made it clear that the climate sensitivity estimated from constant temperature perturbation 
experiments is not a good indicator of the climate sensitivity that is estimated from regression techniques of 
abrupt 4xCO2 warming experiments, and that both 
of these measures of sensitivity underestimate the equilibrium sensitivity that is attained when a coupled climate 
model reaches equilibrium after multiple millennia \cite{Paynter_etal_2018,Rugenstein_etal_2020}.     
At least part of the reason for this multiplicity of 
sensitivities obtained from different method of calculation is that variations of the climate sensitivity within 
individual models has been tied to the influence of particular surface temperature patterns 
\cite{Gregory_Andrews_2016, Zhou_etal_2016, Andrews_Webb_2018, Silvers_etal_2018}.   
The influence of a pattern in the surface temperature is communicated to the TOA radiative fluxes by the clouds 
(Gregory and Andrews, 2016; Rose et al.; Silvers et al., 2018).   Thus, clouds are important factors to both the uncertainty 
estimates of climate sensitivity, as well as to the variability in time of the climate sensitivity.

This work assesses the fidelity of the clouds in AM4.0/CM4.0 with observations and compares clouds from experiments 
with differing sensitivities. 
Section two compares the clouds from the \textit{amip} run of AM4.0 with satellite observations.  That section also 
analysis the radiative fluxes at the top-of-the-atmosphere (TOA) and compares them to the observations from 
CERES-EBAF.    Section three documents the climate sensitivities of GFDL models across multiple CMIP6 experiments 
and discusses the potential role played by clouds.   Conclusions are drawn in section four.

\section{Data and Experiments}

We compare output from the AM4.0 GCM to observations from ISCCP, MISR, MODIS, CALIPSO, and CERES-EBAF.
For details of the data used see Table 2.

The comparisons with observations are made mostly with the \textit{amip} experiment.   The experiments used 
in this paper are all part of the GFDL contribution to CMIP6.  We use the \textit{historical, abrupt-4xCO2, and 1pctCO2}
experiments from the CMIP6 DECK.  In addition we utilize several experiments from the CFMIP contributions 
to CMIP6.  These experiments include \textit{amip, amip-p4K, amip-m4K, amip-future4K, aqua-control} and \textit{aqua-p4K}.

\section{Clouds in AM4.0: Comparison between AMIP and observations}

%\begin{figure}
%% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
%  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
%  \caption{Observed and modeled clouds for all heights.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
%  and thin (optical depth between 0.3 and 3.6) 
%  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
%  derived with the MISR simulator.  Mean cloud fraction values for MISR 
%  (AM4) are 32\% (24\%) for thick clouds and 22\% (12\%) for thin clouds.}
%  \label{fig:misr}
%\end{figure}

Before discussing the climate sensitivities of AM4/CM4 and how they are influenced by cloud feedbacks we assess
the clouds and radiative fluxes which are simulated by AM4.0 over the recent period of 1979-2014.  This is done 
by comparing satellite based observations to the \textit{amip} experiment that is part of GFDLs 
contribution to CMIP6.  
During the development and documentation of AM4.0 \cite{Zhao_etal_2018a, Zhao_etal_2018b}, 
(Z18a and Z18b hereafter) 
and CM4 \cite{Held_etal_2019}, specific cloud properties such as the 
cloud droplet number, cloud fraction, and the partition of cloud water into liquid or ice were noted, but 
accurately modeling the radiative fluxes at the top of the atmosphere was determined to be a 
higher priority partly because of the large observational uncertainties of those cloud properties (Z18a,b).   
Based on the initial analysis for those papers, the cloud properties of AM4.0 were determined to be
at least as consistent with observations as previous generations of GFDL models.  Z18a also noted 
that AM4.0 underestimates the liquid droplet number over oceans and downwind of the aerosol emission 
sources.   
Comparisons of AM4.0 with observations from ISCCP and MODIS showed an underestimate of 
the optically thin low clouds and the mid-level clouds (Z18a, Figure 10).  
However, the observational uncertainty for some of these properties prohibited firm conclusions.  This paper
uses additional observations and a more thorough analysis of the clouds in AM4/CM4 to determine 
the quality of the cloud simulations.        
In this section we first compare the simulated and observed cloud fraction.  We then compare  
the simulated TOA radiative fluxes from AM4.0 to those observed by CERES.    
Throughout the paper we utilize what has come to be known as the Cloud Radiative Effect (CRE).  The CRE is the 
difference between the full-sky and clear-sky radiative fluxes (this quantity is also sometimes referred
to in the literature as the cloud radiative forcing, CRF).

\begin{figure}
  \centering
% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
  \caption{Observed and modeled clouds below 2.75km.  Clouds shown are divided into thick 
  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
  (AM4) are 18\% (13\%) for thick clouds and 22\% (6\%) for thin clouds}
  \label{fig:cf_misr_lowcl}
\end{figure}

\subsection{COSP}
In order to compare the observed and modeled clouds as consistently as possible across multiple platforms 
GFDL has implemented a collection of satellite simulators which are part of the 
CFMIP (Cloud Feedback Model Intercomparison Project; see Webb et al., 2017).  Satellite simulator
are software tools that are used in coordination with GCMs to allow for model variables 
to be translated to variables that are more directly comparable with what satellites observe.  
These simulators are often referred to as the CFMIP Observation Simulator Package (COSP); for
details see Bodas-Salcedo et al. 2011.  This paper highlights simulators of the algorithms for 
four satellite datasets: ISCCP (the International Satellite Cloud Climatology Project), 
MODIS (the Moderate Resolution Imaging Spectroradiometer), 
MISR (the Multiangle Imaging Spectro-Radiometer), and 
CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation; 
Chepfer et al., 2010; Cesana and Chepfer, 2013).  By using multiple complimentary satellite 
datasets and simulators we can benefit from the different strengths of each satellite while largely 
minimizing the known problems and discrepancies of the observational data sets.

\begin{figure}
  \centering
% figure generated with cloud_table_AM4fig.ncl
  \includegraphics[width=0.98\columnwidth]{cfmipfigs/Silvers_cfmip_MISR_cloudtable.pdf}
  \caption{Cloud Fraction (colors and numbers (\%)) in joint histograms showing the variations of cloud fraction 
  as a function of cloud top height and optical depth (tau).
  The top panels show observations from MISR, bottom panels show MISR simulator output from the 
  \textit{amip} experiment.  Shown from left to right are the mean values for the full globe, between 30S-60S,
  between 30S-30N, and between 30N-60N.}
  \label{fig:misr_sim_vs_mod}
\end{figure}

Discrepancies among the many observational data sets have been previously discussed in the literature.
Curious readers can find detailed discussions in Kay et al., 2012,
Marchand et al., 2010, Pincus et al., 2012, and Stephens et al., 2018.  However, for the 
purposes of this paper we note the following.  ISCCP is useful due to 
the relative longevity of the record (1983 - 2008 in Z18 figure). 
MODIS has a cloud detection algorithm that is an improvement upon ISCCP's and
thus does a better job of detecting mid-level clouds and excluding partly filled pixels.   
Of the three passive satellite products (ISCCP, MODIS, and MISR), MODIS is considered to have the most 
accurate readings of high-topped clouds.  The height of clouds is determined with a stereo height retrieval 
method in MISR that is distinct from that used by both ISCCP and MODIS.  Because of this we have more 
confidence in the low and mid-level cloud readings 
from MISR, as well as the cumulus clouds (Marchand et al. 2010; Zhang et al., 2019).   The CALIPSO observations
are derived from a Lidar that allows for active and direct measurements of the vertical structure of the clouds and thus 
provides information that is not available from the passive sensors.

As a starting point we look at the total cloud fraction in Figure \ref{fig:clt_isccp_calipso}.  The ISCCP and 
CALIPSO products agree fairly well on the 
global mean cloud fraction (65 and 67\%, respectively).   By this measure there are too few clouds in AM4.0 
(biases of -15 and -12 \%).   The ISCCP and CALIPSO data agree well over the oceans, with most of the differences
occuring over land (particularly north of 30) and the region with deep convection in the west Pacific.

The MISR satellite provides good estimates of low-level cloud heights and amounts.  
For this reason and for comparison with both Kay et al., 2012, and Zhang et al., 2019 we compare the cloud fraction 
between observations from MISR and the AM4.0 simulator output in Figure \ref{fig:cf_misr_lowcl}.  
The optical depth is used to distinguish between the thick and thin clouds.  
Consistent with comparisons with ISCCP and CALIPSO we see that AM4.0 has fewer clouds than observed.  
AM4.0 produces the observed pattern of thick clouds, except in the tropical Indian Ocean, with a 
bias of -5\% for low, thick clouds.  
The pattern of thin clouds is not reproduced as well, particularly in the southern hemisphere tropics
and has a bias of -16\%.

The distribution of clouds can also be divided into different cloud types based on the height of the cloud and
the optical thickness to create a joint histogram.  
Data from AM4.0 has been compared in a similar way to the observations from ISCCP and MODIS in Z18a.  
Compared to the joint histograms of ISCCP and MODIS data, MISR has a finer
vertical resolution and does a better job detecting the low-level clouds.  We compare the observations to 
\textit{amip} output for the global mean, the tropical mean, and for the midlatitude regions of both hemispheres 
in Figure \ref{fig:misr_sim_vs_mod}.
Consistent with the findings based on ISCCP and MODIS observations, and with Figure \ref{fig:cf_misr_lowcl},
AM4.0 underestimates the cloud fraction, especially for thin low-level clouds.  Figure \ref{fig:misr_sim_vs_mod}
shows that much of this underestimate occurs in the tropical regions.  We can also see differences in the
midlatitude response.  Clouds from AM4.0 agree best with the MISR observations between 30-60S.  In this 
region there are even a few cloud types that overestimate the cloud fraction.

\begin{figure}
  \centering
  \includegraphics[angle=90,width=0.85\columnwidth]{cfmipfigs/calip_9pan_amip_obs_vs_AM4.eps}
  \caption{Cloud Fraction observed by CALIPSO (2007-2016) and modeled with the CALIPSO satelite simulator 
  (amip experiment).
  Dashed line shows meridional profiles of AM4.0 cloud fraction and solid line shows
  the meridional profile of observed cloud fraction.  With only a few exceptions in the polar regions, AM4 underestimates
  clouds in all three vertical ranges with the largest underestimate being of low-level clouds between +/-30.}
  \label{fig:calipso_9pan}
\end{figure}

The global structure of the cloud fields is shown for the upper level, mid level, and low levels in 
Figure \ref{fig:calipso_9pan} in a comparison between observations from CALIPSO and AM4.0.
The longitudinally averaged cloud fraction is shown as a function of latitude in the left most panels.  
Consistent with the comparison with MISR data in Figure \ref{fig:misr_sim_vs_mod} there is a large under-estimation 
of cloud fraction (AM4.0: dashed; CALIPSO: solid) between 
$\pm$ 30 degrees for both mid and low-level clouds (biases of -4.9\% (mid) and -10.2 \% (low)). 
According to the comparison with MISR data this negative bias is especially pronounced below about 4km
for clouds with an optical depth less than 6.5.    
AM4.0 does a better job with the upper level tropical clouds although there is still a negative bias (-2.8\%) 
that is most prominent in the midlatitudes.   
The global maps  in the center and right columns detail where the biases are occurring.  
In the upper levels the clouds are underestimated over most land regions and the storm tracks but are 
slightly overestimated in several tropical oceanic regions.  In the mid-levels the negative bias tends to be larger 
over tropical land and in the region of the inter-tropical convergence zone.  
The low-levels have large biases over much of the tropical Pacific ocean, as well as in the stratocumulus zones 
and the southern tropical Atlantic ocean.   
AM4.0 produces more Low-level clouds than observed over land in the high-latitudes.  
The zonal mean cloud fraction profiles from CALIPSO that are shown in the left panel of  Figure \ref{fig:calipso_9pan}
will be discussed more in the next section in comparison to some of the coupled model CM4 experiments and
several of the CFMIP experiments that were run with AM4.0.

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_climo_hist_amip_obs_10yr.eps}
  \caption{Comparison of cloud fraction among observations from CALIPSO, the \textit{amip} and 
  \textit{historical} experiments.  To maximize the overlapping years with the observation period of CALIPSO
  (January 2007 - December 2016), only the 10 year period between January 2005 and December 2014 is
  used from the \textit{amip} and  \textit{historical} experiments.  The cloud fraction from the full \textit{amip}
  time period and from early periods of the historical experiment are very similar 
  (almost entirely less than 1\% difference).   Note that the regions poleward of
  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  
  Coupling the atmosphere to a dynamic ocean only leads to slight improvements in the CF bias.}
  \label{fig:calipso_amip_historical}
\end{figure}

\textit{This paragraph should serve as a bridge between the COSP observations, amip and historical experiments, TOA fluxes, and feedbacks.
While direct comparisons between GCM output and satellite observations are only possible over the recent decades, experiments that use
historically based data and extend over longer time periods can give insight into the relationship between cloud area, radiative fluxes
and the decadal variability of the climate feedback parameter.  The \textit{amip}, \textit{amipPIforcing}, and \textit{historical} experiments are useful
for these purposes.  Pronounced decadal variability of the climate feedback parameter has been shown to be closely tied to 
variations of the SW CRE and the low-level clouds (Gregory and Andrews, 2016; Zhou et al., 2016; Silvers et al., 2018).}
Plotting the cloud fields as a function of latitude and height emphasizes the similarities and differences 
between the various experiments while also allowing for a comparison with the high-, mid-, and low-level clouds 
that have been observed by CALIPSO.  Overall the clouds in the $amip$ and $historical$ simulations are similar to 
each other, as we would expect (Figure \ref{fig:calipso_amip_historical}) given their similar radiative forcing 
and experimental configuration.  The differences between the clouds of 
these two experiments are due to the different SST and sea-ice patterns.  The SST patterns and 
sea ice concentrations in the \textit{amip} experiment are
prescribed based on observations, while those of the \textit{historical} experiment are the result of the 
interactions between the atmosphere and dynamic ocean and sea-ice models.  
Figure \ref{fig:calipso_amip_historical} thus shows how the clouds change 
as a result of SST biases over the observational period.   There are two distinct biases in this case, 
the bias in SST generated from differences between the SST of the coupled model and observations,
%the SST bias  that is due to the difference between the SST generated 
%from the coupled model and observations 
as well as the bias in the cloud field relative to observations that is present in both 
experiments.  As reference, the latitudinal profiles of cloud fraction from the CALIPSO observations that 
were discussed in the previous section are also plotted in  Figure \ref{fig:calipso_amip_historical}.
The overall latitudinal structure of the cloud fraction profiles match well between the model results and 
CALIPSO but the negative cloud bias from AM4 and CM4 is apparent at most latitudes and all three levels.  
There is a particularly large positive bias poleward of about 60N in the low-level clouds.

\subsection {Top-of-Atmosphere Radiative Fluxes}

Clouds have an enormous regional impact on the climate and ecology at the surface of the Earth.   Precipitation 
at a given point can range from zero to XX mm/day and a range of incoming solar radiation at the surface of 
(range of rsus (contrasting with rsuscs?)).  However, the impact of clouds on climate is felt, not at the surface, 
but through the fluxes of radiation at the TOA.   These fluxes show directly how clouds (and other elements) alter
the incoming and outgoing energy of the Earth system and are fundamental to all estimates of the 
climate sensitivity.

During the developmental of the AM4.0 GFDL model particular care was given to ensuring that the energy budget at 
the top of the atmosphere compared well with observations (Z18a).  The data set that was used as a target
was the CERES-EBAF TOA radiative fluxes, version 2.8 (Loeb et al., 2009).  
% probably don't need the next few sentences but here they are for now...
As a result of this focus AM4.0 succeeded at decreasing several long standing biases from previous GFDL models.  
In particular AM4.0 has a reduced tropical OLR bias and a reduced SW bias over much of the southern hemisphere oceans.   
Based on AM4.0 data that was used for the CMIP6 \textit{amip} experiment, the total TOA flux bias is -0.15 $ \rm{W m^{-2}}$,  % Fig 6 from Z18a
the bias in CRE due to longwave radiative fluxes is $-2.4 \rm{W m^{-2}} $ and the bias due to CRE of the shortwave radiative fluxes   
is $-1.1 \rm{W m^{-2}} $.  
% https://eosweb.larc.nasa.gov/project/ceres/ebaf_toa_table.    % webpage with CERES info
After the AM4.0 development was frozen and the process of documentation 
was underway, the CERES-EBAF data version 4.1 was released.  When comparing the same 
AM4.0 \textit{amip} experiment to the 
newer version of CERES-EBAF data we find biases of $-2.2 \rm{W m^{-2}} $ for the longwave CRE and 
$-2.9 \rm{W m^{-2}} $ for the shortwave CRE (Figure \ref{fig:ceres_cre_4p1}).  Although the magnitude of bias 
differs when compared to the two versions of CERES-EBAF, the spatial pattern is very similar.   
The comparison of the total 
CRE in Figure \ref{fig:ceres_cre_4p1}  shows a cooling of about 25 $\rm{W m^{-2}}$ in AM4.0 which is about 
5 $\rm{W m^{-2}}$ more than CERES-EBAF.  The overall pattern compares
well with the observations although the cooling from the highly reflective stratocumulus regions is too small and
too far from the coastlines. 
This bias is clearly seen in the SW CRE and highlights the regions with the largest
positive CRE bias resulting from too few stratocumulus clouds.  Also of note is a pervasive negative bias in the SH oceans.   
  As previously discussed (e.g. Kay et al., 2012) these longwave and shortwave CRE 
biases are difficult to interpret because model developers often tune models to match particular CERES-EBAF data 
sets despite the well known fact that different versions of the CERES-EBAF data lead to changes in the observed CRE of
several $\rm{W m^{-2}}$.   Our aim in discussing this for AM4.0 is transparency in the model development process, 
as well as to point out that AM4.0 represents a significant improvement in the spatial biases over previous versions
of GFDL models (Z18a) and that both versions of the CERES-EBAF data show similar spatial patterns of bias in the 
simulated clouds  from the AM4.0 \textit{amip} experiment.

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/radflux_toa_netcre_ceres4p1.eps}
  \caption{Top-of-the-atmosphere CRE from CERES-EBAF ed4.1 and from the AM4.0 \textit{amip} experiment.  
  The bottom row shows the AM4.0 bias (CERES-AM4.0) for the LW CRE and SW CRE components.}
  \label{fig:ceres_cre_4p1}
\end{figure}

Should these biases be computed using only the AMIP years that 
correspond to the CERES years? 
Can we conclude that we have a problem of too few and too bright clouds?   (Webb et al., 2001? Nam et al., 2012)

\section{The Role of Clouds in AM4.0/CM4.0/Aquaplanets in Determining and Influencing Climate Sensitivity}

% A paragraph, either here or earlier that clearly states to what degree and why we think that changes in clouds
% are a critical element in determining why different models have different sensitivities.  Papers that should probably
% be cited are Bony and Dufresne, 2005, Webb et al. (the convection off paper), the Bretherton review on cloud 
% feedbacks, the CFMIP paper?  It would be  nice to cite more of the original papers and less of the review papers.  
% Probably some of Zelinka's papers.

The set of new models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate sensitivities.  
One way of quantifying this sensitivity is with the climate feedback parameter, which 
varies among a suite of CMIP6 experiments between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).  
The models that are the focus of this paper (AM4.0 Aquaplanet, AM4.0, CM4.0) simulate several 
distinct configurations which account for some of the differences in the climate feedback parameter.  
After a brief review of the methods for estimating the climate sensitivity we show in this section how much of the difference is 
due to experimental configuration and how much is due to differences in the CRE.  
We also show how the cloud fraction varies among
the experiments as a function of latitude and consider the cloud distribution in the context of the observed
CRE from the previous section.  The CRE is an effective tool for evaluating the influence of 
clouds on the climate.  It is well known (Soden et al., 2004) that a change in the CRE is not a direct measure of the cloud 
feedback, and that non-cloud related values of CRE can occur.  However, there are many cases of 
the productive use of the CRE as a way to diagnose cloud effects (e.g. Cess et al., 1989; Webb et al., 2001; 
\citeA{Ringer_etal_2014}; Andrews et al., 2015), it is simple to calculate, and
it allows for direct comparisons with previous studies.  The true cloud feedback usually corresponds 
to a positive shift of the change in CRE values by roughly 0.3 $\rm{W m^{-2}K^{-1}}$ (Soden et al., 2004).  The total cloud feedback of a model 
is therefore more positive than will be implied by the CRE.

Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
The clouds in these simulations respond to a variety of different conditions including different
patterns of prescribed SST, the presence or absence of land/sea ice, and in the case of the aquaplanet
experiments, a lack of cloud-aerosol interactions which are present in the AGCM and coupled 
experiments (AOGCM).

\subsection{The Cloud Radiative Effect - Probably should Change.. What is the Climate Sensitivity?}

Due to a combination of changing computing power and differing objectives, the sensitivity of Earth's climate to 
perturbations has been estimated in many different ways over the past few decades.  
We have computed the climate feedback parameter that appears in Table 1 with multiple methods.  
Three common methods are briefly described here.  
First, the climate sensitivity can be estimated from the change in radiative flux at the top of the 
atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990).  
Second, the climate
sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
instantaneously quadrupled relative to the pre-Industrial values.  Linear regression can then be used to 
estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
and used by the IPCC.  Third, the climate sensitivity
can be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
$\rm{CO}_{2}$ concentration.   This method is used to define the Transient Climate Response (TCR).
For a particular climate model, the only way to be sure of the climate sensitivity is to run the 
coupled model after a perturbation has been applied and wait until the model has fully 
equilibrated.  Evidence indicates that this takes thousands of years of 
simulation (Stouffer, 2004; Li et al., 2012; Paynter et al., 2018; Rugenstein et al., 2019).
Because of the limiting cost of such long experiments, determining an accurate measure 
of the climate sensitivity to perturbations from a simulation that is not fully equilibrated is an 
essential component of climate science.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).  The \textit{amip p8K} is not a separate experiment but
shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
    \begin{tabular}{*{8}{c}}
    \hline
    \hline
 Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
    Net          &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
    \\
    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11          & 0.65   & -0.30  \\  
    \\
    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10          & 0.14  & 0.02    \\  
    \\
    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21         & 0.5  & -0.32       \\  
    \\
    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03         & -1.7   & -1.94      \\  
    \\
    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30          & 0.6    & 0.76        \\  \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:lambda}
\end{center}
\end{table}

The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
differences in the measures of sensitivity reveal important details of the physics that underly the response
of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
experiments are the historical simulation (\textit{historical}: years 1850-2014),  the abrupt quadrupling of 
$\rm{CO}_2$ concentration (\textit{abrupt-4xCO$_2$}: 300 years for this paper), and the experiment in 
which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: 150 years, doubling at year 70).  
The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
observed historical record.  This has frequently been used to estimate the climate sensitivity using the 
energy budget method 
(Otto et al., 2013, Armour et al., Andrews et al., \citeA{Winton_etal_2020}; Lewis and Curry?).  
The \textit{abrupt-4xCO$_2$} experiment has been utilized by the IPCC to derive measures of the 
ECS among the CMIP5 and CMIP6 models using a linear regression of the change in TOA radiative fluxes 
and surface air temperature over the first 150 years of the response to the increase in $CO_2$ 
concentration (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
$\rm{CO}_2$ concentration, the \textit{1pctCO2} is an experiment of the Earth system when 
there is a  1 \% per year increase of the $\rm{CO}_2$ concentration until it is doubled relative to the 
pre-Industrial values.  The sensitivity at the point of doubling is defined 
as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
will reach (insert 2xCO2 value) around the middle of this century.

The radiative feedbacks at the TOA were computed for a collection of CMIP5 models by Ringer et al., 2014.  
The results from that study provide a convenient point of reference for our findings.  
Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models.  
That is, for the coupled abrupt $4xCO_{2}$ experiment, feedbacks are computed as  
the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
(\cite{Gregory_etal_2004}; Andrews et al., 2012).  For the atmosphere only experiments 
(\textit{amip-p4K, amip-m4K, amipFuture}, and \textit{aqua-p4K}), the feedbacks are calculated as the 
differences in TOA flux anomalies between the perturbation and control experiments, normalized 
by the change in surface air temperature.  In addition, we include values that have been computed from the 
\textit{1pctCO2} experiment.   Positive values indicate a feedback that leads to warming of the climate system.

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
  \caption{Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
  shows the measured CRE from CERES-EBAF 
  observations compared to simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
  shown at left is the simulated CRE from three fully coupled experiments with CM4.0 (\textit{historical},
  \textit{abrupt-4xCO$_2$}, and \textit{1pctCO$_2$}).  Right panel, the CRE feedback from four 
  amip-like experiments.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
  been reversed.}
  \label{fig:CRE_feedback}
\end{figure}

% tentative hypothesis: 
% Amip Future shows a significant difference from amip p4K between about 15S and 65S.  This should lead 
% to a CRE feedback that is quite a bit larger than for amip p4k because the two experiments are have
% nearly identical CRE's at other latitudes.  
%
% meanwhile, plotting the CRE differences from amip shows that amip-p4K and amip-m4K are not as 
% similar as initially suspected from non difference plots.  When the values of amip-m4K are reversed 
% for easier comparison with the warming experiments we see that in the SH amip-m4K is actually between
% amip-future4K and amip-p4K.  In the NH amip-m4K has the strongest CRE response of all three experiments, 
% this is true north of about 40N.  Why?  
%
% I also suspect that this is largely due to the sw_cre.  
% net_cre:  0.0; 0.07; -0.11             range of 0.18. --> amip -m4K is in the middle
%  lw_cre:   0.16;  0.13;   0.10         range of 0.06
%  sw_cre: -0.16; -0.07; -0.21         range of 0.14  --> amip -m4K is in the middle

The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback 
(-0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$, climate feedback parameter?) that results from differences in 
both the cloudy and clear sky fluxes.   The LW CLR feedback is nearly constant between the 
aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   The SW CLR 
feedback is nearly constant across the \textit{amip} experiments but varies significantly
between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
The relatively large range of the SW CRE (either 0.58 $\rm{W m^{-2}K^{-1}}$ or 1.15 $\rm{W m^{-2}K^{-1}}$)
confirms the important role played by mid- and low-level clouds outside of the region of 
deep tropical convection where the LW and SW effects of clouds largely cancel each other.

As described by Ringer et al., 2014, the changes in the SW CLR feedback are largely due to differences 
in the experimental configurations of ice.  The aquaplanet experiments have no land and no sea ice.  
The \textit{amip} experiments have ice in the polar regions, but the ice is prescribed based on observations and 
only changes to a limited degree.  However, the fully coupled experiments \textit{abrupt-4xCO$_2$} and 
\textit{1pctCO2} both allow the extent of sea-ice to change and therefore have a larger positive SW CLR
feedback that results in part from the positive ice-albedo feedback.  Thus, the range of values in the clear
sky radiative fluxes are the result of differences in the physical configuration of the various experiments.  
However, the remaining spread of total feedback parameter among experiments is due to differences
in cloud feedbacks that are not as easily connected to particular experimental configurations.  For 
most of the experiments the SW CRE is negative and exerts a cooling on the system while the 
LW CRE is positive.  For experiments such as \textit{aqua p4K}, \textit{aqua p4K}, and \textit{amip-future4K} 
this results in some cancelation between the CRE feedback terms.  However, in the 
two coupled experiments shown in Table \ref{tab:lambda}, there is little cancelation between
the two components of the CRE feedback.  For the
\textit{abrupt-4xCO$_2$} experiment both LW and SW cloud feedback are positive with a total 
CRE feedback of $0.65 \rm{W\, m^{-2} K^{-1}}$, and in the \textit{1pctCO2} experiment the LW 
CRE feedback is nearly zero 
resulting in a fairly strong  negative total CRE feedback of $-0.30 \rm{W\, m^{-2} K^{-1}}$.      
While the net feedback is the critical measure of sensitivity, the individual components 
reveal much about the experiments.  The LW CLR is nearly uniform across experiments 
due to the fundamental 
physics of the Planck feedback, the SW CLR varies as we expect it to based on the 
physical configuration of the experiments.  It is the relationship between the LW and SW 
components of the CRE that reveals the different ways in which clouds are influencing the 
net climate feedback.

As discussed in the previous section and in Z18a,b, both AM4.0 (\textit{amip}) and 
CM4.0 (\textit{historical}) compare well to the global mean CERES-EBAF TOA radiative fluxes.  
It is also interesting to see how the CRE from warming experiments contrast with the current observations
and the experiments based on historical simulations. 
Figure \ref{fig:CRE_feedback} shows the latitudinal distribution of CRE from the CERES-EBAF
observations, two historical experiments (\textit{amip} and \textit{historical}) and two warming 
experiments (\textit{abrupt-4xCO$_2$} and \textit{1pctCO2}).    
Comparing the coupled simulations of warming experiments from CM4.0 to the the CERES-EBAF 
and \textit{amip} TOA fluxes shows how the CRE differs in the \textit{abrupt-4xCO$_2$} and 
\textit{1pctCO2} experiments (Figure \ref{fig:CRE_feedback}).
Despite similar biases relative to observations, these warming experiments show a much
stronger negative CRE in the arctic than the historical experiments, more cloud related 
cooling around 20S and a poleward shifted cloud related cooling around 50S-60S.

To compute the cloud feedback based on the CRE, the control state CRE of 
the \textit{amip} and \textit{aqua} experiments is subtracted from the CRE in the perturbed experiment.  
The latitudinal distribution of the SW CRE is shown in the right panel of Figure \ref{fig:CRE_feedback}.  
This shows which regions are responsible for the large range of differences in the SW CRE shown in Table \ref{tab:lambda}.  
Note from Table 1 that the net CRE is -0.27, -0.11, 0.0, and 0.07 for the \textit{aqua-p4K}, 
\textit{amip-Future4K}, \textit{amip-m4K}, and \textit{amip-p4K}, respectively.  
While some of this range is due to contributions from the LW CRE, the relative values of the net feedback are reflected in the SW CRE.  
Figure (\ref{fig:CRE_feedback}) shows the p4K aquaplanet experiment to have a hemispherically symmetric response 
that is dominated by three bands of cloud response in the deep tropics, at 30, and at 55 degrees.   
\textit{For the three \textit{amip} experiments the hemispheric symmetry is broken by the continents and the strongest cloud 
response is seen to be in the southern hemisphere, specifically between 55S and 65S.}
This figure also shows how different the CRE response for the patterned warming 
(\textit{amip-Future4K}) is from the uniform warming (\textit{amip-p4K}).  
These two experiments both have global mean warming of SST by 4K, but 
the response of the SW CRE is different between 65S and 20N.  The difference 
in the SW CRE between the \textit{amip-p4K} and \textit{amip-Future4K} experiments
is due to the the region between the equator and 65S.  
The meridional distribution of the CRE feedback for the \textit{amip-p4K} and
\textit{amip-m4K} experiments also reveals that despite 
similar net CRE (-1.62 and -1.66), the latitudinal spatial response shown in the CRE
differs considerably between the experiments.

Can we understand these large differences in the cloud feedbacks by looking at the cloud 
fields produced by these experiments?

\subsection{The Distribution of Cloud Fraction in Warming Experiments}

%These different experimental configurations influence how much of an impact the ice-albedo feedback plays.  
%The more dynamic the ice is for a given experiment, the more positive will the SW CLR 
%feedback be as a result of the ice-albedo feedback.

\begin{figure}
  \centering
  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_base_amips_calip.eps}
  \caption{Vertical and latitudinal structure of cloud fraction for \textit{amip}-related experiments and observations from 
  CALIPSO.  The \textit{amip}-related experiments include a uniform warming of 4K (\textit{amip-p4K}), 
  a uniform cooling of 4K (\textit{amip-m4K}), and a 
  patterned warming with a global mean of 4K (\textit{amip-future4K}).  See text for details.}
  \label{fig:calipso_amip_comparison}
\end{figure}

Several of the CFMIP experiments are based on the DECK \textit{amip} experiment.  The cloud fraction from three 
of these \textit{amip}-type experiments (\textit{amip-m4K}, \textit{amip-p4K}, and \textit{amip-future4K}) 
are plotted alongside the CALIPSO observations and the DECK 
\textit{amip} experiment in Figure \ref{fig:calipso_amip_comparison}.  These profiles of cloud fraction verify
several characteristics of warming that we expect based on previous studies.  Warming leads to 
an increase of upper-level tropical clouds and a decrease of low-level tropical clouds.  Probably the most 
obvious warming signal in the cloud fields is an increase in the clouds of the polar regions.  We have also 
including the \textit{amip-m4K} experiment (blue line) in Figure \ref{fig:calipso_amip_comparison} in which the 
SST was decreased uniformly by 4K.  Comparison
with the \textit{amip-p4K} (green line) shows cloud fraction responses that in most cases are mirror images
of each other about the \textit{amip} experiment.   The differences in the cloud response to a uniform warming
of 4K (\textit{amip-p4K}) and a patterned warming of 4K (\textit{amip-future4K}) will be discussed in the 
context of the biases relative to \textit{amip} in a later paragraph.

%\begin{figure}
%  \centering
%  \begin{subfigure}{0.45\textwidth}
% % \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_warming.eps}.
%  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_warming.eps}
%  \caption{Cloud fraction for experiments with warming.  For the coupled model experiments
%  \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted.  
%  For reference cloud fraction from the 
%  \textit{historical} and \textit{amip} are also shown.}
%  \label{fig:warming_exps}
%\end{subfigure}
%\begin{subfigure}{0.45\textWidth}
%  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_warming_amipbias.eps}
%  \caption{Cloud fraction bias (relative to \textit{amip}) for experiments with warming. 
%  For the low-level clouds note that the coupled experiments have a CF maximum bias (5-6\%) at -20 and -75 
%  where the prescribed uniform warming
%  does not.  The coupled model experiments produce much less CF in the latitudes between 30-70.  All warming 
%  experiments have more arctic low-level clouds than the \textit{amip} experiment while the \textit{amip} 
%  experiment has too many arctic low-level clouds based on the CALIPSO data.}
%  \label{fig:warming_exps_bias}
%\end{subfigure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{Silvers_cfmip_SinglePanelFig.pdf}
  \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the right column
  shows values relative to the \textit{amip} experiment.  For the coupled model experiments
 \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted.  
  For reference cloud fraction from the 
 \textit{historical} (purple) and \textit{amip} are also shown.}
  \label{fig:CF_warming}
\end{figure}

Figure \ref{fig:CF_warming}  is similar to Figure \ref{fig:calipso_amip_comparison} but focuses on
warming experiments.  
In addition to the two \textit{amip}-like warming experiments just discussed, Figure \ref{fig:CF_warming} 
plots the cloud fraction of two fully coupled warming experiments from the CMIP6 DECK 
(\textit{abrupt-4xCO2} and \textit{1pctCO2}). The cloud fields in these experiments are 
similar to each other, with the differences arising from either the different SST patterns or the 
different CO$_{2}$ concentrations.  
Overall there is an increase (relative to the historical period) in upper-level cloud fraction and a 
decrease in mid-level cloud fraction for the warming experiments.   The response across warming experiments
of the low-level clouds is more complicated.  Changes relative to the \textit{amip} cloud fraction are shown 
in the right panel of Figure \ref{fig:CF_warming} to help identify the differences.  Two separate cloud responses are apparent.  
%Overall, the coupled warming  experiments and the amip-based warming experiments represent two separate cloud fraction responses to warming.  
Distinctive features of the coupled warming experiments are a strong decrease of NH 
mid-latitude low-level clouds but increases of low-level cloud fraction in the southern hemisphere tropics and the Southern Ocean.  
Distinctive features of the amip-warming experiments are increases of 5-7\% 
upper-level cloud fraction poleward of $-70^\circ$ and large decreases of mid-level SH cloud fraction.  All warming
experiments show an increase of upper-level clouds over the polar regions.  All coupled models 
(including the historical)  have more clouds in the region between 60S and 80S relative to \textit{amip}.
The primary difference between \textit{amip-p4K} and \textit{amip-future4K} is that there is an increase 
throughout much of the SH in low-level clouds in the experiment with a patterned warming.  This is 
reflected in Table 1 where it is clear that the primary differences in radiative feedbacks between these
two experiments is in the SW CRE feedback.

Now that the different cloud fields among the suite of experiments are clear we can revisit the
radiative feedbacks from these experiments to see if there is any correspondence between the 
simulated cloud fields and and the cloud radiative effects.      ???? seems out of place?

%% Beta feedback??  relavent?
%Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
%changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
%low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
%model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
%masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.  
%

% SST patterns, the pattern effect.  Should my discussion paragraph of the pattern effect be 
% the same paragraph/discussion as when I discuss Cess experiments?  
As discussed in Z18b and Winton et al. 2019, despite a Cess sensitivity similar to AM2.1, 
the TCR and ECS of CM4.0 are larger than those of CM2.1, and close to those of CM3.   This implies 
that using the Cess sensitivity to infer the TCR or ECS is not reliable.  
The Cess sensitivity for AM4.0 ($0.57 \, \rm{K\, W^{-1} m^2}$, Z18b, pg 26) is closer to the Cess sensitivity 
% see page 39 of Zhao et al. 2018 part 1 for discussion of Cess sensitivity.  
of AM2.1 ($0.54 \, \rm{K\, W^{-1} m^2}$) than to that of AM3.  This is partly due to the method of converting convective cloud condensate to precipitation in the convection scheme.   
Z18b on the same page describes a Cess sensitivity with AM4.0 when the drop number
is fixed of ($0.52 \, \rm{K\, W^{-1} m^2}$).   
\textit{To what extent is this due to the differences in the SW CRE?  How similar is the interpretation that
Andrews and company put forth with that of Paynter et al?}

The previous section showed that the AM4.0 \textit{amip} simulations underestimates clouds relative to 
the CALIPSO observations.   Simulations over the historical period with the fully coupled model only 
slightly improve on this bias ( Figure \ref{fig:calipso_amip_historical}). 
%and in the case of the abrupt 4xCO2 and gradual 1\% CO2 experiments the bias is worse at almost 
%all latitudes except at 20 degrees south.  
It is instructive to see how the cloud profiles from the different warming experiments compare to 
the \textit{amip} and \textit{historical} experiments.   Figure \ref{fig:warming_exps} shows the basic 
profiles of cloud fraction for \textit{amip}, \textit{amip-future4K}, \textit{amip-p4K}, \textit{abrupt-4xCO2}
 and \textit{1pctCO2} and Figure \ref{fig:warming_exps_bias} shows the biases computed relative to 
 the \textit{amip} experiment.  Relative to \textit{amip} all warming experiments produce an increase 
 of tropical and high-latitude upper-level clouds, and a decrease of mid-level clodus at nearly all latitudes.  
 The low-level cloud response is more complex among the warming experiments with the coupled 
 experiments showing a strong decrease in the northern mid-latitudes, an peaked increase around 
 20S, and an increase in the region of the southern ocean.   The difference between the patterned warming
 experiment (\textit{amip-future4K}) and the uniform warming \textit{amip-p4K} is primarily in an 
 increase of southern hemisphere clouds where the \textit{amip-p4K} actually slightly decreases
 clouds at the same latitudes.  All warming experiments, as well as the \textit{historical} experiment, 
 increase cloud fraction poleward of 70N.  All three coupled experiments have more clouds in the sourthern 
 ocean relative to \textit{amip}.

The two coupled warming experiments (\textit{abrupt 4xCO2} and \textit{1pctCO2}) have some interesting 
differences from both the \textit{amip} and the \textit{historical} simulations.   
These warming experiments have a distinct peak (about 5\%) of low-level cloud fraction 
 at about 20S that both \textit{amip} and \textit{historical} lack (\textit{historical} does have a small but less distinct peak).  
 Additionally, while the low-level clouds of the \textit{amip} and \textit{historical} experiments are almost identical between 
 10-60N, the \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments show a large decrease of cloud fraction between 
 about 30-70N.  Is this decrease of low-level cloud in the NH responsible for a stronger SW cloud feedback relative to the 
 \textit{amip-p4K} and \textit{historical} experiments?  Of the two experiments, the \textit{abrupt-4xCO2} has the 
 least amount of low-level cloud.   Does it also then have the strongest/largest SW CRE?

 When comparing these experiments to the CERES-EBAF observations from the observational period the 
 \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments match the CERES-EBAF CRE better than the 
 \textit{amip} or historical experiments (this doesn't really seem to be the case...).  
 The cloud radiative effect (CRE) is computed for \textit{amip}, \textit{historical}, \textit{abrupt-4xCO2}, and 
 \textit{1pctCO2} and compared to the CRE latitude profile in Figure \ref{fig:CRE_feedback}.
 The AM4.0 simulations shown here compare best with the CERES-EBAF v2.8.  This is likely because v2.8 
 is the version of the data that was used as a reference during the model development.  For comparison we 
 also show the CERES-EBAF v4.1 data.  Although differences between the two versions are clear, the AM4.0 
 models compare relatively well (in the global mean) to both.  The differences between 
 the two observational version are mostly contained to the latitudes between +/- 30.  This excellent agreement with observations 
 of the CRE in the NH for the warming experiments was surprising, but does not in general indicate better observational 
 agreement of the warming experiments relative to the \textit{historical} and \textit{amip} experiments.   
 These warming experiments have a strong arctic and southern ocean response that differs significantly 
 from the historical observations and simulations.   As these are signature CRE changes in a warming 
 climate it is not surprising that they are not present in the historical data.

%\begin{figure}
%  \includegraphics[width=0.6\columnwidth]{cfmipfigs/meridional_CRE_CERES2p8.eps}
%  \caption{The Cloud Radiative Effect}
%  \label{fig:CRE_multiexperiments_ceres}
%\end{figure}
%
%\begin{figure}
%  \includegraphics[width=0.6\columnwidth]{cfmipfigs/cfmip_cre_amip.eps}
%  \caption{The Cloud feedback estimated using cloud radiative effect}
%  \label{fig:CRE_feedback}
%\end{figure}

\section{Conclusions: What can we learn?}

\textit{How much do clouds contribute to our uncertainty in the climate sensitivity?  
Which clouds (high, mid, low, thick, thin, geographic regions) contribute to this uncertainty?
Why do we do a poor job with these clouds in models? }

Comparison with multiple observational datasets has shown that the negative cloud bias
in AM4.0 is strongest in the tropical regions.  However, the cloud distributions and 
cloud radiative effects across multiple experiments reveals that the differences in cloud fields that 
contribute to different sensitivities are in the mid and high latitude regions.  If the bias in 
the tropical regions was remedied would the differences in cloud fields that are important for sensitivity
still be in the higher latitudes or would we find significant differences in the tropical clouds among 
the various warming experiments?

We have shown that the cloud radiative effect makes up a significant part of the difference 
among models in the climate feedback parameter.  These differences in the cloud radiative
effect are clearly connected to differences in the simulated cloud fraction.  
% For example, when comparing the amip-p4K and amip-future4K experiment (Figure 9) we see a SH cloud fraction 
% that is 1-5\% larger in amip-future4K than it is in amip-p4K.  In the NH and the south of about $60^\circ$
% the two experiments have nearly identical cloud fractions.  Table 1 shows the amip-future4K experiment
% to have a more negative feedback parameter (-1.84 compared to -1.62 W/m2K) that is due largely to the
% SW CRE.  This difference of the SW CRE in the SH is also apparent in the meridional profile of 
% the SW CRE (Figure 7).
All of the experiments examined show cloud biases relative to observations that are larger than the differences of cloud fraction among the experiments.

%The recent model development efforts at GFDL, and participation in CMIP6/CFMIP have provided a 
%valuable opportunity to analyze a group of models that are built on the same code base while 
%spanning a wide range of model configurations.  The model types include an Aquaplanet, an AGCM (AM4.0), 
%and an AOGCM (CM4.0).   One of our goals is to utilize this hierarchy of
%models which are all derived from or dependent on the same atmospheric code base 
%%spans a range of complexity 
%to better understand each of the individual models.
%%It is a bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.

%What is the role of clouds?  There is a difference between clouds contributing to the uncertainty in our 
%estimates of climate sensitivity and their contribution to the total quantity of feedback.  How consistent 
%is the cancelation that I am seeing between the LW and SW CRE (Table 1) with the idea that 
%the LW and SW CRE essentially cancel in the tropics?  How relevant is that to the global mean 
%feedback problem?    
%
%Experiments using Cess-like uniform SST warming as a proxy for climate change have successfully predicted 
%that much of the differences among models are due to the cloud radiative affect.  However, we also know that the 
%sensitivity derived from Cess-like experiments is not a good predictor of the climate sensitivity for a parent, coupled 
%model (Paynter et al., 2018, Silvers et al., 2018, Winton et al., 2020).  Comparison of Cess-sensitivities and 
%coupled model sensitivities combined with patterned prescribed SST experiments using AGCM have demonstrated 
%the significant role of a pattern-effect in determining the sensitivity of a model.  The results presented in this 
%paper confirm the importance of the SST pattern.    
%
%We also know that a method which uses linear regression of a constant forcing experiment to estimate the climate sensitivity only 
%provides an accurate measure of the climate sensitivity when the initial 20-50 years of simulation are excluded from the analysis.  
%The climate sensitivities of models that have been run to equilibrium with millenial-scale simulations show a large discrepency in the
%different time periods used to estimate this sensitivity.    \textit{state why, sw cre.  Andrews et al. 2015?  Rugenstein et al.?}
%
%Clouds in a climate model are highly malleable while also being a dominant factor controlling what the climate sensitivity is for that model.  
%Yet we do not have satisfactory clouds constraints to impose on the clouds of a climate model.  If improving the representation of low-level
%clouds in the GFDL model was the first priority, it could be done.  However it is not the first priority and doing so degrades other elements of 
%the climate.  
%
%Can we shed lite on which particular component of the cloud feedbacks lead to large changes in the sensitivity?   % SW CRE right?
%
%One of our goals was to highlight and learn from the influence of clouds feedbacks across a range of GFDL based models.  Our hope 
%is that by looking at models from a single institution rather than a larger ensemble of CMIP models we will avoid inadvertantly 
%masking important relationships by a multi-model ensemble mean.

Citations to add: 
Klein et al. (probably should cite multiple works)
Caldwell et al., 2016
Webb et al., 2013
Andrews et al., 2015
Vignesh et al 2020?    Assessment of CMIP6 cloud fraction and comparison with satellite observations

\acknowledgments
We thank the efforts of the model development team at GFDL who developed AM4.0 and CM4.0 and made it possible to participate in CMIP6.  We thank the World Climate Research Programme which coordinated and promoted CMIP6.  All CMIP data are available from the ESGF at https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.

 \begin{sidewaystable}
 \caption{ Observational Data Sets Used in This Paper}
 \centering
 \begin{tabular}{l l}
 \hline
 Data  & Description  \\
 \hline
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed2.8   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 2.8  \\
                                     & Reference: Loeb et al. (2009); Smith et al. (2011).  \\
                                     & URL: \url{http://ceres.larc.nasa.gov/documents/DQ_summaries/CERES_EBAF_Ed2.8_DQS.pdf}.   \\
   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed4.1   \\
                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 4.1  \\
                                     & Reference:   \\
                                     & URL: \url{http://ceres.larc.nasa.gov}.   \\
   Cloud amount and optical depth (dates) & Short name:  MISR   \\
                                                                   &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: MODIS  \\
                                                                   & Long name: Moderate Resolution Imaging Spectroradiometer.  \\
   Cloud amount and optical depth (dates)  & Short name: ISCCP   \\
                                                                   & Long name: International Satellite Cloud Climatology Project   \\
                                                                   & Reference: Rossow and Schiffer (1991); Pincus et al. (2012)   \\
                                                                   & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
   Cloud amount  & Short name: CALIPSO   \\
                           & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\
                           & Reference: Chepfer et al. (2010); Cesana and Chepfer (2013)      \\
    \hline
 \multicolumn{2}{l}{$^{a}$Footnote text here.}
 \end{tabular}
 \end{sidewaystable}

% MISR data was downloaded using wget and is now here: 
% /Users/silvers/data/SatData/MISR_fromRoj/atmos.uw.edu/~roj/nobackup/MISR_observations/MISR_CTH_OD_histograms/V7/CMOR

\bibliography{master_refs}

\end{document}

### 2020-04-24 Silvers_cfmip_CRE_SinglePanel.tex
addition of three tex files that are used to generate multipanel figures

\documentclass[varwidth, border=10pt]{standalone}

\usepackage{subcaption}
\usepackage[labelformat=parens,labelsep=quad,skip=3pt]{caption}
\usepackage{graphicx}

\begin{document}

\begin{figure}
  \centering
  \begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_net_ceres_cfmipExps.eps}
\end{subfigure}
\begin{subfigure}{0.48\textwidth}
  \includegraphics[width=\linewidth]{cfmipfigs/CRE_SWonly_feedback_amip.eps}
\end{subfigure}
\end{figure}

\end{document}

### 2020-04-24 Silvers_cfmip_MISR_cloudtable.tex
addition of three tex files that are used to generate multipanel figures

\documentclass[varwidth, border=10pt]{standalone}

%\usepackage{subcaption}
\usepackage{graphicx}
%\usepackage[labelformat=parens,labelsep=quad,skip=3pt]{caption}
\usepackage{subfig}

\begin{document}

\begin{figure}
  \centering
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_glbmn.eps}}
%\end{subfigure}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_sh_30t60.eps}}
  \subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_pm30.eps}}
\subfloat{
  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_nh_30t60.eps}}
\end{figure}

%\begin{figure}
%  \centering
%  \begin{subfigure}{0.48\textwidth}
%  \includegraphics[width=\linewidth]{cfmipfigs/cloud_table_misr_am4_glbmn.eps}
%\end{subfigure}
%\begin{subfigure}{0.48\textwidth}
%  \includegraphics[width=\linewidth]{cfmipfigs/cloud_table_misr_am4_sh_30t60.eps}
%\end{subfigure}
%\end{figure}

\end{document}

### 2020-04-24 Silvers_cfmip_SinglePanelFig.tex
addition of three tex files that are used to generate multipanel figures

--- 2020-04-24 Silvers_cfmip_CRE_SinglePanel.tex
@@
   \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\linewidth]{cfmipfigs/CRE_net_ceres_cfmipExps.eps}
+    \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cf_warming.eps}
 \end{subfigure}
 \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\linewidth]{cfmipfigs/CRE_SWonly_feedback_amip.eps}
+  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cf_warming_amipbias.eps}
 \end{subfigure}

### 2020-05-01 Silvers_WalkerCell.tex
mostly text changes to Silvers_WalkerCell.tex and addition of references to the bib file for WalkerCell

@@
 %cell and convectively coupled tropical waves.  
-In global and Earth-like GCM simulations, the interplay between the overturning 
-circulation and clouds is difficult to disentangle from other active processes such as
-the Hadley cell and convectively coupled tropical waves.  
-%the large-scale circulation and clouds do not 
-%act on each other in isolation but are also influenced by a host of other phenomena such as 
-%the Hadley cell and convectively coupled tropical waves.  
-Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized 
-context have been restricted to relatively small domain sizes and highly simplified physics parameterizations.  
-The result is a gap in the types of simulation for this region that is so important to our 
-understanding of clouds in the Earth's climate system.  
-%The Walker circulation embodies an ideal combination of physical processes that can help us to connect the findings from CRMs, 
-%GCMs, and the observed world.
+In global and Earth-like GCM simulations, the interplay between the overturning circulation and clouds is difficult to disentangle from other 
+active processes such as the Hadley cell and convectively coupled tropical waves.  
+Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized context have been restricted to 
+relatively small domain sizes and highly simplified physics parameterizations.  
+The result is a gap in the types of simulation for this region that is so important to our understanding of clouds in the Earth's climate system.
 
 % Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
-% that transports so much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
+% that transports much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
 % Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
@@
 direction allowing for three dimensional simulations but with a reduced computational cost relative to the default global domain.  
-The domain is flat, not rotating, and has uniform and constant insolation.
-The lower boundary of the domain is a water covered surface with the SST prescribed as a time invariant Gaussian function 
+The domain is flat, non rotating, and has uniform and constant insolation.
+The lower boundary is a water covered surface with the SST prescribed as a time invariant Gaussian function 
 which is 4K warmer in the center (301K/27.85C) of the domain then 
@@
 over a wide range of resolutions.   
-Current generation global GFDL models use 
-a cubed-sphere grid that is composed of six tiles.  We use the model on a single doubly-periodic
+Current generation global GFDL models use a cubed-sphere grid composed of six tiles.  We use the model on a single doubly-periodic
 tile.  This allows the grid-spacing and domain size to be easily changed to minimize the cost of computations.
@@
 levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
-8 model levels.  The changes made to the default AM4.0 physics configuration are as follows.  The cloud-aerosol 
+8 model levels.  Changes made to the default AM4.0 physics in this study are as follows.  The cloud-aerosol 
 interactions were turned off to focus on the interaction between clouds, radiation, and the circulation.  The gravity wave drag 
@@
 physics are very similar to those of AM4.0.  
-This configuration of AM4.0 physics was initially used by \citeA{Popp_Silvers_2017} and as the aquaplanet model that 
-was used as part of GFDL's contribution to the CFMIP component of CMIP6.
+This configuration of AM4.0 physics was initially used by \citeA{Popp_Silvers_2017} and more recently for the aquaplanet model
+used as part of GFDL's contribution to the CFMIP component of CMIP6.
 
@@
 
-One tool that has been commonly used to infer the influence of clouds on a model simulation is to make the clouds invisible to the radiation.  
-This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the 
-atmospheric state.   This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
+One technique that has been commonly used to infer the influence of clouds on the atmospheric is to make the clouds invisible to the radiation.  
+Breaking the two-way interaction between clouds and radiation can then be used as a diagnostic tool.  
+%This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.   
+This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
 More recently, it has been
@@
 strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
-fixed SST are the ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
+fixed SST are an ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
 the atmospheric state.
@@
 labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
-grid-spacing of 25km, while E25 refers to an experiment that is identical to P25 except that the convective parameterization is turned off. 
+grid-spacing of 25km. %, while E25 refers to an experiment that is identical to P25 except that both the deep and shallow convective parameterizations have been turned off. 
 The naming convection for each of the experiments shown in Table \ref{tab:experimentspecs}.   
-Throughout this paper the P100 and P25 experiments, both with and without the LWCRE on are referred to as `GCM-like' and
+Throughout this paper the P100 and P25 experiments, with and without the LWCRE are referred to as `GCM-like' and
 `CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
-Using the CRM-like terminology acknowledges that this model configuration has not been developed as a CRM, has a vertical resolution that is more coarse than other CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.
+The CRM-like terminology acknowledges that this configuration % has not been developed as a CRM, 
+has a vertical resolution that is coarser than many CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.
 
@@
 The E1 and E2 simulations are in many ways similar to the configuration of so-called cloud resolving models.  
-In particular both the deep and shallow convective parameterizations are turned off, and the threshold of grid-cell mean relative humidity 
-which triggers new clouds is changed from the default value of 0.8 to 1.0.  While a grid spacing of 1 or 2km is clearly not small enough
-to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  The primary 
-difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
-System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
-has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  The large-scale cloud
-scheme is based on the \citeA{Tiedtke1993} parameterization.  This was originally designed to be used with GCMs having a coarse grid-spacing
-and includes prognostic equations for both cloud liquid water and cloud fraction.  
+In particular all convection is explicitly resolved, %both the deep and shallow convective parameterizations are turned off, 
+and the threshold of grid-cell mean relative humidity which triggers new clouds is changed from the default value of 0.8 to 1.0.  
+While a grid spacing of 1 or 2km is clearly not small enough
+to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  
+%The primary difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
+%System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
+%has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  
+The large-scale cloud scheme is based on the \citeA{Tiedtke1993} parameterization.  
+This was originally designed to be used with GCMs having a coarse grid-spacing and includes prognostic equations for both 
+cloud liquid water and cloud fraction.  
 However, we are not aware of a fundamental problem in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   
@@
     \\
-  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.73 (0.71)           \\  
+  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.74 (0.73)           \\  
     \\
-  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.69)          \\  
+  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.70)          \\  
     \\
-  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.72)          \\  
+  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.74)          \\  
     \\
- E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & -            \\  
+ E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & 0.72 (0.75)            \\  
     \\
- E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.83 (0.77)           \\ 
+ E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.82 (0.75)           \\ 
     \\
- E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.78 (0.78)         \\  \hline
+ E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.80 (0.80)         \\  \hline
 
@@
 
-\section{The Influence of Interactive Radiation on Clouds and the Organization of the mock-Walker Circulation}
+\section{Cloud Radiative Interactions and the Organization of a mock-Walker Circulation}
 
@@
 two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
-High concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
+The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
 circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
@@
 %over a wider range of SSTs, and for the most part stratocumulus clouds are absent.
-It is worth noting that this state of deep overturning circulation with convection 
+This state of deep overturning circulation with convection 
 and precipitation concentrated in the region of ascent and a dry troposphere in the regions of descent is common
@@
 overturning circulation 
-\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}; Li et al??).  This is 
-due to an increased low-level flux
+\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}. 
+%Li et al?? 
+This is due to an increased low-level flux
 of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
@@
 region of persistent deep convection and a state of aggregation (work in a citation of M{\"u}ller and Hohenegger, 2019).   
-\textit{RCE studies showing convective self-aggregation have illustrated the 
-dependence of the details of the aggregation on the domain size, the physics, or other details of the 
-study.  Using a mock-Walker circulation allows one to study controlled convective aggregation rather 
-then spontaneous convective self-aggregation.  The added constraint of the fixed warm-patch could lead 
-to clarification of the processes that drive important atmospheric interactions.}
+%\textit{RCE studies showing convective self-aggregation have illustrated the dependence of the details of the 
+%aggregation on the domain size, the physics, or other details of the study. } 
+Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation.  
+The added constraint of the fixed warm-patch could lead to clarification of the processes that drive important atmospheric interactions.
 One of the simplest measures of convective aggregation and the large-scale circulation is the fraction of the domain 
@@
 have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
-dependence of aggregated atmospheric states on temperature (\citeA{Khairoutdinov2010}; \citeA{Wing2014}; Cronin and Wing, 2017).  
+dependence of aggregated atmospheric states on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}.  
 While there does appear to be a dependence 
@@
 Shown in Figures {\ref{fig:domdep}} and {\ref{fig:domdep_lwoff}} are Hovm{\"o}ller plots of precipitation after 
-averaging along the short horizontal dimension.  The four panels show simulations with a grid-
-spacing of $25\, \rm{km}$ on a domain with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$, and 
-simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and 
-$16000\, \rm{km}$.  Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
+averaging along the short horizontal dimension.  The four panels show simulations with two grid-spacings 
+($25\, \rm{km}$ and $100\, \rm{km}$) using two different domain sizes (long horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$).
+%, and simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$.  
+Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
 
@@
 On the large domains, the difference between experiments with and without LWCRE is extreme.  
-In contrast to the control experiments in Figure {\ref{fig:domdep}} which all show a narrow region of strong 
+In contrast to the control experiments in Figure \ref{fig:domdep} which all show a narrow region of strong 
 precipitation meandering within about 500 km of the SST maximum at the center of the domain,  the large domain experiments 
@@
   \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
-  25km and 100km.  Panel A shows the 100km experiment on the large domain 100km, (P100L); 
-  B, 25km on large domain, (P25L); C, 100km on small domain, (P100); and D, 25km on small domain 
-  (P25).  For each resolution, the only difference between the two experiments shown is a domain length of 
-  16,000 km or 4,000 km.
-All cases have an SST of 301 K at the center and 297K at the edges.
-The plotted values are: 1,5,10,15,20,30,40,50,60,70,80,90.
-Data have been averaged over the short horizontal dimension.}
+  25km and 100km.  Panel A shows the 100km experiment on the large domain (P100L); 
+  B, 25km on large domain (P25L); C, 100km on small domain (P100); and D, 25km on small domain 
+  (P25).  For each resolution, the only difference between the experiments shown is a domain length of 
+  16,000 km or 4,000 km.  All cases have an SST of 301 K at the center and 297K at the edges.  
+  The plotted contour values are: 1,5,10,15,20,30,40,50,60,70,80,90.  Data have been averaged over the short horizontal dimension.}
   \label{fig:domdep}
@@
 by the convective parameterization but from the boundary layer as a result of large-scale upwelling.
-We also see that the LWCRE (thick lines) dramatically increases
-the large-scale precipitation.  The LWCRE has a much smaller effect on the magnitude of the convective 
-precipitation but does act to spatially concentrate it.  With the exception 
+We also see that the LWCRE (solid lines) dramatically increases the large-scale precipitation.  
+The LWCRE has a much smaller effect on the magnitude of the convective precipitation but does act to spatially concentrate it.  
+With the exception 
 of the P100L LWCRE-off experiment, the convective precipitation produces relatively little of the total precipitation for 
@@
 The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low level cloud radiative
-effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction (check 
-the figures that show convective and large-scale precip separately).  
-\textit{We also demonstrate that it is through the LW cloud radiative effect that this connection is enabled.}
-The low-level clouds are strongly influenced by both the size of the domain and by the LW cloud 
-radiative effect.  The fact that the partitioning of precipitation by the convective and large-scale 
+effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction 
+%(check the figures that show convective and large-scale precip separately).  
+and demonstrate that it is through the LW cloud radiative effect that this connection is enabled.
+The fact that the partitioning of precipitation by the convective and large-scale 
 parameterizations depends on both the size of the domain and the longwave cloud 
@@
 sensitivities of the parameterized physics.   
+The low-level clouds are strongly influenced by both the size of the domain and by the LW cloud 
+radiative effect.
 
@@
 
-We now show results from our simulations of a mock-Walker circulation with both a GCM-like and a CRM-like configuration.  
-In this section we focus on simulations with grid-spacing of 
-1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
+We now use the mock-Walker circulation to compare GCM-like simulations with CRM-like simulations.  
+We focus in this section on simulations with grid-spacing of 1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
 The models agree on 
@@
 
-Notable differences in the precipitation structure that result from the overturning circulation at different resolutions are shown in Figure \ref{fig:hov_4mods_6mn}.  
+Notable differences in the structure of the precipitation that result from the overturning circulation at different resolutions are shown in Figure \ref{fig:hov_4mods_6mn}.  
 Shown are 180 days of precipitation from the P25 (left to right), E25, E2, and E1 simulations.  
-As the resolution increases the distribution of precipitation becomes more regular and consistently centered over the SST maxima in the middle of 
-the domain.  Both the P25 and E25 simulations show more variability at later times compared to these 
+As the resolution increases the distribution of precipitation becomes broader, more consistently centered over the SST maxima, and has 
+lower maximum precipitation rates.  
+Both the P25 and E25 simulations show more variability at later times compared to these 
 first 180 days (similar to what is seen in Figures \ref{fig:domdep}  and \ref{fig:domdep_lwoff} for the P25 and P100 LWCRE-off).  
@@
           \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P25 (thin yellow), E25 (yellow), 
-          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on
-          while dashed lines show the LWCRE-off experiments.  All lines correspond to experiments with explicit 
-          convection.}
+          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on,
+          dashed lines show the LWCRE-off experiments.  All experiments have explicit convection.}
   \label{fig:TotCond}
@@
   \item Over the region with warm SST the surface enthalpy flux among models is in much better agreement, 
-  especially between the experiments with 1 and 2 \textit{km} grid-spacing.
-  primarily because of changes in the latent heat flux.
-  \item decrease both the LTS and the EIS, over both the warm and cold regions ???
+  especially between the E1 and E2 experiments.
+  %primarily because of changes in the latent heat flux.
+  %\item decrease both the LTS and the EIS, over both the warm and cold regions ???
   \item A decreased spatial gradient of $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$ on the lowest 
@@
   and $25 \textrm{km}$ experiments.
-  \item Overturning circulations (as measured by vertical velocity) are stronger and are more consistently centered 
+  \item Overturning circulations (as measured by vertical velocity) are stronger and more consistently centered 
   over the maximum of SST.  
@@
 25\%, wildly different precipitation structures, and surface enthalpy fluxes that vary by as much as 
-60 $\rm{W/m^2}$.
+60 $\rm{W/m^2}$ (Table 2, Figures \ref{fig:domdep}, \ref{fig:hov_4mods_6mn}, and \ref{fig:enthalpy}).
 All simulations use the same dynamical core, radiation, turbulence, large-scale cloud and microphysics parameterizations.  
@@
 the large-scale circulation to the moisture.  The large differences in the surface enthalpy flux
-appear to be due to relatively small differences in the winds near the surface.  This is not necessarily
+appear to be due to relatively small differences in the winds near the surface (Figure \ref{fig:enthalpy}).  This is not necessarily
 surprising and is likely the source of much of the differences among the experiments.  The 
@@
 consistent with previous studies showing the importance of the low-level wind fields for precipitation 
-\cite{Wofsy_Kuang_2012}, Fermepin and Bony, 2014, boundary layer properties \cite{Raymond_1994}, and even the climate 
+(\cite{Wofsy_Kuang_2012}, Fermepin and Bony, 2014), boundary layer properties \cite{Raymond_1994}, and even the climate 
 sensitivity (Silvers et al., 2016).
@@
 %Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005).  
-Many of the previous studies of mock-Walker circulations or simplified models of tropical dynamics (e.g. \citeA{Raymond_1994}, Pierrehumbert, 1995; Larson et al., 1999; Neelin and Zeng, 2000; 
+Many of the previous studies of mock-Walker circulations or simplified models of tropical dynamics 
+\cite<e.g. >[]{Raymond_1994, Pierrehumbert_1995, Larson_etal_1999}, Neelin and Zeng, 2000); 
 Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005)
@@
 Experiments with prescribed SST preclude the possibility of studying feedbacks
-between the circulation, and the relative area of warm and cold SST regions.  
-However, the interaction between clouds, radiation, and the circulation does lead to changes in the area of the dry 
-regions above the boundary layer that allow the tropics to efficiently cool to space and maintain an energetic balance.   
+between the circulation, and the relative area of warm and cold SST regions as in \citeA{Pierrehumbert_1995}.  
+However, out study of the interaction between clouds, radiation, and the circulation shows how these interactions 
+lead to changes in the area of the dry regions above the boundary layer.  
+These dry regions allow the tropics to efficiently cool to space and maintain an energetic balance.   
 %Pierrehumbert lists
@@
 %as possible and see what range of equilibrium states are reached.
+
 Using mock-Walker simulations to benchmark a GCM with a CRM was proposed by \citeA{Jeevanjee_etal_2017}.
@@
 circulation, experiments have been performed with and without the radiative effect of clouds, with and without the 
-convective parameterization, using various domain sizes.  Our results show that 
+convective parameterization, and with multiple domain sizes.  Our results show that 
 the convective parameterization and the longwave cloud radiative effect (LWCRE) strongly interact with each other and 
-often lead to asymmetric results and large differences in the equilibrated state of the atmosphere.
+often lead to asymmetric results and large differences in the equilibrated atmospheric state.
 
@@
 change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
-\textit{reference to Watanabe et al 2018?  Watanabe et al., 2018 found a similar relationship between 
-low-clouds and precipitation in the context climate change experiments.}
+Watanabe et al. (2018) found a similar relationship between low-clouds and precipitation in the context climate 
+change experiments.
 This highlights how sensitive the energetics of the tropical atmosphere are to the distribution of clouds and 
@@
 Three striking changes occur as a result of a four-fold increase in domain width.  The low-level clouds shift 
-upward by more than 100 hPa, there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments,  
+upward by more than 100 hPa (Figure 6), there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments (Figure 5),  
 %and a strong dependence of the quantity of precipitation produced by the large-scale cloud scheme on the LWCRE. 
-and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation.    
+and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation (Figure \ref{fig:conv_vs_ls}).    
 This impact on the large-scale precipitation occurs for the GCM-like experiments on smaller domains as well, 
@@
 %simulations give this impression.}.  
-Many of the characteristics from RCE experiments that have aggregated are present in mock-Walker simulations.   
+Many of the characteristics from RCE experiments with convective aggregation are present in mock-Walker simulations.   
 Deep convection is anchored to a single location with high humidity and is surrounded by dry subsiding regions.  
@@
 As the grid-spacing of models decreases so too does the necessity of representing convection with parameterizations. 
-\textit{As a result, the details of the large-scale cloud scheme will be increasingly important for a correct 
-understanding of the role played by tropical clouds in the processes that are linked to interactions between clouds,
-radiation, and the large-scale circulations.}  
+As a result, the details of the large-scale cloud scheme will be increasingly important in the development of GCMs. 
+% a correct 
+%understanding of the role played by tropical clouds in the processes that are linked to interactions between clouds,
+%radiation, and the large-scale circulations.
 For high resolution models with explicit convection, the upper-level clouds dominate the impact of interactions between 

### 2020-05-26 Silvers_WalkerCell.tex
minor changes to Silvers_WalkerCell tex and bib files

@@
 \affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
-\affiliation{2}{SAIC, Science Applications International Corporation, Reston, VA, USA}
+\affiliation{2}{GFDL/NOAA, SAIC, Science Applications International Corporation, Reston, VA, USA}
 \affiliation{*}{Current Affiliation: School of Marine and Atmospheric Sciences, Stony Brook University, Stony Brook, NY, USA}
@@
 
-%\textbf{Key Points: choose three}
+%\textbf{Key Points: choose three}.   % key points can be at most 140 characters
 \begin{keypoints}
@@
 %  maximum.}
-  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant}
+  \item{Cloud resolving simulations result in more upper-level clouds, relative to lower resolution simulations which have more low-level clouds.}
+  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant.}
   \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation 
@@
  % changes in the low-level clouds and boundary layer structure.}
-  \item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
-  region that is 40\% higher than for the coarser cases with parameterized convection.}
+  %\item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
+  %region that is 40\% higher than for the coarser cases with parameterized convection.}
 %  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
@@
 
-% What are climate modelers doing to reduce uncertainties about cloud processes?
-%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
-%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
-%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
-%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
-%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
-%idealized equatorial tropical Pacific over a range of resolutions.
-
-In the western Pacific warm sea surface temperatures (SST) prevail beneath rising atmospheric motion and deep convective 
-storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
-non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
-connected by a large-scale circulation referred to as the Walker circulation.  
-We analyze an idealization of this circulation to compare the multi-scale interactions between circulations,
-cloud systems, and interactive radiation across experiments with grid-spacing ranging from 1km to 100km.  
-These experiments thus span the range of resolutions between General Circulation Models (GCMs) and 
-Cloud-system Resolving Models (CRMs).  
-Our GCM-like experiments have a large low-level cloud fraction but the CRM-like experiments have more
-upper-level clouds.  This difference in the dominant cloud type leads to opposite atmospheric responses 
-to changes in the longwave cloud radiative effect (LWCRE).  An active LWCRE leads to increased 
-precipitation for GCMs, but decreased precipitation for CRMs.  Decreasing the resolution to 1km and 2km
-results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.
-
-Numerous studies of the Walker Circulation have used simplified 
-theoretical or numerical models.  The focus of this paper is to simulate a mock-Walker
-Circulation with a full-physics General Circulation Model (GCM) run with idealized boundary conditions to provide 
-a connection between the simpler models 
-%and the complex interactions between clouds, 
-%radiation and the large-scale circulation that are present in the tropical Pacific 
-and current GCMs.
-The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory (GFDL).
+The Walker circulation connects the regions with deep atmospheric convection in the western tropical Pacific to the shallow-convection, tropospheric subsidence, and stratocumulus cloud decks of the eastern Pacific.
+Although important to many elements of the Earth system such as tropical precipitation, and cloud feedback processes, the interactions between large-scale tropical circulations and these cloud systems are still not well understood.
+The purpose of this study is to better understand the multi-scale interactions between the Walker circulation, cloud systems, and interactive radiation.
+To do this we simulate a mock-Walker Circulation with a full-physics General Circulation Model (GCM) using idealized boundary conditions.
+Our experiments use a doubly-periodic domain with grid-spacing of 1, 2, 25, and 100km.
+We thus span the range from General Circulation Models (GCMs) to Cloud-system Resolving Models (CRMs).
+Our model is derived from the Geophysical Fluid Dynamics Laboratory (GFDL) atmospheric GCM (AM4.0).
+Our GCM-like experiments have a large low-level cloud fraction while the CRM-like experiments have more upper-level clouds.
+This difference leads to opposite atmospheric responses to changes in the longwave cloud radiative effect (LWCRE).
+Active LWCRE lead to increased precipitation for our GCMs, but decreased precipitation for our CRMs.
+The LWCRE leads to a narrower rising branch of the circulation and substantially increases the fraction of precipitation from the large-scale cloud parameterization.
+Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.
+This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.
+
+%% What are climate modelers doing to reduce uncertainties about cloud processes?
+%%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
+%%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
+%%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
+%%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
+%%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
+%%idealized equatorial tropical Pacific over a range of resolutions.
+%
+%In the western Pacific warm sea surface temperatures (SST) prevail beneath rising atmospheric motion and deep convective 
+%storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
+%non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
+%connected by a large-scale circulation referred to as the Walker circulation.  
+%We analyze an idealization of this circulation to compare the multi-scale interactions between circulations,
+%cloud systems, and interactive radiation across experiments with grid-spacing ranging from 1km to 100km.  
+%These experiments thus span the range of resolutions between General Circulation Models (GCMs) and 
+%Cloud-system Resolving Models (CRMs).  
+%% We analyze an idealization of this circulation with experiments that use a range of grid-spacing from 1km to 100km.
+%% These experiments allow us to examine the multi-scale interactions between circulations, cloud systems, and radiation.
+%% Our experiments span the typical range of resolutions between General Circulation Models (GCMs) and 
+%% Cloud-system Resolving Models (CRMs).
+%Our GCM-like experiments have a large low-level cloud fraction but the CRM-like experiments have more
+%upper-level clouds.  This difference in the dominant cloud type leads to opposite atmospheric responses 
+%to changes in the longwave cloud radiative effect (LWCRE).  An active LWCRE leads to increased 
+%precipitation for our GCMs, but decreased precipitation for our CRMs.  Decreasing the resolution to 1km and 2km
+%results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.   
+%
+%Numerous studies of the Walker Circulation have used simplified 
+%theoretical or numerical models.  The focus of this paper is to simulate a mock-Walker
+%Circulation with a full-physics General Circulation Model (GCM) run with idealized boundary conditions to provide 
+%a link between the simpler models 
+%%and the complex interactions between clouds, 
+%%radiation and the large-scale circulation that are present in the tropical Pacific 
+%and current GCMs.
+%The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory (GFDL).
 By dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate
-some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
-This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes
-a large-scale circulation.
-%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
-%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
-%%Earth's sensitivity to changes in greenhouse gas concentrations (think radiator fins).
-%
-%Both models use approximately the same spatial domain.
+%some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
+%This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes
+%a large-scale circulation.
+%%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
+%%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
+%%%Earth's sensitivity to changes in greenhouse gas concentrations (think radiator fins).
+%%
+%%Both models use approximately the same spatial domain.
 
@@
 to the large-scale tropical motions and are fundamental to the Walker circulation.  
-The Walker circulation is the name of the loop consisting of westward surface winds towards the western tropical Pacific, 
-strong upward motion and deep convection over that region, 
-%of the western tropical Pacific, 
-and the return eastward winds aloft that 
+The Walker circulation is the name of the loop consisting of surface winds towards the western tropical Pacific, 
+strong upward motion and deep convection in that region,  and the return eastward winds aloft that 
 eventually sink towards the surface in the eastern Pacific basin.  
@@
 %Interactions between the radiative flux of energy and clouds are fundamental to the nature of the Walker circulation.  
-The results show that the response of the atmosphere to the 
+Our results show that the response of the atmosphere to the 
 radiative flux of energy depends strongly on the relative amount of clouds at different heights. % type of cloud that is dominant in the atmosphere.  
-It is further shown that GCM-like models are dominated by low-clouds while CRM-like models 
+It is further shown that our GCM-like models are dominated by low-clouds while our CRM-like models 
 are dominated by high-clouds.  This work also argues that an idealized Walker circulation is an 
@@
 and to push the development of models forward.   Models of mock-Walker circulations represents
-an intermediate tier in a hierarchy of models between RCE and more Earth-like models.
+an intermediate tier in a hierarchy of models between Earth-like models and the models of 
+radiative convective equilibrium (RCE).
 
@@
 
-%  The reality is that we were also inspired by Schneider et al. 2017.  Is it possible to tie all that together in a sensible way?  
 % Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
 % the thermodynamic arguments of Kloesel and Albrecht (1989) 
-%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995.  What say I?
+%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995. 
 %\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
@@
 The circulation first noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the 
-Indonesian region that is dominated by deep convection to the eastern Pacific region which tends to 
+western Pacific region with warm SST and strong deep convection to the eastern Pacific region which tends to 
 be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  
@@
 In global and Earth-like GCM simulations, the interplay between the overturning circulation and clouds is difficult to disentangle from other 
-active processes such as the Hadley cell and convectively coupled tropical waves.  
-Most of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized context have been restricted to 
+processes such as the Hadley cell and convectively coupled tropical waves.  
+Many of the studies with CRMs that have focused on the tropical overturning circulation in a more idealized context have been restricted to 
 relatively small domain sizes and highly simplified physics parameterizations.  
@@
 of models has become blurred and there is a need to systematically compare the clouds and their 
-influence on the climate produced by each type of model (Schneider et al., 2017).
+influence on the climate produced by each type of model \cite{Schneider_etal_2017}.
 By simulating a mock-Walker Circulation in the context of both a GCM and a CRM we 
@@
 of moisture with the large-scale circulation.     
-The model used here is based on the GFDL AM4.0 GCM that participated in CMIP6, 
-having a full suite of physics parameterizations.  
-%This includes fully interactive radiation and for the GCM-like cases convective parameterization 
-% for both deep and shallow convective clouds.  
+The model used here is based on GFDL's AM4.0 GCM that participated in CMIP6, having a full suite of physics parameterizations.  
 Rather than a full global domain all of our experiments use a doubly-periodic domain.    
-%We use fully interactive radiation 
-%(\citeA{Raymond_1994}; Tompkins, 2001; \citeA{Kuang_2012}; \citeA{Wofsy_Kuang_2012} used either fixed or gray radiative cooling).    
+This is conceptually similar to Held et al., (2007), which used an earlier generation GFDL climate model on a doubly-periodic domain to study RCE.   
 The combination of a doubly periodic domain and a current generation climate model allow us to analyze the interactions of the 
@@
 models of the tropical circulation, and to many of the recent studies of radiative convective equilibrium (RCE).
-%Our experiments with a grid-spacing of 1km have a higher resolution then the previous studies with CRMs.
 
@@
 simulations from a CRM-like model using one modeling framework based on a single code base. 
-This also serves as the framework with which we naively attempt to transition a GCM 
+This serves as the framework with which we naively attempt to transition a GCM 
 towards a CRM.  Our initial motivation for using the 
@@
 The paper is organized as follows.  Details of the model and the particular experiments used are described
-in the next section. Section three describes the tendency of experiments with parameterized convection 
+in the next section. Section three gives a broad description of the mock-Walker circulation in our simulations and
+describes the tendency of experiments with parameterized convection 
 to settle into states which do not mirror the symmetry of the prescribed sea surface temperature.   
@@
 section 6 includes a brief discussion and lists some of the impacts of the LWCRE and changing 
-resolution.  Conclusions from this study will then be summarized in the last section.   
-The LWCRE is an important element for all of the experiments and will be 
-discussed throughout the paper.
+resolution.  Conclusions are given in the last section.   
+%The LWCRE is an important element for all of the experiments and will be discussed throughout the paper.
 
@@
 recently developed atmospheric global climate model AM4.0 \cite{Zhao_etal18a, Zhao_etal18b} (Z18a and Z18b hereafter).
-AM4.0 uses the GFDL finite-volume cubed-sphere dynamical core FV3 (Harris and Lin, 2013) 
-which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations
-over a wide range of resolutions.   
+AM4.0 uses the GFDL finite-volume cubed-sphere dynamical core FV3 \cite{Harris_Lin_2013}
+which can solve either the hydrostatic primitive equations or the nonhydrostatic fully compressible Euler equations over a wide range of resolutions.   
 Current generation global GFDL models use a cubed-sphere grid composed of six tiles.  We use the model on a single doubly-periodic
 tile.  This allows the grid-spacing and domain size to be easily changed to minimize the cost of computations.
-This study focuses on experiments with grid-spacing of 100km, 25km, 2km, and 1km on several different
+This study focuses on experiments with grid-spacing of 1km, 2km, 25km, and 100km on several different
 sizes of domain.  Additional details are given in Table \ref{tab:experimentspecs}.
@@
 The convection, radiation, large-scale cloud, microphysics, and turbulence parameterizations all remain the same 
-as in AM4.0.   Thus for the experiments with convective parameterization (grid-spacing of 25km and 100km), the 
+as in AM4.0.   Thus for the experiments with the convection parameterized (grid-spacing of 25km and 100km), the 
 physics are very similar to those of AM4.0.  
@@
 \begin{center}
-\caption{Specifications of the simulations used most heavily in this study.  The length of time step is represented by `dt'.  In the Convection
+\caption{Specifications of the experiments used most heavily in this study.  The length of computational time step is represented by `dt'.  In the Convection
 column, `prm'  indicates that convection is parameterized and `expl' indicates explicit convection.
-All of the experiments listed here were also run with the LWCRE turned off and are referred to as LWCRE-off.
-These will be referred to as P100L LWCRE-off, etc.  }
+All of the experiments listed here were also run with the LWCRE turned off and are referred to with a LWCRE-off suffix in the text.
+For example, P100L LWCRE-off, etc.  }
     \begin{tabular}{*{6}{c}}
@@
 
-One technique that has been commonly used to infer the influence of clouds on the atmospheric is to make the clouds invisible to the radiation.  
-Breaking the two-way interaction between clouds and radiation can then be used as a diagnostic tool.  
+One technique that has been commonly used to infer the influence of clouds on the atmosphere is to make the clouds invisible to the radiation.  
+The usual two-way interaction between clouds and radiation is thus broken and a useful diagnostic tool is created.  
 %This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.   
 This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
-More recently, it has been
-implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
+More recently, it has been implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
 In the AM4 code, this is done separately for the longwave (LW) and shortwave radiation.  
 In this study we compare control experiments, in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the LW radiation.  
-These experiments in which clouds do not interact with the LW radiation are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
+These experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
 For the LWCRE-off experiments, both the LW and shortwave radiation are present and interact with 
-the atmospheric state, the clouds still interact with the shortwave radiation, and they still precipitate.   
+the atmospheric state, the clouds still precipitate and interact with the shortwave radiation.   
 Turning off the LWCRE would have a large impact on the surface budget of a coupled model.  
 However, because there is no land in our simulations and the SST is held fixed, the energetics of our experiments are not as
-strongly effected as might be expected.  For this reason, experiments with only a water surface at the lower boundary and 
-fixed SST are an ideal configuration to utilize the LWCRE-off experiments as a way of diagnosing how clouds interact with 
-the atmospheric state.
+strongly effected as might be expected.  Experiments with only a water surface at the lower boundary and 
+fixed SST are an ideal configuration to utilize the LWCRE-off configuration.
 
@@
 grid-spacing of 25km. %, while E25 refers to an experiment that is identical to P25 except that both the deep and shallow convective parameterizations have been turned off. 
-The naming convection for each of the experiments shown in Table \ref{tab:experimentspecs}.   
+The naming convention for each of the experiments is shown in Table \ref{tab:experimentspecs}.   
 Throughout this paper the P100 and P25 experiments, with and without the LWCRE are referred to as `GCM-like' and
@@
 To examine the dependence of our results on domain size, as well as the fundamental role that the LW CRE plays in GCMs
-we run the fully parameterized experiments (P25 and P100) on domains with a long dimension of 4000 km (`small') and 16000 km (`large').  
+we run the fully parameterized experiments (P25 and P100) on a `small' and `large' domain.  The long dimension of the small domains is 4000 km and the long dimension of the large domain is 16000 km.  
 To explore the mock-Walker circulation in the context of both a GCM and a CRM we utilize 
@@
 While a grid spacing of 1 or 2km is clearly not small enough
-to resolve all clouds, it is small enough to resolve cloud-systems and medium to larger sized clouds.  
+to resolve all clouds, it is small enough to resolve many clouds and cloud-systems.  
 %The primary difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
@@
 However, we are not aware of a fundamental problem in using the Tiedtke scheme for large-scale clouds in a model with 1km grid-spacing.   
-The advantage is retaining the identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the 
+The advantage of using the Tiedtke scheme is retaining the identical cloud scheme as is used in the parent GCM; the disadvantage is the greatly increased complexity of the 
 cloud computations relative to many other cloud resolving models.
@@
 
-%To illustrate some of the sensitivities of the GCM to convection and the interaction between clouds, radiation, and 
-%the large-scale 
-%circulation we compare the P25 experiment with analogous experiments in which the longwave CRE is turned 
-%off (P25 LWCRE off, middle 
-%panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
-%parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).
-
 \section{Cloud Radiative Interactions and the Organization of a mock-Walker Circulation}
-
-%\section{The radiative influence on the clouds and organization of the mock-Walker circulation}
 
@@
 SSTs and a humid boundary layer across the full length of the domain.    Superposing the circulation and relative 
-humidity (Figure \ref{fig:rh_psi_P25vsE25}) clearly shows the results of subsidence driven 
-drying over regions with cooler SST (at the edges of the domain) and the strong moistening that results from ascent over the region of high
-SST (in the center of the domain) where the latent heat flux is large.   The circulation is illustrated by the combination of 
+humidity (Figure \ref{fig:rh_psi_P25vsE25}) clearly shows the result of subsidence driven 
+drying over regions with cooler SST (at the edges of the domain) and the tropospheric moistening from ascending parcels which 
+originate in the boundary layer over the region of high SST (in the center of the domain).   
+To illustrate some of the sensitivities to convective parameterization and the interaction between clouds, radiation, and the large-scale 
+circulation we compare the P25 experiment with analogous experiments in which the longwave CRE is turned 
+off (P25 LWCRE-off, middle 
+panels of Figure \ref{fig:rh_psi_P25vsE25}) and in which the convection is made explicit by turning off the convective 
+parameterization (E25, right panels of Figure \ref{fig:rh_psi_P25vsE25}).  
+The circulation is illustrated by the combination of 
 the mass streamfunction in Figure \ref{fig:rh_psi_P25vsE25} and the vertical velocity in Figure \ref{fig:precip_vertvel}.   
-The mass streamfunction illustrates the 
-two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
-The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate are present in the mid-troposphere over the warmer SSTs, while the regions with subsiding 
-circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
+%The mass streamfunction illustrates the 
+%two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
+The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate in the mid-troposphere over 
+the warmer SSTs, while the regions with subsiding circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
 Two distinct circulation cells are present with one below, and one above $500 \, \rm{hPa}$.   
-%Deep-convective activity dominates the region over the warm pool, shallow convection is common 
-%over a wider range of SSTs, and for the most part stratocumulus clouds are absent.
 This state of deep overturning circulation with convection 
 and precipitation concentrated in the region of ascent and a dry troposphere in the regions of descent is common
-to the Walker circulation, tropical two-box models (e.g. Pierrehumbert, 1995, Larson et al., 1999), and 
+to the Walker circulation, tropical two-box models \cite<e.g., >[]{Pierrehumbert_1995, Larson_etal_1999, Bretherton_etal_2006}, and 
 experiments of radiative convective equilibrium which equilibrate to a state with deep-overturning circulations 
-and convective aggregation (e.g. Bretherton et al., 2005).
+and convective aggregation \cite<e.g., >[]{Bretherton_etal_2005}.
+
+\begin{figure}
+  \centering
+      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan_new.eps}
+      \caption{The equilibrated state of the Walker cell for three configurations with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.
+      Shown in the top panels is the relative humidity (shading) and mass streamfunction (black contours).
+      The same contour interval for the mass streamfunction ($6 \times 10^9$ kg/s) is used in all panels.
+      The lower panels show the total (liquid + ice) condensate (g/kg).  
+      Deep and shallow convection are fully parameterized (P25) in the panels on the left, the center panels show P25 LWCRE-off, 
+      and the experiment with LWCRE on, but the convective
+      parameterization turned off is on the right (E25).}
+  \label{fig:rh_psi_P25vsE25}
+\end{figure}
 
@@
 region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
-Averaged over the full domain, the P25 case with paramterized convection results in a 
-dryer atmosphere with less condensate (both liquid and ice). 
-%and with weaker radiative cooling and condensational heating (below 800 hPa). 
-A stronger and spatially concentrated circulation for cases when the clouds interact with the LW 
-radiation can also be seen in Figures 4, 5, 9 and 10 and is particularly apparent in 
-the cases with a large domain (16000 km long dimension).   
-We also find large differences among the experiments in the domain mean precipitation, condensate/clouds, 
-and circulation (see Table \ref{tab:experimentmeans}).  In general the experiments with parameterized convection are much more erratic. 
-Active LWCRE also leads to lower
-values of domain mean OLR and higher domain mean precipitable water (PW) in all cases.
-
-%
-%It can be seen in the left panels of Figure \ref{fig:rh_psi_P25vsE25} that this 
-%results in a stronger circulation with more condensate in the deep convective region and a dryer mid-troposphere
-%relative to the case with the LWCRE-off.
-
-\begin{figure}
-  \centering
-      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan_new.eps}
-      \caption{The equilibrated state of the Walker cell for three configurations with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.
-      Shown in the top panels is the relative humidity (shading) and mass streamfunction (black contours).
-      The same contour interval for the mass 
-      streamfunction (kg/s) is used in all panels.
-      The lower panels show the total (liquid + ice) condensate (g/kg).  
-      Deep and shallow convection are fully parameterized (P25) in the panels on the left, the center panels show P25 LWCRE-off, 
-      and the experiment with LWCRE on, but the convective
-      parameterization turned off is on the right (E25).}
-  \label{fig:rh_psi_P25vsE25}
-\end{figure}
-
-%
-One of the most prominent features of our GCM-like (particularly P25) simulations is an asymmetry (relative to the 
+Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate (both liquid and ice). 
+This default configuration in which the clouds interact with the LW radiation results in a stronger,
+spatially concentrated circulation and will be discussed further in later sections (also seen Figures 4, 5, 9 and 10).
+%A stronger and spatially concentrated circulation for cases when the clouds interact with the LW 
+%radiation will be discussed in later sections (also be seen in Figures 4, 5, 9 and 10), and is particularly apparent for 
+%the cases with a large domain (16000 km long dimension).    
+Active LWCRE leads to lower values of domain mean OLR and higher domain mean precipitable water (PW) in all cases (Table \ref{tab:experimentmeans}).
+
+Interactions between clouds and radiation play a dominant role in determining the fundamental  
+characteristics of our system.  The domain mean precipitation ($\overline{\rm{P}}$) provides one example of this.  
+Because of the tight constraints that connect $\overline{\rm{P}}$, atmospheric condensational heating, and 
+the total radiative cooling, the time evolution of the precipitation is a useful measure of whether a model has 
+reached a state of stationarity, or statistical balance.  Figure \ref{fig:precip_dom_mn} demonstrates that this balance is reached after about 30 
+days for the E2, and E1 simulations, and after roughly 100 days for the P25 and P100 simulations.  Although the variability
+of  $\overline{\rm{P}}$ is fairly large (1-2 mm/d), after the initial adjustment period of a few months, the experiments are steady in time.  This
+is demonstrated in Figure \ref{fig:precip_dom_mn} with the colored circles which show the mean values of $\overline{\rm{P}}$ over the last 4 years (5 months) of the experiments for the GCM-like (CRM-like) experiments.
+After the initial adjustments
+the simulations all oscillate about mean precipitation values which tend to increase with the grid-spacing (Table \ref{tab:experimentmeans}).   
+Despite the same boundary conditions and model base, these experiments have a large range of domain mean precipitation 
+(Table \ref{tab:experimentmeans}) that varies by as much as 0.6 $\rm{mm/d}$ (3.5-4.1 in parameterized experiments; 3.1-3.7 in explicit experiments).  
+Note that the GCM-like experiments have a larger $\rm{\overline{P}}$ than the CRM-like experiments, and that the
+LWCRE leads to larger $\rm{\overline{P}}$ in the GCM-like experiments but smaller $\rm{\overline{P}}$ in the CRM experiments.  
+This will be discussed further in section 5. 
+The large oscillations in $\overline{\rm{P}}$ shown in Figure \ref{fig:precip_dom_mn} are similar to those noted in previous studies 
+\cite{Silvers_etal_2016, Patrizio_Randall_2019}.
+Differences in $\rm{\overline{P}}$ can be understood as a consequence of the differences in upper level cloud fraction 
+and the surface energy budget and will be discussed further in section 5.
+
+One of the most prominent features of our GCM-like simulations is an asymmetry (relative to the 
 symmetric SST distribution) in both the time-dependent and steady-state solutions.  
-This asymmetry is also present in P25 experiments on larger domains and with a grid-spacing of $100 \, \rm{km}$ 
-(Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
+This asymmetry is particularly apparent in the P25 experiment on the small domain but is also present on larger domains and 
+with a grid-spacing of $100 \, \rm{km}$ (Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
 The steady-state precipitation maximum is located  not over the warmest SST but is shifted to slightly cooler temperatures.  
-This asymmetry is apparent in the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.  
+This asymmetry is present in the vertical velocity, mass circulation, relative humidity, specific humidity, and radiative heating.  
 In the Hovm{\"o}ller diagrams (Figures \ref{fig:domdep} and \ref{fig:domdep_lwoff}), the precipitation appears to be averse 
@@
 When the convective parameterization is turned off (E25), the overturning circulation 
-becomes weaker and broader (seen in w, and the mass streamfunction), and the precipitation, cloud fields, and 
-circulation reside over the SST maximum (but only for about 1 year before the variability 
+becomes weaker and broader (seen in vertical velocity, and the mass streamfunction, Figures \ref{fig:rh_psi_P25vsE25} and \ref{fig:precip_vertvel}), 
+and the precipitation, cloud fields, and circulation reside over the SST maximum (but only for about 1 year before the variability 
 increases).    
-While the parameterized convection plays a large role in driving this asymmetry, it appears to be not entirely a 
+While the parameterized convection plays a large role in driving this asymmetry, it is not purely a 
 result of the convective parameterization, but also due to an interaction between the convective 
@@
 experiments is unclear.
-
-Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution have been noted 
-many times in previous literature \cite{Bretherton_etal_2006, Wofsy_Kuang_2012}; Ming Zhao, see \citeA{Jeevanjee_etal_2017}
-but the irregularities have tended to be symmetric about the SST maximum.  This is broadly consistent 
-with our simulations when the convection is entirely explicit (E25, E2, and E1, discussed further in section 
-4), but is strikingly different than for the P25 and P100 experiments.
 
@@
   \centering
-      \includegraphics[width=0.8\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
-  \caption{Domain mean precipitation as a function of time.  All data has been smoothed with a running mean filter.  
-  Thick lines are the control experiments, thin lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 cases
-  while the P25 and P100 cases show only the first out of five years of the time series.}
+      %\includegraphics[width=0.8\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+      \includegraphics[width=0.8\columnwidth]{walkerfigs/DomMnPrecip.eps}
+  \caption{Domain mean precipitation as a function of time.  All data have been smoothed twice with a 9-day running mean filter.  
+  Solid lines are the control experiments, dashed lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 experiments
+  while for P25 and P100 only the first two out of five years is shown.
+The dots at far right show the time mean values for the last 4 years (P25, P100) and last 5 months (E1, E2).
+Filled (hollow) dots show values from control (LWCRE-off) experiments.
+}
     \label{fig:precip_dom_mn}
@@
 
-Despite the same boundary conditions and model base, the experiments documented here have a
-large range of domain mean precipitation ($\rm{\overline{P}}$, Table \ref{tab:experimentmeans}) that varies by as much as 
-0.6 $\rm{mm/d}$ (3.5-4.1 in parameterized experiments; 3.1-3.7 in explicit experiments).
-This highlights how dominant the interaction between clouds and radiation can be in determining the 
-characteristics of a system.
-Because of the tight constraints that connect the domain mean precipitation, atmospheric condensational heating, and 
-the total radiative cooling, the time evolution of the precipitation serves as a useful measure of whether a model has 
-reached a state of stationarity, or statistical balance.  Figure \ref{fig:precip_dom_mn} demonstrates that this equilibrium is reached after about 30 
-days for the E2, and E1 simulations, and after about 50 days for the P25 and P100 simulations.   After the initial adjustments
-the simulations all oscillate about mean precipitation values which tend to increase with the grid-spacing 
-(Table \ref{tab:experimentmeans}).   The fact that E1 and E2 reach equilibrium sooner than E25, P25, or P100 and that the period of oscillation 
-about the domain mean precipitation is smaller helps to justify the 6 month simulation times for E1 and E2.  
-%The period of oscillation is much larger for the GCM like simulations than it is for the CRM like oscillations.
-The large oscillations in domain mean precipitation are similar to those noted in previous studies 
-\cite{Silvers2016, Patrizio2019}.
-%(Silvers et al., 2016; Patrizio and Randall, 2019).   
-%The experiments with a higher resolution have a lower value of domain
-%mean precipitation, with the E2 simulation having the lowest (3.1 mm/day).  
-Differences in $\rm{\overline{P}}$ can be understood as a consequence of the differences in upper level cloud fraction 
-and the surface energy budget and will be discussed further in a later section.
-
-Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
-overturning circulation 
-\cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}. 
-%Li et al?? 
-This is due to an increased low-level flux
-of moist static energy into the convective regions.  While our mock-Walker circulation is distinct from radiative
-convective equilibrium and the resulting convective self-aggregation, there are obvious similarities between our 
-region of persistent deep convection and a state of aggregation (work in a citation of M{\"u}ller and Hohenegger, 2019).   
-%\textit{RCE studies showing convective self-aggregation have illustrated the dependence of the details of the 
-%aggregation on the domain size, the physics, or other details of the study. } 
+One of the simplest measures of convective aggregation and the large-scale circulation is the subsidence fraction (SF), the fraction of the domain 
+in which the mid-tropospheric air is subsiding \cite{Coppin_Bony_2015}.  
+As convection becomes more organized, or aggregated, the SF will increase.  For an overturning circulation a contraction of the convective 
+region should result in a larger subsidence fraction.  
+This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
+or equal to the case with LWCRE-off (with the exception of E25).   
+While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
+region of persistent deep convection clearly corresponds to a state of aggregation. 
 Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
-The added constraint of the fixed warm-patch could lead to clarification of the processes that drive important atmospheric interactions.
-One of the simplest measures of convective aggregation and the large-scale circulation is the fraction of the domain 
-in which the air is subsiding, referred to as the subsidence fraction (SF).  
-As convection becomes more organized, or aggregated, the SF will increase.  We expect 
-for an overturning circulation that a contraction of the convective region would result in a larger subsidence 
-fraction.  This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments, the cases with LWCRE-on
-have a larger SF (with the exception of E1, for which SF is constant).  Much has been written about a 
-dependence of aggregated atmospheric states on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}.  
-While there does appear to be a dependence 
-on temperature, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
+%The added constraint (relative to RCE) of the fixed warm-patch of SST could lead to clarification of the processes that drive important atmospheric interactions.
+Previous studies have shown a dependence of aggregation 
+on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
 state can vary among experiments with identical SST.  Having a prescribed SST warm 
 patch ensures that the simulations will be `aggregated' to some degree.  
-The SF indicates not only whether an 
-experiment is aggregated, but also the spatial extent of the overturning circulation.  
+%The SF indicates not only whether an experiment is aggregated, but also the spatial extent of the overturning circulation.  
 Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
@@
 
+%\textit{Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
+%overturning circulation \cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}.  
+%This is due to an increased low-level flux of moist static energy into the convective regions. }
+
 \section{The Influence of Domain Size on Low-level Clouds and the Large-scale Precipitation}
 
-When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
-two of the most fundamental choices that must be made.   One the goals of this study was to explore the results of 
-changing grid-spacing over a wide range of values.  To simplify the analysis we have in most cases chosen to keep the 
-long horizontal dimension fixed at $4000\, \rm{km}$.  However, previous studies 
-\cite{Bretherton2005, Bretherton_etal_2006, Muller2012, Jeevanjee2013, Silvers2016, Patrizio2019}
-have documented sensitivities of the equilibrated state to domain size for similar experiments
-of radiative convective equilibrium.   
-The analysis of the previous, and of the next, sections focus on results from 
-experiments using a domain with a long domain length of $4,000 \, \rm{km}$.  However when comparing those results
-to experiments with a long domain length of $16,000 \, \rm{km}$, we find interesting 
-sensitivities to the domain size that are described in this section.
-
-The evolution in time of the precipitation field clearly illustrates how much the spatial distribution can vary as a 
+The evolution in time of the precipitation field illustrates how much the spatial distribution can vary as a 
 function of domain size, parameterization of convection, and the effect of the LW radiation due to clouds. 
@@
 averaging along the short horizontal dimension.  The four panels show simulations with two grid-spacings 
-($25\, \rm{km}$ and $100\, \rm{km}$) using two different domain sizes (long horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$).
+($25\, \rm{km}$ and $100\, \rm{km}$) using two different domain sizes (long edge length of $4,000\, \rm{km}$ and $16,000\, \rm{km}$).
 %, and simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$.  
-Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.
-
-At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the 
-precipitation over a smaller geographic extent.   This is consistent with previous work showing that CREs 
-strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
-\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  The structure of the precipitation changes more 
+Figure {\ref{fig:domdep}} shows the control GCM-like experiments and Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.    
+%When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
+%two of the most fundamental choices.   
+%One of the goals of this study was to explore the results of changing grid-spacing over a wide range of values.  
+ Previous studies of RCE
+\cite{Bretherton_etal_2005, Bretherton_etal_2006, Muller2012, Jeevanjee2013, Silvers_etal_2016, Dixit_etal_2018, Patrizio_Randall_2019}
+have documented sensitivities of the equilibrated state to domain size.  
+We have in most cases chosen to keep the long edge length fixed at $4,000\, \rm{km}$. 
+The analysis of the previous, and of the next section focuses on results from 
+experiments using a domain with a long edge length of $4,000 \, \rm{km}$.  However, when comparing those results
+to experiments with a long edge length of $16,000 \, \rm{km}$, we find interesting sensitivities to the domain size that are described in this section.
+
+At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the precipitation over a smaller geographic extent.   
+%This is consistent with previous work showing that CREs 
+%strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
+%\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  
+The structure of the precipitation changes more 
 as a function of domain size than it does as a function of resolution. 
-On the large domains, the difference between experiments with and without LWCRE is extreme.  
+On the large domains, the difference between experiments with and without LWCRE is extreme (compare Figure \ref{fig:domdep}a,b to Figure \ref{fig:domdep_lwoff}a,b).  
 In contrast to the control experiments in Figure \ref{fig:domdep} which all show a narrow region of strong 
@@
 Smaller cells and lines of precipitation develop within this large area with no apparent preference to settle
-over the center of the domain where the SST is a maximum.  As previously noted, 
-these GCM-like simulations equilibrate after approximately 50 days.  There is also a dramatic change in 
-the distribution of precipitation on the $4000\, \rm{km}$ domain simulations after almost 2 years.   The domain mean 
-precipitation does not significantly change in these cases, only the spatial structure.
-
-An additional unexpected change that results from increasing the domain size is an upward shift of the cloud fields.  This is 
-shown with the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low level maximum of 
-condensate is shifted from near 900 hPa in the small domain (thin lines) to between 700-800 hPa in 
-the large domain (thick lines).  There is also a vertical shift in the upper level ice condensate, but it is less
-pronounced.  
-As the domain size increases, so does the domain mean precipitable water ($\overline{\rm{PW}}$).  Active LWCREs lead
-to larger values of $\overline{\rm{PW}}$ in all cases (Table \ref{tab:experimentmeans}).  
-%(Does this tell us anything about precipitation efficiency?)  
-$\overline{\rm{PW}}$ varies by as much as 30\% among the experiments.
+over the center of the domain where the SST is a maximum.  
+%As previously noted, these GCM-like simulations equilibrate after approximately 50 days.  
+There is also a dramatic change in the distribution of precipitation on the $4,000\, \rm{km}$ domain simulations after almost 2 years.   
+The domain mean precipitation does not significantly change in these cases, only the spatial structure.
+
+An additional unexpected change that results from increasing the domain size is an upward shift of the cloud fields.  
+The low-level condensate has a cloud base that decreases in magnitude and shifts from  near 900 hPa in the small domain (thin lines, Figure \ref{fig:TotCond_P25P100}) to between 700-800 hPa in 
+the large domain (thick lines) simulations.
+%This can be seen in the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low- level maximum of 
+%condensate is shifted from near 900 hPa in the small domain (thin lines) to between 700-800 hPa in 
+%the large domain (thick lines).  
+There is also a vertical shift in the upper-level ice condensate, but it is less pronounced.  
+As the domain size increases, so too does the domain mean precipitable water ($\overline{\rm{PW}}$) which varies by as much as 30\% among the experiments (Table \ref{tab:experimentmeans}).   
+Smaller domains (1,024 km compared to 4,096 km wide) were found to have a more focused ascent region, larger precipitation rates, and less low-level clouds in the CRM simulations of \citeA{Bretherton_etal_2006}.
+In contrast, here smaller domains have more low-level clouds and slightly less precipitation rates(Table \ref{tab:experimentmeans}, 
+Figure \ref{fig:TotCond_P25P100}).     
+%Overall the large domains show an upward shift of condensate and have 
+%a much stronger upper level response to the LWCRE being turned off.
+%For the LWCRE-off cases, in agreement with \citeA{Bretherton_etal_2006} we find a more 
+%focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
+%changes little between P25 
+%and P25L but for P100 and P100L the ascent region is much more focused on the large domain (Figure \ref{fig:conv_vs_ls}).
 
@@
   \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwon_huge.eps}
-  \caption{Evolution of precipitation through 3 years of simulation for experiments with a grid spacing of
+  \caption{Evolution of precipitation through the first 3 years of simulation for experiments with a grid spacing of
   25km and 100km.  Panel A shows the 100km experiment on the large domain (P100L); 
   B, 25km on large domain (P25L); C, 100km on small domain (P100); and D, 25km on small domain 
-  (P25).  For each resolution, the only difference between the experiments shown is a domain length of 
+  (P25).  For each resolution, the only difference between the experiments shown is a long edge length of 
   16,000 km or 4,000 km.  All cases have an SST of 301 K at the center and 297K at the edges.  
@@
 that the fraction of the precipitation that is due to the large-scale cloud scheme is closely linked 
-to low cloud cover and total condensate.  
+to low-cloud cover and total condensate.  
 The distribution of convective and large-scale precipitation indicates how the condensational heating
@@
 Precipitation from each of these two components is shown in Figure \ref{fig:conv_vs_ls} as a function of 
-both resolution and domain size.  In the regions of large-scale ascent, most of the precipitation derives 
+resolution and domain size.  In the regions of large-scale ascent, most of the precipitation derives 
 from the large-scale cloud scheme.  Following the terminology of \citeA{Held2007} we could say that most 
@@
 The LWCRE has a much smaller effect on the magnitude of the convective precipitation but does act to spatially concentrate it.  
-With the exception 
-of the P100L LWCRE-off experiment, the convective precipitation produces relatively little of the total precipitation for 
-both resolutions and on both domains.  The dramatic dependence on domain size of the precipitation field that is 
-seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in P25L case
+With the exception of the P100L LWCRE-off experiment, the convective precipitation produces relatively little of the total precipitation.  
+The dramatic dependence on domain size of the precipitation field that is 
+seen in Figure \ref{fig:domdep_lwoff} corresponds to a decrease in the large-scale precipitation of about 65\% in the P25L case
 and an almost complete elimination of the large-scale precipitation in the P100L case.    
-The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low level cloud radiative
+The fraction of precipitation that is due to the large-scale cloud scheme was linked to the low-level cloud radiative
 effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction 
@@
 The fact that the partitioning of precipitation by the convective and large-scale 
-parameterizations depends on both the size of the domain and the longwave cloud 
-radiative effect could imply that the changes of the low-level clouds are being driven largely by 
+parameterizations depends on both the size of the domain and the LW CRE 
+could imply that the changes of the low-level clouds are being driven by 
 sensitivities of the parameterized physics.   
-The low-level clouds are strongly influenced by both the size of the domain and by the LW cloud 
-radiative effect.
+The low-level clouds are strongly influenced by both the size of the domain and by the LW CRE.
 
@@
       \includegraphics[width=0.96\columnwidth]{walkerfigs/Conv_vs_LS_Precip.eps}
-  \caption{Precipitation that is due to the large-scale(blue) cloud scheme and to the convective 
+  \caption{Precipitation due to the large-scale (blue) cloud scheme and to the convective 
   parameterization (black).  
-  Panels on the left show large domains with a width of 16000 km and
-  panels on the right show domains with a width of 4000 km.  LWCRE-off experiments are shown with dashed lines.  }
+  Panels on the left show large domains with a long edge width of 16,000 km and
+  panels on the right show domains with a long edge width of 4,000 km.  LWCRE-off experiments are shown with dashed lines.  }
   \label{fig:conv_vs_ls}
@@
 
-Smaller domains were found to have a more focused ascent region and larger precipitation rates in Bretherton et al., 2006.
-They also found less low-level clouds over the colder SSTs in the small domains (1,024 km wide), relative 
-to a control domain with a width of 4,096 km.   In contrast, here larger domains have larger precipitation 
-rates (Table \ref{tab:experimentmeans}).  
-We find fewer low-clouds on the large domain experiments (P25L, P100L), but a mid-level cloud 
-maximum (Figure \ref{fig:TotCond_P25P100}).   There are notable differences in the domain mean condensate between 
-the default and large domains.  Overall the large domains show an upward shift of condensate and have 
-a much stronger upper level response to the LWCRE being turned off.
-For the LWCRE-off cases, in agreement with B06 we find a more 
-focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
-changes little between P25 
-and P25L but for P100 and P100L the ascent region is much more focused on the large domain.
-
 %We hypothesize than an important difference between our simulations and previous studies which use GCMs
-%is that although the deep and shallow convection is parameterized
+%is that although the deep and shallow convection are parameterized
 %with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
@@
   (b) 25km case with no parameterized convection (E25), (c) 2km control (E2), and (d) 1km control (E1).  
-  The horizontal axis shows the entire longitudinal width of 4000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
+  All panels have a long edge width of 4,000 km with the center of the domain having a prescribed SST of 301 K and the edges 297 K.  
   Data have been averaged over the short horizontal dimension.} 
@@
 \end{figure}
+
+We now use the mock-Walker circulation to compare GCM-like simulations to CRM-like simulations.  
+This section focuses on simulations with grid-spacing of 1km, 2km, and 25km all on a domain with the width of 4,000 km for the long edge.  
+The models agree on the basic circulation pattern and the spatial distribution of mid-tropospheric condensate.  
+However, the E25/P25 simulations produce 4 to 5 times as much low-level cloud and 
+condensate as E2/E1 in the subsiding regions.   As a result the models have a different response 
+to the LWCRE.  In the atmospheric boundary layer the differences among the models of the wind, enthalpy flux, and 
+temperature result in different spatial distributions and amounts of precipitation in the equilibrated state.
+
+Notable differences in the structure of the precipitation that result from the overturning circulation at different resolutions are shown in Figure \ref{fig:hov_4mods_6mn}.  
+Shown are 180 days of precipitation from the P25 (left to right), E25, E2, and E1 simulations.  
+As the resolution increases the distribution of precipitation becomes broader, more consistently centered over the SST maxima, and has 
+lower maximum precipitation rates.  
+Both the P25 and E25 simulations show more variability at later times compared to these 
+first 180 days (similar to what is seen in Figures \ref{fig:domdep}  and \ref{fig:domdep_lwoff} for the P25 and P100 LWCRE-off).  
+The simulations with explicit convection at resolutions typical of cloud-resolving models 
+(E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST.
+Relative to the P100, P25 and E25 simulations, the cloud resolving simulations are able to maintain a smoother distribution of 
+precipitation over a broader range of SST values.  Complex patterns of precipitation over a fixed sinusoidal or Gaussian SST distribution 
+have been noted many times in previous literature \cite{Grabowski2000,Bretherton_etal_2006, Wofsy_Kuang_2012,Jeevanjee_etal_2017}. 
+The irregularities have tended to be symmetric about the SST maximum.  This is broadly consistent 
+with our simulations when the convection is entirely explicit (E25, E2, and E1), but is strikingly different than for the P25 and P100 experiments.
 
@@
 
-We now use the mock-Walker circulation to compare GCM-like simulations with CRM-like simulations.  
-We focus in this section on simulations with grid-spacing of 1km, 2km, and 25km all on a domain with the width of 4,000 km for the long side.  
-The models agree on 
-the basic circulation pattern and the spatial distribution of mid-tropospheric condensate.  
-However, the E25/P25 simulations produce 4 to 5 times as much low-level cloud and 
-condensate as E2/E1 in the subsiding regions.   As a result the models have a different response 
-to the LWCRE.  The differences in the boundary layer of the wind, enthalpy flux, and 
-temperature among the models result in different spatial distributions and amounts of 
-precipitation in the equilibrated state.
-
-Notable differences in the structure of the precipitation that result from the overturning circulation at different resolutions are shown in Figure \ref{fig:hov_4mods_6mn}.  
-Shown are 180 days of precipitation from the P25 (left to right), E25, E2, and E1 simulations.  
-As the resolution increases the distribution of precipitation becomes broader, more consistently centered over the SST maxima, and has 
-lower maximum precipitation rates.  
-Both the P25 and E25 simulations show more variability at later times compared to these 
-first 180 days (similar to what is seen in Figures \ref{fig:domdep}  and \ref{fig:domdep_lwoff} for the P25 and P100 LWCRE-off).  
-The simulations with explicit convection at resolutions typical of cloud-resolving models 
-(E2, E1) show little aversion to the precipitation maximum occurring over the maximum in SST.
-Relative to the P100, P25 and E25 simulations, the cloud resolving simulations are able to maintain a smoother distribution of 
-precipitation over a broader range of SST values.
-
 The influence of resolution on the atmospheric state can be clearly seen in the two-dimensional structure 
@@
 Perhaps the most obvious similarity is the double celled structure in the mass streamfunction and the most 
-obvious difference being the humidity in the center of the domains (RH range of $>$ 40\%). % among E1, E2, and E25.  
+obvious difference being the humidity in the center of the domains where the RH differs by as much as 40\%. % among E1, E2, and E25.  
 %The mid-troposphere 
@@
 dominates.  The E25 experiment has a fairly symmetric double celled structure in stark contrast to the irregular circulation 
-that is present in the P25 experiment (compare with Figure \ref{fig:rh_psi_P25vsE25}). 
+that is present in the P25 experiment (Figure \ref{fig:rh_psi_P25vsE25}). 
 A small third cell has developed in the boundary layer of the 1km experiment.   The high resolution experiments also have 
@@
 above 200 hPa.
+
+Compared to E25, the E1 and E2 experiments have stronger deep overturning circulations and substantially 
+more condensate aloft above the warm patch.    It is also apparent in Figures 
+\ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa 
+decreases with increasing resolution.  
+This is consistent with an overturning circulation that 
+strengthens as the resolution increases and transports more moisture from the low-levels to the 
+mid-troposphere.  It is also consistent with weaker mixing from shallow clouds with decreased resolution as
+discussed in \citeA{Pauluis2006}.   Figure \ref{fig:rh_psi_P25E2E1_lwoff}, with LWCRE-off, shows greater asymmetries 
+and generally weaker circulations below about 500 hPa.  
+When the clouds and radiation directly interact with each other the experiments have a better
+organized and stronger circulation below 500 hPa.  Figures \ref{fig:rh_psi_P25E2E1} and 
+\ref{fig:rh_psi_P25E2E1_lwoff} also show that the E2 and E1 simulations are more 
+similar when the clouds and radiation interact than they are with LWCRE-off.  The subsidence 
+region drying and condensate aloft in the upwelling region have a clearer dependence on resolution for the
+LWCRE-off experiments.  This suggests that the interactions between clouds and radiation help the 
+atmosphere to converge towards a particular state that is less dependent on resolution.
+
+%The domain mean condensate is closely related to the distribution of clouds and is an important measure of the 
+%steady state reached by these experiments.  This in turn influences 
+%the distribution and flow of energy throughout the atmosphere and the radiation that is emitted to space.  
+%It also provides clues about the strength of convection and vertical mass transport.     
+The domain mean condensate is closely related to the distribution of clouds and the flow of energy through the atmosphere.  
+It provides clues about the strength of convection and the vertical mass transport.     
+Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
+(solid lines) and the corresponding experiments with the LWCRE-off (dashed lines).  Similar profiles for the experiments
+with parameterized convection were discussed in the previous section (Figure \ref{fig:TotCond_P25P100}).  
+The GCM-like P100, P25, and E25 experiments have much higher values of low-level liquid condensate while the CRM-like 
+E2 and E1 experiments have much higher values of upper level ice condensate.  
+%There is a substantial difference between the GCM-like P100, P25, and E25 experiments and the CRM-like E2 and E1 experiments 
+%with the former having much higher values of low-level liquid condensate and the later having much higher values of upper level ice condensate.  
+Although our experiments differ from RCE, the results are consistent with \citeA{Pauluis2006} who showed that for 
+decreasing resolution an RCE model had a moist bias in the sub-cloud layer and a dry bias in the troposphere above.
 
@@
 
-Compared to E25 both the E1 and E2 experiments have a stronger deep overturning circulation above the warm 
-patch and they have significantly more condensate aloft in this region.    It is also apparent in Figures 
-\ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} that the condensate below 800 hPa 
-decreases with increasing resolution.  
-This is consistent with an overturning circulation that 
-strengthens as the resolution increases and transports more moisture from the low-levels to the 
-mid-troposphere.  It is also consistent with weaker mixing from shallow clouds as resolution decreases as
-discussed in \citeA{Pauluis2006}.   Figure \ref{fig:rh_psi_P25E2E1_lwoff}, with LWCRE-off, shows greater asymmetries 
-and generally weaker circulations below about 500 hPa.  
-When the clouds and radiation directly interact with each other the experiments have a better
-organized and stronger circulation below 500 hPa.  A comparison of Figures \ref{fig:rh_psi_P25E2E1} and 
-\ref{fig:rh_psi_P25E2E1_lwoff} also shows that the E2 and E1 simulations are much more 
-similar when the clouds and radiation interact than they are with LWCRE-off.  However, the subsidence 
-region drying and condensate aloft in the upwelling region have a clearer dependence on resolution for the
-LWCRE-off experiments.  This suggests that the interactions between clouds and radiation help the 
-atmosphere to converge towards a particular state that is less dependent on resolution.
-
-The domain mean condensate is closely related to the distribution of clouds and is an important measure of the 
-steady state reached by these experiments.  This in turn influences 
-the distribution and flow of energy throughout the atmosphere and the radiation that is emitted to space.  
-It can also indicate the strength of convection and vertical mass transport.     
-Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
-(solid lines) and the corresponding experiments with the LWCRE-off (dashed lines).  Similar profiles for the experiments
-with parameterized convection were discussed in the previous section (Figure \ref{fig:TotCond_P25P100}).  
-There is a substantial difference between the GCM-like P100, P25, and E25 experiments and the CRM-like E2 and E1 experiments 
-with the former having much higher values of low-level liquid condensate and the later having much higher values of upper level ice condensate.
-Although our experiments differ from RCE, the results are consistent with \citeA{Pauluis2006} who showed that for
-decreasing resolution an RCE model had a moist bias in the sub-cloud layer and a dry bias in the troposphere above.  
-%Although our experiments are not strictly in RCE, our results agree with those from \citeA{Pauluis2006}.
-
-Comparing experiments with and without the LWCRE highlights key differences between our GCM and CRM experiments.  
+% Is the paragraph below out of place?  As written, it references Figures 9, 10, and 13.  Should it be near the end of this section
+% as a sort of summary of the effects of LWCRE?  I also don't currently like the last sentence.... It has potential but as written it 
+% says nothing.
+
+The LWCRE plays a major role in determining the equilibrium RH, total condensate, and LW radiative heating of the troposphere.  
+This is highlighted by comparing experiments with and without the LWCRE. %  highlights key differences between our GCM and CRM experiments.  
 The upper panels of Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show that the 
-interactions between LW radiation and clouds lead to an enhanced
-drying of the troposphere in regions of subsidence, relative to the cases when the LWCRE is not active.  
-This is especially true for the simulations with a grid-spacing of 1 km and 2 km.  
+interactions between LW radiation and clouds lead to an enhanced drying of the troposphere in regions of subsidence (relative to LWCRE-off).  
+This is especially true for the E1 and E2 simulations.  
 Interactive LWCRE leads to less upper level ice-condensate for our CRM experiments
@@
 the amount of upper level ice-condensate.    
-%The influence of the LWCRE on low-level clouds is consistent for both the 
-%GCM-like and CRM-like experiments.  
 Below about 700 hPa turning off the LWCRE leads to a strong decrease in condensate
 in the GCM experiments, but a negligible decrease in the condensate of the CRMs.    
-The profiles of diabatic cooling are similar among all LWCRE-off experiments.  
-But when the LWCRE is on, the GCM like experiments have up to twice as much diabatic cooling as the GCM like experiments below 850 hPa.
-%While the mid-tropospheric 
-%profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
+The profiles of diabatic cooling are similar among all LWCRE-off experiments (Figure \ref{fig:cf_tdtlw}).  
+But when the LWCRE is on, the GCM-like experiments have up to twice as much diabatic cooling as the CRM-like experiments below 850 hPa.
+%While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
 %response below about 850 hPa for the 25km and 100km models.  
-%At that grid-spacing, with the LWCRE on, significant low-level 
-%clouds are formed, leading to a radiative cooling on the order of -10K/day.   
+%At that grid-spacing, with the LWCRE on, significant low-level clouds are formed, leading to a radiative cooling on the order of -10K/day.   
 %However, when the LWCRE is off the radiative cooling decreases to - 3-5 K/day and there is little appreciable 
-%difference in the low-level diabatic profiles among the 
-%P100, P25, E25, E2, and E1 experiments.   
+%difference in the low-level diabatic profiles among the P100, P25, E25, E2, and E1 experiments.   
 %It is also clearly seen that the LWCRE decreases the upper-level ice-condensate 
-%for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and 
-%P25 (Figure \ref{fig:TotCond}).  
-The LWCRE plays a major role in determining the equilibrium RH, total condensate, and LW radiative 
-heating of the troposphere.  However the manifestations of interactions between clouds and radiation as indicated
+%for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure \ref{fig:TotCond}).  
+The manifestation of interactions between clouds and radiation as indicated
 by these characteristics differ dramatically between the GCM and CRM experiments.   
@@
     \includegraphics[width=0.96\columnwidth]{walkerfigs/lowlevel_New.eps}
-    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection for experiments
-    with explicit convection.  The surface enthalpy flux (a) is the latent plus sensible heat flux.  Panels b and c show 
+    \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
+    The surface enthalpy flux (a) is the latent plus sensible heat flux.  Panels b and c show 
     the equivalent potential temperature (b) and zonal wind (c) at the lowest model level in the atmosphere.  Panel 
@@
 Figure \ref{fig:enthalpy} shows the surface enthalpy flux, 
-the equivalent potential temperature, and the u-component wind field for E1,E2, and E25 both with (thick lines) and 
-without (thin lines) the LWCRE.  Over the SST maximum, E25 has a surface enthalpy flux that is $60 \, \rm{W/m^2}$ 
+the equivalent potential temperature, and the u-component wind field for E1,E2, and E25.  
+Over the SST maximum, E25 has a surface enthalpy flux that is $60 \, \rm{W/m^2}$ 
 larger than that of the E1 experiment, and the E1 experiment has an irregular pattern of enthalpy flux in the middle
@@
 over the warmest SSTs is reduced from $60 \, \rm{W/m^2}$ to about $20 \, \rm{W/m^2}$ and the enthalpy
-flux for E1 and  E2 become very similar over the warmest SSTs.   Thus even for the case of prescribed SSTs and no
+flux for E1 and  E2 are very similar.   Thus even for the case of prescribed SSTs and no
 land surface the interactions between clouds and the LW radiation have a massive influence on the 
@@
 It is also interesting to note that despite stronger low-level winds, E25, E2, and E1 all have a weaker surface
-enthalpy flux when the clouds and radiation are allowed to interact.  This is initially surprising because as represented 
+enthalpy flux when the clouds and radiation are allowed to interact.   As represented 
 by bulk parameterizations, both the sensible heat flux and the latent heat flux are directly proportional to the 
 magnitude of a measure of the low-level wind.  However, the sensible and latent heat fluxes are also 
-proportional to the gradient of moisture and temperature between the surface and lowest atmospheric 
-level.    
-%Figure \ref{fig:enthalpy} also shows that over the warm patch of SST, the surface 
-%enthalpy flux is decreased by the LWCRE for E25, E2, and E1 despite these experiments having stronger low-level winds.  
+proportional to the gradient of moisture and temperature between the surface and lowest atmospheric level.    
 E25, E2, and E1 all show an increased amount of specific humidity (not shown) in the lowest atmospheric 
-model level that is reflected in the equivalent potential temperature (Figure \ref{fig:enthalpy}, top right).  This 
-implies that the gradient of moisture and temperature is smaller when the LWCRE is active and thus accounts 
+model level that is reflected in the equivalent potential temperature (Figure \ref{fig:enthalpy}b).  This 
+implies that the vertical gradient of moisture and temperature is smaller when the LWCRE is active and thus accounts 
 for the lower surface enthalpy flux relative to the LWCRE-off experiments.         
 It is also worth noting that in contrast to the P25 case which has strong domain mean shear, E25 has less domain 
-mean u wind shear then E1.
+mean wind shear then E1.
 
@@
 do the opposite with large amounts of low-level clouds and 5\% or less of upper level-couds.   
-While the large difference among the upper-level clouds only slightly shifts the radiative cooling in the
-upper troposphere, there is a strong change of the radiative cooling around 900 hPa where the 
-differences in low-level clouds occur.  
+The right panel of Figure \ref{fig:cf_tdtlw} shows that the differences among the upper-level clouds only slightly shifts the radiative cooling in the
+upper troposphere, but the differences in low-level clouds correspond to a strong change of the radiative cooling around 900 hPa. 
 %Less upper level clouds will allow more radiative cooling of the atmosphere and 
@@
 
-An interesting point that emerges from the domain mean values of precipitation (see Table \ref{tab:experimentmeans}) 
+An interesting point that emerges from the domain mean values of precipitation ($\overline{\rm{P}}$, see Table \ref{tab:experimentmeans}) 
 is that the sign of the response to LWCRE is not the same between CRM and GCM experiments.
@@
 Examining the energy budget of the surface and the role played by the low-level clouds
-reveals the source of the extra atmospheric heating for the E25, P25, and 
-P100 experiments.  
-Prescribed SST generates an upward flux of LW radiation that is constant.  
+reveals the source of the extra atmospheric heating for the E25, P25, and P100 experiments.  
+Prescribed SST generates a constant upward flux of LW radiation.  
 The upward flux of sensible heat flux will be mostly fixed (barring variations in surface
@@
 %experiments strongly influences the net flux of shortwave energy to the surface (not sure about this sentence). 
-Low-level clouds serve as a significant source of LW radiative cooling 
-for the atmosphere (Figure \ref{fig:cf_tdtlw}).  Making these clouds invisible to radiation creates 
-a source of effective atmospheric warming.   When this source of atmospheric energy loss is 
-removed in the LWCRE-off experiments the upwelling LW flux of radiation plays a larger 
-role in warming the atmosphere that more than compensates for the increased OLR at the 
-top of the atmosphere.  There is an increase in atmospheric warming on the order of 
-$20 \, \rm{W \,m^{-2}}$ for the LWCRE-off experiments and 
+Low-level clouds serve as a significant source of LW radiative cooling for the atmosphere (Figure \ref{fig:cf_tdtlw}).  
+Making these clouds invisible to radiation creates a source of effective atmospheric warming by removing a source of atmospheric energy loss.  
+Invisible low-level clouds also allow the upwelling LW flux of radiation to play a larger role in warming the atmosphere.
+%When this source of atmospheric energy loss is removed in the LWCRE-off experiments the upwelling LW flux of radiation plays a larger 
+%role in warming the atmosphere that more than compensates for the increased OLR at the 
+%top of the atmosphere.  
+These two factors more than compensate for the increased OLR at the TOA of the LWCRE-off experiments.
+There is an increase in atmospheric warming on the order of $20 \, \rm{W \,m^{-2}}$ for the LWCRE-off experiments and 
 thus additional condensational heating is not needed to balance the increase of OLR. 
-Thus the mean precipitation rate actually decreases as shown in Table \ref{tab:experimentmeans}.   
+Thus $\overline{\rm{P}}$ actually decreases (Table \ref{tab:experimentmeans}).   
 These results for E25, P25, and P100 are consistent with \citeA{Popp_Silvers_2017}  who 
-showed dramatically less condensate in the atmosphere and much less precipitation 
+showed less condensate in the atmosphere and much less precipitation 
 (at the equator) for LWCRE-off experiments (see their Figure 1).  
-%Our results here for the E25, P25, and P100 are consistent with those of \citeA{Popp2017} 
-%because the low-level condensate is strongly decreased when the LWCRE is off.  
-The large decrease of low-level clouds also leads to an increase of downward shortwave 
-radiation at the surface.  Because of the low albedo of water
-this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
+The large decrease of low-level clouds also leads to an increase of downward shortwave radiation at the surface.  
+Because of the low albedo of water this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
 and contributes minimally to heating the atmosphere.
@@
 With an interactive surface, the surface temperature would be influenced
-by the downward flux of both LW and shortwave radiation that a change of 
-cloud fraction would lead to.
-
-% The interaction between clouds and the longwave radiation increases, or decreases, precipitation depending
-% on wether high or low clouds are dominant.
+by the downward flux of both LW and shortwave radiation that a change of cloud fraction would lead to.
 
@@
 
-In contrast to the E25, P25, and P100 experiments just discussed, turning the LWCRE off for 
-the E1 and E2 experiments results in more precipitation.  This can be explained as follows.  
+In contrast to the E25, P25, and P100 experiments just discussed, 
+E1 and E2 have larger $\overline{\rm{P}}$ for the LWCRE-off experiments.  This can be explained as follows.  
 One of the primary methods by which the LWCRE influences the atmosphere is by 
@@
 
-\section{Discussion} % and Summary of the Impact of the LWCRE and Grid-spacing on the Atmospheric State}
-
-This section lists some of the main ways in which the LWCRE and the grid spacing influence
-the clouds, the circulation, and the energetics of the mock-Walker circulation.   Some, but not all of these 
-points have been noted by previous studies.  
-Impacts of turning off the interaction between clouds and the LW radiation (LWCRE-off) include the following:
+\section{Summary and Discussion} % and Summary of the Impact of the LWCRE and Grid-spacing on the Atmospheric State}
+
+In summary, this section lists some of the main ways in which the LWCRE and the grid spacing influence
+the clouds, the circulation, and the energetics of the mock-Walker circulation.   
+%Some, but not all of these points have been noted by previous studies.   
+The impacts (relative to the LWCRE-off experiments) of the interaction between clouds and the longwave radiation 
+(LWCRE) include the following:
 
 \begin{itemize}
-  \item A decreased strength of the overturning circulation and the domain mean precipitation (P100,P25,E25).
-  \item The domain mean midtropospheric relative humidity increases by $5-15 \% $.
+  \item An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.
+  \item A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.
+  %\item The domain mean midtropospheric relative humidity increases by $5-15 \% $.  --> Not shown in current draft
  % \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
-  \item The horizontally oriented low-level circulations weaken, and with the regions of high precipitation, spread out 
-  in geographic space.  
-  \item Over the region with warm SST the surface enthalpy flux among models is in much better agreement, 
-  especially between the E1 and E2 experiments.
+  \item The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
+  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  
+ % \item Over the region with warm SST the surface enthalpy flux among models is in much better agreement, 
+  %especially between the E1 and E2 experiments (Figure \ref{fig:enthalpy}).
+  \item The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).
   %primarily because of changes in the latent heat flux.
   %\item decrease both the LTS and the EIS, over both the warm and cold regions ???
-  \item A decreased spatial gradient of $q, \theta_e,$ temperature $T$ and virtual temperature $T_v$ on the lowest 
-  atmospheric level.  
+  \item The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
+  (not shown) increases on the lowest atmospheric level.  
   %\item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
@@
   % \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
-  \item When convection is parameterized the total domain mean condensate decreases at all heights (Figure \ref{fig:TotCond_P25P100}), in contrast to 
-  when the convection is explicit and the LWCRE-off experiments have more condensate aloft and less at low-levels (Figure \ref{fig:TotCond}).    
+  \item When convection is parameterized the total domain mean condensate increases at all heights 
+  (Figure \ref{fig:TotCond_P25P100}), in contrast to when the convection is explicit and 
+  the condensate aloft decreases (Figure \ref{fig:TotCond}).    
 \end{itemize}
@@
 \begin{itemize}
-  \item The domain mean precipitation response to LWCRE is opposite to that of the $100 \textrm{km}$ 
-  and $25 \textrm{km}$ experiments.
+  %\item The domain mean precipitation response to LWCRE is opposite to that of the $100 \textrm{km}$ and $25 \textrm{km}$ experiments (Table 2).
   \item Overturning circulations (as measured by vertical velocity) are stronger and more consistently centered 
-  over the maximum of SST.  
-  \item The regions with upwelling motion as well as the upper troposphere have higher relative humidity.   
-  Between 600-800 hPa the $1 \textrm{km}$ and $2 \textrm{km}$ models can have a relative humidity 
-  that is 40\% higher than in the parameterized, lower resolution simulations.  
-  \item Above about 600 hPa there is two to four times more ice condensate, but only about half as much liquid condensate below 700 hPa.
-  \item There is less domain mean precipitation in the E1 and E2 experiments (Table \ref{tab:experimentmeans}).  Values for 1 and 2 km simulations are in the 3.1-3.7 mm/d range, while those 
+  over the maximum of SST (Figure \ref{fig:precip_vertvel}).  
+  \item %The regions with upwelling motion as well as the upper troposphere have higher relative humidity.   
+  Between 300-800 hPa in the upwelling regions the E1 and E2 %$1 \textrm{km}$ and $2 \textrm{km}$ 
+  models have a relative humidity 
+  as much as 50\% larger than the lower resolution simulations (Figures \ref{fig:rh_psi_P25vsE25} and \ref{fig:rh_psi_P25E2E1}).  
+  \item Above about 600 hPa there is two to four times more ice condensate, but less than half as much liquid condensate below 700 hPa (Figure \ref{fig:TotCond}).
+  \item There is less $\overline{\rm{P}}$ in the E1 and E2 experiments (Table \ref{tab:experimentmeans}).  Values for 1 and 2 km simulations are in the 3.1-3.7 mm/d range, while those 
   for the $100 \textrm{km}$ and $25 \textrm{km}$ experiments are about 10-25\% higher (3.5-4.1 mm/d).  
@@
 the large-scale circulation to the moisture.  The large differences in the surface enthalpy flux
-appear to be due to relatively small differences in the winds near the surface (Figure \ref{fig:enthalpy}).  This is not necessarily
-surprising and is likely the source of much of the differences among the experiments.  The 
-large influence of the low-level wind  and enthalpy flux on the structure of precipitation, 
+appear to be due to differences in the winds near the surface (Figure \ref{fig:enthalpy}).  
+%This is not necessarily surprising and is likely the source of much of the differences among the experiments.  
+The large influence of the low-level wind  and enthalpy flux on the structure of precipitation, 
 low-level moisture and clouds, and mid-tropospheric humidity in the convective regions is 
 consistent with previous studies showing the importance of the low-level wind fields for precipitation 
-(\cite{Wofsy_Kuang_2012}, Fermepin and Bony, 2014), boundary layer properties \cite{Raymond_1994}, and even the climate 
-sensitivity (Silvers et al., 2016).
+\cite{Wofsy_Kuang_2012, Fermepin_Bony_2014}, boundary layer properties \cite{Raymond_1994}, and even the climate 
+sensitivity \cite{Silvers_etal_2016}.
 
@@
 Many of the previous studies of mock-Walker circulations or simplified models of tropical dynamics 
-\cite<e.g. >[]{Raymond_1994, Pierrehumbert_1995, Larson_etal_1999}, Neelin and Zeng, 2000); 
-Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005)
+\cite<e.g., >[]{Raymond_1994, Pierrehumbert_1995, Larson_etal_1999, Neelin_Zeng_2000, 
+Bretherton_Sobel_2002, Sobel_etal_2004, Peters_Bretherton_2005}
 have focused on simplifying the physics parameterizations as much as possible while still maintaining the interactions between convection and radiation.  
-While these have proven useful, they have remained complex enough to make comparisons with other models 
-difficult and the degree to which the simplifying assumptions influence the conclusions is unclear.    
+These have proven useful but have remained complex enough to make comparisons with other models 
+difficult, and the degree to which the simplifying assumptions influence the conclusions is unclear.    
 The approach of this paper is different.  We study an idealized configuration with the full complexity of a GCM. 
-Pierrehumbert (1995) argued that cloud processes are not the leading cause of the 
+\citeA{Pierrehumbert_1995} argued that cloud processes are not the leading cause of the 
 stable tropical climate but that it is, `the ability of
 the atmospheric circulation to create dry air pools in regions of large-scale subsidence' 
--these are the Radiator Fins-, that serve as a cooling (thus stabilizing) mechanism for Earth's tropical climate.  
+-these are the `Radiator Fins'-, that serve as a cooling (thus stabilizing) mechanism for Earth's tropical climate.  
 Our results demonstrate how strongly the cloud radiative effects influence the circulations that set up the Radiator Fins.  
 Experiments with prescribed SST preclude the possibility of studying feedbacks
-between the circulation, and the relative area of warm and cold SST regions as in \citeA{Pierrehumbert_1995}.  
-However, out study of the interaction between clouds, radiation, and the circulation shows how these interactions 
-lead to changes in the area of the dry regions above the boundary layer.  
+between the circulation, and the relative area of warm and cold SST regions as \citeA{Pierrehumbert_1995} did.  
+However, our study shows how the interactions between clouds, radiation, and the circulation lead to changes in the area
+of the dry regions above the boundary layer.
+%However, our study of the interaction between clouds, radiation, and the circulation shows how these interactions 
+%lead to changes in the area of the dry regions above the boundary layer.  
 These dry regions allow the tropics to efficiently cool to space and maintain an energetic balance.   
@@
 Using mock-Walker simulations to benchmark a GCM with a CRM was proposed by \citeA{Jeevanjee_etal_2017}.
-This was part of our initial motivation but is predicated on physics parameterizations that are simple enough 
-to allow for a clean comparison. 
-%generate a better understanding of the physical processes.  
+This was part of our initial motivation but is predicated on physics parameterizations that are simple enough to allow for a clean comparison. 
 Utilizing something like Kessler microphysics, 
@@
 models.  However, making such changes to the GCM used in this paper would result in a model so different from AM4.0 
-that the CRM would no longer serve as a benchmark to AM4.0.   We have chosen to keep the GCM as close as 
-possible to AM4.0.
+that the CRM would no longer serve as a benchmark for AM4.0.   We have chosen to keep the GCM as close as possible to AM4.0.
 More intermediate steps are necessary to create a clean link between CRMs and GCMs.  
@@
 %complicates the outcome of experiments, but also brings the model configuration very close to the original GCM. 
-The complexity of our results highlights the need for continued work with simple theoretical models such as the 
-Quasiequilibrium Tropical Circulation Model (QTCM; Neelin and Zeng, 2000) and the Simplified QTCM, or SQTCM 
-(Sobel et al., 2004; Peters and Bretherton, 2005, Bretherton et al., 2006).  
+The complexity of our results highlight the need for continued work with simple theoretical models such as the 
+Quasiequilibrium Tropical Circulation Model \cite<QTCM;>[]{Neelin_Zeng_2000} and the Simplified QTCM, or SQTCM 
+\cite{Sobel_etal_2004,Peters_Bretherton_2005, Bretherton_etal_2006}.  
 Our results also show that the mock-Walker circulation is an ideal configuration with which to test developments in 
@@
 There is a rich literature on tropical overturning circulations.  While this study has interpreted the experiments 
-in the context of the Walker Circulation, our results are also relevant to the deep overturning circulations and 
+in the context of the Walker Circulation, our results are also relevant to the overturning circulations and 
 meridional SST gradients that define the Intertropical Convergence Zone (ITCZ) and the Hadley Circulation.  
 In that context, our results are consistent with those of several recent studies 
-(e.g. Fermepin and Bony, 2014; Harrop and Hartmann, 2016; Popp and Silvers, 2017; Dixit et al. 2018; Flaschner et al. 2018; Albern et al., 2018).  
+\cite<e.g., >[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Dixit_etal_2018,Flaschner_etal_2018,Albern_etal_2018}.   
 Those studies, as well as the present one, show that the LWCRE acts to constrain, or tighten, the deep convective region.  
-This results from an increased atmospheric energy uptake and strengthening of the overturning circulation where the deep convective clouds occur (Popp and Silvers, 2017).  
+This results from an increased atmospheric energy uptake and strengthening of the overturning circulation where the deep convective clouds occur \cite{Popp_Silvers_2017}.  
 Also consistent with this previous work, the present paper shows that the LWCRE has a strong influence on the low-level circulation.   
 When the LWCRE is turned off, the low-level circulations shift upward and are not as well organized 
-(see Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
+(Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
 There is a corresponding change in the low-level cloud fields, LW radiative cooling, and the domain mean precipitation.
@@
 troposphere.  
-Albern et al., 2018 showed that there is a large spread in the CRE response to warming among GCMs.  
-Our expectation is that the fraction of precipitation that is due to the convective parameterization will be dependent on the 
-GCM.   The disparate influence of the LWCRE on the large-scale precipitation could explain some of the model
+\citeA{Albern_etal_2018} showed that there is a large spread in the CRE response to warming among GCMs.  
+Our expectation is that the fraction of precipitation that is due to the convective parameterization will be particular to individual GCMs. 
+The disparate influence of the LWCRE on the large-scale precipitation could explain some of the model
 spread in the CRE response to warming.
@@
 of precipitation that is expected in the LWCRE-off case as a result of increased LW cooling to space is not enough
-to overcome the decreased condensational heating at low-levels, with a net effect of less precipitation.  
+to overcome the decreased condensational heating at low-levels, with a net effect of less $\overline{\rm{P}}$.  
 Over the regions with cooler SSTs, the CRMs have very few (less than \%5) low-level clouds and as a result the 
 change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
-Watanabe et al. (2018) found a similar relationship between low-clouds and precipitation in the context climate 
+\citeA{Watanabe_etal_2018} found a similar relationship between low-clouds and precipitation in the context climate 
 change experiments.
@@
 fundamental to the overturning tropical circulation.  The resulting atmospheric state has a stronger overturning 
-circulation, a much more humid (40\% higher RH) deep convective region, and less $\overline{\rm{P}}$ .  
+circulation, a much more humid (up to 50\% higher RH) deep convective region, and less $\overline{\rm{P}}$ .  
 Relative to the GCM-like simulations the 1 and 2km simulations have two to four times as much condensate
-aloft but only about half as much below 700 hPa.  This increase of vertical moisture transport with increasing 
-resolution is particularly apparent in the LWCRE-off experiments (Figure \ref{fig:rh_psi_P25E2E1_lwoff}).
+aloft but only about half as much below 700 hPa.  The increase of vertical moisture transport with increasing 
+resolution is particularly apparent in the LWCRE-off experiments (Figure \ref{fig:rh_psi_P25E2E1_lwoff}, lower panels).
 
 Three striking changes occur as a result of a four-fold increase in domain width.  The low-level clouds shift 
-upward by more than 100 hPa (Figure 6), there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments (Figure 5),  
+upward by more than 100 hPa (Figure 6), there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments 
+(compare Figures 4 and Figure 5),  
 %and a strong dependence of the quantity of precipitation produced by the large-scale cloud scheme on the LWCRE. 
@@
 This impact on the large-scale precipitation occurs for the GCM-like experiments on smaller domains as well, 
-but is particularly pronounced in the large domain experiments.  
+but is pronounced in the large domain experiments.  
 %Larger domains have more precipitation.  
@@
 a global CRM which should complement efforts that start with a regional large-eddy simulation (LES) model or CRM model and work 
-towards a global model (e.g. Schneider et al., 2017; Schneider et al., 2019).
+towards a global model \cite<e.g.,>[]{Schneider_etal_2017,Schneider_etal_2019,Satoh_etal_2019}.
 The comparisons presented in this paper have highlighted some of the unexpected behaviors of a GCM-like 
@@
 The comparisons have also illustrated some of the challenges that arise when dramatically increasing the resolution of a GCM.  
-These include the lack of shallow clouds in the CRM (both convective and stratocumulus) and the difficulty of comparing 
+These include the lack of shallow clouds in our CRM (both convective and stratocumulus) and the difficulty of comparing 
 clouds in this CRM to other CRMs due to the prognostic large-scale cloud scheme.  
@@
 The only difference between our simulations and radiative convective equilibrium (RCE) is the gradient of SST at the lower boundary.  
-The addition of this small difference from pure RCE creates a concrete link with the observed tropical atmosphere.  
-The goal in developing and using idealized models is to capitalize on their simplicity in such a way that key elements of the 
+This simple difference from pure RCE creates a concrete link with the observed tropical atmosphere.  
+The goal in developing idealized models is to capitalize on their simplicity in such a way that key elements of the 
 process in question become clear.  
-In this case the processes of interest are the coupling between clouds, radiation, and the large-scale circulation.  
-Studies using RCE have been fruitful but insufficient to fully illuminate these processes while typical GCM studies are often too complex to untangle.  
+In this case the processes of interest are the couplings between clouds, radiation, and the large-scale circulation.  
+Studies using RCE have been fruitful but insufficient to fully illuminate these processes while typical GCM studies 
+can be prohibitively complex.
 %Idealized studies focusing on particular aspects of the Earth system have shown that a danger of idealized models is 
@@
 %to interact with the clouds and the fluxes of energy, both radiative and surface enthalpy.   
-The initial results from the RCE Model Intercomparison Project (RCEMIP; Wing et al., 2020) show a wide range of variability among the models.
-Adding the extra constraint of an overturning circulation forced by a prescribed gradient of SST would provide a context within which the 
+The initial results from the RCE Model Intercomparison Project \cite<RCEMIP; >[]{Wing_etal_2020} show a wide range of variability
+in the temperature, humidity, and clouds among the models.
+Adding the extra constraint of an overturning circulation forced by a prescribed gradient of SST, similar to the recent work of 
+\citeA{Shamekh_etal_EOR} and \citeA{Muller_Hohenegger_2020} would provide a context within which the 
 wide range of results from RCEMIP could be reexamined and expanded upon.
@@
 
-During the course of this research, it became apparent how fundamentally different the calculations of large scale clouds are between CRMs and GCMs.
+%During the course of this research, it became apparent how fundamentally different the calculations of large scale clouds are between CRMs and GCMs.
 Increasing computing resources will continue to blur the line that distinguishes GCMs from CRMs. 
@@
 
-%Kuang and Wofsy
-
-%Randall et al., 1989
-%Slingo and Slingo, 1988
 %Stevens et al. 2012
@@
 %This is both simple, and physically motivated.  
-
+%
 %% computed with matlab, see StreamFunNew.m script
@@
 %\end{equation}
-%
+%%
 %In the previous equation, $w, u,$ and $\rho$ have all been averaged in space and time and $p$ is the pressure on full model levels.  The 
@@
 %
-%
+
 %\section{Cloud Water and Cloud Fraction}
@@
 \acknowledgments
-The authors thank Leo Donner, Nadir Jeevanjee, and Juho Iipponen for discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
+The authors thank Leo Donner, Nadir Jeevanjee, Yi Ming, and Juho Iipponen for discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
 The expertise of Ming Zhao with the physics of AM4.0 also proved helpful in many conversations related to this work.
@@
 LGS also acknowledges recent partial support through Stony Brook University from award NSF AGS1830729.
-Data and scripts are available from author upon request
+The code for the AM4.0 model is available for download at  https://data1.gfdl.noaa.gov/nomads/forms/am4.0/, scripts used to perform the analysis and create figures are available on the GitHub repository (https://github.com/gitleviglenn/SilversWalkerCell.git).
 

### 2020-05-26 Silvers_cfmip_extraTable.tex
extraTable with new feedback numbers from David Paynter

\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers

\draftfalse

\journalname{Journal of Advances in Modeling Earth Systems (JAMES)}

\begin{document}

We calculate feedbacks for the coupled experiments, and amip, as follows.     The difference in surface temperature is calculated 
relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.   
The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
to years 1996-2015.

\begin{equation}
  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
\end{equation}
\begin{equation}
  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_1}
\end{equation}
\begin{equation}
  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
\end{equation}

In the above equations $F_{4xCO_2}=N_{4xCO2}-N_{PiC}$; $F_{hist}=N_{hist(1996-2014)}-N_{PiC}$; 
$F_{1pctCO_2}=0.79F_{4xCO2}$.

\begin{table}
\begin{center}
\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
 the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
have been estimated from a linear fit of the years... }
    \begin{tabular}{*{5}{c}}
    \hline
    \hline
 Feedback   & Abrupt 4xCO2 & 1pct.   & Historical    &  Amip   \\ \hline
    Net          &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
    \\
    Net CRE   & -0.06       &  -0.26          & -0.45         & -0.46           \\  
    \\
    LW CRE   & 0.14        &  0.10            & -0.14           & -0.03          \\  
    \\
    SW CRE  & -0.20       &  -0.26            & -0.31          & -0.43         \\  
    \\
    LW CLR   & -1.70       &  -1.71            & -1.94           & -2.25        \\  
    \\
    SW CLR  & 0.65        & 0.65              & 0.56             & 0.91          \\  
    \\
    $\Delta \rm{T}_s$        & 3.99        &  ??                & 0.8              & 0.76          \\  \hline

    \end{tabular}\par
    %\bigskip 
    \label{tab:lambda}
\end{center}
\end{table}

\end{document}

### 2020-06-04 Silvers_WalkerCell_clean.tex
delete more commented old text and make minor changes to abstract and key points for submission to JAMES in Silvers_WalkerCell.tex and Silvers_WalkerCell_clean.tex

--- 2020-05-26 Silvers_WalkerCell.tex
@@
 \linenumbers
-%\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
-%\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-%\geometry{landscape}                		% Activate for for rotated page geometry
-%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
-%\usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
-								% TeX will automatically convert eps --> pdf in pdflatex		
-%\usepackage{amssymb}
-%\usepackage{gensymb}
-%\usepackage{epstopdf}
-%\usepackage{pdflatex}
-%\usepackage{epsfig}
 
@@
 			% Activate to display a given date or no date
-%\title{Using the Walker Circulation to connect low-level cloud changes to deep convective entrainment}
 \title{Clouds and Radiation in a mock-Walker Circulation}
@@
 \affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
-\affiliation{2}{GFDL/NOAA, SAIC, Science Applications International Corporation, Reston, VA, USA}
+\affiliation{2}{NOAA/GFDL, SAIC, Science Applications International Corporation, Reston, VA, USA}
 \affiliation{*}{Current Affiliation: School of Marine and Atmospheric Sciences, Stony Brook University, Stony Brook, NY, USA}
@@
 \begin{keypoints}
-%  \item{At 25 km, simulations with parameterized shallow- and deep-convection exhibit asymmetries in the circulation, 
- % precipitation, and humidity fields resulting in a steady-state overturning circulation that is not centered on the SST
-%  maximum.}
   \item{Cloud resolving simulations result in more upper-level clouds, relative to lower resolution simulations which have more low-level clouds.}
-  \item{High and low clouds interact differently with longwave radiation to increase or decrease the mean precipitation, depending on which cloud type is dominant.}
-  \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation 
-  maximum away from the SST maximum.}
- % \item{The longwave cloud-radiative effect is a fundamental factor in establishing these asymmetries and leads to dramatic
- % changes in the low-level clouds and boundary layer structure.}
-  %\item{Cloud resolving simulations result in stronger overturning, more condensate aloft, and a RH in the deep convective 
-  %region that is 40\% higher than for the coarser cases with parameterized convection.}
-%  \item{The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.}
+  \item{High and low clouds interact differently with longwave radiation to increase or decrease precipitation, depending on dominant cloud type.}
+  \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation maximum away from the SST maximum.}
 \end{keypoints}
@@
 The Walker circulation connects the regions with deep atmospheric convection in the western tropical Pacific to the shallow-convection, tropospheric subsidence, and stratocumulus cloud decks of the eastern Pacific.
-Although important to many elements of the Earth system such as tropical precipitation, and cloud feedback processes, the interactions between large-scale tropical circulations and these cloud systems are still not well understood.
+Although important to many elements of the Earth system such as tropical precipitation, and cloud feedback processes, interactions between large-scale tropical circulations and these cloud systems are still not well understood.
 The purpose of this study is to better understand the multi-scale interactions between the Walker circulation, cloud systems, and interactive radiation.
@@
 The LWCRE leads to a narrower rising branch of the circulation and substantially increases the fraction of precipitation from the large-scale cloud parameterization.
-Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.
+Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less precipitation.
 This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.
-
-%% What are climate modelers doing to reduce uncertainties about cloud processes?
-%%The representation of clouds in climate models is the most stubborn contributor to uncertainty of the climate response to increased 
-%%greenhouse gases.  A few of the reasons clouds are difficult to represent in models are imprecise definitions of clouds, an existential 
-%%dependence on trace amounts of condensed water, the importance of microphysical processes at scales less than the grid-scale, 
-%%and the close coupling between atmospheric radiative fluxes, clouds, and the large-scale dynamical circulations of Earth.  
-%%To elucidate this coupling between clouds, radiation, and the large-scale circulations of the Earth, we simulate an 
-%%idealized equatorial tropical Pacific over a range of resolutions.
-%
-%In the western Pacific warm sea surface temperatures (SST) prevail beneath rising atmospheric motion and deep convective 
-%storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface temperatures and low-level, 
-%non-precipitating clouds with a dry subsiding atmosphere above the stratus clouds.  These regions are 
-%connected by a large-scale circulation referred to as the Walker circulation.  
-%We analyze an idealization of this circulation to compare the multi-scale interactions between circulations,
-%cloud systems, and interactive radiation across experiments with grid-spacing ranging from 1km to 100km.  
-%These experiments thus span the range of resolutions between General Circulation Models (GCMs) and 
-%Cloud-system Resolving Models (CRMs).  
-%% We analyze an idealization of this circulation with experiments that use a range of grid-spacing from 1km to 100km.
-%% These experiments allow us to examine the multi-scale interactions between circulations, cloud systems, and radiation.
-%% Our experiments span the typical range of resolutions between General Circulation Models (GCMs) and 
-%% Cloud-system Resolving Models (CRMs).
-%Our GCM-like experiments have a large low-level cloud fraction but the CRM-like experiments have more
-%upper-level clouds.  This difference in the dominant cloud type leads to opposite atmospheric responses 
-%to changes in the longwave cloud radiative effect (LWCRE).  An active LWCRE leads to increased 
-%precipitation for our GCMs, but decreased precipitation for our CRMs.  Decreasing the resolution to 1km and 2km
-%results in stronger overturning circulations, more condensate aloft, and less domain mean precipitation.   
-%
-%Numerous studies of the Walker Circulation have used simplified 
-%theoretical or numerical models.  The focus of this paper is to simulate a mock-Walker
-%Circulation with a full-physics General Circulation Model (GCM) run with idealized boundary conditions to provide 
-%a link between the simpler models 
-%%and the complex interactions between clouds, 
-%%radiation and the large-scale circulation that are present in the tropical Pacific 
-%and current GCMs.
-%The climate model used is derived from the most recent version of the atmospheric GCM (AM4.0) developed at the Geophysical Fluid Dynamics Laboratory (GFDL).
-By dramatically decreasing the grid-spacing from its default configuration we resolve much more of the dynamical motion and eliminate
-%some of the statistical approximations of clouds, and thus more explicitly simulate some of their impacts.
-%This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes
-%a large-scale circulation.
-%%% and infer how deep convective heating in the west Pacific can influence the atmospheric cooling 
-%%%thousands of kilometers away in the east Pacific.  This cooling is a key ingredient in the determination of the 
-%%%Earth's sensitivity to changes in greenhouse gas concentrations (think radiator fins).
-%%
-%%Both models use approximately the same spatial domain.
 
@@
 in which the strong rising motion and deep convection is driven by a patch of warm sea surface temperature (SST).  
-%Interactions between the radiative flux of energy and clouds are fundamental to the nature of the Walker circulation.  
 Our results show that the response of the atmosphere to the 
-radiative flux of energy depends strongly on the relative amount of clouds at different heights. % type of cloud that is dominant in the atmosphere.  
+radiative flux of energy depends strongly on the relative amount of clouds at different heights.   
 It is further shown that our GCM-like models are dominated by low-clouds while our CRM-like models 
@@
 excellent configuration with which to better understand the interactions between clouds, radiation and circulation 
-and to push the development of models forward.   Models of mock-Walker circulations represents
+and to push the development of models forward.   Models of mock-Walker circulations represent
 an intermediate tier in a hierarchy of models between Earth-like models and the models of 
@@
 
-%The clouds in this system play a fundamental role in setting the 
-%characteristics of the mock-Walker circulation and the dominant cloud types are heavily dependent on 
-%what type of model is used to simulate them.
-
-%Our simulations are based on the equatorial tropical Pacific.   In the western Pacific warm sea surface temperatures exist beneath 
-%rising atmospheric motion and deep convective storms.   In contrast, the eastern tropical Pacific is characterized by cooler sea surface 
-%temperatures and low-level, non-precipitation clouds with a very dry atmosphere above the clouds.  These regions are connected by a
- %large-scale circulation of winds.  By comparing this scenario in a high-resolution and coarse resolution simulation we can infer how deep 
- %convective heating in the west Pacific can influence the atmospheric cooling thousands of kilometers away in the east Pacific.
-
 \section{Introduction}
-
-%Clouds are much more than passive conglomerates of tracers in a turbulent fluid.  
-%Without question, clouds are more than passive conglomerates of tracers in a turbulent fluid.  If an advance in our understanding 
-%of the role clouds play in our climate is desired, it is essential that we learn to model the two-way interaction between clouds 
-%and the circulation.  The radiative influence of clouds is one of the primary mechanisms by which they influence the circulation 
-%(imp of lwcre off).  Our scientific motivation for this study is to illuminate/clarify the ways in which the large-scale circulation 
-%connects regions of deep convective activity with the prevalent tropical shallow convection and the radiatively critical 
-%stratocumulus cloud decks.  While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
-%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical extra-tropical connections, we 
-%propose that all of the physics of importance to our particular questions are present in the equatorial manifestation of the Walker 
-%circulation.  
-%
-%Current computing capabilities cannot come close to resolving all of the spatial scales which are important in the lifetime of clouds.  
-%As a result, coarse resolution climate models must use statistical representations of the influences from unresolved clouds. 
-%Ideally the statistics of the coarse model should represent the explicitly resolved clouds of the higher resolution model and in 
-%particular as resolution is increased and the statistical approximations eliminated, the solution of the coarse model should be 
-%informed by the solution of the high resolution model.  Demonstration of this would help to show that the influence of clouds on 
-%climate is not an intractable problem.
-%
-%The paradigm of the Walker circulation includes many distinct manifestations of moist convection, interactions between 
-%radiation and clouds, as well as dynamical motions which range from sub-kilometer scales to roughly 10,000 km.     
-%In addition to the scientific interest of the Walker circulation as a link between deep convection, shallow-convection, and 
-%stratocumulus clouds, the tropical Pacific provides an ideal physical context with which to explore the sensitivities and 
-%strengths of theoretical models, high-resolution models and general circulation models.  The tropical system in the Pacific 
-%Ocean including deep, shallow, and mid-level convection, as well as stratocumulus cloud decks and sea-surface 
-%temperature gradients represents a fascinating and useful microcosm of the ways in which clouds can interact with dynamic 
-%circulations.  This region of the Earth system contains clues to the difficult questions of how clouds couple to the circulation 
-%and how the nonlinear interactions within the system contribute to the cloud feedbacks to perturbations and the overall 
-%sensitivity of the system to anthropogenic forcing.
-%
-%It remains unclear what GCM like models should be expected to produce in similar configurations.
-
-%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified 
-%SST. (just before equation 8 of Bretherton et al. 2006)."
-
-%The atmosphere of Earth constantly radiates energy to space.  This cooling of the atmosphere is mostly balanced by 
-%warming from the release of latent energy by convective clouds and precipitation.  The details of this balance between 
-%cooling and warming determine the role that clouds play in setting the Earth's climate sensitivity.  However, clouds 
-%contribute to both warming and cooling of the atmosphere.  Deep convective storms and high clouds warm the 
-%atmosphere by trapping outgoing radiation and absorbing shortwave radiation while clouds at lower levels cool the 
-%atmosphere by reflecting the incoming radiation from the sun.  Previous research has repeatedly shown that low-level 
-%clouds are the single largest factor in the current uncertainty of the Earth's climate response to a doubling of $\rm{CO}_2$ 
-%concentration (Bony and Dufresne, 2005, Sherwood et al. 2014).  However, it has also been shown that the turbulent 
-%mixing of the atmosphere by deep convective clouds provides a strong control within climate models on the climate 
-%sensitivity (Zhao, 2014).  The goal of this project is to elucidate/explore the connection between these two pieces of evidence.
-%
-%Previous studies such as Held et al., 1993; Tompkins et la. 1998, Bretherton et al., 2005; Muller and Held, 2012; Wing and 
-%Emanual, 2014 have shown that idealized models are quite sensitive to the details of the configuration such as domain size 
-%and resolution.  This lack of convergence among high resolution models makes it difficult to know what to expect from 
-%lower resolution models with convective parameterizations which are relevant to our understanding of GCMs.  Part of the 
-%purpose of this paper is to use one modeling framework to illustrate what is obtained from a coarse GCM-like model run 
-%with idealized boundary conditions.  We then use this same modeling framework to compare the results obtained from 
-%simulations with a resolution of 100, 25, 2, and 1km.     
-%
-%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system 
-%the idealization is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, 
-%as compared to the observed world.  These simulations are somewhere in the middle of those extremes.  We have 
-%decided to keep many of the complex elements of the global climate model  so that we can hopefully better understand 
-%the parent model (AM4.0) while learning something concrete about 
-%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke 
-%large-scale cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
-%model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
-%understanding and to illuminate some of the idiosyncrasies of the climate models that are currently looked to for information about the 
-%future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
-%a simple design that incorporates additional complexity which strengthens the connection to observed atmospheric phenomena.
-%
-%
-%Inevitable limitations in computing power necessitate climate studies with Earth-system models to use relatively coarse grid-spacing.  
-%%Coarse, statistical Earth-system models which simulate long periods of the climate are necessitated by the limitations of current computers.  
-%This research uses a high-resolution cloud-resolving model on a limited spatial domain as a benchmark to compare with the same 
-%model at lower resolution configured as a fully 
-%parameterized general circulation model.   The modeling approach presented here, made unique by its clean connection between a global climate 
-%model and a regional cloud resolving model is  made possible by the flexible modeling system at GFDL.   The goal of this paper is to use this 
-%capability to better quantify and understand the connection between tropical convective heating and changes in low clouds.
-
-% Johnson et al. discusses the trade inversion and the high statitic stability in the subtropics.  He contrasts 
-% the thermodynamic arguments of Kloesel and Albrecht (1989) 
-%  and Sun and Lindzen (1993) with the dynamic-thermodynamic argument of Schubert et al. 1995. 
-%\item{The Walker Circulation as way of imposing realistic large-scale circulations, as opposed to spontaneously generated large-scale
-%  circulations.  Previous studies of RCE have proven to be a 
-%  useful tool with which to explore the basic physics of climate and climate sensitivity, but they lack a large-scale circulation.  Many 
-%  studies have also shown the importance and prevalence of convective self aggregation (CSA).  A mock-walker circulation with an
-%  imposed SST gradient can be thought of as studying a partially constrained aggregating or organized system in a way that removes
-%  some of the ambiguity.  The mock-Walker circulation also allows for a simple way of studying in physical space, the connection
-%  between column relative humidity and circulation in a way that is directly tied to the physical state of the system rather than with
-%  a forced compositing of the data  
-%  \cite{Bretherton2005, Muller2012}.}
 
@@
 clouds \cite{Johnson1999} as well as stratocumulus cloud decks along the eastern extremities of the basin.
-%Within the region of the tropical Pacific strong overturning circulations, deep convective towers, abundant shallow 
-%cumulus, and cumulus congestus clouds all interact with each other.  
 These overturning circulations encompass dynamical motions at scales
 ranging from meters to thousands of km's all of which interact with each of the different cloud types.
-% interact with the circulation on scales ranging from meters to thousands of km's.  
-%The Hadley circulation connects the tropical pacific with the subtropics and has been extensively 
-%studied (review paper?).  
 The circulation first noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the 
@@
 
-% Part of our motivations in using the framework of the Walker circulation comes from the fact that 
-% all of the major types of tropical clouds occur regularly within the region identified with the Walker
-% circulation.  In addition, the ability to focus on the equator without rotational effects simplifies
-% the dynamics.
-
 It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
@@
 are coupled to each other in the tropics.  
-%While the meridional temperature gradient is a fundamental driver of the large-scale circulation, and 
-%the Coriolis force is critical in determining the characteristics of tropical waves and the tropical 
-%extra-tropical connections, 
 We propose that focusing on the Walker Circulation can lead to new insights into 
@@
 \end{itemize}
-%These interactions are influenced not only by the Walker circulation, but also the Hadley 
-%cell and convectively coupled tropical waves.  
 In global and Earth-like GCM simulations, the interplay between the overturning circulation and clouds is difficult to disentangle from other 
@@
 The result is a gap in the types of simulation for this region that is so important to our understanding of clouds in the Earth's climate system.
-
-% Deep convective towers release vast amounts of latent heat into the atmosphere and are part of the system
-% that transports much energy poleward.  Trade-wind cumulus and stratocumulus clouds influence the 
-% Pacific-decadal oscillation and ENSO as well as reflecting vast amounts of insolation back to space.
-% This region of the globe has been recognized to be of critical importance to the global energy budget 
-% for decades (Rhiel and Malkus ?, Pierrehumbert, 1995?)
 
@@
 avoiding much of the complexity of those processes.
-%The work presented in this paper uses the full-physics of the recently developed GCM AM4.0
-%in a context usually reserved for CRMs as a means to create more overlap between these 
-%model types and help us to better understand the tropical climate.
-
-%Several elements distinguish this study from previous research on the Walker 
-%circulation.  
+
 Current climate models continue to be developed with an increasingly fine resolution and 
@@
 
-%The unique contribution from this study is to take a new CMIP6 atmospheric global climate model and to use it in the context of a
-%simple mock-Walker circulation configuration while changing as little as possible from the parent model.  The model we 
-%use (GFDL's AM4.0) is flexible enough to operate at grid-spacings ranging from 100km down to 1km in a doubly periodic 
-%domain that is configured similar to the equatorial Pacific.  This allows us to use a single code base to compare a model 
-%run at GCM-like resolution with a full suite of subgrid-scale paremeterizations with a cloud-resolving version of the same 
-%model in which all convective activity is strictly explicit and many more of the important dynamic motions are resolved. 
-%"Effects of cloud on atmospheric radiative cooling must be considered to get a realistic Walker circulation over specified 
-%SST. (just before equation 8 of Bretherton et al. 2006)."
-
-% Muller and Held, 2012 found that self-aggregation was sensitive to both domain 
-% size and resolution because of the sensitivity of the low-level clouds to these parameters.  % the longwave radiative cooling.
-
 The broad goal of this paper is to clarify the two-way interactions between the Walker circulation and 
@@
 resolution.  Conclusions are given in the last section.
-%The LWCRE is an important element for all of the experiments and will be discussed throughout the paper.
 
@@
 The usual two-way interaction between clouds and radiation is thus broken and a useful diagnostic tool is created.  
-%This can tell us the extent to which the specific location of the clouds matters to the radiative interaction with the atmospheric state.   
 This method was originally pioneered by \citeA{Slingo_Slingo_1988} and \citeA{Randall_etal_1989}.  
@@
 labelled with an E prefix, followed by the appropriate number.  Thus P25 refers to an experiment with parameterized convection using a 
-grid-spacing of 25km. %, while E25 refers to an experiment that is identical to P25 except that both the deep and shallow convective parameterizations have been turned off. 
+grid-spacing of 25km. 
 The naming convention for each of the experiments is shown in Table \ref{tab:experimentspecs}.   
@@
 `CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
-The CRM-like terminology acknowledges that this configuration % has not been developed as a CRM, 
+The CRM-like terminology acknowledges that this configuration 
 has a vertical resolution that is coarser than many CRMs, and uses the large-scale cloud scheme from the AM4.0/CM4.0 GCM.
@@
 The E1 and E2 simulations are in many ways similar to the configuration of so-called cloud resolving models.  
-In particular all convection is explicitly resolved, %both the deep and shallow convective parameterizations are turned off, 
+In particular all convection is explicitly resolved, 
 and the threshold of grid-cell mean relative humidity which triggers new clouds is changed from the default value of 0.8 to 1.0.  
@@
 to resolve all clouds, it is small enough to resolve many clouds and cloud-systems.  
-%The primary difference between the CRM simulations presented in this paper and those of more established CRMs such as  the 
-%System for Atmospheric Modeling (SAM; see Khairoutdinov and Randall, 2003) is that our model
-%has a much coarser vertical resolution and a prognostic large-scale cloud scheme inherited from the GCM.  
 The large-scale cloud scheme is based on the \citeA{Tiedtke1993} parameterization.  
@@
 the mass streamfunction in Figure \ref{fig:rh_psi_P25vsE25} and the vertical velocity in Figure \ref{fig:precip_vertvel}.   
-%The mass streamfunction illustrates the 
-%two-dimensional flux of mass and includes information from both the horizontal and vertical velocity components.
 The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate in the mid-troposphere over 
@@
 spatially concentrated circulation and will be discussed further in later sections (also seen Figures 4, 5, 9 and 10).
-%A stronger and spatially concentrated circulation for cases when the clouds interact with the LW 
-%radiation will be discussed in later sections (also be seen in Figures 4, 5, 9 and 10), and is particularly apparent for 
-%the cases with a large domain (16000 km long dimension).    
 Active LWCRE leads to lower values of domain mean OLR and higher domain mean precipitable water (PW) in all cases (Table \ref{tab:experimentmeans}).
@@
 
-%"... the higher mean winds on the flanks of the SST maximum raise the latent heat fluxes and associated rainfall there, resulting in a 
-%double-peak rainfall distribution with a slight local minimum in rainfall at the SST maximum (just before eq. 8)" 
-%was noted by Bretherton et al., 2006.  On the page with equation 20, there is an excellent discussion of the dependence of the 
-%vertical structure of cumulus on two key factors.  First, temperature and moisture in the BL air where the convective updrafts originate.
-%Second, the moisture profile in the lower troposphere above the boundary layer.  This 'dictates the extent to which air
-%turbulently mixed into rising cumulus updrafts dries them out.'  I think most of our simulations with a grid-spacing of 25km or 
-%greater are being dominated by this second factor.
-
-% LWCRE has a large impact on LS precip, not so much on convective precipitation
-% LWCRE has a large impact on the low-level circulation (circulation is stronger when LWCRE is on)
-% Are the low-level clouds a connecting point?
-
 \begin{figure}
@@
 Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
-%The added constraint (relative to RCE) of the fixed warm-patch of SST could lead to clarification of the processes that drive important atmospheric interactions.
 Previous studies have shown a dependence of aggregation 
@@
 patch ensures that the simulations will be `aggregated' to some degree.  
-%The SF indicates not only whether an experiment is aggregated, but also the spatial extent of the overturning circulation.  
 Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
 convection, radiation, and the large-scale circulation.
-
-%\textit{Previous studies have shown that Cloud Radiative Effects (CREs) act to strengthen and contract an 
-%overturning circulation \cite<e.g.>[]{Fermepin_Bony_2014, Harrop_Hartmann_2016b, Popp_Silvers_2017,Albern_etal_2018}.  
-%This is due to an increased low-level flux of moist static energy into the convective regions. }
 
@@
 ($25\, \rm{km}$ and $100\, \rm{km}$) using two different domain sizes (long edge length of $4,000\, \rm{km}$ and $16,000\, \rm{km}$).
-%, and simulations with a grid-spacing of $100\, \rm{km}$ on a grid with a horizontal length of $4000\, \rm{km}$ and $16000\, \rm{km}$.  
 Figure {\ref{fig:domdep}} shows the control GCM-like experiments and Figure  {\ref{fig:domdep_lwoff}} shows the equivalent simulations with LWCRE-off.    
-%When designing numerical experiments the size of the domain and the grid-spacing that determines model resolution are 
-%two of the most fundamental choices.   
-%One of the goals of this study was to explore the results of changing grid-spacing over a wide range of values.  
  Previous studies of RCE
@@
 At all resolutions the Hovm{\"o}ller plots show that the LWCRE acts to concentrate the precipitation over a smaller geographic extent.   
-%This is consistent with previous work showing that CREs 
-%strengthen an overturning circulation and narrow the region of deep convection (see \citeA{Harrop_Hartmann_2016b}; 
-%\citeA{Popp_Silvers_2017}; \citeA{Albern_etal_2018}; \citeA{Dixit_etal_2018}  etc.).  
 The structure of the precipitation changes more 
@@
 over the center of the domain where the SST is a maximum.  
-%As previously noted, these GCM-like simulations equilibrate after approximately 50 days.  
 There is also a dramatic change in the distribution of precipitation on the $4,000\, \rm{km}$ domain simulations after almost 2 years.   
@@
 the large domain (thick lines) simulations.
-%This can be seen in the domain mean total condensate in Figure \ref{fig:TotCond_P25P100}.  The  low- level maximum of 
-%condensate is shifted from near 900 hPa in the small domain (thin lines) to between 700-800 hPa in 
-%the large domain (thick lines).  
 There is also a vertical shift in the upper-level ice condensate, but it is less pronounced.  
@@
 Figure \ref{fig:TotCond_P25P100}).
-%Overall the large domains show an upward shift of condensate and have 
-%a much stronger upper level response to the LWCRE being turned off.
-%For the LWCRE-off cases, in agreement with \citeA{Bretherton_etal_2006} we find a more 
-%focused ascent region in the smaller domain.   But when the LWCRE is on, the extent of the relative ascent region 
-%changes little between P25 
-%and P25L but for P100 and P100L the ascent region is much more focused on the large domain (Figure \ref{fig:conv_vs_ls}).
-
-% new Hovmoller diagram
-\begin{figure}
- % \includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreon.eps}
+
+\begin{figure}
    \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwon_huge.eps}
@@
 \begin{figure}
-  %\includegraphics[angle=90, width=0.95\columnwidth]{walkerfigs/hov_precip_4pan_vert_lwcreoff.eps}
     \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwoff_huge.eps}
@@
 effect in \citeA{Held2007}. Our results show that this fraction is indeed tied to the low-level cloud fraction  
-%(check the figures that show convective and large-scale precip separately).  
 and demonstrate that it is through the LW cloud radiative effect that this connection is enabled.
@@
 
-% Fraction of Precip due to large-scale precip for large/small experiments with a 25km resolution
 \begin{figure}
@@
 
-%We hypothesize than an important difference between our simulations and previous studies which use GCMs
-%is that although the deep and shallow convection are parameterized
-%with the GFDL double-plume parameterization, the fraction of precipitation that is produced by the convective parameterization 
-%is much smaller in our simulations than it is for many GCM-type experiments with parameterized convection.   At 25km grid-spacing, 
-%the majority of condensational heating occurs through the large-scale cloud  scheme (Figure \ref{fig:conv_vs_ls}).
-%%Overall, the fraction of precipitation that is 
-%%due to the large-scale scheme is roughly 40\%, and in many places it is actually greater than the amount of precipitation 
-%%produced by the convection scheme.   
-%%In comparison, many GCMs, have between 70\%-90\% of their precipitation produced by 
-%%the convective parameterization.  
-%There are further surprises in the fraction of precipitation that is large-scale.  On our small 
-%domains, with a bowling alley domain length of 4000 km, the simulations with 100km grid-spacing have values of $f_{ls}$ 
-%of $75-80\%$.  Often, at GCM-like resolutions such as 100km the convective precipitation would be expected to control much of the
-%precipitation rather than the large-scale parameterization.  However, when the domain length is increased to 16000 km
-%$f_{ls}$ decreases to a range of $0-70\%$ that depends strongly on location.  Over the warmest region of the surface the 
-%precipitation is still dominated by the large-scale scheme.   The large domain without the longwave CRE is the 
-%only configuration in which the convective precipitation is dominant.    If the default, or baseline, configuration of a GCM is built 
-%with the expectation that the convective parameterization scheme will dominate the production of tropical precipitation, then 
-%perhaps a configuration that minimizes the convective precipitation will result in a balance between the parameterization 
-%schemes that is less intuitive, such as an asymmetric response to symmetric forcing.
-
-%\section{The mock-Walker Circulation Dependence on Grid-Spacing: A transition from a 
-%General Circulation Model to a Cloud Resolving Model}
 \section{From a General Circulation to Cloud Resolving Model: Dependence on Resolution}
@@
 \begin{figure}
-  %\includegraphics[width=0.96\columnwidth]{walkerfigs/precip_4mods_6mn.eps}
   \includegraphics[width=0.96\columnwidth]{walkerfigs/hov_precip_25vs2vs1_6mn_huge.eps}
@@
   \centering
-      %\includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff.eps}
       \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff_new.eps}
@@
 of circulation and humidity (Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).
-%The steady state relative humidity and overturning circulation show both similarities and differences
-%among the experiments at varying resolutions with and without LWCRE .
 Perhaps the most obvious similarity is the double celled structure in the mass streamfunction and the most 
-obvious difference being the humidity in the center of the domains where the RH differs by as much as 40\%. % among E1, E2, and E25.  
-%The mid-troposphere 
-%of the P25 experiment is more than $40\%$ dryer in the region with deep-convection than for the 2km and 
-%1km experiments.  All experiments have a multicell vertical structure (consistent with B06), in contrast to 
-% the single cell that results from simple theoretical models such as the SQTCM (see B06).   
+obvious difference being the humidity in the center of the domains where the RH differs by as much as 40\%. 
 All experiments show a mid-tropospheric relative humidity minimum over the cooler SSTs where subsidence 
@@
 
-%The domain mean condensate is closely related to the distribution of clouds and is an important measure of the 
-%steady state reached by these experiments.  This in turn influences 
-%the distribution and flow of energy throughout the atmosphere and the radiation that is emitted to space.  
-%It also provides clues about the strength of convection and vertical mass transport.     
 The domain mean condensate is closely related to the distribution of clouds and the flow of energy through the atmosphere.  
@@
 E2 and E1 experiments have much higher values of upper level ice condensate.  
-%There is a substantial difference between the GCM-like P100, P25, and E25 experiments and the CRM-like E2 and E1 experiments 
-%with the former having much higher values of low-level liquid condensate and the later having much higher values of upper level ice condensate.  
 Although our experiments differ from RCE, the results are consistent with \citeA{Pauluis2006} who showed that for 
@@
   \centering
-      %\includegraphics[width=0.3\columnwidth]{walkerfigs/MnTotCondProf.eps}
        \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
@@
 
-% Is the paragraph below out of place?  As written, it references Figures 9, 10, and 13.  Should it be near the end of this section
-% as a sort of summary of the effects of LWCRE?  I also don't currently like the last sentence.... It has potential but as written it 
-% says nothing.
-
 The LWCRE plays a major role in determining the equilibrium RH, total condensate, and LW radiative heating of the troposphere.  
-This is highlighted by comparing experiments with and without the LWCRE. %  highlights key differences between our GCM and CRM experiments.  
+This is highlighted by comparing experiments with and without the LWCRE. 
 The upper panels of Figures \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff} show that the 
@@
 But when the LWCRE is on, the GCM-like experiments have up to twice as much diabatic cooling as the CRM-like experiments below 850 hPa.
-%While the mid-tropospheric profiles of diabatic heating and cooling are similar between the LWCRE on/off simulations, there is a very strong 
-%response below about 850 hPa for the 25km and 100km models.  
-%At that grid-spacing, with the LWCRE on, significant low-level clouds are formed, leading to a radiative cooling on the order of -10K/day.   
-%However, when the LWCRE is off the radiative cooling decreases to - 3-5 K/day and there is little appreciable 
-%difference in the low-level diabatic profiles among the P100, P25, E25, E2, and E1 experiments.   
-%It is also clearly seen that the LWCRE decreases the upper-level ice-condensate 
-%for E25, E2, and E1 experiments but dramatically increases the low-level liquid condensate for E25 and P25 (Figure \ref{fig:TotCond}).  
 The manifestation of interactions between clouds and radiation as indicated
 by these characteristics differ dramatically between the GCM and CRM experiments.
-%Overall, the LWCRE-off experiments influence the low-levels 
-%of the GCM-like experiments, and the upper-level regions of the CRM-like experiments.
-
-%The E25 and P25 experiments have much less condensate aloft and a lower relative humidity in the mid-troposphere
-%where the differences in strength of the overturning circulation are most pronounced. 
-%(can we use this to understand the differences in LWCRE?).
 
@@
   \centering       
-    %\includegraphics[width=0.96\columnwidth]{walkerfigs/LowLevelVars_E25E2E1.eps}
     \includegraphics[width=0.96\columnwidth]{walkerfigs/lowlevel_New.eps}
@@
 
-%The asymmetry in the enthalpy flux is also apparent in the lowest model level of the atmosphere.  
-%This is consistent with the strong asymmetries of the P25 experiment being connected to a large domain 
-%mean wind shear in that experiment.
-
 It is also interesting to note that despite stronger low-level winds, E25, E2, and E1 all have a weaker surface
@@
 
-%This manifestation of the strong interactions between clouds and the circulation 
-%would be entirely absent from high resolution simulations with gray radiation or fixed radiative cooling profiles.
-
 We now turn our attention to the clouds in the regions of subsidence over the cooler SSTs.
@@
 upper troposphere, but the differences in low-level clouds correspond to a strong change of the radiative cooling around 900 hPa.
-%Less upper level clouds will allow more radiative cooling of the atmosphere and 
-%require a correspondingly larger amount of condensational heating and precipitation.
 
@@
 wind) because changes in the downward flux of solar radiation will not warm the surface.   
-%However, the dramatic decrease of low-level clouds for the E25, P25, and P100 LWCRE off 
-%experiments strongly influences the net flux of shortwave energy to the surface (not sure about this sentence). 
 Low-level clouds serve as a significant source of LW radiative cooling for the atmosphere (Figure \ref{fig:cf_tdtlw}).  
@@
 Invisible low-level clouds also allow the upwelling LW flux of radiation to play a larger role in warming the atmosphere.
-%When this source of atmospheric energy loss is removed in the LWCRE-off experiments the upwelling LW flux of radiation plays a larger 
-%role in warming the atmosphere that more than compensates for the increased OLR at the 
-%top of the atmosphere.  
 These two factors more than compensate for the increased OLR at the TOA of the LWCRE-off experiments.
@@
 and contributes minimally to heating the atmosphere.
-%(does the downwelling longwave
-%flux change because there are less clouds or because they are invisible to radiation?).  
 With an interactive surface, the surface temperature would be influenced
 by the downward flux of both LW and shortwave radiation that a change of cloud fraction would lead to.
-
-% The ways in which clouds interact with their local environment: heat exchange through phase changes, 
-% absorption of radiation, emission of radiation.  But how much do these influence the large-scale circulation?
 
@@
 
-%
-%For GCM-like experiments with parameterized convection, the total precipitation is composed of one part from the 
-%convective parameterization, and one part from the large-scale cloud scheme.  Figure \ref{fig:conv_vs_ls} shows 
-%that when the LWCRE is turned off for the P25 and P100 experiments, the decrease in precipitation comes from 
-%a reduction in the large-scale cloud scheme precipitation and not from a decrease in the convective precipitation.
-
-%Similarly, the E2 experiment has lower values 
-%of upper level condensate and higher values of mid-troposphere relative humidity compared to the E1 simulation, which ....??
-
-%Water vapor is an efficient emitter of longwave radiation and thus greatly facilitates the cooling of the troposphere.
-
-%This is not the case for E2 and E1.  Those experiments have little low-level condensate to begin with 
-%%and thus do not experience 
-%%large changes in low-level condensate when the LWCRE is off.  
-%but they do have a large increase of upper
-%level condensate for the LWCRE off experiments.   
-%This is a large difference in the way that models with explicit convection 
-%respond to the LWCRE compared to more traditional large-scale models with parameterized convection.
-
-\section{Summary and Discussion} % and Summary of the Impact of the LWCRE and Grid-spacing on the Atmospheric State}
+\section{Summary and Discussion}
 
@@
   \item A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.
-  %\item The domain mean midtropospheric relative humidity increases by $5-15 \% $.  --> Not shown in current draft
- % \item eliminate the difference of liquid condensate at 900 hPa between explicit and parameterized simulations.
   \item The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
   in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  
- % \item Over the region with warm SST the surface enthalpy flux among models is in much better agreement, 
-  %especially between the E1 and E2 experiments (Figure \ref{fig:enthalpy}).
   \item The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).
-  %primarily because of changes in the latent heat flux.
-  %\item decrease both the LTS and the EIS, over both the warm and cold regions ???
   \item The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
   (not shown) increases on the lowest atmospheric level.  
-  %\item eliminate large differences in the evaporation and lowest level temperature in the center of the domain between 
-  %        the 1 and 2 \textit{km} simulations. 
-  % \item increase evaporation in the 1 and 2 \textit{km} cases, decrease it in the 25 \textit{km} case.
   \item When convection is parameterized the total domain mean condensate increases at all heights 
@@
 \begin{itemize}
-  %\item The domain mean precipitation response to LWCRE is opposite to that of the $100 \textrm{km}$ and $25 \textrm{km}$ experiments (Table 2).
   \item Overturning circulations (as measured by vertical velocity) are stronger and more consistently centered 
   over the maximum of SST (Figure \ref{fig:precip_vertvel}).  
-  \item %The regions with upwelling motion as well as the upper troposphere have higher relative humidity.   
-  Between 300-800 hPa in the upwelling regions the E1 and E2 %$1 \textrm{km}$ and $2 \textrm{km}$ 
+  \item   
+  Between 300-800 hPa in the upwelling regions the E1 and E2 
   models have a relative humidity 
@@
   for the $100 \textrm{km}$ and $25 \textrm{km}$ experiments are about 10-25\% higher (3.5-4.1 mm/d).  
-  %\item a weaker radiative cooling rate (about 2 K/d) and weaker heating rate (about 2 K/d).
-  %\item much less vertical shear.  
   \end{itemize}
@@
 appear to be due to differences in the winds near the surface (Figure \ref{fig:enthalpy}).  
-%This is not necessarily surprising and is likely the source of much of the differences among the experiments.  
 The large influence of the low-level wind  and enthalpy flux on the structure of precipitation, 
@@
 
-%Numerous simplified models of tropical dynamics, or the mock-Walker circulation have been developed 
-%(e.g \citeA{Raymond_1994}, Pierrehumbert, 1995; Larson et al., 1999; Neelin and Zeng, 2000; 
-%Bretherton and Sobel, 2002; Sobel et al., 2004;  Peters and Bretherton, 2005).  
 Many of the previous studies of mock-Walker circulations or simplified models of tropical dynamics 
@@
 of the dry regions above the boundary layer.
-%However, our study of the interaction between clouds, radiation, and the circulation shows how these interactions 
-%lead to changes in the area of the dry regions above the boundary layer.  
 These dry regions allow the tropics to efficiently cool to space and maintain an energetic balance.
-%Pierrehumbert lists
-%determining the size of these 'radiator fins' and the quantity of RH as some of the critical unsolved questions.  That 
-%work depended critically on an interactive surface that allowed for the size of the two regions to change.  It is interesting
-%in the work presented here that the SST is fixed, and yet the subsidence fraction, tropospheric RH over the cold pools, 
-%and overall energetics can still change despite a fixed surface temperature.   
-%While the usefulness of such methods is clear, part of our motivation was to leave the GCM configuration as close to the parent model (AM4.0)
-%as possible and see what range of equilibrium states are reached.
 
@@
 More intermediate steps are necessary to create a clean link between CRMs and GCMs.  
-%Allowing for interactive radiation and sophisticated cloud parameterizations significantly
-%complicates the outcome of experiments, but also brings the model configuration very close to the original GCM. 
 The complexity of our results highlight the need for continued work with simple theoretical models such as the 
@@
 
-%Several different configurations of a mock-Walker circulation have been used to analyze the response of clouds and the 
-%large-scale circulation to a simple Gaussian shaped prescribed SST pattern. 
-%The results presented in this paper show us that (scientific point learned).    Interactions between the clouds and radiation
-%act to spatially concentrate the circulation, strengthen the overturning circulation, and dry out the mid-troposphere where 
-%subsidence dominates (although domain mean condensate is less when LWCRE is on.).
-
-%The goal of designing idealized numerical experiments is to develop a tool that is easier to understand than the system 
-%the idealization is based on.  The goal of adding complexity to a climate model is to achieve a more `realistic' simulation, 
-%as compared to the observed world.  These simulations are somewhere in the middle of those extremes.  We have 
-%decided to keep many of the complex elements of the global climate model  so that we can hopefully better understand 
-%the parent model (AM4.0) while learning something concrete about 
-%the observable world.  By retaining such complexities as interactive radiation, convective parameterization, and the Tiedtke 
-%large-scale cloud scheme we run the risk creating an idealized model which is no easier to understand than the original parent
-%model which compares more readily to observations.  However, it is important to use idealizations such as this to test our current 
-%understanding and to illuminate some of the idiosyncrasies of the climate models that are currently looked to for information about the 
-%future of our climate.  The mock-Walker Circulation can be thought of as RCE plus an imposed gradient in surface temperature.  This is 
-%a simple design that incorporates additional complexity which strengthens the connection to observed atmospheric phenomena.
-
 Perhaps the most interesting result is that the GCM-like experiments have a relatively large low-level 
@@
 (compare Figures 4 and Figure 5),  
-%and a strong dependence of the quantity of precipitation produced by the large-scale cloud scheme on the LWCRE. 
 and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation (Figure \ref{fig:conv_vs_ls}).    
@@
 but is pronounced in the large domain experiments.  
-%Larger domains have more precipitation.  
-%The amount of precipitation, and the structure of the precipitation and clouds 
-%is heavily dependent on the interaction between clouds and the longwave radiation.  This interaction strongly mediates
-%the precipitation from the large-scale cloud parameterization, not the convective precipitation  
 This dependence on domain size could imply that 4000 km is not large enough to contain the largest 
@@
 
-%The longwave cloud radiative effect (LWCRE) has been shown to play a dramatic role in the organization of the precipitation
-%field and the low-level clouds.  
-%%This is primarily accomplished by decreasing the amount of precipitation that is produced 
-%%by the large-scale precipitation scheme.  
-%Two major differences between the GCM-like experiments and the CRM-like 
-%experiments are 4-5 times more low-level clouds and a much dryer mid-troposphere in the GCM-like experiments compared 
-%to the CRM-like experiments.  The LWCRE also highlights the impact of an increased vertical moisture transport 
-%in our CRM-like models.
-
 Mock -Walker cell configurations are an important step between models of RCE and models which simulate a wider range of Earth like conditions.
@@
 can be prohibitively complex.
-%Idealized studies focusing on particular aspects of the Earth system have shown that a danger of idealized models is 
-%that they will not actually be easier to understand than the Earth system.   
-%Sometimes the difficulty of interpreting results from Aquaplanet and full-physics RCE
-%simulations give this impression.}.  
 Many of the characteristics from RCE experiments with convective aggregation are present in mock-Walker simulations.   
@@
 and fluxes of energy (radiative and surface enthalpy).
-%While it may seem that prescribing a warm region of SST fully determines the large-scale circulation, 
-%the results presented in this paper clearly show how much room there is for the large-scale circulation 
-%to interact with the clouds and the fluxes of energy, both radiative and surface enthalpy.   
 The initial results from the RCE Model Intercomparison Project \cite<RCEMIP; >[]{Wing_etal_2020} show a wide range of variability
@@
 
-%\textit{this paragraph is pretty repetative with earlier parts of the section.  do I want these point here or earlier?}
-%What are we to conclude from this array of results?  
-%Our CRMs resolve a far broader 
-%range of turbulent motions and thus do a better job of explicit mixing compared to the GCM-like 
-%configurations.  However, the increase in resolved scales comes at the cost of most of the low-level clouds (\textit{what is 
-%the observed cloud fraction in the tropical Pacific below 700 hPa?}).  The GCM-like simulations match the CRM-like 
-%simulations  in the general two celled structure of the overturning circulation and the approximate distribution of condensate.  
-%While the GCM-like simulations succeed at producing 20-30\% low-level cloud fraction they produce few upper-level 
-%clouds and the distribution of the precipitation is erratic and dependent on interactions between the convective 
-%parameterization and the strength of the longwave cloud radiative effect.  
-%
-
-%During the course of this research, it became apparent how fundamentally different the calculations of large scale clouds are between CRMs and GCMs.
 Increasing computing resources will continue to blur the line that distinguishes GCMs from CRMs. 
@@
 As a result, the details of the large-scale cloud scheme will be increasingly important in the development of GCMs. 
-% a correct 
-%understanding of the role played by tropical clouds in the processes that are linked to interactions between clouds,
-%radiation, and the large-scale circulations.
 For high resolution models with explicit convection, the upper-level clouds dominate the impact of interactions between 
@@
 circulations in the observable atmosphere should be a high priority in future research.
-
-%The domain mean precipitable water is higher (as is P) when the LWCRE is on.   What does this imply?  Precipitation 
-%efficiency or mixing?  The total water is PW plus condensates right?  So the Precipitation efficiency would only speak
-%to the condensed part I think.
-
-%References: 
-%
-
-%Stevens et al. 2012
-%Tompkins, 2001
-% Li et al. 2015?  How do our conclusions about the CRE at TOA relate to their conclusions about the ACRE?  Same question with Harrop and Hartmann
-% Popp and Bony?
-% Kelly and Randall, 2001?
 
@@
 
-%Reference citation instructions and examples:
-%
-% Please use ONLY \cite and \citeA for reference citations.
-% \cite for parenthetical references
-% ...as shown in recent studies (Simpson et al., 2019)
-% \citeA for in-text citations
-% ...Simpson et al. (2019) have shown...
-%
-%
-%...as shown by \citeA{jskilby}.
-%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
-%...has been shown \cite{jskilbye}.
-%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
-%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
-%...has been shown by \cite <e.g.,>[and others]{lewin76}.
-%
-% apacite uses < > for prenotes and [ ] for postnotes
-% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
-%
-
-%%% Acknowledgements
-%\begin{acknowledgments}
-%(Levi's acknowledgements)
-%\end{acknowledgments}
-
 \end{document}

### 2020-06-11 Silvers_cfmip.tex
updated Silvers_cfmip.tex tex file
Silvers_cfmip.tex and Silvers_cfmip_extraTable.tex

@@
 % south of ~60 degrees.
+
+It has been claimed that cloud feedbacks in simplified experiments match those in full models (Ringer et al., 2014, Medeiros et al?).  
+Does this work support such a claim?
 
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
-  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_below3km.eps}
+  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cf_misr_cldfrac_below3km.eps}
   \caption{Observed and modeled clouds below 2.75km.  Clouds shown are divided into thick 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_climo_hist_amip_obs_10yr.eps}
+  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cloudfrac_climo_hist_amip_obs_10yr.eps}
   \caption{Comparison of cloud fraction among observations from CALIPSO, the \textit{amip} and 
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/radflux_toa_netcre_ceres4p1.eps}
+  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/radflux_toa_netcre_ceres4p1.eps}
   \caption{Top-of-the-atmosphere CRE from CERES-EBAF ed4.1 and from the AM4.0 \textit{amip} experiment.  
@@
   \centering
-  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cloudfrac_base_amips_calip.eps}
+  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cloudfrac_base_amips_calip.eps}
   \caption{Vertical and latitudinal structure of cloud fraction for \textit{amip}-related experiments and observations from 
@@
 
+% ceres data is here on my macbook: 
+% /Users/silvers/data/SatData/CERES/CERES_EBAF-TOA_Ed2.8_Subset_200003-201607.nc
+% /Users/silvers/data/SatData/CERES/CERES_EBAF_Ed4.1_Subset_200003-201809.nc
+
+% how exactly should I cite the CERES data?  Looking here: https://eosweb.larc.nasa.gov/project/ceres/ebaf_ed4.1. I don't see a 
+% particular paper to cite, just DOI's.  The info from ncdump implies that the data extends along 200003-201809, which is confirmed by
+% 223 time steps that are presumably monthly....  but in the global attributes section of the output from ncdump it states: 
+%:title = "CERES EBAF TOA and Surface Fluxes. Monthly Averages and 07/2005 to 06/2015 Climatology." ;
+%                :institution = "NASA Langley Research Center" ;
+%                :Conventions = "CF-1.4" ;
+%                :comment = "Climatology from 07/2005 to 06/2015" ;
+%                :version = "Edition 4.1; Release Date May 28, 2019" ;
+%                :DOI = "10.5067/TERRA-AQUA/CERES/EBAF_L3B004.1"
+
+% what does the comment about climatology mean?
+
 \bibliography{master_refs}

### 2020-06-11 Silvers_cfmip_extraTable.tex
Silvers_cfmip.tex and Silvers_cfmip_extraTable.tex

@@
 the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
-to years 1996-2015.
+to years 1996-2015 (Is it correct that $T_2$ and $N_2$ correspond to different years?).
 
@@
 \caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
- the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
-have been estimated from a linear fit of the years... }
+ the clear sky minus all sky TOA flux.}
     \begin{tabular}{*{5}{c}}
@@
     \hline
- Feedback   & Abrupt 4xCO2 & 1pct.   & Historical    &  Amip   \\ \hline
-    Net          &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
+ Feedback   & Abrupt 4x$\rm{CO}_2$ & 1pct$CO_2$.   & Historical    &  Amip   \\ \hline
+    Net $\alpha$         &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
     \\

### 2020-06-19 Silvers_cfmip.tex
added Webb et al. and Eyring et al references for the CMIP6 and CFMIP documentation papers.  added a new table with experiments.  updated some of terrible captions.

@@
 GFDL has implemented a collection of satellite simulators which are part of the 
-CFMIP (Cloud Feedback Model Intercomparison Project; see Webb et al., 2017).  Satellite simulator
+CFMIP (Cloud Feedback Model Intercomparison Project; see \cite{Webb_etal_2017}).  Satellite simulator
 are software tools that are used in coordination with GCMs to allow for model variables 
@@
  Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
-    Net          &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
+    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
     \\
@@
   \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
-  \caption{Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
-  shows the measured CRE from CERES-EBAF 
-  observations compared to simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
-  shown at left is the simulated CRE from three fully coupled experiments with CM4.0 (\textit{historical},
-  \textit{abrupt-4xCO$_2$}, and \textit{1pctCO$_2$}).  Right panel, the CRE feedback from four 
-  amip-like experiments.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
+  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
+  shows (in black) the measured CRE from two versions of the CERES-EBAF observations.   compared to 
+  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
+  shown at left is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (1950-2014),
+  \textit{abrupt-4xCO$_2$} (101-150), and \textit{1pctCO$_2$} (101-150)) and the AM4.0 amip experiment.  Right panel, the CRE feedback from four 
+  of the amip-like experiments from CFMIP.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
   been reversed.}
@@
   \centering
-  \includegraphics[width=\columnwidth]{Silvers_cfmip_SinglePanelFig.pdf}
+  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CF_figure9.pdf}
   \caption{Cloud fraction for experiments with warming.  Cloud fractions are shown for the upper-, mid-, and low-level 
-  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the right column
+  clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the middle column
+  shows values relative to the PI control experiment and the right column
   shows values relative to the \textit{amip} experiment.  For the coupled model experiments
- \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted.  
+ \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted while for the 
+ \textit{historical} experiment the years 1950-2014 are used.  
   For reference cloud fraction from the 
@@
 
-\acknowledgments
-We thank the efforts of the model development team at GFDL who developed AM4.0 and CM4.0 and made it possible to participate in CMIP6.
-We thank the World Climate Research Programme which coordinated and promoted CMIP6.
-All CMIP data are available from the ESGF at https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.
+\appendix
+\section{Experiments and Data}
+
+Tables A1 and A2 describe the details of the observational data sets used and the various model experiments that 
+have been used in this study.  All model experiments were conducted with the GFDL AM4.0 atmospheric general 
+circulation model (Z18a,b), or in the case of the coupled experiments, the GFDL CM4.0 coupled general circulation 
+model \cite{Held_etal_2019}. 
+All experiments are taken from GFDL's contribution to CMIP6, either the DECK experiments, or experiments from CFMIP.
+For additional general details about the experiments see \cite{Eyring_etal_2016} and \cite{Webb_etal_2017}.  All of the 
+data used to analyze these experiments is hosted by the Earth System Grid Federation (ESGF) and is available at 
+https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.
+
+ \begin{table}
+\begin{center}
+\caption{Experiments used.   Should I list the years the experiment simulate or just the years used in the analysis?}
+    \begin{tabular}{*{4}{c}}
+    \hline
+    \hline
+ Experiment & Class & Configuration & Years   \\ \hline
+    historical        &   DECK      &  atmosphere \& ocean   &  Jan 1950 -Dec 2014               \\ 
+    \\
+    abrupt 4xCO2   & DECK       &  atmosphere \& ocean       & 150 years  \\  
+    \\
+    1pct CO2   & DECK        &  atmosphere \& ocean  & 150 years \\  
+    \\
+    PI Control  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
+    \\
+    amip  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
+    \\
+    amip +4K  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
+    amip -4K   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
+    amip Future 4K  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
+    aqua control        & CFMIP  & atmosphere  & 10 years \\
+    aqua +4K.  & CFMIP    & atmosphere  &  10 years \\ \hline
+
+    \end{tabular}\par
+    %\bigskip 
+    \label{tab:lambda}
+\end{center}
+\end{table}
 
@@
 
+\acknowledgments
+We thank the efforts of the model development team at GFDL who developed AM4.0 and CM4.0 and made it possible to participate in CMIP6.
+We thank the World Climate Research Programme which coordinated and promoted CMIP6.
+All CMIP data are available from the ESGF at https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.
+
+% \begin{sidewaystable}
+% \caption{ Observational Data Sets Used in This Paper}
+% \centering
+% \begin{tabular}{l l}
+% \hline
+% Data  & Description  \\
+% \hline
+%   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed2.8   \\
+%                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 2.8  \\
+%                                     & Reference: Loeb et al. (2009); Smith et al. (2011).  \\
+%                                     & URL: \url{http://ceres.larc.nasa.gov/documents/DQ_summaries/CERES_EBAF_Ed2.8_DQS.pdf}.   \\
+%   TOA radiative fluxes (dates)  & Short name: CERES-EBAF-ed4.1   \\
+%                                     & Long name: Clouds \& Earth's Radiant Energy Systems Energy Balanced \& Filled data, edition 4.1  \\
+%                                     & Reference:   \\
+%                                     & URL: \url{http://ceres.larc.nasa.gov}.   \\
+%   Cloud amount and optical depth (dates) & Short name:  MISR   \\
+%                                                                   &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
+%   Cloud amount and optical depth (dates)  & Short name: MODIS  \\
+%                                                                   & Long name: Moderate Resolution Imaging Spectroradiometer.  \\
+%   Cloud amount and optical depth (dates)  & Short name: ISCCP   \\
+%                                                                   & Long name: International Satellite Cloud Climatology Project   \\
+%                                                                   & Reference: Rossow and Schiffer (1991); Pincus et al. (2012)   \\
+%                                                                   & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
+%   Cloud amount  & Short name: CALIPSO   \\
+%                           & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\
+%                           & Reference: Chepfer et al. (2010); Cesana and Chepfer (2013)      \\
+%    \hline
+% \multicolumn{2}{l}{$^{a}$Footnote text here.}
+% \end{tabular}
+% \end{sidewaystable}
+
 % MISR data was downloaded using wget and is now here: 
@@
 %:title = "CERES EBAF TOA and Surface Fluxes. Monthly Averages and 07/2005 to 06/2015 Climatology." ;
-%                :institution = "NASA Langley Research Center" ;
+%                :institution = "NASA Langley Research Center" 
 %                :Conventions = "CF-1.4" ;

### 2020-07-04 Silvers_cfmip.tex
changes to Silvers_cfmip.tex, minor changes to Silvers_cfmip_extraTable.tex, and Silvers_cfmip_CRE_SinglePanel.tex

@@
 We compare output from the AM4.0 GCM to observations from ISCCP, MISR, MODIS, CALIPSO, and CERES-EBAF.
-For details of the data used see Table 2.
+More details are provided in the appendix.  The CMIP6 and CFMIP experiments used in this study are given in Table
+\ref{tab:exps} and the observational data sets used are given in Table \ref{tab:obs}.
 
@@
 We have computed the climate feedback parameter that appears in Table 1 with multiple methods.    
-Three common methods are briefly described here.  
-First, the climate sensitivity can be estimated from the change in radiative flux at the top of the 
+The climate sensitivity can be estimated from the change in radiative flux at the top of the 
 atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
 as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990).  
-Second, the climate
+Additionally, the climate
 sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
-instantaneously quadrupled relative to the pre-Industrial values.  Linear regression can then be used to 
+instantaneously increased relative to the pre-Industrial values.  Linear regression can then be used to 
 estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
 This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
-and used by the IPCC.  Third, the climate sensitivity
-can be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
+and used by the IPCC.  The climate sensitivity
+can also be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
 has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
@@
 \caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
- the clear sky minus all sky TOA flux. The values for the Abrupt 4xCO2 experiment
-have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).  The \textit{amip p8K} is not a separate experiment but
+ the clear sky minus all sky TOA flux.   The \textit{amip p8K} is not a separate experiment but
 shows the feedbacks computed from the \textit{amip-p4K} when the \textit{amip-m4K} is the control experiment.}
-    \begin{tabular}{*{8}{c}}
+    \begin{tabular}{*{6}{c}}
     \hline
     \hline
- Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future & Abrupt 4xCO2  & 1\% $CO_2$  \\ \hline
-    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84        &    -0.46   & -1.48      \\ 
-    \\
-    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11          & 0.65   & -0.30  \\  
-    \\
-    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10          & 0.14  & 0.02    \\  
-    \\
-    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21         & 0.5  & -0.32       \\  
-    \\
-    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03         & -1.7   & -1.94      \\  
-    \\
-    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30          & 0.6    & 0.76        \\  \hline
+ Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future   \\ \hline
+    Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84           \\ 
+    \\
+    Net CRE   & -0.27       &  0.00              & 0.07         & 0.03         & -0.11            \\  
+    \\
+    LW CRE   & 0.38        &  0.16              & 0.13           & 0.15        & 0.10             \\  
+    \\
+    SW CRE  & -0.65     &  -0.16              & -0.07          & -0.12        & -0.21            \\  
+    \\
+    LW CLR   & -1.96       &  -2.02            & -2.02           & -2.02       & -2.03            \\  
+    \\
+    SW CLR  & 0.09        & 0.36              & 0.32             & 0.34        & 0.30             \\  \hline
 
@@
 which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
-284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: 150 years, doubling at year 70).  
+284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: total of 150 years, doubling at year 70).  
 The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
@@
 The results from that study provide a convenient point of reference for our findings.  
-Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models.  
+Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models in Table \ref{tab:lambda}.  
 That is, for the coupled abrupt $4xCO_{2}$ experiment, feedbacks are computed as  
@@
   \centering
-  \includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
-  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  Left panel 
-  shows (in black) the measured CRE from two versions of the CERES-EBAF observations.   compared to 
+  %\includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
+  \includegraphics[width=0.75\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
+  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  The top panel 
+  shows (black) the CRE from two versions of the CERES-EBAF observations compared to 
   simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
-  shown at left is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (1950-2014),
-  \textit{abrupt-4xCO$_2$} (101-150), and \textit{1pctCO$_2$} (101-150)) and the AM4.0 amip experiment.  Right panel, the CRE feedback from four 
-  of the amip-like experiments from CFMIP.  To aid comparisons the sign of the \textit{amip-m4K} experiment has 
+  shown in the top panel is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (yrs. 1950-2014),
+  \textit{abrupt-4$\times$CO2} (yrs. 101-150), and \textit{1pctCO2} (yrs. 101-150)).  The middle panel shows an estimate of the 
+  CRE feedback of the data in the top panels, computed by normalized according to the warming of surface air temperature over 
+  the relevant time period.  The bottom panel shows the CRE feedback from four 
+  CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}).  The sign of the \textit{amip-m4K} experiment has 
   been reversed.}
@@
 
-The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback 
-(-0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$, climate feedback parameter?) that results from differences in 
+The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback parameter 
+($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in 
 both the cloudy and clear sky fluxes.   The LW CLR feedback is nearly constant between the 
@@
 
+\begin{table}
+\begin{center}
+\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
+ the clear sky minus all sky TOA flux.  The values for the Abrupt 4x$\rm{CO}_2^{a}$ experiment
+have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).}
+    \begin{tabular}{*{6}{c}}
+    \hline
+    \hline
+ Feedback   &    Abrupt 4x$\rm{CO}_2^{a}$   &  Abrupt 4x$\rm{CO}_2^{b}$  & 1pct$CO_2$   & Historical    &  Amip   \\ \hline
+    Net $\alpha$    &     -0.46     &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
+    \\
+    Net CRE  &    0.65    & -0.06       &  -0.26          & -0.45         & -0.46           \\  
+    \\
+    LW CRE    &   0.14       & 0.14        &  0.10            & -0.14           & -0.03          \\  
+    \\
+    SW CRE  &    0.5     &    -0.20       &  -0.26            & -0.31          & -0.43         \\  
+    \\
+    LW CLR   &   -1.7     &  -1.70       &  -1.71            & -1.94           & -2.25        \\  
+    \\
+    SW CLR  &      0.6         &   0.65        & 0.65              & 0.56             & 0.91          \\  
+    \\
+    $\Delta \rm{T}_s$     &     ?     & 3.99        &  ??                & 0.8              & 0.76          \\  \hline
+
+    \end{tabular}\par
+    %\bigskip 
+    \label{tab:lambdahist}
+\end{center}
+\end{table}
+
+It is also instructive to examine the values of the climate feedback parameter that result from simulations of 
+recent decades.  In Table \ref{tab:lambdahist} we calculate the feedbacks for the coupled and amip experiments 
+using   the difference in surface temperature  
+relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.
+\begin{equation}
+  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
+\end{equation}
+\begin{equation}
+  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
+\end{equation}
+\begin{equation}
+  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
+\end{equation}
+\begin{equation}
+  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
+\end{equation}
+
+In the above equations $F_{4xCO_2}=N_{4xCO2}-N_{PiC}$; $F_{hist}=N_{hist(1996-2014)}-N_{PiC}$; 
+$F_{1pctCO_2}=0.79F_{4xCO2}$.  The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  
+%In all cases the years used for $N$ and $T$ are the same.  
+$N_1$ and $T_1$ corresponds to years 101-150, while $N_2$ and $T_2$ corresponds to years 1996-2015.  
+The relatively small span of years for $T_2$ were chosen to avoid the impact of volcanic behavior in the early 1990's that if included
+complicate the interpretation of the climate feedback.  Feedbacks thus calculated are given in Table \ref{tab:lambdahist}.
+
 As discussed in the previous section and in Z18a,b, both AM4.0 (\textit{amip}) and 
@@
   clouds in the top, middle, and bottom rows, respectively.  The left column shows control values, the middle column
-  shows values relative to the PI control experiment and the right column
+  shows values relative to the \textit{piControl} experiment and the right column
   shows values relative to the \textit{amip} experiment.  For the coupled model experiments
@@
     \\
-    PI Control  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
+    piControl  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
     \\
@@
     %\bigskip 
-    \label{tab:lambda}
+    \label{tab:exps}
 \end{center}
@@
  \multicolumn{2}{l}{$^{a}$Footnote text here.}
+ \label{tab:obs}
  \end{tabular}

### 2020-07-04 Silvers_cfmip_extraTable.tex
changes to Silvers_cfmip.tex, minor changes to Silvers_cfmip_extraTable.tex, and Silvers_cfmip_CRE_SinglePanel.tex

@@
 The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  In all cases
-the years used for $N$ and $T$ are taken from the same years.  $N_1$ corresponds to years 101-150, $N_2$ corresponds
-to years 1996-2015 (Is it correct that $T_2$ and $N_2$ correspond to different years?).
+the years used for $N$ and $T$ are the same.  $N_1$ and $T_1$ corresponds to years 101-150, while $N_2$ and $T_2$ corresponds
+to years 1996-2015.
 
@@
 \begin{equation}
-  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_1}
+  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
 \end{equation}

### 2020-07-22 Silvers_cfmip.tex
changes mostly related to updating the MISR data to V7 from Roger Marchand: Silvers_cfmip.tex and Silvers_cfmip_MISR_cloudtable.tex

@@
 \section{Clouds in AM4.0: Comparison between AMIP and observations}
-
-%\begin{figure}
-%% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
-%  \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
-%  \caption{Observed and modeled clouds for all heights.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
-%  and thin (optical depth between 0.3 and 3.6) 
-%  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
-%  derived with the MISR simulator.  Mean cloud fraction values for MISR 
-%  (AM4) are 32\% (24\%) for thick clouds and 22\% (12\%) for thin clouds.}
-%  \label{fig:misr}
-%\end{figure}
 
@@
   \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cf_misr_cldfrac_below3km.eps}
-  \caption{Observed and modeled clouds below 2.75km.  Clouds shown are divided into thick 
-  (optical depth between 3.6 and 23) and thin (optical depth between 0.3 and 3.6) 
-  clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
+  \caption{Observed and modeled clouds below 3km.  Clouds shown are divided into thick 
+  (optical depth greater than and equal to 3.6) and thin (optical depth less than 3.6) 
+  clouds.  The observations (bottom) are from the MISR satellite (2000-2019) and the modeled clouds (top) were derived 
   with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
@@
 \end{figure}
+% MISR observations are from March 2000 through November 2019 and came from Roger Marchand
 
@@
 % figure generated with cloud_table_AM4fig.ncl
-  \includegraphics[width=0.98\columnwidth]{cfmipfigs/Silvers_cfmip_MISR_cloudtable.pdf}
+  \includegraphics[width=0.98\columnwidth]{cfmipfigs/Silvers_cfmip_MISRv7_cloudtable.pdf}
   \caption{Cloud Fraction (colors and numbers (\%)) in joint histograms showing the variations of cloud fraction 
@@
                                      & URL: \url{http://ceres.larc.nasa.gov}.   \\
-   Cloud amount and optical depth (dates) & Short name:  MISR   \\
+   Cloud amount and optical depth (03 2000 - 11 2019) & Short name:  MISR   \\
                                                                    &  Long name: Multi-angle Imaging SpectroRadiometer.  \\
@@
                                                                    & URL: \url{ftp://ftp.climserv.ipsl.polytechnique.fr/cfmip/ISCCP}     \\
-   Cloud amount  & Short name: CALIPSO   \\
+   Cloud amount (2007 - 2016)  & Short name: CALIPSO   \\
                            & Long name: Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observations   \\

### 2020-08-25 Silvers_cfmip.tex
added the reference for Soden et al., 2004 and minor edits to the CRE discussion.

@@
 Kristopher Rand, Thomas Robinson, Hans Vahlenkamp, Chandin Wilson, Bruce Wyman, Yujin Zeng, Ming Zhao}
-% Isaac Held?  Michael Winton?  Pu Lin? Songmiao Fan?  M. Daniel Schwarzkopf?
+% Isaac Held?  Michael Winton? Songmiao Fan?  M. Daniel Schwarzkopf?
 
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
-  \includegraphics[width=0.6\columnwidth]{cfmipfigs/ISCCP_CALIPSO_clt_correctedBiasPattern_nogrid.eps}
-  %\includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
+  \includegraphics[width=0.75\columnwidth]{cfmipfigs/ISCCP_CALIPSO_clt_correctedBiasPattern_nogrid.eps}
    \caption{Comparison of total cloud fraction from the AM4 \textit{amip} experiment with two observational 
@@
 However, the observational uncertainty for some of these properties prohibited firm conclusions.  This paper
-uses additional observations and a more thorough analysis of the clouds in AM4/CM4 to determine 
+uses additional observations and a more thorough analysis of the clouds in AM4/CM4 to better determine 
 the quality of the cloud simulations.        
@@
 the simulated TOA radiative fluxes from AM4.0 to those observed by CERES.    
-Throughout the paper we utilize what has come to be known as the Cloud Radiative Effect (CRE).  The CRE is the 
-difference between the full-sky and clear-sky radiative fluxes (this quantity is also sometimes referred
-to in the literature as the cloud radiative forcing, CRF).
+Throughout the paper we utilize what has come to be known as the Cloud Radiative Effect (CRE), calculated 
+as the difference between the full-sky and clear-sky radiative fluxes.  Earlier literature \cite<e.g.,>[]{Cess_etal_1989, Soden_etal_2004} often referred to the CRE as the Cloud 
+Radiative Forcing (CRF).
+
+The CRE is a simple and effective tool for evaluating the influence of 
+clouds on the climate.  It is well known (Soden et al., 2004) that a change in the CRE is not a direct measure of the cloud 
+feedback, and that non-cloud related values of CRE can occur.  However, there are many examples of 
+the productive use of the CRE as a way to diagnose cloud effects (e.g. Cess et al., 1989; Webb et al., 2001; 
+\citeA{Ringer_etal_2014}; Andrews et al., 2015), it is simple to calculate, and
+it allows for direct comparisons with previous studies.  The pure cloud feedback usually corresponds 
+to a positive shift of the change in CRE values by roughly 0.3 $\rm{W m^{-2}K^{-1}}$ (Soden et al., 2004).  The total cloud 
+feedback of a model is therefore more positive than will be implied by the CRE.
 
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 3
-  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cf_misr_cldfrac_below3km.eps}
+  \includegraphics[width=0.75\columnwidth]{/Users/silvers/Research/Silvers_cfmip_paper/cf_misr_cldfrac_below3km.eps}
   \caption{Observed and modeled clouds below 3km.  Clouds shown are divided into thick 
   (optical depth greater than and equal to 3.6) and thin (optical depth less than 3.6) 
-  clouds.  The observations (bottom) are from the MISR satellite (2000-2019) and the modeled clouds (top) were derived 
-  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
-  (AM4) are 18\% (13\%) for thick clouds and 22\% (6\%) for thin clouds}
+  clouds.  The observations (bottom) are from the MISR satellite (2000-2019) the clouds from AM4.0 (top) were derived 
+  with the MISR simulator in the \textit{amip} experiment. Mean cloud fraction values for MISR 
+  (AM4) are 35.6\% (21.7\%) for thick clouds and 18.7\% (6.4\%) for thin clouds}
   \label{fig:cf_misr_lowcl}
@@
 
-\subsection{COSP}
+\subsection{COSP: change title}
 In order to compare the observed and modeled clouds as consistently as possible across multiple platforms 
@@
   \includegraphics[width=0.98\columnwidth]{cfmipfigs/Silvers_cfmip_MISRv7_cloudtable.pdf}
-  \caption{Cloud Fraction (colors and numbers (\%)) in joint histograms showing the variations of cloud fraction 
+  \caption{Joint histograms of cloud fraction (colors and numbers (\%)) showing the variations of cloud fraction 
   as a function of cloud top height and optical depth (tau).
@@
   the meridional profile of observed cloud fraction.  With only a few exceptions in the polar regions, AM4 underestimates
-  clouds in all three vertical ranges with the largest underestimate being of low-level clouds between +/-30.}
+  clouds in all three vertical ranges with the largest underestimate being of tropical ($\pm \, 30^\circ$) low-level clouds.}
   \label{fig:calipso_9pan}
@@
 
-\section{The Role of Clouds in AM4.0/CM4.0/Aquaplanets in Determining and Influencing Climate Sensitivity}
+\section{The Role of Clouds in CM4.0, AM4.0, and Aquaplanets in Determining and Influencing Climate Sensitivity}
 
@@
 
-The set of new models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate sensitivities.  
-One way of quantifying this sensitivity is with the climate feedback parameter, which 
-varies among a suite of CMIP6 experiments between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).  
-The models that are the focus of this paper (AM4.0 Aquaplanet, AM4.0, CM4.0) simulate several 
-distinct configurations which account for some of the differences in the climate feedback parameter.  
-After a brief review of the methods for estimating the climate sensitivity we show in this section how much of the difference is 
+%The range of ways that the climate sensitivity can be quantified using a single model can be revealing or confusing.  
+%Recently, \cite{Zelinka_etal_2020} found the sensitivity of CM4.0 using the first 150 years of data from the \textit{abrupt-4xCO$_2$}
+%experiment and the regression method of \cite{Gregory_etal_2004} to be 3.89K while \cite{Winton_etal_2020} found the sensitivity to be 5.0K using years 50-300 of the same experiment.
+\citeA{Winton_etal_2020} also showed the TCR of CM4.0 to be 2.1 using the
+%\textit{1pctCO$_2$} experiment.
+Additionally one could calculate the climate sensitivity by running CM4.0 for thousands of years until is equilibrated (as in \citeA{Paynter_etal_2018} for CM2 and CM3) or by using a method similar to that employed by Otto et al., 2014 to infer the sensitivity from \textit{historical} experiment.
+
+The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate sensitivities (possibly cite Held et al., Winton et al., Dunne et al.).  
+One way of quantifying this sensitivity is with the climate feedback parameter, which, for the subset of GFDL models and CMIP6 experiments studied in this paper, varies between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).
+These models (AM4.0 Aquaplanet, AM4.0, CM4.0) simulate several 
+distinct geophysical configurations which account for some of the range in values of the climate feedback parameter.  
+However, our hypothesis is that the large range of climate sensitivities that are found within this 
+group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
+
+After briefly noting different methods of estimating the climate sensitivity we show in the first subsection how much of the difference is 
 due to experimental configuration and how much is due to differences in the CRE.  
-We also show how the cloud fraction varies among
-the experiments as a function of latitude and consider the cloud distribution in the context of the observed
-CRE from the previous section.  The CRE is an effective tool for evaluating the influence of 
-clouds on the climate.  It is well known (Soden et al., 2004) that a change in the CRE is not a direct measure of the cloud 
-feedback, and that non-cloud related values of CRE can occur.  However, there are many cases of 
-the productive use of the CRE as a way to diagnose cloud effects (e.g. Cess et al., 1989; Webb et al., 2001; 
-\citeA{Ringer_etal_2014}; Andrews et al., 2015), it is simple to calculate, and
-it allows for direct comparisons with previous studies.  The true cloud feedback usually corresponds 
-to a positive shift of the change in CRE values by roughly 0.3 $\rm{W m^{-2}K^{-1}}$ (Soden et al., 2004).  The total cloud feedback of a model 
-is therefore more positive than will be implied by the CRE.
-
-Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
-group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
-The clouds in these simulations respond to a variety of different conditions including different
-patterns of prescribed SST, the presence or absence of land/sea ice, and in the case of the aquaplanet
-experiments, a lack of cloud-aerosol interactions which are present in the AGCM and coupled 
-experiments (AOGCM).
-
-\subsection{The Cloud Radiative Effect - Probably should Change.. What is the Climate Sensitivity?}
-
-Due to a combination of changing computing power and differing objectives, the sensitivity of Earth's climate to 
-perturbations has been estimated in many different ways over the past few decades.  
-We have computed the climate feedback parameter that appears in Table 1 with multiple methods.    
-The climate sensitivity can be estimated from the change in radiative flux at the top of the 
-atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
-as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990).  
-Additionally, the climate
-sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
-instantaneously increased relative to the pre-Industrial values.  Linear regression can then be used to 
-estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
-This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
-and used by the IPCC.  The climate sensitivity
-can also be computed from simply measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
-has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
-$\rm{CO}_{2}$ concentration.   This method is used to define the Transient Climate Response (TCR).
-For a particular climate model, the only way to be sure of the climate sensitivity is to run the 
-coupled model after a perturbation has been applied and wait until the model has fully 
-equilibrated.  Evidence indicates that this takes thousands of years of 
-simulation (Stouffer, 2004; Li et al., 2012; Paynter et al., 2018; Rugenstein et al., 2019).
-Because of the limiting cost of such long experiments, determining an accurate measure 
-of the climate sensitivity to perturbations from a simulation that is not fully equilibrated is an 
-essential component of climate science.
-
+We also show (second subsection) how the cloud fraction varies among
+the experiments as a function of latitude and consider the cloud distributions in the context of the observed
+cloud fraction and CRE from section 3.
+
+%\subsection{The Cloud Radiative Effect - Probably should Change.. What is the Climate Sensitivity?} 
+\subsection{The Radiative Response to Warming}
+
+%% tentative hypothesis: 
+%% Amip Future shows a significant difference from amip p4K between about 15S and 65S.  This should lead 
+%% to a CRE feedback that is quite a bit larger than for amip p4k because the two experiments are have
+%% nearly identical CRE's at other latitudes.  
+%%
+%% meanwhile, plotting the CRE differences from amip shows that amip-p4K and amip-m4K are not as 
+%% similar as initially suspected from non difference plots.  When the values of amip-m4K are reversed 
+%% for easier comparison with the warming experiments we see that in the SH amip-m4K is actually between
+%% amip-future4K and amip-p4K.  In the NH amip-m4K has the strongest CRE response of all three experiments, 
+%% this is true north of about 40N.  Why?  
+%%
+%% I also suspect that this is largely due to the sw_cre.  
+%% net_cre:  0.0; 0.07; -0.11             range of 0.18. --> amip -m4K is in the middle
+%%  lw_cre:   0.16;  0.13;   0.10         range of 0.06
+%%  sw_cre: -0.16; -0.07; -0.21         range of 0.14  --> amip -m4K is in the middle
+%
+
+% these numbers were computed using glbmn_toa_cfmip_fb_driver.m and glbmn_toa_cfmip_fb.m
 \begin{table}
@@
     %\bigskip 
-    \label{tab:lambda}
+    \label{tab:lambda_AGCM}
 \end{center}
@@
 
-The DECK experiments of CMIP6 can be used to provide a measure of the climate sensitivity based on 
-three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
-differences in the measures of sensitivity reveal important details of the physics that underly the response
-of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
-experiments are the historical simulation (\textit{historical}: years 1850-2014),  the abrupt quadrupling of 
-$\rm{CO}_2$ concentration (\textit{abrupt-4xCO$_2$}: 300 years for this paper), and the experiment in 
-which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
-284.262 ppm(?units?) until the concentration is doubled  (\textit{1pctCO$_2$}: total of 150 years, doubling at year 70).  
-The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
-observed historical record.  This has frequently been used to estimate the climate sensitivity using the 
-energy budget method 
-(Otto et al., 2013, Armour et al., Andrews et al., \citeA{Winton_etal_2020}; Lewis and Curry?).  
-The \textit{abrupt-4xCO$_2$} experiment has been utilized by the IPCC to derive measures of the 
-ECS among the CMIP5 and CMIP6 models using a linear regression of the change in TOA radiative fluxes 
-and surface air temperature over the first 150 years of the response to the increase in $CO_2$ 
-concentration (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
-$\rm{CO}_2$ concentration, the \textit{1pctCO2} is an experiment of the Earth system when 
-there is a  1 \% per year increase of the $\rm{CO}_2$ concentration until it is doubled relative to the 
-pre-Industrial values.  The sensitivity at the point of doubling is defined 
-as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
-near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
-will reach (insert 2xCO2 value) around the middle of this century.
-
+Due to a combination of changing computing power and differing objectives, the sensitivity of Earth's climate to 
+perturbations has been estimated in many different ways over the past few decades.  
+We have computed the climate feedback parameter that appears in Tables 1 and 2 with multiple methods.    
+The climate sensitivity can be estimated from the change in radiative flux at the top of the 
+atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
+as a proxy for climate change was pioneered by Robert Cess and his colleagues (e.g. 1989, 1990) and has been widely used since.  
+Additionally, the climate
+sensitivity can be estimated from a fully coupled experiment in which the $\rm{CO}_{2}$ concentration is 
+instantaneously increased relative to the pre-Industrial values.  Linear regression can then be used to 
+estimate the sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  
+This is the method used to compute the climate sensitivity reported in Andrews et al., 2012 
+and used by the IPCC.  The Transient Climate Response (TCR), an alternate measure of climate sensitivity that is more 
+relevant for the near future can be computed by measuring the change of surface temperature after the $\rm{CO}_{2}$ concentration
+has been doubled in a fully coupled climate model following an increase of 1\% per year in the 
+$\rm{CO}_{2}$ concentration.   
+The only way to be sure of the equilibrium climate sensitivity for a particular model is to run the 
+coupled model after a perturbation of $\rm{CO}_{2}$ concentration has been applied and wait until the model has fully 
+equilibrated.  Evidence indicates that this takes thousands of years of 
+simulation (Stouffer, 2004; Li et al., 2012; Paynter et al., 2018; Rugenstein et al., 2019).
+Because of the limiting cost of such long experiments, determining an accurate measure 
+of the climate sensitivity to perturbations from a simulation that is not fully equilibrated is an 
+essential component of climate science.  Additional details about the efforts to determine Earth's climate sensitivity 
+and relevant background can be found in Sherwood et al., 2015, Stevens et al., 2016, Knutti et al., 2017, Rugenstein et al., 2020, and Sherwood et al., 2020.
+
+% merge the paragraph below with that above...
+
+%The DECK experiments of CMIP6 can be used to provide estimates of the climate sensitivity based on 
+%three different fully coupled experiments.  The methods used to determine the sensitivity are distinct, and the resulting 
+%differences in the measures of sensitivity reveal important details of the physics that underly the response
+%of the climate system to a perturbation such as increased concentrations of carbon dioxide.  The three 
+%experiments are the historical simulation (\textit{historical}: years 1850-2014),  the abrupt quadrupling of 
+%$\rm{CO}_2$ concentration (\textit{abrupt-4xCO$_2$}: 300 years for this paper), and the experiment in 
+%which the concentration of $\rm{CO}_2$ is increased by 1\%  per year from the pre-industrial value of 
+%284.262 ppm until the concentration is doubled  (\textit{1pctCO$_2$}: total of 150 years, doubling at year 70).  
+%The \textit{historical} simulation is our best attempt at using a coupled GCM to reproduce the 
+%observed historical record.  This has frequently been used to estimate the climate sensitivity using the 
+%energy budget method 
+%(Otto et al., 2013, Armour et al., Andrews et al., \citeA{Winton_etal_2020}; Lewis and Curry).  
+%The \textit{abrupt-4xCO$_2$} experiment has been utilized by the IPCC to derive measures of the 
+%ECS among the CMIP5 and CMIP6 models using a linear regression of the change in TOA radiative fluxes 
+%and surface air temperature over the first 150 years of the response to the increase in $CO_2$ 
+%concentration (Gregory et al., 2004; Andrews et al., 2012; Zelinka et al., 2020).  In contrast to the abrupt change of 
+%$\rm{CO}_2$ concentration, the \textit{1pctCO2} is an experiment of the Earth system when 
+%there is a  1 \% per year increase of the $\rm{CO}_2$ concentration until it is doubled (after 70 years of simulation) relative to the 
+%pre-Industrial values.  The sensitivity at the point of doubling is defined 
+%as the Transient Climate Response (TCR).  The TCR for CM4.0 is $2.05 (\pm0.10) K$ \cite{Winton_etal_2020} and is the relevant 
+%measure of climate sensitivity for near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
+%will double relative to the pre-industrial period near the end of this century.         
+%% one discussion of this is here: 
+%%https://www.climate.gov/news-features/climate-qa/how-much-will-earth-warm-if-carbon-dioxide-doubles-pre-industrial-levels
+%% levels rise by around 2 or 2.5 ppm per year.  They quote PI levels as 275ppm.
+%
+While the net feedback ($\alpha$) is a critical measure of sensitivity, the individual components of the feedback reveal 
+more about the different processes that are active in the experiments.    
 The radiative feedbacks at the TOA were computed for a collection of CMIP5 models by Ringer et al., 2014.  
-The results from that study provide a convenient point of reference for our findings.  
-Accordingly, we use the same method to compute the radiative feedbacks for the GFDL models in Table \ref{tab:lambda}.  
-That is, for the coupled abrupt $4xCO_{2}$ experiment, feedbacks are computed as  
-the slopes of a linear regression calculation using annual, global-mean top-of-atmosphere flux anomalies 
-(\cite{Gregory_etal_2004}; Andrews et al., 2012).  For the atmosphere only experiments 
-(\textit{amip-p4K, amip-m4K, amipFuture}, and \textit{aqua-p4K}), the feedbacks are calculated as the 
+\textit{The results from that study provide a convenient point of reference for our findings.}  
+Table \ref{tab:lambda_AGCM} shows feedback values for several of the CFMIP atmosphere only experiments 
+(\textit{amip-p4K, amip-m4K, amipFuture}, and \textit{aqua-p4K}).  These feedbacks are calculated as the 
 differences in TOA flux anomalies between the perturbation and control experiments, normalized 
-by the change in surface air temperature.  In addition, we include values that have been computed from the 
-\textit{1pctCO2} experiment.   Positive values indicate a feedback that leads to warming of the climate system.
+by the change in surface air temperature.   Positive values indicate a feedback that leads to warming of the climate system. 
+Table \ref{tab:lambda_AGCM}  shows is that the AM4.0 aquaplanet is substantially less sensitive 
+($\alpha$ is more negative) than any of the \textit{amip}-type experiments.  Approximately 0.3 $W\, m^{-2} K^{-1}$ 
+of this difference is due to a weak surface-albedo feedback (SW CLR) in the aquaplanet expderiment, and the other roughly 
+0.2 $W\, m^{-2} K^{-1}$ is due to a more negative net CRE.  Overall, there are strong similarities among the 
+\textit{amip}-type experiments, especially in the clear sky feedback terms.  Among the \textit{amip}-type experiments, the 
+patterned warming experiment (\textit{amipFuture}) is a bit (0.2 $W\, m^{-2} K^{-1}$) less sensitive, largely due to a more 
+negative SW CRE response.
+
+% Now we need to describe how the feedbacks in Table 2 have been computed...
+
+It is also instructive to examine the values of the climate feedback parameters that result from experiments that include a 
+dynamic ocean.  Feedbacks computed for the coupled model experiments (\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , and 
+\textit{historical}) are shown in Table \ref{tab:lambda_AOGCM}.  The Earth's global mean energy budget is frequently used 
+to compute sensitivities in the context of a forcing-response framework (e.g. Gregory et al., 2004; Andrews et al., 2015; 
+Sherwood et al. 2015).  This is expressed as $N=F-R$ where the global heat uptake, or the radiative imbalance at the TOA 
+($N; W\, m^{-2}$) is equal to the radiative forcing ($F;  W\, m^{-2}$) minus the radiative response, ($R; W\, m^{-2}$) which is 
+often assumed to be $-\alpha T$, the product of the climate feedback parameter ($\alpha;  W\, m^{-2} K^{-1}$) and the change 
+of the surface air temperature ($T; K$).  
+Rather than using the linear regression method to calculate the ECS from the \textit{abrupt-4xCO$_2$} experiment, or calculating the 
+traditional TCR value from the \textit{1pctCO2} experiment we use the differences in the global mean energy budget between control 
+periods and the period of interest to calculate the climate feedback parameter as $-\alpha = (F-N)/T$. 
+The advantage of this is that we can then use the same method to compute radiative feedback values from particular periods of the 
+\textit{abrupt-4xCO$_2$}, \textit{1pctCO2} , \textit{historical} and \textit{amip} experiments.
+
+The energy budget framework as applied to particular experiments can be written as:
+\begin{equation}
+  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
+\end{equation}
+\begin{equation}
+  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
+\end{equation}
+\begin{equation}
+  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
+\end{equation}
+\begin{equation}
+  \alpha_{amip}=-\frac{F_{amip}-N_3}{T_3}
+\end{equation}
+where $F_{4xCO_2}=N_{4xCO2}-N_{piControl}$; $F_{hist}=N_{hist(1996-2014)}-N_{piControl}$; 
+$F_{1pctCO_2}=0.79F_{4xCO2}$.  
+%The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  
+$N_1$ and $T_1$ correspond to differences between years 101-150 and 100 years of \textit{piControl}, $N_2$ and $T_2$ correspond to differences between years 1996-2014 and 100 years of \textit{piControl}, and $N_3$ and $T_3$ correspond to differences between years 1996-2014 and 1870-1890 of a long \textit{amip} experiment.
+%Note that the subscript indicates the time period over which a variable is calculated, not the value of the variable, 
+% so $T_1$ is different in the \textit{abrupt-4xCO$_2$} and \textit{1pctCO2} experiments.
+The relatively small span of years for $T_2$ and $T_3$ were chosen to avoid the impact of volcanic behavior in the early 1990's 
+that, if included, complicate the interpretation of the climate feedback.  
+As in Table \ref{tab:lambda_AGCM}, positive values indicate a feedback that leads to warming of the climate system.
+
+To facilitate comparison with the recent decades over which the observations in the first part of this paper are relevant 
+we calculate feedbacks from the \textit{historical} and \textit{amip} experiments using the years 1996-2015 
+(feedbacks are relative to piControl).  We also calculate feedbacks from the coupled warming experiments 
+\textit{abrupt-4xCO$_2$} and \textit{1pctCO$_2$} over the years 100-150.
+Coupled simulations of future warming show a LW CRE feedback in which the effect of clouds is to increase warming while 
+the simulations of the years 1996-2014 show feedbacks that lead to cooling from both the SW CRE and the 
+LW CRE.   This leads to a substantial difference in the net CRE feedback between warming experiments and those simulating recent 
+decades.  Feedback values of the net CRE for the \textit{abrupt-4xCO$_2$} experiment computed with linear regression show an even 
+larger difference (SW CRE is positive) compared to recent decades.  
+%The SW CRE in the later term warming (\textit{abrupt-4xCO$_2$}) is strongly positive, while for all of the experiments covering
+%earlier periods it is negative. 
+% This underscores previous literature that shows the climate feedback parameter to be highly variable and illustrates why calculations of 
+% climate sensitivity using recent observations (e.g. Otto et al.) arrive at such different numbers than do studies which look at model 
+% simulations of future warming (e.g. Winton et al.).   Perhaps this type of sentence is better in the conclusions?
+
+The radiative feedbacks shown in Tables \ref{tab:lambda_AGCM} and \ref{tab:lambda_AOGCM} reveal a large range of 
+net climate feedback parameter ($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in both the 
+cloudy and clear sky fluxes.   
+% The LW CLR feedback is nearly constant between the aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   
+% The SW CLR feedback is nearly constant across the \textit{amip} experiments but varies significantly
+%between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
+%The relatively large range of the SW CRE (from -0.65 $\rm{W m^{-2}K^{-1}}$ to 0.5 $\rm{W m^{-2}K^{-1}}$)
+%confirms the important role played by mid- and low-level clouds outside of the region of 
+%deep tropical convection where the LW and SW effects of clouds largely cancel.  
+%
+As described by Ringer et al., 2014, much of the range in the short wave clear-sky feedback can be attributed to differences 
+in the experimental configurations of ice.  The aquaplanet experiments have no land and no sea ice.  
+The \textit{amip} experiments have ice in the polar regions, but the ice is prescribed based on observations and 
+only changes to a limited degree.  However, the fully coupled experiments \textit{abrupt-4xCO$_2$}, 
+\textit{1pctCO2}, and \textit{historical} predict changes in the extent of sea-ice and show a larger positive SW CLR
+feedback that results in part from the positive ice-albedo feedback.  
+Thus, part of the range of values in the clear sky radiative fluxes is the result of differences in the physical configuration 
+of the various experiments.  
+However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations.
+
+\textit{The clouds in these simulations respond to a variety of different conditions including different
+patterns of SST, the presence or absence of land or sea ice, and in the case of the aquaplanet
+experiments, a lack of cloud-aerosol interactions which are present in the AGCM (AM4.0) and coupled 
+experiments (AOGCM; CM4.0).  }
+
+%The LW CLR is nearly uniform across experiments due to the fundamental physics of the Planck feedback.  
+%, the SW CLR varies as we expect it to based on the physical configuration of the experiments and is strongly dependent on 
+% surface albedo.
+
+%The relationship between the LW CRE and SW CRE can reveal the different ways in which clouds influence the net climate feedback.  
+%For many experiments the SW CRE is negative and exerts a cooling on the system while the 
+%LW CRE is positive.  For experiments such as \textit{aqua p4K}, \textit{amip p4K}, and \textit{amip-future4K} 
+%this results in some cancelation between the CRE feedback terms (Table \ref{tab:lambda_AGCM}).  However, for several of the 
+%coupled experiments shown in Table \ref{tab:lambda_AOGCM} the two components of the CRE feedback are
+%of the same sign and do not cancel.  For the
+%\textit{abrupt-$4x\rm{CO}^a_2$} experiment both LW and SW cloud feedback are positive with a total 
+%CRE feedback of $0.65 \rm{W\, m^{-2} K^{-1}}$, while the \textit{historical} experiment has both the LW and SW
+%CRE feedbacks as negative, which results in a fairly strong  negative total CRE feedback of $-0.45 \rm{W\, m^{-2} K^{-1}}$.    
+%% why does the LWCRE flip sign?  reduced extent of anvils?
+
+%The cloud radiative effect (CRE) is computed as the clear sky minus all sky TOA flux.
+
+\begin{table}
+\begin{center}
+\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  Values in the first four columns are calculated as differences for 
+particular years (see text).  The values for the \textit{abrupt 4x$\rm{CO}_2^{b}$} and  \textit{abrupt 4x$\rm{CO}_2^{c}$} experiments
+have been calculated using linear regression over years 1-150 and 51-300, respectively.  
+\textit{abrupt 4x$\rm{CO}_2^{a}$}, \textit{abrupt 4x$\rm{CO}_2^{b}$}, and \textit{abrupt 4x$\rm{CO}_2^{c}$} represent data from the same experiment, the feedback values have simply been calculated differently.
+}
+    \begin{tabular}{*{7}{c}}
+    \hline
+    \hline
+ Feedback     &  Amip   & Historical   &  1pct$CO_2$ & Abrupt 4x$\rm{CO}_2^{a}$ &  Abrupt 4x$\rm{CO}_2^{b}$ &  Abrupt 4x$\rm{CO}_2^{c}$ \\ \hline
+    Net $\alpha$    & -1.77      &   -1.83      &  -1.22          &  -1.11    &  -0.82   &   -0.46              \\ 
+    \\
+    Net CRE  &    -0.46            &   -0.45       &  -0.16          & -0.06   & ?      &   0.65         \\  
+    \\
+    LW CRE    &   -0.03           &   -0.14        &  0.10            & 0.14   &  ?        & 0.14          \\  
+    \\
+    SW CRE  &     -0.43             &    -0.31       &  -0.26            & -0.20    &  ?      &  0.5         \\  
+    \\
+    LW CLR   &     -2.25             &    -1.94       &  -1.71            & -1.70    &   ?      & -1.7        \\  
+    \\
+    SW CLR  &      0.91            &     0.56        & 0.65              & 0.65    &    ?         & 0.6          \\  
+    \\
+    $\Delta \rm{T}_s$     &     1.3     & 0.8        &  4.3           & 5.7     &   -         & -          \\  \hline
+
+    \end{tabular}\par
+    \label{tab:lambda_AOGCM}
+\end{center}
+\end{table}
 
@@
   %\includegraphics[width=\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_SinglePanel_negativesign.pdf}
-  \includegraphics[width=0.75\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
+  \includegraphics[width=0.5\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
   \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  The top panel 
@@
 
-% tentative hypothesis: 
-% Amip Future shows a significant difference from amip p4K between about 15S and 65S.  This should lead 
-% to a CRE feedback that is quite a bit larger than for amip p4k because the two experiments are have
-% nearly identical CRE's at other latitudes.  
-%
-% meanwhile, plotting the CRE differences from amip shows that amip-p4K and amip-m4K are not as 
-% similar as initially suspected from non difference plots.  When the values of amip-m4K are reversed 
-% for easier comparison with the warming experiments we see that in the SH amip-m4K is actually between
-% amip-future4K and amip-p4K.  In the NH amip-m4K has the strongest CRE response of all three experiments, 
-% this is true north of about 40N.  Why?  
-%
-% I also suspect that this is largely due to the sw_cre.  
-% net_cre:  0.0; 0.07; -0.11             range of 0.18. --> amip -m4K is in the middle
-%  lw_cre:   0.16;  0.13;   0.10         range of 0.06
-%  sw_cre: -0.16; -0.07; -0.21         range of 0.14  --> amip -m4K is in the middle
-
-The radiative feedbacks shown in Table \ref{tab:lambda} reveal a large range of net feedback parameter 
-($\alpha$; -0.46 to -2.13 $\rm{W m^{-2}K^{-1}}$) that results from differences in 
-both the cloudy and clear sky fluxes.   The LW CLR feedback is nearly constant between the 
-aquaplanet and various \textit{amip} experiments (LWCLR for abrupt??).   The SW CLR 
-feedback is nearly constant across the \textit{amip} experiments but varies significantly
-between the \textit{aqua p4K} and the two coupled experiments (0.67 $\rm{W m^{-2}K^{-1}}$).
-The relatively large range of the SW CRE (either 0.58 $\rm{W m^{-2}K^{-1}}$ or 1.15 $\rm{W m^{-2}K^{-1}}$)
-confirms the important role played by mid- and low-level clouds outside of the region of 
-deep tropical convection where the LW and SW effects of clouds largely cancel each other.
-
-As described by Ringer et al., 2014, the changes in the SW CLR feedback are largely due to differences 
-in the experimental configurations of ice.  The aquaplanet experiments have no land and no sea ice.  
-The \textit{amip} experiments have ice in the polar regions, but the ice is prescribed based on observations and 
-only changes to a limited degree.  However, the fully coupled experiments \textit{abrupt-4xCO$_2$} and 
-\textit{1pctCO2} both allow the extent of sea-ice to change and therefore have a larger positive SW CLR
-feedback that results in part from the positive ice-albedo feedback.  Thus, the range of values in the clear
-sky radiative fluxes are the result of differences in the physical configuration of the various experiments.  
-However, the remaining spread of total feedback parameter among experiments is due to differences
-in cloud feedbacks that are not as easily connected to particular experimental configurations.  For 
-most of the experiments the SW CRE is negative and exerts a cooling on the system while the 
-LW CRE is positive.  For experiments such as \textit{aqua p4K}, \textit{aqua p4K}, and \textit{amip-future4K} 
-this results in some cancelation between the CRE feedback terms.  However, in the 
-two coupled experiments shown in Table \ref{tab:lambda}, there is little cancelation between
-the two components of the CRE feedback.  For the
-\textit{abrupt-4xCO$_2$} experiment both LW and SW cloud feedback are positive with a total 
-CRE feedback of $0.65 \rm{W\, m^{-2} K^{-1}}$, and in the \textit{1pctCO2} experiment the LW 
-CRE feedback is nearly zero 
-resulting in a fairly strong  negative total CRE feedback of $-0.30 \rm{W\, m^{-2} K^{-1}}$.      
-While the net feedback is the critical measure of sensitivity, the individual components 
-reveal much about the experiments.  The LW CLR is nearly uniform across experiments 
-due to the fundamental 
-physics of the Planck feedback, the SW CLR varies as we expect it to based on the 
-physical configuration of the experiments.  It is the relationship between the LW and SW 
-components of the CRE that reveals the different ways in which clouds are influencing the 
-net climate feedback.
-
-\begin{table}
-\begin{center}
-\caption{Global mean radiative feedbacks ($\rm{W\, m^{-2} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
- the clear sky minus all sky TOA flux.  The values for the Abrupt 4x$\rm{CO}_2^{a}$ experiment
-have been estimated from a linear fit of the years 51-300 (\textit{the Net value reported by Zelinka from a 150 yr regression was -0.82}).}
-    \begin{tabular}{*{6}{c}}
-    \hline
-    \hline
- Feedback   &    Abrupt 4x$\rm{CO}_2^{a}$   &  Abrupt 4x$\rm{CO}_2^{b}$  & 1pct$CO_2$   & Historical    &  Amip   \\ \hline
-    Net $\alpha$    &     -0.46     &   -1.11      &  -1.22          &  -1.83         & -1.77               \\ 
-    \\
-    Net CRE  &    0.65    & -0.06       &  -0.26          & -0.45         & -0.46           \\  
-    \\
-    LW CRE    &   0.14       & 0.14        &  0.10            & -0.14           & -0.03          \\  
-    \\
-    SW CRE  &    0.5     &    -0.20       &  -0.26            & -0.31          & -0.43         \\  
-    \\
-    LW CLR   &   -1.7     &  -1.70       &  -1.71            & -1.94           & -2.25        \\  
-    \\
-    SW CLR  &      0.6         &   0.65        & 0.65              & 0.56             & 0.91          \\  
-    \\
-    $\Delta \rm{T}_s$     &     ?     & 3.99        &  ??                & 0.8              & 0.76          \\  \hline
-
-    \end{tabular}\par
-    %\bigskip 
-    \label{tab:lambdahist}
-\end{center}
-\end{table}
-
-It is also instructive to examine the values of the climate feedback parameter that result from simulations of 
-recent decades.  In Table \ref{tab:lambdahist} we calculate the feedbacks for the coupled and amip experiments 
-using   the difference in surface temperature  
-relative to the piControl experiment for $T_1$ and as a difference from the first 20 years of the amip experiment for $T_2$.
-\begin{equation}
-  \alpha_{4xCO_2}=-\frac{F_{4xCO_2}-N_1}{T_1}
-\end{equation}
-\begin{equation}
-  \alpha_{1\%CO_2}=-\frac{F_{1\%CO_2}-N_1}{T_1}
-\end{equation}
-\begin{equation}
-  \alpha_{hist}=-\frac{F_{hist}-N_2}{T_2}
-\end{equation}
-\begin{equation}
-  \alpha_{amip}=-\frac{F_{amip}-N_2}{T_2}
-\end{equation}
-
-In the above equations $F_{4xCO_2}=N_{4xCO2}-N_{PiC}$; $F_{hist}=N_{hist(1996-2014)}-N_{PiC}$; 
-$F_{1pctCO_2}=0.79F_{4xCO2}$.  The radiative imbalance at TOA, $N$ is calculated over different periods depending on the experiment.  
-%In all cases the years used for $N$ and $T$ are the same.  
-$N_1$ and $T_1$ corresponds to years 101-150, while $N_2$ and $T_2$ corresponds to years 1996-2015.  
-The relatively small span of years for $T_2$ were chosen to avoid the impact of volcanic behavior in the early 1990's that if included
-complicate the interpretation of the climate feedback.  Feedbacks thus calculated are given in Table \ref{tab:lambdahist}.
-
-As discussed in the previous section and in Z18a,b, both AM4.0 (\textit{amip}) and 
-CM4.0 (\textit{historical}) compare well to the global mean CERES-EBAF TOA radiative fluxes.  
-It is also interesting to see how the CRE from warming experiments contrast with the current observations
-and the experiments based on historical simulations. 
-Figure \ref{fig:CRE_feedback} shows the latitudinal distribution of CRE from the CERES-EBAF
-observations, two historical experiments (\textit{amip} and \textit{historical}) and two warming 
-experiments (\textit{abrupt-4xCO$_2$} and \textit{1pctCO2}).    
-Comparing the coupled simulations of warming experiments from CM4.0 to the the CERES-EBAF 
-and \textit{amip} TOA fluxes shows how the CRE differs in the \textit{abrupt-4xCO$_2$} and 
-\textit{1pctCO2} experiments (Figure \ref{fig:CRE_feedback}).
-Despite similar biases relative to observations, these warming experiments show a much
-stronger negative CRE in the arctic than the historical experiments, more cloud related 
-cooling around 20S and a poleward shifted cloud related cooling around 50S-60S.
-
-To compute the cloud feedback based on the CRE, the control state CRE of 
-the \textit{amip} and \textit{aqua} experiments is subtracted from the CRE in the perturbed experiment.  
-The latitudinal distribution of the SW CRE is shown in the right panel of Figure \ref{fig:CRE_feedback}.  
-This shows which regions are responsible for the large range of differences in the SW CRE shown in Table \ref{tab:lambda}.  
-Note from Table 1 that the net CRE is -0.27, -0.11, 0.0, and 0.07 for the \textit{aqua-p4K}, 
-\textit{amip-Future4K}, \textit{amip-m4K}, and \textit{amip-p4K}, respectively.  
-While some of this range is due to contributions from the LW CRE, the relative values of the net feedback are reflected in the SW CRE.  
-Figure (\ref{fig:CRE_feedback}) shows the p4K aquaplanet experiment to have a hemispherically symmetric response 
-that is dominated by three bands of cloud response in the deep tropics, at 30, and at 55 degrees.   
-\textit{For the three \textit{amip} experiments the hemispheric symmetry is broken by the continents and the strongest cloud 
-response is seen to be in the southern hemisphere, specifically between 55S and 65S.}
-This figure also shows how different the CRE response for the patterned warming 
-(\textit{amip-Future4K}) is from the uniform warming (\textit{amip-p4K}).  
-These two experiments both have global mean warming of SST by 4K, but 
-the response of the SW CRE is different between 65S and 20N.  The difference 
-in the SW CRE between the \textit{amip-p4K} and \textit{amip-Future4K} experiments
-is due to the the region between the equator and 65S.  
-The meridional distribution of the CRE feedback for the \textit{amip-p4K} and
-\textit{amip-m4K} experiments also reveals that despite 
-similar net CRE (-1.62 and -1.66), the latitudinal spatial response shown in the CRE
-differs considerably between the experiments.
-
-Can we understand these large differences in the cloud feedbacks by looking at the cloud 
-fields produced by these experiments?
-
-\subsection{The Distribution of Cloud Fraction in Warming Experiments}
-
-%These different experimental configurations influence how much of an impact the ice-albedo feedback plays.  
-%The more dynamic the ice is for a given experiment, the more positive will the SW CLR 
-%feedback be as a result of the ice-albedo feedback.
+%% Table 2 shows that the hist and amip experiments over this time period can be grouped together, as can the abrupt and 
+%% 1pct CO2 experiments.  This is distinct from looking at the longer term results 
+%% of the abrupt 4xCO2 experiment as is done with the  abrupt 4x$\rm{CO}_2^{a}$ column.    Why 
+%% is the LW CLR feedback for \textit{amip} so much more negative than the other experiments (possibly related to the lapse rate feedback)?   
+%
+%% questions for David: 
+%% 1.  why do we use years 101-150 in equations 1 and 2 to calculate feedbacks for the abrupt and 1pct experiments?  According
+%% to Winton et al., at 140 the 1pctCO2 experiment reaches a 4xCO2 concentration.... Does this period, between 101-150 then
+%% lead to a better comparison?
+%%
+%% 4.  What are the forcing values used for the alpha_historical and alpha_amip? F(mean year 1996-2015)?  
+%%
+%% 5.  Why is LW CLR for amip so much more negative relative to the other experiments?  
+%
+%%  4xCO2a is the only case for which the SWCRE is strongly positive.  
+%
+%%. how does the ratio of warming between 100-300 mb and the surface warming in the tropics compare between the 
+%%  experiments in Table 2?    Is this evidence for a stronger lapse-rate feedback in the amip experiments relative to the 
+%%. coupled case?   
+%
+%As discussed in the previous section and in Z18a,b, both AM4.0 (\textit{amip}) and 
+%CM4.0 (\textit{historical}) compare well to the global mean CERES-EBAF TOA radiative fluxes.  
+%How do the radiative TOA fluxes compare at different latitudes?  Does the latitudinal structure of the TOA 
+%radiative fluxes change in the warming experiments?    
+%%It is also interesting to see how the CRE from warming experiments contrast with the current observations
+%%and the experiments based on historical simulations. 
+%Figure \ref{fig:CRE_feedback} shows the latitudinal distribution of CRE from the CERES-EBAF
+%observations, two historical experiments (\textit{amip} and \textit{historical}) and two warming 
+%experiments (\textit{abrupt-4xCO$_2$} and \textit{1pctCO2}).    
+%Comparing the coupled CM4.0 simulations of warming experiments with the \textit{historical}
+%and \textit{amip} TOA fluxes shows that in both of the warming experiments the CRE is more negative in the arctic 
+%and that the Southern Hemisphere minimum near 50$^{\circ}$ shifts poleward.
+
+%  
+%How does the CRE differ between the \textit{abrupt-4xCO$_2$} and 
+%\textit{1pctCO2} experiments (Figure \ref{fig:CRE_feedback}).
+%Despite similar biases relative to observations, these warming experiments show a much
+%stronger negative CRE in the arctic than the historical experiments, more cloud related 
+%cooling around 20S and a poleward shifted cloud related cooling around 50S-60S.
+
+%To compute the cloud feedback based on the CRE, the control state CRE of 
+%the \textit{amip} and \textit{aqua} experiments is subtracted from the CRE in the perturbed experiment.  
+To gain further insight into the sources of differences among the CRE values in Tables  \ref{tab:lambda_AGCM}  and  
+\ref{tab:lambda_AOGCM}  we plot the observed CRE as a function of latitude alongside the CRE from the 
+experiments shown in Table  \ref{tab:lambda_AOGCM}.  Observations from CERES-EBAF are shown for version 
+2.8 (black dashed) and for version 4.1 (black).  During the development of AM4.0 version 2.8 of CERES-EBAF was 
+used extensively \cite{Zhao_etal_2018a}.  The distributions of CRE in warming experiments are not directly comparable 
+to observations from recent periods but rather show how potential changes in the effects of clouds vary with latitude.   
+Note the large differences in the arctic and the shift poleward in the SH of the minimum in CRE.
+
+The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback in the three coupled CM4.0 experiments and in the \textit{amip} experiment.
+Values shown in Table 2 imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
+do not have as much of a cooling effect as they do in the \textit{historical} and \textit{amip} experiments.
+The middle panel of Figure \ref{fig:CRE_feedback} illustrates that this is due to the warming experiments having a CRE feedback that is near zero or slightly positive throughout much of the mid-latitudes and tropics while the \textit{historical} experiment shows a negative CRE feedback at nearly all latitudes.
+Comparing the \textit{amip} CRE feedback to the warming experiments in the
+middle panel of Figure \ref{fig:CRE_feedback} is more difficult due to the large positive CRE in the tropics and the very strong negative feedback between about 40-65$^{\circ}$S.
+Anomalies in the middle panel of Figure \ref{fig:CRE_feedback} have been computed relative to the \textit{piControl} experiment.
+The CRE and warming are
+computed for the years 1996-2014 (\textit{historical} and \textit{amip}) and years 100-150 (\textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$}).
+
+Latitudinal distributions of the SW CRE are shown for the \textit{amip}-type and the aqua-p4K experiments in the bottom 
+panel of Figure \ref{fig:CRE_feedback}.  Shown are the \textit{amip-Future4K} (red), \textit{amip-p4K} (green), 
+\textit{amip-m4K} (dark blue), and the aqua-p4K (light blue).   Table 1 shows the aqua-p4K experiment to have a net CRE 
+that is 0.2-0.3  $\rm{W\, m^{-2} K^{-1}}$ more negative than the \textit{amip}-type experiments.  Figure 
+\ref{fig:CRE_feedback} shows this as due to a negative SW CRE feedback in the deep tropics, and a strong negative 
+SW CRE feedback poleward of about 45$^{\circ}$.  
+Also note that despite similar amounts of global mean warming in the \textit{amip-p4K} (green) and 
+\textit{amip-Future4K} (red), the net climate feedback parameter ($\alpha$) is 0.2 $\rm{W\, m^{-2} K^{-1}}$ more negative
+in the \textit{amip-Future4K} experiment due to a different SW CRE response in the southern hemisphere.  
+The sign of the feedback values for the \textit{amip-m4K} experiment was reversed so that the symmetry with the CRE
+feedback from the \textit{amip-p4K} experiment can be easily assessed.  An interesting point that emerges is that 
+despite very similar net feedback values (-1.62 and -1.66), there are noticeable differences in the SW CRE between 
+these two experiments, in particular in the southern hemisphere between -40 and -65$^{\circ}$.
+
+All of the panels in Figure \ref{fig:CRE_feedback} point to the importance of the cloudy response in the southern 
+hemisphere.   The net CRE is notably stronger compared to the northern hemisphere, and the many of the differences 
+in the CRE among the various experiments studied here can be seen as a result of different distributions of southern 
+hemisphere CRE responses.  The region between 40-70$^{\circ}$ is particularly important.
+
+%In the bottom panel the feedback for the \textit{amip}-type experiments is calculated
+%relative to \textit{amip} while the feedback for the \textit{aqua-p4K} is computed relative to the \textit{aqua-control}
+%experiment.
+
+% discusses the amip like experiments...
+%
+%This shows which regions are responsible for the large range of differences in the SW CRE shown in Table \ref{tab:lambda_AGCM}.  
+%Note from Table 1 that the net CRE is -0.27, -0.11, 0.0, and 0.07 for the \textit{aqua-p4K}, 
+%\textit{amip-Future4K}, \textit{amip-m4K}, and \textit{amip-p4K}, respectively.  
+%While some of this range is due to contributions from the LW CRE, the relative values of the net feedback are reflected in the SW CRE.  
+%Figure (\ref{fig:CRE_feedback}) shows the p4K aquaplanet experiment to have a hemispherically symmetric response 
+%that is dominated by three bands of cloud response in the deep tropics, at 30, and at 55 degrees.   
+%\textit{For the three \textit{amip} experiments the hemispheric symmetry is broken by the continents and the strongest cloud 
+%response is seen to be in the southern hemisphere, specifically between 55S and 65S.}
+%This figure also shows how different the CRE response for the patterned warming 
+%(\textit{amip-Future4K}) is from the uniform warming (\textit{amip-p4K}).  
+%These two experiments both have global mean warming of SST by 4K, but 
+%the response of the SW CRE is different between 65S and 20N.  The difference 
+%in the SW CRE between the \textit{amip-p4K} and \textit{amip-Future4K} experiments
+%is due to the the region between the equator and 65S.  
+%The meridional distribution of the CRE feedback for the \textit{amip-p4K} and
+%\textit{amip-m4K} experiments also reveals that despite 
+%similar net CRE (-1.62 and -1.66), the latitudinal spatial response shown in the CRE
+%differs considerably between the experiments.                                                
+%
+%Can we understand these large differences in the cloud feedbacks by looking at the cloud 
+%fields produced by these experiments?
+
+\subsection{The Response of Clouds to Warming}
+
+The anticipated responses of clouds to warming include anvil clouds rising to higher altitudes, a 
+shift of cloud phase towards more liquid clouds at high-latitude, and in many cases a decrease in the 
+low-level cloud amount (references).  This subsection examines the latitudinal distribution of low-, mid-, and upper-level clouds across 
+several of CMIP6 and CFMIP experiments that the AM4.0 Aquaplanet, AM4.0, and CM4.0 participated in.  First, we compare the 
+cloud fraction from the \textit{amip}-type experiments to the observations from CALIPSO (Figure \ref{fig:calipso_amip_comparison}).   
+We will then look at the cloud fields for warming experiments and examine the cloud fraction biases relative to the \textit{piControl} 
+experiment and relative to the \textit{amip} experiment (Figure \ref{fig:CF_warming}).   All results from AM4.0 or CM4.0 are from 
+the CALIPSO satellite simulator.
+
+For the low-level clouds, and the tropical mid-level clouds, the range of cloud fraction among the \textit{amip}-type
+experiments is less than the cloud fraction bias with observations.  However, at high latitudes for the mid-level and upper-level, 
+the range of cloud fraction is larger and in some cases approaches the observed cloud fraction.   
+ %%These different experimental configurations influence how much of an impact the ice-albedo feedback plays.  
+%%The more dynamic the ice is for a given experiment, the more positive will the SW CLR 
+%%feedback be as a result of the ice-albedo feedback.
 
@@
 
-Several of the CFMIP experiments are based on the DECK \textit{amip} experiment.  The cloud fraction from three 
-of these \textit{amip}-type experiments (\textit{amip-m4K}, \textit{amip-p4K}, and \textit{amip-future4K}) 
-are plotted alongside the CALIPSO observations and the DECK 
-\textit{amip} experiment in Figure \ref{fig:calipso_amip_comparison}.  These profiles of cloud fraction verify
-several characteristics of warming that we expect based on previous studies.  Warming leads to 
-an increase of upper-level tropical clouds and a decrease of low-level tropical clouds.  Probably the most 
-obvious warming signal in the cloud fields is an increase in the clouds of the polar regions.  We have also 
-including the \textit{amip-m4K} experiment (blue line) in Figure \ref{fig:calipso_amip_comparison} in which the 
-SST was decreased uniformly by 4K.  Comparison
-with the \textit{amip-p4K} (green line) shows cloud fraction responses that in most cases are mirror images
-of each other about the \textit{amip} experiment.   The differences in the cloud response to a uniform warming
-of 4K (\textit{amip-p4K}) and a patterned warming of 4K (\textit{amip-future4K}) will be discussed in the 
-context of the biases relative to \textit{amip} in a later paragraph.
-
-%\begin{figure}
-%  \centering
-%  \begin{subfigure}{0.45\textwidth}
-% % \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_warming.eps}.
-%  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_warming.eps}
-%  \caption{Cloud fraction for experiments with warming.  For the coupled model experiments
-%  \textit{1pctCO2} and \textit{abrupt-4xCO2} the average of years 100-150 of the simulation is plotted.  
-%  For reference cloud fraction from the 
-%  \textit{historical} and \textit{amip} are also shown.}
-%  \label{fig:warming_exps}
-%\end{subfigure}
-%\begin{subfigure}{0.45\textWidth}
-%  \includegraphics[width=0.6\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_warming_amipbias.eps}
-%  \caption{Cloud fraction bias (relative to \textit{amip}) for experiments with warming. 
-%  For the low-level clouds note that the coupled experiments have a CF maximum bias (5-6\%) at -20 and -75 
-%  where the prescribed uniform warming
-%  does not.  The coupled model experiments produce much less CF in the latitudes between 30-70.  All warming 
-%  experiments have more arctic low-level clouds than the \textit{amip} experiment while the \textit{amip} 
-%  experiment has too many arctic low-level clouds based on the CALIPSO data.}
-%  \label{fig:warming_exps_bias}
-%\end{subfigure}
+%Several of the CFMIP experiments are based on the DECK \textit{amip} experiment.  The cloud fraction from three 
+%of these \textit{amip}-type experiments (\textit{amip-m4K}, \textit{amip-p4K}, and \textit{amip-future4K}) 
+%are plotted alongside the CALIPSO observations and the DECK 
+%\textit{amip} experiment in Figure \ref{fig:calipso_amip_comparison}.  These profiles of cloud fraction verify
+%several characteristics of warming that we expect based on previous studies.  Warming leads to 
+%an increase of upper-level tropical clouds and a decrease of low-level tropical clouds.  Probably the most 
+%obvious warming signal in the cloud fields is an increase in the clouds of the polar regions.  We have also 
+%including the \textit{amip-m4K} experiment (blue line) in Figure \ref{fig:calipso_amip_comparison} in which the 
+%SST was decreased uniformly by 4K.  Comparison
+%with the \textit{amip-p4K} (green line) shows cloud fraction responses that in most cases are mirror images
+%of each other about the \textit{amip} experiment.   The differences in the cloud response to a uniform warming
+%of 4K (\textit{amip-p4K}) and a patterned warming of 4K (\textit{amip-future4K}) will be discussed in the 
+%context of the biases relative to \textit{amip} in a later paragraph.
 
@@
 
-Figure \ref{fig:CF_warming}  is similar to Figure \ref{fig:calipso_amip_comparison} but focuses on
-warming experiments.  
-In addition to the two \textit{amip}-like warming experiments just discussed, Figure \ref{fig:CF_warming} 
-plots the cloud fraction of two fully coupled warming experiments from the CMIP6 DECK 
-(\textit{abrupt-4xCO2} and \textit{1pctCO2}). The cloud fields in these experiments are 
-similar to each other, with the differences arising from either the different SST patterns or the 
-different CO$_{2}$ concentrations.  
-Overall there is an increase (relative to the historical period) in upper-level cloud fraction and a 
-decrease in mid-level cloud fraction for the warming experiments.   The response across warming experiments
-of the low-level clouds is more complicated.  Changes relative to the \textit{amip} cloud fraction are shown 
-in the right panel of Figure \ref{fig:CF_warming} to help identify the differences.  Two separate cloud responses are apparent.  
-%Overall, the coupled warming  experiments and the amip-based warming experiments represent two separate cloud fraction responses to warming.  
-Distinctive features of the coupled warming experiments are a strong decrease of NH 
-mid-latitude low-level clouds but increases of low-level cloud fraction in the southern hemisphere tropics and the Southern Ocean.  
-Distinctive features of the amip-warming experiments are increases of 5-7\% 
-upper-level cloud fraction poleward of $-70^\circ$ and large decreases of mid-level SH cloud fraction.  All warming
-experiments show an increase of upper-level clouds over the polar regions.  All coupled models 
-(including the historical)  have more clouds in the region between 60S and 80S relative to \textit{amip}.
-The primary difference between \textit{amip-p4K} and \textit{amip-future4K} is that there is an increase 
-throughout much of the SH in low-level clouds in the experiment with a patterned warming.  This is 
-reflected in Table 1 where it is clear that the primary differences in radiative feedbacks between these
-two experiments is in the SW CRE feedback.
-
-Now that the different cloud fields among the suite of experiments are clear we can revisit the
-radiative feedbacks from these experiments to see if there is any correspondence between the 
-simulated cloud fields and and the cloud radiative effects.      ???? seems out of place?
-
-%% Beta feedback??  relavent?
-%Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
-%changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
-%low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
-%model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
-%masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.  
-%
-
-% SST patterns, the pattern effect.  Should my discussion paragraph of the pattern effect be 
-% the same paragraph/discussion as when I discuss Cess experiments?  
-As discussed in Z18b and Winton et al. 2019, despite a Cess sensitivity similar to AM2.1, 
-the TCR and ECS of CM4.0 are larger than those of CM2.1, and close to those of CM3.   This implies 
-that using the Cess sensitivity to infer the TCR or ECS is not reliable.  
-The Cess sensitivity for AM4.0 ($0.57 \, \rm{K\, W^{-1} m^2}$, Z18b, pg 26) is closer to the Cess sensitivity 
-% see page 39 of Zhao et al. 2018 part 1 for discussion of Cess sensitivity.  
-of AM2.1 ($0.54 \, \rm{K\, W^{-1} m^2}$) than to that of AM3.  This is partly due to the method of converting convective cloud condensate to precipitation in the convection scheme.   
-Z18b on the same page describes a Cess sensitivity with AM4.0 when the drop number
-is fixed of ($0.52 \, \rm{K\, W^{-1} m^2}$).   
-\textit{To what extent is this due to the differences in the SW CRE?  How similar is the interpretation that
-Andrews and company put forth with that of Paynter et al?}
-
-The previous section showed that the AM4.0 \textit{amip} simulations underestimates clouds relative to 
-the CALIPSO observations.   Simulations over the historical period with the fully coupled model only 
-slightly improve on this bias ( Figure \ref{fig:calipso_amip_historical}). 
-%and in the case of the abrupt 4xCO2 and gradual 1\% CO2 experiments the bias is worse at almost 
-%all latitudes except at 20 degrees south.  
-It is instructive to see how the cloud profiles from the different warming experiments compare to 
-the \textit{amip} and \textit{historical} experiments.   Figure \ref{fig:warming_exps} shows the basic 
-profiles of cloud fraction for \textit{amip}, \textit{amip-future4K}, \textit{amip-p4K}, \textit{abrupt-4xCO2}
- and \textit{1pctCO2} and Figure \ref{fig:warming_exps_bias} shows the biases computed relative to 
- the \textit{amip} experiment.  Relative to \textit{amip} all warming experiments produce an increase 
- of tropical and high-latitude upper-level clouds, and a decrease of mid-level clodus at nearly all latitudes.  
- The low-level cloud response is more complex among the warming experiments with the coupled 
- experiments showing a strong decrease in the northern mid-latitudes, an peaked increase around 
- 20S, and an increase in the region of the southern ocean.   The difference between the patterned warming
- experiment (\textit{amip-future4K}) and the uniform warming \textit{amip-p4K} is primarily in an 
- increase of southern hemisphere clouds where the \textit{amip-p4K} actually slightly decreases
- clouds at the same latitudes.  All warming experiments, as well as the \textit{historical} experiment, 
- increase cloud fraction poleward of 70N.  All three coupled experiments have more clouds in the sourthern 
- ocean relative to \textit{amip}.
-
-The two coupled warming experiments (\textit{abrupt 4xCO2} and \textit{1pctCO2}) have some interesting 
-differences from both the \textit{amip} and the \textit{historical} simulations.   
-These warming experiments have a distinct peak (about 5\%) of low-level cloud fraction 
- at about 20S that both \textit{amip} and \textit{historical} lack (\textit{historical} does have a small but less distinct peak).  
- Additionally, while the low-level clouds of the \textit{amip} and \textit{historical} experiments are almost identical between 
- 10-60N, the \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments show a large decrease of cloud fraction between 
- about 30-70N.  Is this decrease of low-level cloud in the NH responsible for a stronger SW cloud feedback relative to the 
- \textit{amip-p4K} and \textit{historical} experiments?  Of the two experiments, the \textit{abrupt-4xCO2} has the 
- least amount of low-level cloud.   Does it also then have the strongest/largest SW CRE?
-
- When comparing these experiments to the CERES-EBAF observations from the observational period the 
- \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments match the CERES-EBAF CRE better than the 
- \textit{amip} or historical experiments (this doesn't really seem to be the case...).  
- The cloud radiative effect (CRE) is computed for \textit{amip}, \textit{historical}, \textit{abrupt-4xCO2}, and 
- \textit{1pctCO2} and compared to the CRE latitude profile in Figure \ref{fig:CRE_feedback}.
- The AM4.0 simulations shown here compare best with the CERES-EBAF v2.8.  This is likely because v2.8 
- is the version of the data that was used as a reference during the model development.  For comparison we 
- also show the CERES-EBAF v4.1 data.  Although differences between the two versions are clear, the AM4.0 
- models compare relatively well (in the global mean) to both.  The differences between 
- the two observational version are mostly contained to the latitudes between +/- 30.  This excellent agreement with observations 
- of the CRE in the NH for the warming experiments was surprising, but does not in general indicate better observational 
- agreement of the warming experiments relative to the \textit{historical} and \textit{amip} experiments.   
- These warming experiments have a strong arctic and southern ocean response that differs significantly 
- from the historical observations and simulations.   As these are signature CRE changes in a warming 
- climate it is not surprising that they are not present in the historical data.
-
-%\begin{figure}
-%  \includegraphics[width=0.6\columnwidth]{cfmipfigs/meridional_CRE_CERES2p8.eps}
-%  \caption{The Cloud Radiative Effect}
-%  \label{fig:CRE_multiexperiments_ceres}
-%\end{figure}
-%
-%\begin{figure}
-%  \includegraphics[width=0.6\columnwidth]{cfmipfigs/cfmip_cre_amip.eps}
-%  \caption{The Cloud feedback estimated using cloud radiative effect}
-%  \label{fig:CRE_feedback}
-%\end{figure}
+%Figure \ref{fig:CF_warming}  is similar to Figure \ref{fig:calipso_amip_comparison} but focuses on
+%warming experiments.  
+%In addition to the two \textit{amip}-like warming experiments just discussed, Figure \ref{fig:CF_warming} 
+%plots the cloud fraction of two fully coupled warming experiments from the CMIP6 DECK 
+%(\textit{abrupt-4xCO2} and \textit{1pctCO2}). The cloud fields in these experiments are 
+%similar to each other, with the differences arising from either the different SST patterns or the 
+%different CO$_{2}$ concentrations.  
+%Overall there is an increase (relative to the historical period) in upper-level cloud fraction and a 
+%decrease in mid-level cloud fraction for the warming experiments.   The response across warming experiments
+%of the low-level clouds is more complicated.  Changes relative to the \textit{amip} cloud fraction are shown 
+%in the right panel of Figure \ref{fig:CF_warming} to help identify the differences.  Two separate cloud responses are apparent.  
+%%Overall, the coupled warming  experiments and the amip-based warming experiments represent two separate cloud fraction responses to warming.  
+%Distinctive features of the coupled warming experiments are a strong decrease of NH 
+%mid-latitude low-level clouds but increases of low-level cloud fraction in the southern hemisphere tropics and the Southern Ocean.  
+%Distinctive features of the amip-warming experiments are increases of 5-7\% 
+%upper-level cloud fraction poleward of $-70^\circ$ and large decreases of mid-level SH cloud fraction.  All warming
+%experiments show an increase of upper-level clouds over the polar regions.  All coupled models 
+%(including the historical)  have more clouds in the region between 60S and 80S relative to \textit{amip}.
+%The primary difference between \textit{amip-p4K} and \textit{amip-future4K} is that there is an increase 
+%throughout much of the SH in low-level clouds in the experiment with a patterned warming.  This is 
+%reflected in Table 1 where it is clear that the primary differences in radiative feedbacks between these
+%two experiments is in the SW CRE feedback.  
+%
+%Now that the different cloud fields among the suite of experiments are clear we can revisit the
+%radiative feedbacks from these experiments to see if there is any correspondence between the 
+%simulated cloud fields and and the cloud radiative effects.      ???? seems out of place?
+
+%%% Beta feedback??  relavent?
+%%Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
+%%changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
+%%low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
+%%model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
+%%masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.  
+%% 
+%
+%
+%% SST patterns, the pattern effect.  Should my discussion paragraph of the pattern effect be 
+%% the same paragraph/discussion as when I discuss Cess experiments?  
+%As discussed in Z18b and Winton et al. 2019, despite a Cess sensitivity similar to AM2.1, 
+%the TCR and ECS of CM4.0 are larger than those of CM2.1, and close to those of CM3.   This implies 
+%that using the Cess sensitivity to infer the TCR or ECS is not reliable.  
+%The Cess sensitivity for AM4.0 ($0.57 \, \rm{K\, W^{-1} m^2}$, Z18b, pg 26) is closer to the Cess sensitivity 
+%% see page 39 of Zhao et al. 2018 part 1 for discussion of Cess sensitivity.  
+%of AM2.1 ($0.54 \, \rm{K\, W^{-1} m^2}$) than to that of AM3.  This is partly due to the method of converting convective cloud condensate to precipitation in the convection scheme.   
+%Z18b on the same page describes a Cess sensitivity with AM4.0 when the drop number
+%is fixed of ($0.52 \, \rm{K\, W^{-1} m^2}$).   
+%\textit{To what extent is this due to the differences in the SW CRE?  How similar is the interpretation that
+%Andrews and company put forth with that of Paynter et al?}
+%
+%The previous section showed that the AM4.0 \textit{amip} simulations underestimates clouds relative to 
+%the CALIPSO observations.   Simulations over the historical period with the fully coupled model only 
+%slightly improve on this bias ( Figure \ref{fig:calipso_amip_historical}). 
+%%and in the case of the abrupt 4xCO2 and gradual 1\% CO2 experiments the bias is worse at almost 
+%%all latitudes except at 20 degrees south.  
+%It is instructive to see how the cloud profiles from the different warming experiments compare to 
+%the \textit{amip} and \textit{historical} experiments.   Figure \ref{fig:warming_exps} shows the basic 
+%profiles of cloud fraction for \textit{amip}, \textit{amip-future4K}, \textit{amip-p4K}, \textit{abrupt-4xCO2}
+% and \textit{1pctCO2} and Figure \ref{fig:warming_exps_bias} shows the biases computed relative to 
+% the \textit{amip} experiment.  Relative to \textit{amip} all warming experiments produce an increase 
+% of tropical and high-latitude upper-level clouds, and a decrease of mid-level clodus at nearly all latitudes.  
+% The low-level cloud response is more complex among the warming experiments with the coupled 
+% experiments showing a strong decrease in the northern mid-latitudes, an peaked increase around 
+% 20S, and an increase in the region of the southern ocean.   The difference between the patterned warming
+% experiment (\textit{amip-future4K}) and the uniform warming \textit{amip-p4K} is primarily in an 
+% increase of southern hemisphere clouds where the \textit{amip-p4K} actually slightly decreases
+% clouds at the same latitudes.  All warming experiments, as well as the \textit{historical} experiment, 
+% increase cloud fraction poleward of 70N.  All three coupled experiments have more clouds in the sourthern 
+% ocean relative to \textit{amip}.
+
+%The two coupled warming experiments (\textit{abrupt 4xCO2} and \textit{1pctCO2}) have some interesting 
+%differences from both the \textit{amip} and the \textit{historical} simulations.   
+%These warming experiments have a distinct peak (about 5\%) of low-level cloud fraction 
+% at about 20S that both \textit{amip} and \textit{historical} lack (\textit{historical} does have a small but less distinct peak).  
+% Additionally, while the low-level clouds of the \textit{amip} and \textit{historical} experiments are almost identical between 
+% 10-60N, the \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments show a large decrease of cloud fraction between 
+% about 30-70N.  Is this decrease of low-level cloud in the NH responsible for a stronger SW cloud feedback relative to the 
+% \textit{amip-p4K} and \textit{historical} experiments?  Of the two experiments, the \textit{abrupt-4xCO2} has the 
+% least amount of low-level cloud.   Does it also then have the strongest/largest SW CRE?  
+% 
+% When comparing these experiments to the CERES-EBAF observations from the observational period the 
+% \textit{abrupt 4xCO2} and \textit{1pctCO2} experiments match the CERES-EBAF CRE better than the 
+% \textit{amip} or historical experiments (this doesn't really seem to be the case...).  
+% The cloud radiative effect (CRE) is computed for \textit{amip}, \textit{historical}, \textit{abrupt-4xCO2}, and 
+% \textit{1pctCO2} and compared to the CRE latitude profile in Figure \ref{fig:CRE_feedback}.
+% The AM4.0 simulations shown here compare best with the CERES-EBAF v2.8.  This is likely because v2.8 
+% is the version of the data that was used as a reference during the model development.  For comparison we 
+% also show the CERES-EBAF v4.1 data.  Although differences between the two versions are clear, the AM4.0 
+% models compare relatively well (in the global mean) to both.  The differences between 
+% the two observational version are mostly contained to the latitudes between +/- 30.  This excellent agreement with observations 
+% of the CRE in the NH for the warming experiments was surprising, but does not in general indicate better observational 
+% agreement of the warming experiments relative to the \textit{historical} and \textit{amip} experiments.   
+% These warming experiments have a strong arctic and southern ocean response that differs significantly 
+% from the historical observations and simulations.   As these are signature CRE changes in a warming 
+% climate it is not surprising that they are not present in the historical data.
 
@@
 Why do we do a poor job with these clouds in models? }
+
+Probably have to cite Armour, 2017.
+He does put the time varying sensitivity in context, and discusses the use of the energy budget constraints.
+But then I also need to determine how to contextualize the information published by Armour, Andrews, and Lewis.
+What are the takeaways?
+
+\textit{We should probably mention that we have used the CALIPSO simulator to predict cloud changes in the future...}
+
+\textit{Numerous studies have documented the range of sensitivities among an ensemble of models from different
+generations of CMIP and from a wide range of modeling centers (e.g.
+Cess et al.
+1989, Andrews et al., 2012, Rinter et al., 2014, Zelinka et al., 2020).
+In contrast, this study focuses on several models from a single modeling center, all based on the same generation of code.
+By so doing we can more clearly attach the source of spread in the climate sensitivity to differences in the geophysical configuration and to the responses of the clouds to different boundary conditions...
+with less ambiguity.}
 
@@
 https://esgdata.gfdl.noaa.gov/search/cmip6-gfdl.
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.9\columnwidth]{/Users/silvers/code/latex_git/cfmipfigs/Silvers_cfmip_MISRprof_SinglePanel.pdf}
+  \caption{Mean total cloud fraction as a function of height for different geographic regions.
+The observations (solid lines) are from the MISR satellite (2000-2019) and the modeled clouds (dashed lines)
+  were derived with the MISR simulator (amip experiment).}
+  \label{fig:cf_misr_lowcl}
+\end{figure}
+
+\begin{figure}
+  \centering
+  \includegraphics[width=0.9\columnwidth]{/Users/silvers/code/latex_git/cfmipfigs/Silvers_cfmip_MISR_cfVtau_SinglePanel.pdf}
+  \caption{Mean total cloud fraction as a function of cloud optical depth for different geographic regions.
+The observations (solid lines) are from the MISR satellite (2000-2019) and the modeled clouds (dashed lines)
+  were derived with the MISR simulator (amip experiment).}
+  \label{fig:cf_misr_lowcl}
+\end{figure}
 

### 2020-08-26 Silvers_cfmip.tex
relatively minor textual edits to Silvers_cfmip.tex

@@
 The comparisons with observations are made mostly with the \textit{amip} experiment.   The experiments used 
-in this paper are all part of the GFDL contribution to CMIP6.  We use the \textit{historical, abrupt-4xCO2, and 1pctCO2}
+in this paper are all part of the GFDL contribution to CMIP6 and as a result, the \textit{amip} and \textit{historical}
+experiments end in the year 2014.  We use the \textit{historical, abrupt-4xCO2, and 1pctCO2}
 experiments from the CMIP6 DECK.  In addition we utilize several experiments from the CFMIP contributions 
 to CMIP6.  These experiments include \textit{amip, amip-p4K, amip-m4K, amip-future4K, aqua-control} and \textit{aqua-p4K}.  
+In order to utilize as much of the available data as possible much of the analysis of the \textit{amip} experiment uses the 
+full span of years (1979-2014) despite the fact that the satellite observations do not extend as far back in time.  However, 
+some of the analysis for the \textit{amip} and \textit{historical} experiments, in particular for the calculation of a climate feedback parameter over recent years, a shorter period (1996-2014) is used in order to eliminate complications due to radiative forcing in the early 1990's due to volcanic activity.
+The relevant time period is stated in the captions of the figures and tables.
 
@@
 
+The comparisons of cloud fraction in Figures 1-4 between observations and the \textit{amip} experiment show a 
+prevailing negative cloud fraction bias across much of the globe for low-, middle-, and upper-level clouds.  Does 
+coupling the AM4.0 atmosphere to a dynamic ocean decrease the cloud bias?   
 \textit{This paragraph should serve as a bridge between the COSP observations, amip and historical experiments, TOA fluxes, and feedbacks.
@@
 
-The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate sensitivities (possibly cite Held et al., Winton et al., Dunne et al.).  
+The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate 
+sensitivities (possibly cite Winton et al., Dunne et al.) depending on the experiment of interest and the method used for 
+calculation.
 One way of quantifying this sensitivity is with the climate feedback parameter, which, for the subset of GFDL models and CMIP6 experiments studied in this paper, varies between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).
@@
 the various warming experiments?
+
+\textit{Put the results of AM4.0/CM4.0 in the context of other modeling studies.  The AR5, chapter 7 describes the primary 
+cloud feedbacks that are thought to be relevant for future warming.
+Are AM4.0/CM4.0 consistent with the expectations from the AR5?
+Can we say something about the large cloud fraction in the arctic?
+Tie into Kay et al.
+2011 and Vavrus et al.
+(2009 or 2011)}
 

### 2020-08-26 Silvers_WalkerCell_response2reviewers.tex
added Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex during the revision stage for my Walker Circulation paper

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% AGUJournalTemplate.tex: this template file is for articles formatted with LaTeX
%
% This file includes commands and instructions
% given in the order necessary to produce a final output that will
% satisfy AGU requirements, including customized APA reference formatting.
%
% You may copy this file and give it your
% article name, and enter your text.
%
%
% Step 1: Set the \documentclass
%
%

%% To submit your paper:
\documentclass[draft]{agujournal2019}
\usepackage{url} %this package should fix any errors with URLs in refs.
\usepackage{lineno}
\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
\usepackage{soul}
\linenumbers
%%%%%%%
% As of 2018 we recommend use of the TrackChanges package to mark revisions.
% The trackchanges package adds five new LaTeX commands:
%
%  \note[editor]{The note}
%  \annote[editor]{Text to annotate}{The note}
%  \add[editor]{Text to add}
%  \remove[editor]{Text to remove}
%  \change[editor]{Text to remove}{Text to add}
%
% complete documentation is here: http://trackchanges.sourceforge.net/
%%%%%%%

\draftfalse

%% Enter journal name below.
%% Choose from this list of Journals:
%
% JGR: Atmospheres
% JGR: Biogeosciences
% JGR: Earth Surface
% JGR: Oceans
% JGR: Planets
% JGR: Solid Earth
% JGR: Space Physics
% Global Biogeochemical Cycles
% Geophysical Research Letters
% Paleoceanography and Paleoclimatology
% Radio Science
% Reviews of Geophysics
% Tectonics
% Space Weather
% Water Resources Research
% Geochemistry, Geophysics, Geosystems
% Journal of Advances in Modeling Earth Systems (JAMES)
% Earth's Future
% Earth and Space Science
% Geohealth
%
% ie, \journalname{Water Resources Research}

\journalname{JAMES}

\begin{document}

%% ------------------------------------------------------------------------ %%
%  Title
%
% (A title should be specific, informative, and brief. Use
% abbreviations only if they are defined in the abstract. Titles that
% start with general keywords then specific terms are optimized in
% searches)
%
%% ------------------------------------------------------------------------ %%

% Example: \title{This is a test title}

\title{Response to Reviewers for: `Clouds and Radiation in a mock-Walker Circulation'}

%% ------------------------------------------------------------------------ %%
%
%  AUTHORS AND AFFILIATIONS
%
%% ------------------------------------------------------------------------ %%

\authors{Levi G. Silvers\affil{1,*}, and Thomas Robinson\affil{2}}

\affiliation{1}{Princeton University/GFDL, Princeton, New Jersey, USA}
\affiliation{2}{NOAA/GFDL, SAIC, Science Applications International Corporation, Reston, VA, USA}
\affiliation{*}{Current Affiliation: School of Marine and Atmospheric Sciences, Stony Brook University, Stony Brook, NY, USA}

\correspondingauthor{Levi Silvers}{levi.silvers@stonybrook.edu}

% (include name and email addresses of the corresponding author.  More
% than one corresponding author is allowed in this LaTeX file and for
% publication; but only one corresponding author is allowed in our
% editorial system.)

% Example: \correspondingauthor{First and Last Name}{email@address.edu}

%% ------------------------------------------------------------------------ %%

\section{Note from LGS and TR}

\textcolor{blue}{All responses and comments by Levi Silvers will be in blue.  Below please find my responses to your particular considerations.  Reviewer \#1 made additional comments in a pdf that was included with the review.  I have responded to those comments within that pdf.  Reviewer \#3 made 15 minor comments in the annotated pdf provided by \textit{JAMES}.  I have responded with my own annotations. }

\section{Reviewer \# 1 Evaluations}

Recommendation: Return to author for minor revisions

Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and 
clarification.

Supported: Yes

Referencing: Yes

Quality: The organization of the manuscript and presentation of the data and results need some improvement.

Data: No

Accurate Key Points: Yes

This paper presents a number of interesting results on the interactions between longwave cloud
radiative effects and the Walker circulation using GCM-like and CRM-like simulations. This
approach provides an important link between more idealized, smaller-scale simulations of the
tropical atmosphere where convection is resolved (i.e. RCE with a CRM) with less-idealized,
larger-scale simulations of the tropical atmosphere where convection is not resolved (i.e.
prescribed SST gradients with a GCM). As such, this work is critical for improving our
understanding of the observed tropical atmosphere.

The central finding is that the CRM-like simulations produce substantially less low clouds than
the GCM-like simulations, and this leads to important differences in the atmospheric response to
longwave cloud radiative effects (LWCRE). In particular, LWCRE act to increase precipitation
in the GCM-like experiments, and act to decrease the precipitation in the CRM-like experiments.
The results have important implications for our understanding of the interactions of clouds and
the tropical circulation in nature as well as in more sophisticated global climate simulations.

In my view the main weakness of the paper is lack of clarity in a few areas. The paper could
benefit from emphasizing the main points, as well as clarification of some of the science ideas.
The figures generally illustrate the main points nicely, but I have included a few notes for
improvements, as well as suggestions for additional plots (particularly a plot of the longwave
heating rate as a function of distance). See attached document for comments*, which have been
highlighted throughout the paper. The suggestions are generally minor, but I think the clarity of
the paper could be improved substantially with these changes.

I have responded to your annotations in the pdf file: 
Silvers\_WalkerCell\_reviewer1\_1592417419\_response.pdf

\section{Reviewer \# 2 Evaluations}

Recommendation: Return to author for major revisions

Significant: The paper has some unclear or incomplete reasoning but will likely be a significant contribution with revision and clarification.

Supported: Yes

Referencing: Yes

Quality: The organization of the manuscript and presentation of the data and results need some improvement.

Data: Yes

Accurate Key Points: Yes

This manuscript examines a simulated Walker circulation-like setup, making use of a flexible model that can be configured into GCM-like and CRM-like states. By focusing primarily on the equilibrium state attained in each simulation, the coupling of clouds, radiation, and circulation is studied. These each change substantially as domain size, resolution, use of a convective parameterization, and interactions between clouds and longwave radiation are altered separately. Results also have potential implications toward studying the complex cloud radiative feedbacks that affect our future climate projections.

The manuscript offers a thorough analysis of this intricate coupling, and will undoubtedly be a significant contribution to the literature. As you will see below, the bulk of my comments relate to the organization of the manuscript, which I believe should be revisited and can be improved to present these meaningful results in a more cohesive and concise manner. In addition, I believe more attention should be given to the comparison between the two 25 km-resolution simulations: those with parameterized convection and explicit convection, respectively. While these suggested organizational edits may be more of a significant undertaking, I ultimately believe this set of revisions to be more minor, and look forward to reading the finished product!

Below, I have organized my comments into a set of general, overarching points first, followed by a handful of individual, line-by-line comments.

\subsection{GENERAL COMMENTS}
*In terms of organization, I believe some reworking and consolidation of results are useful and fairly straightforward. Some examples include:

\begin{enumerate}
  \item Section 3 is meant to focus on the impact of LWCRE, but subsequent sections frequently reference the comparison between LWCRE-on and LWCRE-off as well (i.e. lines 361-373, 398-401, 459-462).
  \item Comparisons between E25 and P25 are made in multiple sections, and some of these results are referenced in passing (i.e. lines 518-519, "It is also worth noting that in contrast to the P25 case which has strong domain shear..."). Given the importance of this resolution in the manuscript to link GCMs and CRMs, I believe that this deserves its own section.
  \item Figure 10, in the context of its section on resolution dependence, seems to convey a similar picture as Figure 9, and its already been well-established that removing LWCRE seems to broaden/weaken the mass circulation robustly.

  \textcolor{blue}{You are right that there is some redundancy of message in Figure 10, but I think there is enough interest in the results of the 1 and 2km simulations to warrant inclusion of Figure 10. }

  \item I believe that Sections 6 and 7 can be consolidated and combined into one, given that the first half of Section 6 is already a well-constructed and well-divided summary of results.
  \item In several parts of the manuscript, multiple references are made to Figures/Tables that appear 10 or more pages earlier. For ease of reading, perhaps quantities such as the domain-mean precipitation can be incorporated into the Figures. For example, Figure 2's legend can list the domain-mean precipitation values next to the labels.
\end{enumerate}

\begin{itemize}
  \item Given the overarching goal of linking CRMs with GCMs, it is understandable that a 25 km resolution is chosen for the sensitivity experiment of using parameterized vs. explicit convection, instead of a finer spacing. I would also be interested to see this comparison at resolutions representative of operational NWP models, roughly 10 km or so. There are several key differences noted in the manuscript between P25 and E25, so performing a similar comparison would be useful to assess the robustness of the results, while also providing potential relevance for regional climate modeling efforts. This is more out of my own curiosity, rather than something I request be done within the scope of this manuscript.

  \textcolor{blue}{This is a good point, and I think that we have similar interests in some of what the paper has not covered.  As you could probably see in the paper, organizing the results was challenging, and interpretation was made difficult by many unexpected complications.  Based on the number of experiments which I was already trying to organize in the writing of the manuscript I chose to keep the focus of the paper rather small.   Another factor which limited the number of experiments that I could include in the paper is that I also performed a number of uninteresting or unsuccessful experiments in which various parameter settings were modified, and in which some minor changes were made in the code of the Tiedtke large scale cloud scheme.  I was already dealing with too many experiments. }

  \item Have any additional simulations been conducted at resolutions between 2-25, and 25-100 km? It would be interesting to see how smooth the transition is between these two regimes of cloud distribution and radiative response, and if a specific threshold could be found, holding all other conditions equal, to significantly affect the cloud distribution.

  \textcolor{blue}{No, I have not performed experiments at other resolutions (a few at 5km, at the very beginning with different code base, but the analysis was not carried very far).  Also see answer to you comment just before this one. }

  \item Some figures are a bit difficult to read, in particular Figures 6 and 13. In particular, for Figure 6 it is difficult to compare the P25 and P25L simulations because the colors on the lines are the same. Figure 13 would be best oriented as a 2X2 window similar to Figure 12, especially given the subtle differences in the rightmost panel.

  \item For each of the figures, especially those later in the manuscript, it would be helpful to make the font size on the axes a bit larger.

  \item Line 63-64, 78, 81, 132-133: These are a few examples within the introduction, but in several spots throughout the manuscript, content could be made more concise by omitting "the".

  \textcolor{blue}{Duly noted and changed.}

  \item Line 180-183: "...The kilometer of atmosphere just above the surface is resolved by 8 model levels." Can you provide a couple of additional details on the vertical grid spacing? Is it a stretched grid with roughly evenly-spaced pressure intervals? Since you point out in line 219-220 that this is coarser than traditional CRMs, these details would be useful to assess the model's upper-tropospheric resolution.

  \textcolor{blue}{Table S1 of the supplementary material that was published as part of Zhao et al., 2018, part 1 lists the model interface levels in pressure and height.  The interface pressure is computing using $p=p_k+(b_k)(p_s)$ with the coefficients also given in Table S1.}

  \item Line 217-220, 276, 302, 485-494: While initially denoting the simulations as "CRM-like" and "GCM-like", there are some inconsistencies later in the manuscript where these are referred to as just "GCMs and CRMs". I would suggest sticking with the latter naming scheme for simplicity, making sure to state the caveats in Section 2 as you already did for the CRM-like cases.

  \textcolor{blue}{I have gone back and forth about what terminology to use.  I hesitate to call a doubly periodic simulation a GCM but you can see the difficulties that arise with the terminology that appends ‘-like’ to the GCMs and CRMs.  For now I have added ‘-like’ in the places that you noticed inconsistencies. }

  \item Line 321-323: "...but also due to an interaction between the convective parameterization and the LWCRE." If this is known, can you elaborate on it? I take this to be the cause of the domain-mean shear alluded to in lines 315-316, and believe this explanation would strengthen the comparison.

  \textcolor{blue}{In contrast to the P25 (lwcre-on) simulation (Figure 1, left; Figure 4d), the initial several months of both P25 
  (lwcre-off; Figure 5d) and E25 (lwcre-on; Figure 8b) show a precipitation maximum that is centered closely on the SST 
  maximum in the middle of the domain.  The steady state solutions from the equilibrated period of these simulations (Figure 1) are 
  also both more symmetric about the center of the domain.  This implies that the source of asymmetry could be either the lwcre, 
  or the parameterized convection.  However, both P25(lwcre-off) and E25(lwcre-on) eventually transition to a much more irregular evolution of precipitation (see Figure 5d after 600 days) in which the precipitation maximum can reside well off of the 
  precipitation maximum for several months at a time.  However, both of these simulations have a more symmetric time-averaged distribution than the P25 case.  I then made the inference that it is the interaction between the two that leads to an asymmetric distribution of the steady state. }

\textcolor{blue}{
This has been concluded mostly because the simulation is markedly more symmetrical when the LWCRE is off but the convection parameterization is still on, and the equilibrium state is more symmetrical when the LWCRE is on but the convection parameterization is off (Figure 1).  The time evolution of precipitation for the LWCRE-off, Conv-off (E25 lwcre off) also shows regular oscillations (large) about the SST maximum in a way that is distinct from either P25 lwcre-off or E25 lwcre-on.  Another piece of this (I was a bit hesitant to include too many Hovmoller plots, fearing Hovmoller fatigue.)  }

  \item Line 326-343: The focus in Table 2 is on the equilibrium state. Is a time evolution of subsidence fraction available? I'd be curious to see how SF changes from the early stages of the simulation, i.e. if it's becoming more or less aggregated over time. The somewhat inconsistent comparison between LWCRE-on and LWCRE-off experiments here is noteworthy, given that LWCRE is arguably the most important mechanism for maintenance of the aggregated state in non-rotating RCE studies.

  \item Line 374-378: "An additional unexpected change that results from increasing the domain size is an upward shift of the cloud fields..." This is an interesting result! Do you have any speculation as to why this happened?

  \item Line 588-589: Is the decrease in surface enthalpy flux from turning on LWCRE mainly due to latent, or sensible heat flux?

  \textcolor{blue}{It is due mostly to the changes in the latent heat flux (~5-10 W/m2) rather than the sensible heat flux (~1 W/m2).}

  \item Line 676-678: This can be a significant result that warrants future research. Has there been any other work into the sensitivity of the large-scale cloud scheme in GCMs besides Held et al. (2007)? If so, this would be useful to cite and elaborate on, either in this section or back in Section 4.

  \textcolor{blue}{I am not aware of other research that has looked into this.  This was one of the points that I found the moist interesting to come out of the analysis.  I am continuously surprised at how infrequently the large-scale vs. convective precipitation is talked about in studies that use GCMs.  I hope that future research does look into this further, whether my own or someone else’s.}

  \item Figure 13 caption: How are the subsidence regions defined? Specifically, is any sort of areal averaging conducted and does this vary between simulations of different domain size/resolution? Apologies if this is something that has already been addressed elsewhere in the manuscript.   
\end{itemize}

\section{Reviewer \# 3 Evaluations}

Recommendation: Return to author for minor revisions

Significant: Yes, the paper is a significant contribution and worthy of prompt publication.

Supported: Yes

Referencing: Yes

Quality: The organization of the manuscript and presentation of the data and results need some improvement.

Data: Yes

Accurate Key Points: Yes

The present manuscript investigates the effect of longwave cloud radiative effect and spatial resolution on the mock-
Walker circulation in a model that can consistently switch between explicit and parametrized convection. More specifically,
the authors design a series of seven experiments using the Geophysical Fluid Dynamics Laboratory (GFDL) general circu-
lation model (GCM) AM 4.0. with prescribed surface temperature and different domain sizes, grid spacing, active/inactive
longwave cloud radiative effect (LWCRE), and explicit/parametrized convection (Section 2). They find that LWCRE orga-
nizes the Walker cell’s mean precipitation and circulation (Section 3), and increases large-scale precipitation while domain
size leads to a more modest increase in precipitation as the condensate peak shifts from high-level clouds to low-level clouds
(Section 4). In contrast, explicit convection tends to lead to more high-level clouds and more convective aggregation, i.e.
stronger circulation, thermodynamic spatial gradients, smaller precipitation mean but larger precipitation variance, and
lower surface enthalpy fluxes, a lot of it forced by LWCRE (Section 5). The findings are then thoroughly summarized in
the discussion (Section 6) and conclusion (Section 7) sections.

This series of mock-Walker cell simulation is new, the manuscript is well-written, the results are consistent with past
literature, and the topic is of interest to the climate community as it fits well within the “climate model hierarchy” [3, 1],
all of which warrant eventual publication in the Journal of Advances in Modeling Earth Systems. I list a few comments
below and would be happy to help with another round of minor revisions if necessary.

\subsection{Major comments}
\subsubsection{Why limit the investigation of cloud radiative effect to LWCRE?}
While the climate dynamics and self-aggregation literature consistently find that the LWCRE is the most important
radiative forcing when it comes to convective aggregation (e.g. [6, 4, 2]), the consensus is less clear when it comes to
shortwave cloud radiative effect (SWCRE). Given the clean simulation setup and the insight obtained from the LWCRE-off
simulations, \textbf{would it be possible to repeat the experiments with SWCRE and/or the full cloud radiative
effect (CRE) turned off?}

I would recommend to:

\begin{itemize}
  \item Rerun at least one simulation with SWCRE-off or the full CRE-off, or
  \item Thoroughly justify why the authors decided to focus on LWCRE only rather than the full CRE. The paragraph
currently introducing the LWCRE-off experiments (L202) does not justify why the experiment is done in the first
place, even if the manuscript’s results confirm the importance of this experiment a posteriori.
\end{itemize}

\subsubsection{Descriptive nature of the manuscript}

I appreciated the explicit questions from line 80 to 84, which respectively correspond to Sections 3, 4, and 5:

\begin{itemize}
  \item How do clouds influence the overturning circulation?
  \item To what extent are the deep convective clouds and the low-level clouds coupled through the overturning circulation?
  \item When simulating tropical overturning circulations, how well does a GCM compare to a cloud-resolving model (CRM)?
\end{itemize}

However, I found the manuscript to be overly descriptive at times, possibly restricting the insight readers could get from
the AM4.0 Walker setup. For each of the three questions, it could be helpful to use the simulation data to offer a simple
rationale if not a quantitative explanation for why the authors find the results summarized in Section 6.

\begin{enumerate}
  \item (Section 3)
    \begin{itemize}
      \item Is it possible to simply relate the difference in circulation/vertical velocity to the difference in CRE (e.g. using the
two box model for a given value of evaporation minus precipitation)?
      \item How does CRE compare to circulation strength throughout each simulation once the simulation has equilibrium
(this would give more data points than a single mean circulation/mean CRE comparison per simulation)?
    \end{itemize}
  \item (Section 4, Lines 407-409)
    \begin{itemize}
      \item Could the authors show correlations or scatter plots across simulations and across time within a given simulation
to back up their claim about the link between low-level cloud fraction, LWCRE, and convective versus large-scale
fraction of total precipitation?
      \item The causality claim also seems a bit bold given that LWCRE is the only effect that the authors turned on/off; it could
be for instance that surface latent heat fluxes plays as big of a role, which could be tested by turning the dependence
of latent heat fluxes on surface wind speed on/off, or by making the surface latent heat fluxes horizontally uniform
at each timestep. If the authors decide not to run additional experiments, I recommend nuancing that statement
given that Figure 7 shows that LWCRE is only responsible for part of this partitioning, and given that Figure 6 is
so hard to read (which could be easily improve by making the P25 and P25L different colors, etc.).
    \end{itemize}
  \item (Section 5)
    \begin{itemize}
      \item The logical flow of the CRM/GCM comparison is relatively easy to follow, but I was wondering if the authors
could expand on their baseline result that the CRM configuration leads to more upper-level clouds while the GCM
configuration leads to more lower-level clouds. Would it be possible to compare the vertically-resolved water species
budget across simulations to understand this difference?
      \item It is reassuring that this result is consistent with [5]; would it be possible to similarly trace back this difference to a
discrepancy in shallow cloud mixing, e.g. by comparing the vertical transport of water vapor between the boundary
layer and the lower troposphere across experiments?
    \end{itemize}
\end{enumerate}

\subsubsection{Assessing the realism of the simulated mock-Walker cell}

As the authors point out (L67), the Walker cell setup can be compared to observations from the Pacific region. As their
results show large differences between the E25/P25 and the E2/E1 simulations (e.g. L420-421), how can the reader
assess which simulation best captures the Walker cell’s hydrological cycle?
Although a direct comparison is impossible because of the idealized mock-Walker cell setup, I would highly suggest
adding observational and/or meteorological reanalysis data to at least some of Section 5’s figures (Figure 8-13) to comment
on which configuration leads to the most observationally consistent Walker cell. To facilitate the comparison, the authors
could e.g. choose a period of time where the Pacific’s zonal surface temperature gradient is in the range of the experiments
listed in Table 1 $(\Delta SST/ \Delta x = 10^{-4} - 10^{-3} K/km).  $

\subsection{Minor comments}

You will find 15 minor comments attached to the annotated PDF of the manuscript. Additional comments that apply
throughout the paper are listed below:
\begin{itemize}
  \item Labeling all figure panels using the conventional notation a/b/c/d (e.g. Figure 1, 2, etc.)
  \item Make titles more formal (e.g. Figure 13) and using a consistently large font size across figures (for instance, the
titles are easy to read in Figures 9 and 10, but not in Figures 11, 12, and 13)

  \textcolor{blue}{The font size for axis and titles in Figure 12 has been increased, x-axis label for Figure 12d corrected to read only units.}
\end{itemize}

%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%  ACKNOWLEDGMENTS
%

%\acknowledgments
%Enter acknowledgments, including your data availability statement, here.

%% ------------------------------------------------------------------------ %%
%% References and Citations

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% \bibliography{<name of your .bib file>} don't specify the file extension
%
% don't specify bibliographystyle
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliography{ enter your bibtex bibliography filename here }

%Reference citation instructions and examples:
%
% Please use ONLY \cite and \citeA for reference citations.
% \cite for parenthetical references
% ...as shown in recent studies (Simpson et al., 2019)
% \citeA for in-text citations
% ...Simpson et al. (2019) have shown...
%
%
%...as shown by \citeA{jskilby}.
%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
%...has been shown \cite{jskilbye}.
%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
%...has been shown by \cite <e.g.,>[and others]{lewin76}.
%
% apacite uses < > for prenotes and [ ] for postnotes
% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
%

\end{document}

More Information and Advice:

%% ------------------------------------------------------------------------ %%
%
%  SECTION HEADS
%
%% ------------------------------------------------------------------------ %%

% Capitalize the first letter of each word (except for
% prepositions, conjunctions, and articles that are
% three or fewer letters).

% AGU follows standard outline style; therefore, there cannot be a section 1 without
% a section 2, or a section 2.3.1 without a section 2.3.2.
% Please make sure your section numbers are balanced.
% ---------------
% Level 1 head
%
% Use the \section{} command to identify level 1 heads;
% type the appropriate head wording between the curly
% brackets, as shown below.
%
%An example:
%\section{Level 1 Head: Introduction}
%
% ---------------
% Level 2 head
%
% Use the \subsection{} command to identify level 2 heads.
%An example:
%\subsection{Level 2 Head}
%
% ---------------
% Level 3 head
%
% Use the \subsubsection{} command to identify level 3 heads
%An example:
%\subsubsection{Level 3 Head}
%
%---------------
% Level 4 head
%
% Use the \subsubsubsection{} command to identify level 3 heads
% An example:
%\subsubsubsection{Level 4 Head} An example.
%
%% ------------------------------------------------------------------------ %%
%
%  IN-TEXT LISTS
%
%% ------------------------------------------------------------------------ %%
%
% Do not use bulleted lists; enumerated lists are okay.
% \begin{enumerate}
% \item
% \item
% \item
% \end{enumerate}
%
%% ------------------------------------------------------------------------ %%
%
%  EQUATIONS
%
%% ------------------------------------------------------------------------ %%

% Single-line equations are centered.
% Equation arrays will appear left-aligned.

Math coded inside display math mode \[ ...\]
 will not be numbered, e.g.,:
 \[ x^2=y^2 + z^2\]

 Math coded inside \begin{equation} and \end{equation} will
 be automatically numbered, e.g.,:
 \begin{equation}
 x^2=y^2 + z^2
 \end{equation}

% To create multiline equations, use the
% \begin{eqnarray} and \end{eqnarray} environment
% as demonstrated below.
\begin{eqnarray}
  x_{1} & = & (x - x_{0}) \cos \Theta \nonumber \\
        && + (y - y_{0}) \sin \Theta  \nonumber \\
  y_{1} & = & -(x - x_{0}) \sin \Theta \nonumber \\
        && + (y - y_{0}) \cos \Theta.
\end{eqnarray}

%If you don't want an equation number, use the star form:
%\begin{eqnarray*}...\end{eqnarray*}

% Break each line at a sign of operation
% (+, -, etc.) if possible, with the sign of operation
% on the new line.

% Indent second and subsequent lines to align with
% the first character following the equal sign on the
% first line.

% Use an \hspace{} command to insert horizontal space
% into your equation if necessary. Place an appropriate
% unit of measure between the curly braces, e.g.
% \hspace{1in}; you may have to experiment to achieve
% the correct amount of space.

%% ------------------------------------------------------------------------ %%
%
%  EQUATION NUMBERING: COUNTER
%
%% ------------------------------------------------------------------------ %%

% You may change equation numbering by resetting
% the equation counter or by explicitly numbering
% an equation.

% To explicitly number an equation, type \eqnum{}
% (with the desired number between the brackets)
% after the \begin{equation} or \begin{eqnarray}
% command.  The \eqnum{} command will affect only
% the equation it appears with; LaTeX will number
% any equations appearing later in the manuscript
% according to the equation counter.
%

% If you have a multiline equation that needs only
% one equation number, use a \nonumber command in
% front of the double backslashes (\\) as shown in
% the multiline equation above.

% If you are using line numbers, remember to surround
% equations with \begin{linenomath*}...\end{linenomath*}

%  To add line numbers to lines in equations:
%  \begin{linenomath*}
%  \begin{equation}
%  \end{equation}
%  \end{linenomath*}

### 2020-08-26 Silvers_WalkerCell_revision.tex
added Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex during the revision stage for my Walker Circulation paper

--- 2020-06-04 Silvers_WalkerCell_clean.tex
@@
 \usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+%\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
 \usepackage{soul}
 \linenumbers
+
+\addeditor{LGS}
 
@@
   \item{Cloud resolving simulations result in more upper-level clouds, relative to lower resolution simulations which have more low-level clouds.}
-  \item{High and low clouds interact differently with longwave radiation to increase or decrease precipitation, depending on dominant cloud type.}
+  \item{High and low clouds interact differently with longwave radiation to increase or decrease precipitation, depending on \add[LGS]{the} dominant cloud type.}
   \item{Interactions between clouds and radiation combined with parameterized convection shift the precipitation maximum away from the SST maximum.}
@@
 These overturning circulations encompass dynamical motions at scales
-ranging from meters to thousands of km's all of which interact with each of the different cloud types.
+ranging from meters to thousands of \change[LGS]{km's}{kilometers} all of which interact with each of the different cloud types.
 The circulation first noted by Sir Gilbert Walker, and described by \citeA{Bjerknes1969} connects the 
@@
 be populated more by shallow cumulus and, in the subtropics, stratocumulus clouds.  
-This circulation, now known as the Walker Circulation, is a response to the 
-longitudinal asymmetries in the tropical atmospheric heating and is tightly coupled with 
+This circulation, now known as the Walker Circulation, is a response to \remove[LGS]{the} 
+longitudinal asymmetries in \remove[LGS]{the} tropical atmospheric heating and is tightly coupled with 
 the El Nino Southern Oscillation.    
@@
 It is also clear that the tropical Pacific plays an important role in the response of the climate to radiative perturbations. 
-Recent work has shown that the interactions between clouds, patterns of Sea Surface Temperature (SST), and the circulation 
+Recent work has shown that the interactions between clouds, patterns of \change[LGS]{S}{s}ea \change[LGS]{S}{s}urface \change[LGS]{T}{t}emperature (SST), and the circulation 
 in the tropical Pacific play an important role in determining the cloud feedback and the decadal 
@@
 We propose that focusing on the Walker Circulation can lead to new insights into 
-several questions that are critical to a better understanding of the tropical climate and cloud processes.    
+several questions that are critical to a better understanding of \remove[LGS]{the} tropical climate and cloud processes.    
 These questions include: 
@@
   \item{How do clouds influence the overturning circulation?}
-  \item{To what extent are the deep convective clouds and the low-level clouds coupled through 
-  the overturning circulation?}
+  \item{To what extent are \remove[LGS]{the} deep convective clouds and \remove[LGS]{the} low-level clouds coupled through 
+  \remove[LGS]{the} overturning circulations?}
   \item{When simulating tropical overturning circulations, how well does a GCM compare to a CRM?}  
@@
 We thus study a full-physics GCM in an idealized context that is relevant to observed tropical systems, to theoretical
-models of the tropical circulation, and to many of the recent studies of radiative convective equilibrium (RCE).
+models of \remove[LGS]{the} tropical circulations, and to many \remove[LGS]{of the} recent studies of radiative convective equilibrium (RCE).
 
@@
 This serves as the framework with which we naively attempt to transition a GCM 
-towards a CRM.  Our initial motivation for using the 
-GFDL AM4.0 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
+towards a CRM.  
+\change[LGS]{Our initial motivation for using the GFDL AM4.0 model on a doubly-periodic domain was to simulate a tropical Pacific-like region 
 in the context of both a GCM and a CRM in the hopes that resolving more of the turbulent motions and circulations
-would help us to better understand the physics and the mechanisms which are at work in the cloud-circulation
+would help us to better understand }{By simulating a tropical Pacific-like region in GCM-like and CRM-like models, we are able to better understand }    
+the physics and the mechanisms which are at work in the cloud-circulation
 interactions of the tropical Pacific and improve our ability to model this region in a GCM.
@@
 Section five will describe and contrast the Walker circulation in a GCM-like and a CRM-like configuration and
-section 6 includes a brief discussion and lists some of the impacts of the LWCRE and changing 
+section \change[LGS]{6}{six} includes a brief discussion and lists some of the impacts of the LWCRE and changing 
 resolution.  Conclusions are given in the last section.
@@
 scheme as described in Z18a,b, and the references therein.  The prognostic moisture variables are the specific 
-humidity (q), liquid (ql) and frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
+humidity (q), liquid (ql), \remove[LGS]{and} frozen water (qi), and cloud fraction.  The top of the model domain is at 1 hPa, with 33 vertical 
 levels and a sponge layer extending downward to 8 hPa.  The kilometer of atmosphere just above the surface is resolved by 
@@
 
-One technique that has been commonly used to infer the influence of clouds on the atmosphere is to make the clouds invisible to the radiation.  
+One technique that has been commonly used to infer the influence of clouds on the atmospheric \add[LGS]{mean state} is to make the clouds invisible to the radiation.  
 The usual two-way interaction between clouds and radiation is thus broken and a useful diagnostic tool is created.  
@@
 More recently, it has been implemented as part of the CFMIP series of experiments \cite{Stevens_etal_2012, Webb_etal_2017}.
-In the AM4 code, this is done separately for the longwave (LW) and shortwave radiation.  
-In this study we compare control experiments, in which clouds and radiation are fully interactive with experiments in which clouds are invisible to the LW radiation.  
+\add[LGS]{Another technique, referred to as `cloud-locking', can be used to infer how interactions between clouds, radiation, and circulation influence the climate variability}  \cite<e.g.,>[]{Radel_etal_2016}.
+\add[LGS]{This method allows one to decouple the cloud radiative effect from the atmospheric state by holding clouds from a control experiment fixed while the rest of the experiment responds to some perturbation.
+This paper does not use the 'cloud-locking' method.}
+In the AM4 code, we make the clouds invisible to the radiation separately for the longwave (LW) and shortwave radiation.  
+In this study we compare control experiments, in which clouds and radiation are fully interactive, with experiments in which clouds are invisible to the LW radiation.  
 These experiments are referred to as Longwave Cloud Radiative Effect Off (LWCRE-off).  
@@
 The lower panels of Figure \ref{fig:rh_psi_P25vsE25} show high concentrations of condensate in the mid-troposphere over 
-the warmer SSTs, while the regions with subsiding circulations are dry ($< 20\% RH$) above about $900\, \rm{hPa}$.  
+the warmer SSTs, while the regions with subsiding circulations are dry \change[LGS]{($< 20\% RH$)}{$RH < 20\% $} above about $900\, \rm{hPa}$.  
 Two distinct circulation cells are present with one below, and one above $500 \, \rm{hPa}$.   
@@
 a stronger, more concentrated overturning circulation than either E25 (right panels) or P25 LWCRE-off (center panels).   
-The control GCM experiment (P25) also has higher RH and more condensate in the convective
+The control GCM\add[LGS]{-like} experiment (P25) also has higher RH and more condensate in the convective
 region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
@@
 Note that the GCM-like experiments have a larger $\rm{\overline{P}}$ than the CRM-like experiments, and that the
-LWCRE leads to larger $\rm{\overline{P}}$ in the GCM-like experiments but smaller $\rm{\overline{P}}$ in the CRM experiments.  
+LWCRE leads to larger $\rm{\overline{P}}$ in the GCM-like experiments but smaller $\rm{\overline{P}}$ in the CRM\add[LGS]{-like} experiments.  
 This will be discussed further in section 5. 
@@
 Smaller domains (1,024 km compared to 4,096 km wide) were found to have a more focused ascent region, larger precipitation rates, and less low-level clouds in the CRM simulations of \citeA{Bretherton_etal_2006}.
-In contrast, here smaller domains have more low-level clouds and slightly less precipitation rates(Table \ref{tab:experimentmeans}, 
+In contrast, here smaller domains have more low-level clouds and slightly less precipitation rates (Table \ref{tab:experimentmeans}, 
 Figure \ref{fig:TotCond_P25P100}).
@@
 and generally weaker circulations below about 500 hPa.  
-When the clouds and radiation directly interact with each other the experiments have a better
+When the clouds and radiation directly interact with each other the experiments have a \change[LGS]{better}{more}
 organized and stronger circulation below 500 hPa.  Figures \ref{fig:rh_psi_P25E2E1} and 
@@
 The domain mean condensate is closely related to the distribution of clouds and the flow of energy through the atmosphere.  
-It provides clues about the strength of convection and the vertical mass transport.     
+\change[LGS]{It}{The condensate} provides clues about the strength of convection and the vertical mass transport.     
 Figure \ref{fig:TotCond} shows the domain mean condensate for E25, E2, and E1
@@
 This is especially true for the E1 and E2 simulations.  
-Interactive LWCRE leads to less upper level ice-condensate for our CRM experiments
+Interactive LWCRE leads to less upper level ice-condensate for our CRM\add[LGS]{-like} experiments
 with the effect increasing as the resolution increases (Figure \ref{fig:TotCond}).  
@@
 Below about 700 hPa turning off the LWCRE leads to a strong decrease in condensate
-in the GCM experiments, but a negligible decrease in the condensate of the CRMs.    
+in the GCM\add[LGS]{-like} experiments, but a negligible decrease in the condensate of the CRM\add[LGS]{-like experiments}.    
 The profiles of diabatic cooling are similar among all LWCRE-off experiments (Figure \ref{fig:cf_tdtlw}).  
@@
 The manifestation of interactions between clouds and radiation as indicated
-by these characteristics differ dramatically between the GCM and CRM experiments.
+by these characteristics differ dramatically between the GCM\add[LGS]{-like} and CRM\add[LGS]{-like} experiments.
 
@@
 emits more radiation to space, as evidenced by larger values of $\overline{\rm{OLR}}$ 
-for all LWCRE-off experiments.  Atmospheric radiative cooling can be thought of 
+for all LWCRE-off experiments.  \add[LGS]{Net} atmospheric radiative cooling can be thought of 
 as a proxy for the mean precipitation because the cooling is usually balanced primarily by 
-condensational heating.  Larger values of $\overline{\rm{OLR}}$ would then correspond to 
+condensational heating.  \add[LGS]{All else remaining equal, }larger values of $\overline{\rm{OLR}}$ would then correspond to 
 larger values of $\overline{\rm{P}}$.  This is clearly not the case for the E25, P25, and 
 P100 experiments.   The domain mean precipitation rates decrease despite an increased 
-amount of atmospheric cooling.  The implication is that the requisite atmospheric heating 
+amount of \change[LGS]{atmospheric cooling}{$\overline{\rm{OLR}}$}.  The implication is that the requisite atmospheric heating 
 must come from a process other than condensation.
@@
 (at the equator) for LWCRE-off experiments (see their Figure 1).  
-The large decrease of low-level clouds also leads to an increase of downward shortwave radiation at the surface.  
+The large decrease of low-level clouds \add[LGS]{when the LWCRE is off} also leads to an increase of downward shortwave radiation at the surface.  
 Because of the low albedo of water this only slightly increases the fluxes of reflected shortwave radiation (about $2 \, \rm{W \,m^{-2}}$) 
@@
 to overcome the decreased condensational heating at low-levels, with a net effect of less $\overline{\rm{P}}$.  
-Over the regions with cooler SSTs, the CRMs have very few (less than \%5) low-level clouds and as a result the 
+Over the regions with cooler SSTs, the CRMs have very few (less than \change[LGS]{\%5}{5\%}) low-level clouds and as a result the 
 change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
-\citeA{Watanabe_etal_2018} found a similar relationship between low-clouds and precipitation in the context climate 
+\citeA{Watanabe_etal_2018} found a similar relationship between low-clouds and precipitation in the context \add[LGS]{of} climate 
 change experiments.

### 2020-09-04 Silvers_WalkerCell_response2reviewers.tex
further changes for the revision of Walker Circulation paper plus changes to Silvers_cfmip.tex, which is in the wrong repo for some reason.

@@
 
-I have responded to your annotations in the pdf file: 
-Silvers\_WalkerCell\_reviewer1\_1592417419\_response.pdf
+%I have responded to your annotations in the pdf file: 
+%Silvers\_WalkerCell\_reviewer1\_1592417419\_response.pdf
+
+\subsection{General Comments}
+
+\begin{itemize}
+\item Abstract: 
+I think your abstract could benefit from some  reorganization/clarification. It seems to me that there are two overarching themes to your paper:
+%%
+    \begin{enumerate}
+  \item There are significant differences between the CRM-like and GCM-simulated Walker circulation, including a stronger/more symmetric and less low clouds in the CRM-like simulations.
+%% 
+  \item The substantial differences in cloud type between the CRM-like and GCM-like simulations lead to substantial differences in the  atmospheric responses to the longwave cloud radiative effect (e.g.
+more precipitation in the GCM-like simulation, and less precipation in the CRM-like simulation).
+    \end{enumerate}
+%%
+    I think the abstract should summarize these points in this order to help improve the clarity.
+   As it stands, you jump around between 1. and 2. and it makes it a bit more difficult to follow.
+
+\item Ln 67-68:  The Walker circulation itself is not really a framework, and comparing it to observations does not really follow since it occurs in reality.
+I think you mean to say that idealized or ‘mock-Walker’ circulations can be used as a framework to understand the interactions between clouds and circulation, both in observations and in comprehensive climate model simulations?
+  \textcolor{blue}{I agree the Walker circulation itself is not a framework.
+The sentence in question now reads, ``The Walker Circulation provides an excellent example with which to compare the overturning circulation and interactions between clouds and radiation using a variety of model configurations.''}
+
+\item Ln 71: Change to lowercase: 'sea surface temperature'  
+  \textcolor{blue}{Done}
+
+  \item Ln 119-120: Best to avoid colloquial phrases.
+I gather that you are saying that it is difficult to compare, for example, a CRM with a large domain, to a GCM, because there the model physics differ in many ways, not just how convection is treated.
+So differences between those models are not necessarily due to the convection alone.
+Your work helps clarify these issues by using the same model.
+
+  \item Ln 123-124: Can you be more specific here?
+  \textcolor{red}{I have struggled with this one... the sentence seems pretty clear to me.  Could I change something else in the this paragraph to 
+  make this more clear?  Add a sentence after this one?}
+
+  \item Ln 139-144: Split into two sentences.
+This also gives the impression that you were not able achieve your goal.
+Maybe rephrase as 'By simulating a tropical Pacific-like region in GCM-like and CRM-like models, we are able to better understand..."
+  \textcolor{blue}{I have used the sentence that you suggested.}
+
+  \item Ln 193: Although not necessary, it might be good to make some reference to 'cloud-locking' experiments in this paragraph (e.g.
+Radel et al.
+2016).
+The cloud-locking method is useful for studying the impact of cloud-radiation-circulation interactions on the atmospheric variability (e.g.
+ENSO), whereas your methodology is useful for understanding the impacts of cloud-radiation-circulation interactions on the mean state.
+  \textcolor{blue}{I have added the reference to Radel et al.
+and briefly mentioned cloud-locking.
+I also inserted 'mean state' into the first sentence of this paragraph to highlight the point that you make about the difference between the uses of cloud-locking compared to the LWCRE-off technique.}
+
+  \item Ln 216-218: It seems to me that it would be better to refer to any experiment in the range of P100-P25 as 'GCM-like' and any experiment in the range of E25-E1 as 'CRM-like'.
+Then, the E25 and P25 experiments serve as the link between GCM-like and CRM-like experiments.
+  \textcolor{blue}{There was a mistake in this sentence, it has been corrected to include, ``...`GCM-like' while the E2 and E1
+  experiments are referred to as CRM-like''. Additionally, you make a good point here, that the distinction between GCMs and CRMs could be made based on whether a 
+  parameterization is used for the convection.
+However, in my opinion, a model with 25km grid-spacing should not be called cloud-resolving.
+I also considered the possibility of referring to the two classes of model-types as 'explicit models' and 'parameterized models' as a way to more clearly distinguish them.
+But I chose against that naming convention because I think it then blurs the natural similarities that my P100, P25, E25 simulations have with GCMs and the natural similarities my E1, E2 simulations have with CRMs.
+Using parameterized and explicit in the naming also overly emphasizes the convective parameterization despite all simulations involving many identical parameterizations.}
+
+  \item Table 2:  This table is helpful. I wonder if adding two columns for high cloud and low cloud fraction could help further summarize some of your key results?
+
+  \item Figure 1: Nice figure.
+It is interesting that the middle and right panels are so similar to each other.
+Does this suggest that the cloud longwave effects are weak in the E25 simulation?
+And potentially much too strong in the P25 simulation?
+It might be useful to show a plot of the longwave heating rate for each simulation...
+  \textcolor{blue}{I agree, the similarity of panels b and c is interesting.  However, I hesitate to conclude that LW CRE is very weak in E25 LWCRE-on and 
+  too strong in the P25 simulation.  Mostly because I don't know what constitutes a LW CRE that is `too strong'.  I interpret the difference between panels
+  a and b to indicate how important the LWCRE is to the atmospheric state, and the symmetry of panel c to indicate the more regular behavior of explicit convection.
+  While panel b is much more symmetric than panel a, there are still notable asymmetries present which supports the idea that part of the asymmetry comes from the convective parameterization and part of it comes from the LWCRE.
+}
+  \textcolor{red}{could plots of longwave heating be part of the extra section comparing E25 and P25?}
+
+  \item Ln 282-284:  Doesn't Fig.
+1 show that P25 control yields a drier atmosphere?
+You also state this in lines 278-280.
+I guess it yields a drier subsiding region, but also a much more humid convective region.
+  \textcolor{blue}{Yes, the end of your statement is correct, the subsiding region is drier, but the convective region is more humid than the other experiments.
+This is stated in the lines you mention, as well as directly in lines 276-278.
+It is the case that the mean values are a bit different than one might expect from looking at Fig.
+1.
+This also highlights the difference between the means of water vapor compared to water condensate.}
+
+  \item Ln 310: I only see prominent asymmetry in the P25 simulations. The P100 simulation is only slightly asymmetric, and the P100L simulation not asymmetric at all.
+
+  \item Ln 321-323:   If I'm understanding this correctly, it seems that Fig. 1 show that it is mostly the interaction between LWCRE and 
+  circulation that drives this asymmetry. Because Fig 1. middle panel is very symmetrical (with LWCRE disabled).
+
+Also, I wonder to what extent the domain shape influences 
+  this result 
+  (the asymmetry is not present in P100L and less prominent in P25L)
+  \textcolor{red}{It should be pointed out that while the middle panel of Fig1 is symmetrical relative to the left panel, 
+  the far right panel is even more symmetrical (at least in terms of the RH and streamfunction).}
+
+  \item Ln 338-343: Yes, but maybe clarify that you must compare similar domain sizes in Table 2. The variation in SF is also influenced by domain size. 
+  \textcolor{red}{I agree in principle that the cleanest comparisons will be with similar domain sizes, but comparing similar domain sizes does not help to clarify the numbers in Table 2.
+For example, both the largest and smallest SF are found on the large domain.
+}
+
+  \item Figure 6: I think there are too many lines on this plot. Maybe two separate plots would be best: one for P25 and one for P100.
+  \textcolor{blue}{Done.  Splitting this into two panels was a good suggestion.}
+
+  \item Ln 461: 'more' instead of 'better'
+  \textcolor{blue}{Done}
+
+  \item Figure 13: These plots are useful, however I still think it might be helpful to show a profile of the longwave heating rate vs. horizontal distance (like Fig. 10)
+%
+Also, the triangle markers for E25 may be obscuring some details. 
+I wonder if just using a slightly different color for E25 and P25 would be better.
+
+  \item Ln 534-540: Although I understand the point you are making here, the wording is a bit unclear.
+If by 'atmospheric radiative cooling' you mean the net cooling of the atmosphere (i.e.
+difference between OLR and net radiation at the surface), then it is true that the precipitation mirrors the atmospheric radiative cooling.
+
+However, the changes in OLR will not necessarily mirror the changes in precipitation, because the net surface radiation has to be considered as well (as you discuss in the next paragraph). 
+%
+I think you need to briefly clarify the above points here.
+  \textcolor{blue}{To help clarify, I have added 'Net' to the beginning of the sentence that used to start with, 'atmospheric radiative cooling'.
+You comments on lines 536 and 538, and my response to those shown below also help to further clarify the text here.
+  Part of what you are seeing is my attempt to write out the way in which I worked through these ideas.
+The clarity of the paragraph which starts on Line 541 only came after I had to stumble through some of the ideas in the current paragraph.
+I
+  wrote these paragraphs in this way  
+  hopeing that readers will be guided through a similar process and find it helpful.}
+
+  \item Ln 536: This is assuming the net surface radiation does not change.
+  \textcolor{blue}{True.  To make this crystal clear I have added, 'All else remaining equal' to the beginning of the sentence.}
+
+  \item Ln 538: I think this should read 'OLR' not 'atmospheric cooling'.
+The atmospheric radiative cooling actually decreases in the experiments without LWCRE (as you discuss in the following paragraph).
+  \textcolor{blue}{Good catch, 'atmospheric cooling' has been changed to, 'OLR'.}
+
+  \item Ln 541: Great discussion in this paragraph.  
+  \textcolor{blue}{Thank you}
+
+  \item Ln 545-546: This is particularly true because the low clouds are found in relatively dry regions.
+Without low clouds, the dry atmosphere would emit less downwelling longwave radiation and roughly the same outgoing longwave radiation.
+In other words, the low clouds effectively increase the downwelling radiation in dry regions, which leads to more atmospheric cooling.
+  \textcolor{blue}{This is a good way of stating the underlying reasons.  I have made some modifications so the sentence now 
+  reads, ``Low-level clouds, especially in dry regions, serve as a significant source of  radiative cooling for the atmosphere (Figure 
+  13) because they increase the downwelling longwave radiation.''}
+
+  \item Ln 556-557: A bit unclear. What decrease of low-level clouds are you referring to here? Are you referring to the fact that the CRM-like simulations have fewer low clouds?
+  \textcolor{blue}{I have added, `when the LWCRE is off' to this sentence to make my meaning clear.
+I am not referring to the fact that CRM-like simulations have fewer clouds, but to the fact that there are far less low-level clouds in the LWCRE-off simulations
+  especially for the GCM-like simulations. }
+
+  \item L584-608: I think it is good to have a summary here, but I'm getting lost in all of the details.
+It would be helpful for the reader if you could summarize only the most important points (maybe 5-6 bullets max).
+For example, I think you could probably eliminate the last 2 points in the first set (i.e.
+about spatial gradients of humidity, etc and about the condensate changes).
+
+You also do not summarize any of the domain size results here, however they are mentioned in your conclusions.
+So I'm left a bit confused about the overall importance of the domain size results...
+to remedy that I suggest 1) mentioning the key domain-size sensitivies here and/or 2)  deleting the discussion of the domain-size sensitivities in the conclusions.
+Just trying to help you better convey the main points to the reader.
+  \textcolor{red}{I sympathize with you.
+This paper has been hard to write because it has been tough to not get lost in all of the details myself.
+The \textit{importance} of several of these results, such as the domain size results, is not clear to me, but they
+  seem both interesting and significant.}
+
+  \item Ln 690-692: Can you speculate about why this might be?
+Could the smaller low-cloud amounts in the CRM-like experiment be due to the stronger overturning circulations, and hence stronger subsidence drying?
+
+  \item Ln 701: 5\%
+  \textcolor{blue}{Done}
+
+  \item Ln 704: context 'of' 
+  \textcolor{blue}{Done}
+
+  \item Ln 704-706: I know this is not the focus of your study, but I wonder which simulation has the more realistic cloud profile: the CRM or GCM-like simulation?
+The low-cloud fraction seems quite small in the CRM-like experiments...
+  \textcolor{red}{This comment overlaps with the desire from reviewer \# 3 (section 4.1.3 of their review).  Would a plot of MISR observations from the tropical Pacific work well?  }
+
+  \item Ln 737-739: This is certainly an interesting result, but I wouldn't say it is a 'consistent asymmetry' given the results in the P100L simulation.
+I think this should be rephrased to reflect that.
+%
+\end{itemize}
 
@@
   \item Section 3 is meant to focus on the impact of LWCRE, but subsequent sections frequently reference the comparison between LWCRE-on and LWCRE-off as well (i.e. lines 361-373, 398-401, 459-462).
+  \textcolor{red}{During the writing I attempted consolidating the comparison between LWCRE on/off to one section but found it to create more problems than it solved because the LWCRE on/off experiments have such a strong influence on all of the other sections.
+As a result, I have chosen to largely focus on your other excellent recommendations for reworking the organization of the manuscript.}
   \item Comparisons between E25 and P25 are made in multiple sections, and some of these results are referenced in passing (i.e.
@@
 Given the importance of this resolution in the manuscript to link GCMs and CRMs, I believe that this deserves its own section.
+  \textcolor{red}{To further aid in the comparison between E25 and P25, the P25 control and P25 LWCRE-off profiles have been added to Figure 11 (note the number of this figure may change depending on the E25/P25 section).
+The color used to show the E25 profiles has also been changed from yellow to purple in several of the figures and I think this also helps readers to compare E25 and P25.}
   \item Figure 10, in the context of its section on resolution dependence, seems to convey a similar picture as Figure 9, and its already been well-established that removing LWCRE seems to broaden/weaken the mass circulation robustly.
@@
   \item I believe that Sections 6 and 7 can be consolidated and combined into one, given that the first half of Section 6 is already a well-constructed and well-divided summary of results.
+  \textcolor{red}{related to comments from Reviewer \# 1 on reducing number of points in section 6...}
   \item In several parts of the manuscript, multiple references are made to Figures/Tables that appear 10 or more pages earlier.
@@
 Figure 13 would be best oriented as a 2X2 window similar to Figure 12, especially given the subtle differences in the rightmost panel.
+  \textcolor{red}{For several of the figures (6, 11,12, and 13) the labels and axis font size has been increased.  Figure 6 has now been split into two figures, one
+  showing results on the small/control domain size and the other showing results on the large domain.}
 
   \item For each of the figures, especially those later in the manuscript, it would be helpful to make the font size on the axes a bit larger.
+  \textcolor{red}{The font size has been increased for Figures 6,11,12, and 13.}
 
@@
 Another piece of this (I was a bit hesitant to include too many Hovmoller plots, fearing Hovmoller fatigue.)  }
+\textcolor{red}{include Hovmoller figure with four different 25km simulations?}
 
@@
 Do you have any speculation as to why this happened?
+  \textcolor{red}{When I first saw this upward shift I thought it must be an error in some part of the setup or analysis...
+when I convinced myself it was not an error I was fascinated.
+However, it is one of several interesting results that I have resisted
+  pursuing in this paper for fear of being pulled in two many directions.  My speculation is that...}
 
@@
 Apologies if this is something that has already been addressed elsewhere in the manuscript.
+  \textcolor{red}{For the figures which show profiles from the 'subsidence' regions, those regions are defined as the quarter of the domain furthest from the SST maximum, or the two sections, each an eighth of the domain width, which are at the outer edges of the domain.
+I played around with this a bit, especially because the asymmetry in some of the runs can complicate things.
+But defining the subsidence region as only a quarter of the domain instead of, say, half of the domain, minimizes the influence of asymmetry.}
+
 \end{itemize}
@@
 place, even if the manuscript’s results confirm the importance of this experiment a posteriori.
+\textcolor{red}{This response should lean heavily on Popp and Silvers.
+It should additionally emphasize the many directions which the paper already hints at due the large amount of experiments that are being compared, domain size differences,
+parameterization differences, resolution differences, and the LWCRE differences.  Adding another tier of simulations would 
+be risky...}
 \end{itemize}
@@
 rationale if not a quantitative explanation for why the authors find the results summarized in Section 6.  
+\textcolor{red}{Perhaps the recommendation from the first reviewer to combine sections 6 and 7 will help to answer this point as well...}
 

### 2020-09-04 Silvers_WalkerCell_revision.tex
further changes for the revision of Walker Circulation paper plus changes to Silvers_cfmip.tex, which is in the wrong repo for some reason.

@@
 longitudinal asymmetries in \remove[LGS]{the} tropical atmospheric heating and is tightly coupled with 
-the El Nino Southern Oscillation.    
-The Walker Circulation is a compelling example of both thermodynamic and dynamic interactions
-between moisture and the large-scale circulation.  It is also a framework that can be compared 
-to observations and tested with a variety of model configurations.
+the El Ni\~{n}o-Southern Oscillation (ENSO).    
+The Walker Circulation \change[LGS]{is a compelling example} 
+{is composed}
+of both thermodynamic and dynamic interactions
+between moisture and the large-scale circulation.  
+\change[LGS]{It is also a framework that can be compared 
+to observations and tested with a variety of model configurations.}
+{The Walker Circulation provides an excellent example with which to compare the overturning circulation and interactions between clouds and radiation using a variety of model configurations.}
 
@@
 both a GCM-like model and a CRM-like model.
- Idealized models of the Walker circulation were first called `mock-Walker circulations' by \citeA{Raymond_1994}.  
+ Idealized models of the Walker circulation were \change[LGS]{first called}{referred to as}  `mock-Walker circulations' by \citeA{Raymond_1994}.  
 \citeA{Raymond_1994} envisioned an idealized Walker circulation as,``a possible venue for testing ideas 
@@
 Current climate models continue to be developed with an increasingly fine resolution and 
-the domain size used with CRMs continues to grow.  As a result the line between these two types 
+the domain size used with CRMs continues to grow.  
+% As a result, the distinction between these two types of models
+% Accordingly, the parameter space of these two types of models has begun to overlap.   As a result, 
+% there is a need to systematically compare the 
+% Nevertheless (or, notwithstanding this,), GCMs and CRMs differ in many ways and there is a need to systematically 
+% compare the simulated clouds from both.  
+As a result the line between these two types 
 of models has become blurred and there is a need to systematically compare the clouds and their 
@@
 of moisture with the large-scale circulation.     
+%
+% This paper uses a mock-Walker Circulation to study the coupling between atmospheric moisture and the large-scale circulation.
+% Using a single model base in the context of both a GCM and a CRM illustrates how inextricable the interactions between clouds and radiation are 
+%
+% Simulating a mock-Walker Circulation in the context of both a GCM and a CRM 
+% shows how the interactions of clouds and radiation interact
+%
+% the mock-Walker Circulation provides a simple dynamical context within which
+% the inextricable interactions between clouds and radiation can be shown to influence the
+% coupling of moisture with the large-scale circulation.
+%
+% illustrates how inextricable the interactions between clouds and radiation is to the coupling 
+% of moisture with the large-scale circulation. 
 The model used here is based on GFDL's AM4.0 GCM that participated in CMIP6, having a full suite of physics parameterizations.  
@@
 The naming convention for each of the experiments is shown in Table \ref{tab:experimentspecs}.   
-Throughout this paper the P100 and P25 experiments, with and without the LWCRE are referred to as `GCM-like' and
-`CRM-like'.  The GCM-like experiments only differ from traditional GCMs in the non-global domain and lack of rotation.  
+Throughout this paper the P100 and P25 experiments, with and without the LWCRE, are referred to as `GCM-like' \change[LGS]
+{and `CRM-like'}{while the E2 and E1 experiments are referred to as `CRM-like'.}  The GCM-like experiments \remove[LGS]{only} differ from traditional GCMs in the non-global domain and lack of rotation.
 The CRM-like terminology acknowledges that this configuration 
@@
   \centering
-      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan_new.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_25km_6pan_new.eps}
       \caption{The equilibrated state of the Walker cell for three configurations with a grid-spacing of 25km on a domain of 200 $\times$ 4000 $\, \rm{km}^2$.
@@
 
+%\begin{figure}
+%  \centering
+%       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
+%          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P100 (red) and P25 (yellow) on the domain 
+%          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
+%          and dashed lines the LWCRE-off experiments.}
+%  \label{fig:TotCond_P25P100}
+%\end{figure}
 \begin{figure}
   \centering
-       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_P100vsP25_lgvsm_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P100 (red) and P25 (yellow) on the domain 
-          with a long dimension of 16,000km (thick) and 4,000 (thin).  Solid lines show experiments with LWCRE on
-          and dashed lines the LWCRE-off experiments.}
+       \includegraphics[width=0.90\columnwidth]{DomainMeanCond_SinglePanel.pdf}
+          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) on the domain with a long dimension of 16,000km (a.)
+          and 4,000 km (b.).  P25 experiments are shown with yellow lines and P100 experiments with red.  Solid lines show 
+          experiments with LWCRE on and dashed lines the LWCRE-off experiments.}
   \label{fig:TotCond_P25P100}
@@
   parameterization (black).  
-  Panels on the left show large domains with a long edge width of 16,000 km and
-  panels on the right show domains with a long edge width of 4,000 km.  LWCRE-off experiments are shown with dashed lines.  }
+  Panels on the left (a.,b.) show large domains with a long edge width of 16,000 km and
+  panels on the right (b.,d.) show domains with a long edge width of 4,000 km.  LWCRE-off experiments are shown with dashed lines.  }
   \label{fig:conv_vs_ls}
@@
   \centering
-      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwon_new.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwon_new.eps}
       \caption{The equilibrated state of the Walker cell as a function of resolution.  
@@
   \centering
-      \includegraphics[angle=90,width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff_new.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/rh_psi_cond_E25E2E1_lwoff_new.eps}
           \caption{Same as previous figure except with the longwave CRE turned off.}
@@
   \centering
-       \includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
-          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) for P25 (thin yellow), E25 (yellow), 
-          E2 (blue), and E1 (green).  Solid lines show experiments with LWCRE on,
-          dashed lines show the LWCRE-off experiments.  All experiments have explicit convection.}
+       %\includegraphics[width=0.45\columnwidth]{walkerfigs/Cond_Walker_E25E2E1_lwoff.eps}
+       \includegraphics[width=0.45\columnwidth]{walkerfigs/DomainMnCond_4mods_new.eps}
+          \caption{Domain mean total condensate (liquid + ice; grams/kilogram).  Solid lines show experiments with LWCRE on,
+          dashed lines show the LWCRE-off experiments.}
   \label{fig:TotCond}
@@
 wind) because changes in the downward flux of solar radiation will not warm the surface.   
-Low-level clouds serve as a significant source of LW radiative cooling for the atmosphere (Figure \ref{fig:cf_tdtlw}).  
+Low-level clouds \add[LGS]{, especially in dry regions,} serve as a significant source of \remove[LGS]{LW} radiative cooling for the atmosphere (Figure \ref{fig:cf_tdtlw}) \add[LGS]{because they increase the downwelling longwave radiation}.
 Making these clouds invisible to radiation creates a source of effective atmospheric warming by removing a source of atmospheric energy loss.  

### 2020-09-04 Silvers_cfmip.tex
further changes for the revision of Walker Circulation paper plus changes to Silvers_cfmip.tex, which is in the wrong repo for some reason.

@@
 More details are provided in the appendix.  The CMIP6 and CFMIP experiments used in this study are given in Table
-\ref{tab:exps} and the observational data sets used are given in Table \ref{tab:obs}.
+\ref{tab:exps} and the observational data sets used are given in Table \ref{tab:obs}.  Additional details about all 
+experiments used in this paper are given in \cite{Eyring_etal_2016} and \cite{Webb_etal_2017}.  The experiments are referred to with the
+appropriate CMIP6 labels.
 
@@
 in this paper are all part of the GFDL contribution to CMIP6 and as a result, the \textit{amip} and \textit{historical}
-experiments end in the year 2014.  We use the \textit{historical, abrupt-4xCO2, and 1pctCO2}
+experiments end in the year 2014.  We use the \textit{historical, abrupt-4xCO2}, and \textit{1pctCO2}
 experiments from the CMIP6 DECK.  In addition we utilize several experiments from the CFMIP contributions 
@@
     \hline
- Feedback & Aqua p4K & Amip m4K & Amip p4K &  Amip p8K & Amip Future   \\ \hline
+ Feedback & \textit{aqua-p4K} & \textit{amip-m4K} & \textit{amip-p4K} &  \textit{amip-p8K} & \textit{amip-future4K}   \\ \hline
     Net  $\alpha$        &   -2.13      &  -1.66          &  -1.62         & -1.64           & -1.84           \\ 
@@
 
+\textit{where should this paragraph go?}
 The radiative feedbacks shown in Tables \ref{tab:lambda_AGCM} and \ref{tab:lambda_AOGCM} reveal a large range of 
@@
 However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations.
-
-\textit{The clouds in these simulations respond to a variety of different conditions including different
-patterns of SST, the presence or absence of land or sea ice, and in the case of the aquaplanet
-experiments, a lack of cloud-aerosol interactions which are present in the AGCM (AM4.0) and coupled 
-experiments (AOGCM; CM4.0).  }
 
@@
 particular years (see text).  The values for the \textit{abrupt 4x$\rm{CO}_2^{b}$} and  \textit{abrupt 4x$\rm{CO}_2^{c}$} experiments
-have been calculated using linear regression over years 1-150 and 51-300, respectively.  
+have been calculated using linear regression of 1 year means over years 1-150 and 51-300, respectively.  
 \textit{abrupt 4x$\rm{CO}_2^{a}$}, \textit{abrupt 4x$\rm{CO}_2^{b}$}, and \textit{abrupt 4x$\rm{CO}_2^{c}$} represent data from the same experiment, the feedback values have simply been calculated differently.
@@
     \hline
- Feedback     &  Amip   & Historical   &  1pct$CO_2$ & Abrupt 4x$\rm{CO}_2^{a}$ &  Abrupt 4x$\rm{CO}_2^{b}$ &  Abrupt 4x$\rm{CO}_2^{c}$ \\ \hline
-    Net $\alpha$    & -1.77      &   -1.83      &  -1.22          &  -1.11    &  -0.82   &   -0.46              \\ 
-    \\
-    Net CRE  &    -0.46            &   -0.45       &  -0.16          & -0.06   & ?      &   0.65         \\  
-    \\
-    LW CRE    &   -0.03           &   -0.14        &  0.10            & 0.14   &  ?        & 0.14          \\  
-    \\
-    SW CRE  &     -0.43             &    -0.31       &  -0.26            & -0.20    &  ?      &  0.5         \\  
-    \\
-    LW CLR   &     -2.25             &    -1.94       &  -1.71            & -1.70    &   ?      & -1.7        \\  
-    \\
-    SW CLR  &      0.91            &     0.56        & 0.65              & 0.65    &    ?         & 0.6          \\  
-    \\
-    $\Delta \rm{T}_s$     &     1.3     & 0.8        &  4.3           & 5.7     &   -         & -          \\  \hline
+ Feedback     &  \textit{amip }  & \textit{historical}   &  \textit{1pctCO$_2$} & \textit{abrupt-4xCO$_2^{a}$} & \textit{abrupt-4xCO$_2^{b}$} & \textit{abrupt-4xCO$_2^{c}$}  \\ \hline
+    Net $\alpha$    & -1.77      &   -1.83      &  -1.22          &  -1.11    &  -0.84   &   -0.55              \\ 
+    \\
+    Net CRE  &    -0.46            &   -0.45       &  -0.16          & -0.06   & 0.17      &   0.62         \\  
+    \\
+    LW CRE    &   -0.03           &   -0.14        &  0.10            & 0.14   &  0.25        & 0.11          \\  
+    \\
+    SW CRE  &     -0.43             &    -0.31       &  -0.26            & -0.20    &  -0.08      &  0.51         \\  
+    \\
+    LW CLR   &     -2.25             &    -1.94       &  -1.71            & -1.70    &   -1.79      & -1.74        \\  
+    \\
+    SW CLR  &      0.91            &     0.56        & 0.65              & 0.65    &    0.79         & 0.57          \\  
+    \\
+    $\Delta \rm{T}_s$     &     1.3     & 0.8        &  4.3           & 5.7     &   3.90 (7.8?)        &   4.60 (9.2?)         \\  \hline
 
@@
 \end{table}
+
+% The wide range of numbers in the 3 different estimates of sensitivities for the abrupt 4xCO2 experiment, especially 
+% the SW CRE raise the question of why.  Is the TOA flux data available from the 3 hundred year abrupt experiment?  
+% I don't see cl calipso date past year 150.
 
@@
 The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback in the three coupled CM4.0 experiments and in the \textit{amip} experiment.
-Values shown in Table 2 imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
+Values shown in Table \ref{tab:lambda_AOGCM} imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
 do not have as much of a cooling effect as they do in the \textit{historical} and \textit{amip} experiments.
@@
 Anomalies in the middle panel of Figure \ref{fig:CRE_feedback} have been computed relative to the \textit{piControl} experiment.
-The CRE and warming are
+The CRE and warming in Table \ref{tab:lambda_AOGCM} are
 computed for the years 1996-2014 (\textit{historical} and \textit{amip}) and years 100-150 (\textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$}).
@@
 in the \textit{amip-Future4K} experiment due to a different SW CRE response in the southern hemisphere.  
-The sign of the feedback values for the \textit{amip-m4K} experiment was reversed so that the symmetry with the CRE
+The sign of the feedback values for the \textit{amip-m4K} experiment have been reversed so that the symmetry with the CRE
 feedback from the \textit{amip-p4K} experiment can be easily assessed.  An interesting point that emerges is that 
@@
 All of the panels in Figure \ref{fig:CRE_feedback} point to the importance of the cloudy response in the southern 
-hemisphere.   The net CRE is notably stronger compared to the northern hemisphere, and the many of the differences 
+hemisphere.   The negative CRE is notably stronger compared to the northern hemisphere, and many of the differences 
 in the CRE among the various experiments studied here can be seen as a result of different distributions of southern 
@@
 
-The anticipated responses of clouds to warming include anvil clouds rising to higher altitudes, a 
-shift of cloud phase towards more liquid clouds at high-latitude, and in many cases a decrease in the 
-low-level cloud amount (references).  This subsection examines the latitudinal distribution of low-, mid-, and upper-level clouds across 
-several of CMIP6 and CFMIP experiments that the AM4.0 Aquaplanet, AM4.0, and CM4.0 participated in.  First, we compare the 
-cloud fraction from the \textit{amip}-type experiments to the observations from CALIPSO (Figure \ref{fig:calipso_amip_comparison}).   
-We will then look at the cloud fields for warming experiments and examine the cloud fraction biases relative to the \textit{piControl} 
-experiment and relative to the \textit{amip} experiment (Figure \ref{fig:CF_warming}).   All results from AM4.0 or CM4.0 are from 
-the CALIPSO satellite simulator.
-
-For the low-level clouds, and the tropical mid-level clouds, the range of cloud fraction among the \textit{amip}-type
-experiments is less than the cloud fraction bias with observations.  However, at high latitudes for the mid-level and upper-level, 
-the range of cloud fraction is larger and in some cases approaches the observed cloud fraction.   
- %%These different experimental configurations influence how much of an impact the ice-albedo feedback plays.  
-%%The more dynamic the ice is for a given experiment, the more positive will the SW CLR 
-%%feedback be as a result of the ice-albedo feedback.
+To what extent can we connect the differences in CRE that are present in Tables  \ref{tab:lambda_AGCM} and \ref{tab:lambda_AOGCM} 
+to differences in the distributions of clouds?  This subsection examines the latitudinal distribution of low-, mid-, and upper-level clouds across 
+several CMIP6 and CFMIP experiments that have been run with the AM4.0 Aquaplanet, AM4.0, and CM4.0 models.  
+All cloud fraction results from AM4.0 or CM4.0 are from the CALIPSO satellite simulator that is part of AM4.0.   
+First, we compare the cloud fraction from the \textit{amip}-type warming experiments to the observations from CALIPSO (Figure 
+\ref{fig:calipso_amip_comparison}).   We will then look at the cloud fields for coupled warming experiments and examine the cloud fraction 
+biases relative to the \textit{piControl} experiment and relative to the \textit{amip} experiment (Figure \ref{fig:CF_warming}).   
+\textcolor{red}{the following should probably move to when we are discussing Figure 9.}
+ The radiative 
+feedback values in Table \ref{tab:lambda_AGCM} have been computed with the \textit{amip} experiment as the control while the feedback
+values from the coupled model warming experiments in Table \ref{tab:lambda_AOGCM} have been computed with the \textit{piControl}
+experiment as the control.  Table  \ref{tab:lambda_AGCM} is therefore most closely tied to the right column of Figure \ref{fig:CF_warming} 
+while the values in Table  \ref{tab:lambda_AOGCM} are most closely tied to the center column of Figure \ref{fig:CF_warming}.
+
+The range of cloud fraction differences among the \textit{amip}-type warming experiments is less than the cloud fraction bias with 
+observations (Figure \ref{fig:calipso_amip_comparison}) for the low-level clouds, the tropical mid-level clouds, and mid-latitude upper-level 
+clouds.  However, at high latitudes for the mid-level and upper-level, the range of cloud fraction is larger and in some cases approaches 
+the observed cloud fraction.  The response of clouds in the \textit{amip} experiment to a uniform 4K increase of SST and to a uniform
+4K cooling of SST is shown to be nearly symmetric, especially in midlatitudes, about the baseline \textit{amip} cloud fields.     
+The uniform cooling (warming) experiment \textit{amip-m4K} (\textit{amip-p4K}) results in an increase (decrease) of tropical low-level clouds 
+and midlatitude mid-level clouds but a decrease (increase) in deep tropical anvil clouds and high-latitude upper-level clouds.  
+Differences between the cloud fields of the \textit{amip-p4K} and \textit{amip-future4K} will be discussed in the context of Figure \ref{fig:CF_warming}.
+Clearly the cloud fraction in warming experiments is not directly comparable to observations of
+present day clouds.  However, the large cloud fraction bias illustrated here (particularly in the low-level clouds and tropical mid-level clouds) 
+highlights the question of whether the baseline cloud fields influence cloud feedbacks.
+
+Recall from Table \ref{tab:lambda_AGCM} that despite a similar global mean increase of surface air temperature, the \textit{amip-p4K} and \textit{amip-future4K} show 
+differences in the climate feedback parameter of about $0.2 \, \rm{W m^{-2} K^{-1}}$.
+Figures  \ref{fig:calipso_amip_comparison} and \ref{fig:CF_warming} show that the cloud fields are similar between these two experiments.
+However, there are important
+differences between \textit{amip-p4K} and \textit{amip-future4K} in the upper-level deep tropics and the southern hemisphere low-level
+clouds, especially when examining the bias relative to \textit{amip} (Figure \ref{fig:CF_warming}, right column).  
+Upper-level anvil clouds shift into the southern hemisphere in the \textit{amip-future4K} experiment which also has more low-level southern 
+hemisphere clouds relative to both \textit{amip} and  \textit{amip-p4K} experiment.  These additional low-level clouds in the southern hemisphere 
+are consistent with a more negative SWCRE in the \textit{amip-future4K} experiment (Table  \ref{tab:lambda_AGCM}).
+
+One of the strongest signals from Table \ref{tab:lambda_AOGCM} is that the net CRE feedback parameter is between 
+$0.3-0.4 \,  \rm{W m^{-2} K^{-1}}$ more negative in the \textit{amip} and \textit{historical} experiments than it is for the coupled 
+warming experiments.  This reflects the fact that both the observed and simulated climate sensitivity over recent decades is 
+notably less than the climate sensitivity found by coupled models when looking at future warming experiments.  
+The difference in the net climate feedback parameter is due to both the LW CRE and SW CRE being more negative in the \textit{amip} and \textit{historical}.
+Differences in cloud response of up to 10\% of the cloud fraction are seen in Figure  \ref{fig:CF_warming} between the coupled warming experiments and 
+the experiments covering the recent observational period.    
+Figure  \ref{fig:CF_warming} (bottom center; bottom right) shows 1-10 \% fewer low-level clouds at most latitudes (particularly mid-latitudes) for the 
+\textit{1pctCO$_2$} and \textit{abrupt-4xCO$_2$} experiments compared to the \textit{amip} and \textit{historical} experiments.  
+%The mid-latitudes of the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments  have fewer low-level clouds 
+Fewer low-level clouds contribute to less negative SW CRE.  Fewer mid-level and more upper-level clouds of the \textit{1pctCO$_2$} and \textit{abrupt-4xCO$_2$} experiments further contribute 
+to the less negative SW CRE and positive LW CRE.  These cloud fraction differences are especially pronounced for the \textit{abrupt-4xCO$_2$} 
+experiment which has the least negative climate feedback parameter (largest climate sensitivity) among the \textit{amip}, \textit{historical}, 
+\textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments.  
+%These differences in clouds are consistent with the \textit{amip} and \textit{historical} experiments having a more negative net CRE.
+
+One consistent finding throughout the \textit{amip}-type and the coupled experiments (Figures \ref{fig:calipso_amip_comparison} 
+and \ref{fig:CF_warming}) is that the largest differences among experiments
+in upper-level cloud fraction occur in the deep tropics or high latitudes.  In contrast, the mid-level clouds show very little 
+difference among experiments in the tropics or high latitudes but instead have large differences in the mid-latitude 
+cloud fractions.  Substantial differences among experiments in the low-level cloud fraction occur in all latitudinal regions.
+
+It has been known for decades that differences in (tropical?) low-level cloud among experiments are a driving factor of the large range in the estimates of climate 
+sensitivity from GCMs.  Accordingly, Tables 1 and 2 show that a large part of the range in climate feedback parameter among the AM4.0 and CM4.0 
+experiments is due to the SW 
+CRE and Figure 9 reveals different low-cloud biases in the tropics for almost every experiment.   
+However, the largest low-cloud feature in Figure 9 is not in the tropics, but the high-latitudes.  Poleward of 70$^\circ$ N and between 
+60-80$^\circ$S the low-cloud response varies by 8-15\%.  What is 
+interesting is that the variations in these regions are sandwiched between the high values from the \textit{piControl} experiments and the low-values
+produced with the \textit{amip} experiment with the cloud fraction from the coupled experiments being near those of \textit{piControl} and the
+cloud fraction in the \textit{amip}-like warming experiments being near those from the \textit{amip} experiment.  
+It is also worth noting that poleward of 70$^\circ$N both the \textit{amip} and \textit{historical} experiments produce more clouds than 
+observed and between 60-80$^\circ$S the \textit{amip} and \textit{historical} low-cloud bias relative to observations is quite low. (Figure 5). 
+Simulations which include a dynamic ocean (\textit{piControl, historical, 1pctCO$_2$}, and \textit{abrupt-4xCO$_2$}) have far more clouds (Figure \ref{fig:CF_warming})
+between  60-80$^\circ$S than do the atmosphere only experiments that used prescribed
+SST.  All experiments have far more clouds in the arctic than does the \textit{amip} experiment (Figure \ref{fig:CF_warming}).  
+\textit{The implication is that....}
+%
+% What does the difference in cloud fields between amip and piControl indicate?  
+%
+% These two regions have been identified as crucial for our understanding future climate changes and highlight important sources of uncertainty. 
+% The Southern Ocean has shown that climate models struggle to simulate the physics of changing temperatures in mixed-phase clouds while 
+% the highly variable arctic regions has repeatedly challenged our understanding of feedback processes under climate change.
 
@@
 
-\textit{How much do clouds contribute to our uncertainty in the climate sensitivity?  
-Which clouds (high, mid, low, thick, thin, geographic regions) contribute to this uncertainty?
-Why do we do a poor job with these clouds in models? }
-
-Probably have to cite Armour, 2017.
-He does put the time varying sensitivity in context, and discusses the use of the energy budget constraints.
-But then I also need to determine how to contextualize the information published by Armour, Andrews, and Lewis.
-What are the takeaways?
-
-\textit{We should probably mention that we have used the CALIPSO simulator to predict cloud changes in the future...}
+Over the recent decades which have had excellent/global satellite coverage both amip and historical experiments significantly underestimate (10-15\%)
+the observed cloud fraction.  This is especially true for low-level, optically thin clouds between $pm 30$.  The comparison with observed TOA 
+radiative fluxes for AM4/CM4 is quite good, which combined with the under-estimate of cloud fraction implies the presence of the so-called
+'too few, too bright' cloud bias which was also present in CMIP3 and CMIP5 global climate models.
+
+What additional constraints can we recommend for GCMs?
 
@@
 In contrast, this study focuses on several models from a single modeling center, all based on the same generation of code.
-By so doing we can more clearly attach the source of spread in the climate sensitivity to differences in the geophysical configuration and to the responses of the clouds to different boundary conditions...
-with less ambiguity.}
+By so doing we can more clearly attach the source of spread in the climate sensitivity not to
+differences in the microphysics or convection parameterizations but to differences in the geophysical configuration and to the responses of the clouds to different boundary 
+conditions... with less ambiguity.}
+
+We have identified/quantified the part of the climate feedback parameter in each experiment that is simply due to differences in the 
+geophysical configuration (e.g. presence of land, sea-ice, etc.).  In addition we illustrate the range of CRE feedbacks among the 
+experiments with AM4/CM4 and show how these CRE feedbacks vary as a function of latitude.  Overall the SH emerges as a  primary 
+region of differences in cloud responses to warming.  In addition, the NH midlatitudes reveal a substantial decrease of cloud cover and 
+subsequent positive shift of the SW CRE in the experiments which are most sensitive to CO2 perturbations (abrupt 4xCO2 and 1pct CO2).
+
+It is well known that the precise value of climate sensitivity is sensitive to the method of calculation.  Table 2 highlights how much the 
+CRE feedback can vary depending on the period of interest and includes, for reference, what has become the common method of 
+calculation using only the first 150 years of the abrupt 4xCO2 experiment.  
+% some variation of years used for Figure 9 indicates that the cloud fraction varies minimally.  If the time period used to plays a large role in the calculation
+% of CS but not in the distribution of cloud fraction, what does that tell us?
+
+One motivation for this paper is to compare the GFDL output of cloud fraction to the recent data sets from satellites.  An additional 
+motivation has been to show that within a single modeling framework the model physics, and in particular the clouds, can dramatically 
+influence the climate sensitivity and care must be taken when discussing...
+
+\textit{The anticipated responses of clouds to warming include anvil clouds rising to higher altitudes, a 
+shift of cloud phase towards more liquid clouds at high-latitude, and in many cases a decrease in the 
+low-level cloud amount (references).}
+
+\textit{How much do clouds contribute to our uncertainty in the climate sensitivity?  
+Which clouds (high, mid, low, thick, thin, geographic regions) contribute to this uncertainty?
+Why do we do a poor job with these clouds in models? }
+
+Probably have to cite Armour, 2017.
+He does put the time varying sensitivity in context, and discusses the use of the energy budget constraints.
+But then I also need to determine how to contextualize the information published by Armour, Andrews, and Lewis.
+What are the takeaways?
+
+\textit{We should probably mention that we have used the CALIPSO simulator to predict cloud changes in the future...}
 
@@
 the various warming experiments?
+
+\textit{The clouds in these simulations respond to a variety of different conditions including different
+patterns of SST, the presence or absence of land or sea ice, and in the case of the aquaplanet
+experiments, a lack of cloud-aerosol interactions which are present in the AGCM (AM4.0) and coupled 
+experiments (AOGCM; CM4.0).  }
 
@@
 All of the experiments examined show cloud biases relative to observations that are larger than the differences of cloud fraction among the experiments.    
+A substantial portion (quantify) of the range in CS among the AM4/CM4 experiments examined here is due to 
+driven by a range in the CRE.  However, the differences in cloud fraction among the experiments is smaller than 
+the bias of the recent decades relative to observations.  Can we say that reducing the observational cloud bias
+should be at least as much of a priority in future development as reducing the spread of cloud feedbacks among
+models?
 
@@
 %clouds in the GFDL model was the first priority, it could be done.  However it is not the first priority and doing so degrades other elements of 
-%the climate.  
+%the climate.    Niavely prioritizing cloud optimization can seriously degrade other aspects of the climate, such as the representation of 
+% ENSO or the MJO.   
 %
@@
  Experiment & Class & Configuration & Years   \\ \hline
-    historical        &   DECK      &  atmosphere \& ocean   &  Jan 1950 -Dec 2014               \\ 
-    \\
-    abrupt 4xCO2   & DECK       &  atmosphere \& ocean       & 150 years  \\  
-    \\
-    1pct CO2   & DECK        &  atmosphere \& ocean  & 150 years \\  
-    \\
-    piControl  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
-    \\
-    amip  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
-    \\
-    amip +4K  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
-    amip -4K   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
-    amip Future 4K  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
-    aqua control        & CFMIP  & atmosphere  & 10 years \\
-    aqua +4K.  & CFMIP    & atmosphere  &  10 years \\ \hline
+    \textit{historical}        &   DECK      &  atmosphere \& ocean   &  Jan 1850 -Dec 2014               \\ 
+    \\
+    \textit{abrupt-4xCO$_2$}   & DECK       &  atmosphere \& ocean       & 150 years  \\  
+    \\
+    \textit{1pctCO$_2$}   & DECK        &  atmosphere \& ocean  & 150 years \\  
+    \\
+    \textit{piControl}  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
+    \\
+    \textit{amip}  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
+    \\
+    \textit{amip-p4K}  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
+    \textit{amip-m4K}   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
+    \textit{amip-future4K}  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
+    \textit{aqua-control}        & CFMIP  & atmosphere  & 10 years \\
+    \textit{aqua-p4K}  & CFMIP    & atmosphere  &  10 years \\ \hline
 

### 2020-09-10 Silvers_WalkerCell_response2reviewers.tex
further modifications for the Walker Circulation paper in the files Silvers_WalkerCell_response2reviewers.tex Silvers_WalkerCell_revision.tex

@@
 Below please find my responses to your particular considerations.
+When referring to line numbers that were used in your revues I have done my best to use the same line numbers (those from the original submission) unless otherwise
+noted.
 Reviewer \#1 made additional comments in a pdf that was included with the review.
@@
 Also, I wonder to what extent the domain shape influences 
-  this result 
-  (the asymmetry is not present in P100L and less prominent in P25L)
+  this result (the asymmetry is not present in P100L and less prominent in P25L)
   \textcolor{red}{It should be pointed out that while the middle panel of Fig1 is symmetrical relative to the left panel, 
@@
 I wonder if just using a slightly different color for E25 and P25 would be better.
+\textcolor{red}{Figure 13 has been redone as a 2x2 panel figure using a different color for E25 instead of the triangles, larger axis labels, and clearer panel titles.}
 
@@
 Just trying to help you better convey the main points to the reader.
+  \textcolor{blue}{The last bullet point (Lines 592-594) of the first list has been removed.  I have also reorganized and combined the material that was 
+  formerly in sections 6 and 7 into one section with the hope of more clearly distinguishing between the summary of our results and the discussion points.
+Hopefully it is not as easy to get lost in the details now.}
   \textcolor{red}{I sympathize with you.
@@
 The somewhat inconsistent comparison between LWCRE-on and LWCRE-off experiments here is noteworthy, given that LWCRE is arguably the most important mechanism for maintenance of the aggregated state in non-rotating RCE studies.
+\textcolor{blue}{Good question.
+Once the experiments equilibrate the subsidence fraction (SF) is quite steady in time, despite rather large variability (on the order of 0.1-0.15).
+Variability increases with grid-spacing to the point that for P100 experiments averages must be taken over at least 3-5 months to obtain the long term mean SF.
+Figure \ref{fig:subsfracTS}  
+shows the subsidence fraction for the control (LWCRE-on) experiments.  The LWCRE-off cases are also very steady in time with a similar degree of variability.  The mean 
+differences of SF between the LWCRE on/off experiments are shown in an updated Table 2.  It should also be noted that SF in the case of the Walker 
+Circulation should be expected to be relatively large, and more consistent across experiments (relative to pure RCE) because of the prescribed SST warm 
+patch that will largely fix the location of deep convection to the middle of the domain and force an overturning circulation.  
+The values used in Table 2 for the originally submitted manuscript were computed 
+using the time averaged mid-tropospheric vertical velocity because I had neglected to save vertical velocity at a daily frequency.  However, I have since 
+found that the daily vertical pressure velocity (omega) was saved on the 500 hPa pressure level.  I have recomputed the SF values using these omega values
+and updated Table 2 (caption has been updated).
+The SF values now consistently show that the LWCRE-off experiments have a lower SF, the values are more consistent across experiments, and the surprisingly large difference between the LWCRE off/on experiments for the P100 large domain experiments is reduced to a value of 0.1.
+I have deleted 'with the exception of E25' from Line 332 of the submitted manuscript.}
+
+\begin{figure}
+  \centering
+    \includegraphics[width=0.8\columnwidth]{walkerfigs/SubsFrac_TS.eps}  
+  \caption{Subsidence Fraction over the first two years of simulation (E1 and E2 only extend for 6 months.).  Values computed from the pressure 
+  velocity on the 500 mb pressure surface.}
+  \label{fig:subsfracTS}
+\end{figure}
 
@@
 Apologies if this is something that has already been addressed elsewhere in the manuscript.
-  \textcolor{red}{For the figures which show profiles from the 'subsidence' regions, those regions are defined as the quarter of the domain furthest from the SST maximum, or the two sections, each an eighth of the domain width, which are at the outer edges of the domain.
-I played around with this a bit, especially because the asymmetry in some of the runs can complicate things.
-But defining the subsidence region as only a quarter of the domain instead of, say, half of the domain, minimizes the influence of asymmetry.}
+  \textcolor{blue}{Subsidence regions are defined as the quarter of the domain furthest from the SST 
+  maximum.  In other words, the two sections, each an eighth of the domain width, which are at the outer edges of the domain.  I played around with this a bit, 
+  especially because the asymmetry in some of the runs can complicate things.  But defining the subsidence region as only a quarter of the domain instead of, 
+  say, half of the domain, minimizes the influence of asymmetry.  This method for defining the subsidence region is systematic across all experiments and while 
+  there are some grid points with subsidence that are not included, the subsidence regions do not include grid-points with ascent.}
 
@@
 place, even if the manuscript’s results confirm the importance of this experiment a posteriori.
+\textcolor{blue}{Good question.  It is possible with this configuration to repeat experiments in which the SWCRE is turned off/on.  
+We are using a very similar physics code as that used by \textit{Popp \& Silvers, 2017, J. of Clim.}.   However, we have chosen to limit ourselves in this case to the 
+LWCRE experiments for several reasons, the foremost being practicality.  As you know, the current study varies LWCRE, resolution, domain size, and 
+the convective parameterization.  As a result, organizing the current range of results is already a challenge and we chose not to 
+expand the study further.  I have no doubt that the impact of the SWCRE on the coupling between the LS circulation and clouds will lead 
+to more insight and I hope that it will be investigated in future studies.  Additional reasons for focusing our study on the LWCRE on/off experiments
+are as follow.  First, this provides a clean overlap with CFMIP experiments which emphasize LWCRE over the SWCRE due to the complicating impacts of
+SWCRE on the surface energy budget.  Second, there are numerous studies which have shown that the atmospheric shortwave heating is 
+much smaller than the longwave heating (e.g. Perdergrass \& Hartmann, 2014; Popp \& Silvers, 2017 (their Figures 1 \& 4)).}
 \textcolor{red}{This response should lean heavily on Popp and Silvers.
 It should additionally emphasize the many directions which the paper already hints at due the large amount of experiments that are being compared, domain size differences,
-parameterization differences, resolution differences, and the LWCRE differences.  Adding another tier of simulations would 
-be risky...}
+parameterization differences, resolution differences, and the LWCRE differences.}
+\textcolor{blue}{draft of additions: Both the shortwave and longwave radiation influence the atmospheric radiative heating.  We have chosen to focus on 
+the LWCRE because it is by far the dominant contributor to atmospheric radiative heating.
+In order to present a relatively simple analysis of the cloud radiative effect we have chosen to explore LWCRE on/off experiments but not SWCRE on/off 
+experiments.  }
 \end{itemize}

### 2020-09-10 Silvers_WalkerCell_revision.tex
further modifications for the Walker Circulation paper in the files Silvers_WalkerCell_response2reviewers.tex Silvers_WalkerCell_revision.tex

@@
 ($\overline{\rm{OLR}}$), precipitable water ($\overline{\rm{PW}}$), and subsidence fraction (SF)  
-or fraction of domain that is subsiding at the 532 hPa level.
+or fraction of domain that is subsiding at the \change[LGS]{532}{500} hPa level.
 Values in parenthesis correspond to LWCRE-off experiments.}
@@
  Name &   $\overline{\rm{P}} (\mathrm{mm \,d^{-1}})$ & $\overline{\rm{OLR}} (\rm{W \, m^{-2}})$ & $\overline{\rm{PW}} (\rm{mm})$ & SF   \\ \hline
-  P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.89 (0.61)      \\ 
-    \\
-  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.74 (0.73)           \\  
-    \\
-  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.78 (0.70)          \\  
-    \\
-  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.80 (0.74)          \\  
-    \\
- E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & 0.72 (0.75)            \\  
-    \\
- E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.82 (0.75)           \\ 
-    \\
- E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.80 (0.80)         \\  \hline
+  P100L   &  4.1 (3.5)   &  283.1 (286.9)  & 36.6 (31.3)  & 0.82 (0.72)      \\ 
+    \\
+  P100 &   3.9 (3.7)   &  283.2 (296.4)  & 28.0 (26.8) & 0.74 (0.74)           \\  
+    \\
+  P25L &   4.0 (3.8)  &  281.2 (290.7)   & 35.0 (32.9) & 0.81 (0.78)          \\  
+    \\
+  P25  &   3.8 (3.7)    & 282.9 (293.6)   & 27.4 (26.4) & 0.82 (0.80)          \\  
+    \\
+ E25  & 3.7 (3.5)    &   271.9 (286.8)   & 28.7 (27.3) & 0.82 (0.81)            \\  
+    \\
+ E2   &  3.1 (3.4)   &  266.2 (285.5)    & 27.0 (25.2) & 0.86 (0.81)           \\ 
+    \\
+ E1   &  3.3 (3.7)   &  269.3 (289.2)    & 27.3 (26.5) & 0.82 (0.79)         \\  \hline
 
@@
       \includegraphics[width=0.8\columnwidth]{walkerfigs/DomMnPrecip.eps}
-  \caption{Domain mean precipitation as a function of time.  All data have been smoothed twice with a 9-day running mean filter.  
+  \caption{Domain mean precipitation as a function of time.
   Solid lines are the control experiments, dashed lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 experiments
-  while for P25 and P100 only the first two out of five years is shown.
-The dots at far right show the time mean values for the last 4 years (P25, P100) and last 5 months (E1, E2).
-Filled (hollow) dots show values from control (LWCRE-off) experiments.
-}
+  while for P25 and P100 only the first two out of five years is shown.  The dots (control) and diamonds (LWCRE-off) at far right show the time 
+  mean values of precipitation for the 
+  last 4 years (P25, P100) and last 5 months (E1, E2).  The mean values are also given in the legend. 
+  All data have been smoothed twice with a 9-day running mean filter.  }
     \label{fig:precip_dom_mn}
@@
 This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
-or equal to the case with LWCRE-off (with the exception of E25).   
+or equal to the case with LWCRE-off \remove[LGS]{(with the exception of E25)}.   
 While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
@@
   \centering       
-    \includegraphics[width=0.96\columnwidth]{walkerfigs/lowlevel_New.eps}
+    \includegraphics[width=0.96\columnwidth]{walkerfigs/lowlevel_New_b.eps}
     \caption{Low-level structure and domain mean wind shear for simulations with explicit convection.  
-    The surface enthalpy flux (a) is the latent plus sensible heat flux.  Panels b and c show 
-    the equivalent potential temperature (b) and zonal wind (c) at the lowest model level in the atmosphere.  Panel 
+    The surface enthalpy flux (a) is the latent plus sensible heat flux.  Also shown are the  
+    equivalent potential temperature (b) and zonal wind (c) at the lowest model level in the atmosphere.  Panel 
     d shows the domain mean zonal wind throughout the depth of the domain.}
@@
   \centering
-      \includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
-  \caption{Cloud fraction (CF) and temperature tendency due to longwave radiation (tdtlw).  Profiles were computed in the 
-  subsidence regions and are shown for the control (LWCRE-on) and LWCRE-off experiments.}
+      %\includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/CF_tdtlw_4pan_fig.eps}
+  \caption{Cloud fraction and temperature tendency due to longwave radiation in subsidence regions.  
+  Top panels (a. and b.) show results from the control experiments while lower panels (c. and d.) show the
+  analogous LWCRE-off experiments.  Note the change of axis in the lower panels.}
   \label{fig:cf_tdtlw}
@@
 \begin{itemize}
-  \item An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.
-  \item A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.
-  \item The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
-  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  
-  \item The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).
-  \item The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
-  (not shown) increases on the lowest atmospheric level.  
-  \item When convection is parameterized the total domain mean condensate increases at all heights 
-  (Figure \ref{fig:TotCond_P25P100}), in contrast to when the convection is explicit and 
-  the condensate aloft decreases (Figure \ref{fig:TotCond}).    
+  \item {An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.}
+  \item {A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.}
+  \item {The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
+  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  }
+  \item {The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).}
+  \item {The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
+  (not shown) increases on the lowest atmospheric level.  }
+ \item {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
+  (Figure 6), in contrast to when the convection is explicit and 
+  the condensate aloft decreases (Figure 11.}    }
 \end{itemize}

### 2020-09-11 Silvers_cfmip.tex
minor changes to the text related to the MISR results.

@@
 
-The MISR satellite provides good estimates of low-level cloud heights and amounts.  
+The MISR satellite provides good observations of low-level cloud heights and amounts.  
 For this reason and for comparison with both Kay et al., 2012, and Zhang et al., 2019 we compare the cloud fraction 
-between observations from MISR and the AM4.0 simulator output in Figure \ref{fig:cf_misr_lowcl}.  
+between observations from MISR and the AM4.0 simulator output for clouds below 3km in Figure \ref{fig:cf_misr_lowcl}.  
 The optical depth is used to distinguish between the thick and thin clouds.  
 Consistent with comparisons with ISCCP and CALIPSO we see that AM4.0 has fewer clouds than observed.
-AM4.0 produces the observed pattern of thick clouds, except in the tropical Indian Ocean, with a 
-bias of -5\% for low, thick clouds.  
-The pattern of thin clouds is not reproduced as well, particularly in the southern hemisphere tropics
-and has a bias of -16\%.
-
-The distribution of clouds can also be divided into different cloud types based on the height of the cloud and
+For thick low-level clouds the negative cloud fraction bias is about 14\%, and 12\% for thin clouds.   
+For thick clouds AM4.0 does reasonably well producing the observed spatial distribution of clouds, except in the tropical Indian Ocean. 
+The pattern of thin clouds is not reproduced as well, particularly in the southern hemisphere and the tropics.
+
+The MISR observations also allow the distribution of clouds to be divided into different cloud types based on the height of the cloud and
 the optical thickness to create a joint histogram.  
@@
 
-\section{The Role of Clouds in CM4.0, AM4.0, and Aquaplanets in Determining and Influencing Climate Sensitivity}
+\section{The Role of Clouds in CM4.0, AM4.0, and the AM4.0 Aquaplanet in Determining and Influencing Climate Sensitivity}
 
@@
 
-Over the recent decades which have had excellent/global satellite coverage both amip and historical experiments significantly underestimate (10-15\%)
-the observed cloud fraction.  This is especially true for low-level, optically thin clouds between $pm 30$.  The comparison with observed TOA 
-radiative fluxes for AM4/CM4 is quite good, which combined with the under-estimate of cloud fraction implies the presence of the so-called
-'too few, too bright' cloud bias which was also present in CMIP3 and CMIP5 global climate models.
-
-What additional constraints can we recommend for GCMs?
-
-\textit{Numerous studies have documented the range of sensitivities among an ensemble of models from different
-generations of CMIP and from a wide range of modeling centers (e.g.
-Cess et al.
-1989, Andrews et al., 2012, Rinter et al., 2014, Zelinka et al., 2020).
-In contrast, this study focuses on several models from a single modeling center, all based on the same generation of code.
-By so doing we can more clearly attach the source of spread in the climate sensitivity not to
-differences in the microphysics or convection parameterizations but to differences in the geophysical configuration and to the responses of the clouds to different boundary 
-conditions... with less ambiguity.}
-
-We have identified/quantified the part of the climate feedback parameter in each experiment that is simply due to differences in the 
-geophysical configuration (e.g. presence of land, sea-ice, etc.).  In addition we illustrate the range of CRE feedbacks among the 
-experiments with AM4/CM4 and show how these CRE feedbacks vary as a function of latitude.  Overall the SH emerges as a  primary 
-region of differences in cloud responses to warming.  In addition, the NH midlatitudes reveal a substantial decrease of cloud cover and 
-subsequent positive shift of the SW CRE in the experiments which are most sensitive to CO2 perturbations (abrupt 4xCO2 and 1pct CO2).
-
+We have shown that the recent generation of GFDL models performs well as measured by the observed TOA radiative fluxes of energy.
+However, there is also a substantial global mean negative cloud bias (10-15\%) in AM4.0 and CM4.0 (Figure 1).  This combination of a small 
+bias in the TOA 
+energy flux and a large negative cloud fraction bias indicates the continued presence of the so-called `too few, too bright' issue with 
+simulated clouds (Webb et al., 2001; Nam et al., 2013).  AM4.0 produces more thick (optical depth $> 3.6$) clouds below 2km in the 
+southern hemisphere ($30-60^{\circ}$) and more clouds than observed globally when the optical depth is greater than about 23 (Figures 3, A2).   
+The negative cloud fraction bias is largest in thin, low-level clouds between $\pm 30^{\circ}$ (Figure 4).   
+We also find little difference of the cloud fraction bias 
+as a function of latitude between the atmosphere only model AM4.0 and CM4.0, in which AM4.0 is coupled to a fully dynamic ocean (Figure 5).
+
+We have also demonstrated that a large part of the range in the climate feedback parameter ($\alpha$ varies between 
+-0.55 and -1.84 $\rm{W m}^{-2} K^{-1}$) of CMIP6 experiments performed with AM4.0 and CM4.0
+derives from the range of the cloud radiative effect (Net CRE varies between -0.46 and 0.62 $\rm{W m}^{-2} K^{-1}$).  This is true for the recent decades which overlap with the observational period
+discussed in the first part of the paper.  But the influence of CRE on the range of climate sensitivity values is also shown to be large for the 
+measures of future sensitivity such as the TCR and ECS.  Further, we show how much the CRE, and consequently the ECS or CS, vary as a result 
+of the method of computation used.  
 It is well known that the precise value of climate sensitivity is sensitive to the method of calculation.  Table 2 highlights how much the 
@@
 
+We have noted the part of the climate feedback parameter in each experiment that is simply due to differences in the 
+geophysical configuration (e.g. presence of land, sea-ice, etc.).  
+The clouds in these simulations respond to a variety of different conditions including different
+patterns of SST, the presence or absence of land or sea ice, and in the case of the aquaplanet
+experiments, a lack of cloud-aerosol interactions which are present in the AGCM (AM4.0) and coupled 
+experiments (AOGCM; CM4.0).  Differences in the experimental configuration such as the presence of land or sea ice, and 
+the prognostic nature of the sea ice are reflected in the SW CLR radiative fluxes.
+
+In addition we illustrate the range of CRE feedbacks among the 
+experiments with AM4/CM4 and show how these CRE feedbacks vary as a function of latitude and height.  
+Overall the SH emerges as a  primary 
+region of differences in cloud responses to warming.  In addition, the NH midlatitudes reveal a substantial decrease of cloud cover and 
+subsequent positive shift of the SW CRE in the experiments with increased $CO_2$ concentrations (\textit{abrupt-4xCO2} and \textit{1pctCO2}).
+
+This work then lends support to the need to clarifying and better constrain present day cloud feedbacks and simulations.  It would seem that 
+determining the correct degree of influence of the CRE on future estimates of CS depends on also clarifying the role and improving the 
+simulation of clouds in the present day climate (Webb et al., 2001 basically said this).
+What additional constraints can we recommend for GCMs?   Does this study suggest priorities for future research?
+Can/should we say that reducing the observational cloud bias
+should be at least as much of a priority in future development as reducing the spread of cloud feedbacks among
+models?
+
 One motivation for this paper is to compare the GFDL output of cloud fraction to the recent data sets from satellites.  An additional 
@@
 
-Probably have to cite Armour, 2017.
+%Probably have to cite Armour, 2017.
 He does put the time varying sensitivity in context, and discusses the use of the energy budget constraints.
@@
 
-\textit{We should probably mention that we have used the CALIPSO simulator to predict cloud changes in the future...}
-
 Comparison with multiple observational datasets has shown that the negative cloud bias
@@
 cloud radiative effects across multiple experiments reveals that the differences in cloud fields that 
-contribute to different sensitivities are in the mid and high latitude regions.  If the bias in 
+contribute to different sensitivities are in the mid and high latitude regions.  One of the benefits of comparing 
+our recent models to observations is that several questions are raised.  For example, if the bias in 
 the tropical regions was remedied would the differences in cloud fields that are important for sensitivity
@@
 
-\textit{The clouds in these simulations respond to a variety of different conditions including different
-patterns of SST, the presence or absence of land or sea ice, and in the case of the aquaplanet
-experiments, a lack of cloud-aerosol interactions which are present in the AGCM (AM4.0) and coupled 
-experiments (AOGCM; CM4.0).  }
-
-\textit{Put the results of AM4.0/CM4.0 in the context of other modeling studies.  The AR5, chapter 7 describes the primary 
+\textit{Numerous studies have documented the range of sensitivities among an ensemble of models from different
+generations of CMIP and from a wide range of modeling centers (e.g. Cess et al. 1989, Andrews et al., 2012, Ringer et al., 2014, Zelinka et al., 2020).  
+In contrast, this study focuses on several models from a single modeling center, all based on the same generation of code.
+By so doing we can more clearly attach the source of spread in the climate sensitivity not to
+differences in the microphysics or convection parameterizations among different models but to differences in the geophysical configuration and to the 
+responses of the clouds to different boundary conditions.}
+
+\textit{Put the results of AM4.0/CM4.0 in the context of other modeling studies.}  
+The AR5, chapter 7 describes the primary 
 cloud feedbacks that are thought to be relevant for future warming.
@@
 2011 and Vavrus et al.
-(2009 or 2011)}
+(2009 or 2011)?
 
 We have shown that the cloud radiative effect makes up a significant part of the difference 
-among models in the climate feedback parameter.  These differences in the cloud radiative
-effect are clearly connected to differences in the simulated cloud fraction.  
+among AM4.0 and CM4.0 experiments in the climate feedback parameter.  These differences in the cloud radiative
+effect are clearly connected to differences in the simulated cloud fraction (how?).  
 % For example, when comparing the amip-p4K and amip-future4K experiment (Figure 9) we see a SH cloud fraction 
@@
 All of the experiments examined show cloud biases relative to observations that are larger than the differences of cloud fraction among the experiments.    
-A substantial portion (quantify) of the range in CS among the AM4/CM4 experiments examined here is due to 
-driven by a range in the CRE.  However, the differences in cloud fraction among the experiments is smaller than 
-the bias of the recent decades relative to observations.  Can we say that reducing the observational cloud bias
-should be at least as much of a priority in future development as reducing the spread of cloud feedbacks among
-models?
+A substantial portion (quantify) of the range in CS among the AM4/CM4 experiments examined here is 
+driven by a range in the CRE.  However, the differences in cloud fraction among the experiments are smaller than 
+the bias of the recent decades relative to observations.
 
@@
 
-Citations to add: 
-Klein et al. (probably should cite multiple works)
-Caldwell et al., 2016
-Webb et al., 2013
-Andrews et al., 2015
-Vignesh et al 2020?    Assessment of CMIP6 cloud fraction and comparison with satellite observations
+%Citations to add: 
+%Klein et al. (probably should cite multiple works)
+%Caldwell et al., 2016
+%Webb et al., 2013
+%Andrews et al., 2015
+%Vignesh et al 2020?    Assessment of CMIP6 cloud fraction and comparison with satellite observations
 
@@
   were derived with the MISR simulator (amip experiment).}
-  \label{fig:cf_misr_lowcl}
+  \label{fig:cf_misr_vsHeight}
 \end{figure}
@@
   were derived with the MISR simulator (amip experiment).}
-  \label{fig:cf_misr_lowcl}
+  \label{fig:cf_misr_vsTau}
 \end{figure}

### 2020-09-11 Silvers_WalkerCell_revision.tex
further changes to Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex in the revisions of the WalkerCirculation paper.  This commit is just before I attempt to break section 3 into two subsections.

@@
 \usepackage{lineno}
-\usepackage[inline]{trackchanges} %for better track changes. finalnew option will compile document with changes incorporated.
+\usepackage[inline]{trackchanges}        % for track changes. finalnew option will compile document with changes incorporated.
 %\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
@@
   (not shown) increases on the lowest atmospheric level.  }
- \item {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
+ {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
   (Figure 6), in contrast to when the convection is explicit and 

### 2020-09-18 Silvers_WalkerCell_response2reviewers.tex
further changes to Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex in the revisions of the WalkerCirculation paper.  This commit is just before I attempt to break section 3 into two subsections.
substantial additions to both Silvers_WalkerCell_response2reviewers.tex and Silvers_WalkerCell_revision.tex as part of the revisions for Silvers and Robinson, 2020

@@
 
+   \textcolor{blue}{We have taken your advice, mostly by moving the content from the former second to last sentence in the abstract to earlier in the abstract and rewriting lines 27-28 of 
+   the originally submitted manuscript.}
+
 \item Ln 67-68:  The Walker circulation itself is not really a framework, and comparing it to observations does not really follow since it occurs in reality.
@@
   \item Ln 310: I only see prominent asymmetry in the P25 simulations. The P100 simulation is only slightly asymmetric, and the P100L simulation not asymmetric at all.
+  \textcolor{red}{The language describing this has been changed to reflect off center features, rather than just asymmetric.  Please see the discussion in the subsection which discussed 
+  the comparison between P25 and E25.   While P100 is only slightly asymmetric, it is 
+  consistently off center.  The asymmetry of P25L is greater than may be initially apparent because of the difference in domain size.  A similar asymmetry to the P25 case would 
+  be shown with a shift off-center that appears smaller than for P25 (see Figs 5 and 8 of revised manuscript).  }
 
@@
 The low-cloud fraction seems quite small in the CRM-like experiments...
-  \textcolor{red}{This comment overlaps with the desire from reviewer \# 3 (section 4.1.3 of their review).  Would a plot of MISR observations from the tropical Pacific work well?  }
+  \textcolor{blue}{I have added a new figure that looks at observations from the tropical Pacific in order to give a sense of how these model results compare to observations.  
+  Figure 15 shows cloud fraction from the MISR instrument on board NASA's Terra satellite.
+I focused on a region that is usually identified with the Walker Circulation and plotted profiles for the domain mean, a region with upwelling, and a region with downwelling.
+If comparing to figure 14 in our manuscript in which we look at the cloud fraction in the subsidence
+  region it is seen that both the upper-level and low-level cloud fraction observed by MISR in the downwelling region is closer to that of the GCM-like simulations.  This is 
+  somewhat surprising but it should be kept in mind that this type of comparison is very qualitative and subject to numerous caveats.  For example, impacts from the Hadley cell 
+  have not been filtered out of this observational data.  I am hopefully that a quick look at data like this could help to motivate future studies in which a more detailed comparison 
+  between models of the Walker Circulation and observations.  The following red text has been added to the manuscript:}
+
+  \textcolor{red}{In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative study we look at the clouds observed with the MISR instrument 
+  on board NASA's Terra satellite.  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the regional Walker circulation in the Pacific.  
+  The left panel of Figure 15 shows the cloud fraction averaged from March 2000-November 2019 of the full domain of the Pacific regional Walker circulation.  This region 
+  includes much of the so-called warm pool beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the stratocumulus
+  cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a function of height we sum the MISR data over all optical depths 
+  and plot the domain mean (dashed line), a region of subsidence ($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a regions that is characterized by deep 
+  convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction from MISR are closer to the cloud profiles 
+  simulated by the GCM-like models.  It would be interesting in future studies to sample the observations for time periods in which the Walker Circulation is strong}
 
@@
 I think this should be rephrased to reflect that.
+  \textcolor{blue}{This sentence now reads: Two examples include the consistently off-center circulations, and precipitation patterns,
+relative to the fixed SST pattern, and the dominance of the large-scale precipitation over the convective precipitation.}
 %
@@
   \item Section 3 is meant to focus on the impact of LWCRE, but subsequent sections frequently reference the comparison between LWCRE-on and LWCRE-off as well (i.e. lines 361-373, 398-401, 459-462).
-  \textcolor{red}{During the writing I attempted consolidating the comparison between LWCRE on/off to one section but found it to create more problems than it solved because the LWCRE on/off experiments have such a strong influence on all of the other sections.
+  \textcolor{red}{During the writing I attempted consolidating the comparison between LWCRE on/off to one section but found it to create more problems than it 
+  solved because the LWCRE on/off experiments have such a strong influence on all of the other sections.  You mention lines 361-373, which happens to be a 
+  perfect example of the difficult.  Figures 5 and 6 illustrate the overlapping influence of the LWCRE on/off effects and domain size dependence.  
   As a result, I have chosen to largely focus on your other excellent recommendations for reworking the organization of the manuscript.}
@@
 For example, Figure 2's legend can list the domain-mean precipitation values next to the labels.
+  \textcolor{red}{I have added domain-mean values to the precipitation shown in Figure 3, and extended the markers at the end of the time series to make Figure 3 easier to read.  
+  In response to several comments from you and the other reviewers, section 3, 6, and 7 have been somewhat reorganized and hopefully make the manuscript easier to read.}
 \end{enumerate}
@@
 Another factor which limited the number of experiments that I could include in the paper is that I also performed a number of uninteresting or unsuccessful experiments in which various parameter settings were modified, and in which some minor changes were made in the code of the Tiedtke large scale cloud scheme.
-I was already dealing with too many experiments.
+I have more experiments than I can handle!
 }
@@
 Figure 13 would be best oriented as a 2X2 window similar to Figure 12, especially given the subtle differences in the rightmost panel.
-  \textcolor{red}{For several of the figures (6, 11,12, and 13) the labels and axis font size has been increased.  Figure 6 has now been split into two figures, one
+  \textcolor{red}{For several of the figures (6, 11,12, and 13) the labels and axis font size has been increased.}  
+  \textcolor{blue}{Figure 6 has now been split into two figures, one
   showing results on the small/control domain size and the other showing results on the large domain.}
@@
   \item Labeling all figure panels using the conventional notation a/b/c/d (e.g. Figure 1, 2, etc.)
+  \textcolor{blue}{Figures 1-14 now have panels labelled with a/b etc., when multiple panels are present.}
+
   \item Make titles more formal (e.g. Figure 13) and using a consistently large font size across figures (for instance, the
 titles are easy to read in Figures 9 and 10, but not in Figures 11, 12, and 13)
-
   \textcolor{blue}{The font size for axis and titles in Figure 12 has been increased, x-axis label for Figure 12d corrected to read only units.}

### 2020-09-18 Silvers_WalkerCell_revision.tex
substantial additions to both Silvers_WalkerCell_response2reviewers.tex and Silvers_WalkerCell_revision.tex as part of the revisions for Silvers and Robinson, 2020

@@
 Our model is derived from the Geophysical Fluid Dynamics Laboratory (GFDL) atmospheric GCM (AM4.0).
-Our GCM-like experiments have a large low-level cloud fraction while the CRM-like experiments have more upper-level clouds.
-This difference leads to opposite atmospheric responses to changes in the longwave cloud radiative effect (LWCRE).
+\change[LGS]{Our GCM-like experiments have a large low-level cloud fraction while the CRM-like experiments have more upper-level clouds.}{We find substantial differences in the mock-Walker simulated by our GCM-like and CRM-like experiments.
+The CRM-like experiments have more upper level clouds, stronger overturning circulations, and more precipitation.
+The GCM-like experiments have a low-level cloud fraction that is up to 20\% larger.}
+These differences lead to opposite atmospheric responses to changes in the longwave cloud radiative effect (LWCRE).
 Active LWCRE lead to increased precipitation for our GCMs, but decreased precipitation for our CRMs.
 The LWCRE leads to a narrower rising branch of the circulation and substantially increases the fraction of precipitation from the large-scale cloud parameterization.
-Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less precipitation.
-This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.
+\remove[LGS]{Decreasing the grid-spacing to 1km and 2km results in stronger overturning circulations, more condensate aloft, and less precipitation.}  This work demonstrates that a mock-Walker circulation is a useful generalization of RCE that includes a large-scale circulation.
+
+%We find substantial differences in the mock-Walker simulated by our GCM-like and CRM-like experiments.
+The CRM-like experiments have more upper level clouds, stronger overturning circulations, and more precipitation.
+The GCM-like experiments have a low-level cloud fraction that is up to 20\% larger.
 
@@
 
+\subsection{\add[LGS]{General Characteristics of the mock-WalkerCirculation}}
+
 The mock-Walker Circulation that emerges from these simulations is shown in Figures \ref{fig:rh_psi_P25vsE25} and 
@@
 LW radiation, the atmospheric state is more symmetric about the maximum SST and the weaker circulation
-is more spread out horizontally.   The mass streamfunction and vertical velocity both show the 
-P25 (Figure \ref{fig:rh_psi_P25vsE25}, left panels; Figure \ref{fig:precip_vertvel}) experiment to have 
-a stronger, more concentrated overturning circulation than either E25 (right panels) or P25 LWCRE-off (center panels).   
-The control GCM\add[LGS]{-like} experiment (P25) also has higher RH and more condensate in the convective
+is more spread out horizontally.   
+\note[LGS]{The following lines, which appear to have been deleted have been moved to subsection 3.2 and 
+slightly rewritten for clarity.}
+\remove[LGS]{The mass streamfunction and vertical velocity both show the 
+P25 (Figure }\ref{fig:rh_psi_P25vsE25}, 
+\change[LGS]{left panels}{a,d}; Figure \ref{fig:precip_vertvel})
+\remove[LGS]{ experiment to have 
+a stronger, more concentrated overturning circulation than either the P25 LWCRE-off (Figure} 
+\ref{fig:rh_psi_P25vsE25} 
+\remove[LGS]{b,e) or E25 (Figure} 
+\ref{fig:rh_psi_P25vsE25} 
+\remove[LGS]{c,f) experiments.   
+The control GCM-like experiment (P25) also has higher RH and more condensate in the convective
 region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
-Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate (both liquid and ice). 
-This default configuration in which the clouds interact with the LW radiation results in a stronger,
+Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate (both liquid and ice).}
+\change[LGS]{This}{The} default configuration in which the clouds interact with the LW radiation results in a stronger,
 spatially concentrated circulation and will be discussed further in later sections (also seen Figures 4, 5, 9 and 10).
 Active LWCRE leads to lower values of domain mean OLR and higher domain mean precipitable water (PW) in all cases (Table \ref{tab:experimentmeans}).
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.8\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
+  \caption{Precipitation (a.,b.) and vertical velocity (c.,d.) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
+  The data have been averaged over the short horizontal dimension of the channel and over the 
+  equilibrated part of the experiments.  Panels a. and b. show the control configurations with default model physics. 
+  Panels b. and d. show the corresponding experiments with the longwave cloud radiative effect turned
+  off (LWCRE-off).}
+  \label{fig:precip_vertvel}
+\end{figure}
 
@@
 
-One of the most prominent features of our GCM-like simulations is an asymmetry (relative to the 
-symmetric SST distribution) in both the time-dependent and steady-state solutions.  
-This asymmetry is particularly apparent in the P25 experiment on the small domain but is also present on larger domains and 
+\begin{figure}
+  \centering
+      %\includegraphics[width=0.8\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
+      \includegraphics[width=0.8\columnwidth]{walkerfigs/DomMnPrecip.eps}
+  \caption{Domain mean precipitation as a function of time.
+  Solid lines are the control experiments, dashed lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 experiments
+  while for P25 and P100 only the first two out of five years is shown.  The dots (control) and diamonds (LWCRE-off) at far right show the time 
+  mean values of precipitation for the 
+  last 4 years (P25, P100) and last 5 months (E1, E2).  The mean values are also given in the legend. 
+  All data have been smoothed twice with a 9-day running mean filter.  }
+    \label{fig:precip_dom_mn}
+\end{figure}
+
+\note[LGS]{This paragraph was originally on lines 326-343 but has been moved to accommodate the reorganization of section 3.}
+One of the simplest measures of convective aggregation and the large-scale circulation is the subsidence fraction (SF), the fraction of the domain 
+in which the mid-tropospheric air is subsiding \cite{Coppin_Bony_2015}.  
+As convection becomes more organized, or aggregated, the SF will increase.  For an overturning circulation a contraction of the convective 
+region should result in a larger subsidence fraction.  
+This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
+or equal to the case with LWCRE-off \remove[LGS]{(with the exception of E25)}.   
+While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
+region of persistent deep convection clearly corresponds to a state of aggregation. 
+Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
+Previous studies have shown a dependence of aggregation 
+on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
+state can vary among experiments with identical SST.  Having a prescribed SST warm 
+patch ensures that the simulations will be `aggregated' to some degree.  
+Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
+convection, radiation, and the large-scale circulation.
+
+\subsection{\add[LGS]{Comparison of Experiments with Parameterized or Explicit Convection}}
+
+Before analyzing the CRM-like experiments E1 and E2 in which there is no parameterized convection we examine the influence of 
+the double plume convective parameterization in the P25 and P100 experiments.  The E25 experiment, identical to P25 except with 
+fully explicit convection, then can serve as a link between the GCM-like experiments and the CRM-like experiments.
+
+The mass streamfunction and vertical velocity both show the P25 (Figure \ref{fig:rh_psi_P25vsE25}, a,d; Figure \ref{fig:precip_vertvel}) experiment to have 
+a stronger, more concentrated overturning circulation than either the P25 LWCRE-off (Figure \ref{fig:rh_psi_P25vsE25} b,e) or E25 (Figure 
+\ref{fig:rh_psi_P25vsE25} c,f) experiments.   The control GCM-like experiment (P25) also has larger values of RH and more condensate in the convective
+region and a dryer subsidence region, relative to the P25 LWCRE-off and E25 experiments. 
+Averaged over the full domain, the P25 case with parameterized convection results in a dryer atmosphere with less condensate 
+(Figure \ref{fig:profiles_P100P25E25} a.,b.).  Mean relative humidity profiles from the regions with 
+mid-tropospheric subsidence (Figure \ref{fig:profiles_P100P25E25} a., dashed lines) further accentuate the dryness of P100 and P25 relative
+to E25.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.95\columnwidth]{walkerfigs/MeanStructure_P100P25E25.eps}
+  \caption{Domain mean vertical structure of the P100, P25, and E25 experiments.  The dashed lines of relative humidity (a.) show the values 
+  in the region with subsidence.  The positive heating profiles (d.) show the heating due to both convection and the large-scale cloud scheme, the negative
+  profiles show the sum of the heating due to longwave and shortwave radiation.  Panel e. shows the atmospheric temperature relative to the P100 experiment.}
+  \label{fig:profiles_P100P25E25}
+\end{figure}
+
+The influence of different grid-spacing, and convective parameterization can be seen in the vertical profiles of several key variables for 
+the P100, P25, and E25 experiments (Figure \ref{fig:profiles_P100P25E25} b.).  
+Overall the experiments with parameterized convection transport more moisture (both condensate and water vapor)
+out of the boundary layer and into the lower troposphere.  The parameterized experiments are also substantially warmer in the mid-troposphere compared to 
+the E25 experiment which is forced to transport all moisture and heat with explicit dynamical motions.  In contrast, near 900 hPa, the E25 experiment has nearly twice
+as much low-level condensate (Figure \ref{fig:profiles_P100P25E25} b.), a cloud fraction that is about 10 \% higher, larger condensational heating, and 
+stronger cloud-top radiative cooling.  It is also worth noting that the condensational heating above 850 hPa (Figure \ref{fig:profiles_P100P25E25} d.) is dominated by 
+the large-scale cloud scheme rather than the convective parameterization.  This is presumably because of the large-scale overturning circulation that is 
+being forced by the SST pattern.  Overturning circulations tend to trigger the large-scale cloud scheme.  The fraction of precipitation that is due to either 
+the large-scale or convective parameterizations will be discussed in the next section.
+
+Figure \ref{fig:rh_psi_P25vsE25} suggests that the strong asymmetries of the circulation, moisture fields, and precipitation in P25 could be eliminated 
+by either turning off the convective parematerization (E25) or by turning off the LWCRE.  Examining the evolving structure of the 
+precipitation (Hovm{\"o}ller diagrams) over the full 5 year simulations for P25, P25 LWCRE-off, E25, and E25 LWCRE-off offers more insight into the role of the convective parameterization and the CRE.
+
+While the P25 experiment shows a fairly consistent irregularity (a.), both the P25 LWCRE-off (b.) and the E25 experiments (c.) have distinct patterns that 
+can remain steady for years before changing.  In contrast to the precipitation structures in panels a,b, and c of Figure \ref{fig:hov_25km_4pan}, the E25 LWCRE-off experiment 
+shows (d.) a zipper-like structure of strong precipitation that persists throughout the entire 5 years of the experiment.
+
+%The patterns of precipitation in Figure \ref{fig:hov_25km_4pan} show an asymmetric and sporadic evolution in time as well as an oscillating pattern that is remarkably steady 
+%in time.
+
+\begin{figure}
+  \centering
+      \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_25km4pan_huge.eps}
+  \caption{Evolution of precipitation through 5 years of simulation for four experiments with a grid spacing of
+  25km.  Panel a shows the  control 25km experiment (P25); 
+  panel b, P25 with LWCRE turned off; panel c, both deep and shallow convective parameterization schemes are turned off (E25); 
+  and panel d shows the E25 experiment shown in panel c except with the LWCRE turned off.  
+  All cases have an SST of 301 K at the center and 297K at the edges.  
+  The plotted contour values are: 1,5,10,15,20,30,40,50,60,70,80,90.  Data have been averaged over the short horizontal dimension.}
+  \label{fig:hov_25km_4pan}
+\end{figure}
+
+% discussing the asymmetry of P25 could/should lead into a discussion of Figure \ref{fig:hov_25km_4pan}...
+
+One of the most prominent features of our GCM-like simulations is \change[LGS]{an asymmetry (relative to the 
+symmetric SST distribution) in both the time-dependent and steady-state solutions}{the erratic (relative to the symmetric SST distribution) 
+structure of the precipitation field}.  
+This \remove[LGS]{asymmetry} is particularly apparent in the P25 experiment on the small domain but is also present on larger domains and 
 with a grid-spacing of $100 \, \rm{km}$ (Figures  \ref{fig:precip_vertvel}, \ref{fig:domdep} and  \ref{fig:conv_vs_ls}). 
@@
 
-\begin{figure}
-  \centering
-      \includegraphics[width=0.8\columnwidth]{walkerfigs/PrecipVertVelocity_LWCRE_onoff.eps}
-  \caption{Precipitation (top) and vertical velocity (bottom) at approximately 530 hPa for P100, P25, E2, and E1 experiments.  
-  The data have been averaged over the short horizontal dimension of the channel and over the 
-  equilibrated part of the experiments.  Control configurations with default model physics are on the 
-  left.  On the right are the corresponding experiments with the longwave cloud radiative effect turned
-  off (LWCRE-off).}
-  \label{fig:precip_vertvel}
-\end{figure}
 %
@@
 %(0)	max/min of psiplot2 is: 0.4634904466711686 and: -0.3170573366946793               diff = 0.78
-
-\begin{figure}
-  \centering
-      %\includegraphics[width=0.8\columnwidth]{walkerfigs/Precip_DMN_4models_1yr.eps}
-      \includegraphics[width=0.8\columnwidth]{walkerfigs/DomMnPrecip.eps}
-  \caption{Domain mean precipitation as a function of time.
-  Solid lines are the control experiments, dashed lines show the LWCRE-off experiments.  All data is shown for the E1 and E2 experiments
-  while for P25 and P100 only the first two out of five years is shown.  The dots (control) and diamonds (LWCRE-off) at far right show the time 
-  mean values of precipitation for the 
-  last 4 years (P25, P100) and last 5 months (E1, E2).  The mean values are also given in the legend. 
-  All data have been smoothed twice with a 9-day running mean filter.  }
-    \label{fig:precip_dom_mn}
-\end{figure}
-
-One of the simplest measures of convective aggregation and the large-scale circulation is the subsidence fraction (SF), the fraction of the domain 
-in which the mid-tropospheric air is subsiding \cite{Coppin_Bony_2015}.  
-As convection becomes more organized, or aggregated, the SF will increase.  For an overturning circulation a contraction of the convective 
-region should result in a larger subsidence fraction.  
-This is precisely what we see in Table \ref{tab:experimentmeans}.  For each of our experiments with LWCRE-on the SF is larger than 
-or equal to the case with LWCRE-off \remove[LGS]{(with the exception of E25)}.   
-While our mock-Walker circulation is distinct from radiative convective equilibrium (RCE) and the resulting spontaneous self-aggregation, our 
-region of persistent deep convection clearly corresponds to a state of aggregation. 
-Using a mock-Walker circulation allows one to study controlled convective aggregation rather then spontaneous convective self-aggregation. 
-Previous studies have shown a dependence of aggregation 
-on temperature \cite{Khairoutdinov2010, Wing2014, Cronin2017}, Table \ref{tab:experimentmeans} illustrates how much the aggregated 
-state can vary among experiments with identical SST.  Having a prescribed SST warm 
-patch ensures that the simulations will be `aggregated' to some degree.  
-Given identical SSTs, the  range of different SFs provide a measure of variability that is driven entirely by the interactions between 
-convection, radiation, and the large-scale circulation.
 
@@
     \includegraphics[width=0.95\columnwidth]{walkerfigs/hov_precip_lwoff_huge.eps}
-  \caption{Identical to previous figure, except that the clouds do not interact with the longwave radiation; the LWCRE is off.}
+  \caption{Identical to Figure \ref{fig:domdep}, except that the clouds do not interact with the longwave radiation; the LWCRE is off.}
   \label{fig:domdep_lwoff}
@@
        \includegraphics[width=0.90\columnwidth]{DomainMeanCond_SinglePanel.pdf}
-          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) on the domain with a long dimension of 16,000km (a.)
-          and 4,000 km (b.).  P25 experiments are shown with yellow lines and P100 experiments with red.  Solid lines show 
+          \caption{Domain mean total condensate (liquid + ice; grams/kilogram) on the domain with a long dimension of 4,000km (a.)
+          and 16,000 km (b.).  P25 experiments are shown with yellow lines and P100 experiments with red.  Solid lines show 
           experiments with LWCRE on and dashed lines the LWCRE-off experiments.}
@@
 lower maximum precipitation rates.  
-Both the P25 and E25 simulations show more variability at later times compared to these 
-first 180 days (similar to what is seen in Figures \ref{fig:domdep}  and \ref{fig:domdep_lwoff} for the P25 and P100 LWCRE-off).  
+Note that both the P25 and E25 simulations show more variability at later times compared to these 
+first 180 days (see Figure \ref{fig:hov_25km_4pan} a and c.).  
 The simulations with explicit convection at resolutions typical of cloud-resolving models 
@@
 must come from a process other than condensation.
+
+\begin{figure}
+  \centering
+      %\includegraphics[width=0.96\columnwidth]{walkerfigs/CloudFractdtRad_lwcre.eps}
+      \includegraphics[width=0.96\columnwidth]{walkerfigs/Silvers_WalkerCell_MISR.pdf}
+  \caption{Observations of cloud fraction in the tropical Pacific from the MISR Satellite over the years 2000-2019. Panel on the right shows the cloud 
+  fraction as a function of height from a region dominated by subsidence (solid), the mean of the full domain shown in left panel 
+  (long dashes), and the mean from a region characterized by frequent deep convection (dash-dot).  The latitudinal extent follows that used by Schwendike 
+  et al., 2014 in their definition of the regional Walker circulation (see their figure 2).  }
+  \label{fig:cf_misr}
+\end{figure}
+%Silvers_WalkerCell_MISR.pdf
 
@@
 
-\section{Summary and Discussion}
-
-In summary, this section lists some of the main ways in which the LWCRE and the grid spacing influence
-the clouds, the circulation, and the energetics of the mock-Walker circulation.   
-%Some, but not all of these points have been noted by previous studies.   
-The impacts (relative to the LWCRE-off experiments) of the interaction between clouds and the longwave radiation 
-(LWCRE) include the following:
-
-\begin{itemize}
-  \item {An increase of $\overline{\rm{P}}$  for the P100,P25 and E25 experiments.}
-  \item {A decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.}
-  \item {The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
-  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  }
-  \item {The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).}
-  \item {The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
-  (not shown) increases on the lowest atmospheric level.  }
- {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
-  (Figure 6), in contrast to when the convection is explicit and 
-  the condensate aloft decreases (Figure 11.}    }
-\end{itemize}
-
+In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative study we look at the clouds observed with the MISR instrument 
+  on board NASA's Terra satellite.  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the regional Walker circulation in the Pacific.  
+  The left panel of Figure \ref{fig:cf_misr} shows the cloud fraction averaged from March 2000-November 2019 of the full domain of the Pacific regional Walker circulation.  This region 
+  includes much of the so-called warm pool beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the stratocumulus
+  cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a function of height we sum the MISR data over all optical depths 
+  and plot the domain mean (dashed line), a region of subsidence ($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a regions that is characterized by deep 
+  convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction from MISR are closer to the cloud profiles 
+  simulated by the GCM-like models.  It would be interesting in future studies to sample the observations for time periods in which the Walker Circulation is strong....
+
+\section{Conclusions and Discussion}
+
+\add[LGS]{In this section we conclude by summarizing the primary results of our study, followed by a brief discussion 
+of the proper context and implications of these results.}
+
+\subsection{Summary of Results}
+
+We have used the framework of the tropical overturning circulation, specifically the Walker Circulation, 
+to compare the multi-scale interactions between large-scale circulations, cloud systems, and interactive 
+radiation across experiments with grid-spacing ranging from 1km to 100km.   
+To better isolate the role that clouds and humidity play in driving and responding to the 
+circulation, experiments have been performed with and without the radiative effect of clouds, with and without the 
+convective parameterization, and with multiple domain sizes.  Our results show that 
+the convective parameterization and the longwave cloud radiative effect (LWCRE) strongly interact with each other and 
+often lead to asymmetric results and large differences in the equilibrated atmospheric state.
+
+Perhaps the most interesting result is that the GCM-like experiments have a relatively large low-level 
+cloud fraction while the CRM-like experiments have a large upper-level cloud fraction.  
+This difference in the dominant cloud type leads to opposite atmospheric responses to changes of the LWCRE.  
+The LWCRE increases the domain mean precipitation ($\overline{\rm{P}}$) for the GCMs but 
+decreases it for the CRMs (Table \ref{tab:experimentmeans}).  
+Over the regions with cooler SSTs the large low-level cloud fraction of the GCMs 
+acts as a source of radiative cooling that is balanced by condensational heating in the control case.  
+A strong decrease of low-level clouds in the GCMs
+for the LWCRE-off experiments removes this cooling and condensational heating.  The increase 
+of precipitation that is expected in the LWCRE-off case as a result of increased LW cooling to space is not enough
+to overcome the decreased condensational heating at low-levels, with a net effect of less $\overline{\rm{P}}$.  
+Over the regions with cooler SSTs, the CRMs have very few (less than \change[LGS]{\%5}{5\%}) low-level clouds and as a result the 
+change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
+\citeA{Watanabe_etal_2018} found a similar relationship between low-clouds and precipitation in the context \add[LGS]{of} climate 
+change experiments.  This highlights how sensitive the energetics of the tropical atmosphere are to the distribution of clouds and 
+their interaction with the radiation.
+
+Decreasing the grid-spacing from $100 \textrm{km}$ to 1km allowed for the parameterization of both deep and shallow 
+convection to be turned off, resulting in a more direct simulation of the dynamics that are
+fundamental to the overturning tropical circulation.  
 Relative to simulations with a grid-spacing of $100 \textrm{km}$ and $25 \textrm{km}$, the $1 \textrm{km}$ and 
@@
 \begin{itemize}
-  \item Overturning circulations (as measured by vertical velocity) are stronger and more consistently centered 
+  \item Overturning circulations are stronger and more consistently centered 
   over the maximum of SST (Figure \ref{fig:precip_vertvel}).  
@@
   \item Above about 600 hPa there is two to four times more ice condensate, but less than half as much liquid condensate below 700 hPa (Figure \ref{fig:TotCond}).
-  \item There is less $\overline{\rm{P}}$ in the E1 and E2 experiments (Table \ref{tab:experimentmeans}).  Values for 1 and 2 km simulations are in the 3.1-3.7 mm/d range, while those 
-  for the $100 \textrm{km}$ and $25 \textrm{km}$ experiments are about 10-25\% higher (3.5-4.1 mm/d).  
+  \item The E1 and E2 experiments have about 10-25\% less $\overline{\rm{P}}$ (3.1-3.7 mm/d) compared to
+  P25 and P100 (3.5-4.1 mm/d).  See Table \ref{tab:experimentmeans}.  
 \end{itemize}
+%The resulting atmospheric state has a stronger overturning 
+%circulation, a much more humid (up to 50\% higher RH) deep convective region, and less $\overline{\rm{P}}$ .  
+%Relative to the GCM-like simulations the 1 and 2km simulations have two to four times as much condensate
+%aloft but only about half as much below 700 hPa.  The increase of vertical moisture transport with increasing 
+%resolution is particularly apparent in the LWCRE-off experiments (Figure \ref{fig:rh_psi_P25E2E1_lwoff}, lower panels).
+
+Three striking changes occur as a result of a four-fold increase in domain width.  The low-level clouds shift 
+upward by more than 100 hPa (Figure 6), there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments 
+(compare Figures 4 and Figure 5),  
+and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation (Figure \ref{fig:conv_vs_ls}).    
+This impact on the large-scale precipitation occurs for the GCM-like experiments on smaller domains as well, 
+but is pronounced in the large domain experiments.  
+This dependence on domain size could imply that 4000 km is not large enough to contain the largest 
+scales that are important for the overturning circulation.  Another reason for the domain 
+size dependence could be the changing scale of the warm and cold regions of SST.
 
@@
 sensitivity \cite{Silvers_etal_2016}.
+
+In summary, this section lists some of the main ways in which the LWCRE and the grid spacing influence
+the clouds, the circulation, and the energetics of the mock-Walker circulation.   
+%Some, but not all of these points have been noted by previous studies.   
+The impacts (relative to the LWCRE-off experiments) of the interaction between clouds and the longwave radiation 
+(LWCRE) include the following:
+
+\begin{itemize}
+  \item {An increase of $\overline{\rm{P}}$  for P100,P25 and E25 experiments but a decrease of $\overline{\rm{P}}$  for the E1 and E2 experiments.}
+  \item {The horizontally oriented low-level circulations strengthen, and the regions of high precipitation are more concentrated  
+  in geographic space (Figures \ref{fig:rh_psi_P25vsE25}, \ref{fig:rh_psi_P25E2E1} and \ref{fig:rh_psi_P25E2E1_lwoff}).  }
+  \item {The surface enthalpy flux decreases by tens of $\rm{W m^{-2}}$ and is much more variable among the models over the warm patch (Figure \ref{fig:enthalpy} a).}
+  \item {The spatial gradients of $\theta_e$ (Figure \ref{fig:enthalpy} b), the specific humidity, temperature, and virtual temperature 
+  (not shown) increases on the lowest atmospheric level.  }
+ {\remove[LGS]{When convection is parameterized the total domain mean condensate increases at all heights 
+  (Figure 6), in contrast to when the convection is explicit and 
+  the condensate aloft decreases (Figure 11.}    }
+\end{itemize}
+
+\subsection{Discussion}
 
@@
 
-\section{Conclusions}
-
-We have used the framework of the tropical overturning circulation, specifically the Walker Circulation, 
-to compare the multi-scale interactions between large-scale circulations, cloud systems, and interactive 
-radiation across experiments with grid-spacing ranging from 1km to 100km.   
-To better isolate the role that clouds and humidity play in driving and responding to the 
-circulation, experiments have been performed with and without the radiative effect of clouds, with and without the 
-convective parameterization, and with multiple domain sizes.  Our results show that 
-the convective parameterization and the longwave cloud radiative effect (LWCRE) strongly interact with each other and 
-often lead to asymmetric results and large differences in the equilibrated atmospheric state.
-
-Perhaps the most interesting result is that the GCM-like experiments have a relatively large low-level 
-cloud fraction while the CRM-like experiments have a large upper-level cloud fraction.  
-This difference in the dominant cloud type leads to opposite atmospheric responses to changes of the LWCRE.  
-The LWCRE increases the domain mean precipitation ($\overline{\rm{P}}$) for the GCMs but 
-decreases it for the CRMs (Table \ref{tab:experimentmeans}).  
-Over the regions with cooler SSTs the large low-level cloud fraction of the GCMs 
-acts as a source of radiative cooling that is balanced by condensational heating in the control case.  
-A strong decrease of low-level clouds in the GCMs
-for the LWCRE-off experiments removes this cooling and condensational heating.  The increase 
-of precipitation that is expected in the LWCRE-off case as a result of increased LW cooling to space is not enough
-to overcome the decreased condensational heating at low-levels, with a net effect of less $\overline{\rm{P}}$.  
-Over the regions with cooler SSTs, the CRMs have very few (less than \change[LGS]{\%5}{5\%}) low-level clouds and as a result the 
-change of $\overline{\rm{P}}$ is driven by the increased LW cooling to space in the LWCRE-off case.
-\citeA{Watanabe_etal_2018} found a similar relationship between low-clouds and precipitation in the context \add[LGS]{of} climate 
-change experiments.
-This highlights how sensitive the energetics of the tropical atmosphere are to the distribution of clouds and 
-their interaction with the radiation.
-
-Decreasing the grid-spacing from $100 \textrm{km}$ to 1km allowed for the parameterization of both deep and shallow 
-convection to be turned off, resulting in a more direct simulation of the dynamics that are
-fundamental to the overturning tropical circulation.  The resulting atmospheric state has a stronger overturning 
-circulation, a much more humid (up to 50\% higher RH) deep convective region, and less $\overline{\rm{P}}$ .  
-Relative to the GCM-like simulations the 1 and 2km simulations have two to four times as much condensate
-aloft but only about half as much below 700 hPa.  The increase of vertical moisture transport with increasing 
-resolution is particularly apparent in the LWCRE-off experiments (Figure \ref{fig:rh_psi_P25E2E1_lwoff}, lower panels).
-
-Three striking changes occur as a result of a four-fold increase in domain width.  The low-level clouds shift 
-upward by more than 100 hPa (Figure 6), there is a dramatic widening of the precipitation distribution in the LWCRE-off experiments 
-(compare Figures 4 and Figure 5),  
-and the LWCRE mediates the precipitation from the large-scale cloud parameterization but not the convective precipitation (Figure \ref{fig:conv_vs_ls}).    
-This impact on the large-scale precipitation occurs for the GCM-like experiments on smaller domains as well, 
-but is pronounced in the large domain experiments.  
-This dependence on domain size could imply that 4000 km is not large enough to contain the largest 
-scales that are important for the overturning circulation.  Another reason for the domain 
-size dependence could be the changing scale of the warm and cold regions of SST.
-
 The flexible modeling system at GFDL has allowed us to use a single code base in a GCM-like configuration with 
@@
 configuration when used with idealized boundary conditions.  
-Two examples include the consistent asymmetry of the circulation and precipitation relative 
-to the fixed SST pattern, and the dominance of the large-scale precipitation over the convective precipitation.  
+Two examples include the \change[LGS]{consistent asymmetry of the}{consistently off-center} circulation\add{s}, and precipitation \add{patterns}, 
+relative to the fixed SST pattern, and the dominance of the large-scale precipitation over the convective precipitation.  
 The comparisons have also illustrated some of the challenges that arise when dramatically increasing the resolution of a GCM.  

### 2020-09-18 Silvers_WalkerCell_response2reviewers.tex
changes to Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex as part of my revision for Silvers and Robinson, 2020.

@@
 
-%% Enter journal name below.
-%% Choose from this list of Journals:
-%
-% JGR: Atmospheres
-% JGR: Biogeosciences
-% JGR: Earth Surface
-% JGR: Oceans
-% JGR: Planets
-% JGR: Solid Earth
-% JGR: Space Physics
-% Global Biogeochemical Cycles
-% Geophysical Research Letters
-% Paleoceanography and Paleoclimatology
-% Radio Science
-% Reviews of Geophysics
-% Tectonics
-% Space Weather
-% Water Resources Research
-% Geochemistry, Geophysics, Geosystems
-% Journal of Advances in Modeling Earth Systems (JAMES)
-% Earth's Future
-% Earth and Space Science
-% Geohealth
-%
-% ie, \journalname{Water Resources Research}
-
 \journalname{JAMES}
@@
 \begin{document}
-
-%% ------------------------------------------------------------------------ %%
-%  Title
-%
-% (A title should be specific, informative, and brief. Use
-% abbreviations only if they are defined in the abstract. Titles that
-% start with general keywords then specific terms are optimized in
-% searches)
-%
-%% ------------------------------------------------------------------------ %%
-
-% Example: \title{This is a test title}
 
@@
     \end{itemize}
+  \textcolor{red}{Figure 6 has been split into two panels and is now easier to read.  I have rewritten the lines in question here to be more consistent
+  with what is clearly shown in this paper.  I have concluded that more research is needed before drawing firm conclusions about the connection 
+  between low-level clouds and the fraction of precipitation that is due to either the convection or the large-scale schemes.}
   \item (Section 5)
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-%  ACKNOWLEDGMENTS
-%
-
-%\acknowledgments
-%Enter acknowledgments, including your data availability statement, here.
-
-%% ------------------------------------------------------------------------ %%
-%% References and Citations
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%
-% \bibliography{<name of your .bib file>} don't specify the file extension
-%
-% don't specify bibliographystyle
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
 \bibliography{ enter your bibtex bibliography filename here }
-
-%Reference citation instructions and examples:
-%
-% Please use ONLY \cite and \citeA for reference citations.
-% \cite for parenthetical references
-% ...as shown in recent studies (Simpson et al., 2019)
-% \citeA for in-text citations
-% ...Simpson et al. (2019) have shown...
-%
-%
-%...as shown by \citeA{jskilby}.
-%...as shown by \citeA{lewin76}, \citeA{carson86}, \citeA{bartoldy02}, and \citeA{rinaldi03}.
-%...has been shown \cite{jskilbye}.
-%...has been shown \cite{lewin76,carson86,bartoldy02,rinaldi03}.
-%... \cite <i.e.>[]{lewin76,carson86,bartoldy02,rinaldi03}.
-%...has been shown by \cite <e.g.,>[and others]{lewin76}.
-%
-% apacite uses < > for prenotes and [ ] for postnotes
-% DO NOT use other cite commands (e.g., \citet, \citep, \citeyear, \nocite, \citealp, etc.).
-%
 
@@
 %
-%% ------------------------------------------------------------------------ %%
-%
-%  IN-TEXT LISTS
-%
-%% ------------------------------------------------------------------------ %%
-%
-% Do not use bulleted lists; enumerated lists are okay.
-% \begin{enumerate}
-% \item
-% \item
-% \item
-% \end{enumerate}
-%
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATIONS
-%
-%% ------------------------------------------------------------------------ %%
 
@@
 % the correct amount of space.
-
-%% ------------------------------------------------------------------------ %%
-%
-%  EQUATION NUMBERING: COUNTER
-%
-%% ------------------------------------------------------------------------ %%
-
-% You may change equation numbering by resetting
-% the equation counter or by explicitly numbering
-% an equation.
-
-% To explicitly number an equation, type \eqnum{}
-% (with the desired number between the brackets)
-% after the \begin{equation} or \begin{eqnarray}
-% command.  The \eqnum{} command will affect only
-% the equation it appears with; LaTeX will number
-% any equations appearing later in the manuscript
-% according to the equation counter.
-%
-
-% If you have a multiline equation that needs only
-% one equation number, use a \nonumber command in
-% front of the double backslashes (\\) as shown in
-% the multiline equation above.
-
-% If you are using line numbers, remember to surround
-% equations with \begin{linenomath*}...\end{linenomath*}
-
-%  To add line numbers to lines in equations:
-%  \begin{linenomath*}
-%  \begin{equation}
-%  \end{equation}
-%  \end{linenomath*}

### 2020-09-18 Silvers_WalkerCell_revision.tex
changes to Silvers_WalkerCell_revision.tex and Silvers_WalkerCell_response2reviewers.tex as part of my revision for Silvers and Robinson, 2020.

@@
 \usepackage{lineno}
-\usepackage[inline]{trackchanges}        % for track changes. finalnew option will compile document with changes incorporated.
-%\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
+%\usepackage[inline]{trackchanges}        % for track changes. finalnew option will compile document with changes incorporated.
+\usepackage[finalnew]{trackchanges}   % use this to create the final pdf without the changes shown.
 \usepackage{soul}
@@
 \remove[LGS]{The mass streamfunction and vertical velocity both show the 
-P25 (Figure }\ref{fig:rh_psi_P25vsE25}, 
-\change[LGS]{left panels}{a,d}; Figure \ref{fig:precip_vertvel})
+P25 (Figure 1 a,d; Figure 2) }
+%\ref{fig:rh_psi_P25vsE25}, 
+%\change[LGS]{left panels}{a,d}%; Figure \ref{fig:precip_vertvel})
 \remove[LGS]{ experiment to have 
 a stronger, more concentrated overturning circulation than either the P25 LWCRE-off (Figure} 
-\ref{fig:rh_psi_P25vsE25} 
+%\ref{fig:rh_psi_P25vsE25} 
 \remove[LGS]{b,e) or E25 (Figure} 
-\ref{fig:rh_psi_P25vsE25} 
+%\ref{fig:rh_psi_P25vsE25} 
 \remove[LGS]{c,f) experiments.   
@@
 characteristics of our system.  The domain mean precipitation ($\overline{\rm{P}}$) provides one example of this.  
-Because of the tight constraints that connect $\overline{\rm{P}}$, atmospheric condensational heating, and 
+Because of the \change[LGS]{tight}{energetic} constraints that connect $\overline{\rm{P}}$, atmospheric condensational heating, and 
 the total radiative cooling, the time evolution of the precipitation is a useful measure of whether a model has 
@@
 of  $\overline{\rm{P}}$ is fairly large (1-2 mm/d), after the initial adjustment period of a few months, the experiments are steady in time.  This
-is demonstrated in Figure \ref{fig:precip_dom_mn} with the colored circles which show the mean values of $\overline{\rm{P}}$ over the last 4 years (5 months) of the experiments for the GCM-like (CRM-like) experiments.
+is demonstrated in Figure \ref{fig:precip_dom_mn} with the colored circles \add[LGS]{and diamonds} which show the mean values of $\overline{\rm{P}}$ over the last 4 years (5 months) of the experiments for the GCM-like (CRM-like) experiments.
 After the initial adjustments
 the simulations all oscillate about mean precipitation values which tend to increase with the grid-spacing (Table \ref{tab:experimentmeans}).   
-Despite the same boundary conditions and model base, these experiments have a large range of domain mean precipitation 
+Despite the same boundary conditions and base model, these experiments have a large range of domain mean precipitation 
 (Table \ref{tab:experimentmeans}) that varies by as much as 0.6 $\rm{mm/d}$ (3.5-4.1 in parameterized experiments; 3.1-3.7 in explicit experiments).  
@@
 as a function of domain size than it does as a function of resolution. 
-On the large domains, the difference between experiments with and without LWCRE is extreme (compare Figure \ref{fig:domdep}a,b to Figure \ref{fig:domdep_lwoff}a,b).  
+On the large domains, the difference between experiments with and without LWCRE is extreme 
+(compare Figure \ref{fig:domdep}a,b to Figure \ref{fig:domdep_lwoff}a,b).  
 In contrast to the control experiments in Figure \ref{fig:domdep} which all show a narrow region of strong 
@@
 \add[LGS]{In this section we conclude by summarizing the primary results of our study, followed by a brief discussion 
-of the proper context and implications of these results.}
+of the context and implications of these results.}
 
@@
 The authors thank Leo Donner, Nadir Jeevanjee, Yi Ming, and Juho Iipponen for discussions  that helped to motivate this work as well as useful comments on drafts of the manuscript.
+Comments from three anonymous reviewers also helped to improve the manuscript.
 The expertise of Ming Zhao with the physics of AM4.0 also proved helpful in many conversations related to this work.

### 2020-11-03 Silvers_WalkerCell_response2reviewers.tex

@@
 
-\textcolor{blue}{All responses and comments by Levi Silvers will be in blue.
+\textcolor{blue}{All responses and comments by the authors are in blue.
 Below please find my responses to your particular considerations.
@@
 Reviewer \#1 made additional comments in a pdf that was included with the review.
-I have responded to those comments within that pdf.
+I have imported those comments to this document.
 Reviewer \#3 made 15 minor comments in the annotated pdf provided by \textit{JAMES}.
-I have responded with my own annotations.
+I have responded with my own annotations in the annotated pdf.
 }
@@
 
-%I have responded to your annotations in the pdf file: 
-%Silvers\_WalkerCell\_reviewer1\_1592417419\_response.pdf
+\textcolor{blue}{Thank you for your review and the encouraging synopsis, it has helped me to improve the paper.  I think that 
+the changes made as a result of the comments from you and the other reviewers has substantially improved the clarity of the 
+results and descriptions.  Your comments have helped to better emphasize the main points and to improve the representation
+of the data with the figures.}
 
@@
 Your work helps clarify these issues by using the same model.
+  \textcolor{blue}{The text now reads: Current climate models continue to be developed with an increasingly fine resolution and 
+the domain sizes used with CRMs continues to grow.  The parameter space of GCMs and CRMs has begun to overlap but the representation of 
+physics continues to differ by much more than grid-spacing and the treatment of convection.  As a result there is a need to systematically compare the 
+clouds and their influence on the climate produced by each type of model.
+By simulating a mock-Walker Circulation in the context of both a GCM and a CRM that have been derived from the same model we 
+illustrate how inextricable the interactions between clouds and radiation are to the coupling of moisture with the large-scale circulation.}
 
   \item Ln 123-124: Can you be more specific here?
-  \textcolor{red}{I have struggled with this one... the sentence seems pretty clear to me.  Could I change something else in the this paragraph to 
-  make this more clear?  Add a sentence after this one?}
+  \textcolor{blue}{Please see my response to your previous comment, on Ln 119-120, I trust this has clarified the statement for readers.}
 
@@
   \item Table 2:  This table is helpful. I wonder if adding two columns for high cloud and low cloud fraction could help further summarize some of your key results?
+  \textcolor{blue}{Good suggestion.  I have made several additions to the paper that I think further clarify the results as related to the cloud and moisture 
+  distributions with height.  The new Figure 4 shows profiles of cloud fraction and cloud condensate for the P100, P25, and E25 experiments.  I have also 
+  added a panel to Figure 13 which  shows the profiles of specific humidity.}
 
@@
   While panel b is much more symmetric than panel a, there are still notable asymmetries present which supports the idea that part of the asymmetry comes from the convective parameterization and part of it comes from the LWCRE.
-}
-  \textcolor{red}{could plots of longwave heating be part of the extra section comparing E25 and P25?}
+Figure 5 of the revised manuscript, with five year Hovmoller diagrams for the cases in Figure 1 will be interesting for you to see.
+I have almost added plots of the 2D longwave heating many times to this paper.
+However, they don't add much insight and the paper is already bordering on unwieldy, so I have refrained.}
 
@@
   \item Ln 310: I only see prominent asymmetry in the P25 simulations. The P100 simulation is only slightly asymmetric, and the P100L simulation not asymmetric at all.
-  \textcolor{red}{The language describing this has been changed to reflect off center features, rather than just asymmetric.  Please see the discussion in the subsection which discussed 
-  the comparison between P25 and E25.   While P100 is only slightly asymmetric, it is 
-  consistently off center.  The asymmetry of P25L is greater than may be initially apparent because of the difference in domain size.  A similar asymmetry to the P25 case would 
-  be shown with a shift off-center that appears smaller than for P25 (see Figs 5 and 8 of revised manuscript).  }
+  \textcolor{blue}{The language describing this (in multiple places) has been changed to reflect off center features, rather than just asymmetric.  Please see the discussion in 
+  the new subsection (3.2) which discusses the comparison between P100, P25 and E25.   While P100 is only slightly asymmetric, it is 
+  consistently off center.  The asymmetry of P25L is greater than may be initially apparent because of the difference in domain size.  I am happy to change 
+  the language here as I don't think the 'asymmetry' is important scientifically.}
 
@@
   circulation that drives this asymmetry. Because Fig 1. middle panel is very symmetrical (with LWCRE disabled).
-
 Also, I wonder to what extent the domain shape influences 
   this result (the asymmetry is not present in P100L and less prominent in P25L)
-  \textcolor{red}{It should be pointed out that while the middle panel of Fig1 is symmetrical relative to the left panel, 
+  \textcolor{blue}{The new subsection, 3.2, and especially the new Figure 5, will clarify this further.
+It should be pointed out that while the middle panel of Fig1 is symmetrical relative to the left panel,
   the far right panel is even more symmetrical (at least in terms of the RH and streamfunction).}
@@
   \item Ln 338-343: Yes, but maybe clarify that you must compare similar domain sizes in Table 2. The variation in SF is also influenced by domain size. 
-  \textcolor{red}{I agree in principle that the cleanest comparisons will be with similar domain sizes, but comparing similar domain sizes does not help to clarify the numbers in Table 2.
+  \textcolor{blue}{I agree in principle that the cleanest comparisons will be with similar domain sizes, but comparing similar domain sizes does not help to clarify the numbers in Table 2.
 For example, both the largest and smallest SF are found on the large domain.
-}
+I also think there is still some value
+  in the comparison even across different domain sizes.}
 
@@
 I wonder if just using a slightly different color for E25 and P25 would be better.
-\textcolor{red}{Figure 13 has been redone as a 2x2 panel figure using a different color for E25 instead of the triangles, larger axis labels, and clearer panel titles.}
+\textcolor{blue}{Figure 13 has been redone as a 2x2 panel figure using a different color for E25 instead of the triangles, larger axis labels, and clearer panel 
+titles.  I have opted to not include figures of the longwave heating vs horizontal distance.  I have not found them to provide unique insight and are best 
+understood in combination with the shortwave heating, convective heating, and heating due to large-scale physics plots.  Including this all would significantly 
+bulk up the paper with minimal gain.}
 
@@
 Hopefully it is not as easy to get lost in the details now.}
-  \textcolor{red}{I sympathize with you.
-This paper has been hard to write because it has been tough to not get lost in all of the details myself.
-The \textit{importance} of several of these results, such as the domain size results, is not clear to me, but they
-  seem both interesting and significant.}
 
@@
 Could the smaller low-cloud amounts in the CRM-like experiment be due to the stronger overturning circulations, and hence stronger subsidence drying?
+  \textcolor{blue}{I have included the following in the freshly organized concluding section: 
+  Our results show a stronger of the overturning circulation (Figures 1,2, and 11)
+ in the CRM-like experiments compared to the GCM-like experiments.  
+ Accompanying this is a difference in the vertical mixing of water condensate, specific
+ humidity and temperature (Figures 4, 8, and 13).  We conclude that the CRM-like experiments (E1 and E2) transport more specific humidity 
+ and liquid water from the lowest 200 hPa of the atmosphere into the troposphere above than do the GCM-like experiments 
+ (P100 and P25).  While the E25 experiment does not use convective parameterizations, in terms of the vertical distribution of water
+ species and clouds it is more similar to the GCM-like experiments than to the CRM-like experiments.}
 
@@
   have not been filtered out of this observational data.  I am hopefully that a quick look at data like this could help to motivate future studies in which a more detailed comparison 
-  between models of the Walker Circulation and observations.  The following red text has been added to the manuscript:}
+  between models of the Walker Circulation and observations.  The following text has been added to the manuscript:}
 
-  \textcolor{red}{In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative study we look at the clouds observed with the MISR instrument 
-  on board NASA's Terra satellite.  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the regional Walker circulation in the Pacific.  
-  The left panel of Figure 15 shows the cloud fraction averaged from March 2000-November 2019 of the full domain of the Pacific regional Walker circulation.  This region 
-  includes much of the so-called warm pool beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the stratocumulus
-  cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a function of height we sum the MISR data over all optical depths 
-  and plot the domain mean (dashed line), a region of subsidence ($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a regions that is characterized by deep 
-  convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction from MISR are closer to the cloud profiles 
-  simulated by the GCM-like models.  It would be interesting in future studies to sample the observations for time periods in which the Walker Circulation is strong}
+  \textcolor{blue}{In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative 
+study we look 
+at the clouds observed with the Multiangle Imaging Spectro-Radiometer (MISR) instrument on board NASA's Terra satellite (see 
+Marchand et al., 2010 for details).  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the 
+regional Walker circulation in the Pacific.  The left panel of Figure 16 shows the cloud fraction averaged from March 2000-
+November 2019 of the full domain of the Pacific regional Walker circulation.  This region includes much of the so-called warm pool 
+beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the 
+stratocumulus cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a 
+function of height we sum the MISR data over all optical depths  and plot the domain mean (dashed line), a region of subsidence 
+($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a region that is characterized by deep 
+convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction 
+from MISR are closer to the cloud profiles simulated by the GCM-like models.  However, it should be kept in mind that there are 
+several substantial differences between our mock Walker circulation and the observed Walker circulation.}
 
@@
 
+\textcolor{blue}{Thank you for your review and the encouraging synopsis, it has helped me to improve the paper.  I think that 
+the changes made as a result of the comments from you and the other reviewers has substantially improved the clarity of the 
+results and descriptions.  I have incorporated most of you recommendations and trust that you will find the manuscript substantially 
+improved.}
+
 \subsection{GENERAL COMMENTS}
@@
   \item Section 3 is meant to focus on the impact of LWCRE, but subsequent sections frequently reference the comparison between LWCRE-on and LWCRE-off as well (i.e. lines 361-373, 398-401, 459-462).
-  \textcolor{red}{During the writing I attempted consolidating the comparison between LWCRE on/off to one section but found it to create more problems than it 
-  solved because the LWCRE on/off experiments have such a strong influence on all of the other sections.  You mention lines 361-373, which happens to be a 
-  perfect example of the difficult.  Figures 5 and 6 illustrate the overlapping influence of the LWCRE on/off effects and domain size dependence.  
-  As a result, I have chosen to largely focus on your other excellent recommendations for reworking the organization of the manuscript.}
+  \textcolor{blue}{I have added this sentence to the end of the introduction where the layout of the paper is described: 'The longwave 
+  cloud radiative effect (LWCRE) is an important element for all of the experiments and will be discussed throughout the paper.'  My 
+  response to your next point is also relevant to this point.   During the writing I attempted consolidating the comparison between 
+  LWCRE on/off to one section but found it to 
+  create more problems than it solved because the LWCRE on/off experiments have such a strong influence on all of the other   
+  sections.  You mention lines 361-373, which happens to be a perfect example of the difficulty.  Figures 5 and 6 illustrate the 
+  overlapping influence of the LWCRE on/off effects and domain size dependence.  As a result, I have chosen to largely focus on your 
+  other excellent recommendations for reworking the organization of the manuscript.}
   \item Comparisons between E25 and P25 are made in multiple sections, and some of these results are referenced in passing (i.e.
@@
 Given the importance of this resolution in the manuscript to link GCMs and CRMs, I believe that this deserves its own section.
-  \textcolor{red}{To further aid in the comparison between E25 and P25, the P25 control and P25 LWCRE-off profiles have been added to Figure 11 (note the number of this figure may change depending on the E25/P25 section).
+  \textcolor{blue}{Your review has convinced me.
+I have reorganized the paper to include a new subsection 3.2 in which P100, P25, and E25 are compared to highlight the impact that resolution and the convective parameterization have.
+I think this makes the overall
+  comparison between GCM-like and CRM-like models more logical.
+The new subsection shows domain mean profiles of RH, domain mean condensate, cloud fraction, atmospheric heating, and temperature.
+I have also included a figure with additional Hovmoller precipitation diagrams focusing on P25 and E25.
+To further aid in the comparison between E25 and P25, the P25 control and P25 LWCRE-off profiles of total condensate have been added to Figure 11 (note the number of this figure will change depending on the E25/P25 section).
+An additional panel was added to that figure showing the vertical distribution of specific humidity.
 The color used to show the E25 profiles has also been changed from yellow to purple in several of the figures and I think this also helps readers to compare E25 and P25.}
@@
   \item I believe that Sections 6 and 7 can be consolidated and combined into one, given that the first half of Section 6 is already a well-constructed and well-divided summary of results.
-  \textcolor{red}{related to comments from Reviewer \# 1 on reducing number of points in section 6...}
+  \textcolor{blue}{Section 6 and 7 have been combined and reorganized into one section with two subsections, one with results and one with discussion.
+I think this improves the clarity.
+Please see the revised manuscript.}
   \item In several parts of the manuscript, multiple references are made to Figures/Tables that appear 10 or more pages earlier.
@@
 For example, Figure 2's legend can list the domain-mean precipitation values next to the labels.
-  \textcolor{red}{I have added domain-mean values to the precipitation shown in Figure 3, and extended the markers at the end of the time series to make Figure 3 easier to read.  
-  In response to several comments from you and the other reviewers, section 3, 6, and 7 have been somewhat reorganized and hopefully make the manuscript easier to read.}
+  \textcolor{blue}{I have added domain-mean values to the precipitation shown in Figure 3, and extended the markers at the end of the time series to make Figure 3 easier to read.  
+  In response to several comments from you and the other reviewers, section 3, 6, and 7 have been somewhat reorganized and hopefully make the manuscript easier to read. }
 \end{enumerate}
@@
 
-  \textcolor{blue}{No, I have not performed experiments at other resolutions (a few at 5km, at the very beginning with different code base, but the analysis was not carried very far).
+  \textcolor{blue}{Because this study focuses on LWCRE, convective parameterizations, and domain size in addition to grid-spacing I have not performed experiments at other resolutions (a few at 5km, at the very beginning with different code base, but the analysis was not carried very far).
 Also see answer to you comment just before this one.
@@
 Figure 13 would be best oriented as a 2X2 window similar to Figure 12, especially given the subtle differences in the rightmost panel.
-  \textcolor{red}{For several of the figures (6, 11,12, and 13) the labels and axis font size has been increased.}  
-  \textcolor{blue}{Figure 6 has now been split into two figures, one
-  showing results on the small/control domain size and the other showing results on the large domain.}
+  \textcolor{blue}{For most of the figures (3, 6, 7, 11,12, and 13) the labels and axis font size has been increased.  
+  Figure 6 has now been split into two figures, one showing results on the small/control domain size and the other showing 
+  results on the large domain.  Figure 13 have been shift to a 2x2 panel format, the color used for E25 is now purple, and the 
+  title are clearer.}
 
   \item For each of the figures, especially those later in the manuscript, it would be helpful to make the font size on the axes a bit larger.
-  \textcolor{red}{The font size has been increased for Figures 6,11,12, and 13.}
+  \textcolor{blue}{The font size has been increased.}
 
@@
 
-  \textcolor{blue}{In contrast to the P25 (lwcre-on) simulation (Figure 1, left; Figure 4d), the initial several months of both P25 
+  \textcolor{blue}{The new subsection, 3.2 should clarify this, especially Figure 5. In contrast to the P25 (lwcre-on) simulation (Figure 1, left; Figure 4d), the initial several months of both P25 
   (lwcre-off; Figure 5d) and E25 (lwcre-on; Figure 8b) show a precipitation maximum that is centered closely on the SST 
@@
 The time evolution of precipitation for the LWCRE-off, Conv-off (E25 lwcre off) also shows regular oscillations (large) about the SST maximum in a way that is distinct from either P25 lwcre-off or E25 lwcre-on.
-Another piece of this (I was a bit hesitant to include too many Hovmoller plots, fearing Hovmoller fatigue.)  }
-\textcolor{red}{include Hovmoller figure with four different 25km simulations?}
+}
 
@@
 The somewhat inconsistent comparison between LWCRE-on and LWCRE-off experiments here is noteworthy, given that LWCRE is arguably the most important mechanism for maintenance of the aggregated state in non-rotating RCE studies.
-\textcolor{blue}{Good question.
+\textcolor{blue}{Good question, please see the included Figure 1.
 Once the experiments equilibrate the subsidence fraction (SF) is quite steady in time, despite rather large variability (on the order of 0.1-0.15).
@@
 Do you have any speculation as to why this happened?
-  \textcolor{red}{When I first saw this upward shift I thought it must be an error in some part of the setup or analysis...
+  \textcolor{blue}{When I first saw this upward shift I thought it must be an error in some part of the setup or analysis...
 when I convinced myself it was not an error I was fascinated.
 However, it is one of several interesting results that I have resisted
-  pursuing in this paper for fear of being pulled in two many directions.  My speculation is that...}
+  pursuing in this paper for fear of being pulled in two many directions.
+My speculation is that this is due to a difference of mixing between the BL and the lower troposphere for the large domain experiments, there are much higher values of specific humidity in the BL for the P100L.
+Perhaps with a larger physical extent of the SST warm patch there is simply more convective mixing?}
 
@@
 
+\textcolor{blue}{Thank you for your review and the encouraging synopsis, it has helped me to improve the paper.  I think that 
+the changes made as a result of the comments from you and the other reviewers has substantially improved the clarity of the 
+results and descriptions.  I have incorporated many of your suggestions, in particular a panel looking at the vertically resolved 
+specific humidity and a simple look at observations from MISR.}
+
 \subsection{Major comments}
@@
 We are using a very similar physics code as that used by \textit{Popp \& Silvers, 2017, J. of Clim.}.   However, we have chosen to limit ourselves in this case to the 
-LWCRE experiments for several reasons, the foremost being practicality.  As you know, the current study varies LWCRE, resolution, domain size, and 
+LWCRE experiments for several reasons, the foremost being simplicity of focus.  In addition, the current study varies LWCRE, resolution, domain size, and 
 the convective parameterization.  As a result, organizing the current range of results is already a challenge and we chose not to 
@@
 SWCRE on the surface energy budget.  Second, there are numerous studies which have shown that the atmospheric shortwave heating is 
-much smaller than the longwave heating (e.g. Perdergrass \& Hartmann, 2014; Popp \& Silvers, 2017 (their Figures 1 \& 4)).}
-\textcolor{red}{This response should lean heavily on Popp and Silvers.
-It should additionally emphasize the many directions which the paper already hints at due the large amount of experiments that are being compared, domain size differences,
-parameterization differences, resolution differences, and the LWCRE differences.}
-\textcolor{blue}{draft of additions: Both the shortwave and longwave radiation influence the atmospheric radiative heating.  We have chosen to focus on 
-the LWCRE because it is by far the dominant contributor to atmospheric radiative heating.
-In order to present a relatively simple analysis of the cloud radiative effect we have chosen to explore LWCRE on/off experiments but not SWCRE on/off 
-experiments.  }
+much smaller than the longwave heating (e.g. Pendergrass \& Hartmann, 2014; Popp \& Silvers, 2017 (their Figures 1 \& 4)).}
+
+\textcolor{blue}{The following has been added to the text: One of the ways in which clouds influence the flow of energy through the 
+atmosphere is by absorbing and 
+reemitting longwave radiation....  and later in the same paragraph..... Clouds also interact with shortwave radiation.  We have chosen 
+to only focus on the LWCRE for several reasons.  
+On timescales of years and over large domains, the LWCRE has been shown (e.g. Popp \& Silvers, 2017) to have a much larger 
+influence on the atmospheric 
+heating and the large-scale circulations compared to the SWCRE.  The SWCRE is important on diurnal timescales and for the surface
+energy budget.  However, we choose to leave simulations exploring the SWCRE in the context of the mock-Walker circulation
+for a later study.}
 \end{itemize}
@@
 rationale if not a quantitative explanation for why the authors find the results summarized in Section 6.
-\textcolor{red}{Perhaps the recommendation from the first reviewer to combine sections 6 and 7 will help to answer this point as well...}
+
+\textcolor{blue}{Sections 6 and 7 have been combined and edited to help clarify the end of the paper.  The goal has been to 
+maximize the insight that readers can get without overloading them with too many details.  I think the revised manuscript 
+succeeds in this and is also more quantitative than the original submission.}
 
@@
     \end{itemize}
+  \textcolor{blue}{These are good questions.  There is great appeal to me in the simplicity and physical reasoning that drives many of the two box models, and other idealized
+  theoretical studies of overturning circulations.  However, the focus of this work has always been more on the comparison between the
+  GCM-like and CRM-like configurations.  I think a comparison between a two-box model and some of these simulations would be 
+  very interesting, but in my opinion I needed to get a sense of what was happening with these experiments before bringing in an 
+  additional framework for comparison.  In addition, the interesting differences in the structure of precipitation, the strong influence
+  on the LWCRE and the significant differences in the vertical structure of the condensate between the GCM-like and CRM-like 
+  models essentially distracted me from two-box model type work that helped to motivate the original study.
+It is also not immediately clear to me which two-box model, which measure of CRE and which measure of circulation strength you have in mind.
+I would hope
+  that multiple two-box models, various measures of CRE (TOA CRE, ACRE, or differences of particular variables between a control and LWCRE-off experiment), and various measures of the circulation strength would all point to similar insights into the underlying physics, but the ambiguity of the current questions highlights the need for a future study rather than quick inclusion in this paper.}
   \item (Section 4, Lines 407-409)
@@
     \end{itemize}
-  \textcolor{red}{Figure 6 has been split into two panels and is now easier to read.  I have rewritten the lines in question here to be more consistent
-  with what is clearly shown in this paper.  I have concluded that more research is needed before drawing firm conclusions about the connection 
-  between low-level clouds and the fraction of precipitation that is due to either the convection or the large-scale schemes.}
+  \textcolor{blue}{These are good points you are making.  I have rewritten the lines in question here to be more consistent
+  with what is clearly shown in this paper, and to not so strongly implicate a connection with low-level clouds.  
+  I have concluded that more research is needed before drawing firm conclusions about the connection 
+  between low-level clouds and the fraction of precipitation that is due to either the convection or the large-scale schemes.  In response 
+  to your questions I have computed correlations in time (on monthly data because I don't have daily) between the convective precipitation and the 
+  low-level clouds, as well as with the high-level clouds.  There are a lot of high correlation numbers, but clear conclusions are not obvious and I 
+  would prefer to not commit to conclusions in print yet.  In short, several of the experiments (but not all) show high correlations between low-level 
+  clouds and convective precip.  But the correlations with high-level clouds are also high.  In addition, the correlation is still high for the experiments 
+  with the LWCRE-off.  So I am left desiring more information or experiments, but not for this paper.
+  Figure 6 has been split into two panels and is now easier to read. }
   \item (Section 5)
@@
     \end{itemize}
+    \textcolor{blue}{I have worked to clarify what was Figure 11 in the submitted manuscript.  An additional panel has been added showing 
+    the vertical profiles of specific humidity, similar to figure 2 in Pauluis and Garner, 2006.  I have also noted in the caption, that the liquid
+    condensate is less than 0.005 g/kg above 600 hPa.  I hesitate to add the sperate profiles of liquid and ice because when combined with 
+    lwcre-off profiles, it makes for a very busy figure and I am not sure that it adds much.  }
 \end{enumerate}
@@
 
+\textcolor{blue}{As you imply, it is challenging to compare a mock-Walker circulation to observations.  I have added 
+figure 16 which uses cloud fraction data from the MISR instrument in the tropical Pacific.  The following text was added near the 
+end of section 5: }
+
+\textcolor{blue}{In order to make a qualitative connection to observed clouds and hopefully motivate a more detailed comparative 
+study we look 
+at the clouds observed with the Multiangle Imaging Spectro-Radiometer (MISR) instrument on board NASA's Terra satellite (see 
+Marchand et al., 2010 for details).  We use the domain (10N-35S) which was identified by Schwendike et al., 2014 as defining the 
+regional Walker circulation in the Pacific.  The left panel of Figure 16 shows the cloud fraction averaged from March 2000-
+November 2019 of the full domain of the Pacific regional Walker circulation.  This region includes much of the so-called warm pool 
+beneath the ascending branch of the Walker Circulation as well as the eastern Pacific subsidence regions that encompass the 
+stratocumulus cloud decks that are common off the west coast of South America.   To calculate profiles of the cloud fraction as a 
+function of height we sum the MISR data over all optical depths  and plot the domain mean (dashed line), a region of subsidence 
+($10^\circ$ N-$35^\circ$S; $120^\circ$W-$60^\circ$W, solid line), and a region that is characterized by deep 
+convection ($10^\circ$N-$35^\circ$S; $120^\circ$E-$180^\circ$, dash-dot line).  Overall, both the upper- and low-level cloud fraction 
+from MISR are closer to the cloud profiles simulated by the GCM-like models.  However, it should be kept in mind that there are 
+several substantial differences between our mock Walker circulation and the observed Walker circulation.}
+
 \subsection{Minor comments}
 
-You will find 15 minor comments attached to the annotated PDF of the manuscript. Additional comments that apply
+You will find 15 minor comments attached to the annotated PDF of the manuscript. 
+\textcolor{blue}{Thank you.  I have responded to your comments in the annotated PDF.}
+
+Additional comments that apply
 throughout the paper are listed below:
@@
   \item Labeling all figure panels using the conventional notation a/b/c/d (e.g. Figure 1, 2, etc.)
-  \textcolor{blue}{Figures 1-14 now have panels labelled with a/b etc., when multiple panels are present.}
+  \textcolor{blue}{Figures 1-15 now have panels labelled with a/b etc., when multiple panels are present.}
 

### 2020-11-03 Silvers_cfmip.tex

@@
 models that participated in CMIP6.  This constitutes a hierarchy of configurations that ranges from an atmosphere only 
-aquaplanet to a fully coupled 
-climate model.  Previously the range of climate sensitivities and feedbacks among the ensemble of climate models 
-the world has to offer have been documented largely by examining the multi-model mean results with less attention to 
-the variability of sensitivity within a single modeling framework (IPCC; \citeA{Andrews_etal_2012, Ringer_etal_2014}).  By 
-focusing on the models from a single modeling center we seek fresh insight that could be buried within a large ensemble.
+aquaplanet to a fully coupled global
+climate model.  Evaluating the range of climate sensitivities and feedbacks among climate models 
+has previously been documented most commonly by examining the multi-model mean results (IPCC; \citeA{Andrews_etal_2012, Ringer_etal_2014}) with less attention to 
+the variability of sensitivity within a single modeling framework.  
+The exception to this multi-model ensemble approach is to examine the impact of a large number of parameter perturbations
+within a single model (referred to as a Perturbed Physics Ensemble, see Murphy et al., 2004; Stainforth et al., 2005; Klocke et al. 2011).  
+In this paper we focusing on a single base model across a range of different warming scenarios and model configurations.
 
@@
 
-A second motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
-have participated in CMIP6.  This will largely be done in the context of the amip experiment and comparisons to observations
-that overlap with parts of that time period (1979-2014).  The experiments and diagnostics used are taken from the latest 
-round of CFMIP which has provided a useful framework with which to evaluate cloud feedbacks.
-
 It has been known for decades that  the spread of cloud feedbacks among models contributes to a large portion of the 
@@
 At least part of the reason for this multiplicity of 
-sensitivities obtained from different method of calculation is that variations of the climate sensitivity within 
+sensitivities obtained from different methods of calculation is that variations of the climate feedback within 
 individual models has been tied to the influence of particular surface temperature patterns 
-\cite{Gregory_Andrews_2016, Zhou_etal_2016, Andrews_Webb_2018, Silvers_etal_2018}.   
+\cite{Gregory_Andrews_2016, Zhou_etal_2016, Silvers_etal_2018, Andrews_Webb_2018}.   
 The influence of a pattern in the surface temperature is communicated to the TOA radiative fluxes by the clouds 
@@
 
+A second motivation for this paper is to document the simulation of clouds in the newly developed GFDL models that 
+have participated in CMIP6.  This will largely be done in the context of the \textit{amip} experiment and comparisons to observations
+that overlap with parts of the textit{amip} time period (1979-2014).  The experiments and diagnostics used are taken from the latest 
+round of CFMIP which has provided a useful framework with which to evaluate cloud feedbacks.
+
 This work assesses the fidelity of the clouds in AM4.0/CM4.0 with observations and compares clouds from experiments 
 with differing sensitivities. 
-Section two compares the clouds from the \textit{amip} run of AM4.0 with satellite observations.  That section also 
-analysis the radiative fluxes at the top-of-the-atmosphere (TOA) and compares them to the observations from 
-CERES-EBAF.    Section three documents the climate sensitivities of GFDL models across multiple CMIP6 experiments 
-and discusses the potential role played by clouds.   Conclusions are drawn in section four.
+Section two briefly outlines the data used and the methods of analysis, with further details presented in the appendix.  Section
+three compares the clouds from the \textit{amip} run of AM4.0 with satellite observations.  That section also 
+analyzes the radiative fluxes at the top-of-the-atmosphere (TOA) and compares them to the observations from 
+CERES-EBAF.    Section four documents the climate sensitivities of GFDL models across multiple CMIP6 experiments 
+and discusses the potential role played by clouds.   Conclusions are drawn in section five.
 
@@
 
-We compare output from the AM4.0 GCM to observations from ISCCP, MISR, MODIS, CALIPSO, and CERES-EBAF.
+The comparisons with observations are made mostly with the \textit{amip} experiment that serves as one of the DECK CMIP6 
+experiments (\cite{Eyring_etal_2016},  \cite{Webb_etal_2017}).   The experiments used 
+in this paper are all part of the GFDL contribution to CMIP6 and as a result, the \textit{amip} and \textit{historical}
+experiments end in the year 2014.  In addition to the \textit{amip} experiment we use the \textit{historical, abrupt-4xCO2}, and \textit{1pctCO2}
+experiments from the CMIP6 DECK.  Several experiments from the CFMIP contributions 
+to CMIP6 are also utilized.  These experiments include \textit{amip, amip-p4K, amip-m4K, amip-future4K, aqua-control} and \textit{aqua-p4K}.  
+In order to utilize as much of the available data as possible much of the analysis of the \textit{amip} experiment uses the 
+full span of years (1979-2014) despite the fact that the satellite observations do not extend as far back in time.  However, 
+some of the analysis for the \textit{amip} and \textit{historical} experiments, in particular for the calculation of a climate feedback parameter over recent years, a shorter period (1996-2014) is used in order to eliminate complications due to radiative forcing in the early 1990's due to volcanic activity.
+The relevant time period is stated in the captions of the figures and tables.
+
+We compare output from the AM4.0 GCM \textit{amip} experiment to observations from ISCCP (the International Satellite Cloud Climatology Project), MISR (the Multiangle Imaging Spectro-Radiometer), MODIS (the Moderate Resolution Imaging Spectroradiometer),
+CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation; 
+Chepfer et al., 2010; Cesana and Chepfer, 2013), and CERES-EBAF.
 More details are provided in the appendix.  The CMIP6 and CFMIP experiments used in this study are given in Table
@@
 
-The comparisons with observations are made mostly with the \textit{amip} experiment.   The experiments used 
-in this paper are all part of the GFDL contribution to CMIP6 and as a result, the \textit{amip} and \textit{historical}
-experiments end in the year 2014.  We use the \textit{historical, abrupt-4xCO2}, and \textit{1pctCO2}
-experiments from the CMIP6 DECK.  In addition we utilize several experiments from the CFMIP contributions 
-to CMIP6.  These experiments include \textit{amip, amip-p4K, amip-m4K, amip-future4K, aqua-control} and \textit{aqua-p4K}.  
-In order to utilize as much of the available data as possible much of the analysis of the \textit{amip} experiment uses the 
-full span of years (1979-2014) despite the fact that the satellite observations do not extend as far back in time.  However, 
-some of the analysis for the \textit{amip} and \textit{historical} experiments, in particular for the calculation of a climate feedback parameter over recent years, a shorter period (1996-2014) is used in order to eliminate complications due to radiative forcing in the early 1990's due to volcanic activity.
-The relevant time period is stated in the captions of the figures and tables.
+Throughout the paper we utilize what has come to be known as the Cloud Radiative Effect (CRE), calculated 
+as the difference between the full-sky and clear-sky radiative fluxes.  
+The CRE is a simple and effective tool for evaluating the influence of 
+clouds on the climate.
+Note that CRE is often referred to as the Cloud Radiative Forcing (CRF) in earlier literature \cite<e.g.,>[]{Cess_etal_1989, Soden_etal_2004}.
+It is well known (Soden et al., 2004) that a change in the CRE is not a direct measure of the cloud
+feedback, and that the CRE can be influenced by non-cloud factors.  However, there are many examples of 
+the productive use of the CRE as a way to diagnose cloud effects (e.g. Cess et al., 1989; Webb et al., 2001; 
+\citeA{Ringer_etal_2014}; Andrews et al., 2015), it is simple to calculate, and
+it allows for direct comparisons with previous studies.  Cloud feedbacks calculated with either the so-called 
+`partial radiative purturbation' or `radiative kernels' method correspond
+to a positive shift (on the order of 0.5 $\rm{W m^{-2}K^{-1}}$) of the change in CRE values (Soden et al., 2004; Soden et al., 2008).  
+The total cloud feedback of a model is therefore usually more positive than will be implied by the CRE.
 
@@
 sources.   
-Comparisons of AM4.0 with observations from ISCCP and MODIS showed an underestimate of 
-the optically thin low clouds and the mid-level clouds (Z18a, Figure 10).  
+Comparisons of AM4.0 with observations from ISCCP and MODIS in Z18a (their Figure 10) showed an underestimate of 
+the optically thin low clouds and the mid-level clouds.  
 However, the observational uncertainty for some of these properties prohibited firm conclusions.  This paper
@@
 the simulated TOA radiative fluxes from AM4.0 to those observed by CERES.
-Throughout the paper we utilize what has come to be known as the Cloud Radiative Effect (CRE), calculated 
-as the difference between the full-sky and clear-sky radiative fluxes.  Earlier literature \cite<e.g.,>[]{Cess_etal_1989, Soden_etal_2004} often referred to the CRE as the Cloud 
-Radiative Forcing (CRF).
-
-The CRE is a simple and effective tool for evaluating the influence of 
-clouds on the climate.  It is well known (Soden et al., 2004) that a change in the CRE is not a direct measure of the cloud 
-feedback, and that non-cloud related values of CRE can occur.  However, there are many examples of 
-the productive use of the CRE as a way to diagnose cloud effects (e.g. Cess et al., 1989; Webb et al., 2001; 
-\citeA{Ringer_etal_2014}; Andrews et al., 2015), it is simple to calculate, and
-it allows for direct comparisons with previous studies.  The pure cloud feedback usually corresponds 
-to a positive shift of the change in CRE values by roughly 0.3 $\rm{W m^{-2}K^{-1}}$ (Soden et al., 2004).  The total cloud 
-feedback of a model is therefore more positive than will be implied by the CRE.
 
@@
 to be translated to variables that are more directly comparable with what satellites observe.  
-These simulators are often referred to as the CFMIP Observation Simulator Package (COSP); for
-details see Bodas-Salcedo et al. 2011.  This paper highlights simulators of the algorithms for 
-four satellite datasets: ISCCP (the International Satellite Cloud Climatology Project), 
-MODIS (the Moderate Resolution Imaging Spectroradiometer), 
-MISR (the Multiangle Imaging Spectro-Radiometer), and 
-CALIPSO (the Cloud-Aerosol Lidar and Infrared Pathfinder Satellite Observation; 
-Chepfer et al., 2010; Cesana and Chepfer, 2013).  By using multiple complimentary satellite 
+These simulators are often referred to as the CFMIP Observation Simulator Package (COSP; see Bodas-Salcedo et al. 2011).  
+This paper highlights simulators of the algorithms for 
+four satellite datasets: ISCCP, 
+MODIS, 
+MISR, and 
+CALIPSO.  By using multiple complimentary satellite 
 datasets and simulators we can benefit from the different strengths of each satellite while largely 
@@
 between observations from MISR and the AM4.0 simulator output for clouds below 3km in Figure \ref{fig:cf_misr_lowcl}.  
-The optical depth is used to distinguish between the thick and thin clouds.  
+The optical depth is used to distinguish between the thick and thin clouds (optical depth greater than (thick), or less than (thin) 3.6).  
 Consistent with comparisons with ISCCP and CALIPSO we see that AM4.0 has fewer clouds than observed.
@@
 For thick clouds AM4.0 does reasonably well producing the observed spatial distribution of clouds, except in the tropical Indian Ocean. 
-The pattern of thin clouds is not reproduced as well, particularly in the southern hemisphere and the tropics.
+The observed pattern of thin clouds is not reproduced as well by the model in the tropics, and this is largely due to the 
+presence of small cumulus.
 
@@
   \caption{Cloud Fraction observed by CALIPSO (2007-2016) and modeled with the CALIPSO satelite simulator 
-  (amip experiment).
+  (amip experiment) over the three vertical ranges of upper-level (top row), mid-level (middle row), 
+  and low-level (bottom row).
   Dashed line shows meridional profiles of AM4.0 cloud fraction and solid line shows
@@
 over tropical land and in the region of the inter-tropical convergence zone.  
-The low-levels have large biases over much of the tropical Pacific ocean, as well as in the stratocumulus zones 
-and the southern tropical Atlantic ocean.   
+As was noted in the comparison with MISR thin cloud amount, much of the underestimation in tropical and subtropical low
+cloud coverage over ocean occurs in regions where small cumulus are prevalent.  Low clouds also show obvious large biases in 
+regions dominated by stratocumulus clouds.
 AM4.0 produces more Low-level clouds than observed over land in the high-latitudes.  
@@
 coupling the AM4.0 atmosphere to a dynamic ocean decrease the cloud bias?   
-\textit{This paragraph should serve as a bridge between the COSP observations, amip and historical experiments, TOA fluxes, and feedbacks.
+\textit{This paragraph should serve as a bridge between the COSP observations, amip and historical experiments, TOA fluxes, and feedbacks.}
 While direct comparisons between GCM output and satellite observations are only possible over the recent decades, experiments that use
@@
 for these purposes.  Pronounced decadal variability of the climate feedback parameter has been shown to be closely tied to 
-variations of the SW CRE and the low-level clouds (Gregory and Andrews, 2016; Zhou et al., 2016; Silvers et al., 2018).}
+variations of the SW CRE and the low-level clouds (Gregory and Andrews, 2016; Zhou et al., 2016; Silvers et al., 2018).
 Plotting the cloud fields as a function of latitude and height emphasizes the similarities and differences 
@@
 
+\textit{There have been several papers that suggest that changes in cloud phase have led to an increased shortwave cloud feedback in CMIP6 models (Flynn and Mauritsen, 2020).
+With the exception of the aquaplanet experiment, all the experiments examined in this paper have identical microphysics parameterizations and tuning.
+So the changes in high-latitude cloud feedback and distribution must be due to differences in boundary conditions or the atmospheric circulations.}
+
 %Probably have to cite Armour, 2017.
@@
 \begin{center}
-\caption{Experiments used.   Should I list the years the experiment simulate or just the years used in the analysis?}
+\caption{Experiments used.   The years listed for each experiment correspond to the years specified by 
+CMIP6, except for \textit{piControl}.  In most cases these are also the years used for analysis, but some 
+figures use shorter time periods, see Figure captions for details.  }
     \begin{tabular}{*{4}{c}}

### 2020-11-03 Silvers_cfmip_MISR_cloudtable.tex

@@
   \subfloat{
-  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_glbmn.eps}}
+  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_glbmn.eps}}
 %\end{subfigure}
   \subfloat{
-  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_sh_30t60.eps}}
+  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_sh_30t60.eps}}
   \subfloat{
-  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_pm30.eps}}
+  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_pm30.eps}}
 \subfloat{
-  \includegraphics[width=0.2\linewidth]{cfmipfigs/cloud_table_misr_am4_nh_30t60.eps}}
+  \includegraphics[width=0.2\linewidth]{/Users/silvers/code/silversCFMIP/cloud_table_misrV7_am4_nh_30t60.eps}}
 \end{figure}

### 2020-11-03 Silvers_cfmip_SinglePanelFig.tex

--- 2020-04-24 Silvers_cfmip_CRE_SinglePanel.tex
@@
   \centering
-  \begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\linewidth]{cfmipfigs/CRE_net_ceres_cfmipExps.eps}
+  \begin{subfigure}{0.31\textwidth}
+    \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_climo-eps-converted-to.pdf}
 \end{subfigure}
-\begin{subfigure}{0.48\textwidth}
-  \includegraphics[width=\linewidth]{cfmipfigs/CRE_SWonly_feedback_amip.eps}
+\begin{subfigure}{0.31\textwidth}
+  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_vs_piC-eps-converted-to.pdf}
+\end{subfigure}
+\begin{subfigure}{0.31\textwidth}
+  \includegraphics[width=\linewidth]{/Users/silvers/Research/cfmip_paper/cfmip_cf_vs_amip-eps-converted-to.pdf}
 \end{subfigure}

### 2020-11-03 Silvers_cfmip_draft.tex

@@
 \geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
-%\geometry{landscape}                		% Activate for for rotated page geometry
-%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
 \usepackage{graphicx}				% Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
@@
 \usepackage{epstopdf}
-%\usepackage{pdflatex}
-%\usepackage{epsfig}
 
@@
 \begin{abstract}
-The newest atmospheric climate model at GFDL, AM4, succeeded at significantly reducing the TOA radiative flux biases as compared to CERES observations.
-Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs (Cess warming experiments), the corresponding coupled climate model, CM4, has high transient and equilibrium climate sensitivities.
+Clouds observed from multiple satellites are compared to the clouds simulated by GFDL's new AM4 climate model.  
+The new atmospheric climate model succeeded at significantly reducing the TOA radiative flux biases as compared 
+to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs 
+(Cess-type warming experiments), the corresponding coupled climate model, CM4, has high transient and 
+equilibrium climate sensitivities.
 
@@
 
-%\section{Key Questions}
-
 \textbf{Key Points}
@@
   \item{Too few clouds are simulated by AM4.0 at high, middle, and low-levels, as compared to observations from CALIPSO.}
+  \item{AM4.0 low-level clouds have a negative bias (relative to MISR) that is larger for thin clouds, relative to thick.}
   \item{Various configurations of a single global climate model lead to climate sensitivities that range from 2.1K (Cess) to 
@@
 \section{Introduction}
+
+% thoughts from Zhao et al. 2018 part 1, section 4
+% Attention to the observed TOA radiative fluxes were given a high priority during the development of AM4.0 first 
+% of the relatively high confidence in the observations, and second because it was anticipated that these fluxes
+% are an important component in the coupled simulations of CM4.0.   Figure 2 shows that AM4.0 does a better 
+% job simulating RLUT and RSUT than any other of the compared CMIP5 models.   Not only was the global 
+% mean bias of (-0.77 W/m2) an improvement over AM3 and AM2.1 (-4.11 and -3.16 W/m2), but the spatial pattern 
+% was improved over almost the entire world ocean.   Fluxes at the TOA for AM4.0 largely corrected over reflection
+% throughout most of the oceans and an over absorption of solar radiation in the Southern Hemisphere ocean 
+% south of ~60 degrees.
+
+From Poster
+It has been known for decades that  the spread of cloud feedbacks among models contributes to a large portion of the spread in climate sensitivity among those same models (Cess et al., 1989; Bony and Dufresne, 2005).
+It also now clear that the climate sensitivity estimated from constant temperature perturbation experiments is not a good indicator of the climate sensitivity that is estimated from regression techniques of abrupt 4xCO2 warming experiments (e.g.
+Andrews et al., 2012), and that both of these measures of sensitivity underestimate the equilibrium sensitivity that is attained when a coupled climate model reaches equilibrium after multiple millennia (Paynter et al., 2018).
+
+Variation of the climate sensitivity within individual models has been tied to the influence of particular surface temperature patterns.
+This work assesses the fidelity of the clouds in AM4.0/CM4.0 with observations and compares clouds from experiments with differing sensitivities.
+end from Poster
 
@@
 % figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
-  \includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
-  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
-  \label{fig:clt_isccp_calipso}
-\end{figure}
-
-\begin{figure}
-% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
   \includegraphics[width=0.95\columnwidth]{/Users/silvers/Research/cfmip_paper/cf_misr_cldfrac_allheights.eps}
-  \caption{Observed and modeled clouds.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
+  \caption{Observed and modeled clouds for all heights.  Clouds shown are divided into thick (optical depth between 3.6 and 23) 
   and thin (optical depth between 0.3 and 3.6) 
   clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were 
-  derived with the MISR simulator.  Data from all vertical levels is used.}
+  derived with the MISR simulator.  Mean cloud fraction values for MISR 
+  (AM4) are 32\% (24\%) for thick clouds and 22\% (12\%) for thin clouds.}
   \label{fig:misr}
@@
   clouds.  The observations (bottom) are from the MISR satellite (2000-2013) and the modeled clouds (top) were derived 
-  with the MISR simulator (amip experiment).}
+  with the MISR simulator (amip experiment). Mean cloud fraction values for MISR 
+  (AM4) are 21\% (17\%) for thick clouds and 17\% (6\%) for thin clouds}
   \label{fig:calipso_sim_vs_mod}
@@
 
+\begin{figure}
+% figure generated with calip25_isccp_am4_totcld.ncl, figurenumber = 1
+  \includegraphics[width=0.75\columnwidth]{cfmipfigs/ISCCP_CALIPSO_clt_correctedBiasPattern_nogrid.eps}
+  %\includegraphics[width=0.75\columnwidth]{cfmipfigs/clt_isccp_calipso_am4_4pan.eps}
+  \caption{Comparison of total cloud fraction from AM4 with two observational data sets: ISCCP (left) and CALIPSO (right).}
+  \label{fig:clt_isccp_calipso}
+\end{figure}
+
 The MISR satellite is thought to provide good estimates of low-level clouds heights and amounts.  For this reason
@@
 
+\begin{figure}
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_clim_amip_hist.eps}
+  \caption{Cloud fraction between 1979-2014 for the amip and historical experiments.  The CALIPSO
+  observations range from January 2007 through December 2016.  Note that the regions poleward of
+  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  It is 
+  also interesting that having an interactive surface only leads to a minimally improved CF bias.}
+  \label{fig:calipso_amip_comparison}
+\end{figure}
+
 The recent model development efforts at GFDL, and participation in CMIP6/CFMIP have provided a 
@@
 spanning a wide range of model configurations.  The model types include (should we include any of the
-efforts from the RCE or Walker Cell configurations?) an Aquaplanet, and AGCM, 
-and a AOGCM.  When combined with a variety of boundary conditions this creates a hierarchy of
-models which are all derived from or dependent on the same atmospheric code base (AM4.0).  It is a 
-bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.      
+efforts from the RCE or Walker Cell configurations?) an Aquaplanet, an AGCM (AM4.0), 
+and an AOGCM (CM4.0).  When combined with a variety of boundary conditions this creates a hierarchy of
+models which are all derived from or dependent on the same atmospheric code base (AM4.0).  
+%It is a bit like a group of siblings sharing the same gene pool but at various stages of intelligence or education.      
 Our hypothesis for this study is that the large range of climate sensitivities that are found within this 
 group of models is in large part due to variations in the clouds (both their climatology and their feedbacks).
-The clouds in these simulations are responding to a variety of different conditions including different
+The clouds in these simulations respond to a variety of different conditions including different
 patterns of prescribed SST, the presence or absence of land/ice, and in the case of the aquaplanet
-experiments, a lack of cloud-aerosol interactions which is present in the amip and coupled experiments.
+experiments, a lack of cloud-aerosol interactions which are present in the amip and coupled experiments.
+
+Due to a combination of changing computing power and differing priorities, the sensitivity of Earth's climate to 
+perturbations has been estimated in many different ways.  Three very common methods are documented 
+here.  First, the climate sensitivity can be estimated from the change in radiative flux at the top of the 
+atmosphere after imposing a prescribed change of surface temperature.  This method of using SST changes
+as a proxy for climate change was pioneered by Robert Cess (e.g. 1989, 1990).  Second, the climate
+sensitivity can be estimated from a fully coupled experiment in which the CO2 concentration is instantaneously 
+quadrupled relative to the pre-Industrial values.  Linear regression can then be used to estimate the 
+sensitivity of the model (Gregory et al., 2004, Andrews we al., 2012, IPCC).  This is the origin of the 
+so-called equilibrium climate sensitivity in Andrews et al., 2012 and the IPCC.  Third, the climate sensitivity
+can be computed from simply measuring the change of surface temperature after the CO2 concentration
+has been doubled in a fully coupled climate model following an increase of 1\% per year in the CO2 concentration.
+This defines the transient climate response.
 
@@
 of the climate system to a perturbation such as increasing concentrations of carbon dioxide.  The three 
-experiments are the historical simulation (historical: 1850-2014),  the abrupt quadroupling of CO2 concentration 
- (abrupt-4xCO2: 150 years), and the experiment in which the concentration of CO2 is increased by 1\% 
- per year from the pre-industrial until the concentration is doubled (1pctCO2: 150 years, doubling at year 70).  
+experiments are the historical simulation (historical: 1850-2014),  the abrupt quadroupling of 
+$\rm{CO}_2$ concentration ($abrupt-4xCO2$: 300 years), and the experiment in which the 
+concentration of $\rm{CO}_2$ is increased by 1\% 
+ per year from the pre-industrial value of 284.262 ppm(?units?) until the concentration is doubled ($1pctCO2$: 150 years, doubling at year 70).  
 The historical simulation is our best attempt at using our coupled GCM to reproduce the historical 
 record found in observations.  This has frequently been used to estimate the climate sensitivity using the 
-energy budget method (Otto et al., 2013, Armour et al., Andrews et al., Winton et al., 2020).  The abrupt-4xCO2
+energy budget method (Otto et al., 2013, Armour et al., Andrews et al., Winton et al., 2020).  The 
+$abrupt-4xCO2$
 experiment has been utilized by the IPCC to derive measures ECS among the CMIP5 and CMIP6 models
@@
 150 years of simulation (Gregory et al., 2004; Andrews et al., 2012).  In contrast to the abrupt change of 
-CO2 concentration, the 1pctCO2 experiment allows the Earth system to adjust to slowly increasing concentrations.  
-The sensitivity taken from this experiment is argued to be more relevant for an assessment of the 
-near term impact of the climate change because it is calculated based on a doubling of CO2.
+$\rm{CO}_2$ concentration, the $1pctCO2$ experiment allows the Earth system to adjust to 
+a 1 \% per year increasing of $\rm{CO}_2$ concentration until they are doubled relative to the 
+pre-Industrial values.  The sensitivity at this point is defined 
+as the Transient Climate Response (TCR).  The TCR is the relevant measure of climate sensitivity for 
+near term climate change because it is expected that the atmospheric concentrations of $\rm{CO}_2$ 
+will reach (insert 2xCO2 value) around the middle of this century.
 
@@
 
-\begin{figure}
-  \includegraphics[width=0.86\columnwidth]{cfmipfigs/cf_clim_amip_hist.eps}
-  \caption{Cloud fraction between 1979-2014 for the amip and historical experiments.  The CALIPSO
-  observations range from January 2007 through December 2016.  Note that the regions poleward of
-  50 degrees are the only regions in which AM4/CM4 produce more clouds than observed.  It is 
-  also interesting that having an interactive surface only leads to a minimally improved CF bias.}
-  \label{fig:calipso_amip_comparison}
-\end{figure}
-
 Plotting the cloud fields as a function of latitude and height highlights some of the similarities and differences 
-between the various experiments.  In general the clouds in the amip and historical simulations are similar to 
+between the various experiments.  In general the clouds in the $amip$ and historical simulations are similar to 
 each other, as we would expect.  The differences between the clouds of these experiments are due to the 
@@
 
-% Beta feedback??  relavent?
-Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
-changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
-low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
-model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
-masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.
-
-The cloud radiative effect (CRE) is computed as the difference between the all-sky and clear-sky TOA fluxes.
+%% Beta feedback??  relavent?
+%Brient and Bony (2012) proposed what they call the $\beta$ feedback as a way to quantify whether or not ' models have 
+%changes in low-cloud cloud radiative effects which are proportional to the strength of the cloud radiative effects of their
+%low clouds.'  See $\it{Stevens etal, Cookie Overview}$ for details.   That paper asks the question of whether single 
+%model relationships between low-cloud amounts and the sensitivity of low clouds to warming can be 
+%masked by changes in multi-model ensembles.  This should be checked for the GFDL model in this paper.  
+%
+%The cloud radiative effect (CRE) is computed as the difference between the all-sky and clear-sky TOA fluxes.
 
@@
 \begin{center}
-\caption{Global mean radiative feedbacks.  The cloud radiative effect (CRE) is computed as
+\caption{Global mean radiative feedbacks ($\rm{W\, m^{-1} K^{-1}}$).  The cloud radiative effect (CRE) is computed as
  the clear sky minus all sky flux. The values for the Abrupt 4xCO2 experiment
@@
 
+The previous section showed that the AM4.0 amip simulations underestimates clouds relative to the CALIPSO observations.  
+Simulations over the historical period with the fully coupled model do not improve on this bias, and in the case of the abrupt
+4xCO2 and gradual 1\% CO2 experiments the bias is worse at almost all latitudes except at 20 degrees south.  The two coupled
+warming experiments (abrupt and ramp) have some interesting differences from both the \textit{amip} and the
+ \textit{historical} simulations.   These warming experiments have a distinct peak (about 5\%) of low-level cloud fraction at about 20N that 
+ both \textit{amip} and \textit{historical} lack (\textit{historical} does have a small but less distinct peak).  Additionally, 
+ while the low-level clouds of the \textit{amip} and \textit{historical} experiments are almost identical between 10-60N, the 
+ \textit{abrupt} and \textit{ramp} experiments show a large decrease of cloud fraction between about 30-70N.  Is this decrease
+ of low-level cloud in the NH responsible for a stronger sw cloud feedback relative to the amip p4K and historical simulations?  Of the 
+ two experiments, the abrupt has the least amount of low-level cloud.  Does it also then have the strongest/largest SW CRE?  
+ When comparing these experiments to the CERES0-EBAF observations from the observational period the \textit{abrupt} and 
+ \textit{ramp} experiments match the CERES-EBAF CRE better than the amip or historical experiments.  All of the AM4.0 
+ simulations shown here compare best with the CERES-EBAF v2.8.  This is likely because this is the version of the data that 
+ was used as a reference during the model development.  For comparison we also show the CERES-EBAF v4.1 data.  Although 
+ differences between the two versions are clear, the AM4.0 models compare relatively well to both.  The differences between 
+ the two observational version are mostly contained to the latitudes between +/- 30.  This excellent agreement with observations 
+ of the CRE in the NH for the warming experiments was surprising, but does not in general indicate better observational 
+ agreement of the warming experiments relative to the \textit{historical} and \textit{amip} experiments.   These warming 
+ experiments have a very strong arctic and southern ocean response that differs significantly from the historical observations 
+ and simulations.   As these are signature CRE changes in a warming climate it is not surprising that they are not 
+ present in the historical data.
+
+\begin{figure}
+  \includegraphics[width=0.86\columnwidth]{cfmipfigs/meridional_CRE_CERES2p8.eps}
+  \caption{.}
+  \label{fig:CRE_multiexperiments_ceres}
+\end{figure}
+
 \section{What are we learning?}

### 2020-11-03 Silvers_cfmip.tex
rename Silvers_cfmip_CRE_SinglePanel.tex -> Silvers_cfmip_CRE_3Pan_SingleFig.tex and include minor changes to Silvers_cfmip.tex

@@
 
+\subsection{Overall assessment of AM4 and CM4? Here or beginning of next section?}
+
+\subsection{data and experiments}
+
 The comparisons with observations are made mostly with the \textit{amip} experiment that serves as one of the DECK CMIP6 
@@
 that AM4.0 underestimates the liquid droplet number over oceans and downwind of the aerosol emission 
-sources.   
+sources.    \textcolor{red}{Could be a good place to state phase related findings and results from Fan et al.}
 Comparisons of AM4.0 with observations from ISCCP and MODIS in Z18a (their Figure 10) showed an underestimate of 
@@
 
+\textit{should this go in the section that is a general summary of AM4/CM4?}
+
 Clouds have an enormous regional impact on the climate and ecology at the surface of the Earth.   Precipitation 
@@
 After the AM4.0 development was frozen and the process of documentation 
-was underway, the CERES-EBAF data version 4.1 was released.  When comparing the same 
+was underway, the CERES-EBAF data version 4.1 was released (Loeb et al., 2018).  When comparing the same 
 AM4.0 \textit{amip} experiment to the 
@@
 The most recent generation of models developed at NOAA's GFDL that have participated in CMIP6 have a large range of climate 
-sensitivities (possibly cite Winton et al., Dunne et al.) depending on the experiment of interest and the method used for 
-calculation.
+sensitivities (possibly cite Winton et al., Dunne et al.) depending on the experiment of interest, the method used for 
+calculation, and the particular model configuration.
 One way of quantifying this sensitivity is with the climate feedback parameter, which, for the subset of GFDL models and CMIP6 experiments studied in this paper, varies between -0.46 and -2.1 $\rm{W m^{-2}K^{-1}}$ (Table 1).
@@
 of the surface air temperature ($T; K$).  
-Rather than using the linear regression method to calculate the ECS from the \textit{abrupt-4xCO$_2$} experiment, or calculating the 
-traditional TCR value from the \textit{1pctCO2} experiment we use the differences in the global mean energy budget between control 
+Rather than using the linear regression method to calculate the ECS from the \textit{abrupt-4xCO$_2$} experiment (ECS of CM4.0 = 34543, Zelinka et al., 2019), or calculating the 
+traditional TCR value from the \textit{1pctCO2} experiment (TCR of CM4.0 = 345, Winton et al., 2020) we use the differences in the global mean energy budget between control 
 periods and the period of interest to calculate the climate feedback parameter as $-\alpha = (F-N)/T$. 
@@
 of the various experiments.  
-However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations.
+However, the range of total feedback parameter among experiments that is due to differences in cloud feedbacks is not as easily connected to particular experimental configurations and requires further investigation.
+One of the aims of this paper is to clarify the role that clouds play in
+these different feedback values.
 
@@
   \includegraphics[width=0.5\columnwidth]{cfmipfigs/Silvers_cfmip_CRE_3Pan_vert.pdf}
-  \caption{The Cloud Radiative Effect (CRE) and CRE feedback of several CMIP6 experiments.  The top panel 
-  shows (black) the CRE from two versions of the CERES-EBAF observations compared to 
-  simulations of CRE using AM4.0 driven by the observed SST (\textit{amip}).  Also 
-  shown in the top panel is the simulated CRE from three fully coupled CM4.0 experiments (\textit{historical} (yrs. 1950-2014),
-  \textit{abrupt-4$\times$CO2} (yrs. 101-150), and \textit{1pctCO2} (yrs. 101-150)).  The middle panel shows an estimate of the 
-  CRE feedback of the data in the top panels, computed by normalized according to the warming of surface air temperature over 
-  the relevant time period.  The bottom panel shows the CRE feedback from four 
-  CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}).  The sign of the \textit{amip-m4K} experiment has 
-  been reversed.}
+  \caption{The observed and modeled Cloud Radiative Effect (CRE) and CRE feedback.  The top panel 
+  shows the CRE from two versions of the CERES-EBAF observations (dashed black, version 2.8; solid black, version 4.1) as well as the CRE from four CMIP6 experiments.
+These include one atmosphere only (\textit{amip}), and three fully coupled (\textit{historical} (yrs.
+1950-2014), \textit{abrupt-4$\times$CO2} (yrs.
+101-150), and \textit{1pctCO2} (yrs.
+101-150)) experiments.
+  The middle panel shows an estimate of the CRE feedback of the experiments in the top panel, computed by normalizing according to the     
+  warming of surface air temperature over the time period indicated in this caption, relative to the CMIP6 \textit{piControl} experiment.  
+  The bottom panel shows the CRE feedback from four CFMIP experiments (\textit{amip-p4K, amip-m4K, amip-future4K, aqua-p4K}), computed relative to the \textit{amip} and \textit{aqua-Control} experiments.
+The sign of the \textit{amip-m4K} experiment has been reversed.}
   \label{fig:CRE_feedback}
@@
 To gain further insight into the sources of differences among the CRE values in Tables  \ref{tab:lambda_AGCM}  and  
-\ref{tab:lambda_AOGCM}  we plot the observed CRE as a function of latitude alongside the CRE from the 
+\ref{tab:lambda_AOGCM}  we plot (Figure \ref{fig:CRE_feedback}) the observed CRE as a function of latitude alongside the CRE from the 
 experiments shown in Table  \ref{tab:lambda_AOGCM}.  Observations from CERES-EBAF are shown for version 
-2.8 (black dashed) and for version 4.1 (black).  During the development of AM4.0 version 2.8 of CERES-EBAF was 
-used extensively \cite{Zhao_etal_2018a}.  The distributions of CRE in warming experiments are not directly comparable 
-to observations from recent periods but rather show how potential changes in the effects of clouds vary with latitude.   
+2.8 (black dashed) and for version 4.1 (black).  
+%During the development of AM4.0 version 2.8 of CERES-EBAF was used extensively \cite{Zhao_etal_2018a}.  
+While the distributions of CRE in warming experiments are not directly comparable to observations from recent periods, they provide context for how potential changes in the effects of clouds could vary with latitude.
 Note the large differences in the arctic and the shift poleward in the SH of the minimum in CRE.
 
-The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback in the three coupled CM4.0 experiments and in the \textit{amip} experiment.
+The middle panel of Figure \ref{fig:CRE_feedback} shows the CRE feedback from three coupled CM4.0 experiments and the \textit{amip} experiment.
 Values shown in Table \ref{tab:lambda_AOGCM} imply that the clouds present in the \textit{1pctCO$_2$} and \textit{abrupt4xCO$_2$} experiments
@@
 \end{figure}
+
+While potentially confusing, we show cloud fraction anomalies computed relative to two different control experiments, \textit{piControl} and \textit{amip}.
+This is important because the cloud feedback values are usually computed relative to these control experiments and we find it instructive to see how the control experiment used can influence the cloud anomalies which are found.
+First, there are many similarities in the cloud anomalies regardless of the control used (e.g.
+Increased upper-level deep tropical and polar clouds, decreased mid-level mid-latitude clouds, and in some cases, decreases of low-level tropical clouds).
+Where the anomalies differ substantively is between the low-level clouds in the high-latitude regions.
+If we take the \textit{amip} experiment to be the one that is closest to the observations, then the bottom center panel shows a different of about 8\% in the cloud fraction between the \textit{amip} and \textit{piControl} experiments between $60-80^\circ$.
+Is this an artifact of sea ice being prescribed in \textit{amip}??
+It seems that the large diffference between the low-level clouds of this region in the amip-like and coupled experiments indicates either a sensitivity to the configuration (sea-ice differences), or the result of SST biases that are created by the coupled models.
+
+The bottom right panel shows very clearly the different responses of clouds to the amip-p4K and amip-future4K experiments.
+The low-level cloud fraction of the amip-p4K and amip-future4K are nearly identical in the NH but are not even the same sign in the SH.
 
@@
 figures use shorter time periods, see Figure captions for details.  }
-    \begin{tabular}{*{4}{c}}
+    \begin{tabular}{*{5}{c}}
     \hline
     \hline
- Experiment & Class & Configuration & Years   \\ \hline
-    \textit{historical}        &   DECK      &  atmosphere \& ocean   &  Jan 1850 -Dec 2014               \\ 
-    \\
-    \textit{abrupt-4xCO$_2$}   & DECK       &  atmosphere \& ocean       & 150 years  \\  
-    \\
-    \textit{1pctCO$_2$}   & DECK        &  atmosphere \& ocean  & 150 years \\  
-    \\
-    \textit{piControl}  & DECK   &  atmosphere \& ocean  &   years 250-350  \\  
-    \\
-    \textit{amip}  & DECK \& CFMIP   &  atmosphere   & Jan 1979 - Dec 2014  \\  
-    \\
-    \textit{amip-p4K}  & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014  \\ 
-    \textit{amip-m4K}   & CFMIP       &  atmosphere   & Jan 1979 - Dec 2014 \\ 
-    \textit{amip-future4K}  & CFMIP  & atmosphere & Jan 1979 - Dec 2014 \\
-    \textit{aqua-control}        & CFMIP  & atmosphere  & 10 years \\
-    \textit{aqua-p4K}  & CFMIP    & atmosphere  &  10 years \\ \hline
+ Experiment & Class & Configuration & Years  &   Data doi  \\ \hline
+    \textit{historical}        &   DECK      &  CM4.0: AOGCM   &  Jan 1850 -Dec 2014               \\ 
+    \\
+    \textit{abrupt-4xCO$_2$}   & DECK       &  CM4.0: AOGCM       & 150 years  \\  
+    \\
+    \textit{1pctCO$_2$}   & DECK        &  CM4.0: AOGCM  & 150 years \\  
+    \\
+    \textit{piControl}  & DECK   &  CM4.0: AOGCM  &   years 250-350  \\  
+    \\
+    \textit{amip}  & DECK/CFMIP   &  AM4.0: AGCM   & Jan 1979 - Dec 2014  \\  
+    \\
+    \textit{amip-p4K}  & CFMIP       &  AM4.0: AGCM   & Jan 1979 - Dec 2014  & 10.22033/ESGF/CMIP6.8508  \\ 
+    \textit{amip-m4K}   & CFMIP       &  AM4.0: AGCM   & Jan 1979 - Dec 2014 \\ 
+    \textit{amip-future4K}  & CFMIP  & AM4.0: AGCM & Jan 1979 - Dec 2014 \\
+    \textit{aqua-control}        & CFMIP  & AM4.0: Aqua  & 10 years \\
+    \textit{aqua-p4K}  & CFMIP    & AM4.0: Aqua &  10 years \\ \hline
 

### 2020-11-18 Silvers_cfmip.tex
modify abstract for the U Wy seminar

@@
 \begin{abstract}
-Observations of cloud fraction from multiple satellites are compared to the clouds simulated by 
-GFDL's new AM4 climate model.  
-The new atmospheric climate model succeeded at significantly reducing the TOA radiative flux biases as compared 
-to CERES observations.  Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs 
-(Cess-type warming experiments), the corresponding coupled climate model, CM4, has high transient and 
-equilibrium climate sensitivities.
-
-A systematic picture is presented of the modeled clouds across a hierarchy of model configurations which utilize 
-the AM4 and CM4 climate models.  This hierarchy includes the CFMIP Aquaplanet and \textit{amip} experiments, 
-fully coupled model experiments as well as additional \textit{amip}-like experiments with particular SST patterns.  
-We demonstrate the large range of sensitivities that are possible from a single parent atmospheric climate model.   
+
+A systematic picture will be presented of the simulated clouds across a hierarchy of CMIP6 model configurations  that have been run with 
+the AM4 and CM4 climate models from GFDL.
+This hierarchy is composed of both CMIP6 and CFMIP (Cloud Feedback Model Intercomparison Project) experiments that include an ocean covered planet, atmosphere/land only Earth-like experiments, and fully coupled model experiments both of the historical era and future warming scenarios (\textit{aqua-control, amip, historical, amip-p4K, amip-future4K, abrupt-4xCO2}, and \textit{1pctCO2}).
+We demonstrate the large range of climate sensitivities that can result from a single parent atmospheric climate model.   
+Despite a relatively low top-of-atmosphere sensitivity to uniform warming of SSTs 
+(Cess-type warming experiments), the corresponding coupled climate model, CM4, has high transient (2 K) and 
+equilibrium climate sensitivities (~ 5K).  Cloud feedbacks play a large role in setting these sensitivities.  
 Looking at the global mean radiative feedbacks across the different model configurations as well as in the context 
 of CMIP5 and CMIP6 models will allow us to assess to what extent the cloud feedbacks in the idealized 
-experiments relate to the fully coupled experiments and to observed clouds.  
+experiments relate to the fully coupled experiments and to the clouds observed in Earth's atmosphere.
+
+Observations of cloud fraction from multiple satellite products (CALIPSO, MISR, MODIS, and ISCCP)  are compared to the clouds simulated by the AM4 and CM4 climate models.  
+The AM4 and CM4 climate models succeeded at significantly reducing the TOA radiative flux biases as compared 
+to CERES-EBAF observations.  Partly as a result of this realistic representation of the TOA energetics the coupled model
+improved the representation of precipitation, reduced the Intertropical Convergence Zone bias, and produces an excellent El Nino-Southern Oscillation.
+However, we find large biases in cloud fraction relative to observations across wide regions of the globe and throughout the depth of the atmosphere.
+
+I will discuss some of the challenges that are inherent to improving cloud simulations in GCMs.
+This work points to the need for drawing dependable cloud constraints from the observations we have.
+The important challenge will then be to implement the cloud constraints while continuing to maintain a realistic representation of the radiative fluxes at the TOA of global models.
+
 \end{abstract}
@@
     \\
-    $\Delta \rm{T}_s$     &     1.3     & 0.8        &  4.3           & 5.7     &   3.90 (7.8?)        &   4.60 (9.2?)         \\  \hline
+    $\Delta \rm{T}_s$     &     1.3     & 0.8        &  4.3           & 5.7     &   3.90 (7.8)        &   4.60 (9.2)         \\  \hline
 
